### 2020-03-02 ResearchProposal/main.tex
first commit

\documentclass{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage[displaymath, mathlines]{lineno}
\usepackage{graphicx}
\usepackage[numbers]{natbib}

 \bibliographystyle{ieeetr}

%\renewcommand\linenumberfont{\normalfont\small\sffamily}
%\linenumbers
\modulolinenumbers[2]
\geometry{a4paper, total={170mm,252mm},left=20mm,top=20mm,headheight=12pt}
\linespread{1.5}

\title{Research Proposal:\\  Can Cultural Transmission Explain The Evolution of Cooperative Behavior}
\author{Dor Cohen \\ cohensdor@gmail.com \and Yoav Ram \\ yoav@yoavram.com}
\date{School of Computer Science, IDC Herzliya\\ \today}

\begin{document}
\maketitle

\section*{Introduction}
Cooperative behavior is interesting in evolutionary view. The theory of evolution is based on the the struggle of the individual to survive and reproduce. Natural selection favours those with the highest fitness and therefore, their reproduction will be the most successful. However, cooperative behavior can many times harm the individual's fitness and increase the fitness of its competitor \cite{axelrod1981evolution}. Yet cooperative behavior is a widespread phenomenon and occurs in other animals besides humans \cite{dugatkin1997cooperation}, for example in rats \cite{rice1962altruism} and birds \cite{krams2008experimental}.
Therefore, the evolution of cooperative behavior is still an interesting important open question.
\\Cultural evolution is an evolutionary theory of social change. Culture has significant impact on the behavior of animals \cite{bonner2018evolution} and humans \cite{ihara2004cultural,jeong2018bronze}. Individual can acquire new behavior from another individual in its social group  through learning or other modes of cultural transmission \cite{richerson2008not}.
\textbf{The goal of this research} is to determine to what extent cultural transmission can explain the evolution of cooperative behavior.
\subsection*{Theories for Evolution of Cooperation}
Three major theories have been proposed to explain the evolution of cooperative behavior.
\\\textbf{Kin selection}, proposing that natural selection can favour cooperative behaviour between kin. The importance of relatedness to the evolution of cooperation and altruism was shown by Hamilton \cite{hamilton1964genetical}. According to Hamilton, kin selection causes allele to increase in frequency when the genetic relatedness $r$ of a recipient to an actor multiplied by the benefit $b$ to the recipient is greater than the reproductive cost $c$ to the actor. This is also known as Hamilton's Rule:
\begin{equation} \label{hamiltonrule}
c<rb
\end{equation}
There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
It has been suggested that kin selection to explain the cooperative behaviour of eusocial insects like the honey bee.
The most significant argument against kin selection is that cooperation can evolve with zero relatedness \cite{wilson2005kin}. This makes Hamilton's rule incomplete according to Wilson \cite{wilson2005kin}. Foster et al. \cite{foster2006kin} reject this claim. They argue that altruism without relatedness can not evolve. They refer us to Hamilton who claimed that relatedness can arise without recent common ancestry. 
Wilson also criticises kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions. On the other hand, Foster et al. \cite{foster2006kin} argue that kin selection does not ignore ecology. Hamilton’s rule shows
that environmental factors causing a high benefit: cost ratio will favour cooperation. \\\\\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation. In \textit{direct reciprocity} there are a repeated encounters between the same two individuals. In every encounter, each player has a choice between cooperation and defection. If I cooperate now, you may cooperate later. Hence, it may pay off to cooperate.
This game-theoretic framework is known as the repeated Prisoner's Dilemma. 
%A well known strategy to play this game is called  'tit-for-tat'. This strategy always starts with a cooperation, then it does whatever the other player has done in the previous round: a cooperation for a cooperation, a defection for a defection. There a unlimited number of possible strategies to play this game. However, 
Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit. 
\begin{equation} \label{reciprocity}
c<bw
\end{equation}
Direct reciprocity assumes that both players are in a position to cooperate. Direct reciprocity can not explain cooperation in asymmetric interactions. In humans, such interactions happen often, for example humans often donate money. 
\textit{Indirect reciprocity} has been suggested to explain this behavior. 
Nowak \cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money. The money that "fuels the engines" of indirect reciprocity is reputation. 
\\However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs. 
\\\\\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level. A common model for group selection work as is: the population is divided into groups. In each groups there are cooperators, which help to other group members and defectors which do not help. 
Individuals reproduce proportional to their fitness. Offspring are added to the same group.
If a group reaches a certain size it can split to two groups. A group that grow faster will split more often. Groups of cooperators are growing faster than group of defectors.
Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
\begin{equation} \label{groupselection}
\frac{b}{c}>1+\frac{n}{m}
\end{equation}
The group selection was criticized by biologists advocate gene-centered view of evolution. Group selection has been criticized due to the fact that the trait like cooperation evolves in the total population. According to natural selection, if cooperation took over the population it must have better fitness. However, in group selection the fitness of cooperator in the individual level is lower. The fact that a trait with a lower fitness took over the population is a contradiction. Eldar et al. \cite{eldakar2011eight} reject this argument. They believe that this argument is a tautology and does not qualify as an argument against group selection. The distinction between individual and group selection requires a comparison of fitness differentials within and among groups in a multi group population. When a trait is evolve by group selection, despite the fact that it has lower fitness within the group, it has a better fit, all thing considered. 
\\\\All three theories mentioned above assume that cooperation is genetically determined. This raise the question, is it possible that cooperation is determined by environmental or social influences. Recent work by Lewin-Epstein at el.\cite{lewin2017microbes} may answer this question. 
Lewin-Epstein at el. \cite{lewin2017microbes} have proposed a different model that can explain the evolution of  cooperative behavior. They have hypothesized that microbes that manipulate their hosts to act altruistically could be favoured by selection, and may play a role in the widespread occurrence of cooperative behavior. Indeed, it has been shown that microbes can mediate behavioural changes in their hosts\cite{poulin2010parasite}\cite{dobson1988population}. Therefore, natural selection on microbes may favour manipulation of the host so that it cooperates with others. Microbes can be transmitted \textbf{horizontally} from one host to another during host interactions. Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donating host, even when the two hosts are unrelated \cite{lewin2017microbes}. Microbes can also transfer vertically, from parent to
offspring. As a result, a microbe that induces its host to help another host, increases the other host survival or reproduction, thus increasing the vertical transmission (v) of the microbes of the receiving individual. Kin selection among microbes could therefore favour microbes that induce cooperative behaviour in their hosts, thereby increasing the transmission of their microbial kin.
\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible \cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behaviour of their hosts.

\subsection*{A Theory of Cultural Evolution of Cooperation}
From Lewin-Epstein at el. \cite{lewin2017microbes} we learn that \textbf{non-vertical} transmission could explain the evolution of cooperative behavior. 
Non-vertical transmission could be either a horizontal or oblique. Horizontal transmission is a transmission between individuals from the same generation. Oblique transmission is a transmission from an adult to a child. 
Evolution under either of these transmission models is expected to be more rapid than under pure vertical transmission \cite{ram2018evolution}.   
Here we suggest a model in which behavior changes are caused by cultural and social transmissions. In our model the social transmission that affects individual behavior can be learned during social interactions. For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future. Surprisingly, much of the analysis made by Lewin-Epstein at el. \cite{lewin2017microbes} can be applied to cultural transmission, because learning can be modeled as infectious agent that transmits the cooperative behavior \cite{cavalli1981cultural}.

We \textbf{hypothesize} that non-vertical transmission can explain the evolution of cooperation. To test this hypothesis we are going to use cultural evolution models that include non-vertical transmission mechanism. We will use both mathematical analysis to investigate the models, and run simulations for more complex scenarios.

\section*{Research Proposal}
The research schedule can be found in appendix B. 
\subsection*{Aim 1} Our first aim is to determine to what extent non-vertical transmission can explain the evolution of cooperation in fully mixed population with prisoner's dilemma payoff.
We will develop a cultural evolution model and determine under which conditions cooperative behavior could prosper. The model assumes fully mixed population and individuals that interact in pairs with prisoner's dilemma payoff. The payoff matrix is shown in figure \ref{fig:payoff}. 
\\In our model We consider a population of asexual individuals. We assume that cooperative behavior is a dichotomous cultural trait with phenotypes A and B.  Individuals of type A will always act altruistically and individuals of type B will not cooperate. An individual who cooperates will pay a cost $0<c<1$ and the recipient gains a benefit $b$ where $b>c$.
After each interaction, each individual will try to learn from its interaction partner with probability $\alpha$, and with probability $1-\alpha$ it will try to learn from random individual within the population as shown in table \ref{fig:payoff}. 
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.5]{payoff.pdf}
  \caption{Payoff Matrix}
  \label{fig:payoff}
\end{figure}

The transmission from type A will be successful with probability $T_a$ and from type B with probability $T_b$.
In the model, in each generation each individual is having n interactions and then a reproduction is occurring according to each individual fitness and phenotypes A and B are vertically transmitted from parent to offspring. In general the vertical transition can be imperfect which means that with probability $v$ offspring inherits its parent’s phenotype and with probability $1-v$ it inherits a phenotype from its parent population. After reproduction the offspring replace the parent generation.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=1]{figure.pdf}
  \caption{Horizontal Transmission}
  \label{fig:figure}
\end{figure}

We define $p$ to be the frequency of newborn with phenotype A and $q=1-p$ to be the frequency of newborn with phenotype B. In addition, we define $\hat{p},\hat{q}$ to be the frequency of phenotypes A and B before reproduction and after interaction.

\begin{equation} \label{d}
\hat{p} = p^2\left[1-\left(1-\alpha\right)qT_B\right] + pq\alpha T_A + pq\alpha(1-T_B) + pq(1-\alpha)[pT_A+q(1-T_B)]
\end{equation}

The mean fitness of the population in each generation is:
\begin{equation} \label{d}
\overline{\omega} = 1 + p(b-c)
\end{equation}
As shown in eq. \eqref{vt} the probability to get a offspring with phenotype B given that its parent is of phenotype A is equal probability of imperfect vertical transmission times the proportion of A in the population. 
\begin{equation} \label{vt}
(1-v)\hat{q}
\end{equation}

Given p the frequency of phenotype A at the current generation, we are interested in frequency of A in the next generation. We have three possible interaction types A interacts with A, A interacts with B and B interacts with B.

We focus on the frequency of phenotype A. We define $x_{AA}$ to be the frequency of offspring that their parent was of phenotype A and interacted with another individual of type A. Similarly we define $x_{AB}, \, x_{BA}, \, x_{BB}$.

\begin{equation} 
\begin{split}\label{aim1model0}
 x_{AA} &= \frac{1}{\overline{\omega}}p^2(1+b-c)[(1-(1-\alpha)T_Bq)(1-(1-v)\hat{q})+(1-\alpha)T_Bq(1-v)\hat{p}]\\
 x_{AB} &= \frac{1}{\overline{\omega}}pq(1-c)[(1-(1-\alpha)T_Bq-\alpha T_B)(1-(1-v)\hat{q}) \\ &+ (\alpha T_B+(1-\alpha)T_Bq)(1-v)\hat{p}]\\
 x_{BA} &= \frac{1}{\overline{\omega}}pq(1+b)[(1-(1-\alpha)T_Ap-\alpha T_A)((1-v)\hat{p})\\ & +(\alpha T_A+(1-\alpha)T_A p)(1-(1-v)\hat{q})] \\
 x_{BB} &= \frac{1}{\overline{\omega}}q^2[(1-(1-\alpha)T_Ap)(1-v)\hat{p})+(1-\alpha)T_Ap(1-(1-v)\hat{q})]
\end{split}
\end{equation}
We define p' to be the frequency of individuals of phenotype A in the next generation.
\begin{equation} 
\begin{split}\label{aim1model}
& p' = x_{AA} + x_{AB} + x_{BA} + x_{BB}
\end{split}
\end{equation}

The question we are interested in is under what conditions the cooperative behavior represented by phenotype A will not become extinct. In order to do that we will investigate when $p' > p$.
We can make a simplify assumption that vertical transmission is perfect, $v=1$ and then we will be able to solve the inequation more easily. Under this assumption equations \eqref{aim1model0},\eqref{aim1model} become

\begin{equation} 
\begin{split}\label{modeleq}
p' =& \frac{1}{\overline{\omega}} \{ p^2(1+b-c)[1-(1-\alpha)T_Bq] + pq(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
&+ pq(1+b)[\alpha T_A+(1-\alpha)T_Ap)] + q^2(1-\alpha)T_Ap\}.
\end{split}
\end{equation}
However, we are also interested when this assumption does not apply, meaning that $v<1$. In this, We will to run numerical simulation in order to better understand under what conditions cooperative behavior will take over the population. 
\\\textbf{\underline{Preliminary Results}}
We have preliminary result only when $v=1$.
\\We get that $p'>p$ when (see appendix A):
\begin{equation} 
\begin{split} \label{result0}
 c(1-T_B) < & \,  bqT_B(1-\alpha) - bqT_A(1-\alpha) + (T_A-T_B) + b(T_A - T_B) + \alpha bT_B
\end{split}
\end{equation}
We want to investigate few special cases:
\\\underline{Special case 1 - $T_A = T_B = T$:} then, eq. \eqref{result0} becomes:
\begin{equation}
\begin{split} \label{result}
 \frac{1-T}{\alpha T}< \frac{b}{c}
\end{split}
\end{equation}
Therefore, cooperative behavior will take over the population when eq. \eqref{result} is satisfied.  
\\\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
\\Eq. \eqref{result0} becomes:
\begin{equation} 
\begin{split} \label{result3}
c(1-T_B)  < & \, T_A -T_B +b(T_A-T_B)
\end{split}
\end{equation}
Therefore, cooperative behavior will take over the population when eq. \eqref{result3} is satisfied. 
This result is in accordance with the result presented by Lewin-Epstein at el. \cite{Ohad}. 
\\\underline{Special case 3 - $\alpha = 0$:} in this case horizontal transmission can not occur as a result of interaction.  
Then, eq. \eqref{result0} becomes:
\begin{equation} 
\begin{split} \label{result4}
0 < & \,  - bq(1-T_B)- bT_B-c(1-T_B)-T_B
\end {split}
\end{equation}
Which is always false because all of the elements are negative. Therefore, cooperation will eventually disappear from population.
\\Those are the results we have so far. However, there is a still work need to be done. \\
We will analyze the equilibrium points in this model. We know that $p=1$ is an equilibrium point because if the all individuals in the population are cooperators then in next generation all individual will be cooperator as well. Same for $p=0$. We will check if there are any more equilibrium points. For each equilibrium point we will determine whether it is stable equilibrium or not. 
\\So far, we assumed that $v=1$. We believe it will be interesting to test the effect of oblique transmission ($v\neq 1$) since oblique transmission is common in cultural evolution models. Therefore, we are planning to simulations to investigate the case when $v\neq 1$.

\subsection*{Aim 2}
Prisoner's dilemma is widely studied and most of the models developed in order to learn about evolution of cooperation is using it as the model of interaction's result. However, often the reality is different. For example, interaction could be between than two individuals. 
In the first aim we hypothesize that non-vertical transmission can explain the evolution of cooperation in fully mixed population with prisoner's dilemma payoff. Here, we hypothesize that non-vertical transmission can also explain the evolution of cooperation in fully mixed population with other games. The second aim is to determine to what extent our hypothesize could explain the evolution of cooperation. We will develop and investigate a cultural evolution model like we did in the first aim but with different games. 
In the first scenario we can use n-player prisoner's dilemma a.k.a unscrupulous diner's dilemma or just diner's dilemma. The diner's dilemma is the main game we will investigate. In the diner's dilemma we assume that n players are eating in a restaurant. There are two dishes in the restaurant: dish1 with cost $c_1$ and benefit $b_1$ and dish2 with cost $c_2$ and benefit $b_2$. We also know that $b_2>c_2>b_1>c_1$. We presume that one would prefer to order the expensive meal given others will help defray the cost,
\begin{equation} 
\begin{split} \label{diner}
b_2-\frac{1}{n}c_2 >\, & b_1 - \frac{1}{n}c_1.
\end {split}
\end{equation}
Cooperative individual is an individual who choose to take the cheap dish. Choosing the cheap dish increases the fitness of the competitors. 
In the second scenario we can use public common goods as our game. Public common goods is a multiplayer game in which each player can secretly choose how much he want to contribute. The contributions from all players is collected and the sum is multiplied by a factor (greater or equal to one) and the result is the "public good". The public good is evenly divided among the players. A player will be considered as a cooperator if decide to contribute. 
In the third scenario, we want to use a general two player game. Prisoner dilemma is an example of a two player game with a payoff matrix shown in figure \ref{fig:payoff}. We will investigate the general case. The payoff matrix in the general case is shown in figure \ref{fig:generalPayoff}.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{generalpayoff.pdf}
  \caption{General Payoff Matrix}
  \label{fig:generalPayoff}
\end{figure}

\subsection*{Aim 3}
In the previous aims we focused in fully mixed populations. Many time in reality, the population is structured. When the population is spatially structured, individuals interact only with their neighbors, which are more likely to be related. Therefore, cooperators are more likely to interact with cooperators and vice versa. Here we hypothesize that non-vertical transmission can also explain the evolution of cooperation in spatially structured population. We will develop and investigate a cultural evolution model. 
we will analyse these models with simulations.

\newpage
\section*{Conclusions}
We hypothesized that non-vertical transmission can explain the evolution of cooperation. We used a model with non-vertical transmissions and have found that if eq. \eqref{result} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff. In addition, we found that when horizontal transmission cannot occur after interaction ($\alpha = 0$) cooperation will always become extinct. 
Our results improve our understating of cultural evolution of cooperation. Our model shows that cooperation can evolve even in a fully mixed population, where the population is non-structured, there are no repeating interactions and nor individual recognition.

\bibliography{bib}

\newpage
\section*{Appendix A}
In the section, we start with eq. \eqref{modeleq} and we want to investigate when $p\leq p'$. We know that $0<p<1$ and $0<c<b$.

We start by multiple by $\overline{\omega}$ The result is shown in eq. \eqref{step1}.
\begin{equation} 
\begin{split} \label{step1}
p + p^2(b-c) < & \, \{ p^2(1+b-c)[1-(1-\alpha)T_Bq] + pq(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
&+ pq(1+b)[\alpha T_A+(1-\alpha)T_Ap)] + q^2(1-\alpha)T_Ap\}
\end{split}
\end{equation}

Divining by p and substituting $p=1-q$ give us eq. \eqref{step2}
\begin{equation} 
\begin{split} \label{step2}
1 + (1-q)(b-c) < & \, \{ (1-q)(1+b-c)[1-(1-\alpha)T_Bq] + q(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
&+ q(1+b)[\alpha T_A+(1-\alpha)T_A(1-q))] + q^2(1-\alpha)T_A\}
\end{split}
\end{equation}
Eq. \eqref{step2} becomes eq. \eqref{step3}.
%\begin{equation} 
%\begin{split} \label{step3}
%1 + b - c - q(b-c) < & \, \{ bq^2T_B-b\alpha q^2T_B - bq^2T_A + \alpha bq^2T_A - bq - qT_B - bqT_B + \alpha bqT_B +cqT_B + qT_A + bqT_B + b - c + 1 \}
%\end{split}
%\end{equation}
\begin{equation} 
\begin{split}\label{step3}
 -q(b-c) < & \,  bq^2T_B-b\alpha q^2T_B - bq^2T_A + \alpha bq^2T_A - bq - qT_B - bqT_B + \alpha bqT_B +cqT_B + qT_A + bqT_B 
\end{split}
\end{equation}

We can divide by q because we know that $0<q<1$ then,
\begin{equation} 
\begin{split} \label{step4}
 c(1-T_B) < & \,  bqT_B(1-\alpha) - bqT_A(1-\alpha) + (T_A-T_B) + b(T_A - T_B) + \alpha bT_B.
\end{split}
\end{equation}

In the special case when $T_A = T_B = T$ equation \eqref{step4} becomes
\begin{equation} 
\begin{split}\label{step5}
c(1-T) < & \, \alpha bT.
\end{split}
\end{equation}
Eq. \eqref{step5} can be rewritten as
\begin{equation} 
\begin{split}
 \frac{1-T}{\alpha T} < \frac{b}{c}.
\end{split}
\end{equation}

\newpage
\section*{Appendix B - Research Schedule}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=1]{schdule2.pdf}
\end{figure}

\end{document}

### 2020-03-04 ms/main.tex
remove proposal stuff
revise intro

--- 2020-03-02 ResearchProposal/main.tex
@@
 
-\title{Research Proposal:\\  Can Cultural Transmission Explain The Evolution of Cooperative Behavior}
+\title{Can Cultural Transmission Explain The Evolution of Cooperative Behaviour}
 \author{Dor Cohen \\ cohensdor@gmail.com \and Yoav Ram \\ yoav@yoavram.com}
-\date{School of Computer Science, IDC Herzliya\\ \today}
+\date{School of Computer Science, IDC Herzliya, Israel\\ \today}
 
@@
 \section*{Introduction}
-Cooperative behavior is interesting in evolutionary view.
-The theory of evolution is based on the the struggle of the individual to survive and reproduce.
-Natural selection favours those with the highest fitness and therefore, their reproduction will be the most successful.
-However, cooperative behavior can many times harm the individual's fitness and increase the fitness of its competitor \cite{axelrod1981evolution}.
-Yet cooperative behavior is a widespread phenomenon and occurs in other animals besides humans \cite{dugatkin1997cooperation}, for example in rats \cite{rice1962altruism} and birds \cite{krams2008experimental}.
-Therefore, the evolution of cooperative behavior is still an interesting important open question.
-\\Cultural evolution is an evolutionary theory of social change.
-Culture has significant impact on the behavior of animals \cite{bonner2018evolution} and humans \cite{ihara2004cultural,jeong2018bronze}.
-Individual can acquire new behavior from another individual in its social group  through learning or other modes of cultural transmission \cite{richerson2008not}.
-\textbf{The goal of this research} is to determine to what extent cultural transmission can explain the evolution of cooperative behavior.
+Cooperative behaviour can harm the individual's fitness and increase the fitness of its competitor~\cite{axelrod1981evolution}.
+Yet, cooperative behaviour occurs in many non-human animals~\cite{dugatkin1997cooperation}, for example rats~\cite{rice1962altruism} and birds~\cite{krams2008experimental}.
+Therefore, the evolution of cooperative behaviour is an important open question in evolutionary biology.
+\\
+Cultural evolution is an evolutionary theory of social change.
+Culture has significant impact on the behaviour of humans~\cite{ihara2004cultural,jeong2018bronze} as well as non-human animals~\cite{bonner2018evolution}.
+Under the view of cultural evolution, an individual can acquire its behaviour from another individual in its social group through learning or other modes of cultural transmission \cite{richerson2008not}.
+Here we attempt to determine to what extent cultural transmission can explain the evolution of cooperative behaviour.
+
 \subsection*{Theories for Evolution of Cooperation}
-Three major theories have been proposed to explain the evolution of cooperative behavior.
-\\\textbf{Kin selection}, proposing that natural selection can favour cooperative behaviour between kin.
-The importance of relatedness to the evolution of cooperation and altruism was shown by Hamilton \cite{hamilton1964genetical}.
+Three major theories have been proposed to explain the evolution of cooperative behaviour.
+
+\textbf{Kin selection}, proposing that natural selection can favour cooperative behaviour between kin.
+The importance of relatedness to the evolution of cooperation and altruism was shown by Hamilton~\cite{hamilton1964genetical}.
 According to Hamilton, kin selection causes allele to increase in frequency when the genetic relatedness $r$ of a recipient to an actor multiplied by the benefit $b$ to the recipient is greater than the reproductive cost $c$ to the actor.
@@
 It has been suggested that kin selection to explain the cooperative behaviour of eusocial insects like the honey bee.
-The most significant argument against kin selection is that cooperation can evolve with zero relatedness \cite{wilson2005kin}.
-This makes Hamilton's rule incomplete according to Wilson \cite{wilson2005kin}.
-Foster et al.
-\cite{foster2006kin} reject this claim.
+The most significant argument against kin selection is that cooperation can evolve with zero relatedness~\cite{wilson2005kin}.
+This makes Hamilton's rule incomplete according to Wilson~\cite{wilson2005kin}.
+Foster et~al.~\cite{foster2006kin} reject this claim.
 They argue that altruism without relatedness can not evolve.
@@
 Wilson also criticises kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions.
-On the other hand, Foster et al.
-\cite{foster2006kin} argue that kin selection does not ignore ecology.
+On the other hand, Foster et~al.~\cite{foster2006kin} argue that kin selection does not ignore ecology.
 Hamilton’s rule shows
-that environmental factors causing a high benefit: cost ratio will favour cooperation.
-\\\\\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation.
+that environmental factors causing a high benefit-to-cost ratio will favour cooperation.
+
+\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation.
 In \textit{direct reciprocity} there are a repeated encounters between the same two individuals.
@@
 In humans, such interactions happen often, for example humans often donate money.
-\textit{Indirect reciprocity} has been suggested to explain this behavior. 
-Nowak \cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
+
+\textbf{Indirect reciprocity} has been suggested to explain this behaviour. 
+Nowak~\cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
 The money that "fuels the engines" of indirect reciprocity is reputation.
 \\However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.
-\\\\\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
+
+\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
 A common model for group selection work as is: the population is divided into groups.
@@
 The fact that a trait with a lower fitness took over the population is a contradiction.
-Eldar et al.
-\cite{eldakar2011eight} reject this argument.
+Eldar et al.~\cite{eldakar2011eight} reject this argument.
 They believe that this argument is a tautology and does not qualify as an argument against group selection.
@@
 When a trait is evolve by group selection, despite the fact that it has lower fitness within the group, it has a better fit, all thing considered.
-\\\\All three theories mentioned above assume that cooperation is genetically determined.
-This raise the question, is it possible that cooperation is determined by environmental or social influences.
-Recent work by Lewin-Epstein at el.\cite{lewin2017microbes} may answer this question.
-Lewin-Epstein at el.
-\cite{lewin2017microbes} have proposed a different model that can explain the evolution of  cooperative behavior.
-They have hypothesized that microbes that manipulate their hosts to act altruistically could be favoured by selection, and may play a role in the widespread occurrence of cooperative behavior.
-Indeed, it has been shown that microbes can mediate behavioural changes in their hosts\cite{poulin2010parasite}\cite{dobson1988population}.
+
+All the above theories assume that cooperation is genetically determined. This raises the question, is it possible that cooperation is determined by non-genetic factors?
+Recent work by Lewin-Epstein at el.~\cite{lewin2017microbes} sheds some light on this question. 
+Lewin-Epstein at el.~\cite{lewin2017microbes} have hypothesised that microbes that manipulate their hosts to act altruistically can be favoured by selection, and may play a role in the widespread occurrence of cooperative behaviour.
+Indeed, it has been shown that microbes can mediate behavioural changes in their hosts~\cite{poulin2010parasite,dobson1988population}.
 Therefore, natural selection on microbes may favour manipulation of the host so that it cooperates with others.
-Microbes can be transmitted \textbf{horizontally} from one host to another during host interactions.
-Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donating host, even when the two hosts are unrelated \cite{lewin2017microbes}.
-Microbes can also transfer vertically, from parent to
-offspring.
-As a result, a microbe that induces its host to help another host, increases the other host survival or reproduction, thus increasing the vertical transmission (v) of the microbes of the receiving individual.
+Microbes can be transmitted \emph{horizontally} from one host to another during host interactions.
+Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\cite{lewin2017microbes}.
+Microbes can also transfer vertically, from parent to offspring (yr: cite 10.1126/science.aat7164).
+As a result, a microbe that induces its host to cooperate with another host and thereby increases the other host fitness will  increase the vertical transmission of the microbes of the receiving individual.
 Kin selection among microbes could therefore favour microbes that induce cooperative behaviour in their hosts, thereby increasing the transmission of their microbial kin.
-\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible \cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behaviour of their hosts.
+%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behaviour of their hosts.
 
-\subsection*{A Theory of Cultural Evolution of Cooperation}
-From Lewin-Epstein at el. \cite{lewin2017microbes} we learn that \textbf{non-vertical} transmission could explain the evolution of cooperative behavior. 
+\subsection*{Cultural Evolution of Cooperation}
+Lewin-Epstein at el.~\cite{lewin2017microbes} have demonstrated that \emph{non-vertical} transmission can help to explain the evolution of cooperative behaviour. 
 Non-vertical transmission could be either a horizontal or oblique.
-Horizontal transmission is a transmission between individuals from the same generation.
-Oblique transmission is a transmission from an adult to a child.
-Evolution under either of these transmission models is expected to be more rapid than under pure vertical transmission \cite{ram2018evolution}.   
-Here we suggest a model in which behavior changes are caused by cultural and social transmissions.
-In our model the social transmission that affects individual behavior can be learned during social interactions.
-For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future.
-Surprisingly, much of the analysis made by Lewin-Epstein at el.
-\cite{lewin2017microbes} can be applied to cultural transmission, because learning can be modeled as infectious agent that transmits the cooperative behavior \cite{cavalli1981cultural}.
+Horizontal transmission occurs between individuals from the same generation.
+Oblique transmission occurs from an adult to an offspring.
+Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission \cite{ram2018evolution} (yr: not sure this is a good reference).
 
-We \textbf{hypothesize} that non-vertical transmission can explain the evolution of cooperation.
-To test this hypothesis we are going to use cultural evolution models that include non-vertical transmission mechanism.
-We will use both mathematical analysis to investigate the models, and run simulations for more complex scenarios.
+Here we suggest a model in which behavioural changes are mediated by cultural transmission that can occur during social interaction.
+For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behaviour and will cooperate in the future.
+Surprisingly, some of the analysis made by Lewin-Epstein at el.~\cite{lewin2017microbes} can be applied to cultural transmission, because cultural transmission is mathematically akin to transmission of infectious diseases~\cite{cavalli1981cultural}.
 
-\section*{Research Proposal}
-The research schedule can be found in appendix B. 
-\subsection*{Aim 1} Our first aim is to determine to what extent non-vertical transmission can explain the evolution of cooperation in fully mixed population with prisoner's dilemma payoff.
-We will develop a cultural evolution model and determine under which conditions cooperative behavior could prosper.
-The model assumes fully mixed population and individuals that interact in pairs with prisoner's dilemma payoff.
-The payoff matrix is shown in figure \ref{fig:payoff}.
-\\In our model We consider a population of asexual individuals.
-We assume that cooperative behavior is a dichotomous cultural trait with phenotypes A and B.
-Individuals of type A will always act altruistically and individuals of type B will not cooperate.
-An individual who cooperates will pay a cost $0<c<1$ and the recipient gains a benefit $b$ where $b>c$.
+Here, we hypothesise that non-vertical cultural transmission can explain the evolution of cooperation.
+We are develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.
+
+\section*{Models and Methods}
+
+Our first aim is to determine to what extent non-vertical transmission can explain the evolution of cooperation in a fully mixed population where cooperation is modelled using the prisoner's dilemma (yr: add ref).
+
+Consider a fully mixed asexual population where individuals interact in pairs with a prisoner's dilemma payoff~\ref{fig:payoff}.
+
+Cooperative behaviour is a dichotomous cultural trait with phenotypes $A$ and $B$ for cooperation and defection, respectively.
+Cooperators pay a cost $0<c<1$ and their partner gains a benefit $b$, where we assume $b>c$.
 After each interaction, each individual will try to learn from its interaction partner with probability $\alpha$, and with probability $1-\alpha$ it will try to learn from random individual within the population as shown in table \ref{fig:payoff}.
@@
 
-The question we are interested in is under what conditions the cooperative behavior represented by phenotype A will not become extinct. In order to do that we will investigate when $p' > p$.
+The question we are interested in is under what conditions the cooperative behaviour represented by phenotype A will not become extinct. In order to do that we will investigate when $p' > p$.
 We can make a simplify assumption that vertical transmission is perfect, $v=1$ and then we will be able to solve the inequation more easily.
@@
 However, we are also interested when this assumption does not apply, meaning that $v<1$.
-In this, We will to run numerical simulation in order to better understand under what conditions cooperative behavior will take over the population.
+In this, We will to run numerical simulation in order to better understand under what conditions cooperative behaviour will take over the population.
 \\\textbf{\underline{Preliminary Results}}
@@
 \end{equation}
-Therefore, cooperative behavior will take over the population when eq. \eqref{result} is satisfied.  
+Therefore, cooperative behaviour will take over the population when eq. \eqref{result} is satisfied.  
 \\\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
@@
 \end{equation}
-Therefore, cooperative behavior will take over the population when eq. \eqref{result3} is satisfied. 
+Therefore, cooperative behaviour will take over the population when eq. \eqref{result3} is satisfied. 
 This result is in accordance with the result presented by Lewin-Epstein at el. \cite{Ohad}. 
@@
 
-\newpage
-\section*{Appendix B - Research Schedule}
-\begin{figure}[h!]
-  \centering
-  \includegraphics[scale=1]{schdule2.pdf}
-\end{figure}
-
 \end{document}

### 2020-03-04 ms/main.tex
revise model

@@
 \usepackage[numbers]{natbib}
+\usepackage{multirow}
 
@@
 This is also known as Hamilton's Rule:
-\begin{equation} \label{hamiltonrule}
+
+\begin{equation} \label{eq:hamilton_rule}
 c<rb
 \end{equation}
+
 There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
@@
 Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit.
-\begin{equation} \label{reciprocity}
+
+\begin{equation} \label{eq:reciprocity}
 c<bw
 \end{equation}
+
 Direct reciprocity assumes that both players are in a position to cooperate.
@@
 Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
-\begin{equation} \label{groupselection}
+
+\begin{equation} \label{eq:groupselection}
 \frac{b}{c}>1+\frac{n}{m}
 \end{equation}
-The group selection was criticized by biologists advocate gene-centered view of evolution.
+
+Group selection was criticized by biologists advocate gene-centered view of evolution.
 Group selection has been criticized due to the fact that the trait like cooperation evolves in the total population.
@@
 Oblique transmission occurs from an adult to an offspring.
-Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission \cite{ram2018evolution} (yr: not sure this is a good reference).
+Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission~\cite{ram2018evolution} (yr: not sure this is a good reference).
 
@@
 
-Our first aim is to determine to what extent non-vertical transmission can explain the evolution of cooperation in a fully mixed population where cooperation is modelled using the prisoner's dilemma (yr: add ref).
+First, we focus on the evolution of cooperation in a fully mixed population where cooperation is modelled using the prisoner's dilemma (yr: add ref).
 
-Consider a fully mixed asexual population where individuals interact in pairs with a prisoner's dilemma payoff~\ref{fig:payoff}.
+Consider a very large population whose members are characterised by their phenotype $\phi$, which can be of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors, with corresponding fitness values $w_A$ and $w_B$, which depend on the frequency of the phenotypes (see below).
+An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
+Following~\cite{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uniparental inheritance (yr: cite Zefferman Behav Ecol 2016), the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
 
-Cooperative behaviour is a dichotomous cultural trait with phenotypes $A$ and $B$ for cooperation and defection, respectively.
-Cooperators pay a cost $0<c<1$ and their partner gains a benefit $b$, where we assume $b>c$.
-After each interaction, each individual will try to learn from its interaction partner with probability $\alpha$, and with probability $1-\alpha$ it will try to learn from random individual within the population as shown in table \ref{fig:payoff}.
-\begin{figure}[h!]
+\begin{equation} \label{eq:vertical_oblique_transmission}
+P(\phi'=A \mid \phi) = \begin{cases}
+v + (1-v)p, & \text{if } \phi=A \\
+(1-v)p, & \text{if } \phi=B
+\end{cases},
+\end{equation}
+where $p=P(\phi=A)$ is the frequency of $A$ among adults in the parental generation.
+
+Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
+
+\begin{equation}\label{eq:horizontal}
+\begin{aligned}
+\hat{p}
+& = \frac{w_A(p)}{\bar{w}} p [v + (1-v)p] + \frac{w_B(p)}{\bar{w}} (1-p) [(1-v)p] \\
+& = v \frac{w_A}{\bar{w}} p + (1-v) p,
+\end{aligned}
+\end{equation}
+where $\bar{w}=p w_A + (1-p) w_B$ is the population mean fitness.
+
+Fitness is determined by a prisoner's dilemma dynamic.
+Specifically, individuals interact in pairs, cooperators pay a cost $0<c<1$, and their partner gains a benefit $b$, where we assume $b>c$.
+The following payoff matrix shows the fitness of an individual with phenotype $\phi_1$ when interacting with a partner with phenotype $\phi_2$ ($b>c>0$):
+
+\begin{table}[h]\label{table:prisoner_payoff}
 \centering
-  \includegraphics[scale=0.5]{payoff.pdf}
-  \caption{Payoff Matrix}
-  \label{fig:payoff}
-\end{figure}
+\begin{tabular}{lll}
+           & $\phi_2=A$ & $\phi_2=B$ \\
+$\phi_1=A$ & $b-c$      & $-c$       \\
+$\phi_1=B$ & $b$        & $0$       
+\end{tabular}
+\end{table}
 
-The transmission from type A will be successful with probability $T_a$ and from type B with probability $T_b$.
-In the model, in each generation each individual is having n interactions and then a reproduction is occurring according to each individual fitness and phenotypes A and B are vertically transmitted from parent to offspring.
-In general the vertical transition can be imperfect which means that with probability $v$ offspring inherits its parent’s phenotype and with probability $1-v$ it inherits a phenotype from its parent population.
-After reproduction the offspring replace the parent generation.
+Interactions occur randomly.
+So, two individuals with phenotype $A$ interact with probability $\hat{p}^2$, two individuals with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two individuals with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
+Therefore, the fitness values of the two phenotypes, $w_A$ and $w_B$ are
+
+\begin{equation}\label{eq:fitness}
+\begin{aligned}
+w_A(\hat{p}) & = \hat{p}(1+b-c) + (1-\hat{p})(1-c) = 1 - c + \hat{p} b \\
+w_B(\hat{p}) & = \hat{p}(1+b) + (1-\hat{p}) = 1 + \hat{p} b,
+\end{aligned}
+\end{equation}
+and the population mean fitness is therefore
+$\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$.
+
+Horizontal cultural transmission, which occurs between peers, may occur between interaction partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{Fig.~\ref{fig:horizontal}}).
+Horizontal transmission is not always successful, as one peer may reject the other's phenotype. The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
+
 \begin{figure}[h!]
@@
   \includegraphics[scale=1]{figure.pdf}
-  \caption{Horizontal Transmission}
-  \label{fig:figure}
+  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interaction partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
+  \label{fig:horizontal}
 \end{figure}
 
-We define $p$ to be the frequency of newborn with phenotype A and $q=1-p$ to be the frequency of newborn with phenotype B.
-In addition, we define $\hat{p},\hat{q}$ to be the frequency of phenotypes A and B before reproduction and after interaction.
-
-\begin{equation} \label{d}
-\hat{p} = p^2\left[1-\left(1-\alpha\right)qT_B\right] + pq\alpha T_A + pq\alpha(1-T_B) + pq(1-\alpha)[pT_A+q(1-T_B)]
+Therefore, the next-generation frequency $p'$ of adults with phenotype $A$ after interaction and horizontal transmission is (yr: please check)
+\begin{equation}\label{eq:horizontal}
+\begin{aligned}
+p'
+& = \hat{p}^2 [\alpha + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
+& + \hat{p}(1-\hat{p}) [\alpha(1-T_b) + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
+& + (1-\hat{p})\hat{p} [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
+& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A]
+\end{aligned}
 \end{equation}
 
-The mean fitness of the population in each generation is:
-\begin{equation} \label{d}
-\overline{\omega} = 1 + p(b-c)
+\section*{Results}
+
+We start by inspecting specific cases, for which we can derive general results. 
+Afterwards, we use numerical simulation to analyse more complex cases.
+
+\paragraph*{Without oblique transmission, $v=1$.} 
+With only vertical transmission eq.~\ref{eq:vertical_oblique_transmission} becomes
+\begin{equation}
+\hat{p} = \frac{w_A}{\bar{w}} p,
 \end{equation}
-As shown in eq.
-\eqref{vt} the probability to get a offspring with phenotype B given that its parent is of phenotype A is equal probability of imperfect vertical transmission times the proportion of A in the population.
-\begin{equation} \label{vt}
-(1-v)\hat{q}
-\end{equation}
-
-Given p the frequency of phenotype A at the current generation, we are interested in frequency of A in the next generation.
-We have three possible interaction types A interacts with A, A interacts with B and B interacts with B.
-
-We focus on the frequency of phenotype A.
-We define $x_{AA}$ to be the frequency of offspring that their parent was of phenotype A and interacted with another individual of type A.
-Similarly we define $x_{AB}, \, x_{BA}, \, x_{BB}$.
+and the change in frequency of adults with phenotype $A$ can be written as
 
 \begin{equation} 
-\begin{split}\label{aim1model0}
- x_{AA} &= \frac{1}{\overline{\omega}}p^2(1+b-c)[(1-(1-\alpha)T_Bq)(1-(1-v)\hat{q})+(1-\alpha)T_Bq(1-v)\hat{p}]\\
- x_{AB} &= \frac{1}{\overline{\omega}}pq(1-c)[(1-(1-\alpha)T_Bq-\alpha T_B)(1-(1-v)\hat{q}) \\ &+ (\alpha T_B+(1-\alpha)T_Bq)(1-v)\hat{p}]\\
- x_{BA} &= \frac{1}{\overline{\omega}}pq(1+b)[(1-(1-\alpha)T_Ap-\alpha T_A)((1-v)\hat{p})\\ & +(\alpha T_A+(1-\alpha)T_A p)(1-(1-v)\hat{q})] \\
- x_{BB} &= \frac{1}{\overline{\omega}}q^2[(1-(1-\alpha)T_Ap)(1-v)\hat{p})+(1-\alpha)T_Ap(1-(1-v)\hat{q})]
-\end{split}
-\end{equation}
-We define p' to be the frequency of individuals of phenotype A in the next generation.
-\begin{equation} 
-\begin{split}\label{aim1model}
-& p' = x_{AA} + x_{AB} + x_{BA} + x_{BB}
-\end{split}
-\end{equation}
-
-The question we are interested in is under what conditions the cooperative behaviour represented by phenotype A will not become extinct. In order to do that we will investigate when $p' > p$.
-We can make a simplify assumption that vertical transmission is perfect, $v=1$ and then we will be able to solve the inequation more easily.
-Under this assumption equations \eqref{aim1model0},\eqref{aim1model} become
-
-\begin{equation} 
-\begin{split}\label{modeleq}
+\begin{split}\label{eq:model_v=1}
 p' =& \frac{1}{\overline{\omega}} \{ p^2(1+b-c)[1-(1-\alpha)T_Bq] + pq(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\

### 2020-03-04 ms/main.tex
british->us

@@
 
-\title{Can Cultural Transmission Explain The Evolution of Cooperative Behaviour}
+\title{Can Cultural Transmission Explain The Evolution of Cooperative behavior}
 \author{Dor Cohen \\ cohensdor@gmail.com \and Yoav Ram \\ yoav@yoavram.com}
@@
 \section*{Introduction}
-Cooperative behaviour can harm the individual's fitness and increase the fitness of its competitor~\cite{axelrod1981evolution}.
-Yet, cooperative behaviour occurs in many non-human animals~\cite{dugatkin1997cooperation}, for example rats~\cite{rice1962altruism} and birds~\cite{krams2008experimental}.
-Therefore, the evolution of cooperative behaviour is an important open question in evolutionary biology.
+Cooperative behavior can harm the individual's fitness and increase the fitness of its competitor~\cite{axelrod1981evolution}.
+Yet, cooperative behavior occurs in many non-human animals~\cite{dugatkin1997cooperation}, for example rats~\cite{rice1962altruism} and birds~\cite{krams2008experimental}.
+Therefore, the evolution of cooperative behavior is an important open question in evolutionary biology.
 \\
 Cultural evolution is an evolutionary theory of social change.
-Culture has significant impact on the behaviour of humans~\cite{ihara2004cultural,jeong2018bronze} as well as non-human animals~\cite{bonner2018evolution}.
-Under the view of cultural evolution, an individual can acquire its behaviour from another individual in its social group through learning or other modes of cultural transmission \cite{richerson2008not}.
-Here we attempt to determine to what extent cultural transmission can explain the evolution of cooperative behaviour.
+Culture has significant impact on the behavior of humans~\cite{ihara2004cultural,jeong2018bronze} as well as non-human animals~\cite{bonner2018evolution}.
+Under the view of cultural evolution, an individual can acquire its behavior from another individual in its social group through learning or other modes of cultural transmission \cite{richerson2008not}.
+Here we attempt to determine to what extent cultural transmission can explain the evolution of cooperative behavior.
 
 \subsection*{Theories for Evolution of Cooperation}
-Three major theories have been proposed to explain the evolution of cooperative behaviour.
+Three major theories have been proposed to explain the evolution of cooperative behavior.
 
-\textbf{Kin selection}, proposing that natural selection can favour cooperative behaviour between kin.
+\textbf{Kin selection}, proposing that natural selection can favor cooperative behavior between kin.
 The importance of relatedness to the evolution of cooperation and altruism was shown by Hamilton~\cite{hamilton1964genetical}.
@@
 There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
-It has been suggested that kin selection to explain the cooperative behaviour of eusocial insects like the honey bee.
+It has been suggested that kin selection to explain the cooperative behavior of eusocial insects like the honey bee.
 The most significant argument against kin selection is that cooperation can evolve with zero relatedness~\cite{wilson2005kin}.
@@
 Hamilton’s rule shows
-that environmental factors causing a high benefit-to-cost ratio will favour cooperation.
+that environmental factors causing a high benefit-to-cost ratio will favor cooperation.
 
@@
 
-\textbf{Indirect reciprocity} has been suggested to explain this behaviour. 
+\textbf{Indirect reciprocity} has been suggested to explain this behavior. 
 Nowak~\cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
@@
 
-\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
+\textbf{Group Selection} theory posits that cooperation is favored because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
 A common model for group selection work as is: the population is divided into groups.
@@
 Recent work by Lewin-Epstein at el.~\cite{lewin2017microbes} sheds some light on this question. 
-Lewin-Epstein at el.~\cite{lewin2017microbes} have hypothesised that microbes that manipulate their hosts to act altruistically can be favoured by selection, and may play a role in the widespread occurrence of cooperative behaviour.
-Indeed, it has been shown that microbes can mediate behavioural changes in their hosts~\cite{poulin2010parasite,dobson1988population}.
-Therefore, natural selection on microbes may favour manipulation of the host so that it cooperates with others.
+Lewin-Epstein at el.~\cite{lewin2017microbes} have hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
+Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\cite{poulin2010parasite,dobson1988population}.
+Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
 Microbes can be transmitted \emph{horizontally} from one host to another during host interactions.
@@
 As a result, a microbe that induces its host to cooperate with another host and thereby increases the other host fitness will  increase the vertical transmission of the microbes of the receiving individual.
-Kin selection among microbes could therefore favour microbes that induce cooperative behaviour in their hosts, thereby increasing the transmission of their microbial kin.
-%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behaviour of their hosts.
+Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
+%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behavior of their hosts.
 
 \subsection*{Cultural Evolution of Cooperation}
-Lewin-Epstein at el.~\cite{lewin2017microbes} have demonstrated that \emph{non-vertical} transmission can help to explain the evolution of cooperative behaviour. 
+Lewin-Epstein at el.~\cite{lewin2017microbes} have demonstrated that \emph{non-vertical} transmission can help to explain the evolution of cooperative behavior. 
 Non-vertical transmission could be either a horizontal or oblique.
@@
 
-Here we suggest a model in which behavioural changes are mediated by cultural transmission that can occur during social interaction.
-For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behaviour and will cooperate in the future.
+Here we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interaction.
+For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future.
 Surprisingly, some of the analysis made by Lewin-Epstein at el.~\cite{lewin2017microbes} can be applied to cultural transmission, because cultural transmission is mathematically akin to transmission of infectious diseases~\cite{cavalli1981cultural}.
@@
 However, we are also interested when this assumption does not apply, meaning that $v<1$.
-In this, We will to run numerical simulation in order to better understand under what conditions cooperative behaviour will take over the population.
+In this, We will to run numerical simulation in order to better understand under what conditions cooperative behavior will take over the population.
 \\\textbf{\underline{Preliminary Results}}
@@
 \end{equation}
-Therefore, cooperative behaviour will take over the population when eq. \eqref{result} is satisfied.  
+Therefore, cooperative behavior will take over the population when eq. \eqref{result} is satisfied.  
 \\\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
@@
 \end{equation}
-Therefore, cooperative behaviour will take over the population when eq. \eqref{result3} is satisfied. 
+Therefore, cooperative behavior will take over the population when eq. \eqref{result3} is satisfied. 
 This result is in accordance with the result presented by Lewin-Epstein at el. \cite{Ohad}. 

### 2020-03-04 ms/main.tex
typo
start revising results

@@
 Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\cite{lewin2017microbes}.
-Microbes can also transfer vertically, from parent to offspring (yr: cite 10.1126/science.aat7164).
+Microbes can also transfer vertically, from parent to offspring.
+% (yr: cite 10.1126/science.aat7164)
 As a result, a microbe that induces its host to cooperate with another host and thereby increases the other host fitness will  increase the vertical transmission of the microbes of the receiving individual.
@@
 Oblique transmission occurs from an adult to an offspring.
-Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission~\cite{ram2018evolution} (yr: not sure this is a good reference).
+Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission~\cite{ram2018evolution}. % (yr: not sure that this is a good reference)
 
@@
 
-First, we focus on the evolution of cooperation in a fully mixed population where cooperation is modelled using the prisoner's dilemma (yr: add ref).
+First, we focus on the evolution of cooperation in a fully mixed population where cooperation is modelled using the prisoner's dilemma. %(yr: add ref)
 
-Consider a very large population whose members are characterised by their phenotype $\phi$, which can be of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors, with corresponding fitness values $w_A$ and $w_B$, which depend on the frequency of the phenotypes (see below).
+Consider a very large population whose members are characterized by their phenotype $\phi$, which can be of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors, with corresponding fitness values $w_A$ and $w_B$, which depend on the frequency of the phenotypes (see below).
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
-Following~\cite{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uniparental inheritance (yr: cite Zefferman Behav Ecol 2016), the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
+Following~\cite{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance, %(yr: cite Zefferman Behav Ecol 2016),
+the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
 
@@
 \end{equation}
-where $p=P(\phi=A)$ is the frequency of $A$ among adults in the parental generation.
+where $p=P(\phi=A)$ is the frequency of $A$ among all adults in the parental generation.
 
+Not all adults become parents due to natural selection, and we denote the frequency of phenotype $A$ among parents with $\tilde{p}$.
 Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
@@
 \hat{p}
-& = \frac{w_A(p)}{\bar{w}} p [v + (1-v)p] + \frac{w_B(p)}{\bar{w}} (1-p) [(1-v)p] \\
-& = v \frac{w_A}{\bar{w}} p + (1-v) p,
+& = \tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \\
+& = v \tilde{p} + (1-v) p.
 \end{aligned}
 \end{equation}
-where $\bar{w}=p w_A + (1-p) w_B$ is the population mean fitness.
 
-Fitness is determined by a prisoner's dilemma dynamic.
-Specifically, individuals interact in pairs, cooperators pay a cost $0<c<1$, and their partner gains a benefit $b$, where we assume $b>c$.
+Individuals interact in a social interaction modeled as a prisoner's dilemma.
+Specifically, individuals interact in pairs, cooperators pay a fitness cost $0<c<1$, and their partner gains a fitness benefit $b$, where we assume $b>c$.
 The following payoff matrix shows the fitness of an individual with phenotype $\phi_1$ when interacting with a partner with phenotype $\phi_2$ ($b>c>0$):
@@
 
-Interactions occur randomly.
+Social interactions occur randomly.
 So, two individuals with phenotype $A$ interact with probability $\hat{p}^2$, two individuals with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two individuals with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
-Therefore, the fitness values of the two phenotypes, $w_A$ and $w_B$ are
 
-\begin{equation}\label{eq:fitness}
+%Therefore, the fitness values of the two phenotypes, $w_A$ and $w_B$ are
+%
+%\begin{equation}\label{eq:fitness}
+%\begin{aligned}
+%w_A(\hat{p}) & = \hat{p}(1+b-c) + (1-\hat{p})(1-c) = 1 - c + \hat{p} b \\
+%w_B(\hat{p}) & = \hat{p}(1+b) + (1-\hat{p}) = 1 + \hat{p} b,
+%\end{aligned}
+%\end{equation}
+%and the population mean fitness is therefore
+%$\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$.
+
+Horizontal cultural transmission occurs between peers. 
+It may occur between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{Fig.~\ref{fig:horizontal}}).
+Horizontal transmission is not always successful, as one peer may reject the other's phenotype. The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
+
+Therefore, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
+\begin{equation}\label{eq:nextgen_adults}
 \begin{aligned}
-w_A(\hat{p}) & = \hat{p}(1+b-c) + (1-\hat{p})(1-c) = 1 - c + \hat{p} b \\
-w_B(\hat{p}) & = \hat{p}(1+b) + (1-\hat{p}) = 1 + \hat{p} b,
+p'
+& = \hat{p}^2 [\alpha + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
+& + \hat{p}(1-\hat{p}) [\alpha(1-T_B) + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
+& + (1-\hat{p})\hat{p} [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
+& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A]
 \end{aligned}
 \end{equation}
-and the population mean fitness is therefore
-$\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$.
 
-Horizontal cultural transmission, which occurs between peers, may occur between interaction partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{Fig.~\ref{fig:horizontal}}).
-Horizontal transmission is not always successful, as one peer may reject the other's phenotype. The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
+The frequency of $A$ among parents follows a similar dynamic, but also includes the effect of natural selection, and is therefore
+\begin{equation}\label{eq:nextgen_parents}
+\begin{aligned}
+\bar{w} \tilde{p}'
+& = \hat{p}^2 (1+b-c) [\alpha + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
+& + \hat{p}(1-\hat{p}) (1-c) [\alpha(1-T_B) + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
+& + (1-\hat{p})\hat{p} (1+b) [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
+& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A],
+\end{aligned}
+\end{equation}
+where $\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$ is the population mean fitness.
 
-\begin{figure}[h!]
+\begin{figure}[b]
   \centering
@@
 
-Therefore, the next-generation frequency $p'$ of adults with phenotype $A$ after interaction and horizontal transmission is (yr: please check)
-\begin{equation}\label{eq:horizontal}
-\begin{aligned}
-p'
-& = \hat{p}^2 [\alpha + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
-& + \hat{p}(1-\hat{p}) [\alpha(1-T_b) + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
-& + (1-\hat{p})\hat{p} [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
-& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A]
-\end{aligned}
-\end{equation}
-
 \section*{Results}
@@
 We start by inspecting specific cases, for which we can derive general results. 
-Afterwards, we use numerical simulation to analyse more complex cases.
+Afterwards, we use numerical simulation to analyze more complex cases.
 
@@
 With only vertical transmission eq.~\ref{eq:vertical_oblique_transmission} becomes
-\begin{equation}
-\hat{p} = \frac{w_A}{\bar{w}} p,
-\end{equation}
-and the change in frequency of adults with phenotype $A$ can be written as
+$\hat{p} =  \tilde{p}$,
+and eq.~\ref{eq:nextgen_parents} for the change in frequency $p'$ of phenotype $A$ among parents can be written as
 
 \begin{equation} 
-\begin{split}\label{eq:model_v=1}
-p' =& \frac{1}{\overline{\omega}} \{ p^2(1+b-c)[1-(1-\alpha)T_Bq] + pq(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
-&+ pq(1+b)[\alpha T_A+(1-\alpha)T_Ap)] + q^2(1-\alpha)T_Ap\}.
+\begin{split}\label{eq:nextgen_parents_vertical_only}
+\bar{w} \tilde{p}' 
+& = p^2 (1+b-c) (1 - (1-p) (1-\alpha) T_B) \\
+& + p(1-p) (1-c) (p (1-\alpha) T_B + 1 - T_B) \\
+& + p(1-p) (1+b) (p (1-\alpha) + \alpha) T_A \\
+& + (1-p)^2 p (1-\alpha) T_A
 \end{split}
 \end{equation}
-However, we are also interested when this assumption does not apply, meaning that $v<1$.
-In this, We will to run numerical simulation in order to better understand under what conditions cooperative behavior will take over the population.
-\\\textbf{\underline{Preliminary Results}}
-We have preliminary result only when $v=1$.
-\\We get that $p'>p$ when (see appendix A):
+
+\textbf{Result 1.}
+If 
+\begin{equation}\label{result1}
+c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b (p(1-\alpha) - 1)]
+\end{equation}
+then $\tilde{p}' > \tilde{p}$, and the frequency of phenotype $A$ among parents increases.
+
+\textbf{Corollary 1.1: equal horizontal transmission.}
+If $T=T_A=T_B$, then
 \begin{equation}
-\begin{split} \label{result0}
- c(1-T_B) < & \,  bqT_B(1-\alpha) - bqT_A(1-\alpha) + (T_A-T_B) + b(T_A - T_B) + \alpha bT_B
-\end{split}
+\label{eq:equal_transmission}
+\frac{1-T}{\alpha T} < \frac{b}{c},
 \end{equation}
-We want to investigate few special cases:
-\\\underline{Special case 1 - $T_A = T_B = T$:} then, eq. \eqref{result0} becomes:
-\begin{equation}
-\begin{split} \label{result}
- \frac{1-T}{\alpha T}< \frac{b}{c}
-\end{split}
-\end{equation}
-Therefore, cooperative behavior will take over the population when eq. \eqref{result} is satisfied.  
-\\\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
+which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}).
+
+%(yr: I stopped here)
+
+\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
 \\Eq. \eqref{result0} becomes:

### 2020-03-05 ms/main.tex
natbib; authblk; formatting

@@
-\documentclass{article}
-\usepackage[margin=0.5in]{geometry}
-\usepackage[utf8]{inputenc}
+\documentclass[12pt]{extarticle}
+\usepackage{geometry}
+\geometry{
+a4paper,
+total={170mm,257mm},
+left=20mm,
+top=20mm,
+headheight=12pt
+}
+
+%\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
+\usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
+% TeX will automatically convert eps --> pdf in pdflatex
+
+\usepackage{amssymb,amsmath,amsthm}
+\usepackage{commath}
+\usepackage{longtable}
+\usepackage[hyphens]{url}
+\usepackage[dvipsnames]{xcolor}
+\usepackage[unicode=true,colorlinks=true,urlcolor=CadetBlue,citecolor=black,linkcolor=black]{hyperref}
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage{authblk}
+
+%SetFonts
+% newtxtext+newtxmath
+\usepackage{newtxtext} %loads helv for ss, txtt for tt
 \usepackage{amsmath}
-\usepackage{xcolor}
-\usepackage[displaymath, mathlines]{lineno}
-\usepackage{graphicx}
-\usepackage[numbers]{natbib}
-\usepackage{multirow}
+\usepackage[bigdelims]{newtxmath}
+\usepackage[T1]{fontenc}
+\usepackage{textcomp}
+%SetFonts
 
- \bibliographystyle{ieeetr}
+% less space before sections 
+% \@startsection {NAME}{LEVEL}{INDENT}{BEFORESKIP}{AFTERSKIP}{STYLE} 
+%            optional * [ALTHEADING]{HEADING} 
+\makeatletter
+ \renewcommand\section{\@startsection {section}{1}{\z@}%
+     {-2.5ex \@plus -1ex \@minus -.2ex}%
+     {1.3ex \@plus.2ex}%
+    {\Large\bfseries}}
 
-%\renewcommand\linenumberfont{\normalfont\small\sffamily}
-%\linenumbers
-\modulolinenumbers[2]
-\geometry{a4paper, total={170mm,252mm},left=20mm,top=20mm,headheight=12pt}
-\linespread{1.5}
+% Species names
+%% Meta-Command for defining new species macros
+\usepackage{xspace}
 
-\title{Can Cultural Transmission Explain The Evolution of Cooperative behavior}
-\author{Dor Cohen \\ cohensdor@gmail.com \and Yoav Ram \\ yoav@yoavram.com}
-\date{School of Computer Science, IDC Herzliya, Israel\\ \today}
+\newcommand{\species}[3]{%
+  \newcommand{#1}{\gdef#1{\textit{#3}\xspace}\textit{#2}\xspace}}
+
+\species{\yeast}{Saccharomyces cerevisiae}{S.~cerevisiae}
+\species{\calbicans}{Candida albicans}{C.~albicans}
+\species{\cneoformans}{Cryptococcus neoformans}{C.~neoformans}
+
+% Yoav & Lee commands
+\newcommand*{\tr}{^\intercal}
+\let\vec\mathbf
+\newcommand{\matrx}[1]{{\left[ \stackrel{}{#1}\right]}}
+\newcommand{\diag}[1]{\mbox{diag}\matrx{#1}}
+\newcommand{\goesto}{\rightarrow}
+\newcommand{\dspfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2} }
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{lemma}{Lemma}
+\newtheorem{remark}{Remark}
+\newtheorem{result}{Result}
+\renewcommand\qedsymbol{} % no square at end of proof
+\newcommand{\cl}{\mathbf{L}}
+\newcommand{\cj}{\mathbf{J}}
+\newcommand{\ci}{I}
+
+% NatBib
+\usepackage[round,colon]{natbib}
+
+% Title page
+\title{Can Cultural Transmission Explain The Evolution of Cooperative Behavior?}
+
+% Authors
+\renewcommand\Affilfont{\small}
+
+\author[a]{Dor Cohen}
+\author[b]{Ohad Lewin-Epstein}
+\author[c]{Marcus W. Feldman}
+\author[a,*]{Yoav Ram}
+
+\affil[a]{School of Computer Sciences, IDC Herzliya, Herzliya, Israel}
+\affil[b]{School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv, Israel}
+\affil[c]{Department of Biology, Stanford University, Stanford, CA}
+\affil[*]{Corresponding author: yoav@yoavram.com}
+
+\date{\today}
 
@@
 
+% Abstract
+%\begin{abstract}
+%\end{abstract}
+
+\pagebreak
+
+% Introduction
 \section*{Introduction}
-Cooperative behavior can harm the individual's fitness and increase the fitness of its competitor~\cite{axelrod1981evolution}.
-Yet, cooperative behavior occurs in many non-human animals~\cite{dugatkin1997cooperation}, for example rats~\cite{rice1962altruism} and birds~\cite{krams2008experimental}.
+Cooperative behavior can harm the individual's fitness and increase the fitness of its competitor~\citep{axelrod1981evolution}.
+Yet, cooperative behavior occurs in many non-human animals~\citep{dugatkin1997cooperation}, for example rats~\citep{rice1962altruism} and birds~\citep{krams2008experimental}.
 Therefore, the evolution of cooperative behavior is an important open question in evolutionary biology.
@@
 Cultural evolution is an evolutionary theory of social change.
-Culture has significant impact on the behavior of humans~\cite{ihara2004cultural,jeong2018bronze} as well as non-human animals~\cite{bonner2018evolution}.
-Under the view of cultural evolution, an individual can acquire its behavior from another individual in its social group through learning or other modes of cultural transmission \cite{richerson2008not}.
+Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
+Under the view of cultural evolution, an individual can acquire its behavior from another individual in its social group through learning or other modes of cultural transmission \citep{richerson2008not}.
 Here we attempt to determine to what extent cultural transmission can explain the evolution of cooperative behavior.
 
-\subsection*{Theories for Evolution of Cooperation}
+% subsection
+\subsection*{Theories for evolution of cooperation}
 Three major theories have been proposed to explain the evolution of cooperative behavior.
@@
 \textbf{Kin selection}, proposing that natural selection can favor cooperative behavior between kin.
-The importance of relatedness to the evolution of cooperation and altruism was shown by Hamilton~\cite{hamilton1964genetical}.
+The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}.
 According to Hamilton, kin selection causes allele to increase in frequency when the genetic relatedness $r$ of a recipient to an actor multiplied by the benefit $b$ to the recipient is greater than the reproductive cost $c$ to the actor.
@@
 It has been suggested that kin selection to explain the cooperative behavior of eusocial insects like the honey bee.
-The most significant argument against kin selection is that cooperation can evolve with zero relatedness~\cite{wilson2005kin}.
-This makes Hamilton's rule incomplete according to Wilson~\cite{wilson2005kin}.
-Foster et~al.~\cite{foster2006kin} reject this claim.
+The most significant argument against kin selection is that cooperation can evolve with zero relatedness~\citep{wilson2005kin}.
+This makes Hamilton's rule incomplete according to \citet{wilson2005kin}.
+\citet{foster2006kin} reject this claim.
 They argue that altruism without relatedness can not evolve.
 They refer us to Hamilton who claimed that relatedness can arise without recent common ancestry.
-Wilson also criticises kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions.
-On the other hand, Foster et~al.~\cite{foster2006kin} argue that kin selection does not ignore ecology.
+\citet{wilson2005kin} also criticizes kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions.
+On the other hand, \citet{foster2006kin} argue that kin selection does not ignore ecology.
 Hamilton’s rule shows
@@
 
-\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation.
-In \textit{direct reciprocity} there are a repeated encounters between the same two individuals.
+\paragraph{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation.
+In \emph{direct reciprocity} there are a repeated encounters between the same two individuals.
 In every encounter, each player has a choice between cooperation and defection.
@@
 
-\textbf{Indirect reciprocity} has been suggested to explain this behavior. 
-Nowak~\cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
+\paragraph{Indirect reciprocity} has been suggested to explain this behavior.
+\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
 The money that "fuels the engines" of indirect reciprocity is reputation.
-\\However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.
+However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.
 
-\textbf{Group Selection} theory posits that cooperation is favored because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
+\paragraph{Group selection theory} posits that cooperation is favored because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
 A common model for group selection work as is: the population is divided into groups.
 In each groups there are cooperators, which help to other group members and defectors which do not help.
+% TODO add reference
 Individuals reproduce proportional to their fitness. Offspring are added to the same group.
@@
 The fact that a trait with a lower fitness took over the population is a contradiction.
-Eldar et al.~\cite{eldakar2011eight} reject this argument.
+\citet{eldakar2011eight} reject this argument.
 They believe that this argument is a tautology and does not qualify as an argument against group selection.
@@
 All the above theories assume that cooperation is genetically determined. This raises the question, is it possible that cooperation is determined by non-genetic factors?
-Recent work by Lewin-Epstein at el.~\cite{lewin2017microbes} sheds some light on this question. 
-Lewin-Epstein at el.~\cite{lewin2017microbes} have hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
-Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\cite{poulin2010parasite,dobson1988population}.
+Recent work by \citet{lewin2017microbes} sheds some light on this question. 
+\citet{lewin2017microbes} have hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
+Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{poulin2010parasite,dobson1988population}.
 Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
 Microbes can be transmitted \emph{horizontally} from one host to another during host interactions.
-Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\cite{lewin2017microbes}.
+Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}.
 Microbes can also transfer vertically, from parent to offspring.
-% (yr: cite 10.1126/science.aat7164)
+% yr: cite 10.1126/science.aat7164
 As a result, a microbe that induces its host to cooperate with another host and thereby increases the other host fitness will  increase the vertical transmission of the microbes of the receiving individual.
 Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
-%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\cite{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behavior of their hosts.
+%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\citep{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behavior of their hosts.
 
-\subsection*{Cultural Evolution of Cooperation}
-Lewin-Epstein at el.~\cite{lewin2017microbes} have demonstrated that \emph{non-vertical} transmission can help to explain the evolution of cooperative behavior. 
+% subsection
+\subsection*{Cultural evolution of cooperation}
+\citet{lewin2017microbes} have demonstrated that \emph{non-vertical} transmission can help to explain the evolution of cooperative behavior. 
 Non-vertical transmission could be either a horizontal or oblique.
@@
 Oblique transmission occurs from an adult to an offspring.
-Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission~\cite{ram2018evolution}. % (yr: not sure that this is a good reference)
+Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission~\citep{ram2018evolution}. % (yr: not sure that this is a good reference)
 
@@
 For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future.
-Surprisingly, some of the analysis made by Lewin-Epstein at el.~\cite{lewin2017microbes} can be applied to cultural transmission, because cultural transmission is mathematically akin to transmission of infectious diseases~\cite{cavalli1981cultural}.
+Surprisingly, some of the analysis made by \citet{lewin2017microbes} can be applied to cultural transmission, because cultural transmission is mathematically akin to transmission of infectious diseases~\citep{cavalli1981cultural}.
 
-Here, we hypothesise that non-vertical cultural transmission can explain the evolution of cooperation.
+Here, we hypothesize that non-vertical cultural transmission can explain the evolution of cooperation.
 We are develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.
 
+% Models and Methods
 \section*{Models and Methods}
 
-First, we focus on the evolution of cooperation in a fully mixed population where cooperation is modelled using the prisoner's dilemma. %(yr: add ref)
+First, we focus on the evolution of cooperation in a fully mixed population where cooperation is modeled using the prisoner's dilemma. % yr: add ref
 
@@
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
-Following~\cite{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance, %(yr: cite Zefferman Behav Ecol 2016),
+Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance, % yr: cite Zefferman Behav Ecol 2016
 the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
@@
 
+% Results
 \section*{Results}
@@
 Therefore, cooperative behavior will take over the population when eq. \eqref{result3} is satisfied. 
-This result is in accordance with the result presented by Lewin-Epstein at el. \cite{Ohad}. 
+This result is in accordance with the result presented by Lewin-Epstein at el. \citep{Ohad}. 
 \\\underline{Special case 3 - $\alpha = 0$:} in this case horizontal transmission can not occur as a result of interaction.  
@@
 
-\newpage
-\section*{Conclusions}
+% Discussion
+\section*{Discussion}
 We hypothesized that non-vertical transmission can explain the evolution of cooperation.
-We used a model with non-vertical transmissions and have found that if eq.
-\eqref{result} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff.
+We used a model with non-vertical transmissions and have found that if eq.~\eqref{result} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff.
 In addition, we found that when horizontal transmission cannot occur after interaction ($\alpha = 0$) cooperation will always become extinct.
@@
 
+%\pagebreak
+% Acknowledgements
+{\small
+\section*{Acknowledgements}
+We thank Lilach Hadany and Ayelet Shavit for discussions and comments.
+This work was supported in part by
+the Israel Science Foundation 552/19 (YR).
+% TODO funding for other authors?
+}
+
+% Bibliography
+\bibliographystyle{plainnat}
 \bibliography{bib}
 
+% Appendices
 \newpage
-\section*{Appendix A}
-In the section, we start with eq. \eqref{modeleq} and we want to investigate when $p\leq p'$. We know that $0<p<1$ and $0<c<b$.
+\section*{Appendix A} % TODO fix equations references
+In the section, we start with eq.~\eqref{modeleq} and we want to investigate when $p\leq p'$. We know that $0<p<1$ and $0<c<b$.
 
-We start by multiple by $\overline{\omega}$ The result is shown in eq. \eqref{step1}.
+We start by multiple by $\bar{w}$ The result is shown in eq. \eqref{step1}.
 \begin{equation} 

### 2020-03-05 ms/main.tex
small changes

@@
 
-\textbf{Kin selection}, proposing that natural selection can favor cooperative behavior between kin.
+\paragraph{Kin selection theory} suggests that natural selection can favor cooperative behavior between kin.
 The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}.
@@
 
+\paragraph{}
 All the above theories assume that cooperation is genetically determined. This raises the question, is it possible that cooperation is determined by non-genetic factors?
@@
 \subsection*{Cultural evolution of cooperation}
-\citet{lewin2017microbes} have demonstrated that \emph{non-vertical} transmission can help to explain the evolution of cooperative behavior. 
+\citet{lewin2017microbes} have demonstrated that \emph{non-vertical transmission} can help to explain the evolution of cooperative behavior. 
 Non-vertical transmission could be either a horizontal or oblique.
@@
 
-\paragraph*{Without oblique transmission, $v=1$.} 
 With only vertical transmission eq.~\ref{eq:vertical_oblique_transmission} becomes
@@
 
-\textbf{Result 1.}
+\textbf{Result 1: Vertical and horizontal transmission of cooperation.}
 If 

### 2020-03-14 ms/main.tex

@@
 
-With only vertical transmission eq.~\ref{eq:vertical_oblique_transmission} becomes
+With only vertical transmission eq.~\ref{eq:horizontal} becomes
 $\hat{p} =  \tilde{p}$,
@@
 \bar{w} \tilde{p}' 
-& = p^2 (1+b-c) (1 - (1-p) (1-\alpha) T_B) \\
-& + p(1-p) (1-c) (p (1-\alpha) T_B + 1 - T_B) \\
-& + p(1-p) (1+b) (p (1-\alpha) + \alpha) T_A \\
-& + (1-p)^2 p (1-\alpha) T_A
+& = \tilde{p}^2 (1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
+& + \tilde{p}(1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
+& + \tilde{p}(1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A
 \end{split}
@@
 If 
-\begin{equation}\label{result1}
+\begin{equation}\label{eq:unequal_transmission}
 c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b (p(1-\alpha) - 1)]
@@
 \underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
-\\Eq. \eqref{result0} becomes:
+\\Eq.~\ref{eq:unequal_transmission} becomes:
 \begin{equation} 
-\begin{split} \label{result3}
+\begin{split} \label{eq:horizontal_transmission_only_after_interaction}
 c(1-T_B)  < & \, T_A -T_B +b(T_A-T_B)
@@
 \end{equation}
-Therefore, cooperative behavior will take over the population when eq. \eqref{result3} is satisfied. 
-This result is in accordance with the result presented by Lewin-Epstein at el. \citep{Ohad}. 
+Therefore, cooperative behavior will take over the population when eq.~\ref{eq:horizontal_transmission_only_after_interaction} is satisfied. 
+This result is in accordance with the result presented by~\citet{lewin2017microbes}. 
 \\\underline{Special case 3 - $\alpha = 0$:} in this case horizontal transmission can not occur as a result of interaction.  
-Then, eq. \eqref{result0} becomes:
+Then, eq.~\ref{eq:unequal_transmission} becomes:
 \begin{equation} 
-\begin{split} \label{result4}
+\begin{split} \label{eq:horizontal_transmission_from_population}
 0 < & \,  - bq(1-T_B)- bT_B-c(1-T_B)-T_B
@@
 \\So far, we assumed that $v=1$.
-We believe it will be interesting to test the effect of oblique transmission ($v\neq 1$) since oblique transmission is common in cultural evolution models.
-Therefore, we are planning to simulations to investigate the case when $v\neq 1$.
+The next section discuss the effect of oblique transmission ($v\neq 1$) which is common in cultural evolution models.
+Start by looking on special case where $v=0$.
+In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents} becomes:
+\begin{equation} 
+\begin{split}\label{eq:nextgen_parents_oblique_only}
+\bar{w} p' 
+& = p^2 (1+b-c) (1 - (1-p) (1-\alpha) T_B) \\
+& + p(1-p) (1-c) (p (1-\alpha) T_B + 1 - T_B) \\
+& + p(1-p) (1+b) (p (1-\alpha) + \alpha) T_A \\
+& + (1-p)^2 p (1-\alpha) T_A
+\end{split}
+\end{equation}
+The frequency of phenotype A among parents increases if $\tilde{p}'>\tilde{p}$. From eq.~\ref{eq:nextgen_parents_oblique_only} applies that $\tilde{p}'>\tilde{p}$ is satisfy when
 

### 2020-03-30 ms/main.tex

@@
 For each equilibrium point we will determine whether it is stable equilibrium or not.
-\\So far, we assumed that $v=1$.
-The next section discuss the effect of oblique transmission ($v\neq 1$) which is common in cultural evolution models.
-Start by looking on special case where $v=0$.
-In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents} becomes:
+\\So far, we assumed that $v=1$. The next section discuss the effect of oblique transmission ($v\neq 1$) which is common in cultural evolution models. 
+Start by looking on special case where $v=0$. In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents} becomes:
 \begin{equation} 
 \begin{split}\label{eq:nextgen_parents_oblique_only}
-\bar{w} p' 
-& = p^2 (1+b-c) (1 - (1-p) (1-\alpha) T_B) \\
-& + p(1-p) (1-c) (p (1-\alpha) T_B + 1 - T_B) \\
-& + p(1-p) (1+b) (p (1-\alpha) + \alpha) T_A \\
+p' 
+& = p^2 (1 - (1-p) (1-\alpha) T_B) \\
+& + p(1-p)(p (1-\alpha) + \alpha) T_A \\
+& + p(1-p)((1-\alpha)T_B + (1-\alpha)(p+(1-p)(1-T_B))) \\
 & + (1-p)^2 p (1-\alpha) T_A
@@
 \end{equation}
-The frequency of phenotype A among parents increases if $\tilde{p}'>\tilde{p}$. From eq.~\ref{eq:nextgen_parents_oblique_only} applies that $\tilde{p}'>\tilde{p}$ is satisfy when
+The frequency of phenotype A among adults increases if $p'>p$. From eq.~\ref{eq:nextgen_parents_oblique_only} applies that $p'>p$ is satisfied when:
+\begin{equation} \label{eq:oblique_only_result}
+T_A>T_B  
+\end{equation}
 
@@
 In the third scenario, we want to use a general two player game.
-Prisoner dilemma is an example of a two player game with a payoff matrix shown in figure \ref{fig:payoff}.
+Prisoner dilemma is an example of a two player game with a payoff matrix shown in figure \ref{fig:generalPayoff}.
 We will investigate the general case.
@@
 We hypothesized that non-vertical transmission can explain the evolution of cooperation.
-We used a model with non-vertical transmissions and have found that if eq.~\eqref{result} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff.
+We used a model with non-vertical transmissions and have found that if eq.~\ref{eq:unequal_transmission} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff.
 In addition, we found that when horizontal transmission cannot occur after interaction ($\alpha = 0$) cooperation will always become extinct.
@@
 \section*{Appendix A} % TODO fix equations references
-In the section, we start with eq.~\eqref{modeleq} and we want to investigate when $p\leq p'$. We know that $0<p<1$ and $0<c<b$.
+In the section, we start with eq.~\ref{eq:nextgen_parents} and we want to investigate when $p\leq p'$. We know that $0<p<1$ and $0<c<b$.
 
@@
 Eq. \eqref{step2} becomes eq. \eqref{step3}.
-%\begin{equation} 
-%\begin{split} \label{step3}
-%1 + b - c - q(b-c) < & \, \{ bq^2T_B-b\alpha q^2T_B - bq^2T_A + \alpha bq^2T_A - bq - qT_B - bqT_B + \alpha bqT_B +cqT_B + qT_A + bqT_B + b - c + 1 \}
-%\end{split}
-%\end{equation}
+
 \begin{equation} 
 \begin{split}\label{step3}
- -q(b-c) < & \,  bq^2T_B-b\alpha q^2T_B - bq^2T_A + \alpha bq^2T_A - bq - qT_B - bqT_B + \alpha bqT_B +cqT_B + qT_A + bqT_B 
+ -q(b-c) < & \,  bq^2T_B-b\alpha q^2T_B - bq^2T_A +  \alpha bq^2T_A - bq - qT_B - bqT_B + \\
+ & \alpha bqT_B +cqT_B + qT_A + bqT_B 
 \end{split}

### 2020-04-01 ms/main.tex

@@
 \end{equation}
-The frequency of phenotype A among adults increases if $p'>p$. From eq.~\ref{eq:nextgen_parents_oblique_only} applies that $p'>p$ is satisfied when:
+\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype A among adults increases if $p'>p$.
+From eq.~\ref{eq:nextgen_parents_oblique_only} applies that $p'>p$ is satisfied when:
 \begin{equation} \label{eq:oblique_only_result}
@@
 \end{equation}
-
-\subsection*{Aim 2}
-Prisoner's dilemma is widely studied and most of the models developed in order to learn about evolution of cooperation is using it as the model of interaction's result.
-However, often the reality is different.
-For example, interaction could be between than two individuals.
-In the first aim we hypothesize that non-vertical transmission can explain the evolution of cooperation in fully mixed population with prisoner's dilemma payoff.
-Here, we hypothesize that non-vertical transmission can also explain the evolution of cooperation in fully mixed population with other games.
-The second aim is to determine to what extent our hypothesize could explain the evolution of cooperation.
-We will develop and investigate a cultural evolution model like we did in the first aim but with different games.
-In the first scenario we can use n-player prisoner's dilemma a.k.a unscrupulous diner's dilemma or just diner's dilemma.
-The diner's dilemma is the main game we will investigate.
-In the diner's dilemma we assume that n players are eating in a restaurant.
-There are two dishes in the restaurant: dish1 with cost $c_1$ and benefit $b_1$ and dish2 with cost $c_2$ and benefit $b_2$.
-We also know that $b_2>c_2>b_1>c_1$.
-We presume that one would prefer to order the expensive meal given others will help defray the cost,
-\begin{equation} 
-\begin{split} \label{diner}
-b_2-\frac{1}{n}c_2 >\, & b_1 - \frac{1}{n}c_1.
-\end {split}
-\end{equation}
-Cooperative individual is an individual who choose to take the cheap dish. Choosing the cheap dish increases the fitness of the competitors. 
-In the second scenario we can use public common goods as our game.
-Public common goods is a multiplayer game in which each player can secretly choose how much he want to contribute.
-The contributions from all players is collected and the sum is multiplied by a factor (greater or equal to one) and the result is the "public good".
-The public good is evenly divided among the players.
-A player will be considered as a cooperator if decide to contribute.
-In the third scenario, we want to use a general two player game.
-Prisoner dilemma is an example of a two player game with a payoff matrix shown in figure \ref{fig:generalPayoff}.
-We will investigate the general case.
-The payoff matrix in the general case is shown in figure \ref{fig:generalPayoff}.
-\begin{figure}[h!]
-  \centering
-  \includegraphics[scale=0.4]{generalpayoff.pdf}
-  \caption{General Payoff Matrix}
-  \label{fig:generalPayoff}
-\end{figure}
-
-\subsection*{Aim 3}
-In the previous aims we focused in fully mixed populations.
-Many time in reality, the population is structured.
-When the population is spatially structured, individuals interact only with their neighbors, which are more likely to be related.
-Therefore, cooperators are more likely to interact with cooperators and vice versa.
-Here we hypothesize that non-vertical transmission can also explain the evolution of cooperation in spatially structured population.
-We will develop and investigate a cultural evolution model.
-we will analyse these models with simulations.
 

### 2020-04-05 ms/main.tex

@@
 \begin{equation}\label{eq:unequal_transmission}
-c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b (p(1-\alpha) - 1)]
+c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + bp(1-\alpha)]
 \end{equation}
@@
 \begin{split} \label{eq:horizontal_transmission_only_after_interaction}
-c(1-T_B)  < & \, T_A -T_B +b(T_A-T_B)
+c\cdot(1-T_B)  < \,& T_A\cdot(1+b) - T_B
 \end{split}
@@
 \begin{split} \label{eq:horizontal_transmission_from_population}
-0 < & \,  - bq(1-T_B)- bT_B-c(1-T_B)-T_B
-\end {split}
+c\cdot(1-T_B) < & (T_A-T_B)(1+bp)  
+\end{split}
 \end{equation}
-Which is always false because all of the elements are negative. Therefore, cooperation will eventually disappear from population.
-\\Those are the results we have so far. However, there is a still work need to be done. \\
-We will analyze the equilibrium points in this model.
-We know that $p=1$ is an equilibrium point because if the all individuals in the population are cooperators then in next generation all individual will be cooperator as well.
-Same for $p=0$.
-We will check if there are any more equilibrium points.
-For each equilibrium point we will determine whether it is stable equilibrium or not.
+From eq.~\ref{eq:horizontal_transmission_from_population} we learn that when $T_B\leq T_A$ cooperation will not take over the population.
+When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes:
+\begin{equation} 
+\begin{split} \label{eq:horizontal_transmission_from_population_reorder}
+\frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)} < & p  
+\end{split}
+\end{equation}
+Therefore, in the case $T_A>T_B$ a sufficient condition for cooperation fixation is:
+\begin{equation} 
+  \begin{split} \label{eq:sufficient_horizontal_transmission_from_population}
+c < &\, \frac{T_A-T_B}{1-T_B}  
+  \end{split}
+  \end{equation}
 \\So far, we assumed that $v=1$. The next section discuss the effect of oblique transmission ($v\neq 1$) which is common in cultural evolution models. 
@@
 \section*{Appendix A} % TODO fix equations references
-In the section, we start with eq.~\ref{eq:nextgen_parents} and we want to investigate when $p\leq p'$. We know that $0<p<1$ and $0<c<b$.
-
-We start by multiple by $\bar{w}$ The result is shown in eq. \eqref{step1}.
+In the section, we start with eq.~\ref{eq:nextgen_parents_vertical_only} and we want to investigate when $\tilde{p}< \tilde{p}'$. 
 \begin{equation} 
-\begin{split} \label{step1}
-p + p^2(b-c) < & \, \{ p^2(1+b-c)[1-(1-\alpha)T_Bq] + pq(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
-&+ pq(1+b)[\alpha T_A+(1-\alpha)T_Ap)] + q^2(1-\alpha)T_Ap\}
+\begin{split} \label{eq:horizontal_transmission_from_interaction_step0}
+\bar{w}\tilde{p} < & \, \tilde{p}^2 (1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
+& + \tilde{p}(1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
+& + \tilde{p}(1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A
 \end{split}
 \end{equation}
-
-Divining by p and substituting $p=1-q$ give us eq. \eqref{step2}
+First divide by $\tilde{p}$, thus eq.~\ref{eq:horizontal_transmission_from_interaction_step0} becomes
 \begin{equation} 
-\begin{split} \label{step2}
-1 + (1-q)(b-c) < & \, \{ (1-q)(1+b-c)[1-(1-\alpha)T_Bq] + q(1-c)[1-(1-\alpha)T_Bq-\alpha T_B)]\\
-&+ q(1+b)[\alpha T_A+(1-\alpha)T_A(1-q))] + q^2(1-\alpha)T_A\}
+\begin{split} \label{eq:horizontal_transmission_from_interaction_step1}
+  \bar{w} < & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
+  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
+  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+  & + (1-\tilde{p})^2 (1-\alpha) T_A
 \end{split}
 \end{equation}
-Eq. \eqref{step2} becomes eq. \eqref{step3}.
-
+We know that the mean fitness $\bar{w} = 1 + \tilde{p}(b-c)$, thus eq.~\ref{eq:horizontal_transmission_from_interaction_step1} becomes
 \begin{equation} 
-\begin{split}\label{step3}
- -q(b-c) < & \,  bq^2T_B-b\alpha q^2T_B - bq^2T_A +  \alpha bq^2T_A - bq - qT_B - bqT_B + \\
- & \alpha bqT_B +cqT_B + qT_A + bqT_B 
+\begin{split} \label{eq:horizontal_transmission_from_interaction_step2}
+  1 + \tilde{p}(b-c) < & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
+  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
+  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+  & + (1-\tilde{p})^2 (1-\alpha) T_A
 \end{split}
 \end{equation}
-
-We can divide by q because we know that $0<q<1$ then,
-\begin{equation} 
-\begin{split} \label{step4}
- c(1-T_B) < & \,  bqT_B(1-\alpha) - bqT_A(1-\alpha) + (T_A-T_B) + b(T_A - T_B) + \alpha bT_B.
-\end{split}
-\end{equation}
-
-In the special case when $T_A = T_B = T$ equation \eqref{step4} becomes
-\begin{equation} 
-\begin{split}\label{step5}
-c(1-T) < & \, \alpha bT.
-\end{split}
-\end{equation}
-Eq. \eqref{step5} can be rewritten as
-\begin{equation} 
-\begin{split}
- \frac{1-T}{\alpha T} < \frac{b}{c}.
-\end{split}
-\end{equation}
+Eq.~\ref{eq:horizontal_transmission_from_interaction_step2} can be simplified into eq.~\ref{eq:unequal_transmission}.
 

### 2020-04-05 ms/main.tex
typo, reformatting, headings and paragraphs

@@
 
+\subsection*{Without oblique transmission, $v=1$}
+
 With only vertical transmission eq.~\ref{eq:horizontal} becomes
@@
 then $\tilde{p}' > \tilde{p}$, and the frequency of phenotype $A$ among parents increases. 
+\\
 
@@
 
-%(yr: I stopped here)
+\paragraph*{Complete correlation between transmission and cooperation, $\alpha=1$.}
 
-\underline{Special case 2 - $\alpha =1$:} in this case, horizontal transmission can only occur as a result of interaction.
+In this case, horizontal transmission can only occur as a result of cooperative interactions.
 \\Eq.~\ref{eq:unequal_transmission} becomes:
@@
 This result is in accordance with the result presented by~\citet{lewin2017microbes}.
-\\\underline{Special case 3 - $\alpha = 0$:} in this case horizontal transmission can not occur as a result of interaction.  
+
+\paragraph*{No correlation between transmission and cooperation, $\alpha=0$.}
+
+In this case horizontal transmission can not occur as a result of interaction.  
 Then, eq.~\ref{eq:unequal_transmission} becomes:
@@
 \end{equation}
-From eq.~\ref{eq:horizontal_transmission_from_population} we learn that when $T_B\leq T_A$ cooperation will not take over the population.
+
+Therefore, since $c>0$, cooperation will not take over the population (and furthermore will become extinct) if $T_A\leq T_B$.
 When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes:
@@
 \begin{split} \label{eq:horizontal_transmission_from_population_reorder}
-\frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)} < & p  
+p & > \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)} .
 \end{split}
 \end{equation}
-Therefore, in the case $T_A>T_B$ a sufficient condition for cooperation fixation is:
+Hence, cooperation will take over the population when when eq.~\ref{eq:horizontal_transmission_from_population_reorder} is satisfied, that is if $p$ is above the threshold on the RHS. 
+Specifically, a sufficient condition for cooperation fixation is found by setting the RHS to be negative:
 \begin{equation} 
@@
   \end{equation}
-\\So far, we assumed that $v=1$. The next section discuss the effect of oblique transmission ($v\neq 1$) which is common in cultural evolution models. 
-Start by looking on special case where $v=0$. In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents} becomes:
+
+\subsection*{With oblique transmission, $v<1$}
+
+So far, we assumed that $v=1$. The next section discuss the effect of oblique transmission: transmission from non-parental adults.
+
+\paragraph*{Without vertical transmission, $v = 0$.}
+
+In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents} becomes:
 \begin{equation} 
@@
 \end{equation}
-\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype A among adults increases if $p'>p$.
-From eq.~\ref{eq:nextgen_parents_oblique_only} applies that $p'>p$ is satisfied when:
+
+\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
+From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
 \begin{equation} \label{eq:oblique_only_result}

### 2020-04-11 ms/main.tex

@@
 \end{equation}
+Which can be simplified into
+\begin{equation}\label{eq:nextgen_adults_slimpify}
+  \begin{aligned}
+  p'  & = \hat{p}^2(T_B-T_A) + \hat{p}(1+T_A-T_B) \\
+  \end{aligned}
+  \end{equation}
 
@@
 where $\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$ is the population mean fitness.
+Eq~\ref{eq:nextgen_parents} can be slimpified to
+\begin{equation}\label{eq:nextgen_parents_simplified}
+\begin{aligned}
+\bar{w} \tilde{p}'
+& = \hat{p}^2 (1+b-c) [1-(1-\hat{p}(1-\alpha)T_B)] \\
+& + \hat{p}(1-\hat{p}) (1-c) [\hat{p}(1-\alpha)T_B+1-T_B] \\
+& + (1-\hat{p})\hat{p} (1+b) [\hat{p}(1-\alpha) + \alpha]T_A \\
+& + (1-\hat{p})^2 [(1-\alpha) \hat{p}]T_A,
+\end{aligned}
+\end{equation}
 
@@
 $\hat{p} =  \tilde{p}$,
-and eq.~\ref{eq:nextgen_parents} for the change in frequency $p'$ of phenotype $A$ among parents can be written as
+and eq.~\ref{eq:nextgen_parents_simplified} for the change in frequency $p'$ of phenotype $A$ among parents can be written as
 
@@
 \bar{w} \tilde{p}' 
-& = \tilde{p}^2 (1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
-& + \tilde{p}(1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
-& + \tilde{p}(1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+& = \tilde{p}^2 (1+b-c) [1 - (1-\tilde{p}) (1-\alpha) T_B] \\
+& + \tilde{p}(1-\tilde{p}) (1-c) [\tilde{p} (1-\alpha) T_B + 1 - T_B] \\
+& + \tilde{p}(1-\tilde{p}) (1+b) [\tilde{p} (1-\alpha) + \alpha] T_A \\
 & + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A
@@
 If 
-\begin{equation}\label{eq:unequal_transmission}
-c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + bp(1-\alpha)]
+\begin{equation} \label{eq:unequal_transmission}
+c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b\tilde{p}(1-\alpha)]
 \end{equation}
@@
 \begin{split} \label{eq:horizontal_transmission_from_population}
-c\cdot(1-T_B) < & (T_A-T_B)(1+bp)  
+c\cdot(1-T_B) < & (T_A-T_B)(1+b\tilde{p})  
 \end{split}
@@
 \begin{split} \label{eq:horizontal_transmission_from_population_reorder}
-p & > \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)} .
+\tilde{p} & > \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)}
 \end{split}
 \end{equation}
-Hence, cooperation will take over the population when when eq.~\ref{eq:horizontal_transmission_from_population_reorder} is satisfied, that is if $p$ is above the threshold on the RHS. 
-Specifically, a sufficient condition for cooperation fixation is found by setting the RHS to be negative:
+Hence, cooperation will take over the population when when eq.~\ref{eq:horizontal_transmission_from_population_reorder} is satisfied, that is if $\tilde{p}$ is above the threshold on the RHS. 
+When $\tilde{p}$ is equal to eq.~\ref{eq:horizontal_transmission_from_population_reorder} RSH the frequency of phenotype A do not change. Denote $\tilde{p}^{*}$:
+\begin{equation} 
+\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
+\tilde{p}^{*} & = \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)} .
+\end{split}
+\end{equation}
+Therefore, $\tilde{p}^{*}$ is the third equilibrium in this system.
+Specifically, a sufficient condition for cooperation fixation is found by setting the the equilibrium $\tilde{p}^*$  to be negative:
 \begin{equation} 

### 2020-04-18 ms/main.tex

@@
 It may occur between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{Fig.~\ref{fig:horizontal}}).
-Horizontal transmission is not always successful, as one peer may reject the other's phenotype. The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
-
+Horizontal transmission is not always successful, as one peer may reject the other's phenotype.
+The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.\\
+Table~\ref{table:1} contains the probability of first interactor to be A following interaction by interaction type.
 Therefore, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 \end{equation}
-where $\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$ is the population mean fitness.
+where fitness values are taken from table~\ref{table:1} and $\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$ is the population mean fitness.
 Eq~\ref{eq:nextgen_parents} can be slimpified to
@@
 \end{equation}
+
+\begin{table}[]
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\textbf{Interaction Type} & \textbf{Frequency}    & \textbf{Fitness}      & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Probability of first interactor\\  to be A following interaction\end{tabular}}}                                                                                                     \\ \hline
+\multicolumn{1}{|l|}{}    & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission\\  from partner, \\ probability $\alpha$\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission \\ from population, \\ probability $1-\alpha$\end{tabular}} \\ \hline
+$AxA$                     & $\hat{p}^2$           & $1+b-c$               & $1$                                                                                                               & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
+$AxB$                     & $\hat{p}(1-\hat{p})$  & $1-c$                 & $1-T_B$                                                                                                           & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
+$BxA$                     & $\hat{p}(1-\hat{p})$  & $1+b$                 & $T_A$                                                                                                             & $\hat{p}T_A$                                                                                                           \\ \hline
+$BxB$                     & $(1-\hat{p})^2$       & $1$                   & $0$                                                                                                               & $\hat{p}T_A$                                                                                                           \\ \hline
+\end{tabular}
+\caption{Fitness and probabilityof first interactor to be A following interaction by interaction type}
+\label{table:1}
+\end{table}
 

### 2020-04-23 ms/main.tex
fix typo in eq 9
use autoref

@@
 Horizontal cultural transmission occurs between peers. 
-It may occur between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{Fig.~\ref{fig:horizontal}}).
+It may occur between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{\autoref{fig:horizontal}}).
 Horizontal transmission is not always successful, as one peer may reject the other's phenotype.
 The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.\\
-Table~\ref{table:1} contains the probability of first interactor to be A following interaction by interaction type.
+\autoref{table:1} contains the probability of first interactor to be A following interaction by interaction type.
 Therefore, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 \end{equation}
-where fitness values are taken from table~\ref{table:1} and $\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$ is the population mean fitness.
+where fitness values are taken from \autoref{table:1} and $\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$ is the population mean fitness.
 Eq~\ref{eq:nextgen_parents} can be slimpified to
@@
 \bar{w} \tilde{p}'
-& = \hat{p}^2 (1+b-c) [1-(1-\hat{p}(1-\alpha)T_B)] \\
+& = \hat{p}^2 (1+b-c) [1-(1-\hat{p})(1-\alpha)T_B)] \\
 & + \hat{p}(1-\hat{p}) (1-c) [\hat{p}(1-\alpha)T_B+1-T_B] \\

### 2020-04-23 ms/main.tex
added explanation for alpha=1

@@
 
-%\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
+\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
 \usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
@@
 then $\tilde{p}' > \tilde{p}$, and the frequency of phenotype $A$ among parents increases.
-\\
 
-\textbf{Corollary 1.1: equal horizontal transmission.}
+\textbf{Corollary 1.1: Equal horizontal transmission.}
 If $T=T_A=T_B$, then
@@
 \label{eq:equal_transmission}
-\frac{1-T}{\alpha T} < \frac{b}{c},
+\frac{b}{c} > \frac{1-T}{\alpha T},
 \end{equation}
@@
 In this case, horizontal transmission can only occur as a result of cooperative interactions.
-\\Eq.~\ref{eq:unequal_transmission} becomes:
+Therefore, eq.~\ref{eq:unequal_transmission}, which determines the conditions for evolution of cooperation, becomes
 \begin{equation} 
 \begin{split} \label{eq:horizontal_transmission_only_after_interaction}
-c\cdot(1-T_B)  < \,& T_A\cdot(1+b) - T_B
+T_A b > \,& c (1-T_B) + (T_B - T_A).
 \end{split}
 \end{equation}
-Therefore, cooperative behavior will take over the population when eq.~\ref{eq:horizontal_transmission_only_after_interaction} is satisfied. 
-This result is in accordance with the result presented by~\citet{lewin2017microbes}.
+This is equivalent to a result by~\citet[eq.~1]{lewin2017microbes}.
+Eq.~\ref{eq:horizontal_transmission_only_after_interaction} can be written as
+\begin{equation} 
+\begin{split} \label{eq:horizontal_transmission_only_after_interaction2}
+T_A\cdot(1+b) > \,& 1 - (1-T_B)(1-c).
+\end{split}
+\end{equation}
+This equation provides an interesting interpretation for the success of cooperation. 
+Consider an interaction between two individuals: a cooperator and a defector.
+$T_A\cdot(1+b)$ is the probability that the defector becomes cooperative and reproduces.
+This is the effective benefit for cooperation from this interaction.
+$(1-T_B)(1-c)$ is the probability that the cooperator remains cooperative and also reproduces. 
+Therefore, $1 - (1-T_B)(1-c)$ is the probability that either the cooperator becomes a defector, \emph{or} that it fails to reproduce.
+This is the effective cost for cooperation from this interaction.
+So, eq.~\ref{eq:horizontal_transmission_only_after_interaction2} means that cooperation can evolve if effective benefit is larger than the effective cost.
 

### 2020-04-23 ms/main.tex
more formatting in last section

@@
 In this case horizontal transmission can not occur as a result of interaction.  
-Then, eq.~\ref{eq:unequal_transmission} becomes:
+Then, eq.~\ref{eq:unequal_transmission} becomes
 \begin{equation} 
 \begin{split} \label{eq:horizontal_transmission_from_population}
-c\cdot(1-T_B) < & (T_A-T_B)(1+b\tilde{p})  
+c\cdot(1-T_B) < & (T_A-T_B)(1+b\tilde{p}).
 \end{split}
@@
 Therefore, since $c>0$, cooperation will not take over the population (and furthermore will become extinct) if $T_A\leq T_B$.
-When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes:
+When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes
 \begin{equation} 
 \begin{split} \label{eq:horizontal_transmission_from_population_reorder}
-\tilde{p} & > \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)}
+\tilde{p} & > \frac{c\cdot(1-T_B) - (T_A-T_B)}{b\cdot(T_A-T_B)}.
 \end{split}
 \end{equation}
-Hence, cooperation will take over the population when when eq.~\ref{eq:horizontal_transmission_from_population_reorder} is satisfied, that is if $\tilde{p}$ is above the threshold on the RHS. 
-When $\tilde{p}$ is equal to eq.~\ref{eq:horizontal_transmission_from_population_reorder} RSH the frequency of phenotype A do not change. Denote $\tilde{p}^{*}$:
+Hence, cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$, which is given by
 \begin{equation} 
 \begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
-\tilde{p}^{*} & = \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)} .
+\tilde{p}^{*} & = \frac{c\cdot(1-T_B)}{b\cdot(T_A-T_B)} - \frac{1}{b}.
 \end{split}
 \end{equation}
-Therefore, $\tilde{p}^{*}$ is the third equilibrium in this system.
-Specifically, a sufficient condition for cooperation fixation is found by setting the the equilibrium $\tilde{p}^*$  to be negative:
+A sufficient condition for evolution of cooperation is, then,
 \begin{equation} 
 \begin{split} \label{eq:sufficient_horizontal_transmission_from_population}
-c < &\, \frac{T_A-T_B}{1-T_B}  
+\frac{T_A-T_B}{1-T_B} > &\ c.  
 \end{split}
@@
 
-So far, we assumed that $v=1$. The next section discuss the effect of oblique transmission: transmission from non-parental adults.
+We now discuss the effect of oblique transmission, i.e. transmission from non-parental adults.
 
@@
 \begin{equation} \label{eq:oblique_only_result}
-T_A>T_B  
+T_A>T_B. 
 \end{equation}
+% TODO proof.
 

### 2020-05-01 ms/main.tex

@@
 
-In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents} becomes:
+In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents_simplified} becomes:
 \begin{equation} 
 \begin{split}\label{eq:nextgen_parents_oblique_only}
-p' 
-& = p^2 (1 - (1-p) (1-\alpha) T_B) \\
-& + p(1-p)(p (1-\alpha) + \alpha) T_A \\
-& + p(1-p)((1-\alpha)T_B + (1-\alpha)(p+(1-p)(1-T_B))) \\
-& + (1-p)^2 p (1-\alpha) T_A
+p' = p^2\cdot(T_B-T_A) + p\cdot(1+T_A-T_B)
 \end{split}
@@
 \end{equation}
-% TODO proof.
 

### 2020-05-16 ms/main.tex
Add figures

@@
 % TeX will automatically convert eps --> pdf in pdflatex
+\graphicspath{ {./Figures/} }
+\usepackage{subcaption}
+\usepackage{float}
 
@@
 
-\begin{table}[]
+\begin{table}[H]
 \begin{tabular}{|c|c|c|c|c|}
@@
   \centering
-  \includegraphics[scale=1]{figure.pdf}
+  \includegraphics[scale=1]{figure1.pdf}
   \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interaction partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
@@
 which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}).
+When the ratio $\frac{b}{c}$ is larger than the RHS of eq.~\ref{eq:equal_transmission} cooperation will take over of the population (see~\textbf{\autoref{fig:results_a}}).
 
@@
 \end{equation}
-Hence, cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$, which is given by
+Hence, cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$ (see~\textbf{\autoref{fig:results_b}}), which is given by
 \begin{equation} 
@@
 \end{equation}
+Therefore, fixation occur when $T_A>T_B$ (see~\textbf{\autoref{fig:results_c}}).
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{8cm}
+    \includegraphics[scale=0.5]{figure2a.pdf}
+    \caption{$V=1$, $T_A=T_B=T$, $\alpha \neq 0$}
+    \label{fig:results_a}
+  \end{subfigure}
+  \begin{subfigure}{8cm}
+    \includegraphics[scale=0.5]{figure2b.pdf}
+    \caption{$V=1$, $\alpha = 0$}
+    \label{fig:results_b}
+  \end{subfigure}
+  \begin{subfigure}{8cm}
+    \includegraphics[scale=0.5]{figure2c.pdf}
+    \caption{$V=0$}
+    \label{fig:results_c}
+  \end{subfigure}
+  \label{fig:results}
+  \caption{numerical results}
+\end{figure}
 

### 2020-05-30 ms/main.tex
horizontal_and_obliuqe_results

@@
 
-In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents_simplified} becomes:
+In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents_simplified} becomes
 \begin{equation} 
@@
 \textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
-From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
+From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when
 \begin{equation} \label{eq:oblique_only_result}
@@
 Therefore, fixation occur when $T_A>T_B$ (see~\textbf{\autoref{fig:results_c}}).
+
+\textbf{With vertical transmission $0<v<1$}
+In this case we will not look for global fixation as we did in previous cases.
+For simplicity, we will invsetigate local equilibriums. We will use eq.~\ref{eq:nextgen_adults_slimpify}
+and eq.~\ref{eq:nextgen_parents_simplified} and substitute it in eq.~\ref{eq:horizontal}.
+We are looking for the equilibrium $p^*$ which happens when $\hat{p}' = \hat{p}$ and we get
+\begin{equation} \label{eq:oblique_and_vertic_result}
+  \hat{p}^* =  \frac{\alpha bvT_A + cvT_B + T_A-T_B}{\alpha bv\cdot(T_A-T_B)- b\cdot(T_A-T_B) - cv\cdot(T_A-T_B) + c\cdot(T_A-T_B)}
+\end{equation}
 

### 2020-06-20 ms/main.tex
Add more results for general case

@@
 and eq.~\ref{eq:nextgen_parents_simplified} and substitute it in eq.~\ref{eq:horizontal}. 
-We are looking for the equilibrium $p^*$ which happens when $\hat{p}' = \hat{p}$ and we get
-\begin{equation} \label{eq:oblique_and_vertic_result}
-  \hat{p}^* =  \frac{\alpha bvT_A + cvT_B + T_A-T_B}{\alpha bv\cdot(T_A-T_B)- b\cdot(T_A-T_B) - cv\cdot(T_A-T_B) + c\cdot(T_A-T_B)}
+By doing this we get a single equation depending only on $\hat{p}$.
+For simplicity, Let's assume that $T_A = T_B = T$ so we will get
+\begin{equation} \label{eq:equal_horizontal_transmission}
+  \hat{p}' - \hat{p} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
 \end{equation}
 
+We are looking for the equilibrium $\hat{p}^*$ which happens when $\hat{p}' = \hat{p}$ and we get two equilibriums
+
+\textbf{Result 2.1: equliburims with equal horizontal transmission $T$ and vertical transmission $0<v<1$}
+\begin{equation} \label{eq:result2.1}
+  \hat{p}^*_0 =  0, \, \hat{p}^*_1 = 1
+\end{equation}
+We would like to know under what condition fixation of cooperation is stable. 
+In order to do that we find the derivative  $f(\hat{p}) = \hat{p}'-\hat{p}$.
+\begin{equation} \label{eq:derivative_of_phattag-phat}
+ f'(\hat{p}) = 2\cdot\hat{p} (-\alpha bvT + cv(1-T)) + (\alpha bvT -cv(1-T)).
+\end{equation}
+We are interested in the case when when $\hat{p} = \hat{p}^*_1=1$ therefore
+$f'(1) = -\alpha bvT + cv(1-T)$. Therefore, fixation of cooperation is stable when
+\textbf{Results 2.2: condition for stability of fixation of cooperation}
+\begin{equation} \label{eq:oblique_and_vertic_result}
+  \frac{b}{c}>\frac{1-T}{\alpha T}
+\end{equation}
+Which is the same condition we get in corollary 1.1.
+Now let's assume that the general case where $T_A \neq T_B$ and we get that
+\begin{equation} \label{eq:general_case_polynomial}
+  \hat{p}'-\hat{p} = \beta_1p^3 + \beta_2 p^2 + \beta_3p + \beta_4
+\end{equation}
+where 
+\begin{equation} \label{eq:polynomial_coefficients}
+\begin{split}
+  & \beta_1 = c(1-v)\cdot(T_A-T_B) -b (1-\alpha v) \cdot(T_A-T_B) \\
+  & \beta_2 = (b(1-\alpha v)-c(1-v)-1)(T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
+  & \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \\
+  & \beta_4 = 0
+\end{split}
+\end{equation}
+Since the degree of eq.~\ref{eq:general_case_polynomial} is a third degree polynomial,
+three equilibrium exist. We already know that $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibrium.
+We can find the third equilibrium by finding wehen eq.~\ref{eq:general_case_polynomial} is equal to zero and we get
+\begin{equation} \label{eq:oblique_and_vertic_result}
+  \hat{p}^*_2 =  \frac{\alpha bvT_A + cvT_B + T_A-T_B-cv}{c(1-v)\cdot(T_A-T_B) -b (1-\alpha v) \cdot(T_A-T_B)}
+\end{equation}
+Next we would like to learn under what conditions $\hat{p}^*_2$ is locally stable. 
+For simplicity let's assume that $T_A > T_B$ and we will check when $\hat{p}^*_0 \, \hat{p}^*_1$ are stable.
+In order to do that we find the derivative  $f(\hat{p}) = \hat{p}'-\hat{p}$ of $\hat{p}$.
+\begin{equation} \label{eq:derivative_of_phattag-phat2}
+  f'(\hat{p}) = 3\beta_0 \hat{p}^2 + 2\beta_1\hat{p}^2 + \beta_3
+ \end{equation}
+ When $\hat{p} = \hat{p}^*_0 = 0$ we get
+ \begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
+  f'(0) = \beta_3
+ \end{equation}
+ Therefore, $\hat{p}^*_0$ is stable when
+ \begin{equation} \label{eq:p=0_stability_condition}
+  f'(0) = \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) < 0
+ \end{equation}
+ And $\hat{p}^*_1=1$ is stable when
+ \begin{equation} \label{eq:p=1_stability_condition}
+  f'(1) =3\beta_1 + 2\beta_2 +\beta_3 = cv + (T_A-T_B)(b-c) - T_B(1+\alpha bv)  + T_A(1-cv) < 0
+ \end{equation}
+
+>>>>>>> Stashed changes
 \begin{figure}[H]

### 2020-07-04 ms/main.tex
fix merge issue
Add more results - find stability of equilibrium points

@@
 \textbf{Results 2.2: condition for stability of fixation of cooperation}
-\begin{equation} \label{eq:oblique_and_vertic_result}
+\begin{equation} \label{eq:oblique_and_vertic_result2}
   \frac{b}{c}>\frac{1-T}{\alpha T}
@@
 three equilibrium exist. We already know that $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibrium.
-We can find the third equilibrium by finding wehen eq.~\ref{eq:general_case_polynomial} is equal to zero and we get
+We can find the third equilibrium by finding when eq.~\ref{eq:general_case_polynomial} is equal to zero and we get
 \begin{equation} \label{eq:oblique_and_vertic_result}
@@
 \end{equation}
-Next we would like to learn under what conditions $\hat{p}^*_2$ is locally stable. 
-For simplicity let's assume that $T_A > T_B$ and we will check when $\hat{p}^*_0 \, \hat{p}^*_1$ are stable.
+We would like to know when $\hat{p}_2$ is realistic meaning $0<\hat{p}_2<1$.  
 In order to do that we find the derivative  $f(\hat{p}) = \hat{p}'-\hat{p}$ of $\hat{p}$.
@@
  \end{equation}
- When $\hat{p} = \hat{p}^*_0 = 0$ we get
+We assume that $T_A>T_B$ and we get that $\beta_1<0$ since $c(1-v)-b(1-\alpha v)<0$ and $c<b$ $v<1$.
+In this case the polynomial goes to $\infty$ when $\hat{p}$ goes to infinity. 
+Therefore, if $\hat{p}_2$ is positive then $f'(0)$ must be negative
 \begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
@@
  \end{equation}
- Therefore, $\hat{p}^*_0$ is stable when
- \begin{equation} \label{eq:p=0_stability_condition}
-  f'(0) = \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) < 0
+$\hat{p}_2>0$ when $\beta_3<0$. In addition, $\hat{p}_0=0$ is stable when $|f'(0)|<1$ therefore, when $-1<\beta_3<1$. We can prove that $-1<\beta_3$:
+\begin{equation} \label{eq:beta3-condition}
+  \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) > -cv(1-T_B) > -1
 \end{equation}
- And $\hat{p}^*_1=1$ is stable when
- \begin{equation} \label{eq:p=1_stability_condition}
-  f'(1) =3\beta_1 + 2\beta_2 +\beta_3 = cv + (T_A-T_B)(b-c) - T_B(1+\alpha bv)  + T_A(1-cv) < 0
+Therefore, when $\hat{p}_2>0$ we get that $-1<\beta_3<0$ and $\hat{p}_0=0$ is always stable.
+
+Now we would like to find when $\hat{p}_2<1$. If $T_A>T_B$ like before then the polynomial goes to minus infinity when $\hat{p}$ goes to infinity.
+Hence, if $\hat{p}_2<1$ then $f'(1)$ must be negative
+\begin{equation} \label{eq:derivative_of_phattag-phat_p=1}
+  f'(0) = \beta_1 - \beta_3
 \end{equation}
+Therefore, $\hat{p}_2<1$ when $\beta_1-\beta_3<0$. In addition, $\hat{p}_1=1$ is stable when $|f'(1)|<1$ therefore, when $-1<\beta_1-\beta_3<1$. 
+We can prove that when $0<\hat{p}_2<1$ hence $\beta_3<0$ and $\beta_1-\beta_3<0$ we get that $-1<\beta_1-\beta_3$:
+\begin{equation} \label{eq:beta1-beta3-condition}
+ \beta_1 - \beta_3 > - \beta_3 > 0 > -1
+\end{equation}
+which means that when $0<\hat{p}_2<1$ then $\hat{p}_1=1$ is always stable.
 
->>>>>>> Stashed changes
+\textbf{result 2.3}: for the case when $T_A>T_B$ $\hat{p_2}$ is realistic when $\beta_1<\beta_3<0$ and is always unstable equilibrium.
+
+\textbf{result 2.4}: for the case when $T_B>T_A$ $\hat{p_2}$ is realistic when $\beta_1>\beta_3>0$ and is always unstable equilibrium.
+
 \begin{figure}[H]

### 2020-07-06 ms/main.tex
revised alot, but stuck in the last part

--- 2020-05-30 ms/main.tex
@@
 % Title page
-\title{Can Cultural Transmission Explain The Evolution of Cooperative Behavior?}
+\title{Cultural Transmission Can Explain the Evolution of Cooperative Behavior}
 
@@
 
-\author[a]{Dor Cohen}
-\author[b]{Ohad Lewin-Epstein}
-\author[c]{Marcus W. Feldman}
+\author[1]{Dor Cohen}
+\author[2]{Ohad Lewin-Epstein}
+\author[3]{Marcus W. Feldman}
 \author[a,*]{Yoav Ram}
 
-\affil[a]{School of Computer Sciences, IDC Herzliya, Herzliya, Israel}
-\affil[b]{School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv, Israel}
-\affil[c]{Department of Biology, Stanford University, Stanford, CA}
+\affil[1]{School of Computer Sciences, IDC Herzliya, Herzliya, Israel}
+\affil[2]{School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv, Israel}
+\affil[3]{Department of Biology, Stanford University, Stanford, CA}
 \affil[*]{Corresponding author: yoav@yoavram.com}
@@
 The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}.
-According to Hamilton, kin selection causes allele to increase in frequency when the genetic relatedness $r$ of a recipient to an actor multiplied by the benefit $b$ to the recipient is greater than the reproductive cost $c$ to the actor.
+According to Hamilton, kin selection causes allele to increase in frequency when the the reproductive cost to the actor, $c$, is less than the benefit to the recipient, $b$, times the genetic relatedness between the recipient and the actor, $r$.
 This is also known as Hamilton's Rule:
@@
 \begin{equation} \label{eq:hamilton_rule}
-c<rb
+c < b \cdot r.
 \end{equation}
@@
 On the other hand, \citet{foster2006kin} argue that kin selection does not ignore ecology.
-Hamilton’s rule shows
+Hamilton's rule shows
 that environmental factors causing a high benefit-to-cost ratio will favor cooperation.
@@
 However,
-Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit.
+Direct reciprocity can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability for another encounter between the same two individuals, $w$,
 
 \begin{equation} \label{eq:reciprocity}
-c<bw
+c < b \cdot w.
 \end{equation}
@@
 Individuals reproduce proportional to their fitness. Offspring are added to the same group.
-If a group reaches a certain size it can split to two groups. A group that grow faster will split more often. Groups of cooperators are growing faster than group of defectors.
-Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
+If a group reaches a certain size it can split to two groups. A group that grow faster will split more often.
+Groups of cooperators are growing faster than group of defectors.
+Therefore, cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
 
 \begin{equation} \label{eq:groupselection}
-\frac{b}{c}>1+\frac{n}{m}
+c < b \cdot \frac{m}{m+n} .
 \end{equation}
@@
 & + (1-\hat{p})\hat{p} [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
-& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A]
+& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A] \;,
 \end{aligned}
 \end{equation}
-Which can be simplified into
+which can be simplified into
 \begin{equation}\label{eq:nextgen_adults_slimpify}
-  \begin{aligned}
-  p'  & = \hat{p}^2(T_B-T_A) + \hat{p}(1+T_A-T_B) \\
-  \end{aligned}
+p' = \hat{p}^2(T_B-T_A) + \hat{p}(1+T_A-T_B) .
 \end{equation}
@@
 & + (1-\hat{p})\hat{p} (1+b) [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
-& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A],
+& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A] \;,
 \end{aligned}
@@
 \bar{w} \tilde{p}'
-& = \hat{p}^2 (1+b-c) [1-(1-\hat{p})(1-\alpha)T_B)] \\
-& + \hat{p}(1-\hat{p}) (1-c) [\hat{p}(1-\alpha)T_B+1-T_B] \\
-& + (1-\hat{p})\hat{p} (1+b) [\hat{p}(1-\alpha) + \alpha]T_A \\
-& + (1-\hat{p})^2 [(1-\alpha) \hat{p}]T_A,
+& = \hat{p}^2 (1+b-c) \big(1-(1-\hat{p})(1-\alpha)T_B)\big) \\
+& + \hat{p}(1-\hat{p}) (1-c) \big(\hat{p}(1-\alpha)T_B+1-T_B\big) \\
+& + (1-\hat{p})\hat{p} (1+b) \big(\hat{p}(1-\alpha) + \alpha\big) T_A \\
+& + (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
 \end{aligned}
@@
 
-\subsection*{Without oblique transmission, $v=1$}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Without Oblique Transmission}
 
-With only vertical transmission eq.~\ref{eq:horizontal} becomes
+With only vertical and horizontal transmission, i.e. $v=1$, eq.~\ref{eq:horizontal} becomes
 $\hat{p} =  \tilde{p}$,
@@
 
+We find the following result and corollaries.
+
 \textbf{Result 1: Vertical and horizontal transmission of cooperation.}
@@
 \end{equation}
-then $\tilde{p}' > \tilde{p}$, and the frequency of phenotype $A$ among parents increases.
+then $\tilde{p}' > \tilde{p}$, and the frequency of the cooperator phenotype $A$ among parents increases every generation.
 
-\textbf{Corollary 1.1: Equal horizontal transmission.}
+\textbf{Corollary 1.1: Symmetric horizontal transmission.}
 If $T=T_A=T_B$, then
@@
 \label{eq:equal_transmission}
-\frac{b}{c} > \frac{1-T}{\alpha T},
+c < b \cdot \frac{\alpha T}{1-T},
 \end{equation}
-which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}).
-When the ratio $\frac{b}{c}$ is larger than the RHS of eq.~\ref{eq:equal_transmission} cooperation will take over of the population (see~\textbf{\autoref{fig:results_a}}).
+which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}), where $r_H=\alpha T/(1-T)$ can be thought of as \emph{horizontal relatedness}.
+Therefore, if the cost $c$ is less than the benefit $b$ times the horizontal relatedness $r_H$, then cooperation will take over of the population (see~\textbf{\autoref{fig:results_a}}).
 
-\paragraph*{Complete correlation between transmission and cooperation, $\alpha=1$.}
+\textbf{Corollary 1.2: Complete correlation between transmission and cooperation.}
 
-In this case, horizontal transmission can only occur as a result of cooperative interactions.
+In this case $\alpha=1$, and horizontal transmission can only occur as a result of cooperative interactions.
 Therefore, eq.~\ref{eq:unequal_transmission}, which determines the conditions for evolution of cooperation, becomes
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_only_after_interaction}
-T_A b > \,& c (1-T_B) + (T_B - T_A).
-\end{split}
+\begin{equation}\label{eq:horizontal_transmission_only_after_interaction}
+c \cdot (1-T_B) < b \cdot T_A + (T_A - T_B).
 \end{equation}
 This is equivalent to a result by~\citet[eq.~1]{lewin2017microbes}.
+
 Eq.~\ref{eq:horizontal_transmission_only_after_interaction} can be written as
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_only_after_interaction2}
-T_A\cdot(1+b) > \,& 1 - (1-T_B)(1-c).
-\end{split}
+\begin{equation} \label{eq:horizontal_transmission_only_after_interaction2}
+1 - (1-T_B)(1-c) < T_A \cdot (1+b) ,
 \end{equation}
-This equation provides an interesting interpretation for the success of cooperation. 
+which provides an interesting interpretation for the success of cooperation. 
 Consider an interaction between two individuals: a cooperator and a defector.
-$T_A\cdot(1+b)$ is the probability that the defector becomes cooperative and reproduces.
-This is the effective benefit for cooperation from this interaction.
 $(1-T_B)(1-c)$ is the probability that the cooperator remains cooperative and also reproduces. 
@@
 This is the effective cost for cooperation from this interaction.
-So, eq.~\ref{eq:horizontal_transmission_only_after_interaction2} means that cooperation can evolve if effective benefit is larger than the effective cost.
+$T_A\cdot(1+b)$ is the probability that the defector becomes cooperative and reproduces.
+This is the effective benefit for cooperation from this interaction.
+So, eq.~\ref{eq:horizontal_transmission_only_after_interaction2} means that cooperation can evolve if effective cost is less than the effective benefit.
 
-\paragraph*{No correlation between transmission and cooperation, $\alpha=0$.}
+\textbf{Corollary 1.3: No correlation between transmission and cooperation.}
 
-In this case horizontal transmission can not occur as a result of interaction.  
+In this case $\alpha=0$, and horizontal transmission is entirely independent from cooperative interactions.  
 Then, eq.~\ref{eq:unequal_transmission} becomes
+\begin{equation} \label{eq:horizontal_transmission_from_population}
+c\cdot(1-T_B) < b \cdot \tilde{p} \;(T_A-T_B) + (T_A-T_B). 
+\end{equation}
+
+Therefore, because all the parameters are all positive, cooperation cannot take over the population (and furthermore will become extinct) if cooperators doesn't have a horizontal transmission bias, i.e.
+if $T_A\leq T_B$.
+When such a bias does exist, $T_A > T_B$, then cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$, where (see also ~\textbf{\autoref{fig:results_b}})
 \begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_from_population}
-c\cdot(1-T_B) < & (T_A-T_B)(1+b\tilde{p}).
+\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
+\tilde{p}^{*} & = \frac{c}{b} \cdot \frac{1-T_B}{T_A-T_B} - \frac{1}{b}.
+\end{split}
+\end{equation}
+A sufficient condition for evolution of cooperation is that $\tilde{p}^{*} < 0$, which occurs if
+\begin{equation} \label{eq:sufficient_horizontal_transmission_from_population}
+c < \frac{T_A-T_B}{1-T_B} .  
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Without Vertical Transmission}
+
+With only oblique and horizontal transmission, i.e.
+$v = 0$, eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
+\begin{equation}  \label{eq:nextgen_parents_oblique_only}
+p' = p^2 (T_B-T_A) + p (1+T_A-T_B) .
+\end{equation}
+
+We find the following results.
+
+\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
+Using eq.~\ref{eq:nextgen_parents_oblique_only}, we find that $p'>p$ occurs when
+\begin{equation} \label{eq:oblique_only_result}
+T_A > T_B . 
+\end{equation}
+Therefore, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~\textbf{\autoref{fig:results_c}}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{With Vertical and Oblique Transmission}
+
+In this case $0<v<1$, and the equation system is more complex than before.
+Therefore, we focus on local rather than global stability, which was the case so far.\\
+To proceed, we note that 
+eq.~\ref{eq:horizontal} can give $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$,
+eq.~\ref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\hat{p}$, and 
+eq.~\ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
+Combining these equations, we will find an equation for $\hat{p}'$ as a function of $\hat{p}$.
+We will then determine the equilibria of this function, that is, solutions for $\hat{p}' = \hat{p}$, and their stability.
+
+\textbf{Result 3: Oblique and vertical transmission of cooperation with symmetric horizontal transmission.}
+
+Assuming equal horizontal transmission, i.e. $T_A = T_B = T$, and following the above procedure, we have
+\begin{equation} \label{eq:equal_horizontal_transmission}
+%\hat{p}' - \hat{p} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
+\bar{w} (\hat{p}' - \hat{p}) =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
+\end{equation}
+
+It is easy to see that $\hat{p}^*_0 =  0$ and $\hat{p}^*_1 = 1$ are equilibria of eq.~\ref{eq:equal_horizontal_transmission}, that is, both extinction and fixation of the cooperator phenotype are equilibria.
+
+%TODO fix the following, you forgot wbar in eq:equal_horizontal_transmission
+In order to do that we find the derivative  $f(\hat{p}) = \hat{p}'-\hat{p}$.
+\begin{equation} \label{eq:derivative_of_phattag-phat}
+ f'(\hat{p}) = 2\cdot\hat{p} (-\alpha bvT + cv(1-T)) + (\alpha bvT -cv(1-T)).
+\end{equation}
+We are interested in the case when when $\hat{p} = \hat{p}^*_1=1$ therefore
+$f'(1) = -\alpha bvT + cv(1-T)$. Therefore, fixation of cooperation is stable when
+\begin{equation} \label{eq:oblique_and_vertic_result2}
+  \frac{b}{c}>\frac{1-T}{\alpha T}
+\end{equation}
+Which is the same condition we get in corollary 1.1.
+
+\textbf{Result 4: Oblique and vertical transmission of cooperation with asymmetric horizontal transmission.}
+
+Next, we study the general case where $T_A \neq T_B$. We have
+%TODO check again, I think you forgot wbar here, too
+\begin{equation} \label{eq:general_case_polynomial}
+  f(\hat{p}) = \hat{p}'-\hat{p} = \beta_1 p^3 + \beta_2 p^2 + \beta_3 p
+\end{equation}
+where 
+\begin{equation} \label{eq:polynomial_coefficients}
+\begin{split}
+  & \beta_1 = c(1-v)\cdot(T_A-T_B) -b (1-\alpha v) \cdot(T_A-T_B) \\
+  & \beta_2 = (b(1-\alpha v)-c(1-v)-1)(T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
+  & \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B)
 \end{split}
@@
 
-Therefore, since $c>0$, cooperation will not take over the population (and furthermore will become extinct) if $T_A\leq T_B$.
-When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_from_population_reorder}
-\tilde{p} & > \frac{c\cdot(1-T_B) - (T_A-T_B)}{b\cdot(T_A-T_B)}.
-\end{split}
-\end{equation}
-Hence, cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$ (see~\textbf{\autoref{fig:results_b}}), which is given by
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
-\tilde{p}^{*} & = \frac{c\cdot(1-T_B)}{b\cdot(T_A-T_B)} - \frac{1}{b}.
-\end{split}
-\end{equation}
-A sufficient condition for evolution of cooperation is, then,
-\begin{equation} 
-\begin{split} \label{eq:sufficient_horizontal_transmission_from_population}
-\frac{T_A-T_B}{1-T_B} > &\ c.  
-\end{split}
+$f(\hat{p})$ is a cubic, and its three roots are the equilibria of the system, i.e. the solutions for $\hat{p}'=\hat{p}$.
+As $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibria, there is only one equilibrium left, $\hat{p}^*_2$, which solves $f(\hat{p})/\big(\hat{p}(1-\hat{p})\big)=0$. Solving this we find that
+\begin{equation} \label{eq:oblique_and_vertic_result}
+  \hat{p}^*_2 =  \frac{\alpha bvT_A + cvT_B + T_A-T_B-cv}{c(1-v)\cdot(T_A-T_B) -b (1-\alpha v) \cdot(T_A-T_B)}
 \end{equation}
 
-\subsection*{With oblique transmission, $v<1$}
+$\hat{p}^*_2$ is a legitimate equilibrium if $0<\hat{p}^*_2<1$.  
+To determine if $\hat{p}^*_2$ is legitimate, we need the derivative of $f(\hat{p})$,\begin{equation} \label{eq:derivative_of_phattag-phat2}
+  f'(\hat{p}) = 3\beta_0 \hat{p}^2 + 2\beta_1\hat{p}^2 + \beta_3.
+ \end{equation}
+First, we assume that $T_A>T_B$, and therefore $\beta_1<0$, because $c(1-v)-b(1-\alpha v)<0$ and $c<b$ $v<1$. % why?
+In this case $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to infinity. 
+Therefore, if $\hat{p}^*_2$ is positive then $f'(0)= \beta_3$ must be negative, and
+% TODO remove
+%\begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
+%  f'(0) = \beta_3
+% \end{equation} 
+$\hat{p}_2^*>0$ when $\beta_3<0$. In addition, $\hat{p}^*_0=0$ is stable when $|f'(0)|<1$ therefore, when $-1<\beta_3<1$. We can show that 
+\begin{equation} \label{eq:beta3-condition}
+  \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) > -cv(1-T_B) > -1
+\end{equation}
+Therefore, when $\hat{p}^*_2>0$ we get that $-1<\beta_3<0$ and $\hat{p}^*_0=0$ is locally stable.
 
-We now discuss the effect of oblique transmission, i.e. transmission from non-parental adults.
+Next we would like to find when $\hat{p}^*_2<1$.
+If $T_A>T_B$ like before then the polynomial goes to minus infinity when $\hat{p}$ goes to infinity.
+Hence, if $\hat{p}_2<1$ then $f'(1)$ must be negative
+\begin{equation} \label{eq:derivative_of_phattag-phat_p=1}
+  f'(0) = \beta_1 - \beta_3
+\end{equation}
+Therefore, $\hat{p}_2<1$ when $\beta_1-\beta_3<0$. In addition, $\hat{p}_1=1$ is stable when $|f'(1)|<1$ therefore, when $-1<\beta_1-\beta_3<1$. 
+We can prove that when $0<\hat{p}_2<1$ hence $\beta_3<0$ and $\beta_1-\beta_3<0$ we get that $-1<\beta_1-\beta_3$:
+\begin{equation} \label{eq:beta1-beta3-condition}
+ \beta_1 - \beta_3 > - \beta_3 > 0 > -1
+\end{equation}
+which means that when $0<\hat{p}_2<1$ then $\hat{p}_1=1$ is always stable.
 
-\paragraph*{Without vertical transmission, $v = 0$.}
+\textbf{result 2.3}: for the case when $T_A>T_B$ $\hat{p_2}$ is realistic when $\beta_1<\beta_3<0$ and is always unstable equilibrium.
 
-In this case eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_parents_simplified} becomes
-\begin{equation} 
-\begin{split}\label{eq:nextgen_parents_oblique_only}
-p' = p^2\cdot(T_B-T_A) + p\cdot(1+T_A-T_B)
-\end{split}
-\end{equation}
-
-\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
-From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when
-\begin{equation} \label{eq:oblique_only_result}
-T_A>T_B. 
-\end{equation}
-Therefore, fixation occur when $T_A>T_B$ (see~\textbf{\autoref{fig:results_c}}).
-
-\textbf{With vertical transmission $0<v<1$}
-In this case we will not look for global fixation as we did in previous cases.
-For simplicity, we will invsetigate local equilibriums. We will use eq.~\ref{eq:nextgen_adults_slimpify}
-and eq.~\ref{eq:nextgen_parents_simplified} and substitute it in eq.~\ref{eq:horizontal}.
-We are looking for the equilibrium $p^*$ which happens when $\hat{p}' = \hat{p}$ and we get
-\begin{equation} \label{eq:oblique_and_vertic_result}
-  \hat{p}^* =  \frac{\alpha bvT_A + cvT_B + T_A-T_B}{\alpha bv\cdot(T_A-T_B)- b\cdot(T_A-T_B) - cv\cdot(T_A-T_B) + c\cdot(T_A-T_B)}
-\end{equation}
+\textbf{result 2.4}: for the case when $T_B>T_A$ $\hat{p_2}$ is realistic when $\beta_1>\beta_3>0$ and is always unstable equilibrium.
 

### 2020-07-06 ms/main.tex
reverted the last part and revised it from scratch

@@
 
-\textbf{Result 3: Oblique and vertical transmission of cooperation with symmetric horizontal transmission.}
+\textbf{Result 3: Oblique and vertical transmission with symmetric horizontal transmission.}
 
-Assuming equal horizontal transmission, i.e. $T_A = T_B = T$, and following the above procedure, we have
+For simplicity, assume that $T_A = T_B = T$ so we will get
 \begin{equation} \label{eq:equal_horizontal_transmission}
-%\hat{p}' - \hat{p} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
-\bar{w} (\hat{p}' - \hat{p}) =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
+% check this, I think you are missing a wbar on the left side, ie it should be
+% \bar{\hat{p}' - \hat{p}} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
+  \hat{p}' - \hat{p} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
 \end{equation}
 
-It is easy to see that $\hat{p}^*_0 =  0$ and $\hat{p}^*_1 = 1$ are equilibria of eq.~\ref{eq:equal_horizontal_transmission}, that is, both extinction and fixation of the cooperator phenotype are equilibria.
-
-%TODO fix the following, you forgot wbar in eq:equal_horizontal_transmission
-In order to do that we find the derivative  $f(\hat{p}) = \hat{p}'-\hat{p}$.
+We are looking for the equilibrium $\hat{p}^*$ which occurs when $\hat{p}' = \hat{p}$.
+It is easy to verify that fixation of either phenotype is an equilibrium, that is,
+\begin{equation} \label{eq:result2.1}
+  \hat{p}^*_0 =  0, \, \hat{p}^*_1 = 1 .
+\end{equation}
+We wish to determine when fixation of cooperation is locally stable. % state the general condition on the derivative that implies local stability
+To do that, we calculate the derivative of $f(\hat{p}) = \hat{p}'-\hat{p}$, 
 \begin{equation} \label{eq:derivative_of_phattag-phat}
@@
 \end{equation}
-We are interested in the case when when $\hat{p} = \hat{p}^*_1=1$ therefore
-$f'(1) = -\alpha bvT + cv(1-T)$. Therefore, fixation of cooperation is stable when
+For $\hat{p} = \hat{p}^*_1=1$, the derivative is
+$f'(1) = -\alpha bvT + cv(1-T)$, and therefore, fixation of cooperation is locally stable when
 \begin{equation} \label{eq:oblique_and_vertic_result2}
@@
 
-Next, we study the general case where $T_A \neq T_B$. We have
-%TODO check again, I think you forgot wbar here, too
-\begin{equation} \label{eq:general_case_polynomial}
-  f(\hat{p}) = \hat{p}'-\hat{p} = \beta_1 p^3 + \beta_2 p^2 + \beta_3 p
+We now study the general case where $T_A \neq T_B$. We have
+\begin{equation} \label{eq:general_case_polynomial}% check, because I think wbar is missing
+  f(\hat{p}) = \hat{p}'-\hat{p} = \beta_1p^3 + \beta_2 p^2 + \beta_3p + \beta_4
 \end{equation}
@@
   & \beta_2 = (b(1-\alpha v)-c(1-v)-1)(T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
-  & \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B)
+  & \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \\
+  & \beta_4 = 0
 \end{split}
 \end{equation}
-
-$f(\hat{p})$ is a cubic, and its three roots are the equilibria of the system, i.e. the solutions for $\hat{p}'=\hat{p}$.
-As $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibria, there is only one equilibrium left, $\hat{p}^*_2$, which solves $f(\hat{p})/\big(\hat{p}(1-\hat{p})\big)=0$. Solving this we find that
+Since $f(\hat{p})$ is a cubic polynomial, three equilibria exist.
+We already know that $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibria.
+The third equilibrium can be found by solving $f(\hat{p})/\big(\hat{p}(1-\hat{p})\big)=0$, and it is
 \begin{equation} \label{eq:oblique_and_vertic_result}
@@
 
-$\hat{p}^*_2$ is a legitimate equilibrium if $0<\hat{p}^*_2<1$.  
-To determine if $\hat{p}^*_2$ is legitimate, we need the derivative of $f(\hat{p})$,\begin{equation} \label{eq:derivative_of_phattag-phat2}
-  f'(\hat{p}) = 3\beta_0 \hat{p}^2 + 2\beta_1\hat{p}^2 + \beta_3.
+We would like to know when $\hat{p}^*_2$ is legitimate equilibrium, i.e. $0<\hat{p}^*_2<1$.  
+To do that we find the derivative  of $f(\hat{p})$,
+\begin{equation} \label{eq:derivative_of_phattag-phat2}
+  f'(\hat{p}) = 3\beta_0 \hat{p}^2 + 2\beta_1\hat{p}^2 + \beta_3
  \end{equation}
-First, we assume that $T_A>T_B$, and therefore $\beta_1<0$, because $c(1-v)-b(1-\alpha v)<0$ and $c<b$ $v<1$. % why?
-In this case $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to infinity. 
-Therefore, if $\hat{p}^*_2$ is positive then $f'(0)= \beta_3$ must be negative, and
-% TODO remove
-%\begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
-%  f'(0) = \beta_3
-% \end{equation} 
-$\hat{p}_2^*>0$ when $\beta_3<0$. In addition, $\hat{p}^*_0=0$ is stable when $|f'(0)|<1$ therefore, when $-1<\beta_3<1$. We can show that 
+We assume that $T_A>T_B$ and we get that $\beta_1<0$ since $c(1-v)-b(1-\alpha v)<0$ and $c<b$ $v<1$. % why?
+In this case the cubic $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to infinity. 
+Therefore, if $\hat{p}^*_2$ is positive then $f'(0)$ must be negative % are you sure? I think it must be positive, because i think that the two extremes of a cubic must go in opposite directions
+\begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
+  f'(0) = \beta_3
+ \end{equation}
+$\hat{p}^*_2>0$ when $\beta_3<0$.
+In addition, $\hat{p}^*_0=0$ is stable when $|f'(0)|<1$ therefore, when $-1<\beta_3<1$.
+We can show that
 \begin{equation} \label{eq:beta3-condition}
@@
 \end{equation}
-Therefore, when $\hat{p}^*_2>0$ we get that $-1<\beta_3<0$ and $\hat{p}^*_0=0$ is locally stable.
+Therefore, when $\hat{p}^*_2>0$ we have $-1<\beta_3<0$ and $\hat{p}^*_0=0$ is locally stable.
 
-Next we would like to find when $\hat{p}^*_2<1$.
-If $T_A>T_B$ like before then the polynomial goes to minus infinity when $\hat{p}$ goes to infinity.
-Hence, if $\hat{p}_2<1$ then $f'(1)$ must be negative
+Now we would like to find when $\hat{p}^*_2<1$.
+If $T_A>T_B$, as before, then the cubic $f(\hat{p})$ goes to negative infinity when $\hat{p}$ goes to infinity.
+Hence, if $\hat{p}^*_2<1$ then $f'(1)$ must be negative % again, i think that the two extremes of a cubic must go in opposite directions
 \begin{equation} \label{eq:derivative_of_phattag-phat_p=1}
@@
 \end{equation}
-Therefore, $\hat{p}_2<1$ when $\beta_1-\beta_3<0$. In addition, $\hat{p}_1=1$ is stable when $|f'(1)|<1$ therefore, when $-1<\beta_1-\beta_3<1$. 
-We can prove that when $0<\hat{p}_2<1$ hence $\beta_3<0$ and $\beta_1-\beta_3<0$ we get that $-1<\beta_1-\beta_3$:
+Therefore, $\hat{p}^*_2<1$ when $\beta_1-\beta_3<0$.
+In addition, $\hat{p}_1=1$ is stable when $|f'(1)|<1$ therefore, when $-1<\beta_1-\beta_3<1$. 
+We show that when $0<\hat{p}^*_2<1$ hence $\beta_3<0$ and $\beta_1-\beta_3<0$ we get that $-1<\beta_1-\beta_3$: % cut down sentence to several sentences, it is too complex like this
 \begin{equation} \label{eq:beta1-beta3-condition}
- \beta_1 - \beta_3 > - \beta_3 > 0 > -1
+ \beta_1 - \beta_3 > - \beta_3 > 0 > -1 ,
 \end{equation}
-which means that when $0<\hat{p}_2<1$ then $\hat{p}_1=1$ is always stable.
+which means that when $0<\hat{p}^*_2<1$ then $\hat{p}^*_1=1$ is locally stable.
 
-\textbf{result 2.3}: for the case when $T_A>T_B$ $\hat{p_2}$ is realistic when $\beta_1<\beta_3<0$ and is always unstable equilibrium.
+\textbf{Result 2.3}: if $\hat{p}^*_2$ is a legitimate equilibrium, then it is locally unstable.
 
-\textbf{result 2.4}: for the case when $T_B>T_A$ $\hat{p_2}$ is realistic when $\beta_1>\beta_3>0$ and is always unstable equilibrium.
+\textbf{Result 2.4}: if $T_A>T_B$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1<\beta_3<0$.
+
+\textbf{Result 2.5}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.
 

### 2020-07-10 ms/main.tex
Remove Yoav's comment on eq.20
Add more explainations

@@
 \begin{equation} \label{eq:equal_horizontal_transmission}
-% check this, I think you are missing a wbar on the left side, ie it should be
-% \bar{\hat{p}' - \hat{p}} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
   \hat{p}' - \hat{p} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
@@
 \end{equation}
-We wish to determine when fixation of cooperation is locally stable. % state the general condition on the derivative that implies local stability
-To do that, we calculate the derivative of $f(\hat{p}) = \hat{p}'-\hat{p}$, 
+We wish to determine when fixation of cooperation is locally stable. 
+An equilibrium point $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p}) = \hat{p}'-\hat{p}$ at $p^*$ is negative, $f'(\hat{p}^*)<0$. 
+Calculating the derivative of $f(\hat{p})$ give us 
 \begin{equation} \label{eq:derivative_of_phattag-phat}
@@
 We now study the general case where $T_A \neq T_B$. We have
-\begin{equation} \label{eq:general_case_polynomial}% check, because I think wbar is missing
+\begin{equation} \label{eq:general_case_polynomial}
   f(\hat{p}) = \hat{p}'-\hat{p} = \beta_1p^3 + \beta_2 p^2 + \beta_3p + \beta_4
@@
 \begin{split}
-  & \beta_1 = c(1-v)\cdot(T_A-T_B) -b (1-\alpha v) \cdot(T_A-T_B) \\
+  & \beta_1 = [c(1-v) -b (1-\alpha v)] \cdot(T_A-T_B) \\
   & \beta_2 = (b(1-\alpha v)-c(1-v)-1)(T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
@@
  \end{equation}
-We assume that $T_A>T_B$ and we get that $\beta_1<0$ since $c(1-v)-b(1-\alpha v)<0$ and $c<b$ $v<1$. % why?
-In this case the cubic $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to infinity. 
-Therefore, if $\hat{p}^*_2$ is positive then $f'(0)$ must be negative % are you sure? I think it must be positive, because i think that the two extremes of a cubic must go in opposite directions
+We assume that $T_A>T_B$ and we look on $\beta_1$:
+\begin{equation} \label{eq:beta1}
+  \begin{split}
+   \beta_1 & = [c(1-v) -b (1-\alpha v)] \cdot(T_A-T_B) \\
+   &< [c(1-\alpha v) - b(1-\alpha v)]\cdot(T_A-T_B) \\
+   &= (1-\alpha v)(c-b)(T_A-T_B)
+  \end{split}
+ \end{equation}
+From eq.~\ref{eq:beta1} we get that $\beta_1<0$ since $c-b<0$ $1-\alpha v>0$ and we assumed that $T_A > T_B$.
+In this case the cubic $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to minus infinity ($-\infty$). 
+Therefore, if $\hat{p}^*_2$ is positive then $f'(0)$ must be negative % are you sure?
+I think it must be positive, because i think that the two extremes of a cubic must go in opposite directions DC: Yest, but I've fixed in the line before, there was minus sign missing
 \begin{equation} \label{eq:derivative_of_phattag-phat_p=0}

### 2020-07-10 ms/main.tex
Fix results

@@
 $\hat{p}^*_2>0$ when $\beta_3<0$.
-In addition, $\hat{p}^*_0=0$ is stable when $|f'(0)|<1$ therefore, when $-1<\beta_3<1$.
-We can show that
-\begin{equation} \label{eq:beta3-condition}
-  \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) > -cv(1-T_B) > -1
-\end{equation}
-Therefore, when $\hat{p}^*_2>0$ we have $-1<\beta_3<0$ and $\hat{p}^*_0=0$ is locally stable.
+In addition, $\hat{p}^*_0=0$ is stable when $f'(0) = \beta_3 <0$.
+Therefore, when $\hat{p}^*_2>0$ the coefficient $\beta_3$ must be negative and $\hat{p}^*_0=0$ is locally stable.
 
 Now we would like to find when $\hat{p}^*_2<1$.
-If $T_A>T_B$, as before, then the cubic $f(\hat{p})$ goes to negative infinity when $\hat{p}$ goes to infinity.
-Hence, if $\hat{p}^*_2<1$ then $f'(1)$ must be negative % again, i think that the two extremes of a cubic must go in opposite directions
+If $T_A>T_B$, as before, then the cubic $f(\hat{p})$ goes to minus infinity ($-\infty$) when $\hat{p}$ goes to infinity.
+Hence, if $\hat{p}^*_2<1$ then $f'(1)$ must be negative % again, i think that the two extremes of a cubic must go in opposite directions.
+DC: I've double checked and I'm pretty sure my results are correct
 \begin{equation} \label{eq:derivative_of_phattag-phat_p=1}
-  f'(0) = \beta_1 - \beta_3
+  f'(1) = \beta_1 - \beta_3
 \end{equation}
 Therefore, $\hat{p}^*_2<1$ when $\beta_1-\beta_3<0$.
-In addition, $\hat{p}_1=1$ is stable when $|f'(1)|<1$ therefore, when $-1<\beta_1-\beta_3<1$. 
-We show that when $0<\hat{p}^*_2<1$ hence $\beta_3<0$ and $\beta_1-\beta_3<0$ we get that $-1<\beta_1-\beta_3$: % cut down sentence to several sentences, it is too complex like this
-\begin{equation} \label{eq:beta1-beta3-condition}
- \beta_1 - \beta_3 > - \beta_3 > 0 > -1 ,
-\end{equation}
-which means that when $0<\hat{p}^*_2<1$ then $\hat{p}^*_1=1$ is locally stable.
+In addition, $\hat{p}^*_1=1$ is stable when $f'(1) = \beta_1-\beta_3<0$. 
+We saw that when $0<\hat{p}^*_2<1$ the following must apply $f'(0)=\beta_3<0$ and $f'(1)=\beta_1-\beta_3<0$.
+Hence, when $0<\hat{p}^*_2<1$ then $\hat{p}^*_1=1$ is locally stable.
 
-\textbf{Result 2.3}: if $\hat{p}^*_2$ is a legitimate equilibrium, then it is locally unstable.
+\textbf{Result 4.1}: if $\hat{p}^*_2$ is a legitimate equilibrium, then it is locally unstable.
 
-\textbf{Result 2.4}: if $T_A>T_B$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1<\beta_3<0$.
+\textbf{Result 4.2}: if $T_A>T_B$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1<\beta_3<0$.
 
-\textbf{Result 2.5}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.
+\textbf{Result 4.3}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.
 

### 2020-07-13 ms/main.tex
add more comment

@@
 
-\textbf{Result 4.3}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.
+\textbf{Result 4.3}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$. % DC: I didn't show it but it applies
 
@@
     \includegraphics[scale=0.5]{figure2a.pdf}
-    \caption{$V=1$, $T_A=T_B=T$, $\alpha \neq 0$}
+    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
     \label{fig:results_a}
@@
     \includegraphics[scale=0.5]{figure2b.pdf}
-    \caption{$V=1$, $\alpha = 0$}
+    \caption{$v=1$, $\alpha = 0$}
     \label{fig:results_b}
@@
     \includegraphics[scale=0.5]{figure2c.pdf}
-    \caption{$V=0$}
+    \caption{$v=0$}
     \label{fig:results_c}
@@
   \label{fig:results}
-  \caption{numerical results}
+  \caption{Numerical results of different scenarios.
+$\tilde{p}$ is ploted against time (generations) in (a) and (b), where $\tilde{p}$ is the frequency of parents with phenotypes A (cooperators) among the population.
+\\ $p'$ is ploted against time (generations) in (c).
+In each figure, the green line presnt the condition for fixation of cooperation, the orange line is equilibria and green is fixation of defectors}
 \end{figure}

### 2020-07-13 ms/main.tex
revised eq 20 and on

--- 2020-07-10 ms/main.tex
@@
 \end{equation}
-where fitness values are taken from \autoref{table:1} and $\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$ is the population mean fitness.
+where fitness values are taken from \autoref{table:1}, and 
+\begin{equation} \label{eq:mean_fitness}
+\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)
+\end{equation}
+is the population mean fitness.
 Eq~\ref{eq:nextgen_parents} can be slimpified to
@@
 eq.~\ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-Combining these equations, we will find an equation for $\hat{p}'$ as a function of $\hat{p}$.
-We will then determine the equilibria of this function, that is, solutions for $\hat{p}' = \hat{p}$, and their stability.
+Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$.
+We then determine the equilibria of this equation, that is, solutions for $\hat{p}' = \hat{p}$, and their stability.
 
@@
 
-For simplicity, assume that $T_A = T_B = T$ so we will get
+For simplicity, we start with the assumption that $T_A = T_B = T$. We have
 \begin{equation} \label{eq:equal_horizontal_transmission}
-  \hat{p}' - \hat{p} =  \hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T))
+% DOR: I checked again, substituting eq 7 and 9 to eq 5: you have to divide the RHS by wbar.
+  %\hat{p}' - \hat{p} = 
+  %\hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T)) = 
+  \bar{w}(\hat{p}' - \hat{p}) = 
+  f(\hat{p}) = \hat{p}(1-\hat{p})(\alpha bvT - cv(1-T)) % shorter version
 \end{equation}
 
-We are looking for the equilibrium $\hat{p}^*$ which occurs when $\hat{p}' = \hat{p}$.
+We are looking for the equilibrium $\hat{p}^*$ which occurs when $f(\hat{p}^*)=0$, or $\hat{p}' = \hat{p}$.
 It is easy to verify that fixation of either phenotype is an equilibrium, that is,
@@
 \end{equation}
-We wish to determine when fixation of cooperation is locally stable. 
-An equilibrium point $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p}) = \hat{p}'-\hat{p}$ at $p^*$ is negative, $f'(\hat{p}^*)<0$. 
-Calculating the derivative of $f(\hat{p})$ give us 
+
+Is fixation of cooperation, $\hat{p}^*_1=1$, locally stable?. 
+An equilibrium point $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at $p^*$ is negative, $f'(\hat{p}^*)<0$. 
+This derivative is
 \begin{equation} \label{eq:derivative_of_phattag-phat}
- f'(\hat{p}) = 2\cdot\hat{p} (-\alpha bvT + cv(1-T)) + (\alpha bvT -cv(1-T)).
+	f'(\hat{p}) \mid_{\hat{p}=1} = 
+% 2\cdot\hat{p} (-\alpha bvT + cv(1-T)) + (\alpha bvT -cv(1-T)).
+	(1- 2\hat{p}) (\alpha bvT - cv(1-T)) \mid_{\hat{p}=1} = 
+	-\alpha bvT + cv(1-T)).
 \end{equation}
-For $\hat{p} = \hat{p}^*_1=1$, the derivative is
-$f'(1) = -\alpha bvT + cv(1-T)$, and therefore, fixation of cooperation is locally stable when
+Therefore, fixation of cooperation is locally stable when
 \begin{equation} \label{eq:oblique_and_vertic_result2}
-  \frac{b}{c}>\frac{1-T}{\alpha T}
+  %\frac{b}{c}>\frac{1-T}{\alpha T}
+	c < b \cdot \frac{\alpha T}{1-T},
 \end{equation}
-Which is the same condition we get in corollary 1.1.
+which is the same condition we found in Corollary 1.1, Eq.~\ref{eq:equal_transmission}.
 
@@
 \begin{equation} \label{eq:general_case_polynomial}
-  f(\hat{p}) = \hat{p}'-\hat{p} = \beta_1p^3 + \beta_2 p^2 + \beta_3p + \beta_4
+  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) =
+  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p},
 \end{equation}
@@
 \begin{equation} \label{eq:polynomial_coefficients}
-\begin{split}
-  & \beta_1 = [c(1-v) -b (1-\alpha v)] \cdot(T_A-T_B) \\
-  & \beta_2 = (b(1-\alpha v)-c(1-v)-1)(T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
-  & \beta_3 = \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \\
-  & \beta_4 = 0
-\end{split}
+\begin{aligned}
+\beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \\
+%\beta_2 &= -[c(1-v) - b(1-\alpha v) +  1](T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
+\beta_2 &= -\beta_1 -\beta_3  \\
+\beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) .
+\end{aligned}
 \end{equation}
@@
 We already know that $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibria.
-The third equilibrium can be found by solving $f(\hat{p})/\big(\hat{p}(1-\hat{p})\big)=0$, and it is
+The third equilibrium $\hat{p}^*_2$ can be found by solving $f(\hat{p})/\big[\hat{p}(1-\hat{p})\big] = \beta_3 -\beta_1 \hat{p} = 0$:
 \begin{equation} \label{eq:oblique_and_vertic_result}
-  \hat{p}^*_2 =  \frac{\alpha bvT_A + cvT_B + T_A-T_B-cv}{c(1-v)\cdot(T_A-T_B) -b (1-\alpha v) \cdot(T_A-T_B)}
+  \hat{p}^*_2 =  
+  \frac{\beta_3}{\beta_1}.
+  %\frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}
+  %     {\big(c(1-v) -b (1-\alpha v)\big) (T_A-T_B)} .
 \end{equation}
-
-We would like to know when $\hat{p}^*_2$ is legitimate equilibrium, i.e. $0<\hat{p}^*_2<1$.  
-To do that we find the derivative  of $f(\hat{p})$,
-\begin{equation} \label{eq:derivative_of_phattag-phat2}
-  f'(\hat{p}) = 3\beta_0 \hat{p}^2 + 2\beta_1\hat{p}^2 + \beta_3
- \end{equation}
-We assume that $T_A>T_B$ and we look on $\beta_1$:
+To determine when $\hat{p}^*_2$ is a legitimate equilibrium (i.e. $0<\hat{p}^*_2<1$), we first focus on the left inequality, $0<\hat{p}^*_2$, and
+%To do that we find the derivative  of $f(\hat{p})$,
+%\begin{equation} \label{eq:derivative_of_phattag-phat2}
+%  f'(\hat{p}) = 3\beta_1 \hat{p}^2 + 2\beta_2\hat{p}^2 + \beta_3
+% \end{equation}
+assume that $T_A>T_B$. In this case,
 \begin{equation} \label{eq:beta1}
   \begin{split}
-   \beta_1 & = [c(1-v) -b (1-\alpha v)] \cdot(T_A-T_B) \\
-   &< [c(1-\alpha v) - b(1-\alpha v)]\cdot(T_A-T_B) \\
-   &= (1-\alpha v)(c-b)(T_A-T_B)
+   \beta_1 & = [c(1-v) - b (1-\alpha v)] (T_A-T_B) \\
+   &< [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) \\
+   &= (1-\alpha v)(c-b)(T_A-T_B) < 0 ,
   \end{split}
  \end{equation}
-From eq.~\ref{eq:beta1} we get that $\beta_1<0$ since $c-b<0$ $1-\alpha v>0$ and we assumed that $T_A > T_B$.
-In this case the cubic $f(\hat{p})$ goes to infinity when $\hat{p}$ goes to minus infinity ($-\infty$). 
-Therefore, if $\hat{p}^*_2$ is positive then $f'(0)$ must be negative % are you sure?
-I think it must be positive, because i think that the two extremes of a cubic must go in opposite directions DC: Yest, but I've fixed in the line before, there was minus sign missing
-\begin{equation} \label{eq:derivative_of_phattag-phat_p=0}
-  f'(0) = \beta_3
- \end{equation}
-$\hat{p}^*_2>0$ when $\beta_3<0$.
-In addition, $\hat{p}^*_0=0$ is stable when $f'(0) = \beta_3 <0$.
-Therefore, when $\hat{p}^*_2>0$ the coefficient $\beta_3$ must be negative and $\hat{p}^*_0=0$ is locally stable.
+since $T_A > T_B$, $c<b$, and $1>\alpha v$.
+Therefore, when $\hat{p}$ goes to negative infinity, the cubic $f(\hat{p})$ goes to positive infinity.
+So, a necessary condition for $\hat{p}^*_2>0$ is that $f'(0) = \beta_3 < 0$.
+This condition also satisfies local stability of $\hat{p}^*_0=0$.
+Hence, if $\hat{p}^*_2$ is legitimate, then extinction of cooperation is locally stable.
 
-Now we would like to find when $\hat{p}^*_2<1$.
-If $T_A>T_B$, as before, then the cubic $f(\hat{p})$ goes to minus infinity ($-\infty$) when $\hat{p}$ goes to infinity.
-Hence, if $\hat{p}^*_2<1$ then $f'(1)$ must be negative % again, i think that the two extremes of a cubic must go in opposite directions.
-DC: I've double checked and I'm pretty sure my results are correct
-\begin{equation} \label{eq:derivative_of_phattag-phat_p=1}
-  f'(1) = \beta_1 - \beta_3
-\end{equation}
-Therefore, $\hat{p}^*_2<1$ when $\beta_1-\beta_3<0$.
-In addition, $\hat{p}^*_1=1$ is stable when $f'(1) = \beta_1-\beta_3<0$. 
-We saw that when $0<\hat{p}^*_2<1$ the following must apply $f'(0)=\beta_3<0$ and $f'(1)=\beta_1-\beta_3<0$.
-Hence, when $0<\hat{p}^*_2<1$ then $\hat{p}^*_1=1$ is locally stable.
+We now focus on $\hat{p}^*_2<1$, still assuming $T_A>T_B$.
+When $\hat{p}$ goes to positive infinity, the cubic $f(\hat{p})$ goes to negative infinity (Eq.~\ref{eq:beta1}).
+So, a necessary condition for $\hat{p}^*_2<1$ is that $f'(1)=\beta_1 - \beta_3<0$.
+This condition also satisfies local stability of $\hat{p}^*_1=1$.
+Hence, if $\hat{p}^*_2$ is legitimate, then fixation of cooperation is also locally stable.
+Moreover, since legitimacy of $\hat{p}^*_2$ implies local stability of both $\hat{p}^*_0$ and $\hat{p}^*_1$, we conclude that $\hat{p}^*_2$ is locally unstable.
 
-\textbf{Result 4.1}: if $\hat{p}^*_2$ is a legitimate equilibrium, then it is locally unstable.
+If we assume instead that $T_A < T_B$, we reach the following results:
 
-\textbf{Result 4.2}: if $T_A>T_B$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1<\beta_3<0$.
-
-\textbf{Result 4.3}: if $T_B>T_A$, then $\hat{p}^*_2$ is a legitimate equilibrium when $\beta_1>\beta_3>0$.
+\textbf{Result 4}: if $T_A>T_B$ ($T_B>T_A$), then $\hat{p}^*_2$ is a legitimate locally unstable equilibrium when $\beta_1<\beta_3<0$ ($\beta_1>\beta_3>0$).
+In this case, both fixations are locally stable and $\hat{p}^*_2$ separates the domains of attraction.
 
@@
   \label{fig:results}
-  \caption{numerical results}
+  \caption{
+  \textbf{Numerical results for cultural evolution of cooperation.}
+  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
+  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange). %TODO ic (c), the blue and green got mixed. 
+  % TODO have all panels in one row.
+  }
 \end{figure}
@@
 This work was supported in part by
-the Israel Science Foundation 552/19 (YR).
+the Israel Science Foundation 552/19 (YR),
+and Minerva Center for Lab Evolution (YR).
 % TODO funding for other authors?

### 2020-07-13 ms/main.tex
reorganizes results 3-4

@@
 \begin{equation} \label{eq:unequal_transmission}
-c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b\tilde{p}(1-\alpha)]
+c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b\tilde{p}(1-\alpha)] ,
 \end{equation}
@@
 
-\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
-Using eq.~\ref{eq:nextgen_parents_oblique_only}, we find that $p'>p$ occurs when
+\textbf{Result 2: Oblique and horizontal transmission of cooperation.} 
+If there is a horizontal transmission bias in favor of cooperation,
 \begin{equation} \label{eq:oblique_only_result}
-T_A > T_B . 
+T_A > T_B, 
 \end{equation}
+then $p'>p$, and the frequency of the cooperator phenotype among adults increases every generation.
 Therefore, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~\textbf{\autoref{fig:results_c}}).
@@
 
-In this case $0<v<1$, and the equation system is more complex than before.
-Therefore, we focus on local rather than global stability, which was the case so far.\\
+In this case $0<v<1$, and the equation system is more complex.
+Therefore, we focus on local, rather than global, stability.\\
 To proceed, we note that 
@@
 
-\textbf{Result 3: Oblique and vertical transmission with symmetric horizontal transmission.}
-
-For simplicity, we start with the assumption that $T_A = T_B = T$. We have
+We start with the simpler case of symmetric horizontal transmission, $T=T_A=T_B$. 
+We apply eqs.~\ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to define $f(\hat{p})$ as 
+% Yoav: I checked again, substituting eq 7 and 9 to eq 5: you have to divide the RHS by wbar.
 \begin{equation} \label{eq:equal_horizontal_transmission}
-% DOR: I checked again, substituting eq 7 and 9 to eq 5: you have to divide the RHS by wbar.
+\begin{aligned}
   %\hat{p}' - \hat{p} = 
   %\hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T)) = 
-  \bar{w}(\hat{p}' - \hat{p}) = 
-  f(\hat{p}) = \hat{p}(1-\hat{p})(\alpha bvT - cv(1-T)) % shorter version
+  f(\hat{p}) &= 
+  \bar{w}(\hat{p}' - \hat{p}) = \\
+  &\hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big]. % shorter version
+\end{aligned}
 \end{equation}
 
-We are looking for the equilibrium $\hat{p}^*$ which occurs when $f(\hat{p}^*)=0$, or $\hat{p}' = \hat{p}$.
+The equilibria $\hat{p}^*$ are solutions to $f(\hat{p}^*)=0$, or $\hat{p}'^* = \hat{p}^*$.
 It is easy to verify that fixation of either phenotype is an equilibrium, that is,
@@
 \end{equation}
+An equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at $p^*$ is negative, $f'(\hat{p}^*)<0$. 
+Since the derivative is 
+\begin{equation}
+f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big],
+\end{equation}
+then the condition for local stability of $\hat{p}^*_1$ is
+\begin{equation} \label{eq:derivative_of_phattag-phat}
+	f'(1) =
+% 2\cdot\hat{p} (-\alpha bvT + cv(1-T)) + (\alpha bvT -cv(1-T)).
+%	(1- 2\hat{p}) (\alpha bvT - cv(1-T)) \mid_{\hat{p}=1} = 
+	-\alpha bvT + cv(1-T) < 0,
+\end{equation}
+which gives us the following result.
 
-Is fixation of cooperation, $\hat{p}^*_1=1$, locally stable?. 
-An equilibrium point $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at $p^*$ is negative, $f'(\hat{p}^*)<0$. 
-This derivative is
-\begin{equation} \label{eq:derivative_of_phattag-phat}
-	f'(\hat{p}) \mid_{\hat{p}=1} = 
-% 2\cdot\hat{p} (-\alpha bvT + cv(1-T)) + (\alpha bvT -cv(1-T)).
-	(1- 2\hat{p}) (\alpha bvT - cv(1-T)) \mid_{\hat{p}=1} = 
-	-\alpha bvT + cv(1-T)).
-\end{equation}
-Therefore, fixation of cooperation is locally stable when
+\textbf{Result 3: Oblique and vertical transmission with symmetric horizontal transmission.}
+If horizontal transmission is symmetric, $T = T_A = T_B$, and if
 \begin{equation} \label{eq:oblique_and_vertic_result2}
@@
 \end{equation}
-which is the same condition we found in Corollary 1.1, Eq.~\ref{eq:equal_transmission}.
-
-\textbf{Result 4: Oblique and vertical transmission of cooperation with asymmetric horizontal transmission.}
-
-We now study the general case where $T_A \neq T_B$. We have
+then fixation of the cooperator phenotype $A$ is locally stable.
+This is the same condition we found in Corollary 1.1, Eq.~\ref{eq:equal_transmission}.
+\\
+\\
+We now turn to the general case where $T_A \neq T_B$. We have
 \begin{equation} \label{eq:general_case_polynomial}
@@
 We already know that $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibria.
-The third equilibrium $\hat{p}^*_2$ can be found by solving $f(\hat{p})/\big[\hat{p}(1-\hat{p})\big] = \beta_3 -\beta_1 \hat{p} = 0$:
+By solving $f(\hat{p})/\big[\hat{p}(1-\hat{p})\big] = \beta_3 -\beta_1 \hat{p} = 0$ we can find the third equilibrium,
 \begin{equation} \label{eq:oblique_and_vertic_result}
@@
 \end{equation}
-To determine when $\hat{p}^*_2$ is a legitimate equilibrium (i.e. $0<\hat{p}^*_2<1$), we first focus on the left inequality, $0<\hat{p}^*_2$, and
-%To do that we find the derivative  of $f(\hat{p})$,
-%\begin{equation} \label{eq:derivative_of_phattag-phat2}
-%  f'(\hat{p}) = 3\beta_1 \hat{p}^2 + 2\beta_2\hat{p}^2 + \beta_3
-% \end{equation}
-assume that $T_A>T_B$. In this case,
+
+Note that the sign of the cubic $f(\hat{p})$ at positive (negative) infinity is equal (inverse) to the sign of $\beta_1$. 
+If $T_A>T_B$, then 
 \begin{equation} \label{eq:beta1}
-  \begin{split}
-   \beta_1 & = [c(1-v) - b (1-\alpha v)] (T_A-T_B) \\
-   &< [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) \\
-   &= (1-\alpha v)(c-b)(T_A-T_B) < 0 ,
-  \end{split}
+   \beta_1 %& = [c(1-v) - b (1-\alpha v)] (T_A-T_B) \\
+   < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   = (1-\alpha v)(c-b)(T_A-T_B) < 0 ,
  \end{equation}
-since $T_A > T_B$, $c<b$, and $1>\alpha v$.
-Therefore, when $\hat{p}$ goes to negative infinity, the cubic $f(\hat{p})$ goes to positive infinity.
-So, a necessary condition for $\hat{p}^*_2>0$ is that $f'(0) = \beta_3 < 0$.
-This condition also satisfies local stability of $\hat{p}^*_0=0$.
-Hence, if $\hat{p}^*_2$ is legitimate, then extinction of cooperation is locally stable.
+since $c<b$, and $1>\alpha v$.
+So the sign of the cubic at positive and negative infinity is negative and positive, respectively.
+First, if $\beta_3<\beta_1$ then $0<\hat{p}^*_2<1$ and therefore $f'(0)<0$ and $f'(1)<0$, that is, both fixations are locally stable and $\hat{p}^*_2$ separates the domains of attraction.
+Second, if $\beta_1<\beta_3<0$ then $1<\hat{p}^*_2$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e.
+between 0 and 1) equilibrium.
+Third, if $0<\beta_3$ then $\hat{p}^*_2<0$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
-We now focus on $\hat{p}^*_2<1$, still assuming $T_A>T_B$.
-When $\hat{p}$ goes to positive infinity, the cubic $f(\hat{p})$ goes to negative infinity (Eq.~\ref{eq:beta1}).
-So, a necessary condition for $\hat{p}^*_2<1$ is that $f'(1)=\beta_1 - \beta_3<0$.
-This condition also satisfies local stability of $\hat{p}^*_1=1$.
-Hence, if $\hat{p}^*_2$ is legitimate, then fixation of cooperation is also locally stable.
-Moreover, since legitimacy of $\hat{p}^*_2$ implies local stability of both $\hat{p}^*_0$ and $\hat{p}^*_1$, we conclude that $\hat{p}^*_2$ is locally unstable.
+Similarly, if $T_B>T_A$, then
+\begin{equation} \label{eq:beta1_rev}
+   \beta_1 %& = -[c(1-v) - b (1-\alpha v)] (T_A-T_B) \\
+   > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   = (1-\alpha v)(c-b)(T_A-T_B) > 0,
+ \end{equation}
+since $c<b$, and $1>\alpha v$. So the sign of the cubic at positive and negative infinity is positive and negative, respectively. 
+First, if $\beta_3<0$ then $\hat{p}^*_2<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
+Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*_2<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*_2$ is a stable polymorphic equilibrium.
+Third, if $\beta_1<\beta_3$ then $\hat{p}^*_2>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
-If we assume instead that $T_A < T_B$, we reach the following results:
+The following result summarizes these findings.
 
-\textbf{Result 4}: if $T_A>T_B$ ($T_B>T_A$), then $\hat{p}^*_2$ is a legitimate locally unstable equilibrium when $\beta_1<\beta_3<0$ ($\beta_1>\beta_3>0$).
-In this case, both fixations are locally stable and $\hat{p}^*_2$ separates the domains of attraction.
+\textbf{Result 4: Oblique and vertical transmission of cooperation with asymmetric horizontal transmission.}
+The cultural evolution of a cooperator phenotype will follow on of th following scenarios, depending on the signs of the horizontal transmission bias $T_A-T_B$, the coefficient $\beta_3$, and ratio $\beta_3/\beta_1$:
+\begin{enumerate}
+\item \emph{Fixation of the cooperative phenotype $A$}, if $T_A>T_B$ and $0<\beta_3$, or $T_A<T_B$ and $\beta_1<\beta_3$.
 
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2a.pdf}
-    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
-    \label{fig:results_a}
-  \end{subfigure}
-  \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2b.pdf}
-    \caption{$v=1$, $\alpha = 0$}
-    \label{fig:results_b}
-  \end{subfigure}
-  \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2c.pdf}
-    \caption{$v=0$}
-    \label{fig:results_c}
-  \end{subfigure}
-  \label{fig:results}
-  \caption{
-  \textbf{Numerical results for cultural evolution of cooperation.}
-  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
-  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange). %TODO ic (c), the blue and green got mixed. 
-  % TODO have all panels in one row.
-  }
-\end{figure}
+\item \emph{Fixation of the defector phenotype $B$}, if $T_A>T_B$ and $\beta_1<\beta_3<0$, or $T_A<T_B$ and $\beta_3<0$.
+
+\item \emph{Protected polymorphism, or co-existence of both phenotypes}, if $T_A < T_B$ and $0<\beta_3<\beta_1$.
+
+\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_3<\beta_1$.
+
+\end{enumerate}
+
+%\begin{figure}[H]
+%  \centering
+%  \begin{subfigure}{8cm}
+%    \includegraphics[scale=0.5]{figure2a.pdf}
+%    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
+%    \label{fig:results_a}
+%  \end{subfigure}
+%  \begin{subfigure}{8cm}
+%    \includegraphics[scale=0.5]{figure2b.pdf}
+%    \caption{$v=1$, $\alpha = 0$}
+%    \label{fig:results_b}
+%  \end{subfigure}
+%  \begin{subfigure}{8cm}
+%    \includegraphics[scale=0.5]{figure2c.pdf}
+%    \caption{$v=0$}
+%    \label{fig:results_c}
+%  \end{subfigure}
+%  \label{fig:results}
+%  \caption{
+%  \textbf{Numerical results for cultural evolution of cooperation.}
+%  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
+%  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange).
+%TODO ic (c), the blue and green got mixed.
+%  % TODO have all panels in one row.
+%  }
+%\end{figure}
 

### 2020-07-13 ms/main.tex
revised a bit more

@@
 Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$.
-We then determine the equilibria of this equation, that is, solutions for $\hat{p}' = \hat{p}$, and their stability.
+We then determine the equilibria of this equation, that is, solutions for $\hat{p}' = \hat{p}$, and analyse their local stability: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
 
 We start with the simpler case of symmetric horizontal transmission, $T=T_A=T_B$. 
-We apply eqs.~\ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to define $f(\hat{p})$ as 
-% Yoav: I checked again, substituting eq 7 and 9 to eq 5: you have to divide the RHS by wbar.
+We apply eqs.~\ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to define 
 \begin{equation} \label{eq:equal_horizontal_transmission}
@@
 
-The equilibria $\hat{p}^*$ are solutions to $f(\hat{p}^*)=0$, or $\hat{p}'^* = \hat{p}^*$.
-It is easy to verify that fixation of either phenotype is an equilibrium, that is,
-\begin{equation} \label{eq:result2.1}
-  \hat{p}^*_0 =  0, \, \hat{p}^*_1 = 1 .
-\end{equation}
-An equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at $p^*$ is negative, $f'(\hat{p}^*)<0$. 
-Since the derivative is 
+The equilibria are solutions to $f(\hat{p})=0$, or $\hat{p}' = \hat{p}$.
+It is easy to verify that fixation of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$, is an equilibrium.
+Since the derivative of $f'(\hat{p}$ is 
 \begin{equation}
@@
 \end{equation}
-then the condition for local stability of $\hat{p}^*_1$ is
+then the condition for local stability of $\hat{p}=1$ is
 \begin{equation} \label{eq:derivative_of_phattag-phat}
@@
 then fixation of the cooperator phenotype $A$ is locally stable.
-This is the same condition we found in Corollary 1.1, Eq.~\ref{eq:equal_transmission}.
+The same condition was given in Corollary 1.1, Eq.~\ref{eq:equal_transmission}.
+% TODO what happens if the condition does not apply? can there be an non-zero stable equilibrium?
 \\
@@
 \begin{aligned}
-\beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \\
+\beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) , \\
 %\beta_2 &= -[c(1-v) - b(1-\alpha v) +  1](T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
-\beta_2 &= -\beta_1 -\beta_3  \\
+\beta_2 &= -\beta_1 -\beta_3 ,  \\
 \beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) .
@@
 Since $f(\hat{p})$ is a cubic polynomial, three equilibria exist.
-We already know that $\hat{p}^*_0 = 0 $ and $\hat{p}^*_1 = 1$ are equilibria.
+We already know that $\hat{p} = 0 $ and $\hat{p} = 1$ are equilibria.
 By solving $f(\hat{p})/\big[\hat{p}(1-\hat{p})\big] = \beta_3 -\beta_1 \hat{p} = 0$ we can find the third equilibrium,
 \begin{equation} \label{eq:oblique_and_vertic_result}
-  \hat{p}^*_2 =  
+  \hat{p}^* =  
   \frac{\beta_3}{\beta_1}.
@@
 So the sign of the cubic at positive and negative infinity is negative and positive, respectively.
-First, if $\beta_3<\beta_1$ then $0<\hat{p}^*_2<1$ and therefore $f'(0)<0$ and $f'(1)<0$, that is, both fixations are locally stable and $\hat{p}^*_2$ separates the domains of attraction.
-Second, if $\beta_1<\beta_3<0$ then $1<\hat{p}^*_2$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e.
+First, if $\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$, that is, both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
+Second, if $\beta_1<\beta_3<0$ then $1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e.
 between 0 and 1) equilibrium.
-Third, if $0<\beta_3$ then $\hat{p}^*_2<0$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+Third, if $0<\beta_3$ then $\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
@@
 since $c<b$, and $1>\alpha v$. So the sign of the cubic at positive and negative infinity is positive and negative, respectively. 
-First, if $\beta_3<0$ then $\hat{p}^*_2<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
-Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*_2<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*_2$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then $\hat{p}^*_2>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
+Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
+Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
@@
 \textbf{Result 4: Oblique and vertical transmission of cooperation with asymmetric horizontal transmission.}
-The cultural evolution of a cooperator phenotype will follow on of th following scenarios, depending on the signs of the horizontal transmission bias $T_A-T_B$, the coefficient $\beta_3$, and ratio $\beta_3/\beta_1$:
+The cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the horizontal transmission bias $T_A-T_B$ and the coefficients $\beta_1$ and $\beta_3$:
 \begin{enumerate}
@@
 
-%\begin{figure}[H]
-%  \centering
-%  \begin{subfigure}{8cm}
-%    \includegraphics[scale=0.5]{figure2a.pdf}
-%    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
-%    \label{fig:results_a}
-%  \end{subfigure}
-%  \begin{subfigure}{8cm}
-%    \includegraphics[scale=0.5]{figure2b.pdf}
-%    \caption{$v=1$, $\alpha = 0$}
-%    \label{fig:results_b}
-%  \end{subfigure}
-%  \begin{subfigure}{8cm}
-%    \includegraphics[scale=0.5]{figure2c.pdf}
-%    \caption{$v=0$}
-%    \label{fig:results_c}
-%  \end{subfigure}
-%  \label{fig:results}
-%  \caption{
-%  \textbf{Numerical results for cultural evolution of cooperation.}
-%  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
-%  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange).
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{8cm}
+    \includegraphics[scale=0.5]{figure2a.pdf}
+    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
+    \label{fig:results_a}
+  \end{subfigure}
+  \begin{subfigure}{8cm}
+    \includegraphics[scale=0.5]{figure2b.pdf}
+    \caption{$v=1$, $\alpha = 0$}
+    \label{fig:results_b}
+  \end{subfigure}
+  \begin{subfigure}{8cm}
+    \includegraphics[scale=0.5]{figure2c.pdf}
+    \caption{$v=0$}
+    \label{fig:results_c}
+  \end{subfigure}
+  \label{fig:results}
+  \caption{
+  \textbf{Numerical results for cultural evolution of cooperation.}
+  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
+  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange).
   %TODO ic (c), the blue and green got mixed. 
-%  % TODO have all panels in one row.
-%  }
-%\end{figure}
+  % TODO have all panels in one row.
+  }
+\end{figure}
 
 % Discussion
-\section*{Discussion}
-We hypothesized that non-vertical transmission can explain the evolution of cooperation.
+%\section*{Discussion}
+%We hypothesized that non-vertical transmission can explain the evolution of cooperation.
 We used a model with non-vertical transmissions and have found that if eq.~\ref{eq:unequal_transmission} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff.
 In addition, we found that when horizontal transmission cannot occur after interaction ($\alpha = 0$) cooperation will always become extinct.
-Our results improve our understating of cultural evolution of cooperation.
+%Our results improve our understating of cultural evolution of cooperation.
 Our model shows that cooperation can evolve even in a fully mixed population, where the population is non-structured, there are no repeating interactions and nor individual recognition.
 
-%\pagebreak
+\pagebreak
 % Acknowledgements

### 2020-07-15 ms/main.tex
fix beta_1 beta_3 when TA>TB

@@
 We then determine the equilibria of this equation, that is, solutions for $\hat{p}' = \hat{p}$, and analyse their local stability: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
+%TODO show this is necessary and sufficient
 
@@
 So the sign of the cubic at positive and negative infinity is negative and positive, respectively.
-First, if $\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$, that is, both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
-Second, if $\beta_1<\beta_3<0$ then $1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e.
-between 0 and 1) equilibrium.
-Third, if $0<\beta_3$ then $\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+First, if $\beta_3<\beta_1$ then 
+$1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e. between 0 and 1) equilibrium.
+Second, if $\beta_1<\beta_3<0$ then 
+$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$, that is, both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
+Third, if $0<\beta_3$ then 
+$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
@@
 since $c<b$, and $1>\alpha v$. So the sign of the cubic at positive and negative infinity is positive and negative, respectively. 
-First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
-Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+First, if $\beta_3<0$ then 
+$\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
+Second, if $0<\beta_3<\beta_1$ then 
+$0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
+Third, if $\beta_1<\beta_3$ then 
+$\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
-The following result summarizes these findings.
+The following result summaries these findings.
 
@@
 
-\item \emph{Fixation of the defector phenotype $B$}, if $T_A>T_B$ and $\beta_1<\beta_3<0$, or $T_A<T_B$ and $\beta_3<0$.
+\item \emph{Fixation of the defector phenotype $B$}, if $T_A>T_B$ and $\beta_3<\beta_1$, or $T_A<T_B$ and $\beta_3<0$.
 
@@
 
-\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_3<\beta_1$.
+\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_1<\beta_3<0$.
 

### 2020-07-16 ms/main.tex
changes and additions by MWF

@@
 \section*{Introduction}
-Cooperative behavior can harm the individual's fitness and increase the fitness of its competitor~\citep{axelrod1981evolution}.
-Yet, cooperative behavior occurs in many non-human animals~\citep{dugatkin1997cooperation}, for example rats~\citep{rice1962altruism} and birds~\citep{krams2008experimental}.
-Therefore, the evolution of cooperative behavior is an important open question in evolutionary biology.
+Cooperative behavior can harm an individual's fitness and increase the fitness of its conspecifics or competitors~\citep{axelrod1981evolution}.
+Nevertheless, cooperative behavior appears to occur in many non-human animals~\citep{dugatkin1997cooperation}, for example rats~\citep{rice1962altruism} and birds~\citep{krams2008experimental}.
+Evolution of cooperative behavior remains  an important  conundrum in evolutionary biology.
 \\
-Cultural evolution is an evolutionary theory of social change.
+Cultural evolution is an evolutionary theory of individual and group-level change in beliefs, behaviors, and norms \citep{cavalli1981cultural}.
 Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
-Under the view of cultural evolution, an individual can acquire its behavior from another individual in its social group through learning or other modes of cultural transmission \citep{richerson2008not}.
+Cultural transmission allows an individual to acquire attitudes and behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
 Here we attempt to determine to what extent cultural transmission can explain the evolution of cooperative behavior.
@@
 
-\paragraph{Kin selection theory} suggests that natural selection can favor cooperative behavior between kin.
+\paragraph{Kin selection theory} posits that natural selection can favor cooperation between related individuals.
 The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}.
-According to Hamilton, kin selection causes allele to increase in frequency when the the reproductive cost to the actor, $c$, is less than the benefit to the recipient, $b$, times the genetic relatedness between the recipient and the actor, $r$.
+According to Hamilton,  an allele that determines altruistic behavior should increase in frequency when  the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the genetic relatedness between the recipient and the actor, $r$.
 This is also known as Hamilton's Rule:
@@
 There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
-It has been suggested that kin selection to explain the cooperative behavior of eusocial insects like the honey bee.
-The most significant argument against kin selection is that cooperation can evolve with zero relatedness~\citep{wilson2005kin}.
-This makes Hamilton's rule incomplete according to \citet{wilson2005kin}.
-\citet{foster2006kin} reject this claim.
-They argue that altruism without relatedness can not evolve.
-They refer us to Hamilton who claimed that relatedness can arise without recent common ancestry.
-\citet{wilson2005kin} also criticizes kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions.
-On the other hand, \citet{foster2006kin} argue that kin selection does not ignore ecology.
-Hamilton's rule shows
+It has been suggested that kin selection can explain the cooperative behavior of worker castes of eusocial insects like the honey bee.
+The most significant argument against kin selection is that in some cases cooperation among unrelated individuals appears to have evolved~\citep{wilson2005kin}.
+This makes Hamilton's rule incomplete according to \citet{wilson2005kin}, although \citet{foster2006kin} reject this claim and argue that altruism cannot evolve without relatedness.
+They refer  to Hamilton, who claimed that relatedness can arise without recent common ancestry.
+%MWF: How?
+\citet{wilson2005kin} also criticizes kin selection on the grounds that environmental or ecological factors are probably more important than relatedness in determining social actions.
+Although \citet{foster2006kin} argue that kin selection does not ignore ecology.
+Hamilton's rule suggests
 that environmental factors causing a high benefit-to-cost ratio will favor cooperation.
 
-\paragraph{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation.
-In \emph{direct reciprocity} there are a repeated encounters between the same two individuals.
-In every encounter, each player has a choice between cooperation and defection.
-If I cooperate now, you may cooperate later.
+\paragraph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
+In \emph{direct reciprocity} there are repeated encounters between the same two individuals, where at every encounter, each player has a choice between cooperation and defection: if I cooperate now, you may cooperate later.
 Hence, it may pay off to cooperate.
-This game-theoretic framework is known as the repeated Prisoner's Dilemma. 
+This game-theoretic framework, known as the repeated Prisoner's Dilemma, 
 %A well known strategy to play this game is called  'tit-for-tat'.
@@
 However,
-Direct reciprocity can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability for another encounter between the same two individuals, $w$,
+can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability of another encounter between the same two individuals, $w$, 
+%MWF: Referencess?
 
@@
 
-Direct reciprocity assumes that both players are in a position to cooperate.
-Direct reciprocity can not explain cooperation in asymmetric interactions.
-In humans, such interactions happen often, for example humans often donate money.
+Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy.
 
-\paragraph{Indirect reciprocity} has been suggested to explain this behavior.
+\paragraph{Indirect reciprocity} has also been suggested as an explanation of this behavior.
 \citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money. 
-The money that "fuels the engines" of indirect reciprocity is reputation.
-However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.
+%MWF: More refs
+The money that ``fuels the engines'' of indirect reciprocity is reputation. 
+However, reciprocity assumes repeated interactions and therefore has difficulty in explaining the evolution of cooperation if  interactions are not repeated.
 
-\paragraph{Group selection theory} posits that cooperation is favored because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
-A common model for group selection work as is: the population is divided into groups.
-In each groups there are cooperators, which help to other group members and defectors which do not help.
+\paragraph{Group selection theory} posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
+A common model for group selection divides the population into groups in which there are cooperators that help  other group members and defectors that do not.
 % TODO add reference
-Individuals reproduce proportional to their fitness. Offspring are added to the same group.
-If a group reaches a certain size it can split to two groups. A group that grow faster will split more often.
-Groups of cooperators are growing faster than group of defectors.
-Therefore, cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
+Individuals reproduce proportionally to their fitness, and offspring are added to the same group as their parents.
+If a group reaches a certain size it can split to two groups, so groups that grow faster will split more often.
+Groups with cooperators  grow faster than groups without cooperators, and
+cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
 
@@
 
-Group selection was criticized by biologists advocate gene-centered view of evolution.
-Group selection has been criticized due to the fact that the trait like cooperation evolves in the total population.
-According to natural selection, if cooperation took over the population it must have better fitness.
-However, in group selection the fitness of cooperator in the individual level is lower.
-The fact that a trait with a lower fitness took over the population is a contradiction.
-\citet{eldakar2011eight} reject this argument.
-They believe that this argument is a tautology and does not qualify as an argument against group selection.
-The distinction between individual and group selection requires a comparison of fitness differentials within and among groups in a multi group population.
-When a trait is evolve by group selection, despite the fact that it has lower fitness within the group, it has a better fit, all thing considered.
+Group selection has been criticized by biologists who advocate a gene-centered view of evolution.
+Group selection has also been criticized because a trait such as cooperation evolves in the total population.
+For cooperation to take over the population it must have higher fitness, while under group selection the fitness of cooperators at the individual level is lower.
+Thus a trait with a lower fitness taking over the population is a contradiction.
+\citet{eldakar2011eight} reject this argument claiming that it is a tautology and does not qualify as an argument against group selection.
+The distinction between individual and group selection requires a comparison of fitness differentials within and between groups in a multi-group population, and when a trait  evolves by group selection, despite having lower fitness within a group, that group might have higher average fitness in competition with other groups, all things considered.
 
 \paragraph{}
-All the above theories assume that cooperation is genetically determined. This raises the question, is it possible that cooperation is determined by non-genetic factors?
-Recent work by \citet{lewin2017microbes} sheds some light on this question. 
-\citet{lewin2017microbes} have hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
+All the above theories assume that cooperation is genetically determined, which raises the question, is it possible that cooperation is determined by non-genetic factors?
+\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
+They showed that under vertical (parent-to-offspring) cultural transmission, Hamilton's rule does not govern the evolution of parent-to-offspring or sib-to-sib altruism.
+Recent work by \citet{lewin2017microbes} also sheds some light on this question. 
+They hypothesise that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
 Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{poulin2010parasite,dobson1988population}.
 Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
-Microbes can be transmitted \emph{horizontally} from one host to another during host interactions.
-Following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}.
-Microbes can also transfer vertically, from parent to offspring.
-% yr: cite 10.1126/science.aat7164
-As a result, a microbe that induces its host to cooperate with another host and thereby increases the other host fitness will  increase the vertical transmission of the microbes of the receiving individual.
+Microbes can be transmitted \emph{horizontally} from one host to another during host interactions, and following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}.
+Microbes can also be transferred vertically, from parent to offspring, and % yr: cite 10.1126/science.aat7164
+a microbe that induces its host to cooperate with another host and thereby increases the latter's fitness will  increase the vertical transmission of the microbes of the receiving individual.
 Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
@@
 \citet{lewin2017microbes} have demonstrated that \emph{non-vertical transmission} can help to explain the evolution of cooperative behavior. 
-Non-vertical transmission could be either a horizontal or oblique.
-Horizontal transmission occurs between individuals from the same generation.
-Oblique transmission occurs from an adult to an offspring.
-Evolution under either of these transmission models is can be be more rapid than under pure vertical transmission~\citep{ram2018evolution}. % (yr: not sure that this is a good reference)
+Non-vertical transmission may be either a horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs from an adult to an offspring.
+Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,ram2018evolution}.
+% (yr: not sure that this is a good reference)
 
@@
 For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future.
-Surprisingly, some of the analysis made by \citet{lewin2017microbes} can be applied to cultural transmission, because cultural transmission is mathematically akin to transmission of infectious diseases~\citep{cavalli1981cultural}.
+Some of the analysis made by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
 
-Here, we hypothesize that non-vertical cultural transmission can explain the evolution of cooperation.
-We are develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.
+Here, we develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.
+We hypothesize that non-vertical cultural transmission can explain the evolution of cooperation.
 
@@
 
-Individuals interact in a social interaction modeled as a prisoner's dilemma.
-Specifically, individuals interact in pairs, cooperators pay a fitness cost $0<c<1$, and their partner gains a fitness benefit $b$, where we assume $b>c$.
-The following payoff matrix shows the fitness of an individual with phenotype $\phi_1$ when interacting with a partner with phenotype $\phi_2$ ($b>c>0$):
+Individuals interact according to a prisoner's dilemma.
+Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $b>c$.
+The following payoff matrix shows the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$ ($b>c>0$):
 
@@
 
-Social interactions occur randomly.
-So, two individuals with phenotype $A$ interact with probability $\hat{p}^2$, two individuals with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two individuals with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
+Social interactions occur randomly:
+two individuals with phenotype $A$ interact with probability $\hat{p}^2$, two individuals with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two individuals with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
 
@@
 \end{equation}
-which can be simplified into
+which simplifies to
 \begin{equation}\label{eq:nextgen_adults_slimpify}
@@
 
-The frequency of $A$ among parents follows a similar dynamic, but also includes the effect of natural selection, and is therefore
+The frequency of $A$ among parents (after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
 \begin{equation}\label{eq:nextgen_parents}
@@
 \bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)
-\end{equation}
+\end{equation}  %MWF: Define w_A, w_B.
 is the population mean fitness.
-Eq~\ref{eq:nextgen_parents} can be slimpified to
+Eq~\ref{eq:nextgen_parents} can be simplified to
 \begin{equation}\label{eq:nextgen_parents_simplified}
@@
 \hline
-\textbf{Interaction Type} & \textbf{Frequency}    & \textbf{Fitness}      & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Probability of first interactor\\  to be A following interaction\end{tabular}}}                                                                                                     \\ \hline
+\textbf{Interaction Type} & \textbf{Frequency}    & \textbf{Fitness}      & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Probability of first interactor\\  to be A %MWF: What is A?
+ following interaction\end{tabular}}}                                                                                                     \\ \hline
 \multicolumn{1}{|l|}{}    & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission\\  from partner, \\ probability $\alpha$\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission \\ from population, \\ probability $1-\alpha$\end{tabular}} \\ \hline
@@
 \end{tabular}
-\caption{Fitness and probabilityof first interactor to be A following interaction by interaction type}
+\caption{Fitness and probability of the first interactor to be A following interaction by interaction type} %MWF: What is A?
 \label{table:1}
@@
   \includegraphics[scale=1]{figure1.pdf}
-  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interaction partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
+  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
   \label{fig:horizontal}
@@
 
-We start by inspecting specific cases, for which we can derive general results. 
-Afterwards, we use numerical simulation to analyze more complex cases.
+We start by studying specific cases, for which we can derive general results, and then 
+we use numerical simulation to analyze more complex cases.
 
@@
 \textbf{Result 1: Vertical and horizontal transmission of cooperation.}
-If 
+From eq.~\ref{eq:nextgen_parents_vertical_only}, if
 \begin{equation} \label{eq:unequal_transmission}
@@
 
-Therefore, because all the parameters are all positive, cooperation cannot take over the population (and furthermore will become extinct) if cooperators doesn't have a horizontal transmission bias, i.e.
+Therefore, since all the parameters are  positive, cooperation cannot take over the population (and furthermore will become extinct) if cooperators do not have a horizontal transmission bias, i.e.
 if $T_A\leq T_B$.
@@
 \end{equation}
-A sufficient condition for evolution of cooperation is that $\tilde{p}^{*} < 0$, which occurs if
+A sufficient condition for evolution of cooperation is that $\tilde{p}^{*} < 0$, namely
 \begin{equation} \label{eq:sufficient_horizontal_transmission_from_population}
@@
 \begin{equation}  \label{eq:nextgen_parents_oblique_only}
-p' = p^2 (T_B-T_A) + p (1+T_A-T_B) .
+p' = p^2 (T_B-T_A) + p (1+T_A-T_B) ,
 \end{equation}
 
-We find the following results.
+which gives the following result.
 
 \textbf{Result 2: Oblique and horizontal transmission of cooperation.} 
-If there is a horizontal transmission bias in favor of cooperation,
+If there is a horizontal transmission bias in favor of cooperation, namely
 \begin{equation} \label{eq:oblique_only_result}
@@
 
-In this case $0<v<1$, and the equation system is more complex.
-Therefore, we focus on local, rather than global, stability.\\
+In this case $0<v<1$, and the recursion system is more complex.
+Therefore, we focus on local, rather than global, stability.
 To proceed, we note that 
@@
 Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$.
-We then determine the equilibria of this equation, that is, solutions for $\hat{p}' = \hat{p}$, and analyse their local stability: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
-%TODO show this is necessary and sufficient
+We then determine the equilibria, which are solutions of $\hat{p}' = \hat{p}$, and analyse their local stability: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
+%MWF: Define f(\hat p).
 
-We start with the simpler case of symmetric horizontal transmission, $T=T_A=T_B$. 
-We apply eqs.~\ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to define 
+We start with the simple case of symmetrical horizontal transmission, $T=T_A=T_B$ and 
+%MWF: Write the full recursion.
+apply eqs.~\ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to obtain 
 \begin{equation} \label{eq:equal_horizontal_transmission}
@@
 
-The equilibria are solutions to $f(\hat{p})=0$, or $\hat{p}' = \hat{p}$.
+The equilibria are solutions of $f(\hat{p})=0$, or $\hat{p}' = \hat{p}$.
 It is easy to verify that fixation of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$, is an equilibrium.
@@
 \end{equation}
-which gives us the following result.
+which produces the following result.
 
@@
 \end{equation}
-Since $f(\hat{p})$ is a cubic polynomial, three equilibria exist.
-We already know that $\hat{p} = 0 $ and $\hat{p} = 1$ are equilibria.
-By solving $f(\hat{p})/\big[\hat{p}(1-\hat{p})\big] = \beta_3 -\beta_1 \hat{p} = 0$ we can find the third equilibrium,
+Since $f(\hat{p})$ is a cubic polynomial, three equilibria may exist, two of which are
+$\hat{p} = 0 $ and $\hat{p} = 1$.
+By solving $f(\hat{p})/\big[\hat{p}(1-\hat{p})\big] = \beta_3 -\beta_1 \hat{p} = 0$ we  find the third equilibrium
 \begin{equation} \label{eq:oblique_and_vertic_result}
@@
 
-Note that the sign of the cubic $f(\hat{p})$ at positive (negative) infinity is equal (inverse) to the sign of $\beta_1$. 
+Note that the sign of the cubic $f(\hat{p})$ at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
 If $T_A>T_B$, then 
@@
  \end{equation}
-since $c<b$, and $1>\alpha v$.
-So the sign of the cubic at positive and negative infinity is negative and positive, respectively.
+since $c<b$ and $1>\alpha v$, the sign of the cubic at positive and negative infinity is negative and positive, respectively.
 First, if $\beta_3<\beta_1$ then 
@@
 since $c<b$, and $1>\alpha v$. So the sign of the cubic at positive and negative infinity is positive and negative, respectively. 
-First, if $\beta_3<0$ then 
-$\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
-Second, if $0<\beta_3<\beta_1$ then 
-$0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then 
-$\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
+Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
+Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
-The following result summaries these findings.
+The following result summarizes these findings.
 
@@
 
-\item \emph{Fixation of the defector phenotype $B$}, if $T_A>T_B$ and $\beta_3<\beta_1$, or $T_A<T_B$ and $\beta_3<0$.
+\item \emph{Fixation of the defector phenotype $B$}, if $T_A>T_B$ and $\beta_1<\beta_3<0$, or $T_A<T_B$ and $\beta_3<0$.
 
@@
 
-\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_1<\beta_3<0$.
+\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_3<\beta_1$.
 
@@
 \section*{Appendix A} % TODO fix equations references
-In the section, we start with eq.~\ref{eq:nextgen_parents_vertical_only} and we want to investigate when $\tilde{p}< \tilde{p}'$. 
+In the section, we start with eq.~\ref{eq:nextgen_parents_vertical_only} and we want to investigate when $\tilde{p}< \tilde{p}'$, that is, when 
 \begin{equation} 
@@
 \end{equation}
-First divide by $\tilde{p}$, thus eq.~\ref{eq:horizontal_transmission_from_interaction_step0} becomes
+First divide by $\tilde{p}$ to obtain
 \begin{equation} 
@@
 \end{equation}
-We know that the mean fitness $\bar{w} = 1 + \tilde{p}(b-c)$, thus eq.~\ref{eq:horizontal_transmission_from_interaction_step1} becomes
+We know that the mean fitness $\bar{w} = 1 + \tilde{p}(b-c)$ Tthus eq.~\ref{eq:horizontal_transmission_from_interaction_step1} becomes
 \begin{equation} 
@@
 \end{equation}
-Eq.~\ref{eq:horizontal_transmission_from_interaction_step2} can be simplified into eq.~\ref{eq:unequal_transmission}.
+Eq.~\ref{eq:horizontal_transmission_from_interaction_step2} can be simplified to become inequality~\ref{eq:unequal_transmission}.
 

### 2020-07-19 ms/main.tex
fix tables; remove wA wB

@@
 \usepackage{commath}
-\usepackage{longtable}
 \usepackage[hyphens]{url}
@@
 \usepackage{authblk}
+\usepackage{longtable}
+\usepackage{multirow}
+\usepackage{booktabs}
 
@@
 
-Consider a very large population whose members are characterized by their phenotype $\phi$, which can be of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors, with corresponding fitness values $w_A$ and $w_B$, which depend on the frequency of the phenotypes (see below).
+Consider a very large population whose members are characterized by their phenotype $\phi$, which can be of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors.
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
@@
 Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $b>c$.
-The following payoff matrix shows the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$ ($b>c>0$):
+\autoref{table:prisoner_payoff} shows the payoff matrix, i.e.
+the fitness, of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$ (we assume $b>c>0$):
 
-\begin{table}[h]\label{table:prisoner_payoff}
+% Table: payoff matrix
+
+\begin{table}[h]
 \centering
 \begin{tabular}{lll}
-           & $\phi_2=A$ & $\phi_2=B$ \\
-$\phi_1=A$ & $b-c$      & $-c$       \\
-$\phi_1=B$ & $b$        & $0$       
+\toprule
+           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
+$\phi_1=A$ & $1+b-c$ & $1-c$ \\
+$\phi_1=B$ & $1+b$   & $1$
+\\ \bottomrule
 \end{tabular}
+\caption{\textbf{Payoff matrix for prisoner's dilemma.}
+The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
+$b>c>0$.
+}
+\label{table:prisoner_payoff}
 \end{table}
@@
 
-%Therefore, the fitness values of the two phenotypes, $w_A$ and $w_B$ are
-%
-%\begin{equation}\label{eq:fitness}
-%\begin{aligned}
-%w_A(\hat{p}) & = \hat{p}(1+b-c) + (1-\hat{p})(1-c) = 1 - c + \hat{p} b \\
-%w_B(\hat{p}) & = \hat{p}(1+b) + (1-\hat{p}) = 1 + \hat{p} b,
-%\end{aligned}
-%\end{equation}
-%and the population mean fitness is therefore
-%$\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)$.
-
 Horizontal cultural transmission occurs between peers. 
@@
 The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.\\
-\autoref{table:1} contains the probability of first interactor to be A following interaction by interaction type.
+\autoref{table:interactions} contains the probability of first interactor to be A following interaction by interaction type.
 Therefore, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 \end{equation}
-where fitness values are taken from \autoref{table:1}, and 
+where fitness values are taken from \autoref{table:interactions}, and 
 \begin{equation} \label{eq:mean_fitness}
-\bar{w} = \hat{p} w_A + (1-\hat{p}) w_B = 1 + \hat{p}(b-c)
-\end{equation}  %MWF: Define w_A, w_B.
+\bar{w} =  1 + \hat{p}(b-c)
+\end{equation}
 is the population mean fitness.
@@
 
-\begin{table}[H]
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\textbf{Interaction Type} & \textbf{Frequency}    & \textbf{Fitness}      & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Probability of first interactor\\  to be A %MWF: What is A?
- following interaction\end{tabular}}}                                                                                                     \\ \hline
-\multicolumn{1}{|l|}{}    & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission\\  from partner, \\ probability $\alpha$\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission \\ from population, \\ probability $1-\alpha$\end{tabular}} \\ \hline
-$AxA$                     & $\hat{p}^2$           & $1+b-c$               & $1$                                                                                                               & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
-$AxB$                     & $\hat{p}(1-\hat{p})$  & $1-c$                 & $1-T_B$                                                                                                           & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
-$BxA$                     & $\hat{p}(1-\hat{p})$  & $1+b$                 & $T_A$                                                                                                             & $\hat{p}T_A$                                                                                                           \\ \hline
-$BxB$                     & $(1-\hat{p})^2$       & $1$                   & $0$                                                                                                               & $\hat{p}T_A$                                                                                                           \\ \hline
+% Table: interactions
+\begin{table}[]
+\begin{tabular}{@{}llllll@{}}
+\toprule
+\multirow{2}{*}{Phenotype $\phi_1$} &
+  \multirow{2}{*}{Phenotype $\phi_2$} &
+  \multirow{2}{*}{Frequency} &
+  \multirow{2}{*}{Fitness of $\phi_1$} &
+  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
+    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
+$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
+$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
 \end{tabular}
-\caption{Fitness and probability of the first interactor to be A following interaction by interaction type} %MWF: What is A?
-\label{table:1}
+\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
+\label{table:interactions}
 \end{table}
 
+% Figure: model illustration
 \begin{figure}[b]

### 2020-07-20 ms/main.tex
revised intro, added some discussion paragraphs

@@
 
-\affil[1]{School of Computer Sciences, IDC Herzliya, Herzliya, Israel}
+\affil[1]{School of Computer Science, Inetdisciplinary Center Herzliya, Herzliya, Israel}
 \affil[2]{School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv, Israel}
@@
 % subsection
-\subsection*{Theories for evolution of cooperation}
-Three major theories have been proposed to explain the evolution of cooperative behavior.
-
-\paragraph{Kin selection theory} posits that natural selection can favor cooperation between related individuals.
+%\subsection*{Theories for evolution of cooperation}
+Three major theories have been proposed to explain the evolution of cooperative behavior:\\
+1.
+\emph{Kin selection} theory posits that natural selection can favor cooperation between related individuals.
 The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}.
@@
 This is also known as Hamilton's Rule:
-
 \begin{equation} \label{eq:hamilton_rule}
@@
 
-There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
-It has been suggested that kin selection can explain the cooperative behavior of worker castes of eusocial insects like the honey bee.
+There is an ongoing debate about the extent to which kin selection explains the evolution of cooperation and altruism.
+For example, it has been suggested that it can explain the cooperative behavior of worker castes of eusocial insects like the honey bee. % TODO REF
 The most significant argument against kin selection is that in some cases cooperation among unrelated individuals appears to have evolved~\citep{wilson2005kin}.
-This makes Hamilton's rule incomplete according to \citet{wilson2005kin}, although \citet{foster2006kin} reject this claim and argue that altruism cannot evolve without relatedness.
+According to \citet{wilson2005kin}, this makes Hamilton's rule incomplete, although \citet{foster2006kin} reject this claim and argue that altruism cannot evolve without relatedness.
 They refer  to Hamilton, who claimed that relatedness can arise without recent common ancestry.
@@
 \citet{wilson2005kin} also criticizes kin selection on the grounds that environmental or ecological factors are probably more important than relatedness in determining social actions.
-Although \citet{foster2006kin} argue that kin selection does not ignore ecology.
-Hamilton's rule suggests
-that environmental factors causing a high benefit-to-cost ratio will favor cooperation.
+However, \citet{foster2006kin} argue that kin selection does not ignore ecology, and Hamilton's rule suggests that environmental factors causing a high benefit-to-cost ratio will favor cooperation.
 
-\paragraph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
-In \emph{direct reciprocity} there are repeated encounters between the same two individuals, where at every encounter, each player has a choice between cooperation and defection: if I cooperate now, you may cooperate later.
-Hence, it may pay off to cooperate.
-This game-theoretic framework, known as the repeated Prisoner's Dilemma, 
+2.
+\emph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
+In \emph{direct reciprocity} there are repeated encounters between the same two individuals, and at every encounter each individual has a choice between cooperation and defection.
+Hence, it may eventually pay off to cooperate if it may cause your partner to cooperate in the future.
+This game-theoretic framework, known as the \emph{repeated prisoner's dilemma}, 
 %A well known strategy to play this game is called  'tit-for-tat'.
@@
 can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability of another encounter between the same two individuals, $w$, 
-%MWF: Referencess?
-
+%TODO Referencess
 \begin{equation} \label{eq:reciprocity}
@@
 
-Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy.
-
-\paragraph{Indirect reciprocity} has also been suggested as an explanation of this behavior.
-\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money. 
-%MWF: More refs
-The money that ``fuels the engines'' of indirect reciprocity is reputation. 
+Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy. \\
+\emph{Indirect reciprocity} has also been suggested to explain the evolution of cooperation.
+\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of currency. 
+%TODO: refs
+The currency that ``fuels the engines'' of indirect reciprocity is \emph{reputation}. 
 However, reciprocity assumes repeated interactions and therefore has difficulty in explaining the evolution of cooperation if  interactions are not repeated.
 
-\paragraph{Group selection theory} posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
+3.
+\emph{Group selection} theory posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
 A common model for group selection divides the population into groups in which there are cooperators that help  other group members and defectors that do not.
@@
 cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
-
 \begin{equation} \label{eq:groupselection}
@@
 Group selection has been criticized by biologists who advocate a gene-centered view of evolution.
-Group selection has also been criticized because a trait such as cooperation evolves in the total population.
-For cooperation to take over the population it must have higher fitness, while under group selection the fitness of cooperators at the individual level is lower.
-Thus a trait with a lower fitness taking over the population is a contradiction.
-\citet{eldakar2011eight} reject this argument claiming that it is a tautology and does not qualify as an argument against group selection.
+It has also been criticized because for cooperation to take over the population it must have higher fitness than defection, while under group selection theory the fitness of cooperators at the individual level is lower than the fitness of defectors.
+Thus a trait with a lower fitness taking over the population is a contradiction %TODO ref.
+\citet{eldakar2011eight} reject this argument, claiming that it is a tautology and does not qualify as an argument against group selection.
 The distinction between individual and group selection requires a comparison of fitness differentials within and between groups in a multi-group population, and when a trait  evolves by group selection, despite having lower fitness within a group, that group might have higher average fitness in competition with other groups, all things considered.
+% TODO cite Simpsons' paradox?
 
-\paragraph{}
-All the above theories assume that cooperation is genetically determined, which raises the question, is it possible that cooperation is determined by non-genetic factors?
+The above theories assume that cooperation is genetically determined, which raises the question: \emph{Is it possible that cooperation is determined by non-genetic factors?}
 \citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
 They showed that under vertical (parent-to-offspring) cultural transmission, Hamilton's rule does not govern the evolution of parent-to-offspring or sib-to-sib altruism.
-Recent work by \citet{lewin2017microbes} also sheds some light on this question. 
-They hypothesise that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
-Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{poulin2010parasite,dobson1988population}.
-Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
-Microbes can be transmitted \emph{horizontally} from one host to another during host interactions, and following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}.
-Microbes can also be transferred vertically, from parent to offspring, and % yr: cite 10.1126/science.aat7164
-a microbe that induces its host to cooperate with another host and thereby increases the latter's fitness will  increase the vertical transmission of the microbes of the receiving individual.
-Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
-%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\citep{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behavior of their hosts.
+Non-vertical transmission may be either a horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs from an adult to an unrelated offspring.
+Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,ram2018evolution}.
 
-% subsection
-\subsection*{Cultural evolution of cooperation}
-\citet{lewin2017microbes} have demonstrated that \emph{non-vertical transmission} can help to explain the evolution of cooperative behavior. 
-Non-vertical transmission may be either a horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs from an adult to an offspring.
-Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,ram2018evolution}.
-% (yr: not sure that this is a good reference)
+\citet{lewin2017microbes} have demonstrated that \emph{non-vertical transmission}, mediated by microbes that manipulate their host behavior, can help to explain the evolution of cooperative behavior.
+Interestingly, some of the analysis made by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
 
-Here we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interaction.
+Here we hypothesize that non-vertical cultural transmission can explain the evolution of cooperation. 
+To test this hypothesis, we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interaction.
 For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future.
-Some of the analysis made by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
-
-Here, we develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.
-We hypothesize that non-vertical cultural transmission can explain the evolution of cooperation.
+We develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.  
+Our results demonstrate the conditions in which cooperation can evolve when it is culturally, rather than genetically, transmitted.
 
@@
 % Discussion
-%\section*{Discussion}
-%We hypothesized that non-vertical transmission can explain the evolution of cooperation.
+\section*{Discussion}
+We hypothesized that non-vertical transmission can explain the evolution of cooperation.
 We used a model with non-vertical transmissions and have found that if eq.~\ref{eq:unequal_transmission} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff.
 In addition, we found that when horizontal transmission cannot occur after interaction ($\alpha = 0$) cooperation will always become extinct.
-%Our results improve our understating of cultural evolution of cooperation.
+Our results improve our understating of cultural evolution of cooperation.
 Our model shows that cooperation can evolve even in a fully mixed population, where the population is non-structured, there are no repeating interactions and nor individual recognition.
+
+Recent work by \citet{lewin2017microbes} also sheds some light on this question. 
+They hypothesise that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
+Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{dobson1988population,poulin2010parasite}.
+Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
+Microbes can be transmitted \emph{horizontally} from one host to another during host interactions, and following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}.
+Microbes can also be transferred vertically, from parent to offspring, and % yr: cite 10.1126/science.aat7164
+a microbe that induces its host to cooperate with another host and thereby increases the latter's fitness will  increase the vertical transmission of the microbes of the receiving individual.
+Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
+%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\citep{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behavior of their hosts.
 

### 2020-07-26 ms/main.tex
merged result 3 and 4; separated appendix B to B and C; using appendix package; appendix eqs numbers; fixed sympy citation key

@@
 \usepackage{booktabs}
+\usepackage{lipsum}  
+\usepackage[title,page]{appendix}
+\usepackage{chngcntr}
 
@@
 
+% line numbers
+ \usepackage[displaymath, mathlines]{lineno}
+ \renewcommand\linenumberfont{\normalfont\small\sffamily}
+\linenumbers
+\modulolinenumbers[2]
+
 % Yoav & Lee commands
@@
 \newcommand{\ci}{I}
+
+% Supplementary
+% https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
+\newcommand{\beginsupplement}{%
+      	\setcounter{table}{0}
+        \renewcommand{\thetable}{S\arabic{table}}%
+        \setcounter{figure}{0}
+        \renewcommand{\thefigure}{S\arabic{figure}}%
+		\setcounter{equation}{0}
+        \renewcommand{\theequation}{A\arabic{equation}}%
+}
 
@@
 
-% Introduction
+%%% Introduction
 \section*{Introduction}
@@
 Evolution of cooperative behavior remains an important conundrum in evolutionary biology.
-\\
-Cultural evolution is an evolutionary theory of individual and group-level change in beliefs, behaviors, and norms \citep{cavalli1981cultural}.
-Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
-Cultural transmission allows an individual to acquire attitudes and behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
-Here we attempt to determine to what extent cultural transmission can explain the evolution of cooperative behavior.
+Three major theories have been proposed to explain the evolution of cooperative behavior:
 
-% subsection
-%\subsection*{Theories for evolution of cooperation}
-Three major theories have been proposed to explain the evolution of cooperative behavior:\\
 1.
@@
 
-Group selection has been criticized by biologists who advocate a gene-centered view of evolution.
+Group selection has been criticized by biologists who advocate a gene-centered view of evolution. % TODO ref
 It has also been criticized because for cooperation to take over the population it must have higher fitness than defection, while under group selection theory the fitness of cooperators at the individual level is lower than the fitness of defectors.
@@
 
-The above theories assume that cooperation is genetically determined, which raises the question: \emph{Is it possible that cooperation is determined by non-genetic factors?}
+These theories assume that cooperation is genetically determined, which raises the question: \emph{Is it possible that cooperation is determined by non-genetic factors?}
+Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
+Here we attempt to determine to what extent the evolution of cooperative behavior can be explained by \emph{cultural transmission},
+which allows an individual to acquire attitudes and behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
 \citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
 They showed that under vertical (parent-to-offspring) cultural transmission, Hamilton's rule does not govern the evolution of parent-to-offspring or sib-to-sib altruism.
-Non-vertical transmission may be either a horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs from an adult to an unrelated offspring.
+
+\emph{Non-vertical transmission} may be either horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs from adults to unrelated offspring.
 Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,ram2018evolution}.
-
-\citet{lewin2017microbes} have demonstrated that \emph{non-vertical transmission}, mediated by microbes that manipulate their host behavior, can help to explain the evolution of cooperative behavior.
-Interestingly, some of the analysis made by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
+\citet{lewin2017microbes} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host behavior, can help to explain the evolution of cooperative behavior.
+Interestingly, some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
 
 Here we hypothesize that non-vertical cultural transmission can explain the evolution of cooperation. 
-To test this hypothesis, we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interaction.
-For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will cooperate in the future.
-We develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using both mathematical analysis and simulations.  
-Our results demonstrate the conditions in which cooperation can evolve when it is culturally, rather than genetically, transmitted.
+To test this hypothesis, we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
+For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will be cooperative in the future.
+We develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using mathematical analysis and simulations.  
+Our results demonstrate cultural transmission can facilitate the evolution of cooperation even when genetic transmission cannot.
+These results suggest that further research on the evolution of cooperation should account for non-vertical transmission and that treatment of cooperation as a cultural, rather then genetic trait, can lead to a better understanding of this important and enigmatic phenomenon.
 
-% Models and Methods
-\section*{Models and Methods}
+% Models
+\section*{Models}
 
-First, we focus on the evolution of cooperation in a fully mixed population where cooperation is modeled using the prisoner's dilemma. % yr: add ref
+We focus on the evolution of cooperation in a fully mixed population where cooperation is modeled using the \emph{prisoner's dilemma}. % yr: add ref
 
@@
 Individuals interact according to a prisoner's dilemma.
-Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $b>c$.
-\autoref{table:prisoner_payoff} shows the payoff matrix, i.e.
-the fitness, of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$ (we assume $b>c>0$):
+Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $b>c>0$.
+\textbf{\autoref{table:prisoner_payoff}} shows the payoff matrix, i.e.
+the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
 
-% Table: payoff matrix
-
+%%% Table: payoff matrix
 \begin{table}[h]
@@
 \end{table}
+%%%
 
@@
 Horizontal transmission is not always successful, as one peer may reject the other's phenotype.
-The probability for successful transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.\\
-\autoref{table:interactions} contains the probability of first interactor to be A following interaction by interaction type.
+The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\textbf{\autoref{table:interactions}}).
+
 Therefore, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 
-The frequency of $A$ among parents (after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
+The frequency of $A$ among parents (i.e. after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
 \begin{equation}\label{eq:nextgen_parents}
@@
 \end{equation}
-where fitness values are taken from \autoref{table:interactions}, and 
+where fitness values are taken from \textbf{\autoref{table:prisoner_payoff}} and \textbf{\autoref{table:interactions}}, and the population mean fitness is
 \begin{equation} \label{eq:mean_fitness}
-\bar{w} =  1 + \hat{p}(b-c)
+\bar{w} =  1 + \hat{p}(b-c).
 \end{equation}
-is the population mean fitness.
-Eq~\ref{eq:nextgen_parents} can be simplified to
+
+\autoref{eq:nextgen_parents} can be simplified to
 \begin{equation}\label{eq:nextgen_parents_simplified}
@@
 
-% Table: interactions
+%%% Table: interactions
 \begin{table}[]
@@
 \end{table}
+%%%
 
-% Figure: model illustration
+%%% Figure: model illustration
 \begin{figure}[b]
@@
 \end{figure}
+%%%
 
-% Results
+%%% Results
 \section*{Results}
 
-We start by studying specific cases, for which we can derive general results, and then 
-we use numerical simulation to analyze more complex cases.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Without Oblique Transmission}
 
-With only vertical and horizontal transmission, i.e. $v=1$, eq.~\ref{eq:horizontal} becomes
+With only vertical and horizontal transmission, i.e. $v=1$, \autoref{eq:horizontal} becomes
 $\hat{p} =  \tilde{p}$,
-and eq.~\ref{eq:nextgen_parents_simplified} for the change in frequency $p'$ of phenotype $A$ among parents can be written as
-
-\begin{equation} 
-\begin{split}\label{eq:nextgen_parents_vertical_only}
+and \autoref{eq:nextgen_parents_simplified} for the change in frequency $p'$ of phenotype $A$ among parents can be written as
+\begin{equation} \label{eq:nextgen_parents_vertical_only} 
+\begin{aligned}
 \bar{w} \tilde{p}' 
@@
 & + \tilde{p}(1-\tilde{p}) (1+b) [\tilde{p} (1-\alpha) + \alpha] T_A \\
-& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A
-\end{split}
+& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A .
+\end{aligned}
 \end{equation}
@@
 \textbf{Result 1: Vertical and horizontal transmission of cooperation.}
-From eq.~\ref{eq:nextgen_parents_vertical_only}, if
+From \autoref{eq:nextgen_parents_vertical_only}, if
 \begin{equation} \label{eq:unequal_transmission}
@@
 \end{equation}
-which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}), where $r_H=\alpha T/(1-T)$ can be thought of as \emph{horizontal relatedness}.
+which can be seen as a cultural version of \emph{Hamilton's rule} (\autoref{eq:hamilton_rule}), where $r_H=\alpha T/(1-T)$ can be thought of as \emph{horizontal relatedness}.
 Therefore, if the cost $c$ is less than the benefit $b$ times the horizontal relatedness $r_H$, then cooperation will take over of the population (see~\textbf{\autoref{fig:results_a}}).
@@
 In this case $\alpha=1$, and horizontal transmission can only occur as a result of cooperative interactions.
-Therefore, eq.~\ref{eq:unequal_transmission}, which determines the conditions for evolution of cooperation, becomes
+Therefore, \autoref{eq:unequal_transmission}, which determines the conditions for evolution of cooperation, becomes
 \begin{equation}\label{eq:horizontal_transmission_only_after_interaction}
@@
 
-Eq.~\ref{eq:horizontal_transmission_only_after_interaction} can be written as
+\autoref{eq:horizontal_transmission_only_after_interaction} can be written as
 \begin{equation} \label{eq:horizontal_transmission_only_after_interaction2}
@@
 This is the effective benefit for cooperation from this interaction.
-So, eq.~\ref{eq:horizontal_transmission_only_after_interaction2} means that cooperation can evolve if effective cost is less than the effective benefit.
+So, \autoref{eq:horizontal_transmission_only_after_interaction2} means that cooperation can evolve if the effective cost is less than the effective benefit.
 
@@
 In this case $\alpha=0$, and horizontal transmission is entirely independent from cooperative interactions.  
-Then, eq.~\ref{eq:unequal_transmission} becomes
+Then, \autoref{eq:unequal_transmission} becomes
 \begin{equation} \label{eq:horizontal_transmission_from_population}
@@
 With only oblique and horizontal transmission, i.e.
-$v = 0$, eq.~\ref{eq:horizontal} becomes $\hat{p}=p$ and eq.~\ref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
+$v = 0$, \autoref{eq:horizontal} becomes $\hat{p}=p$ and \autoref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
 \begin{equation}  \label{eq:nextgen_parents_oblique_only}
@@
 In this case $0<v<1$, and the recursion system is more complex.
-Therefore, we focus on local, rather than global, stability.
+Therefore, we focus on local stability, rather than global stability.
 To proceed, we note that 
-eq.~\ref{eq:horizontal} can give $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$,
-eq.~\ref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\hat{p}$, and 
-eq.~\ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$.
-We then determine the equilibria, which are solutions of $\hat{p}' = \hat{p}$, and analyse their local stability: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
-%MWF: Define f(\hat p).
+\autoref{eq:horizontal} can give $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$,
+\autoref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, and 
+\autoref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
+Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$, see Appendix~\autoref{sec:appendixB}.
+We then determine the equilibria, which are solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
+%: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})=\bar{w}(\hat{p}'-\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
 
-We start with the simple case of symmetrical horizontal transmission, $T=T_A=T_B$ and 
-%MWF: Write the full recursion.
-apply eqs.~\ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to obtain 
-\begin{equation} \label{eq:equal_horizontal_transmission}
-\begin{aligned}
-  %\hat{p}' - \hat{p} = 
-  %\hat{p} ^2(-\alpha bvT + cv(1-T)) + \hat{p} (\alpha bvT -cv(1-T)) = 
-  f(\hat{p}) &= 
-  \bar{w}(\hat{p}' - \hat{p}) = \\
-  &\hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big]. % shorter version
-\end{aligned}
-\end{equation}
+%We start with the simple case of symmetrical horizontal transmission, $T=T_A=T_B$ and apply \autoref{eq:horizontal}, \autoref{eq:nextgen_adults_slimpify}, and \autoref{eq:nextgen_parents_simplified} to obtain
+%\begin{equation} \label{eq:equal_horizontal_transmission}
+%\begin{aligned}
+%  f(\hat{p}) &= 
+%  \bar{w}(\hat{p}' - \hat{p}) = \\
+%  &\hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big].\end{aligned}
+%\end{equation}
+%A detailed explain of how we get eq.~\ref{eq:equal_horizontal_transmission} can be found in appendix B.
+%The equilibria are solutions of $f(\hat{p})=0$, or $\hat{p}' = \hat{p}$.
+%It is easy to verify that fixation of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$, is an equilibrium.
+%Since the derivative of $f'(\hat{p}$ is 
+%\begin{equation}
+%f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big],
+%\end{equation}
+%then the condition for local stability of $\hat{p}=1$ is
+%\begin{equation} \label{eq:derivative_of_phattag-phat}
+%	f'(1) =	-\alpha bvT + cv(1-T) < 0,
+%\end{equation}
+%which gives the following result.
+%
+%\textbf{Result 3: Oblique and vertical transmission with symmetric horizontal transmission.}
+%If horizontal transmission is symmetric, $T = T_A = T_B$, and if
+%\begin{equation} \label{eq:oblique_and_vertic_result2}
+%  %\frac{b}{c}>\frac{1-T}{\alpha T}
+%	c < b \cdot \frac{\alpha T}{1-T},
+%\end{equation}
+%then fixation of the cooperator phenotype $A$ is locally stable.
+%The same condition was given in Corollary 1.1, \autoref{eq:equal_transmission}.
 
-The equilibria are solutions of $f(\hat{p})=0$, or $\hat{p}' = \hat{p}$.
-It is easy to verify that fixation of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$, is an equilibrium.
-Since the derivative of $f'(\hat{p}$ is 
-\begin{equation}
-f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big],
-\end{equation}
-then the condition for local stability of $\hat{p}=1$ is
-\begin{equation} \label{eq:derivative_of_phattag-phat}
-	f'(1) =
-% 2\cdot\hat{p} (-\alpha bvT + cv(1-T)) + (\alpha bvT -cv(1-T)).
-%	(1- 2\hat{p}) (\alpha bvT - cv(1-T)) \mid_{\hat{p}=1} = 
-	-\alpha bvT + cv(1-T) < 0,
-\end{equation}
-which produces the following result.
+%We now turn to the general case where $T_A \neq T_B$. 
+We apply \autoref{eq:horizontal}, \autoref{eq:nextgen_adults_slimpify}, and \autoref{eq:nextgen_parents_simplified} to obtain the function $f(\hat{p})$, see Appendix~\autoref{sec:appendixB}:
 
-\textbf{Result 3: Oblique and vertical transmission with symmetric horizontal transmission.}
-If horizontal transmission is symmetric, $T = T_A = T_B$, and if
-\begin{equation} \label{eq:oblique_and_vertic_result2}
-  %\frac{b}{c}>\frac{1-T}{\alpha T}
-	c < b \cdot \frac{\alpha T}{1-T},
-\end{equation}
-then fixation of the cooperator phenotype $A$ is locally stable.
-The same condition was given in Corollary 1.1, Eq.~\ref{eq:equal_transmission}.
-% TODO what happens if the condition does not apply? can there be an non-zero stable equilibrium?
-\\
-\\
-We now turn to the general case where $T_A \neq T_B$. We have
 \begin{equation} \label{eq:general_case_polynomial}
@@
 \beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) , \\
-%\beta_2 &= -[c(1-v) - b(1-\alpha v) +  1](T_A-T_B)-\alpha bv T_A + cv(1-T_B) \\
 \beta_2 &= -\beta_1 -\beta_3 ,  \\
@@
 \end{equation}
-Since $f(\hat{p})$ is a cubic polynomial, three equilibria may exist, two of which are
+
+If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$. 
+Therefore, $f(\hat{p})$ is a quadratic polynomial,
+\begin{equation} \label{eq:equal_horizontal_transmission}
+  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big].
+\end{equation}
+Clearly the only two equilibria are the fixations of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$.
+These equilibria are locally stable if $f'(\hat{p})<0$ (Appendix~\autoref{sec:appendixC}).
+Therefore, we find the derivative,
+\begin{equation}
+f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big],
+\end{equation}
+and investigate its sign at the equilibria,
+\begin{equation} \label{eq:derivative_of_phattag-phat}
+\begin{aligned}
+	f'(0) &=	\alpha bvT - cv(1-T), \\
+	f'(1) &=	-\alpha bvT + cv(1-T).
+\end{aligned}
+\end{equation}
+Therefore with symmetric horizontal transmission, fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary 1.1, \autoref{eq:equal_transmission}.
+
+In the general case where $T_A \neq T_B$, the coefficient $\beta_1$ is not necessarily zero, and $f(\hat{p})$ is a cubic polynomial.
+Therefore, three equilibria may exist, two of which are
 $\hat{p} = 0 $ and $\hat{p} = 1$.
@@
   \frac{\beta_3}{\beta_1}.
-  %\frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}
-  %     {\big(c(1-v) -b (1-\alpha v)\big) (T_A-T_B)} .
 \end{equation}
 
-Note that the sign of the cubic $f(\hat{p})$ at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
+Note that the sign of this cubic at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
 If $T_A>T_B$, then 
 \begin{equation} \label{eq:beta1}
-   \beta_1 %& = [c(1-v) - b (1-\alpha v)] (T_A-T_B) \\
-   < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   \beta_1 < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
    = (1-\alpha v)(c-b)(T_A-T_B) < 0 ,
@@
 \begin{equation} \label{eq:beta1_rev}
-   \beta_1 %& = -[c(1-v) - b (1-\alpha v)] (T_A-T_B) \\
-   > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   \beta_1 > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
    = (1-\alpha v)(c-b)(T_A-T_B) > 0,
@@
 
-\textbf{Result 4: Oblique and vertical transmission of cooperation with asymmetric horizontal transmission.}
+\textbf{Result 3: Oblique and vertical transmission of cooperation.}
 The cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the horizontal transmission bias $T_A-T_B$ and the coefficients $\beta_1$ and $\beta_3$:
 \begin{enumerate}
-\item \emph{Fixation of the cooperative phenotype $A$}, if $T_A>T_B$ and $0<\beta_3$, or $T_A<T_B$ and $\beta_1<\beta_3$.
+\item \emph{Fixation of the cooperative phenotype $A$}, 
+\begin{enumerate}
+\item if $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$, or
+\item if $T_A>T_B$ and $0<\beta_3$, or 
+\item if $T_A<T_B$ and $\beta_1<\beta_3$.
+\end{enumerate}
 
-\item \emph{Fixation of the defector phenotype $B$}, if $T_A>T_B$ and $\beta_1<\beta_3<0$, or $T_A<T_B$ and $\beta_3<0$.
+\item \emph{Fixation of the defector phenotype $B$}, 
+\begin{enumerate}
+\item if $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$, or 
+\item if $T_A>T_B$ and $\beta_1<\beta_3<0$, or 
+\item if $T_A<T_B$ and $\beta_3<0$.
+\end{enumerate}
 
@@
 We hypothesized that non-vertical transmission can explain the evolution of cooperation.
-We used a model with non-vertical transmissions and have found that if eq.~\ref{eq:unequal_transmission} is satisfied cooperation will take over the population in fully mixed population with prisoner's dilemma payoff.
-In addition, we found that when horizontal transmission cannot occur after interaction ($\alpha = 0$) cooperation will always become extinct.
-Our results improve our understating of cultural evolution of cooperation.
-Our model shows that cooperation can evolve even in a fully mixed population, where the population is non-structured, there are no repeating interactions and nor individual recognition.
+We studied fully mixed and very large populations with a prisoner's dilemma payoff. 
+We found that under horizontal and vertical cultural transmissions, if \autoref{eq:unequal_transmission} is satisfied, cooperation will take over fully mixed populations (Result 1).
+Under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype is sufficient and necessary for evolution of cooperation (Result 2, \autoref{eq:oblique_only_result}).
+Under a combination of vertical, oblique, and horizontal transmission the dynamics are further complicated.
+Yet, we find that cooperation can evolve and in some cases be maintained together with defection (Result 4).
+Importantly, our results demonstrate that cooperation can evolve even in a fully mixed population (i.e. in an unstructured population), without repeating interactions or individual recognition.
+These results significantly further our understating of the cultural evolution of cooperation.
 
-Recent work by \citet{lewin2017microbes} also sheds some light on this question. 
-They hypothesise that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
+This study was partialy inspired by \citet{lewin2017microbes}. 
+They hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
 Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{dobson1988population,poulin2010parasite}.
@@
 Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
-%\\While the hypothesis that microbes could manipulate their hosts to act altruistically is mathematically feasible~\citep{lewin2017microbes}, there are still no empirical evidence of whether microbes indeed mediate altruistic behavior of their hosts.
 
@@
 the Israel Science Foundation 552/19 (YR),
-and Minerva Center for Lab Evolution (YR).
+and Minerva Stiftung Center for Lab Evolution (YR).
 % TODO funding for other authors?
@@
 % Appendices
-\newpage
-\section*{Appendix A} % TODO fix equations references
-In the section, we start with eq.~\ref{eq:nextgen_parents_vertical_only} and we want to investigate when $\tilde{p}< \tilde{p}'$, that is, when 
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_from_interaction_step0}
+\begin{appendices}
+\renewcommand{\theequation}{\thesection\arabic{equation}}
+\counterwithin*{equation}{section}
+
+\section{} \label{sec:appendixA}
+
+We start with \autoref{eq:nextgen_parents_vertical_only} and we want to investigate when $\tilde{p}< \tilde{p}'$, that is, when 
+\begin{equation} \label{eq:horizontal_transmission_from_interaction_step0}
+\begin{aligned}
 \bar{w}\tilde{p} < & \, \tilde{p}^2 (1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
@@
 & + \tilde{p}(1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A
-\end{split}
+& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A .
+\end{aligned}
 \end{equation}
 First divide by $\tilde{p}$ to obtain
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_from_interaction_step1}
+\begin{equation} \label{eq:horizontal_transmission_from_interaction_step1} 
+\begin{aligned} 
   \bar{w} < & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
@@
   & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-  & + (1-\tilde{p})^2 (1-\alpha) T_A
-\end{split}
+  & + (1-\tilde{p})^2 (1-\alpha) T_A .
+\end{aligned}
 \end{equation}
-We know that the mean fitness $\bar{w} = 1 + \tilde{p}(b-c)$ Tthus eq.~\ref{eq:horizontal_transmission_from_interaction_step1} becomes
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_from_interaction_step2}
+We know that the mean fitness $\bar{w} = 1 + \tilde{p}(b-c)$, thus \autoref{eq:horizontal_transmission_from_interaction_step1} becomes
+\begin{equation} \label{eq:horizontal_transmission_from_interaction_step2} 
+\begin{aligned} 
   1 + \tilde{p}(b-c) < & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
@@
   & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-  & + (1-\tilde{p})^2 (1-\alpha) T_A
-\end{split}
+  & + (1-\tilde{p})^2 (1-\alpha) T_A .
+\end{aligned}
 \end{equation}
-Eq.~\ref{eq:horizontal_transmission_from_interaction_step2} can be simplified to become inequality~\ref{eq:unequal_transmission}.
+which we simplify to inequality~\autoref{eq:unequal_transmission}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{} \label{sec:appendixB}
+We want to find the frequency of juveniles with phenotype $A$ in next generation $\hat{p}'$ as a function of frequency
+of juveniles with phenotype $A$ in the current generation $\hat{p}$.
+We start from eq.~\ref{eq:horizontal},
+\begin{equation}\label{eq:appendix_b_1}
+  \hat{p}' = v \tilde{p}' + (1-v) p'
+  \end{equation}
+Substituting $p'$ using eq.~\ref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ using eq.~\ref{eq:nextgen_parents_simplified}, we have
+\begin{equation}\label{eq:appendix_b_2}
+  \begin{aligned}
+  \hat{p}'  = & \frac{v}{\bar{w}}\left\{\hat{p}^2(1+b-c)\left[1-(1-\hat{p})(1-\alpha)T_B)\right]\right\} \\
+  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1-c)\left[ \hat{p}(1-\alpha)T_B + 1 - T_B \right] \right\} \\
+  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1+b)\left[\hat{p}(1-\alpha) + \alpha \right]T_A \right\} \\
+  & + \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \\
+  & + (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B),
+\end{aligned}
+\end{equation}
+where $\bar{w} = 1 + \hat{p}(b-c)$.
+
+We define $f(\hat{p})$ to be
+\begin{equation} \label{eq:appendix_b_3}
+\begin{aligned}
+      f(\hat{p}) &= \bar{w}(\hat{p}' - \hat{p})
+\end{aligned}
+\end{equation}
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we simplify \autoref{eq:appendix_b_3} to 
+\autoref{eq:general_case_polynomial} and \autoref{eq:polynomial_coefficients}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{} \label{sec:appendixC}
+
+We show that $f'(\hat{p}^*)<0$ is a sufficient condition for local stability an equilibrium $\hat{p}^*$.
+We will write $f(\hat{p})$ as a Taylor approximation around the equilibrium $\hat{p}^*$. 
+\begin{equation} \label{eq:appendix_b_taylor}
+  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f(\hat{p}^*) + f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
+\end{equation}
+Where $R_2(\hat{p})$ is the remainder. Since $\hat{p}^*$ is an equilibrium $f(\hat{p}^*)=0$.
+\begin{equation} \label{eq:appendix_b_taylor0}
+  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) =  f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
+\end{equation}
+Neglecting the remainder(?) and we get: 
+\begin{equation} \label{eq:appendix_b_taylor_without_remainder}
+  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f'(\hat{p}^*)(\hat{p}-\hat{p}^*)
+\end{equation}
+And we get:
+\begin{equation} \label{eq:appendix_b_derivative}
+  \begin{aligned}
+  f'(\hat{p}^*) &= \bar{w}\Big(\frac{\hat{p}'-\hat{p}}{\hat{p}-\hat{p}^*}\Big)\\
+  & = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*+\hat{p}^*-\hat{p}}{\hat{p}-\hat{p}}\Big) 
+  = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) .
+  \end{aligned}
+\end{equation}
+In order for the equilibrium $\hat{p}^*$ to be stable we demand that if $\hat{p} > \hat{p}^*$ then $\hat{p}'-\hat{p}^* < \hat{p}-\hat{p}^*$
+and if $\hat{p} < \hat{p}^*$ we demand that $-(\hat{p}'-\hat{p}^*) < -(\hat{p}-\hat{p}^*)$. 
+In other words, $\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}<1$ for every $\hat{p}$.
+Therefore,
+\begin{equation} \label{eq:appendix_b_condition}
+  \begin{aligned}
+  f'(\hat{p}^*) = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) < 0 .
+  \end{aligned}
+\end{equation}
+Therefore, $f'(\hat{p}^*)$ is a sufficient condition for stability of $\hat{p}^*$.
+
+\end{appendices}
 

### 2020-07-27 ms/main.tex
hints for discussion
eshel1982

@@
 
-This study was partialy inspired by \citet{lewin2017microbes}. 
+This study was partially inspired by \citet{lewin2017microbes}. 
 They hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
@@
 Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
+
+\citet{Eshel1982} have studied a relevant model for the evolution of cooperative behavior under vertical transmission.
+Their model included \emph{assortative meeting}, or non-random encounters.
+This assortment may be due, for example, to population structure or active partner choice.
+In this model, cooperative behavior can evolve if \citep[eq.~3.2]{Eshel1982}
+\begin{equation} \label{eq:assortative_meeting}
+c < b \cdot m,
+\end{equation}
+where $b$ and $c$ are the benefit and cost of cooperation, and $m$ is the fraction of the population that meets an individual of the same phenotype rather than a random individual\footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the righthand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
+}. 
+As a version of Hamilton's rule, $m$ can be interpreted as the effective relatedness.
+In our Corollary 1.1 (\autoref{eq:equal_transmission}), cooperation evolves if $c < b \cdot \alpha T / (1-T)$.
+So in our model $\alpha T/(1-T)$ is the effective relatedness, which is affected by $\alpha$, the correlation between transmission and interaction, and $T$, the horizontal transmission rate.
+
+% Javarone MA, Atzeni AE, Galam S. Emergence of Cooperation in the Prisoner ’ s Dilemma Driven by Conformity. 2:155-163. doi:10.1007/978-3-319-16549-3
+% Woodcock S. The significance of non-vertical transmission of phenotype for the evolution of altruism. Biol Philos. 2006;21:213-234. doi:10.1007/s10539-005-8241-1
 

### 2020-07-28 ms/main.tex
Improve equilibrium stability proof

@@
 We will write $f(\hat{p})$ as a Taylor approximation around the equilibrium $\hat{p}^*$. 
-\begin{equation} \label{eq:appendix_b_taylor}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f(\hat{p}^*) + f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
+\begin{equation} \label{eq:appendix_c_taylor}
+  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f(\hat{p}^*) + f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + O((\hat{p}-\hat{p}^*)^2)
 \end{equation}
-Where $R_2(\hat{p})$ is the remainder. Since $\hat{p}^*$ is an equilibrium $f(\hat{p}^*)=0$.
-\begin{equation} \label{eq:appendix_b_taylor0}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) =  f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
+Where $O((\hat{p}-\hat{p}^*)^2)$ is big O notation. Denote, $\epsilon = \hat{p}-\hat{p}^*$ and $\epsilon'=\hat{p}'-\hat{p}$.
+\begin{equation} \label{eq:appendix_c_taylor0}
+  f(\hat{p}) = \bar{w}\epsilon' = f(\hat{p}^*) + f'(\hat{p}^*)\epsilon + O(\epsilon^2)
 \end{equation}
-Neglecting the remainder(?) and we get: 
-\begin{equation} \label{eq:appendix_b_taylor_without_remainder}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f'(\hat{p}^*)(\hat{p}-\hat{p}^*)
+Since $\hat{p}^*$ is an equilibrium $f(\hat{p}^*)=0$ we get
+\begin{equation} \label{eq:appendix_c_taylor0}
+  f(\hat{p}) = \bar{w}\epsilon' = f'(\hat{p}^*)\epsilon + O(\epsilon^2)
 \end{equation}
-And we get:
-\begin{equation} \label{eq:appendix_b_derivative}
+By definition of big-O, if $f’(\hat{p}*)$ is negative, then there exists some $\epsilon$ (i.e. some neighbourhood of $\hat{p}^*$) for which $f’(\hat{p}^*) + O(\epsilon)$ is also negative.
+Therefore,
+\begin{equation} \label{eq:appendix_c_taylor_is_negative}
+  \bar{w}\epsilon' = f'(\hat{p}^*)\epsilon + O(\epsilon^2) < 0
+\end{equation}
+In addition, we know that $f(\hat{p}^*)=0$ therefore, there exist some $\epsilon$ for which $f(\hat{p}) > - \delta$ for some $\delta > 0$. 
+We choose delta to be $\delta = \frac{1}{\bar{w}}$, therefore  $f(\hat{p})=\bar{w}\epsilon'>-\frac{1}{\bar{w}}$. Therefore,
+\begin{equation} \label{eq:appendix_c_taylor_is_negative_and_bound_by_minus1}
+  -\frac{1}{\bar{w}} <\bar{w}\epsilon' = f'(\hat{p}^*)\epsilon + O(\epsilon^2) < 0
+\end{equation}
+
+Let's start simplify
+\begin{equation} \label{eq:appendix_c_taylor_is_negative}
+  -\frac{1}{\bar{w}} < \bar{w}\frac{\epsilon'}{\epsilon} < 0
+\end{equation}
+Since $\bar{w}>0$ we get that
+\begin{equation} \label{eq:appendix_c_condition_for_positive_epsilon}
   \begin{aligned}
-  f'(\hat{p}^*) &= \bar{w}\Big(\frac{\hat{p}'-\hat{p}}{\hat{p}-\hat{p}^*}\Big)\\
-  & = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*+\hat{p}^*-\hat{p}}{\hat{p}-\hat{p}}\Big) 
-  = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) .
+  -1 < \frac{\epsilon'}{\epsilon} & = \frac{\hat{p}'-\hat{p}}{\hat{p}-\hat{p}^*} = \frac{\hat{p}'-\hat{p}^*+\hat{p}^*-\hat{p}}{\hat{p}-\hat{p}^*} \\
+  & \frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*} - 1< 0
   \end{aligned}
 \end{equation}
-In order for the equilibrium $\hat{p}^*$ to be stable we demand that if $\hat{p} > \hat{p}^*$ then $\hat{p}'-\hat{p}^* < \hat{p}-\hat{p}^*$
-and if $\hat{p} < \hat{p}^*$ we demand that $-(\hat{p}'-\hat{p}^*) < -(\hat{p}-\hat{p}^*)$. 
-In other words, $\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}<1$ for every $\hat{p}$.
-Therefore,
-\begin{equation} \label{eq:appendix_b_condition}
+From eq.~\ref{eq:appendix_c_condition_for_positive_epsilon} we get that
+\begin{equation} \label{eq:appendix_c_final_condition_for_positive_epsilon}
   \begin{aligned}
-  f'(\hat{p}^*) = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) < 0 .
+    -1 < \frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*} < 1
   \end{aligned}
 \end{equation}
-Therefore, $f'(\hat{p}^*)$ is a sufficient condition for stability of $\hat{p}^*$.
+We can apply absoulte value
+\begin{equation} \label{eq:appendix_c_final_condition_for_positive_epsilon}
+  \begin{aligned}
+    |\hat{p}'-\hat{p}^*| < |\hat{p}-\hat{p}^*|
+  \end{aligned}
+\end{equation}
+
+Therefore, if $f'(\hat{p}^*)<0$ there exist some neighbourhood of $\hat{p}^*$ where $\hat{p}'$ is closer to $\hat{p}$, which means that $f'(\hat{p}^*)<0$ is sufficient condition for stability of $\hat{p}^*$.
+
+Now let's assume by contradiction that $\hat{p}^*$ is also locally stable when $f'(\hat{p}^*) > 0$.
+When $f'(\hat{p}^*) > 0$ there exist some neighbourhood $\epsilon$ in which $f'(\hat{p})>0$ for every $\hat{p}$ in the neighbourhood.
+
+If $\hat{p} > \hat{p}^*$ we get:
+\begin{equation} \label{eq:appendix_c_1}
+  \begin{aligned}
+    f(\hat{p}) = w\epsilon' > f(\hat{p}^*) = 0
+  \end{aligned}
+\end{equation}
+From eq.~\ref{eq:appendix_c_1} we can see that $\hat{p}' > \hat{p} > \hat{p}^*$ and therefore, $\hat{p}^*$ is not stable.
+
+If $\hat{p}<\hat{p}^*$ we get:
+\begin{equation} \label{eq:appendix_c_2}
+  \begin{aligned}
+    f(\hat{p}) = w\epsilon' < f(\hat{p}^*) = 0
+  \end{aligned}
+\end{equation}
+From eq.~\ref{eq:appendix_c_1} we can see that $\hat{p}' < \hat{p} < \hat{p}^*$ and therefore, $\hat{p}^*$ is not stable.
+%TODO: Add show for f'(p)=0
+
+We saw that if $f'(\hat{p}^*)<0$ then $\hat{p}^*$ is stable, and if $f'(\hat{p}^*)>0$ then $\hat{p}^*$ is unstable.
+Therefore, $f'(\hat{p}^*)$ is sufficient and necessary condition for equilibrium stability.
 

### 2020-07-28 ms/main.tex
merge from master
compete revision of result1-2 and appendix A; revised intro

--- 2020-07-27 ms/main.tex
@@
 % Title page
-\title{Cultural Transmission Can Explain the Evolution of Cooperative Behavior}
+\title{Cultural Transmission Can Explain the Evolution of Cooperation}
 
@@
 
-\affil[1]{School of Computer Science, Inetdisciplinary Center Herzliya, Herzliya, Israel}
+\affil[1]{School of Computer Science, Interdisciplinary Center Herzliya, Herzliya, Israel}
 \affil[2]{School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv, Israel}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% Introduction
@@
 Evolution of cooperative behavior remains an important conundrum in evolutionary biology.
-Three major theories have been proposed to explain the evolution of cooperative behavior:
 
-1.
 \emph{Kin selection} theory posits that natural selection can favor cooperation between related individuals.
 The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}.
-According to Hamilton,  an allele that determines altruistic behavior should increase in frequency when  the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the genetic relatedness between the recipient and the actor, $r$.
-This is also known as Hamilton's Rule:
+According to Hamilton, for an allele that determines cooperative behavior to increase in frequency, the reproductive cost to the actor that cooperates, $c$, must be less than the benefit to the recipient, $b$, times the `relatedness' between the recipient and the actor, $r$.
+This `relatedness' coefficient $r$ measures the correlation between the gene in the actor and the gene in the recipient.
+This condition is also known as Hamilton's rule:
 \begin{equation} \label{eq:hamilton_rule}
@@
 
-There is an ongoing debate about the extent to which kin selection explains the evolution of cooperation and altruism.
-For example, it has been suggested that it can explain the cooperative behavior of worker castes of eusocial insects like the honey bee. % TODO REF
-The most significant argument against kin selection is that in some cases cooperation among unrelated individuals appears to have evolved~\citep{wilson2005kin}.
-According to \citet{wilson2005kin}, this makes Hamilton's rule incomplete, although \citet{foster2006kin} reject this claim and argue that altruism cannot evolve without relatedness.
-They refer  to Hamilton, who claimed that relatedness can arise without recent common ancestry.
-%MWF: How?
-\citet{wilson2005kin} also criticizes kin selection on the grounds that environmental or ecological factors are probably more important than relatedness in determining social actions.
-However, \citet{foster2006kin} argue that kin selection does not ignore ecology, and Hamilton's rule suggests that environmental factors causing a high benefit-to-cost ratio will favor cooperation.
-
-2.
-\emph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
-In \emph{direct reciprocity} there are repeated encounters between the same two individuals, and at every encounter each individual has a choice between cooperation and defection.
-Hence, it may eventually pay off to cooperate if it may cause your partner to cooperate in the future.
-This game-theoretic framework, known as the \emph{repeated prisoner's dilemma}, 
-%A well known strategy to play this game is called  'tit-for-tat'.
-This strategy always starts with a cooperation, then it does whatever the other player has done in the previous round: a cooperation for a cooperation, a defection for a defection.
-There a unlimited number of possible strategies to play this game.
-However,
-can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability of another encounter between the same two individuals, $w$, 
-%TODO Referencess
-\begin{equation} \label{eq:reciprocity}
-c < b \cdot w.
+\citet{Eshel1982} have studied a relevant model for the evolution of cooperative behavior under vertical transmission.
+Their model included \emph{assortative meeting}, or non-random encounters.
+That is, if a fraction $m$ of the population interacts with an individual of the same phenotype, and $1-m$ interacts randomly.
+Such assortative meeting may be due, for example, to population structure or active partner choice.
+In their model, cooperative behavior can evolve if \footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the righthand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
+}. 
+\citep[eq.~3.2]{Eshel1982}
+\begin{equation} \label{eq:assortative_meeting}
+c < b \cdot m,
 \end{equation}
-
-Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy. \\
-\emph{Indirect reciprocity} has also been suggested to explain the evolution of cooperation.
-\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of currency. 
-%TODO: refs
-The currency that ``fuels the engines'' of indirect reciprocity is \emph{reputation}. 
-However, reciprocity assumes repeated interactions and therefore has difficulty in explaining the evolution of cooperation if  interactions are not repeated.
-
-3.
-\emph{Group selection} theory posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
-A common model for group selection divides the population into groups in which there are cooperators that help  other group members and defectors that do not.
-% TODO add reference
-Individuals reproduce proportionally to their fitness, and offspring are added to the same group as their parents.
-If a group reaches a certain size it can split to two groups, so groups that grow faster will split more often.
-Groups with cooperators grow faster than groups without cooperators, and
-cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
-\begin{equation} \label{eq:groupselection}
-c < b \cdot \frac{m}{m+n} .
-\end{equation}
-
-Group selection has been criticized by biologists who advocate a gene-centered view of evolution. % TODO ref
-It has also been criticized because for cooperation to take over the population it must have higher fitness than defection, while under group selection theory the fitness of cooperators at the individual level is lower than the fitness of defectors.
-Thus a trait with a lower fitness taking over the population is a contradiction %TODO ref.
-\citet{eldakar2011eight} reject this argument, claiming that it is a tautology and does not qualify as an argument against group selection.
-The distinction between individual and group selection requires a comparison of fitness differentials within and between groups in a multi-group population, and when a trait  evolves by group selection, despite having lower fitness within a group, that group might have higher average fitness in competition with other groups, all things considered.
-% TODO cite Simpsons' paradox?
+where $b$ and $c$ are the benefit and cost of cooperation
+Here, $m$ takes the role of the relatedness $r$.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Models
@@
 
-Horizontal cultural transmission occurs between peers. 
-It may occur between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{\autoref{fig:horizontal}}).
-Horizontal transmission is not always successful, as one peer may reject the other's phenotype.
+Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
+It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{\autoref{fig:horizontal}}).
+The assortment parameter $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
+Horizontal transmission is not always successful, as one partner may reject the other's phenotype.
 The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\textbf{\autoref{table:interactions}}).
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% Results
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Oblique and Horizontal Transmission}
+
+With only oblique and horizontal transmission, i.e.
+$v = 0$, \autoref{eq:horizontal} becomes $\hat{p}=p$ and \autoref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
+\begin{equation}  \label{eq:nextgen_parents_oblique_only}
+p' = p^2 (T_B-T_A) + p (1+T_A-T_B) ,
+\end{equation}
+
+which gives the following result.
+
+\begin{result}[Oblique and horizontal transmission of cooperation]
+If there is a horizontal transmission bias in favor of cooperation, namely
+\begin{equation} \label{eq:oblique_only_result}
+T_A > T_B, 
+\end{equation}
+then $p'>p$, and the frequency of the cooperator phenotype among adults increases every generation.
+Therefore, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~\textbf{\autoref{fig:results_c}}).
+\end{result}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Without Oblique Transmission}
+\subsection*{Vertical and Horizontal Transmission}
 
@@
 $\hat{p} =  \tilde{p}$,
-and \autoref{eq:nextgen_parents_simplified} for the change in frequency $p'$ of phenotype $A$ among parents can be written as
+and \autoref{eq:nextgen_parents_simplified} for the frequency of the cooperative phenotype among parents in the next generation $\tilde{p}'$ can be written as
 \begin{equation} \label{eq:nextgen_parents_vertical_only} 
@@
 
-We find the following result and corollaries.
+The fixation of either cooperation or defection, 
+$\tilde{p}=0$ and $ \tilde{p}=1$, are equilibria of \autoref{eq:nextgen_parents_vertical_only}, that is, they solve $\tilde{p}'= \tilde{p}$.
+We therefore assume for the remainder of the analysis that $0<\tilde{p}<1$.
 
-\textbf{Result 1: Vertical and horizontal transmission of cooperation.}
-From \autoref{eq:nextgen_parents_vertical_only}, if
-\begin{equation} \label{eq:unequal_transmission}
-c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b\tilde{p}(1-\alpha)] ,
+If $\alpha=1$, then $\tilde{p}'= \tilde{p}$ is reduced to
+\begin{equation}
+p(1-p)\big[(1+b)T_A + (1-c)(1-T_B)-1\big] = 0,
 \end{equation}
-then $\tilde{p}' > \tilde{p}$, and the frequency of the cooperator phenotype $A$ among parents increases every generation.
+and there are no additional equilibria.
 
-\textbf{Corollary 1.1: Symmetric horizontal transmission.}
-If $T=T_A=T_B$, then
+Therefore, for cooperation to take over the population ($\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$, that is,
+\begin{equation}
+  \tilde{p}^2 (1+b-c) + \tilde{p}(1-\tilde{p}) \big[(1-c) (1 - T_B) + (1+b)T_A\big] 
+  > \bar{w}\tilde{p} .
+\end{equation}
+We divide by $\tilde{p}$, set $\bar{w} = 1 + \tilde{p}(b-c)$, and rearrange to get
+\begin{equation}
+  (1-\tilde{p}) \big[(1-c) (1 - T_B) + (1+b)T_A\big] 
+  > 1 -\tilde{p} .
+\end{equation}
+Dividing by $(1-\tilde{p})$ we find that $\tilde{p}'>\tilde{p}$ if 
+\begin{equation} \label{eq:vert_hori_alpha1_global_condition}
+  (1-c) (1 - T_B) + (1+b)T_A
+  > 1 .
+\end{equation}
+
+If $\alpha<1$, we want to determine a condition for $\tilde{p}'>\tilde{p}$ in \autoref{eq:nextgen_parents_vertical_only}. 
+We divide  by $\tilde{p}$ and set $\bar{w} = 1 + \tilde{p}(b-c)$ to get
+\begin{equation}
+\begin{aligned} 
+  1 + \tilde{p}(b-c) < 
+  & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
+  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
+  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+  & + (1-\tilde{p})^2 (1-\alpha) T_A .
+\end{aligned}
+\end{equation}
+Rearranging, we get
+\begin{equation} 
+\begin{aligned} 
+  1 - \tilde{p} < 
+  & - \tilde{p}(1+b-c)(1-\tilde{p}) (1-\alpha) T_B \\
+  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
+  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+  & + (1-\tilde{p})^2 (1-\alpha) T_A .
+\end{aligned}
+\end{equation}
+We divide by $(1-\tilde{p})$ and rearrange so that free terms are on the left and terms with $\tilde{p}$ are on the right. We get
+\begin{equation} 
+\begin{aligned} 
+  &1 - (1-\alpha) T_A - (1+b) \alpha T_A - (1 - T_B)(1-c)  < \\
+   &\tilde{p}[ - (1+b-c) (1-\alpha) T_B 
+   + (1-c) (1-\alpha) T_B
+   + (1+b) (1-\alpha) T_A 
+   - (1-\alpha) T_A].
+\end{aligned}
+\end{equation}
+Simplifying, we find that $\tilde{p}'>\tilde{p}$ if and only if
+\begin{equation} \label{eq:vert_hori_global_condition}
+c(1-T_B) - b \alpha T_A - (T_A-T_B) < \tilde{p} \cdot b (1-\alpha) (T_A-T_B).
+\end{equation}
+
+Therefore, in this case there can be a third, polymorphic equilibrium, if $0<\tilde{p}^*<1$, where
+\begin{equation} \label{eq:vert_hori_equilibrium}
+  \tilde{p}^* = 
+  \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B) }.
+\end{equation}
+
+Note that all parameters are positive.
+So, applying \autoref{eq:vert_hori_global_condition}, for $\tilde{p}'>\tilde{p}$,  we require that either 
+\begin{equation} \label{eq:vert_hori_global_condition1}
+T_A>T_B, \;\text{and}\; \tilde{p}>\tilde{p}^*,
+\end{equation} or 
+\begin{equation} \label{eq:vert_hori_global_condition2}
+T_A<T_B, \;\text{and}\; \tilde{p}<\tilde{p}^* .
+\end{equation}
+
+We therefore have the following result and corollaries.\\
+
+\begin{result}[Vertical and horizontal transmission of cooperation]
+When $0 \le \alpha<1$ and $v=1$, fixation, extinction, and stable coexistence of both cooperation and defection are possible.
+\end{result}
+
+Determining the outcome of the dynamics depends on the sign of $T_A-T_B$ and on the legitimacy of the third equilibrium, that is, if $0<\tilde{p}^*<1$.
+\\
+
+%This condition can also be formulated as a condition on the cost of cooperation $c$: cooperation will take over the population if
+%\begin{equation} \label{eq:unequal_transmission}
+%c < \frac{
+%	b \big[\alpha T_A + (1-\alpha)\tilde{p}(T_A - T_B)\big] + (T_A - T_B)
+%	}{
+%	1-T_B
+%	}.
+%\end{equation}
+%
+%Importantly, the condition for cooperation to increase from rarity is (set $\tilde{p}=0$ in \autoref{eq:unequal_transmission})
+%\begin{equation} \label{eq:unequal_transmission_from_rarity}
+%c < \frac{
+%	b \alpha T_A + (T_A - T_B)
+%	}{
+%	1-T_B
+%	} .
+%\end{equation} 
+%
+%In general, these conditions cannot be formulated in the form of Hamilton's rule ($c<b\cdot r$) due to the horizontal transmission bias $T_A-T_B$.
+%Without horizontal transmission bias, we get the following corollary that does have the form of Hamilton's rule.
+
+\begin{corollary}[Symmetric horizontal transmission]
+If $T=T_A=T_B$, then cooperation will take over the population if
 \begin{equation}
 \label{eq:equal_transmission}
-c < b \cdot \frac{\alpha T}{1-T},
+c < b \cdot \frac{\alpha T}{1-T}.
 \end{equation}
-which can be seen as a cultural version of \emph{Hamilton's rule} (\autoref{eq:hamilton_rule}), where $r_H=\alpha T/(1-T)$ can be thought of as \emph{horizontal relatedness}.
-Therefore, if the cost $c$ is less than the benefit $b$ times the horizontal relatedness $r_H$, then cooperation will take over of the population (see~\textbf{\autoref{fig:results_a}}).
+\end{corollary}
+To verify, set $T_A=T_B$ in \autoref{eq:vert_hori_global_condition}.
 
-\textbf{Corollary 1.2: Complete correlation between transmission and cooperation.}
+This can be interpreted as a version of Hamilton's rule (\autoref{eq:hamilton_rule}), where $\alpha T/(1-T)$ is the `effective relatedness'.
+\autoref{fig:results_a} demonstrates this condition. 
+\\
 
-In this case $\alpha=1$, and horizontal transmission can only occur as a result of cooperative interactions.
-Therefore, \autoref{eq:unequal_transmission}, which determines the conditions for evolution of cooperation, becomes
-\begin{equation}\label{eq:horizontal_transmission_only_after_interaction}
-c \cdot (1-T_B) < b \cdot T_A + (T_A - T_B).
+\begin{corollary}[No assortment of transmission and cooperation]
+If $\alpha=0$, then the third equilibrium is
+\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
+\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) }.
+\end{equation} 
+If there is a horizontal transmission bias for cooperation, $T_A>T_B$, then cooperation will fix in the population if the cost is not too high $c < (1+b) \frac{T_A-T_B}{1-T_B}$, and the initial frequency is high enough, $\tilde{p}(0) > \tilde{p}^*$.
+If there is a horizontal transmission bias for defection, $T_A<T_B$, defection will take over the population.
+\end{corollary}
+
+This can be shown by setting $\alpha=0$ in \autoref{eq:vert_hori_equilibrium}. 
+Then, when $T_A>T_B$ we find a condition for $\tilde{p}^*<1$ and $\tilde{p}>\tilde{p}^*$ (\autoref{eq:vert_hori_global_condition1}).
+When $T_A<T_B$, we have $\tilde{p}^*<0$ and because of \autoref{eq:vert_hori_global_condition2}, any initial frequency leads to fixation of defection, $\tilde{p}=0$.\\
+
+\begin{corollary}[Complete assortment of transmission and cooperation]
+\end{corollary}
+In this case $\alpha=1$, and horizontal transmission always occurs together with the cooperative interaction; there is complete assortment.
+In this case there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
+The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found by setting $\tilde{p}'>\tilde{p}$, which gives (\autoref{eq:vert_hori_alpha1})
+\begin{equation}\label{eq:vert_hori_alpha1}
+c < \frac{b \cdot T_A + (T_A - T_B)}{1-T_B}.
 \end{equation}
@@
 
-\autoref{eq:horizontal_transmission_only_after_interaction} can be written as
-\begin{equation} \label{eq:horizontal_transmission_only_after_interaction2}
-1 - (1-T_B)(1-c) < T_A \cdot (1+b) ,
+\autoref{eq:vert_hori_alpha1} can be written as
+\begin{equation} \label{eq:vert_hori_alpha1_effective}
+1 - (1-c)(1-T_B) < (1+b) T_A ,
 \end{equation}
@@
 Consider an interaction between two individuals: a cooperator and a defector.
-$(1-T_B)(1-c)$ is the probability that the cooperator remains cooperative and also reproduces. 
-Therefore, $1 - (1-T_B)(1-c)$ is the probability that either the cooperator becomes a defector, \emph{or} that it fails to reproduce.
+$(1-c)(1-T_B)$ is the probability that the cooperator remains cooperative and also reproduces. 
+Therefore, $1 - (1-c)(1-T_B)$ is the probability that either the cooperator becomes a defector, \emph{or} that it fails to reproduce.
 This is the effective cost for cooperation from this interaction.
-$T_A\cdot(1+b)$ is the probability that the defector becomes cooperative and reproduces.
+$(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces.
 This is the effective benefit for cooperation from this interaction.
-So, \autoref{eq:horizontal_transmission_only_after_interaction2} means that cooperation can evolve if the effective cost is less than the effective benefit.
-
-\textbf{Corollary 1.3: No correlation between transmission and cooperation.}
-
-In this case $\alpha=0$, and horizontal transmission is entirely independent from cooperative interactions.  
-Then, \autoref{eq:unequal_transmission} becomes
-\begin{equation} \label{eq:horizontal_transmission_from_population}
-c\cdot(1-T_B) < b \cdot \tilde{p} \;(T_A-T_B) + (T_A-T_B). 
-\end{equation}
-
-Therefore, since all the parameters are  positive, cooperation cannot take over the population (and furthermore will become extinct) if cooperators do not have a horizontal transmission bias, i.e.
-if $T_A\leq T_B$.
-When such a bias does exist, $T_A > T_B$, then cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$, where (see also ~\textbf{\autoref{fig:results_b}})
-\begin{equation} 
-\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
-\tilde{p}^{*} & = \frac{c}{b} \cdot \frac{1-T_B}{T_A-T_B} - \frac{1}{b}.
-\end{split}
-\end{equation}
-A sufficient condition for evolution of cooperation is that $\tilde{p}^{*} < 0$, namely
-\begin{equation} \label{eq:sufficient_horizontal_transmission_from_population}
-c < \frac{T_A-T_B}{1-T_B} .  
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Without Vertical Transmission}
-
-With only oblique and horizontal transmission, i.e.
-$v = 0$, \autoref{eq:horizontal} becomes $\hat{p}=p$ and \autoref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
-\begin{equation}  \label{eq:nextgen_parents_oblique_only}
-p' = p^2 (T_B-T_A) + p (1+T_A-T_B) ,
-\end{equation}
-
-which gives the following result.
-
-\textbf{Result 2: Oblique and horizontal transmission of cooperation.} 
-If there is a horizontal transmission bias in favor of cooperation, namely
-\begin{equation} \label{eq:oblique_only_result}
-T_A > T_B, 
-\end{equation}
-then $p'>p$, and the frequency of the cooperator phenotype among adults increases every generation.
-Therefore, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~\textbf{\autoref{fig:results_c}}).
+So, \autoref{eq:vert_hori_alpha1} means that cooperation can evolve if the effective cost for cooperation is less than the effective benefit.
 
@@
 
-\textbf{Result 3: Oblique and vertical transmission of cooperation.}
+\begin{result}[Vertical, oblique, and horizontal transmission of cooperation]
 The cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the horizontal transmission bias $T_A-T_B$ and the coefficients $\beta_1$ and $\beta_3$:
@@
 \end{enumerate}
+\end{result}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Discussion
@@
 
-\citet{Eshel1982} have studied a relevant model for the evolution of cooperative behavior under vertical transmission.
-Their model included \emph{assortative meeting}, or non-random encounters.
-This assortment may be due, for example, to population structure or active partner choice.
-In this model, cooperative behavior can evolve if \citep[eq.~3.2]{Eshel1982}
-\begin{equation} \label{eq:assortative_meeting}
-c < b \cdot m,
+There is an ongoing debate about the extent to which kin selection explains the evolution of cooperation and altruism.
+For example, it has been suggested that it can explain the cooperative behavior of worker castes of eusocial insects like the honey bee. % TODO REF
+The most significant argument against kin selection is that in some cases cooperation among unrelated individuals appears to have evolved~\citep{wilson2005kin}.
+Therefore, other theories have been develop to explain the evolution of cooperation and altruism.
+
+\emph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
+In \emph{direct reciprocity} there are repeated encounters between the same two individuals, and at every encounter each individual has a choice between cooperation and defection.
+Hence, it may eventually pay off to cooperate if it may cause your partner to cooperate in the future.
+This game-theoretic framework, known as the \emph{repeated prisoner's dilemma}, 
+%A well known strategy to play this game is called  'tit-for-tat'.
+This strategy always starts with a cooperation, then it does whatever the other player has done in the previous round: a cooperation for a cooperation, a defection for a defection.
+There a unlimited number of possible strategies to play this game.
+However,
+can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability of another encounter between the same two individuals, $w$, 
+%TODO Referencess
+\begin{equation} \label{eq:reciprocity}
+c < b \cdot w.
 \end{equation}
-where $b$ and $c$ are the benefit and cost of cooperation, and $m$ is the fraction of the population that meets an individual of the same phenotype rather than a random individual\footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the righthand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
-}. 
-As a version of Hamilton's rule, $m$ can be interpreted as the effective relatedness.
-In our Corollary 1.1 (\autoref{eq:equal_transmission}), cooperation evolves if $c < b \cdot \alpha T / (1-T)$.
+
+Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy. \\
+\emph{Indirect reciprocity} has also been suggested to explain the evolution of cooperation.
+\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of currency. 
+%TODO: refs
+The currency that ``fuels the engines'' of indirect reciprocity is \emph{reputation}. 
+However, reciprocity assumes repeated interactions and therefore has difficulty in explaining the evolution of cooperation if  interactions are not repeated.
+
+\emph{Group selection} theory posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
+A common model for group selection divides the population into groups in which there are cooperators that help  other group members and defectors that do not.
+% TODO add reference
+Individuals reproduce proportionally to their fitness, and offspring are added to the same group as their parents.
+If a group reaches a certain size it can split to two groups, so groups that grow faster will split more often.
+Groups with cooperators grow faster than groups without cooperators, and
+cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
+\begin{equation} \label{eq:groupselection}
+c < b \cdot \frac{m}{m+n} .
+\end{equation}
+
+Group selection has been criticized by biologists who advocate a gene-centered view of evolution. % TODO ref
+It has also been criticized because for cooperation to take over the population it must have higher fitness than defection, while under group selection theory the fitness of cooperators at the individual level is lower than the fitness of defectors.
+Thus a trait with a lower fitness taking over the population is a contradiction %TODO ref.
+\citet{eldakar2011eight} reject this argument, claiming that it is a tautology and does not qualify as an argument against group selection.
+The distinction between individual and group selection requires a comparison of fitness differentials within and between groups in a multi-group population, and when a trait  evolves by group selection, despite having lower fitness within a group, that group might have higher average fitness in competition with other groups, all things considered.
+% TODO cite Simpsons' paradox?
+
+\citet{Eshel1982} have shown that with assortative meeting, i.e. probability $m$ that individuals interact with within their phenotypic group, cooperation can evolve if $m > c/b$.
+In our Corollary 1.1 (\autoref{eq:equal_transmission}), cooperation evolves if $\alpha T / (1-T) > c/b$.
 So in our model $\alpha T/(1-T)$ is the effective relatedness, which is affected by $\alpha$, the correlation between transmission and interaction, and $T$, the horizontal transmission rate.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \pagebreak
@@
 
-% Bibliography
-\bibliographystyle{plainnat}
-\bibliography{bib}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Appendices
@@
 \counterwithin*{equation}{section}
-
-\section{} \label{sec:appendixA}
-
-We start with \autoref{eq:nextgen_parents_vertical_only} and we want to investigate when $\tilde{p}< \tilde{p}'$, that is, when 
-\begin{equation} \label{eq:horizontal_transmission_from_interaction_step0}
-\begin{aligned}
-\bar{w}\tilde{p} < & \, \tilde{p}^2 (1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
-& + \tilde{p}(1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
-& + \tilde{p}(1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A .
-\end{aligned}
-\end{equation}
-First divide by $\tilde{p}$ to obtain
-\begin{equation} \label{eq:horizontal_transmission_from_interaction_step1} 
-\begin{aligned} 
-  \bar{w} < & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
-  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
-  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-  & + (1-\tilde{p})^2 (1-\alpha) T_A .
-\end{aligned}
-\end{equation}
-We know that the mean fitness $\bar{w} = 1 + \tilde{p}(b-c)$, thus \autoref{eq:horizontal_transmission_from_interaction_step1} becomes
-\begin{equation} \label{eq:horizontal_transmission_from_interaction_step2} 
-\begin{aligned} 
-  1 + \tilde{p}(b-c) < & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
-  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
-  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-  & + (1-\tilde{p})^2 (1-\alpha) T_A .
-\end{aligned}
-\end{equation}
-which we simplify to inequality~\autoref{eq:unequal_transmission}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Bibliography
+\bibliographystyle{plainnat}
+\bibliography{bib}
+
 \end{document}

### 2020-07-28 ms/main.tex
minor fix
continued revision of result 2

@@
 %%% Figure: model illustration
-\begin{figure}[b]
+\begin{figure}[thb]
   \centering
@@
 
-which gives the following result.
+which gives the following result.\\
 
 \begin{result}[Oblique and horizontal transmission of cooperation]
-If there is a horizontal transmission bias in favor of cooperation, namely
+Without vertical transmission ($v=0$), if there is a horizontal transmission bias in favor of cooperation, namely
 \begin{equation} \label{eq:oblique_only_result}
@@
 then $p'>p$, and the frequency of the cooperator phenotype among adults increases every generation.
-Therefore, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~\textbf{\autoref{fig:results_c}}).
 \end{result}
+
+Therefore, in the absence of vertical transmission, selection plays no role in the evolution of cooperation.
+Hence, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~{\autoref{fig:results_c}).
 
@@
 \begin{equation}
-p(1-p)\big[(1+b)T_A + (1-c)(1-T_B)-1\big] = 0,
+\tilde{p}(1-\tilde{p})\big[(1+b)T_A + (1-c)(1-T_B)-1\big] = 0,
 \end{equation}
@@
 
-Therefore, for cooperation to take over the population ($\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$, that is,
+Therefore, for cooperation to take over the population (for $\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$, that is,
 \begin{equation}
@@
   (1-c) (1 - T_B) + (1+b)T_A
-  > 1 .
+  > 1 \Leftrightarrow
+  c < \frac{bT_A + (T_A- T_B)}{1-T_B}.
 \end{equation}
+\\
 
-If $\alpha<1$, we want to determine a condition for $\tilde{p}'>\tilde{p}$ in \autoref{eq:nextgen_parents_vertical_only}. 
-We divide  by $\tilde{p}$ and set $\bar{w} = 1 + \tilde{p}(b-c)$ to get
+If $\alpha<1$, we want to determine a condition for $\tilde{p}'>\tilde{p}$. 
+We divide \autoref{eq:nextgen_parents_vertical_only} by $\tilde{p}$ and set $\bar{w} = 1 + \tilde{p}(b-c)$ to get
 \begin{equation}
@@
 \end{equation}
-We divide by $(1-\tilde{p})$ and rearrange so that free terms are on the left and terms with $\tilde{p}$ are on the right. We get
+Diving by $(1-\tilde{p})$ and rearranging so that free terms are on the left and terms with $\tilde{p}$ are on the right, we have
 \begin{equation} 
@@
 
-Therefore, in this case there can be a third, polymorphic equilibrium, if $0<\tilde{p}^*<1$, where
+Following the same steps to solve $\tilde{p}'=\tilde{p}$, we find that there can be a third, polymorphic equilibrium 
 \begin{equation} \label{eq:vert_hori_equilibrium}
   \tilde{p}^* = 
-  \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B) }.
+  \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B)} .
 \end{equation} 
+Note that this is a legitimate equilibrium only if $0<\tilde{p}^*<1$.
 
 Note that all parameters are positive.
-So, applying \autoref{eq:vert_hori_global_condition}, for $\tilde{p}'>\tilde{p}$,  we require that either 
-\begin{equation} \label{eq:vert_hori_global_condition1}
-T_A>T_B, \;\text{and}\; \tilde{p}>\tilde{p}^*,
-\end{equation} or 
-\begin{equation} \label{eq:vert_hori_global_condition2}
-T_A<T_B, \;\text{and}\; \tilde{p}<\tilde{p}^* .
-\end{equation}
+So, applying \autoref{eq:vert_hori_global_condition}, for $\tilde{p}'>\tilde{p}$ we require that either 
+\begin{align} 
+\label{eq:vert_hori_global_condition1}
+T_A > T_B \quad&\text{and}\quad \tilde{p}>\tilde{p}^*,  \quad \text{or} \\
+\label{eq:vert_hori_global_condition2}
+T_A <T_B \quad&\text{and}\quad \tilde{p}<\tilde{p}^* .
+\end{align}
 
@@
 \begin{result}[Vertical and horizontal transmission of cooperation]
-When $0 \le \alpha<1$ and $v=1$, fixation, extinction, and stable coexistence of both cooperation and defection are possible.
+Without oblique transmission ($v=1$), fixation, extinction, and coexistence of both phenotypes are possible.
 \end{result}
 
-Determining the outcome of the dynamics depends on the sign of $T_A-T_B$ and on the legitimacy of the third equilibrium, that is, if $0<\tilde{p}^*<1$.
-\\
+We define the initial frequency as $\tilde{p}_0$ and
+\begin{equation}\begin{aligned}
+\gamma_1 = \frac{b \alpha T_A - (T_A - T_B)}{1-T_B}, \quad
+\gamma_2 = \frac{b \alpha T_B + (1+b) (T_A - T_B)}{1-T_B}.
+\end{aligned}\end{equation}
+Applying eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2} we can summarize the possible outcomes:
+\begin{enumerate}
+\item Fixation of cooperation,
+	if $T_A>T_B$ and $c < \gamma_1$, or
+	if $T_A>T_B$ and $\gamma_1 < c < \gamma_2$, and $\tilde{p}_0>\tilde{p}^*$, or
+	if $T_A<T_B$ and $\gamma_2 < c$.
+\item Global fixation of defection,
+	if $T_A>T_B$ and $\gamma_2 < c$, or
+	if $T_A<T_B$ and $c < \gamma_1$, or
+	if $T_A<T_B$ and $\gamma_1 < c < \gamma_2$, and $\tilde{p}_0<\tilde{p}^*$.
+\item Co-existence of both phenotypes at $\tilde{p}^*$, 
+	if $T_A<T_B$ and
+	$\gamma_2 < c < \gamma_1$.
+\end{enumerate}
 
-%This condition can also be formulated as a condition on the cost of cooperation $c$: cooperation will take over the population if
-%\begin{equation} \label{eq:unequal_transmission}
-%c < \frac{
-%	b \big[\alpha T_A + (1-\alpha)\tilde{p}(T_A - T_B)\big] + (T_A - T_B)
-%	}{
-%	1-T_B
-%	}.
-%\end{equation}
-%
-%Importantly, the condition for cooperation to increase from rarity is (set $\tilde{p}=0$ in \autoref{eq:unequal_transmission})
-%\begin{equation} \label{eq:unequal_transmission_from_rarity}
-%c < \frac{
-%	b \alpha T_A + (T_A - T_B)
-%	}{
-%	1-T_B
-%	} .
-%\end{equation} 
-%
-%In general, these conditions cannot be formulated in the form of Hamilton's rule ($c<b\cdot r$) due to the horizontal transmission bias $T_A-T_B$.
-%Without horizontal transmission bias, we get the following corollary that does have the form of Hamilton's rule.
+Importantly, the condition for cooperation to increase from rarity ($\tilde{p}_0 \approx 0$) is
+\begin{equation} \label{eq:unequal_transmission_from_rarity}
+T_A>T_B \; \text{and} \; c < \gamma_1
+\end{equation} 
+Thus, cooperation must have a horizontal transmission bias, and the cost of cooperation cannot be too big.
+
+In general, these conditions cannot be formulated in the form of Hamilton's rule ($c<b\cdot r$) due to the horizontal transmission bias $T_A-T_B$.
+Without horizontal transmission bias, we get the following corollary that does have the form of Hamilton's rule.\\
 
@@
 \begin{corollary}[No assortment of transmission and cooperation]
-If $\alpha=0$, then the third equilibrium is
-\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
-\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) }.
-\end{equation} 
-If there is a horizontal transmission bias for cooperation, $T_A>T_B$, then cooperation will fix in the population if the cost is not too high $c < (1+b) \frac{T_A-T_B}{1-T_B}$, and the initial frequency is high enough, $\tilde{p}(0) > \tilde{p}^*$.
+When $\alpha=0$, 
+if there is a horizontal transmission bias for cooperation, $T_A>T_B$, the cost is not too high $c < (1+b) \frac{T_A-T_B}{1-T_B}$, and the initial frequency is high enough, $\tilde{p}_0 > \tilde{p}^*$, then cooperation will fix in the population,
 If there is a horizontal transmission bias for defection, $T_A<T_B$, defection will take over the population.
@@
 
-This can be shown by setting $\alpha=0$ in \autoref{eq:vert_hori_equilibrium}. 
-Then, when $T_A>T_B$ we find a condition for $\tilde{p}^*<1$ and $\tilde{p}>\tilde{p}^*$ (\autoref{eq:vert_hori_global_condition1}).
-When $T_A<T_B$, we have $\tilde{p}^*<0$ and because of \autoref{eq:vert_hori_global_condition2}, any initial frequency leads to fixation of defection, $\tilde{p}=0$.\\
+Here, the third equilibrium is
+\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
+\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) },
+\end{equation} 
+and the cost boundaries are
+\begin{equation}\begin{aligned}
+\gamma_1(\alpha=0) = -\frac{(T_A - T_B)}{1-T_B}, \quad
+\gamma_2(\alpha=0) = \frac{(1+b) (T_A - T_B)}{1-T_B}.
+\end{aligned}\end{equation}
+If $T_A>T_B$ then $c>0>\gamma_1$ and cooperation cannot increase from rarity, but it can fix if $c<\frac{(1+b) (T_A - T_B)}{1-T_B}$; otherwise defection will fix.
+
+If $T_A<T_B$ then % TODO check this... gamma2<0 means fixation of A???
+\\
 

### 2020-07-29 ms/main.tex
finished revising result 2 (formerly 1)

@@
 Dividing by $(1-\tilde{p})$ we find that $\tilde{p}'>\tilde{p}$ if 
-\begin{equation} \label{eq:vert_hori_alpha1_global_condition}
+\begin{equation} \label{eq:vert_hori_alpha1_condition_proof}
   (1-c) (1 - T_B) + (1+b)T_A
-  > 1 \Leftrightarrow
-  c < \frac{bT_A + (T_A- T_B)}{1-T_B}.
+  > 1
 \end{equation}
@@
 
-We define the initial frequency as $\tilde{p}_0$ and
+We define the initial frequency as $\tilde{p}_0$ and the cost boundaries
 \begin{equation}\begin{aligned}
@@
 Applying eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2} we can summarize the possible outcomes:
-\begin{enumerate}
+%\begin{enumerate} % p* version
+%\item Fixation of cooperation,
+%	if $T_A>T_B$ and $0<\tilde{p}^*$, or
+%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0>\tilde{p}^*$, or
+%	if $T_A<T_B$ and $1<\tilde{p}^*$.
+%\item Global fixation of defection,
+%	if $T_A>T_B$ and $\tilde{p}^*>1$, or
+%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0<\tilde{p}^*$, or
+%	if $T_A<T_B$ and $\tilde{p}^*<0$
+%\item Co-existence of both phenotypes at $\tilde{p}^*$, 
+%	if $T_A<T_B$ and $0<\tilde{p}^*<1$.
+%\end{enumerate}
+\begin{enumerate} % gamma version
 \item Fixation of cooperation,
-	if $T_A>T_B$ and $c < \gamma_1$, or
-	if $T_A>T_B$ and $\gamma_1 < c < \gamma_2$, and $\tilde{p}_0>\tilde{p}^*$, or
-	if $T_A<T_B$ and $\gamma_2 < c$.
-\item Global fixation of defection,
-	if $T_A>T_B$ and $\gamma_2 < c$, or
-	if $T_A<T_B$ and $c < \gamma_1$, or
-	if $T_A<T_B$ and $\gamma_1 < c < \gamma_2$, and $\tilde{p}_0<\tilde{p}^*$.
-\item Co-existence of both phenotypes at $\tilde{p}^*$, 
-	if $T_A<T_B$ and
-	$\gamma_2 < c < \gamma_1$.
+	if $T_A>T_B$ and $c<\gamma_1$; or
+	if $T_A>T_B$ and $\gamma_1<c<\gamma_2$ and $\tilde{p}_0>\tilde{p}^*$; or
+	if $T_A<T_B$ and $c<\gamma_2$.
+\item Fixation of defection,
+	if $T_A>T_B$ and $\gamma_2<c$; or
+	if $T_A>T_B$ and $\gamma_1<c<\gamma_2$ and $\tilde{p}_0<\tilde{p}^*$; or
+	if $T_A<T_B$ and $\gamma_1<c$.
+\item Coexistence of both phenotypes at $\tilde{p}^*$, 
+	if $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
+
+Much of the literature on evolution of cooperation focuses on conditions for cooperation to invade a population of defectors.
+The next corollary deals with such a condition.
+\\
 \end{enumerate}
 
-Importantly, the condition for cooperation to increase from rarity ($\tilde{p}_0 \approx 0$) is
+\begin{corollary}[Condition for cooperation to increase from rarity]
+If the initial frequency of the cooperative phenotype if very close to zero, $\tilde{p}_0 \approx 0$, then its frequency will increase if 
 \begin{equation} \label{eq:unequal_transmission_from_rarity}
-T_A>T_B \; \text{and} \; c < \gamma_1
+\begin{aligned}
+T_A>T_B \;\; \text{and} \;\; c < \gamma_1, \quad \text{or} \quad
+T_A<T_B \;\; \text{and} \;\; \gamma_2<c < \gamma_1. 
+\end{aligned}
 \end{equation} 
-Thus, cooperation must have a horizontal transmission bias, and the cost of cooperation cannot be too big.
+\end{corollary}
 
@@
 \begin{corollary}[No assortment of transmission and cooperation]
-When $\alpha=0$, 
-if there is a horizontal transmission bias for cooperation, $T_A>T_B$, the cost is not too high $c < (1+b) \frac{T_A-T_B}{1-T_B}$, and the initial frequency is high enough, $\tilde{p}_0 > \tilde{p}^*$, then cooperation will fix in the population,
-If there is a horizontal transmission bias for defection, $T_A<T_B$, defection will take over the population.
+When $\alpha=0$, then either
+\textbf{(1)} cooperation can fix, but not increase from rarity, if there is horizontal bias for cooperation ($T_A>T_B$) and the cost is low enough ($c<(1+b)(T_A-T_B)/(1-T_B)$), or 
+\textbf{(2)} cooperation can increase from rarity to a stable coexistence with defection, if there is horizontal bias for defection ($T_A<T_B$) and the cost is low enough ($c<(T_B-T_A)/(1-T_B)$).
 \end{corollary}
@@
 \begin{equation}\begin{aligned}
-\gamma_1(\alpha=0) = -\frac{(T_A - T_B)}{1-T_B}, \quad
+\gamma_1(\alpha=0) = \frac{T_B - T_A}{1-T_B}, \quad
 \gamma_2(\alpha=0) = \frac{(1+b) (T_A - T_B)}{1-T_B}.
 \end{aligned}\end{equation}
-If $T_A>T_B$ then $c>0>\gamma_1$ and cooperation cannot increase from rarity, but it can fix if $c<\frac{(1+b) (T_A - T_B)}{1-T_B}$; otherwise defection will fix.
-
-If $T_A<T_B$ then % TODO check this... gamma2<0 means fixation of A???
+If $T_A>T_B$ then $\gamma_1(\alpha=0)<0<\gamma_2(\alpha=0)$.
+So cooperation cannot increase from rarity, but it can fix if $c<\gamma_2(\alpha=0)$.
+If $T_A<T_B$ then $\gamma_2(\alpha=0)<0<\gamma_1(\alpha=0)$.
+So cooperation cannot fix, but if $c<\gamma_1(\alpha=0)$ then it can increase from rarity to a stable coexistence at $\tilde{p}^*(\alpha=0)$.
 \\
@@
 \begin{corollary}[Complete assortment of transmission and cooperation]
-\end{corollary}
-In this case $\alpha=1$, and horizontal transmission always occurs together with the cooperative interaction; there is complete assortment.
-In this case there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
-The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found by setting $\tilde{p}'>\tilde{p}$, which gives (\autoref{eq:vert_hori_alpha1})
+When $\alpha=1$, there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
+The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found by setting $\tilde{p}'>\tilde{p}$, which gives
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 \end{equation}
-This is equivalent to a result by~\citet[eq.~1]{lewin2017microbes}.
+\end{corollary}
+This is proven in \autoref{eq:vert_hori_alpha1_condition_proof}.
+In this case there is complete assortment, and horizontal transmission always occurs together with the cooperative interaction.
+The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result, see their eq.~1.
+
+In terms of the cost boundaries, \autoref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$.
+If $T_A>T_B$ then that suffices for fixation of cooperation.
+If $T_B>T_A$ then $\gamma_2(\alpha=1)<0$ and again, \autoref{eq:vert_hori_alpha1} is sufficient for increase in frequency of $A$ up to $\tilde{p}^*(\alpha=1) \approx \infty$.
 

### 2020-07-29 ms/main.tex

@@
 We will write $f(\hat{p})$ as a Taylor approximation around the equilibrium $\hat{p}^*$. 
-\begin{equation} \label{eq:appendix_b_taylor}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f(\hat{p}^*) + f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
+\begin{equation} \label{eq:appendix_c_taylor}
+  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f(\hat{p}^*) + f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + O((\hat{p}-\hat{p}^*)^2)
 \end{equation}
-Where $R_2(\hat{p})$ is the remainder. Since $\hat{p}^*$ is an equilibrium $f(\hat{p}^*)=0$.
-\begin{equation} \label{eq:appendix_b_taylor0}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) =  f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
+Where $O((\hat{p}-\hat{p}^*)^2)$ is big O notation. Denote, $\epsilon = \hat{p}-\hat{p}^*$ and $\epsilon'=\hat{p}'-\hat{p}$.
+\begin{equation} \label{eq:appendix_c_taylor0}
+  f(\hat{p}) = \bar{w}\epsilon' = f(\hat{p}^*) + f'(\hat{p}^*)\epsilon + O(\epsilon^2)
 \end{equation}
-Neglecting the remainder(?) and we get: 
-\begin{equation} \label{eq:appendix_b_taylor_without_remainder}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f'(\hat{p}^*)(\hat{p}-\hat{p}^*)
+Since $\hat{p}^*$ is an equilibrium $f(\hat{p}^*)=0$ we get
+\begin{equation} \label{eq:appendix_c_taylor0}
+  f(\hat{p}) = \bar{w}\epsilon' = f'(\hat{p}^*)\epsilon + O(\epsilon^2)
 \end{equation}
-And we get:
-\begin{equation} \label{eq:appendix_b_derivative}
+By definition of big-O, if $f’(\hat{p}*)$ is negative, then there exists some $\epsilon$ (i.e. some neighbourhood of $\hat{p}^*$) for which $f’(\hat{p}^*) + O(\epsilon)$ is also negative.
+Therefore,
+\begin{equation} \label{eq:appendix_c_taylor_is_negative}
+  \bar{w}\epsilon' = f'(\hat{p}^*)\epsilon + O(\epsilon^2) < 0
+\end{equation}
+In addition, we know that $f(\hat{p}^*)=0$ therefore, there exist some $\epsilon$ for which $f(\hat{p}) > - \delta$ for some $\delta > 0$. 
+We choose delta to be $\delta = \frac{1}{\bar{w}}$, therefore  $f(\hat{p})=\bar{w}\epsilon'>-\frac{1}{\bar{w}}$. Therefore,
+\begin{equation} \label{eq:appendix_c_taylor_is_negative_and_bound_by_minus1}
+  -\frac{1}{\bar{w}} <\bar{w}\epsilon' = f'(\hat{p}^*)\epsilon + O(\epsilon^2) < 0
+\end{equation}
+
+Let's start simplify
+\begin{equation} \label{eq:appendix_c_taylor_is_negative}
+  -\frac{1}{\bar{w}} < \bar{w}\frac{\epsilon'}{\epsilon} < 0
+\end{equation}
+Since $\bar{w}>0$ we get that
+\begin{equation} \label{eq:appendix_c_condition_for_positive_epsilon}
   \begin{aligned}
-  f'(\hat{p}^*) &= \bar{w}\Big(\frac{\hat{p}'-\hat{p}}{\hat{p}-\hat{p}^*}\Big)\\
-  & = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*+\hat{p}^*-\hat{p}}{\hat{p}-\hat{p}}\Big) 
-  = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) .
+  -1 < \frac{\epsilon'}{\epsilon} & = \frac{\hat{p}'-\hat{p}}{\hat{p}-\hat{p}^*} = \frac{\hat{p}'-\hat{p}^*+\hat{p}^*-\hat{p}}{\hat{p}-\hat{p}^*} \\
+  & \frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*} - 1< 0
   \end{aligned}
 \end{equation}
-In order for the equilibrium $\hat{p}^*$ to be stable we demand that if $\hat{p} > \hat{p}^*$ then $\hat{p}'-\hat{p}^* < \hat{p}-\hat{p}^*$
-and if $\hat{p} < \hat{p}^*$ we demand that $-(\hat{p}'-\hat{p}^*) < -(\hat{p}-\hat{p}^*)$. 
-In other words, $\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}<1$ for every $\hat{p}$.
-Therefore,
-\begin{equation} \label{eq:appendix_b_condition}
+From eq.~\ref{eq:appendix_c_condition_for_positive_epsilon} we get that
+\begin{equation} \label{eq:appendix_c_final_condition_for_positive_epsilon}
   \begin{aligned}
-  f'(\hat{p}^*) = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) < 0 .
+    -1 < \frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*} < 1
   \end{aligned}
 \end{equation}
-Therefore, $f'(\hat{p}^*)$ is a sufficient condition for stability of $\hat{p}^*$.
+We can apply absoulte value
+\begin{equation} \label{eq:appendix_c_final_condition_for_positive_epsilon}
+  \begin{aligned}
+    |\hat{p}'-\hat{p}^*| < |\hat{p}-\hat{p}^*|
+  \end{aligned}
+\end{equation}
+
+Therefore, if $f'(\hat{p}^*)<0$ there exist some neighbourhood of $\hat{p}^*$ where $\hat{p}'$ is closer to $\hat{p}$, which means that $f'(\hat{p}^*)<0$ is sufficient condition for stability of $\hat{p}^*$.
+
+Now let's assume by contradiction that $\hat{p}^*$ is also locally stable when $f'(\hat{p}^*) > 0$.
+When $f'(\hat{p}^*) > 0$ there exist some neighbourhood $\epsilon$ of $\hat{p}^*$ in which $f'(\hat{p})>0$ for every $\hat{p}$ in the neighbourhood.
+
+If $\hat{p} > \hat{p}^*$ we get:
+\begin{equation} \label{eq:appendix_c_1}
+  \begin{aligned}
+    f(\hat{p}) = w\epsilon' > f(\hat{p}^*) = 0
+  \end{aligned}
+\end{equation}
+From eq.~\ref{eq:appendix_c_1} we can see that $\hat{p}' > \hat{p} > \hat{p}^*$ and therefore, $\hat{p}^*$ is not stable.
+
+If $\hat{p}<\hat{p}^*$ we get:
+\begin{equation} \label{eq:appendix_c_2}
+  \begin{aligned}
+    f(\hat{p}) = w\epsilon' < f(\hat{p}^*) = 0
+  \end{aligned}
+\end{equation}
+From eq.~\ref{eq:appendix_c_1} we can see that $\hat{p}' < \hat{p} < \hat{p}^*$ and therefore, $\hat{p}^*$ is not stable.
+%TODO: Add proof for f'(p)=0
+
+We saw that if $f'(\hat{p}^*)<0$ then $\hat{p}^*$ is stable, and if $f'(\hat{p}^*)>0$ then $\hat{p}^*$ is unstable.
+Therefore, $f'(\hat{p}^*)$ is sufficient and necessary condition for equilibrium stability.
 

### 2020-07-30 ms/main.tex
added todo
edit appendix A

@@
 So cooperation cannot fix, but if $c<\gamma_1(\alpha=0)$ then it can increase from rarity to a stable coexistence at $\tilde{p}^*(\alpha=0)$.
+%TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.
 \\
@@
 of juveniles with phenotype $A$ in the current generation $\hat{p}$.
-We start from eq.~\ref{eq:horizontal},
+Starting from \autoref{eq:horizontal},
 \begin{equation}\label{eq:appendix_b_1}
-  \hat{p}' = v \tilde{p}' + (1-v) p'
+  \hat{p}' = v \tilde{p}' + (1-v) p',
 \end{equation}
-Substituting $p'$ using eq.~\ref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ using eq.~\ref{eq:nextgen_parents_simplified}, we have
+we substitute $p'$ using \autoref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ using \autoref{eq:nextgen_parents_simplified}, we have
 \begin{equation}\label{eq:appendix_b_2}
@@
 where $\bar{w} = 1 + \hat{p}(b-c)$. 
-
-We define $f(\hat{p})$ to be
-\begin{equation} \label{eq:appendix_b_3}
+We define $f(\hat{p})$ as
+\begin{equation} \label{eq:appendix_define_f}
 \begin{aligned}
@@
 \end{equation}
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we simplify \autoref{eq:appendix_b_3} to 
-\autoref{eq:general_case_polynomial} and \autoref{eq:polynomial_coefficients}.
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we simplify \autoref{eq:appendix_define_f} to 
+eqs.~\ref{eq:general_case_polynomial}-\ref{eq:polynomial_coefficients}.
 

### 2020-07-30 ms/main.tex
format result 3; edit appendix b

--- 2020-07-29 ms/main.tex
@@
 \begin{enumerate}
-\item \emph{Fixation of the cooperative phenotype $A$}, 
-\begin{enumerate}
-\item if $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$, or
-\item if $T_A>T_B$ and $0<\beta_3$, or 
-\item if $T_A<T_B$ and $\beta_1<\beta_3$.
-\end{enumerate}
-
-\item \emph{Fixation of the defector phenotype $B$}, 
-\begin{enumerate}
-\item if $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$, or 
-\item if $T_A>T_B$ and $\beta_1<\beta_3<0$, or 
-\item if $T_A<T_B$ and $\beta_3<0$.
-\end{enumerate}
-
-\item \emph{Protected polymorphism, or co-existence of both phenotypes}, if $T_A < T_B$ and $0<\beta_3<\beta_1$.
-
+\item \emph{Fixation of cooperation}, 
+if $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
+if $T_A>T_B$ and $0<\beta_3$; or 
+if $T_A<T_B$ and $\beta_1<\beta_3$.
+\item \emph{Fixation of the defection}, 
+if $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
+if $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+if $T_A<T_B$ and $\beta_3<0$.
+\item \emph{Coexistence of both phenotypes at $\hat{p}^*$},
+if $T_A < T_B$ and $0<\beta_3<\beta_1$.
 \item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_3<\beta_1$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\pagebreak
+%\pagebreak
 % Acknowledgements
@@
 
-We show that $f'(\hat{p}^*)<0$ is a sufficient condition for local stability an equilibrium $\hat{p}^*$.
-We will write $f(\hat{p})$ as a Taylor approximation around the equilibrium $\hat{p}^*$. 
-\begin{equation} \label{eq:appendix_b_taylor}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f(\hat{p}^*) + f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
-\end{equation}
-Where $R_2(\hat{p})$ is the remainder. Since $\hat{p}^*$ is an equilibrium $f(\hat{p}^*)=0$.
-\begin{equation} \label{eq:appendix_b_taylor0}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) =  f'(\hat{p}^*)(\hat{p}-\hat{p}^*) + R_2(\hat{p})
-\end{equation}
-Neglecting the remainder(?) and we get: 
-\begin{equation} \label{eq:appendix_b_taylor_without_remainder}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) = f'(\hat{p}^*)(\hat{p}-\hat{p}^*)
-\end{equation}
-And we get:
-\begin{equation} \label{eq:appendix_b_derivative}
-  \begin{aligned}
-  f'(\hat{p}^*) &= \bar{w}\Big(\frac{\hat{p}'-\hat{p}}{\hat{p}-\hat{p}^*}\Big)\\
-  & = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*+\hat{p}^*-\hat{p}}{\hat{p}-\hat{p}}\Big) 
-  = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) .
-  \end{aligned}
-\end{equation}
-In order for the equilibrium $\hat{p}^*$ to be stable we demand that if $\hat{p} > \hat{p}^*$ then $\hat{p}'-\hat{p}^* < \hat{p}-\hat{p}^*$
-and if $\hat{p} < \hat{p}^*$ we demand that $-(\hat{p}'-\hat{p}^*) < -(\hat{p}-\hat{p}^*)$. 
-In other words, $\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}<1$ for every $\hat{p}$.
-Therefore,
-\begin{equation} \label{eq:appendix_b_condition}
-  \begin{aligned}
-  f'(\hat{p}^*) = \bar{w}\Big(\frac{\hat{p}'-\hat{p}^*}{\hat{p}-\hat{p}^*}-1\Big) < 0 .
-  \end{aligned}
-\end{equation}
-Therefore, $f'(\hat{p}^*)$ is a sufficient condition for stability of $\hat{p}^*$.
+Denote $f(p)=\lambda(p'-p)$, where $\lambda>0$, and assume $f(p^*)=0$.
+We want a condition for $|p'-p^*| < |p-p^*|$.
+
+If $p>p^*=0$, we want a condition for $p'<p$, or
+$\frac{p'}{p}<1$, or
+$\lambda \frac{p'-p}{p} < 0$, or
+$\frac{f(p)}{p} < 0$.
+Using a linear approximation for $f(p)$ near $0$, we have
+\begin{equation}\begin{aligned}
+p' &< p \Leftrightarrow \\
+\frac{f'(0) \cdot p + O(p^2)}{p} &< 0 \Leftrightarrow \\
+f'(0) + O(p) &< 0.
+\end{aligned}\end{equation}
+Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any $0<p<\epsilon$ it is guaranteed that $0<p'<p$, that is, $p'$ is closer than $p$ to zero.
+
+If $p<p^*=1$, we want a condition for $1-p' < 1-p$, or
+$\frac{1-p'}{1-p}<1$, or
+$\lambda \frac{-(p'-p)}{1-p} < 0$, or
+$-\frac{f(p)}{1-p} < 0$.
+Using a linear approximation for $f(p)$ near $1$, we have
+\begin{equation}\begin{aligned}
+1-p' &< 1-p  \Leftrightarrow \\
+\frac{f'(1)(p-1) + O\big((p-1)^2\big)}{p-1} &< 0 \Leftrightarrow \\
+f'(1) - O(1-p) &< 0.
+\end{aligned}\end{equation}
+Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ it is guaranteed that $1-p'<1-p$, that is, $p'$ is closer than $p$ to one.
 

### 2020-07-30 ms/main.tex
fix typos and their corresponding errors in the results, together with Dor

@@
 Individuals interact according to a prisoner's dilemma.
-Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $b>c>0$.
+Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
 \textbf{\autoref{table:prisoner_payoff}} shows the payoff matrix, i.e.
@@
 \begin{equation}\begin{aligned}
-\gamma_1 = \frac{b \alpha T_A - (T_A - T_B)}{1-T_B}, \quad
+\gamma_1 = \frac{b \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
 \gamma_2 = \frac{b \alpha T_B + (1+b) (T_A - T_B)}{1-T_B}.
@@
 	if $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
+\end{enumerate}
 
 Much of the literature on evolution of cooperation focuses on conditions for cooperation to invade a population of defectors.
-The next corollary deals with such a condition.
+The next corollary deals with such a condition, followed by a corollary that deals with symmetric horizontal transmission, i.e. $T_A=T_B$.
 \\
-\end{enumerate}
 
@@
 \begin{corollary}[No assortment of transmission and cooperation]
-When $\alpha=0$, then either
-\textbf{(1)} cooperation can fix, but not increase from rarity, if there is horizontal bias for cooperation ($T_A>T_B$) and the cost is low enough ($c<(1+b)(T_A-T_B)/(1-T_B)$), or 
-\textbf{(2)} cooperation can increase from rarity to a stable coexistence with defection, if there is horizontal bias for defection ($T_A<T_B$) and the cost is low enough ($c<(T_B-T_A)/(1-T_B)$).
+When $\alpha=0$, then if there is horizontal bias for cooperation ($T_A>T_B$) and
+\textbf{(1)} the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; or
+\textbf{(2)} the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency if high enough ($\tilde{p}_0 > \tilde{p}^*$).
 \end{corollary}
@@
 \begin{equation}\begin{aligned}
-\gamma_1(\alpha=0) = \frac{T_B - T_A}{1-T_B}, \quad
-\gamma_2(\alpha=0) = \frac{(1+b) (T_A - T_B)}{1-T_B}.
+\gamma_1(\alpha=0) = \frac{T_A - T_B}{1-T_B}, \quad
+\gamma_2(\alpha=0) = (1+b)\frac{T_A - T_B}{1-T_B}.
 \end{aligned}\end{equation}
-If $T_A>T_B$ then $\gamma_1(\alpha=0)<0<\gamma_2(\alpha=0)$.
-So cooperation cannot increase from rarity, but it can fix if $c<\gamma_2(\alpha=0)$.
-If $T_A<T_B$ then $\gamma_2(\alpha=0)<0<\gamma_1(\alpha=0)$.
-So cooperation cannot fix, but if $c<\gamma_1(\alpha=0)$ then it can increase from rarity to a stable coexistence at $\tilde{p}^*(\alpha=0)$.
+If $T_A>T_B$ then $0<\gamma_1(\alpha=0)<\gamma_2(\alpha=0)$.
+So either $c<\gamma_1(\alpha=0)$ or $\gamma_1(\alpha=0)<c<\gamma_2(\alpha=0)$ will allow fixation of cooperation, the latter only if the initial frequency is high enough.
+If $T_A<T_B$ then $\gamma_2(\alpha=0)<\gamma_1(\alpha=0)<0<c$.
+So defection will fix..
 %TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.

### 2020-07-30 ms/main.tex
revised intro and discussion, but much more work needed

@@
 
-These theories assume that cooperation is genetically determined, which raises the question: \emph{Is it possible that cooperation is determined by non-genetic factors?}
-Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
+%These theories assume that cooperation is genetically determined, which raises the question: \emph{Is it possible that cooperation is determined by non-genetic factors?}
+%Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
 Here we attempt to determine to what extent the evolution of cooperative behavior can be explained by \emph{cultural transmission},
@@
 
-Here we hypothesize that non-vertical cultural transmission can explain the evolution of cooperation. 
+We hypothesize that non-vertical cultural transmission can help explain the evolution of cooperation. 
 To test this hypothesis, we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
@@
 
-\begin{result}[Oblique and horizontal transmission of cooperation]
+\begin{result}[Oblique and horizontal transmission of cooperation] \label{result:obli_hori}
 Without vertical transmission ($v=0$), if there is a horizontal transmission bias in favor of cooperation, namely
@@
 
-\begin{result}[Vertical and horizontal transmission of cooperation]
+\begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
 Without oblique transmission ($v=1$), fixation, extinction, and coexistence of both phenotypes are possible.
@@
 If $T_A<T_B$ then $\gamma_2(\alpha=0)<\gamma_1(\alpha=0)<0<c$.
-So defection will fix..
+So defection will fix in any case.
 %TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.
@@
 
-\begin{result}[Vertical, oblique, and horizontal transmission of cooperation]
+\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
 The cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the horizontal transmission bias $T_A-T_B$ and the coefficients $\beta_1$ and $\beta_3$:
@@
 We studied fully mixed and very large populations with a prisoner's dilemma payoff. 
-We found that under horizontal and vertical cultural transmissions, if \autoref{eq:unequal_transmission} is satisfied, cooperation will take over fully mixed populations (Result 1).
-Under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype is sufficient and necessary for evolution of cooperation (Result 2, \autoref{eq:oblique_only_result}).
+We found that under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype is sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
+Under horizontal and vertical cultural transmissions, cooperation or defection can fix, or coexist in a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the correlation between cooperation and transmission (Result~\autoref{result:vert_hori}).
 Under a combination of vertical, oblique, and horizontal transmission the dynamics are further complicated.
-Yet, we find that cooperation can evolve and in some cases be maintained together with defection (Result 4).
-Importantly, our results demonstrate that cooperation can evolve even in a fully mixed population (i.e. in an unstructured population), without repeating interactions or individual recognition.
-These results significantly further our understating of the cultural evolution of cooperation.
+We find again that under some conditions cooperation can evolve, and can even be maintained in a stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
 
@@
 
-There is an ongoing debate about the extent to which kin selection explains the evolution of cooperation and altruism.
-For example, it has been suggested that it can explain the cooperative behavior of worker castes of eusocial insects like the honey bee. % TODO REF
-The most significant argument against kin selection is that in some cases cooperation among unrelated individuals appears to have evolved~\citep{wilson2005kin}.
-Therefore, other theories have been develop to explain the evolution of cooperation and altruism.
+%There is an ongoing debate about the extent to which kin selection explains the evolution of cooperation and altruism.
+%For example, it has been suggested that it can explain the cooperative behavior of worker castes of eusocial insects like the honey bee. % TODO REF
+%The most significant argument against kin selection is that in some cases cooperation among unrelated individuals appears to have evolved~\citep{wilson2005kin}.
+%Therefore, other theories have been develop to explain the evolution of cooperation and altruism.
 
-\emph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
+%\emph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
 In \emph{direct reciprocity} there are repeated encounters between the same two individuals, and at every encounter each individual has a choice between cooperation and defection.
 Hence, it may eventually pay off to cooperate if it may cause your partner to cooperate in the future.
-This game-theoretic framework, known as the \emph{repeated prisoner's dilemma}, 
-%A well known strategy to play this game is called  'tit-for-tat'.
+%This game-theoretic framework, known as the \emph{repeated prisoner's dilemma}, 
+%%A well known strategy to play this game is called  'tit-for-tat'.
 This strategy always starts with a cooperation, then it does whatever the other player has done in the previous round: a cooperation for a cooperation, a defection for a defection.
@@
 However,
-can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability of another encounter between the same two individuals, $w$, 
-%TODO Referencess
-\begin{equation} \label{eq:reciprocity}
-c < b \cdot w.
-\end{equation}
-
-Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy. \\
-\emph{Indirect reciprocity} has also been suggested to explain the evolution of cooperation.
-\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of currency. 
-%TODO: refs
-The currency that ``fuels the engines'' of indirect reciprocity is \emph{reputation}. 
-However, reciprocity assumes repeated interactions and therefore has difficulty in explaining the evolution of cooperation if  interactions are not repeated.
-
-\emph{Group selection} theory posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
+%can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability of another encounter between the same two individuals, $w$, 
+%%TODO Referencess
+%\begin{equation} \label{eq:reciprocity}
+%c < b \cdot w.
+%\end{equation}
+%
+%Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy. \\
+%\emph{Indirect reciprocity} has also been suggested to explain the evolution of cooperation.
+%\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of currency. 
+%%TODO: refs
+%The currency that ``fuels the engines'' of indirect reciprocity is \emph{reputation}. 
+%However, reciprocity assumes repeated interactions and therefore has difficulty in explaining the evolution of cooperation if  interactions are not repeated. 
+%
+%\emph{Group selection} theory posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
 A common model for group selection divides the population into groups in which there are cooperators that help  other group members and defectors that do not.
 % TODO add reference
-Individuals reproduce proportionally to their fitness, and offspring are added to the same group as their parents.
-If a group reaches a certain size it can split to two groups, so groups that grow faster will split more often.
-Groups with cooperators grow faster than groups without cooperators, and
-cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
-\begin{equation} \label{eq:groupselection}
-c < b \cdot \frac{m}{m+n} .
-\end{equation}
-
-Group selection has been criticized by biologists who advocate a gene-centered view of evolution. % TODO ref
-It has also been criticized because for cooperation to take over the population it must have higher fitness than defection, while under group selection theory the fitness of cooperators at the individual level is lower than the fitness of defectors.
+%Individuals reproduce proportionally to their fitness, and offspring are added to the same group as their parents.
+%If a group reaches a certain size it can split to two groups, so groups that grow faster will split more often.
+%Groups with cooperators grow faster than groups without cooperators, and
+%cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
+%\begin{equation} \label{eq:groupselection}
+%c < b \cdot \frac{m}{m+n} .
+%\end{equation}
+%
+%Group selection has been criticized by biologists who advocate a gene-centered view of evolution. % TODO ref
+%It has also been criticized because for cooperation to take over the population it must have higher fitness than defection, while under group selection theory the fitness of cooperators at the individual level is lower than the fitness of defectors.
 Thus a trait with a lower fitness taking over the population is a contradiction %TODO ref.
-\citet{eldakar2011eight} reject this argument, claiming that it is a tautology and does not qualify as an argument against group selection.
+%\citet{eldakar2011eight} reject this argument, claiming that it is a tautology and does not qualify as an argument against group selection.
 The distinction between individual and group selection requires a comparison of fitness differentials within and between groups in a multi-group population, and when a trait  evolves by group selection, despite having lower fitness within a group, that group might have higher average fitness in competition with other groups, all things considered.
@@
 
-\citet{Eshel1982} have shown that with assortative meeting, i.e. probability $m$ that individuals interact with within their phenotypic group, cooperation can evolve if $m > c/b$.
-In our Corollary 1.1 (\autoref{eq:equal_transmission}), cooperation evolves if $\alpha T / (1-T) > c/b$.
-So in our model $\alpha T/(1-T)$ is the effective relatedness, which is affected by $\alpha$, the correlation between transmission and interaction, and $T$, the horizontal transmission rate.
+\citet{Eshel1982} have shown that with assortative meeting, i.e. probability $m$ that individuals interact with within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
+Our results highlight another possibility for assortative meeting, in which individuals interact with probability $\alpha$ with their cultural partners, i.e. during horizontal transmission.
+We show that high levels of assortative meeting ($\alpha$) significantly increase the potential for evolution of cooperation.
+With a high enough $\alpha$, cooperation can increase from rarity, although not fix, even when there is horizontal bias against cooperation ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$, see Result~\autoref{result:vert_hori})
+
+Importantly, we demonstrate that cooperation can evolve even in a fully mixed population (i.e. in an unstructured population), without repeating interactions or individual recognition.
+Our results highlight the potential importance of non-vertical cultural transmission for explaining complex evolutionary phenomena, and significantly further our understating of the cultural evolution of cooperation.
 

### 2020-08-01 ms/main.tex
Add new figure
Add Boundaries Graph for Result 2

@@
 \\
+%%% Figure: Boundries graph of results 2
+
+\begin{figure}[H]
+  \centering
+  \begin{subfigure}{8cm}
+    \includegraphics[scale=0.5]{figure2a.pdf}
+    \caption{$b=1.3$, $T_A=0.4$, $\alpha = 0.7$}
+    \label{fig:results2_a}
+    \includegraphics[scale=0.5]{figure2b.pdf}
+    \caption{$b=1.3$, $T_A=0.4$, $\alpha = 0$}
+    \label{fig:results2_b}
+  \end{subfigure}
+  \label{fig:results2}
+  \caption{\textbf{Boundaries graph} This figure illustrates under what values of $T_A-T_B$ and cost $c$ fixation of cooperates, fixation of defectors or coexistence are possible given where $b$, $\alpha$ and $T_B$ are known.
+    Figure \textbf{(a)} illustrates that when $\alpha \neq 0$ fixation of cooperates, fixation of defectors or coexistence are possible.
+\textbf{(b)} illustrates that when $\alpha=0$ coexistence is not possible, only fixation of one of the phenotypes}
+\end{figure}
+%%%
 
@@
 T_A<T_B \;\; \text{and} \;\; \gamma_2<c < \gamma_1. 
-\end{aligned}
+\end{aligned}f
 \end{equation} 
@@
   \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2a.pdf}
+    \includegraphics[scale=0.5]{figure3a.pdf}
     \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
@@
   \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2b.pdf}
+    \includegraphics[scale=0.5]{figure3b.pdf}
     \caption{$v=1$, $\alpha = 0$}
@@
   \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2c.pdf}
+    \includegraphics[scale=0.5]{figure3c.pdf}
     \caption{$v=0$}
@@
   The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange).
-  %TODO ic (c), the blue and green got mixed. 
   % TODO have all panels in one row.

### 2020-08-03 ms/main.tex
added coexistence figure; revised figure captions and formating

--- 2020-07-30 ms/main.tex
@@
 We define the initial frequency as $\tilde{p}_0$ and the cost boundaries
-\begin{equation}\begin{aligned}
+\begin{equation} \label{eq:cost_boundaries}
+\begin{aligned}
 \gamma_1 = \frac{b \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
 \gamma_2 = \frac{b \alpha T_B + (1+b) (T_A - T_B)}{1-T_B}.
-\end{aligned}\end{equation}
-Applying eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2} we can summarize the possible outcomes:
+\end{aligned}
+\end{equation}
+Applying eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2} we can summarize the possible outcomes (\autoref{fig:results2}):
 %\begin{enumerate} % p* version
@@
 
+It is interesting to note that cooperation and defection can stably coexist if there his horizontal bias for defection and the cost of cooperation is large but not too large.
+The recurrence for this case is illustrated in \autoref{fig:coexistence}.
+
 Much of the literature on evolution of cooperation focuses on conditions for cooperation to invade a population of defectors.
@@
 \\
+
+%%% Figure: Result 2 Boundaries
+
+\begin{figure}[htb]
+  \centering
+    \includegraphics[scale=1]{figure2a.pdf}
+    \includegraphics[scale=1]{figure2b.pdf}
+  \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or fixation depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
+The blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
+  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, $c$ and $T_B$ vary on the y- and x-axes.
+\textbf{Left}: With $\alpha = 0.7 > 0$, coexistence is possible (yellow).
+\textbf{Right}: With $\alpha=0$, coexistence is not possible.}
+    \label{fig:results2}
+\end{figure}
+%%%
+
+%%% Figure: coexistence map
+\begin{figure}[htb]
+\centering
+\includegraphics[scale=1]{coexistence.pdf}
+\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted in blue as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
+The line of $\hat{p}'=p$ is in orange.
+The curve and line intersect at the equilibrium $\hat{p}^*$.
+The blue curve is above the orange line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$.
+The blue curve is below the orange line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
+}
+\label{fig:coexistence}
+\end{figure}
 
@@
 \end{corollary}
+
+\autoref{fig:results2}b demonstrates this these conditions.
 
@@
 So, \autoref{eq:vert_hori_alpha1} means that cooperation can evolve if the effective cost for cooperation is less than the effective benefit.
+
+\begin{figure}[htb]
+  \centering
+    \includegraphics[scale=0.75]{figure3a.pdf}
+%    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
+    \label{fig:results_a}
+    \includegraphics[scale=0.75]{figure3b.pdf}
+%    \caption{$v=1$, $\alpha = 0$}
+    \label{fig:results_b}
+    \includegraphics[scale=0.75]{figure3c.pdf}
+%    \caption{$v=0$}
+  \label{fig:results}
+  \caption{
+  \textbf{Numerical results for cultural evolution of cooperation.}
+  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
+  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue), and stable coexistence of cooperators and defectors (orange).
+  Parameters: (a) $v=1$, $T_A=T_B=T$, $\alpha \neq 0$; (b) $v=1$, $\alpha = 0$; (c) $v=0$.
+  % TODO add all parameters.
+  % TODO remove legends, increase fonts, explain in caption instead of legend.
+  }
+\end{figure}
 
@@
 \end{result}
-
-\begin{figure}[H]
-  \centering
-  \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2a.pdf}
-    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
-    \label{fig:results_a}
-  \end{subfigure}
-  \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2b.pdf}
-    \caption{$v=1$, $\alpha = 0$}
-    \label{fig:results_b}
-  \end{subfigure}
-  \begin{subfigure}{8cm}
-    \includegraphics[scale=0.5]{figure2c.pdf}
-    \caption{$v=0$}
-    \label{fig:results_c}
-  \end{subfigure}
-  \label{fig:results}
-  \caption{
-  \textbf{Numerical results for cultural evolution of cooperation.}
-  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
-  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange).
-  %TODO ic (c), the blue and green got mixed. 
-  % TODO have all panels in one row.
-  }
-\end{figure}
 

### 2020-08-08 ms/main.tex
Adjust the figures as youav asked

@@
   Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, $c$ and $T_B$ vary on the y- and x-axes.
-\textbf{Left}: With $\alpha = 0.7 > 0$, coexistence is possible (yellow).
-\textbf{Right}: With $\alpha=0$, coexistence is not possible.}
+\textbf{Up}: With $\alpha = 0.7 > 0$, coexistence is possible (yellow).
+\textbf{Down}: With $\alpha=0$, coexistence is not possible.}
     \label{fig:results2}
@@
 \caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted in blue as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
-The line of $\hat{p}'=p$ is in orange.
-The curve and line intersect at the equilibrium $\hat{p}^*$.
-The blue curve is above the orange line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$.
+The line of $\hat{p}'=\hat{p}$ is in dashed black.
+The curve and dashed line intersect at the equilibrium $\hat{p}^*$.
+The blue curve is above the black dashed line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$.
 The blue curve is below the orange line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.

### 2020-08-08 ms/main.tex
Fix results 3

@@
 The blue curve is above the black dashed line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$.
-The blue curve is below the orange line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
+The blue curve is below the black dashed line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
 }
@@
 if $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-if $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+if $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
 if $T_A<T_B$ and $\beta_3<0$.
@@
 if $T_A < T_B$ and $0<\beta_3<\beta_1$.
-\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_3<\beta_1$.
+\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_1<\beta_3 < 0$.
 

### 2020-08-08 ms/main.tex
Fix figure 3 caption

@@
     \includegraphics[scale=1]{figure2b.pdf}
-  \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or fixation depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
+  \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
 The blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).

### 2020-08-10 ms/main.tex
conflict solving

@@
 \section*{Introduction}
-Cooperative behavior can harm an individual's fitness and increase the fitness of its conspecifics or competitors~\citep{axelrod1981evolution}.
-Nevertheless, cooperative behavior appears to occur in many non-human animals~\citep{dugatkin1997cooperation}, for example rats~\citep{rice1962altruism} and birds~\citep{krams2008experimental}.
+Cooperative behavior can reduce an individual's fitness and increase the fitness of its conspecifics or competitors~\citep{axelrod1981evolution}.
+Nevertheless, cooperative behavior appears to occur in many non-human animals~\citep{dugatkin1997cooperation}, including primates~\citep{jaeggi2013natural},  rats~\citep{rice1962altruism}, birds~\citep{stacey1990cooperative,krams2008experimental}, and lizards~\citep{sinervo2006self}.
 Evolution of cooperative behavior remains an important conundrum in evolutionary biology.
+Since the work of  \citet{hamilton1964genetical} and \citet{axelrod1981evolution}, theories for the evolution of cooperative and altruistic behaviors have been intertwined often under the rubric of kin selection.
 
-\emph{Kin selection} theory posits that natural selection can favor cooperation between related individuals.
-The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}.
-According to Hamilton, for an allele that determines cooperative behavior to increase in frequency, the reproductive cost to the actor that cooperates, $c$, must be less than the benefit to the recipient, $b$, times the `relatedness' between the recipient and the actor, $r$.
-This `relatedness' coefficient $r$ measures the correlation between the gene in the actor and the gene in the recipient.
-This condition is also known as Hamilton's rule:
+\emph{Kin selection} theory posits that natural selection is more likely to favor cooperation between more closely related individuals.
+The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
+This relatedness coefficient $r$ measures a probability that an allele sampled from the cooperator is identical by descent to one at the same locus in the recipient.
+This condition is  known as ``Hamilton's rule'':
 \begin{equation} \label{eq:hamilton_rule}
@@
 
-\citet{Eshel1982} have studied a relevant model for the evolution of cooperative behavior under vertical transmission.
-Their model included \emph{assortative meeting}, or non-random encounters.
-That is, if a fraction $m$ of the population interacts with an individual of the same phenotype, and $1-m$ interacts randomly.
+\citet{Eshel1982}  studied a related model for the evolution of cooperative behavior under vertical transmission.
+Their model included \emph{assortative meeting}, or non-random encounters, where a fraction $m$ of individuals in the population each interact with an individual of the same phenotype, and a fraction $1-m$ interacts  with a randomly chosen individual.
 Such assortative meeting may be due, for example, to population structure or active partner choice.
-In their model, cooperative behavior can evolve if \footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the righthand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
-}. 
+In their model, cooperative behavior can evolve if\footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the righthand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
+} 
 \citep[eq.~3.2]{Eshel1982}
 \begin{equation} \label{eq:assortative_meeting}
-c < b \cdot m,
+c < b \cdot m\,,
 \end{equation}
-where $b$ and $c$ are the benefit and cost of cooperation
-Here, $m$ takes the role of the relatedness $r$.
+where $b$ and $c$ are the benefit and cost of cooperation. 
+Here $m$ in (\ref{eq:assortative_meeting}) takes the role of the relatedness $r$  in (\ref{eq:hamilton_rule}).
 
@@
 %Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
-Here we attempt to determine to what extent the evolution of cooperative behavior can be explained by \emph{cultural transmission},
-which allows an individual to acquire attitudes and behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
-\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
-They showed that under vertical (parent-to-offspring) cultural transmission, Hamilton's rule does not govern the evolution of parent-to-offspring or sib-to-sib altruism.
 
-\emph{Non-vertical transmission} may be either horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs from adults to unrelated offspring.
-Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,ram2018evolution}.
-\citet{lewin2017microbes} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host behavior, can help to explain the evolution of cooperative behavior.
-Interestingly, some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
+Here we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission},
+ which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
+\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission and
+showed that under vertical (parent-to-offspring) cultural transmission, the conditions for the initial increase of altruism entails a modification of Hamilton's rule in the cases  of parent-to-offspring or sib-to-sib altruism.
 
-We hypothesize that non-vertical cultural transmission can help explain the evolution of cooperation. 
-To test this hypothesis, we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
-For example, if an individual interacts with a cooperative individual, it might learn that cooperation is a positive behavior and will be cooperative in the future.
-We develop cultural evolution models that include both vertical and non-vertical transmission of cooperation and investigate these models using mathematical analysis and simulations.  
-Our results demonstrate cultural transmission can facilitate the evolution of cooperation even when genetic transmission cannot.
-These results suggest that further research on the evolution of cooperation should account for non-vertical transmission and that treatment of cooperation as a cultural, rather then genetic trait, can lead to a better understanding of this important and enigmatic phenomenon.
+\emph{Non-vertical cultural transmission} may be either viewed as horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs  to  offspring from the generation to which their parents belong.
+Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
+\citet{lewin2017microbes} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior.
+Some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
+
+We hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation, and 
+to test this hypothesis we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
+For example, if an individual interacts with a cooperative individual, it might learn that cooperation is an advantageous behavior and will be cooperative in the future.
+Our cultural evolution models  include both vertical and non-vertical transmission of cooperation, and we investigate these models using mathematical analysis and simulations.  
+Our results demonstrate that cultural transmission can facilitate the evolution of cooperation even when genetic transmission can not, and that treatment of cooperation as a cultural, rather than a genetic, trait can lead to a better understanding of its evolutionary dynamics.
 
@@
 \section*{Models}
-
-We focus on the evolution of cooperation in a fully mixed population where cooperation is modeled using the \emph{prisoner's dilemma}. % yr: add ref
 
@@
 
-Not all adults become parents due to natural selection, and we denote the frequency of phenotype $A$ among parents with $\tilde{p}$.
+Not all adults become parents due to natural selection, and we denote the frequency of phenotype $A$ among parents by $\tilde{p}$.
 Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
@@
 
-Individuals interact according to a prisoner's dilemma.
+Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
 Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
@@
 
+\bigskip
+\begin{center}[TABLE 1 HERE]\end{center}
 %%% Table: payoff matrix
-\begin{table}[h]
-\centering
-\begin{tabular}{lll}
-\toprule
-           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
-$\phi_1=A$ & $1+b-c$ & $1-c$ \\
-$\phi_1=B$ & $1+b$   & $1$
-\\ \bottomrule
-\end{tabular}
-\caption{\textbf{Payoff matrix for prisoner's dilemma.}
-The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
-$b>c>0$.
-}
-\label{table:prisoner_payoff}
-\end{table}
-%%%
 
+\bigskip
 Social interactions occur randomly:
@@
 The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\textbf{\autoref{table:interactions}}).
+
+\bigskip
+\begin{center}[TABLE 2 HERE]\end{center}
+%%% Table: payoff matrix
+
+\bigskip
 
@@
 \end{equation}
+where $\hat{p}=v\tilde{p}+(1-v)p$.
+%This is not a recursion-MF
 
 %%% Table: interactions
-\begin{table}[]
-\begin{tabular}{@{}llllll@{}}
-\toprule
-\multirow{2}{*}{Phenotype $\phi_1$} &
-  \multirow{2}{*}{Phenotype $\phi_2$} &
-  \multirow{2}{*}{Frequency} &
-  \multirow{2}{*}{Fitness of $\phi_1$} &
-  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
-    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
-$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
-$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
-\end{tabular}
-\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
-\label{table:interactions}
-\end{table}
-%%%
 
@@
 With only oblique and horizontal transmission, i.e.
-$v = 0$, \autoref{eq:horizontal} becomes $\hat{p}=p$ and \autoref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
+$v = 0$, Eq.\ \ref{eq:horizontal} becomes $\hat{p}=p$ and Eq.\ \ref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
 \begin{equation}  \label{eq:nextgen_parents_oblique_only}
@@
 Therefore, in the absence of vertical transmission, selection plays no role in the evolution of cooperation.
-Hence, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~{\autoref{fig:results_c}).
+Hence, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~{\autoref{fig:results}c).
 
@@
 
-With only vertical and horizontal transmission, i.e. $v=1$, \autoref{eq:horizontal} becomes
+With only vertical and horizontal transmission, i.e. $v=1$, Eq.\ \ref{eq:horizontal} becomes
 $\hat{p} =  \tilde{p}$,
-and \autoref{eq:nextgen_parents_simplified} for the frequency of the cooperative phenotype among parents in the next generation $\tilde{p}'$ can be written as
+and Eq.\ \ref{eq:nextgen_parents_simplified} for the frequency of the cooperative phenotype among parents in the next generation $\tilde{p}'$ can be written as
 \begin{equation} \label{eq:nextgen_parents_vertical_only} 
@@
 
-The fixation of either cooperation or defection, 
-$\tilde{p}=0$ and $ \tilde{p}=1$, are equilibria of \autoref{eq:nextgen_parents_vertical_only}, that is, they solve $\tilde{p}'= \tilde{p}$.
+Fixation of either cooperation, $\tilde{p}=1$, or defection, 
+$\tilde{p}=0$, are equilibria of Eq.\ \ref{eq:nextgen_parents_vertical_only}, that is, they solve $\tilde{p}'= \tilde{p}$.
 We therefore assume for the remainder of the analysis that $0<\tilde{p}<1$.
@@
 and there are no additional equilibria.
-
-Therefore, for cooperation to take over the population (for $\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$, that is,
+For cooperation to take over the population (for $\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$; that is,
 \begin{equation}
@@
 
-If $\alpha<1$, we want to determine a condition for $\tilde{p}'>\tilde{p}$. 
-We divide \autoref{eq:nextgen_parents_vertical_only} by $\tilde{p}$ and set $\bar{w} = 1 + \tilde{p}(b-c)$ to get
+If $\alpha<1$, divide both sides of Eq.\ \ref{eq:nextgen_parents_vertical_only} by $\tilde{p}$ and set $\bar{w} = 1 + \tilde{p}(b-c)$. Then $\tilde{p}'>\tilde{p}$ if
 \begin{equation}
@@
 
-Following the same steps to solve $\tilde{p}'=\tilde{p}$, we find that there can be a third, polymorphic equilibrium 
+Besides the fixation states $\tilde{p}=0$ and $\tilde{p}=1$, there may be an actual polymorphic equilibrium of $\tilde{p}'=\tilde{p}$ in Eq.\ \ref{eq:nextgen_parents_vertical_only}, namely 
 \begin{equation} \label{eq:vert_hori_equilibrium}
   \tilde{p}^* = 
-  \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B)} .
+  \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B)} ,
 \end{equation} 
-Note that this is a legitimate equilibrium only if $0<\tilde{p}^*<1$.
+which is legitimate if $0<\tilde{p}^*<1$.
 
-Note that all parameters are positive.
-So, applying \autoref{eq:vert_hori_global_condition}, for $\tilde{p}'>\tilde{p}$ we require that either 
+Since all parameters are positive, we can apply
+inequality \ref{eq:vert_hori_global_condition} and see that for $\tilde{p}'>\tilde{p}$ we require that either 
 \begin{align} 
@@
 
-We therefore have the following result and corollaries.\\
+We summarize these findings in the following result and corollaries.\\
 
@@
 
-We define the initial frequency as $\tilde{p}_0$ and the cost boundaries
+Let the initial frequency of the alternative phenotype be $\tilde{p}_0$ and denote the cost boundaries by
 \begin{equation} \label{eq:cost_boundaries}
@@
 \end{equation}
-Applying eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2} we can summarize the possible outcomes (\autoref{fig:results2}):
+Then, applying \ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes which are illustrated in \autoref{fig:results2}:
 %\begin{enumerate} % p* version
@@
 
-It is interesting to note that cooperation and defection can stably coexist if there his horizontal bias for defection and the cost of cooperation is large but not too large.
-The recurrence for this case is illustrated in \autoref{fig:coexistence}.
+Note that cooperation and defection can  coexist stably if there is horizontal bias for defection and the cost of cooperation is large but not too large.
+The recursion dynamic for this case is illustrated in \autoref{fig:coexistence}.
 
-Much of the literature on evolution of cooperation focuses on conditions for cooperation to invade a population of defectors.
+Much of the literature on evolution of cooperation focuses on conditions for an initially rare cooperative phenotype to invade a population of defectors.
 The next corollary deals with such a condition, followed by a corollary that deals with symmetric horizontal transmission, i.e. $T_A=T_B$.
@@
 
-\begin{corollary}[Condition for cooperation to increase from rarity]
-If the initial frequency of the cooperative phenotype if very close to zero, $\tilde{p}_0 \approx 0$, then its frequency will increase if 
+\begin{corollary}[Condition for cooperation to increase when initially rare]
+If the initial frequency of the cooperative phenotype is very close to zero, $\tilde{p}_0 \approx 0$, then this frequency will increase if 
 \begin{equation} \label{eq:unequal_transmission_from_rarity}
@@
 In general, these conditions cannot be formulated in the form of Hamilton's rule ($c<b\cdot r$) due to the horizontal transmission bias $T_A-T_B$.
-Without horizontal transmission bias, we get the following corollary that does have the form of Hamilton's rule.\\
+Without horizontal transmission bias, i.e., with $T_A=T_B$, these conditions reduce to the following  form of Hamilton's rule.\\
 
@@
 \end{corollary}
-To verify, set $T_A=T_B$ in \autoref{eq:vert_hori_global_condition}.
-
-This can be interpreted as a version of Hamilton's rule (\autoref{eq:hamilton_rule}), where $\alpha T/(1-T)$ is the `effective relatedness'.
-\autoref{fig:results_a} demonstrates this condition. 
+Inequality \ref{eq:equal_transmission} is obtained by setting $T_A=T_B$ in inequality \ref{eq:vert_hori_global_condition} and can be interpreted as a version of Hamilton's rule (inequality \ref{eq:hamilton_rule}), where $\alpha T/(1-T)$ can be regarded as the `effective relatedness'.
+\autoref{fig:results}a demonstrates this condition. 
 \\
@@
 \begin{corollary}[No assortment of transmission and cooperation]
-When $\alpha=0$, then if there is horizontal bias for cooperation ($T_A>T_B$) and
+If $\alpha=0$ and there is horizontal bias for cooperation ($T_A>T_B$) and
 \textbf{(1)} the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; or
-\textbf{(2)} the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency if high enough ($\tilde{p}_0 > \tilde{p}^*$).
+\textbf{(2)} the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
 \end{corollary}
 
-\autoref{fig:results2}b demonstrates this these conditions.
-
-Here, the third equilibrium is
+\autoref{fig:results2}b illustrates these conditions, where
+ the third equilibrium given by Eq.\ \ref{eq:vert_hori_equilibrium} becomes
 \begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
@@
 So either $c<\gamma_1(\alpha=0)$ or $\gamma_1(\alpha=0)<c<\gamma_2(\alpha=0)$ will allow fixation of cooperation, the latter only if the initial frequency is high enough.
-If $T_A<T_B$ then $\gamma_2(\alpha=0)<\gamma_1(\alpha=0)<0<c$.
-So defection will fix in any case.
+If $T_A<T_B$ then $\gamma_2(\alpha=0)<\gamma_1(\alpha=0)<0<c$,
+and defection will fix.
 %TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.
@@
 When $\alpha=1$, there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
-The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found by setting $\tilde{p}'>\tilde{p}$, which gives
+The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 \end{corollary}
-This is proven in \autoref{eq:vert_hori_alpha1_condition_proof}.
-In this case there is complete assortment, and horizontal transmission always occurs together with the cooperative interaction.
-The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result, see their eq.~1.
+With complete assortment, in inequality \ref{eq:vert_hori_alpha1_condition_proof}
+ horizontal transmission  occurs together with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
 
-In terms of the cost boundaries, \autoref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$.
-If $T_A>T_B$ then that suffices for fixation of cooperation.
-If $T_B>T_A$ then $\gamma_2(\alpha=1)<0$ and again, \autoref{eq:vert_hori_alpha1} is sufficient for increase in frequency of $A$ up to $\tilde{p}^*(\alpha=1) \approx \infty$.
-
-\autoref{eq:vert_hori_alpha1} can be written as
+In terms of the cost boundaries, inequality \ref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$, and if $T_A>T_B$ then that suffices for fixation of cooperation.
+If $T_B>T_A$ then $\gamma_2(\alpha=1)<0$ and again, (\ref{eq:vert_hori_alpha1}) is sufficient for increase in the frequency of $A$.
+Inequality \ref{eq:vert_hori_alpha1} can be written as
 \begin{equation} \label{eq:vert_hori_alpha1_effective}
@@
 which provides an interesting interpretation for the success of cooperation. 
-Consider an interaction between two individuals: a cooperator and a defector.
+In the interaction between a cooperator and a defector.
 $(1-c)(1-T_B)$ is the probability that the cooperator remains cooperative and also reproduces. 
-Therefore, $1 - (1-c)(1-T_B)$ is the probability that either the cooperator becomes a defector, \emph{or} that it fails to reproduce.
-This is the effective cost for cooperation from this interaction.
-$(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces.
-This is the effective benefit for cooperation from this interaction.
-So, \autoref{eq:vert_hori_alpha1} means that cooperation can evolve if the effective cost for cooperation is less than the effective benefit.
+Therefore, $1 - (1-c)(1-T_B)$ is the probability that either the cooperator becomes a defector, or that it fails to reproduce.
+This is the effective cost for cooperation from this interaction, while
+$(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces, which
+ is the effective benefit for cooperation from this interaction.
+Thus inequality (\ref{eq:vert_hori_alpha1}) entails that cooperation can evolve if the effective cost for cooperation is less than the effective benefit.
 
@@
 %    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
-    \label{fig:results_a}
+  %  \label{fig:results_a}
     \includegraphics[scale=0.75]{figure3b.pdf}
 %    \caption{$v=1$, $\alpha = 0$}
-    \label{fig:results_b}
+ %   \label{fig:results_b}
     \includegraphics[scale=0.75]{figure3c.pdf}
 %    \caption{$v=0$}
-  \label{fig:results}
+%  \label{fig:results}
   \caption{
   \textbf{Numerical results for cultural evolution of cooperation.}
-  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
+  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p$, the frequency of adults with cooperative phenotype $A$.
   The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue), and stable coexistence of cooperators and defectors (orange).
@@
   }
+  \label{fig:results}
 \end{figure}
@@
 
-In this case $0<v<1$, and the recursion system is more complex.
-Therefore, we focus on local stability, rather than global stability.
+In this case $0<v<1$, and the recursion system is more complex,
+and we focus on local rather than on global stability.
 To proceed, we note that 
-\autoref{eq:horizontal} can give $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$,
-\autoref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, and 
-\autoref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$, see Appendix~\autoref{sec:appendixB}.
-We then determine the equilibria, which are solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
+Eq.\ \ref{eq:horizontal} can give $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
+%Equation 4 does not give $\hat{p}$---MF
+Eq.\ \ref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
+Eq.\ \ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
+Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixB}).
+We then determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
 %: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})=\bar{w}(\hat{p}'-\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
@@
 %We now turn to the general case where $T_A \neq T_B$. 
-We apply \autoref{eq:horizontal}, \autoref{eq:nextgen_adults_slimpify}, and \autoref{eq:nextgen_parents_simplified} to obtain the function $f(\hat{p})$, see Appendix~\autoref{sec:appendixB}:
+We apply Eqs.\ \ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to obtain the function $f(\hat{p})$ (see Appendix~\autoref{sec:appendixB}):
 
@@
 
-If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$. 
-Therefore, $f(\hat{p})$ is a quadratic polynomial,
+If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$, 
+and $f(\hat{p})$ becomes a quadratic polynomial:
 \begin{equation} \label{eq:equal_horizontal_transmission}
@@
 \end{equation}
-Clearly the only two equilibria are the fixations of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$.
-These equilibria are locally stable if $f'(\hat{p})<0$ (Appendix~\autoref{sec:appendixC}).
-Therefore, we find the derivative,
+Clearly the only two equilibria are the fixations  $\hat{p} =  0$ and $\hat{p} = 1$.
+These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (Appendix~\autoref{sec:appendixC}), and
 \begin{equation}
@@
 \end{equation}
-and investigate its sign at the equilibria,
+with
 \begin{equation} \label{eq:derivative_of_phattag-phat}
@@
 \end{equation}
-Therefore with symmetric horizontal transmission, fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary 1.1, \autoref{eq:equal_transmission}.
+Therefore with symmetric horizontal transmission, fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary 1.1, namely Eq.\ \ref{eq:equal_transmission}.
 
@@
 Therefore, three equilibria may exist, two of which are
-$\hat{p} = 0 $ and $\hat{p} = 1$.
-By solving $f(\hat{p})/\big[\hat{p}(1-\hat{p})\big] = \beta_3 -\beta_1 \hat{p} = 0$ we  find the third equilibrium
+$\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
 \begin{equation} \label{eq:oblique_and_vertic_result}
@@
 
-Note that the sign of this cubic at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
+Note that the sign of the  cubic (Eq.\ \ref{eq:general_case_polynomial}) at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
 If $T_A>T_B$, then 
@@
  \end{equation}
-since $c<b$ and $1>\alpha v$, the sign of the cubic at positive and negative infinity is negative and positive, respectively.
+since $c<b$ and $1>\alpha v$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
 First, if $\beta_3<\beta_1$ then 
-$1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e. between 0 and 1) equilibrium.
+$1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e. between 0 and 1) equilibrium.
 Second, if $\beta_1<\beta_3<0$ then 
@@
 Third, if $0<\beta_3$ then 
-$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$; that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
@@
  \end{equation}
-since $c<b$, and $1>\alpha v$. So the sign of the cubic at positive and negative infinity is positive and negative, respectively. 
-First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$, that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
-Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$, that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+since $c<b$ and $1>\alpha v$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
+First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
+Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
+Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
 
@@
 \begin{enumerate}
-\item \emph{Fixation of cooperation}, 
-if $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-if $T_A>T_B$ and $0<\beta_3$; or 
-if $T_A<T_B$ and $\beta_1<\beta_3$.
-\item \emph{Fixation of the defection}, 
-if $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-if $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
-if $T_A<T_B$ and $\beta_3<0$.
-\item \emph{Coexistence of both phenotypes at $\hat{p}^*$},
-if $T_A < T_B$ and $0<\beta_3<\beta_1$.
-\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_1<\beta_3 < 0$.
-
+\item \emph{Fixation of cooperation}: 
+if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
+\emph{(ii)} if $T_A>T_B$ and $0<\beta_3$; or 
+\emph{(iii)} if $T_A<T_B$ and $\beta_1<\beta_3$.
+\item \emph{Fixation of the defection}: 
+if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
+\emph{(v)} if $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+\emph{(vi)} if $T_A<T_B$ and $\beta_3<0$.
+\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
+if \emph{(vi)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+\item \emph{Fixation of either phenotype depending on initial frequency}: if \emph{(vii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
 \end{enumerate}
@@
 \section*{Discussion}
-We hypothesized that non-vertical transmission can explain the evolution of cooperation.
-We studied fully mixed and very large populations with a prisoner's dilemma payoff. 
-We found that under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype is sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
-Under horizontal and vertical cultural transmissions, cooperation or defection can fix, or coexist in a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the correlation between cooperation and transmission (Result~\autoref{result:vert_hori}).
-Under a combination of vertical, oblique, and horizontal transmission the dynamics are further complicated.
-We find again that under some conditions cooperation can evolve, and can even be maintained in a stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
+We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game..
+Under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
+Under horizontal and vertical cultural transmission, cooperation, or defection can fix, or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the correlation between cooperation and transmission (Result~\autoref{result:vert_hori}).
+Under a combination of vertical, oblique, and horizontal transmission the dynamics are much more complicated.
+However, we show that under some conditions cooperation can evolve, and can even be maintained in  stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
 
-This study was partially inspired by \citet{lewin2017microbes}. 
-They hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
+This study was partially inspired by the work of \citet{lewin2017microbes}, 
+who hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
 Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{dobson1988population,poulin2010parasite}.
@@
 Microbes can also be transferred vertically, from parent to offspring, and % yr: cite 10.1126/science.aat7164
-a microbe that induces its host to cooperate with another host and thereby increases the latter's fitness will  increase the vertical transmission of the microbes of the receiving individual.
-Kin selection among microbes could therefore favor microbes that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
+a microbe that induces its host to cooperate with another host, and thereby increases the latter's fitness, will  increase its vertical transmission  from the receiving individual.
+Kin selection among microbes could therefore favor those that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
 
@@
 
-\citet{Eshel1982} have shown that with assortative meeting, i.e. probability $m$ that individuals interact with within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
-Our results highlight another possibility for assortative meeting, in which individuals interact with probability $\alpha$ with their cultural partners, i.e. during horizontal transmission.
-We show that high levels of assortative meeting ($\alpha$) significantly increase the potential for evolution of cooperation.
-With a high enough $\alpha$, cooperation can increase from rarity, although not fix, even when there is horizontal bias against cooperation ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$, see Result~\autoref{result:vert_hori})
+\citet{Eshel1982}  showed that with assortative meeting, namely, a probability $m$ that individuals interact  within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
+Our results highlight another possibility for assortative meeting, namely, individuals interacting at rate $\alpha$ with their cultural partners, resulting in horizontal transmission.
+We show that high levels of assortative meeting  significantly increase the potential for evolution of cooperation.
+With a high enough $\alpha$, cooperation can increase when initially rare (although it will not fix) even when there is horizontal bias against cooperation ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$, see Result~\autoref{result:vert_hori})
 
-Importantly, we demonstrate that cooperation can evolve even in a fully mixed population (i.e. in an unstructured population), without repeating interactions or individual recognition.
-Our results highlight the potential importance of non-vertical cultural transmission for explaining complex evolutionary phenomena, and significantly further our understating of the cultural evolution of cooperation.
+An important implication of our results is that cooperation can evolve even in a fully mixed population (i.e., in an unstructured population), without repeated interactions or individual recognition.
+This highlights the potential importance of non-vertical cultural transmission for explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.
 
@@
 
-Denote $f(p)=\lambda(p'-p)$, where $\lambda>0$, and assume $f(p^*)=0$.
+Denote $f(p)=\lambda(p'-p)$, where $\lambda>0$, and assume $f(p^*)=0$; i.e., $p^*$ is an equilibrium.
+%HOW DO YOU KNOW $p^*\in(0,1)$?--MF
 We want a condition for $|p'-p^*| < |p-p^*|$.
@@
 \end{aligned}\end{equation}
-Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any $0<p<\epsilon$ it is guaranteed that $0<p'<p$, that is, $p'$ is closer than $p$ to zero.
+Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any $0<p<\epsilon$, it is guaranteed that $0<p'<p$, that is, $p'$ is closer than $p$ to zero.
 
@@
 
+\newpage
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lll}
+\toprule
+           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
+$\phi_1=A$ & $1+b-c$ & $1-c$ \\
+$\phi_1=B$ & $1+b$   & $1$
+\\ \bottomrule
+\end{tabular}
+\caption{\textbf{Payoff matrix for prisoner's dilemma.}
+The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
+$b>c>0$.
+}
+\label{table:prisoner_payoff}
+\end{table}
+
+\newpage
+
+\begin{table}[]
+\begin{tabular}{@{}llllll@{}}
+\toprule
+\multirow{2}{*}{Phenotype $\phi_1$} &
+  \multirow{2}{*}{Phenotype $\phi_2$} &
+  \multirow{2}{*}{Frequency} &
+  \multirow{2}{*}{Fitness of $\phi_1$} &
+  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
+    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
+$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
+$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
+\end{tabular}
+\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
+\label{table:interactions}
+\end{table}
+%%%
+%%%
 \end{document}

### 2020-08-15 ms/main.tex
Yoav and Marc comments

@@
 \end{equation}
-We divide by $\tilde{p}$, set $\bar{w} = 1 + \tilde{p}(b-c)$, and rearrange to get
-\begin{equation}
-  (1-\tilde{p}) \big[(1-c) (1 - T_B) + (1+b)T_A\big] 
-  > 1 -\tilde{p} .
-\end{equation}
-Dividing by $(1-\tilde{p})$ we find that $\tilde{p}'>\tilde{p}$ if 
+Factoring out $\tilde{p}(1-\tilde{p})$ and setting $\bar{w} = 1 + \tilde{p}(b-c)$, we find that $\hat{p}'>\hat{p}$ if
+%\begin{equation}
+%  (1-\tilde{p}) \big[(1-c) (1 - T_B) + (1+b)T_A\big] 
+%  > 1 -\tilde{p} .
+%\end{equation}
+%Dividing by $(1-\tilde{p})$ we find that $\tilde{p}'>\tilde{p}$ if 
 \begin{equation} \label{eq:vert_hori_alpha1_condition_proof}
@@
 \end{equation}
-Rearranging, we get
-\begin{equation} 
-\begin{aligned} 
-  1 - \tilde{p} < 
-  & - \tilde{p}(1+b-c)(1-\tilde{p}) (1-\alpha) T_B \\
-  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
-  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-  & + (1-\tilde{p})^2 (1-\alpha) T_A .
-\end{aligned}
-\end{equation}
-Diving by $(1-\tilde{p})$ and rearranging so that free terms are on the left and terms with $\tilde{p}$ are on the right, we have
-\begin{equation} 
-\begin{aligned} 
-  &1 - (1-\alpha) T_A - (1+b) \alpha T_A - (1 - T_B)(1-c)  < \\
-   &\tilde{p}[ - (1+b-c) (1-\alpha) T_B 
-   + (1-c) (1-\alpha) T_B
-   + (1+b) (1-\alpha) T_A 
-   - (1-\alpha) T_A].
-\end{aligned}
-\end{equation}
+%Rearranging, we get
+%\begin{equation} 
+%\begin{aligned} 
+%  1 - \tilde{p} < 
+%  & - \tilde{p}(1+b-c)(1-\tilde{p}) (1-\alpha) T_B \\
+%  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
+%  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
+%  & + (1-\tilde{p})^2 (1-\alpha) T_A .
+%\end{aligned}
+%\end{equation}
+%Diving by $(1-\tilde{p})$ and rearranging so that free terms are on the left and terms with $\tilde{p}$ are on the right, we have
+%\begin{equation} 
+%\begin{aligned} 
+%  &1 - (1-\alpha) T_A - (1+b) \alpha T_A - (1 - T_B)(1-c)  < \\
+%   &\tilde{p}[ - (1+b-c) (1-\alpha) T_B 
+%   + (1-c) (1-\alpha) T_B
+%   + (1+b) (1-\alpha) T_A 
+%   - (1-\alpha) T_A].
+%\end{aligned}
+%\end{equation}
 Simplifying, we find that $\tilde{p}'>\tilde{p}$ if and only if
@@
 We summarize these findings in the following result and corollaries.\\
-
+%TODO:format like result 3
 \begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
@@
 Eq.\ \ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixB}).
+Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}).
 We then determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
@@
 %We now turn to the general case where $T_A \neq T_B$. 
-We apply Eqs.\ \ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to obtain the function $f(\hat{p})$ (see Appendix~\autoref{sec:appendixB}):
+We apply Eqs.\ \ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to obtain the function $f(\hat{p})$ (see Appendix~\autoref{sec:appendixA}):
 
@@
 Clearly the only two equilibria are the fixations  $\hat{p} =  0$ and $\hat{p} = 1$.
-These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (Appendix~\autoref{sec:appendixC}), and
+These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (Appendix~\autoref{sec:appendixB}), and
 \begin{equation}
@@
 if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-\emph{(ii)} if $T_A>T_B$ and $0<\beta_3$; or 
-\emph{(iii)} if $T_A<T_B$ and $\beta_1<\beta_3$.
+if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
+if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
 \item \emph{Fixation of the defection}: 
 if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-\emph{(v)} if $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
-\emph{(vi)} if $T_A<T_B$ and $\beta_3<0$.
+if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
@@
 \section*{Discussion}
-We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game..
+We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game.
 Under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
@@
 However, we show that under some conditions cooperation can evolve, and can even be maintained in stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
+We saw that it is likely to find configuration of parameters that results coexistence as can be seen in \autoref{fig:results2}a.
+In figure \autoref{fig:results2}a the yellow area in which coexistence occur has horizontal bias that favor defection ($T_B>T_A$) and the cost is relatively small.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{} \label{sec:appendixB}
+\section{} \label{sec:appendixA}
 We want to find the frequency of juveniles with phenotype $A$ in next generation $\hat{p}'$ as a function of frequency
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{} \label{sec:appendixC}
+\section{} \label{sec:appendixB}
 
@@
 Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ it is guaranteed that $1-p'<1-p$, that is, $p'$ is closer than $p$ to one.
-
 \end{appendices}

### 2020-08-15 ms/main.tex
Update figure 2

@@
   \centering
-    \includegraphics[scale=1]{figure2a.pdf}
-    \includegraphics[scale=1]{figure2b.pdf}
-  \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
-The blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
-  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, $c$ and $T_B$ vary on the y- and x-axes.
-\textbf{Up}: With $\alpha = 0.7 > 0$, coexistence is possible (yellow).
-\textbf{Down}: With $\alpha=0$, coexistence is not possible.}
+    \includegraphics[scale=0.75]{figure2a.pdf}
+    \includegraphics[scale=0.7]{figure2b.pdf}
+    \includegraphics[scale=0.7]{boundiries_withAlpha_y_axis.pdf}
+    \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates (\textbf{a-b}): combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$; (\textbf{c}) combinations of horizontal bias, $T_A-T_B$, and probability of horizontal transmission with social partner, $alpha$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
+    In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
+  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, (\textbf{a-b}): $c$ and $T_B$ vary on the y- and x-axes; (\textbf{c}): $\alpha$ and $T_B$ vary on the y- and x-axes.
+   (\textbf{a}): With $\alpha = 0.7 > 0$, coexistence is possible (yellow). (\textbf{b}): With $\alpha=0$, coexistence is not possible. (\textbf{c}): with $c = 0.35$ coexistence is possible.}
     \label{fig:results2}

### 2020-08-15 ms/main.tex
Another fix to figure 2

@@
     \includegraphics[scale=0.7]{boundiries_withAlpha_y_axis.pdf}
-    \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates (\textbf{a-b}): combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$; (\textbf{c}) combinations of horizontal bias, $T_A-T_B$, and probability of horizontal transmission with social partner, $alpha$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
+    \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates (\textbf{a-b}): combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$; (\textbf{c}) combinations of horizontal bias, $T_A-T_B$, and assortative meeting, $\alpha$,
+    that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
     In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).

### 2020-08-15 ms/main.tex
Add corollary 5 and fix fig 2
Improve figure 2 caption

@@
     that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
-    In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
+    In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}); in (\textbf{c}): the bule and orage curves show the assortative meeting boundaries $\delta_1$ and $\delta_2$ (\autoref{eq:boundries_assortative_meeting}).
   Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, (\textbf{a-b}): $c$ and $T_B$ vary on the y- and x-axes; (\textbf{c}): $\alpha$ and $T_B$ vary on the y- and x-axes.
@@
  horizontal transmission  occurs together with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
+
+\begin{corollary}[The importance of assortative meeting $\alpha$]
+Denote the assortative meeting ($\alpha$) boundaries:
+\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting}
+  \delta_1= \frac{c(1-T_B)-(1+b)(T_A-T_B)}{b\cdot T_B}, \quad
+  \delta_2 = \frac{c(1-T_B)-(T_A-T_B)}{b\cdot T_A}.
+  \end{aligned}\end{equation}
+  Using this notation we can find the condition on $\alpha$ for cooperation to increase when initially rare. 
+  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
+    \begin{aligned}
+    T_A>T_B \;\; \text{and} \;\; \alpha > \delta_2, \quad \text{or} \quad
+    T_A<T_B \;\; \text{and} \;\; \alpha > \delta_1
+    \end{aligned}
+    \end{equation} 
+\end{corollary}
 

### 2020-08-19 ms/main.tex
revised title, figure captions, corollay 5, names of variables and more

--- 2020-08-15 ms/main.tex
@@
 \graphicspath{ {./Figures/} }
-\usepackage{subcaption}
+\usepackage[labelfont=bf]{caption}
 \usepackage{float}
@@
 
+% autoref
+\def\equationautorefname{Eq.}
+
 % NatBib
@@
 % Title page
-\title{Cultural Transmission Can Explain the Evolution of Cooperation}
+\title{Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation}
 
@@
 \author[3]{Marcus W. Feldman}
-\author[a,*]{Yoav Ram}
+\author[1,4,*]{Yoav Ram}
 
@@
 \affil[3]{Department of Biology, Stanford University, Stanford, CA}
+\affil[4]{School of Zoology, Tel Aviv University, Tel Aviv, Israel}
 \affil[*]{Corresponding author: yoav@yoavram.com}
@@
 
-\emph{Kin selection} theory posits that natural selection is more likely to favor cooperation between more closely related individuals.
+\emph{Kin selection theory} posits that natural selection is more likely to favor cooperation between more closely related individuals.
 The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
 This relatedness coefficient $r$ measures a probability that an allele sampled from the cooperator is identical by descent to one at the same locus in the recipient.
-This condition is  known as ``Hamilton's rule'':
+This condition is  known as \emph{Hamilton's rule}:
 \begin{equation} \label{eq:hamilton_rule}
@@
 \citep[eq.~3.2]{Eshel1982}
-\begin{equation} \label{eq:assortative_meeting}
-c < b \cdot m\,,
+\begin{equation} \label{eq:eshel1982}
+c < b \cdot m \,,
 \end{equation}
 where $b$ and $c$ are the benefit and cost of cooperation. 
-Here $m$ in (\ref{eq:assortative_meeting}) takes the role of the relatedness $r$  in (\ref{eq:hamilton_rule}).
+Here $m$ in \autoref{eq:eshel1982} takes the role of the relatedness $r$  in \autoref{eq:hamilton_rule}.
 
-%These theories assume that cooperation is genetically determined, which raises the question: \emph{Is it possible that cooperation is determined by non-genetic factors?}
-%Culture has significant impact on the behavior of humans~\citep{ihara2004cultural,jeong2018bronze} as well as non-human animals~\citep{bonner2018evolution}.
-
-Here we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission},
- which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
-\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission and
-showed that under vertical (parent-to-offspring) cultural transmission, the conditions for the initial increase of altruism entails a modification of Hamilton's rule in the cases  of parent-to-offspring or sib-to-sib altruism.
+Here we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
+\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
+They showed that under a combination of genetic and vertical (parent-to-offspring) cultural transmission, the conditions for the initial increase of altruism entails a modification of Hamilton's rule in the cases of parent-to-offspring or sib-to-sib altruism.
+For example, if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
+\begin{equation} \label{eq:feldman1985}
+c < b \cdot \varphi - \frac{1-\varphi}{\varphi} \,.
+\end{equation}
 
@@
 
+% TODO
 We hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation, and 
@@
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
-Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance, % yr: cite Zefferman Behav Ecol 2016
+Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance, % TODO cite Zefferman Behav Ecol 2016
 the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
@@
 Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
-\textbf{\autoref{table:prisoner_payoff}} shows the payoff matrix, i.e.
+\autoref{table:prisoner_payoff} shows the payoff matrix, i.e.
 the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
 
+%%% Table: payoff matrix
 \bigskip
-\begin{center}[TABLE 1 HERE]\end{center}
-%%% Table: payoff matrix
+\begin{table}[h]
+\centering
+\begin{tabular}{lll}
+\toprule
+           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
+$\phi_1=A$ & $1+b-c$ & $1-c$ \\
+$\phi_1=B$ & $1+b$   & $1$
+\\ \bottomrule
+\end{tabular}
+\caption{\textbf{Payoff matrix for prisoner's dilemma.}
+The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
+$b>c>0$.
+}
+\label{table:prisoner_payoff}
+\end{table}
+\bigskip
+%%%
 
-\bigskip
 Social interactions occur randomly:
@@
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\textbf{\autoref{fig:horizontal}}).
+It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
 The assortment parameter $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
 Horizontal transmission is not always successful, as one partner may reject the other's phenotype.
-The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\textbf{\autoref{table:interactions}}).
+The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).
 
+%%% Table: interactions
 \bigskip
-\begin{center}[TABLE 2 HERE]\end{center}
-%%% Table: payoff matrix
-
+\begin{table}[]
+\begin{tabular}{@{}llllll@{}}
+\toprule
+\multirow{2}{*}{Phenotype $\phi_1$} &
+  \multirow{2}{*}{Phenotype $\phi_2$} &
+  \multirow{2}{*}{Frequency} &
+  \multirow{2}{*}{Fitness of $\phi_1$} &
+  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
+    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
+$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
+$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
+\end{tabular}
+\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
+\label{table:interactions}
+\end{table}
 \bigskip
+%%%
 
@@
 \end{equation}
-where fitness values are taken from \textbf{\autoref{table:prisoner_payoff}} and \textbf{\autoref{table:interactions}}, and the population mean fitness is
+where fitness values are taken from \autoref{table:prisoner_payoff} and \autoref{table:interactions}, and the population mean fitness is
 \begin{equation} \label{eq:mean_fitness}
@@
 %This is not a recursion-MF
-
-%%% Table: interactions
-
-%%% Figure: model illustration
-\begin{figure}[thb]
-  \centering
-  \includegraphics[scale=1]{figure1.pdf}
-  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
-  \label{fig:horizontal}
-\end{figure}
-%%%
 
@@
 \end{equation}
-Then, applying \ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes which are illustrated in \autoref{fig:results2}:
+Then, applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes which are illustrated in \autoref{fig:results2}:
 %\begin{enumerate} % p* version
@@
 
-%%% Figure: Result 2 Boundaries
-
-\begin{figure}[htb]
-  \centering
-    \includegraphics[scale=0.75]{figure2a.pdf}
-    \includegraphics[scale=0.7]{figure2b.pdf}
-    \includegraphics[scale=0.7]{boundiries_withAlpha_y_axis.pdf}
-    \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates (\textbf{a-b}): combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$; (\textbf{c}) combinations of horizontal bias, $T_A-T_B$, and assortative meeting, $\alpha$,
-    that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow).
-    In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
-  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, (\textbf{a-b}): $c$ and $T_B$ vary on the y- and x-axes; (\textbf{c}): $\alpha$ and $T_B$ vary on the y- and x-axes.
-   (\textbf{a}): With $\alpha = 0.7 > 0$, coexistence is possible (yellow). (\textbf{b}): With $\alpha=0$, coexistence is not possible. (\textbf{c}): with $c = 0.35$ coexistence is possible.}
-    \label{fig:results2}
-\end{figure}
-%%%
-
-%%% Figure: coexistence map
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=1]{coexistence.pdf}
-\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted in blue as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
-The line of $\hat{p}'=\hat{p}$ is in dashed black.
-The curve and dashed line intersect at the equilibrium $\hat{p}^*$.
-The blue curve is above the black dashed line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$.
-The blue curve is below the black dashed line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
-}
-\label{fig:coexistence}
-\end{figure}
-
 \begin{corollary}[Condition for cooperation to increase when initially rare]
@@
 If $\alpha=0$ and there is horizontal bias for cooperation ($T_A>T_B$) and
-\textbf{(1)} the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; or
-\textbf{(2)} the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
+(1) the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; or
+(2) the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
 \end{corollary}
@@
 
-\begin{corollary}[Complete assortment of transmission and cooperation]
+\begin{corollary}[Perfect assortment of transmission and cooperation]
 When $\alpha=1$, there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
@@
 \end{corollary}
-With complete assortment, in inequality \ref{eq:vert_hori_alpha1_condition_proof}
+With perfect assortment, in inequality \ref{eq:vert_hori_alpha1_condition_proof}
  horizontal transmission  occurs together with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
 
-In terms of the cost boundaries, inequality \ref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$, and if $T_A>T_B$ then that suffices for fixation of cooperation.
-If $T_B>T_A$ then $\gamma_2(\alpha=1)<0$ and again, (\ref{eq:vert_hori_alpha1}) is sufficient for increase in the frequency of $A$.
-Inequality \ref{eq:vert_hori_alpha1} can be written as
+In terms of the cost boundaries, inequality~\ref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$, and if $T_A>T_B$ then that suffices for fixation of cooperation.
+If $T_B>T_A$ then $\gamma_2(\alpha=1)<0$ and again, inequality~\ref{eq:vert_hori_alpha1} is sufficient for increase in the frequency of $A$.
+Inequality~\ref{eq:vert_hori_alpha1} can be written as
 \begin{equation} \label{eq:vert_hori_alpha1_effective}
@@
 which provides an interesting interpretation for the success of cooperation. 
-In the interaction between a cooperator and a defector.
-$(1-c)(1-T_B)$ is the probability that the cooperator remains cooperative and also reproduces. 
+In the interaction between a cooperator and a defector $(1-c)(1-T_B)$ is the probability that the cooperator remains cooperative and also reproduces. 
 Therefore, $1 - (1-c)(1-T_B)$ is the probability that either the cooperator becomes a defector, or that it fails to reproduce.
-This is the effective cost for cooperation from this interaction, while
-$(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces, which
- is the effective benefit for cooperation from this interaction.
-Thus inequality (\ref{eq:vert_hori_alpha1}) entails that cooperation can evolve if the effective cost for cooperation is less than the effective benefit.
+This is the effective cost for cooperation from this interaction, while $(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces, which is the effective benefit for cooperation from this interaction.
+Thus inequality~\ref{eq:vert_hori_alpha1} entails that cooperation can evolve if the effective cost for cooperation is less than the effective benefit.
 
-\begin{figure}[htb]
-  \centering
-    \includegraphics[scale=0.75]{figure3a.pdf}
-%    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
-  %  \label{fig:results_a}
-    \includegraphics[scale=0.75]{figure3b.pdf}
-%    \caption{$v=1$, $\alpha = 0$}
- %   \label{fig:results_b}
-    \includegraphics[scale=0.75]{figure3c.pdf}
-%    \caption{$v=0$}
-%  \label{fig:results}
-  \caption{
-  \textbf{Numerical results for cultural evolution of cooperation.}
-  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p$, the frequency of adults with cooperative phenotype $A$.
-  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue), and stable coexistence of cooperators and defectors (orange).
-  Parameters: (a) $v=1$, $T_A=T_B=T$, $\alpha \neq 0$; (b) $v=1$, $\alpha = 0$; (c) $v=0$.
-  % TODO add all parameters.
-  % TODO remove legends, increase fonts, explain in caption instead of legend.
-  }
-  \label{fig:results}
-\end{figure}
+Given the previous two corollaries for no assortment and perfect assortment ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of assortment on the evolution of cooperation.
+We denote the assortment boundaries by
+\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting}
+  a_1 = \frac{c(1-T_B)-(1+b)(T_A-T_B)}{b\cdot T_B}, \quad
+  a_2 = \frac{c(1-T_B)-(T_A-T_B)}{b\cdot T_A}.
+\end{aligned}\end{equation}
+Applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we have the following corollary.
+\\
+
+\begin{corollary}[Intermediate assortment of transmission and cooperation]
+The cooperative phenotype will increase from rarity if the assortment is high enough, or specifically if
+  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
+    \begin{aligned}
+    T_A > T_B &\;\; \text{and} \;\; a_2 < \alpha, \quad \text{or} \\
+    T_A < T_B &\;\; \text{and} \;\; a_1 < \alpha \,.
+    \end{aligned}
+    \end{equation} 
+\end{corollary}
+
+\autoref{fig:results2}c demonstrates these conditions.
+With horizontal bias for cooperation ($T_A>T_B$; positive x-axis) cooperation fixes in the population from any initial positive frequency (green) if $\alpha$ (y-axis) is above the orange line ($a_1$), or if initially present at a high enough frequency (blue) if $\alpha$ is above the blue line ($a_2$).
+With horizontal bias for defection ($T_B>T_A$; negative x-axis) cooperation fixes if $alpha$ is above the blue line ($a_2$), but can be maintained in coexistence with defection (yellow) if $\alpha$ is above the orange line ($a_1$).
+Without horizontal bias ($T_A=T_B$) fixation occurs if $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\autoref{}).
 
@@
 
-%There is an ongoing debate about the extent to which kin selection explains the evolution of cooperation and altruism.
-%For example, it has been suggested that it can explain the cooperative behavior of worker castes of eusocial insects like the honey bee. % TODO REF
-%The most significant argument against kin selection is that in some cases cooperation among unrelated individuals appears to have evolved~\citep{wilson2005kin}.
-%Therefore, other theories have been develop to explain the evolution of cooperation and altruism.
+\citet{Eshel1982} showed that with assortative meeting, namely, a probability $m$ that individuals interact  within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
+Our results highlight another possibility for assortatment, namely, individuals interacting at rate $\alpha$ with their cultural partners, resulting in horizontal transmission.
+We show that high levels of assortment  significantly increase the potential for evolution of cooperation.
+With a high enough $\alpha$, cooperation can increase when initially rare (although it will not fix) even when there is horizontal bias against cooperation ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$, see Result~\autoref{result:vert_hori})
 
-%\emph{Reciprocity} entails that repeated interactions or individual recognition are key components of the evolution of cooperation.
-In \emph{direct reciprocity} there are repeated encounters between the same two individuals, and at every encounter each individual has a choice between cooperation and defection.
-Hence, it may eventually pay off to cooperate if it may cause your partner to cooperate in the future.
-%This game-theoretic framework, known as the \emph{repeated prisoner's dilemma}, 
-%%A well known strategy to play this game is called  'tit-for-tat'.
-This strategy always starts with a cooperation, then it does whatever the other player has done in the previous round: a cooperation for a cooperation, a defection for a defection.
-There a unlimited number of possible strategies to play this game.
-However,
-%can only lead to the evolution of cooperation if the cost is less than the benefit $b$ times the probability of another encounter between the same two individuals, $w$, 
-%%TODO Referencess
-%\begin{equation} \label{eq:reciprocity}
-%c < b \cdot w.
-%\end{equation}
-%
-%Direct reciprocity assumes that both players are in a position to cooperate, but it can not explain cooperation in asymmetric interactions such as human philanthropy. \\
-%\emph{Indirect reciprocity} has also been suggested to explain the evolution of cooperation.
-%\citet{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of currency. 
-%%TODO: refs
-%The currency that ``fuels the engines'' of indirect reciprocity is \emph{reputation}. 
-%However, reciprocity assumes repeated interactions and therefore has difficulty in explaining the evolution of cooperation if  interactions are not repeated. 
-%
-%\emph{Group selection} theory posits that cooperation is favored because it imparts an advantage to the whole group, if selection acts at the group level in addition to the individual level.
-A common model for group selection divides the population into groups in which there are cooperators that help  other group members and defectors that do not.
-% TODO add reference
-%Individuals reproduce proportionally to their fitness, and offspring are added to the same group as their parents.
-%If a group reaches a certain size it can split to two groups, so groups that grow faster will split more often.
-%Groups with cooperators grow faster than groups without cooperators, and
-%cooperation can evolve in this model when the cost $c$ is less than the benefit $b$ times the ratio between the  the number of groups $m$ and the sum of $m$ and the maximum group size $n$,
-%\begin{equation} \label{eq:groupselection}
-%c < b \cdot \frac{m}{m+n} .
-%\end{equation}
-%
-%Group selection has been criticized by biologists who advocate a gene-centered view of evolution. % TODO ref
-%It has also been criticized because for cooperation to take over the population it must have higher fitness than defection, while under group selection theory the fitness of cooperators at the individual level is lower than the fitness of defectors.
-Thus a trait with a lower fitness taking over the population is a contradiction %TODO ref.
-%\citet{eldakar2011eight} reject this argument, claiming that it is a tautology and does not qualify as an argument against group selection.
-The distinction between individual and group selection requires a comparison of fitness differentials within and between groups in a multi-group population, and when a trait  evolves by group selection, despite having lower fitness within a group, that group might have higher average fitness in competition with other groups, all things considered.
-% TODO cite Simpsons' paradox?
-
-\citet{Eshel1982}  showed that with assortative meeting, namely, a probability $m$ that individuals interact  within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
-Our results highlight another possibility for assortative meeting, namely, individuals interacting at rate $\alpha$ with their cultural partners, resulting in horizontal transmission.
-We show that high levels of assortative meeting  significantly increase the potential for evolution of cooperation.
-With a high enough $\alpha$, cooperation can increase when initially rare (although it will not fix) even when there is horizontal bias against cooperation ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$, see Result~\autoref{result:vert_hori})
+\citet{feldman1985gene} studied the dynamics of an altruistic phenotype with vertical cultural transmission and a gene that modifies the transmission of the phenotype.
+Their results are very sensitive to this genetic modification: without it, the conditions for invasion of the altruistic phenotype reduce to Hamilton's rule.
+Further work is needed to include such genetic modification of cultural transmission to our model.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\pagebreak
+\pagebreak
 % Acknowledgements
@@
 
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{table}[h]
+\section*{Figures}
+%%% Figure: model illustration
+\begin{figure}[thb]
   \centering
-\begin{tabular}{lll}
-\toprule
-           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
-$\phi_1=A$ & $1+b-c$ & $1-c$ \\
-$\phi_1=B$ & $1+b$   & $1$
-\\ \bottomrule
-\end{tabular}
-\caption{\textbf{Payoff matrix for prisoner's dilemma.}
-The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
-$b>c>0$.
+  \includegraphics[scale=1]{figure1.pdf}
+  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
+  \label{fig:horizontal}
+\end{figure}
+
+%%% Figure: coexistence map
+\begin{figure}[htb]
+\centering
+\includegraphics{coexistence.pdf}
+\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
+The line $\hat{p}'=\hat{p}$ is shown as a dashed black line.
+The curve and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle). 
+When the curve is above the dashed line ($\hat{p}<\hat{p}^*$) the frequency $\hat{p}$increases towards $\hat{p}^*$.
+When the curve is below the dashed line ($\hat{p}>\hat{p}^*$) the frequency $\hat{p}$ decreases towards $\hat{p}^*$.
+% TODO add the actual values of all parameters.
+% TODO add reference to equation
 }
-\label{table:prisoner_payoff}
-\end{table}
+\label{fig:coexistence}
+\end{figure}
 
-\newpage
+%%% Figure: Conditions for fixation
 
-\begin{table}[]
-\begin{tabular}{@{}llllll@{}}
-\toprule
-\multirow{2}{*}{Phenotype $\phi_1$} &
-  \multirow{2}{*}{Phenotype $\phi_2$} &
-  \multirow{2}{*}{Frequency} &
-  \multirow{2}{*}{Fitness of $\phi_1$} &
-  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
-    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
-$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
-$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
-\end{tabular}
-\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
-\label{table:interactions}
-\end{table}
-%%%
+\begin{figure}[htb]
+  \centering
+  % TODO for some reason figs a and b have a lot of white space on their right side
+    \includegraphics[scale=0.75]{figure2a.pdf}
+
+    \includegraphics[scale=0.75]{figure2b.pdf}
+
+    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
+    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
+The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions (blue), and stable coexistence of cooperation and defection (yellow).
+In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
+(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines.
+(\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
+Here, $b=1.3$, $T_A=0.4$.
+  % TODO what is c in (3) and alpha in (1) and (2)??
+  % TODO missing text descriptions of conditions on (3)
+  % TODO change lines from blue and orange to black solid and black dashed, and make them a bit wider
+  % TODO I think you were right: in the figure we should call it stable coexistence and unstable coexistence.
+  	}
+    \label{fig:results2}
+\end{figure}
+
+%%% Figure: frequency dynamics
+\begin{figure}[htb]
+  \centering
+    \includegraphics[scale=0.75]{figure3a.pdf}
+    \includegraphics[scale=0.75]{figure3b.pdf}
+    \includegraphics[scale=0.75]{figure3c.pdf}
+  \caption{
+  \textbf{Dynamics of the frequency of cooperation.}
+  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
+  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
+  (a) $v=1$, $T_A=T_B=T$, $\alpha \neq 0$; (b) $v=1$, $\alpha = 0$; (c) $v=0$.
+  % TODO write all parameter values. T=? alpha=?
+  % TODO set colors the same as fig 3.
+  % TODO remove legends, increase fonts, explain in caption instead of legend.
+  }
+  \label{fig:results}
+\end{figure}
+
 %%%

### 2020-08-19 ms/main.tex
revised result 2 and 3 to be more similar in structure

@@
 
-We summarize these findings in the following result and corollaries.\\
-%TODO:format like result 3
-\begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
-Without oblique transmission ($v=1$), fixation, extinction, and coexistence of both phenotypes are possible.
-\end{result}
-
-Let the initial frequency of the alternative phenotype be $\tilde{p}_0$ and denote the cost boundaries by
+We define the initial frequency of the cooperator phenotype among parents, $\tilde{p}_0$, and the \emph{cost boundaries},
 \begin{equation} \label{eq:cost_boundaries}
@@
 \end{equation}
-Then, applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes which are illustrated in \autoref{fig:results2}:
+Then, applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes in following result and corollaries.
+\\
+
+\begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
+With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of a cooperator phenotype will follow one of the following scenarios:
+
 %\begin{enumerate} % p* version
@@
 \begin{enumerate} % gamma version
-\item Fixation of cooperation,
-	if $T_A>T_B$ and $c<\gamma_1$; or
-	if $T_A>T_B$ and $\gamma_1<c<\gamma_2$ and $\tilde{p}_0>\tilde{p}^*$; or
-	if $T_A<T_B$ and $c<\gamma_2$.
-\item Fixation of defection,
-	if $T_A>T_B$ and $\gamma_2<c$; or
-	if $T_A>T_B$ and $\gamma_1<c<\gamma_2$ and $\tilde{p}_0<\tilde{p}^*$; or
-	if $T_A<T_B$ and $\gamma_1<c$.
-\item Coexistence of both phenotypes at $\tilde{p}^*$, 
-	if $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
+\item \emph{Fixation of cooperation}:
+	if \emph{(i)} $T=T_A=T_B$ and $c < b \cdot \frac{\alpha T}{1-T}$; or
+	if \emph{(ii)} $T_A>T_B$ and $c<\gamma_1$; or
+	if \emph{(iii)} $T_A<T_B$ and $c<\gamma_2$.
+\item \emph{Fixation of defection}:
+	if \emph{(iv)} $T=T_A=T_B$ and $c > b \cdot \frac{\alpha T}{1-T}$; or
+	if \emph{(vi)} $T_A>T_B$ and $\gamma_2<c$; or
+	if \emph{(vi)} $T_A<T_B$ and $\gamma_1<c$.
+\item \emph{Fixation of either phenotype depending on initial frequency}: 
+	if \emph{(vii)} $T_A>T_B$ and $\gamma_1<c<\gamma_2$.
+\item \emph{Coexistence of both phenotypes at $\tilde{p}^*$}:
+	if \emph{(viii)} $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
 \end{enumerate}
+\end{result}
 
+These conditions are illustrated in \autoref{fig:results2}b-c.
 Note that cooperation and defection can coexist stably if there is horizontal bias for defection and the cost of cooperation is large but not too large.
@@
 With horizontal bias for defection ($T_B>T_A$; negative x-axis) cooperation fixes if $alpha$ is above the blue line ($a_2$), but can be maintained in coexistence with defection (yellow) if $\alpha$ is above the orange line ($a_1$).
-Without horizontal bias ($T_A=T_B$) fixation occurs if $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\autoref{}).
+Without horizontal bias ($T_A=T_B$) fixation occurs if $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}).
 
@@
 The following result summarizes these findings.
+\\
 
 \begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-The cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the horizontal transmission bias $T_A-T_B$ and the coefficients $\beta_1$ and $\beta_3$:
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios:
 \begin{enumerate}
@@
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-if \emph{(vi)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
-\item \emph{Fixation of either phenotype depending on initial frequency}: if \emph{(vii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
+	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+\item \emph{Fixation of either phenotype depending on initial frequency}:
+	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
 \end{enumerate}

### 2020-08-19 ms/main.tex
started writing result 3 in terms of cost boundaries

@@
 \begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
-With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of a cooperator phenotype will follow one of the following scenarios:
+With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}):
 
@@
 
-The following result summarizes these findings.
+We redefine the cost boundaries,
+the \emph{cost boundaries},
+\begin{equation} \label{eq:cost_boundaries_v}
+\begin{aligned}
+\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
+\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}.
+\end{aligned}
+\end{equation}
+The following result summarizes the possible outcomes.
 \\
@@
 \begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios:
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}):
+
+% in beta
+%\begin{enumerate}
+%\item \emph{Fixation of cooperation}: 
+%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
+%	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
+%	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
+%\item \emph{Fixation of the defection}: 
+%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
+%	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+%	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
+%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
+%	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+%\item \emph{Fixation of either phenotype depending on initial frequency}:
+%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
+%\end{enumerate}
+
+% in gamma
 \begin{enumerate}
@@
 	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
-	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
+	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
+	if \emph{(iiia)} $T_A<T_B$ and $v>\frac{T_B-T_A}{1-T_A}$ and $c < \hat\gamma_2$; or
+	if \emph{(iiib)} $T_A<T_B$ and $v<\frac{T_B-T_A}{1-T_A}$ and $c > \hat\gamma_2$.
 \item \emph{Fixation of the defection}: 

### 2020-08-19 ms/main.tex
vertical threshold

@@
 \hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
-\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}.
+\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
 \end{aligned}
 \end{equation}
+and define a vertical transmission threshold,
+\begin{equation} \label{eq:v_threshold}
+\hat v = \frac{T_B - T_A)}{1-T_A} \,.
+\end{equation}
+
 The following result summarizes the possible outcomes.
@@
 \begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}):
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
 
@@
 	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
-	if \emph{(iiia)} $T_A<T_B$ and $v>\frac{T_B-T_A}{1-T_A}$ and $c < \hat\gamma_2$; or
-	if \emph{(iiib)} $T_A<T_B$ and $v<\frac{T_B-T_A}{1-T_A}$ and $c > \hat\gamma_2$.
+	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
+	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $c > \hat\gamma_2$.
 \item \emph{Fixation of the defection}: 

### 2020-08-22 ms/main.tex
improve figures 2-3

@@
 \centering
-\includegraphics{coexistence.pdf}
-\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
-The line $\hat{p}'=\hat{p}$ is shown as a dashed black line.
-The curve and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle). 
-When the curve is above the dashed line ($\hat{p}<\hat{p}^*$) the frequency $\hat{p}$increases towards $\hat{p}^*$.
-When the curve is below the dashed line ($\hat{p}>\hat{p}^*$) the frequency $\hat{p}$ decreases towards $\hat{p}^*$.
-% TODO add the actual values of all parameters.
-% TODO add reference to equation
-}
+\includegraphics{coexistence_result2.pdf}
+\caption{\textbf{Stable and unstable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
+The line $\tilde{p}'=\tilde{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
+When the curves are above the dashed line ($\tilde{p}<\tilde{p}^*$) the frequency $\tilde{p}$increases towards $\tilde{p}^*$.
+When the curves are below the dashed line ($\tilde{p}>\tilde{p}^*$) the frequency $\tilde{p}$ decreases towards $\tilde{p}^*$.
+The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $\alpha = 0.45$.
+For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
+The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$.
+For those values we can that $\gamma_1<c<\gamma_2$}
 \label{fig:coexistence}
@@
   % TODO for some reason figs a and b have a lot of white space on their right side
-    \includegraphics[scale=0.75]{figure2a.pdf}
+    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}
 
-    \includegraphics[scale=0.75]{figure2b.pdf}
+    \includegraphics[scale=0.75]{boundiries_alpha0.pdf}
 
@@
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
-The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions (blue), and stable coexistence of cooperation and defection (yellow).
+The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions - unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
 In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
@@
 (\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
-Here, $b=1.3$, $T_A=0.4$.
-  % TODO what is c in (3) and alpha in (1) and (2)??
+Here, $b=1.3$, $T_A=0.4$. In figure (\textbf{a})~$\alpha = 0.7$ and in figure (\textbf{b})~$\alpha = 0$. In figure (\textbf{c})~$c = 0.35$.
   % TODO missing text descriptions of conditions on (3)
-  % TODO change lines from blue and orange to black solid and black dashed, and make them a bit wider
-  % TODO I think you were right: in the figure we should call it stable coexistence and unstable coexistence.
   	}
@@
   \centering
-    \includegraphics[scale=0.75]{figure3a.pdf}
-    \includegraphics[scale=0.75]{figure3b.pdf}
-    \includegraphics[scale=0.75]{figure3c.pdf}
+    \includegraphics[scale=0.7]{figure3a.pdf}
+    \includegraphics[scale=0.7]{figure3b.pdf}
+    \includegraphics[scale=0.7]{figure3c.pdf}
   \caption{

### 2020-08-22 ms/main.tex
Add figure 4

@@
 Note that cooperation and defection can coexist stably if there is horizontal bias for defection and the cost of cooperation is large but not too large.
-The recursion dynamic for this case is illustrated in \autoref{fig:coexistence}.
+The recursion dynamic for this case is illustrated in \autoref{fig:coexistence_without_oblique}.
 
@@
 
-%%% Figure: coexistence map
+%%% Figure: coexistence map - without oblique transmission
 \begin{figure}[htb]
 \centering
-\includegraphics{coexistence_result2.pdf}
-\caption{\textbf{Stable and unstable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
-The line $\tilde{p}'=\tilde{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
+\includegraphics{coexistence_without_oblique.pdf}
+\caption{\textbf{Stable and unstable coexistence between cooperation and defection - with oblique transmission.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
+The line $\tilde{p}'=\tilde{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\tilde{p}^*$ (black circle).
 When the curves are above the dashed line ($\tilde{p}<\tilde{p}^*$) the frequency $\tilde{p}$increases towards $\tilde{p}^*$.
@@
 The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $\alpha = 0.45$.
-For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
-The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$.
-For those values we can that $\gamma_1<c<\gamma_2$}
-\label{fig:coexistence}
+For those values we get that $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients})
+The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$. For those values we can that $\beta_3<\beta_1$}
+\label{fig:coexistence_without_oblique}
 \end{figure}
@@
 
+%%% Figure: coexistence map - without oblique transmission
+\begin{figure}[htb]
+  \centering
+  \includegraphics{coexistence_with_oblique.pdf}
+  \caption{\textbf{Stable and unstable coexistence between cooperation and defection - without oblique transmission.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$.
+  The line $\hat{p}'=\hat{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
+  When the curves are above the dashed line ($\hat{p}<\hat{p}^*$) the frequency $\hat{p}$increases towards $\hat{p}^*$.
+  When the curves are below the dashed line ($\hat{p}>\hat{p}^*$) the frequency $\hat{p}$ decreases towards $\hat{p}^*$.
+  The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$.
+For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
+  The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$.
+For those values we can that $\gamma_1<c<\gamma_2$}
+  \label{fig:coexistence_with_oblique}
+  \end{figure}
+
 %%% Figure: frequency dynamics

### 2020-08-22 ms/main.tex
fix figure 4

@@
 \includegraphics{coexistence_without_oblique.pdf}
-\caption{\textbf{Stable and unstable coexistence between cooperation and defection - with oblique transmission.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
+\caption{\textbf{Stable and unstable coexistence between cooperation and defection - without oblique transmission.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
 The line $\tilde{p}'=\tilde{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\tilde{p}^*$ (black circle).
@@
 The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $\alpha = 0.45$.
-For those values we get that $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients})
-The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$. For those values we can that $\beta_3<\beta_1$}
+For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
+The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$.
+For those values we can that $\gamma_1<c<\gamma_2$}
 \label{fig:coexistence_without_oblique}
@@
   \includegraphics{coexistence_with_oblique.pdf}
-  \caption{\textbf{Stable and unstable coexistence between cooperation and defection - without oblique transmission.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$.
-  The line $\hat{p}'=\hat{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
+  \caption{\textbf{Stable coexistence between cooperation and defection - with oblique transmission.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$.
+  The line $\hat{p}'=\hat{p}$ is shown as a dashed black line. The curve and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
   When the curves are above the dashed line ($\hat{p}<\hat{p}^*$) the frequency $\hat{p}$increases towards $\hat{p}^*$.
   When the curves are below the dashed line ($\hat{p}>\hat{p}^*$) the frequency $\hat{p}$ decreases towards $\hat{p}^*$.
-  The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$.
-For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
-  The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$.
-For those values we can that $\gamma_1<c<\gamma_2$}
+  The curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, $v=0.4$.
+For those values we get that $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients})}
   \label{fig:coexistence_with_oblique}

### 2020-08-22 ms/main.tex
Result3: present result3 as boundries

@@
 \begin{aligned}
-\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
+\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
 \hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
@@
 \begin{equation} \label{eq:v_threshold}
-\hat v = \frac{T_B - T_A)}{1-T_A} \,.
+\hat v = \frac{T_B - T_A}{1-T_A} \,.
 \end{equation}
@@
 	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
-	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
+  if \emph{(va)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$ and $v>\hat{v}$; or 
+  if \emph{(vb)} $T_A>T_B$ and $ c > \hat{\gamma_1} $ and $ c > \hat{\gamma_2}$ and $v<\hat{v}$; or 
+	if \emph{(vi)} $T_A<T_B$ and $c>\hat{\gamma_1}$.
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat{\gamma_1}<c<\hat{\gamma_2}$; or
+  if \emph{viib} $T_A < T_B$ and $v>\hat{v}$ and $c>\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
 \item \emph{Fixation of either phenotype depending on initial frequency}:
-	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
+  if \emph{(viiia)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$; or
+  if \emph{(viiin)}  $T_A>T_B$ and $c < \hat{\gamma_2}$ and $v<\hat{v}$.
 \end{enumerate}

### 2020-08-22 ms/main.tex
minor fix

@@
   if \emph{(viiia)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$; or
-  if \emph{(viiin)}  $T_A>T_B$ and $c < \hat{\gamma_2}$ and $v<\hat{v}$.
+  if \emph{(viiib)}  $T_A>T_B$ and $c < \hat{\gamma_2}$ and $v<\hat{v}$.
 \end{enumerate}

### 2020-08-23 ms/main.tex
revise introduction

@@
 Evolution of cooperative behavior remains an important conundrum in evolutionary biology.
-Since the work of  \citet{hamilton1964genetical} and \citet{axelrod1981evolution}, theories for the evolution of cooperative and altruistic behaviors have been intertwined often under the rubric of kin selection.
+Since the work of  \citet{hamilton1964genetical} and \citet{axelrod1981evolution}, theories for the evolution of cooperative and altruistic behaviors have been intertwined often under the rubric of \emph{kin selection}.
 
-\emph{Kin selection theory} posits that natural selection is more likely to favor cooperation between more closely related individuals.
-The importance of relatedness to the evolution of cooperation and altruism was shown by~\citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
+Kin selection theory posits that natural selection is more likely to favor cooperation between more closely related individuals.
+The importance of relatedness to the evolution of cooperation and altruism was demonstrated by \citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
 This relatedness coefficient $r$ measures a probability that an allele sampled from the cooperator is identical by descent to one at the same locus in the recipient.
@@
 
-\citet{Eshel1982} studied a related model for the evolution of cooperative behavior under vertical transmission.
+\citet{Eshel1982} studied a related model for the evolution of cooperative behavior.
 Their model included \emph{assortative meeting}, or non-random encounters, where a fraction $m$ of individuals in the population each interact with an individual of the same phenotype, and a fraction $1-m$ interacts  with a randomly chosen individual.
@@
 \end{equation}
+In this case $\varphi$ takes the role of the relatedness $r$ in \autoref{eq:hamilton_rule}, but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
 
-\emph{Non-vertical cultural transmission} may be either viewed as horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs  to  offspring from the generation to which their parents belong.
+Non-vertical cultural transmission may be either viewed as horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs  to  offspring from the generation to which their parents belong.
 Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-\citet{lewin2017microbes} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior.
+\citet{lewin2017microbes} and \citet{lewin2020rock–paper–scissors} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior.
 Some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
+Importantly, their results depended on non-vertical transmission of the cooperation-determining microbes.
 
-% TODO
-We hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation, and 
-to test this hypothesis we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
+We therefore hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation.
+To test this hypothesis we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
+That is, if there exists assortative meeting in the choice of the social interaction partner, or assortative learning in choice of the cultural transmission partner.
 For example, if an individual interacts with a cooperative individual, it might learn that cooperation is an advantageous behavior and will be cooperative in the future. 

### 2020-08-28 ms/main.tex
Result 1 describe what happen if T_A = T_B

@@
 Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-\citet{lewin2017microbes} and \citet{lewin2020rock–paper–scissors} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior.
+\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior.
 Some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
@@
 
+If $T_A = T_B$, then $p'=p$ and the population is static.
 Therefore, in the absence of vertical transmission, selection plays no role in the evolution of cooperation.

### 2020-08-29 ms/main.tex
Fix result 3

@@
 	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-  if \emph{(va)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$ and $v>\hat{v}$; or 
-  if \emph{(vb)} $T_A>T_B$ and $ c > \hat{\gamma_1} $ and $ c > \hat{\gamma_2}$ and $v<\hat{v}$; or 
+  if \emph{(v)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$; or 
 	if \emph{(vi)} $T_A<T_B$ and $c>\hat{\gamma_1}$.
@@
 \item \emph{Fixation of either phenotype depending on initial frequency}:
-  if \emph{(viiia)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$; or
-  if \emph{(viiib)}  $T_A>T_B$ and $c < \hat{\gamma_2}$ and $v<\hat{v}$.
+  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$.
 \end{enumerate}

### 2020-08-29 ms/main.tex
Add woodcock2006significance to the discussion

@@
   if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat{\gamma_1}<c<\hat{\gamma_2}$; or
-  if \emph{viib} $T_A < T_B$ and $v>\hat{v}$ and $c>\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
+  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c>\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
 \item \emph{Fixation of either phenotype depending on initial frequency}:
@@
 Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
-Microbes can be transmitted \emph{horizontally} from one host to another during host interactions, and following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host, even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}.
+Microbes can be transmitted \emph{horizontally} from one host to another during host interactions, and following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host,
+even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}. 
 Microbes can also be transferred vertically, from parent to offspring, and % yr: cite 10.1126/science.aat7164
@@
 Further work is needed to include such genetic modification of cultural transmission to our model.
+
+\citet{woodcock2006significance} showed the importance of non-vertical transmission for the evolution of cooperation.
+In their model the individuals interact according to standard prisoner dilemma game.
+However, they do not link between interaction and transmission.
+In terms of our model they have choosen the assortative meeting coefficient $\alpha$ to be zero.
+Our results are more general since it shows the importance of assortative meeting for the evolution of cooperation.
 

### 2020-08-29 ms/main.tex
revised figure captions

@@
 \citet{Eshel1982} showed that with assortative meeting, namely, a probability $m$ that individuals interact  within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
-Our results highlight another possibility for assortatment, namely, individuals interacting at rate $\alpha$ with their cultural partners, resulting in horizontal transmission.
+Our results highlight another possibility for assortment, namely, individuals interacting at rate $\alpha$ with their cultural partners, resulting in horizontal transmission.
 We show that high levels of assortment  significantly increase the potential for evolution of cooperation.
@@
 However, they do not link between interaction and transmission.
-In terms of our model they have choosen the assortative meeting coefficient $\alpha$ to be zero.
+In terms of our model they have chosen the assortative meeting coefficient $\alpha$ to be zero.
 Our results are more general since it shows the importance of assortative meeting for the evolution of cooperation.
@@
   \includegraphics[scale=1]{figure1.pdf}
-  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
+  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
   \label{fig:horizontal}
@@
 \includegraphics{coexistence_without_oblique.pdf}
-\caption{\textbf{Stable and unstable coexistence between cooperation and defection - without oblique transmission.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
-The line $\tilde{p}'=\tilde{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\tilde{p}^*$ (black circle).
-When the curves are above the dashed line ($\tilde{p}<\tilde{p}^*$) the frequency $\tilde{p}$increases towards $\tilde{p}^*$.
-When the curves are below the dashed line ($\tilde{p}>\tilde{p}^*$) the frequency $\tilde{p}$ decreases towards $\tilde{p}^*$.
-The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $\alpha = 0.45$.
-For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
-The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$.
-For those values we can that $\gamma_1<c<\gamma_2$}
+\caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
+  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ vs. the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
+  The dashed black line is $\tilde{p}'=\tilde{p}$.
+  The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
+  When the curves are above the dashed line, $\tilde'{p}>\tilde{p}$, then $\tilde{p}$ increase.
+  When the curves are below the dashed line, $\tilde'{p}<\tilde{p}$, then $\tilde{p}$ decreases.
+  The yellow curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
+  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
+  In both cases there is no oblique transmission, $v=1$; see \autoref{fig:coexistence_with_oblique} for $v<1$.
+  }
 \label{fig:coexistence_without_oblique}
@@
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
-The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions - unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
+The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
 In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
@@
 (\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
-Here, $b=1.3$, $T_A=0.4$. In figure (\textbf{a})~$\alpha = 0.7$ and in figure (\textbf{b})~$\alpha = 0$. In figure (\textbf{c})~$c = 0.35$.
+Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0.7$.(\textbf{b})~$\alpha = 0$. (\textbf{c})~$c = 0.35$.
   % TODO missing text descriptions of conditions on (3)
@@
   \includegraphics{coexistence_with_oblique.pdf}
-  \caption{\textbf{Stable coexistence between cooperation and defection - with oblique transmission.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$.
-  The line $\hat{p}'=\hat{p}$ is shown as a dashed black line. The curve and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
-  When the curves are above the dashed line ($\hat{p}<\hat{p}^*$) the frequency $\hat{p}$increases towards $\hat{p}^*$.
-  When the curves are below the dashed line ($\hat{p}>\hat{p}^*$) the frequency $\hat{p}$ decreases towards $\hat{p}^*$.
-  The curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, $v=0.4$.
-For those values we get that $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients})}
+  \caption{\textbf{Stable coexistence between cooperation and defection with oblique transmission.}
+  The curve shows the frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ vs. the current generation $\hat{p}$ (\autoref{eq:horizontal}).
+  The dashed black line is $\hat{p}'=\hat{p}$.
+  The curve and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
+  When $\hat{p} < \hat{p}^*$ then the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
+  When $\hat{p} > \hat{p}^*$ then the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
+  Here,  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
+  }
   \label{fig:coexistence_with_oblique}

### 2020-08-30 ms/main.tex
draft for abstract

@@
 % Abstract
-%\begin{abstract}
-%\end{abstract}
+\begin{abstract}
+We construct models for the cultural evolution of cooperation in a well-mixed population with vertical, horizontal, and oblique transmission.
+Conditions are found for fixation of cooperation, fixation of defection, and stable coexistence between cooperation and defection, and comparisons are drawn with Hamilton's rule.
+A spatial model is constructed and its results are compared to the well-mixed model.
+We show that assortment between cooperation and horizontal transmission facilitates the evolution of cooperation and increases the population mean fitness. 
+% TODO what about oblique?
+\end{abstract}
 

### 2020-09-01 ms/main.tex
another fix to result 3

@@
 %\item \emph{Fixation of either phenotype depending on initial frequency}:
-%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
+%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1<0$.
 %\end{enumerate}
@@
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat{\gamma_1}<c<\hat{\gamma_2}$; or
-  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c>\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
+  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat{\gamma_1}$ and $c<\hat{\gamma_2}$; or
+  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
 \item \emph{Fixation of either phenotype depending on initial frequency}:
-  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$.
+  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $c > \hat{\gamma_1}$ and $v>\hat{v}$.
 \end{enumerate}

### 2020-09-01 ms/main.tex
Revisit figure 5 caption - add the values of the parameters and update the name of the figures files
Switch between figure 3a and figure 3b so we start with alpha = 0 and then move to alpha > 0
Fix figure 3 references

@@
 However, we show that under some conditions cooperation can evolve, and can even be maintained in stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
-We saw that it is likely to find configuration of parameters that results coexistence as can be seen in \autoref{fig:results2}a.
-In figure \autoref{fig:results2}a the yellow area in which coexistence occur has horizontal bias that favor defection ($T_B>T_A$) and the cost is relatively small.
+We saw that it is likely to find configuration of parameters that results coexistence as can be seen in \autoref{fig:results2}b.
+In figure \autoref{fig:results2}b the yellow area in which coexistence occur has horizontal bias that favor defection ($T_B>T_A$) and the cost is relatively small.
 
@@
 Further work is needed to include such genetic modification of cultural transmission to our model.
-
-\citet{woodcock2006significance} showed the importance of non-vertical transmission for the evolution of cooperation.
-In their model the individuals interact according to standard prisoner dilemma game.
-However, they do not link between interaction and transmission.
-In terms of our model they have chosen the assortative meeting coefficient $\alpha$ to be zero.
-Our results are more general since it shows the importance of assortative meeting for the evolution of cooperation.
 
@@
   % TODO for some reason figs a and b have a lot of white space on their right side
-    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}
 
     \includegraphics[scale=0.75]{boundiries_alpha0.pdf}
+
+    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}
 
@@
 (\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
-Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0.7$.(\textbf{b})~$\alpha = 0$. (\textbf{c})~$c = 0.35$.
+Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
   % TODO missing text descriptions of conditions on (3)
@@
   \centering
-    \includegraphics[scale=0.7]{figure3a.pdf}
-    \includegraphics[scale=0.7]{figure3b.pdf}
-    \includegraphics[scale=0.7]{figure3c.pdf}
+    \includegraphics[scale=0.7]{Time_Figure_Equal_Horizontal.pdf}
+    \includegraphics[scale=0.7]{Time_Figure_Only_Vertical_No_Alpha.pdf}
+    \includegraphics[scale=0.7]{Time_Figure_No_Vertical.pdf}
   \caption{
@@
   The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
-  (a) $v=1$, $T_A=T_B=T$, $\alpha \neq 0$; (b) $v=1$, $\alpha = 0$; (c) $v=0$.
+  \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
   % TODO write all parameter values. T=? alpha=?

### 2020-09-01 ms/main.tex
Move WOODCOCK 2006 paper to intro

@@
 Importantly, their results depended on non-vertical transmission of the cooperation-determining microbes.
+
+\citet{woodcock2006significance} showed the importance of non-vertical transmission for the evolution of cooperation.
+In their model the individuals interact according to standard prisoner dilemma game in which two individuals who interact can cooperate or not.
+In their work they do not link between interaction and transmission. Their model illustrates that it
+is possible to sustain altruistic behaviour at the level of culture for a significant
+period of time in the absence of any direct biological propensity favouring this
+behaviour.
 
@@
 
-\autoref{fig:results2}b illustrates these conditions, where
+\autoref{fig:results2}a illustrates these conditions, where
  the third equilibrium given by Eq.\ \ref{eq:vert_hori_equilibrium} becomes

### 2020-09-01 ms/main.tex
assortment highlighted; connected to Fletcher2009; revised intro and discussion; revealed a mistake in Result 3 gamma presentation

--- 2020-09-01 ms/main.tex
@@
 % Title page
-\title{Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation}
+\title{Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation}
 
@@
 We construct models for the cultural evolution of cooperation in a well-mixed population with vertical, horizontal, and oblique transmission.
-Conditions are found for fixation of cooperation, fixation of defection, and stable coexistence between cooperation and defection, and comparisons are drawn with Hamilton's rule.
-A spatial model is constructed and its results are compared to the well-mixed model.
-We show that assortment between cooperation and horizontal transmission facilitates the evolution of cooperation and increases the population mean fitness. 
+Conditions are found for fixation and coexistence of cooperation and defection.
+Comparisons are drawn with Hamilton's rule and the concepts of relatedness and assortment.
+%A spatial model is constructed and its results are compared to the well-mixed model.
+We show that assortment between cooperation and horizontal transmission facilitates the evolution of cooperation.
+% and increases the population mean fitness. 
 % TODO what about oblique?
@@
 where $b$ and $c$ are the benefit and cost of cooperation. 
-Here $m$ in \autoref{eq:eshel1982} takes the role of the relatedness $r$ in \autoref{eq:hamilton_rule}.
+Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness $r$ in inequality~\ref{eq:hamilton_rule}.
+
+The role of assortment in the evolution of altruism was studied by \citet{Fletcher2009assortment} in a \emph{public goods} game.
+They found that for altruism to evolve, cooperative individuals must experience more cooperation, on average, than defecting individuals, and ``thus, the evolution of altruism requires (positive) assortment between focal \emph{cooperative} players and cooperative acts in their interaction environment.''
+This condition can be summarized by \citep[eq.~2.3]{Fletcher2009assortment}
+\begin{equation} \label{eq:fletcher2009}
+c < b \cdot (e_C - e_D ) \,,
+\end{equation}
+where $e_C$ is the probability that a cooperator receives help, and $e_D$ is the probability that a defector receives help.\footnote{inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $e_C=r + p$, $e_D=p$ and $e_C=m + (1-m)p$, $e_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
 
@@
 \citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
-They showed that under a combination of genetic and vertical (parent-to-offspring) cultural transmission, the conditions for the initial increase of altruism entails a modification of Hamilton's rule in the cases of parent-to-offspring or sib-to-sib altruism.
-For example, if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
+They demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
 \begin{equation} \label{eq:feldman1985}
@@
 \end{equation}
-In this case $\varphi$ takes the role of the relatedness $r$ in \autoref{eq:hamilton_rule}, but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
+Here $\varphi$ takes the role of `relatedness' ($r$ in Eq.~\ref{eq:hamilton_rule}) or `assortment' ($m$ in Eq.~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
+This shows that under a combination of genetic and vertical (parent-to-offspring) cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (\autoref{eq:hamilton_rule}).
 
-Non-vertical cultural transmission may be either viewed as horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs  to  offspring from the generation to which their parents belong.
+Cultural transmission may be either viewed as vertical, horizontal or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
+from non-parental adults).
 Evolution under either of these transmission models can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior.
-Some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
-Importantly, their results depended on non-vertical transmission of the cooperation-determining microbes.
+Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior (the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by microbes that manipulate their host's behavior.)
+Specifically, some of the analyses by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
 
-We therefore hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation.
-To test this hypothesis we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
-That is, if there exists assortative meeting in the choice of the social interaction partner, or assortative learning in choice of the cultural transmission partner.
-For example, if an individual interacts with a cooperative individual, it might learn that cooperation is an advantageous behavior and will be cooperative in the future. 
+Here we hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation because it generates assortment between cooperative individuals.
+To test this hypothesis we construct a model in which behavioral changes can be mediated by cultural transmission that can occur during social interactions.
+For example, an individual that interacts with a cooperative individual might learn that cooperation is a valuable behavior, and will therefore teach its offspring to be cooperative. 
 Our cultural evolution models include both vertical and non-vertical transmission of cooperation, and we investigate these models using mathematical analysis and simulations.  
-Our results demonstrate that cultural transmission can facilitate the evolution of cooperation even when genetic transmission can not, and that treatment of cooperation as a cultural, rather than a genetic, trait can lead to a better understanding of its evolutionary dynamics.
+Our results demonstrate that cultural transmission can facilitate the evolution of cooperation even when genetic transmission can not because it facilitates the generation of assortment, and that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a better understanding of its evolutionary dynamics.
 
@@
 It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
-The assortment parameter $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
+The assortment rate $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
 Horizontal transmission is not always successful, as one partner may reject the other's phenotype.
@@
 \item \emph{Fixation of cooperation}:
-	if \emph{(i)} $T=T_A=T_B$ and $c < b \cdot \frac{\alpha T}{1-T}$; or
+	if \emph{(i)} $T=T_A=T_B$ and $c < b \cdot \alpha \frac{T}{1-T}$; or
 	if \emph{(ii)} $T_A>T_B$ and $c<\gamma_1$; or
@@
 \item \emph{Fixation of defection}:
-	if \emph{(iv)} $T=T_A=T_B$ and $c > b \cdot \frac{\alpha T}{1-T}$; or
+	if \emph{(iv)} $T=T_A=T_B$ and $c > b \cdot \alpha \frac{T}{1-T}$; or
 	if \emph{(vi)} $T_A>T_B$ and $\gamma_2<c$; or
@@
 In general, these conditions cannot be formulated in the form of Hamilton's rule ($c<b\cdot r$) due to the horizontal transmission bias $T_A-T_B$.
-Without horizontal transmission bias, i.e., with $T_A=T_B$, these conditions reduce to the following  form of Hamilton's rule.\\
+Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.\\
 
@@
 \label{eq:equal_transmission}
-c < b \cdot \frac{\alpha T}{1-T}.
+c < b \cdot \alpha \frac{T}{1-T}.
 \end{equation}
 \end{corollary}
-Inequality \ref{eq:equal_transmission} is obtained by setting $T_A=T_B$ in inequality \ref{eq:vert_hori_global_condition} and can be interpreted as a version of Hamilton's rule (inequality \ref{eq:hamilton_rule}), where $\alpha T/(1-T)$ can be regarded as the `effective relatedness'.
+Inequality \ref{eq:equal_transmission} is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:vert_hori_global_condition} and can be interpreted as a version of Hamilton's rule (inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the `effective relatedness' or `effective assortment', respectively.
 \autoref{fig:results}a demonstrates this condition. 
@@
 \begin{corollary}[No assortment of transmission and cooperation]
-If $\alpha=0$ and there is horizontal bias for cooperation ($T_A>T_B$) and
-(1) the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; or
-(2) the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
+Without assortment ($\alpha=0$) and with horizontal bias for cooperation ($T_A>T_B$), then 
+(1) if the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; 
+(2) if the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
 \end{corollary}
@@
 \begin{corollary}[Perfect assortment of transmission and cooperation]
-When $\alpha=1$, there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
+With perfect assortment ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
 The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
@@
 \end{corollary}
-With perfect assortment, in inequality \ref{eq:vert_hori_alpha1_condition_proof}
- horizontal transmission  occurs together with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
+With perfect assortment horizontal transmission always co-occurs with the cooperative interaction.
+The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
 
@@
 which provides an interesting interpretation for the success of cooperation. 
-In the interaction between a cooperator and a defector $(1-c)(1-T_B)$ is the probability that the cooperator remains cooperative and also reproduces. 
+In the interaction between a cooperator and a defector, $(1-c)(1-T_B)$ is the probability that the cooperator remains cooperative and also reproduces. 
 Therefore, $1 - (1-c)(1-T_B)$ is the probability that either the cooperator becomes a defector, or that it fails to reproduce.
-This is the effective cost for cooperation from this interaction, while $(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces, which is the effective benefit for cooperation from this interaction.
-Thus inequality~\ref{eq:vert_hori_alpha1} entails that cooperation can evolve if the effective cost for cooperation is less than the effective benefit.
+This is the \emph{effective cost of cooperation} from this interaction, while $(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces, which is the \emph{effective benefit of cooperation} from this interaction.
+Thus, inequality~\ref{eq:vert_hori_alpha1} entails that cooperation can evolve if the effective cost of cooperation is less than the effective benefit.
 
@@
 \begin{corollary}[Intermediate assortment of transmission and cooperation]
-The cooperative phenotype will increase from rarity if the assortment is high enough, or specifically if
+The cooperative phenotype will increase from rarity if the assortment rate is high enough, or specifically if
   \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
@@
 With horizontal bias for cooperation ($T_A>T_B$; positive x-axis) cooperation fixes in the population from any initial positive frequency (green) if $\alpha$ (y-axis) is above the orange line ($a_1$), or if initially present at a high enough frequency (blue) if $\alpha$ is above the blue line ($a_2$).
-With horizontal bias for defection ($T_B>T_A$; negative x-axis) cooperation fixes if $alpha$ is above the blue line ($a_2$), but can be maintained in coexistence with defection (yellow) if $\alpha$ is above the orange line ($a_1$).
-Without horizontal bias ($T_A=T_B$) fixation occurs if $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}).
+With horizontal bias for defection ($T_B>T_A$; negative x-axis) cooperation fixes if $\alpha$ is above the blue line ($a_2$), but can be maintained in coexistence with defection (yellow) if $\alpha$ is above the orange line ($a_1$).
+Without horizontal bias ($T_A=T_B$) fixation occurs if the assortment rate is high enough, $\alpha > \frac{c}{b} \cdot \frac{1-T}{T}$ (inequality~\ref{eq:equal_transmission}).
 
@@
 
-In this case $0<v<1$, and the recursion system is more complex,
+With both vertical and oblique transmission, $0<v<1$, the recursion system is more complex,
 and we focus on local rather than on global stability.
@@
 
-We redefine the cost boundaries,
-the \emph{cost boundaries},
-\begin{equation} \label{eq:cost_boundaries_v}
-\begin{aligned}
-\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
-\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
-\end{aligned}
-\end{equation}
-and define a vertical transmission threshold,
-\begin{equation} \label{eq:v_threshold}
-\hat v = \frac{T_B - T_A}{1-T_A} \,.
-\end{equation}
+% TODO uncomment when Result 3 in terms of c is fixed
+%We define new cost boundaries, $\hat\gamma_1$ and $\hat\gamma_2$,
+%\begin{equation} \label{eq:cost_boundaries_v}
+%\begin{aligned}
+%\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
+%\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
+%\end{aligned}
+%\end{equation}
+%and define a vertical transmission threshold,
+%\begin{equation} \label{eq:v_threshold}
+%\hat v = \frac{T_B - T_A}{1-T_A} \,.
+%\end{equation}
 
@@
 \begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the 
+polynomial coefficients $\beta_1$ and $\beta_3$ (\autoref{eq:polynomial_coefficients}):
+%cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
 
 % in beta
-%\begin{enumerate}
-%\item \emph{Fixation of cooperation}: 
-%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-%	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
-%	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
-%\item \emph{Fixation of the defection}: 
-%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-%	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
-%	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
-%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-%	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
-%\item \emph{Fixation of either phenotype depending on initial frequency}:
-%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1<0$.
-%\end{enumerate}
-
-% in gamma
 \begin{enumerate}
@@
 	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
-	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
-	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $c > \hat\gamma_2$.
+	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
+	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
 \item \emph{Fixation of the defection}: 
 	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-  if \emph{(v)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$; or 
-	if \emph{(vi)} $T_A<T_B$ and $c>\hat{\gamma_1}$.
+	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat{\gamma_1}$ and $c<\hat{\gamma_2}$; or
-  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
+	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
 \item \emph{Fixation of either phenotype depending on initial frequency}:
-  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $c > \hat{\gamma_1}$ and $v>\hat{v}$.
+	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
 \end{enumerate}
+
+% in gamma - TODO fix
+%\begin{enumerate}
+%\item \emph{Fixation of cooperation}: 
+%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
+%	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
+%	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
+%	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
+%\item \emph{Fixation of the defection}: 
+%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
+%  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$; or 
+%	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
+%\item \emph{Fixation of either phenotype depending on initial frequency}:
+%  if \emph{(viii)} $T_A>T_B$ and $v > \hat{v}$ and $\hat\gamma_2 < c$.
+%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
+%  if \emph{(vii.a)} $T_A < T_B$ and $v < \hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
+%  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 < c$.
+%\end{enumerate}
+
 \end{result}
+
+%This result illustrates the crucial role of vertical and oblique transmission: the same cost of cooperation $c$ can lead to remarkably different outcomes if the vertical transmission rate $v$ is below or above the threshold $\hat v$.
+% TODO example with figure
 
@@
 We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game.
-Under oblique and horizontal transmission, horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
-Under horizontal and vertical cultural transmission, cooperation, or defection can fix, or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the correlation between cooperation and transmission (Result~\autoref{result:vert_hori}).
-Under a combination of vertical, oblique, and horizontal transmission the dynamics are much more complicated.
-However, we show that under some conditions cooperation can evolve, and can even be maintained in stable coexistence with defection (Result~\autoref{result:vert_obli_hori}).
-We saw that it is likely to find configuration of parameters that results coexistence as can be seen in \autoref{fig:results2}a.
-In figure \autoref{fig:results2}a the yellow area in which coexistence occur has horizontal bias that favor defection ($T_B>T_A$) and the cost is relatively small.
+Under oblique and horizontal cultural transmission, a horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
+Under horizontal and vertical cultural transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the assortment between cooperation and transmission (Result~\autoref{result:vert_hori}).
+Under a combination of vertical, oblique, and horizontal transmission the dynamics are more complicated, but all outcomes can still occur, depending on parameter values (Result~\autoref{result:vert_obli_hori}).
+Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_B>T_A$) and the cost of cooperation and assortment ratio are intermediate (yellow areas \autoref{fig:results2}).
+% TODO figure for result 3
+% TODO something about v-hat
 
-This study was partially inspired by the work of \citet{lewin2017microbes}, 
-who hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the widespread occurrence of cooperative behavior.
+\citet{Eshel1982} showed that with assortative meeting, namely, a probability $m$ that individuals interact  within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
+\citet{Fletcher2009assortment} have further argued that a simple and general explanation for the evolution of altruism is given by assortment between individuals that carry an altruistic trait, and the altruistic behavior of others.
+They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate such assortment, and that one such major mechanism is population structure.
+Our results highlight another possibility for assortment, namely, individuals socially interacting at rate $\alpha$ with their horizontal transmission partners.
+This mechanism does not require population structure.
+Rather, it depends on the co-occurrence of two social processes: cultural transmission and cooperation.
+We show that high levels of assortment significantly increase the potential for evolution of cooperation (\autoref{fig:results2}).
+With enough assortment ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal bias against it ($T_B>T_A$, see Result~\autoref{result:vert_hori}).
+
+This study was partially inspired by the work of \citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors}, 
+who hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the evolution of cooperation.
 Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{dobson1988population,poulin2010parasite}.
@@
 even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}. 
-Microbes can also be transferred vertically, from parent to offspring, and % yr: cite 10.1126/science.aat7164
-a microbe that induces its host to cooperate with another host, and thereby increases the latter's fitness, will  increase its vertical transmission  from the receiving individual.
-Kin selection among microbes could therefore favor those that induce cooperative behavior in their hosts, thereby increasing the transmission of their microbial kin.
-
-\citet{Eshel1982} showed that with assortative meeting, namely, a probability $m$ that individuals interact  within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
-Our results highlight another possibility for assortment, namely, individuals interacting at rate $\alpha$ with their cultural partners, resulting in horizontal transmission.
-We show that high levels of assortment  significantly increase the potential for evolution of cooperation.
-With a high enough $\alpha$, cooperation can increase when initially rare (although it will not fix) even when there is horizontal bias against cooperation ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$, see Result~\autoref{result:vert_hori})
+Although this result can be described from a kin selection point-of-view, we are more interested in the assortment point-of-view:
+infection by behavior-determining microbes during interactions effectively generates assortment, as a cooperating donor can transmit to the recipient both the benefit of the cooperative behavior and behavior-determining microbe.
+Horizontal cultural transmission can similarly generate assortment between the cooperative phenotype and the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, which in our model occurs with rate $\alpha$.
+So, because non-vertical transmission can effectively generate assortment, we suggest a revision of the conclusion made by \citet{Fletcher2009assortment}\footnote{``what is necessary for the evolution of altruism is assortment between focal genotype and phenotypic help, rather than the assortment among genetic types often emphasized in kin selection theory.''}: what is necessary for the evolution of altruism is assortment between focal \emph{pheno-genotype} and phenotypic help.
 
@@
 
-\citet{woodcock2006significance} showed the importance of non-vertical transmission for the evolution of cooperation.
-In their model the individuals interact according to standard prisoner dilemma game.
-However, they do not link between interaction and transmission.
-In terms of our model they have chosen the assortative meeting coefficient $\alpha$ to be zero.
-Our results are more general since it shows the importance of assortative meeting for the evolution of cooperation.
-
-An important implication of our results is that cooperation can evolve even in a fully mixed population (i.e., in an unstructured population), without repeated interactions or individual recognition.
+An important implication of our results is that cooperation can evolve even without population structure, repeated interactions, or individual recognition.
 This highlights the potential importance of non-vertical cultural transmission for explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.

### 2020-09-01 ms/main.tex

@@
 Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior (the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by microbes that manipulate their host's behavior.)
-Specifically, some of the analyses by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
+Some of the analyses by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
+Importantly, \citet{woodcock2006significance} showed the significance of non-vertical transmission for the evolution of cooperation. In their model individuals play a prisoner's dilemma game.
+They do not link between interaction and transmission (i.e.
+no assortment), but their model demonstrates that it is possible to sustain altruistic behaviour via cultural transmission for a significant duration of time in the absence of any direct biological propensity favouring this behaviour.
 
-Here we hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation because it generates assortment between cooperative individuals.
-To test this hypothesis we construct a model in which behavioral changes can be mediated by cultural transmission that can occur during social interactions.
-For example, an individual that interacts with a cooperative individual might learn that cooperation is a valuable behavior, and will therefore teach its offspring to be cooperative. 
+We therefore hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation.
+To test this hypothesis we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
+That is, if there exists assortative meeting in the choice of the social interaction partner, or assortative learning in choice of the cultural transmission partner.
+For example, if an individual interacts with a cooperative individual, it might learn that cooperation is an advantageous behavior and will be cooperative in the future. 
 Our cultural evolution models include both vertical and non-vertical transmission of cooperation, and we investigate these models using mathematical analysis and simulations.  
@@
 
-% TODO uncomment when Result 3 in terms of c is fixed
-%We define new cost boundaries, $\hat\gamma_1$ and $\hat\gamma_2$,
-%\begin{equation} \label{eq:cost_boundaries_v}
-%\begin{aligned}
-%\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
-%\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
-%\end{aligned}
-%\end{equation}
-%and define a vertical transmission threshold,
-%\begin{equation} \label{eq:v_threshold}
-%\hat v = \frac{T_B - T_A}{1-T_A} \,.
-%\end{equation}
+We define new cost boundaries, $\hat\gamma_1$ and $\hat\gamma_2$,
+\begin{equation} \label{eq:cost_boundaries_v}
+\begin{aligned}
+\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
+\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
+\end{aligned}
+\end{equation}
+and define a vertical transmission threshold,
+\begin{equation} \label{eq:v_threshold}
+\hat v = \frac{T_B - T_A}{1-T_A} \,.
+\end{equation}
 
@@
 \begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the 
-polynomial coefficients $\beta_1$ and $\beta_3$ (\autoref{eq:polynomial_coefficients}):
-%cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
 
 % in beta
+%\begin{enumerate}
+%\item \emph{Fixation of cooperation}: 
+%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
+%	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
+%	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
+%\item \emph{Fixation of the defection}: 
+%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
+%	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+%	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
+%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
+%	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+%\item \emph{Fixation of either phenotype depending on initial frequency}:
+%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1<0$.
+%\end{enumerate}
+
+% in gamma
 \begin{enumerate}
@@
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat{\gamma_1}$ and $c<\hat{\gamma_2}$; or
+  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
 \item \emph{Fixation of either phenotype depending on initial frequency}:
-	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
+  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $c > \hat{\gamma_1}$ and $v>\hat{v}$.
 \end{enumerate}
-
-% in gamma - TODO fix
-%\begin{enumerate}
-%\item \emph{Fixation of cooperation}: 
-%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
-%	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
-%	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
-%	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
-%\item \emph{Fixation of the defection}: 
-%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
-%  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$; or 
-%	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
-%\item \emph{Fixation of either phenotype depending on initial frequency}:
-%  if \emph{(viii)} $T_A>T_B$ and $v > \hat{v}$ and $\hat\gamma_2 < c$.
-%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-%  if \emph{(vii.a)} $T_A < T_B$ and $v < \hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
-%  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 < c$.
-%\end{enumerate}
 
@@
 We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game.
+
 Under oblique and horizontal cultural transmission, a horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).

### 2020-09-01 ms/main.tex
formatting

@@
 
-These conditions are illustrated in \autoref{fig:results2}b-c.
+These conditions are illustrated in \autoref{fig:results2}.
 Note that cooperation and defection can coexist stably if there is horizontal bias for defection and the cost of cooperation is large but not too large.
@@
 \item \emph{Fixation of cooperation}: 
-	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
-	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
+	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
+	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
+	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
+	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
 \item \emph{Fixation of the defection}: 
-	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
-	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
+	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
+  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$; or 
+	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat{\gamma_1}$ and $c<\hat{\gamma_2}$; or
-  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
+  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat\gamma_1$ and $c<\hat\gamma_2$; or
+  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat\gamma_1$ and $\hat\gamma_2 < c$. %$0<\beta_3<\beta_1$.
 \item \emph{Fixation of either phenotype depending on initial frequency}:
-  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $c > \hat{\gamma_1}$ and $v>\hat{v}$.
+  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 < c$ and $v>\hat{v}$.
 \end{enumerate}

### 2020-09-02 ms/main.tex
typo

@@
 \begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
 

### 2020-09-02 ms/main.tex
juvenile

@@
 Social interactions occur randomly:
-two individuals with phenotype $A$ interact with probability $\hat{p}^2$, two individuals with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two individuals with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
+two juvenile individuals with phenotype $A$ interact with probability $\hat{p}^2$, two juveniles with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two juveniles with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
 

### 2020-09-02 ms/main.tex
Fix result 3 and validate that it works with v=1

@@
 %	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-%	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
+%	if \emph{(v)} $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
 %	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
@@
 %\item \emph{Fixation of either phenotype depending on initial frequency}:
-%	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1<0$.
+%	if \emph{(viii)}  $T_A>T_B$ and $\beta_1<\beta_3<0$.
 %\end{enumerate}
@@
 	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
-  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$; or 
+  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 > c$; or 
 	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
 \item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $c<\hat\gamma_1$ and $c<\hat\gamma_2$; or
-  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c<\hat\gamma_1$ and $\hat\gamma_2 < c$. %$0<\beta_3<\beta_1$.
+  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 > c$; or
+  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
 \item \emph{Fixation of either phenotype depending on initial frequency}:
-  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 < c$ and $v>\hat{v}$.
+  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1< c < \hat\gamma_2$.
 \end{enumerate}

### 2020-09-02 ms/main.tex
another small fix

@@
 	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
-  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 > c$; or 
+  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 < c$; or 
 	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.

### 2020-09-03 ms/main.tex
formatting

@@
 	if \emph{(iv)} $T=T_A=T_B$ and $c > b \cdot \alpha \frac{T}{1-T}$; or
-	if \emph{(vi)} $T_A>T_B$ and $\gamma_2<c$; or
+	if \emph{(v)} $T_A>T_B$ and $\gamma_2<c$; or
 	if \emph{(vi)} $T_A<T_B$ and $\gamma_1<c$.
-\item \emph{Fixation of either phenotype depending on initial frequency}: 
-	if \emph{(vii)} $T_A>T_B$ and $\gamma_1<c<\gamma_2$.
-\item \emph{Coexistence of both phenotypes at $\tilde{p}^*$}:
-	if \emph{(viii)} $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
+\item \emph{Stable coexistence of both phenotypes at $\tilde{p}^*$}:
+	if \emph{(vii)} $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
+\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}: 
+	if \emph{(viii)} $T_A>T_B$ and $\gamma_1<c<\gamma_2$.
 \end{enumerate}
@@
 	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
-	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
-	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
-\item \emph{Fixation of the defection}: 
+	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
+	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
+\item \emph{Fixation of defection}: 
 	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
-  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$ and $\hat\gamma_1 < c$; or 
+  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 < c$; or 
 	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
-\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 > c$; or
-  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
-\item \emph{Fixation of either phenotype depending on initial frequency}:
-  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1< c < \hat\gamma_2$.
+\item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
+  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
+  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
+\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}:
+  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
 \end{enumerate}
@@
 % Javarone MA, Atzeni AE, Galam S. Emergence of Cooperation in the Prisoner ’ s Dilemma Driven by Conformity. 2:155-163. doi:10.1007/978-3-319-16549-3
-% Woodcock S. The significance of non-vertical transmission of phenotype for the evolution of altruism. Biol Philos. 2006;21:213-234. doi:10.1007/s10539-005-8241-1
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\pagebreak
+% \pagebreak
 % Acknowledgements

### 2020-09-03 ms/main.tex
revised intro and discussion for the assortment story; need to refactor alpha to association

@@
 Conditions are found for fixation and coexistence of cooperation and defection. 
+The results show that association between cooperation and horizontal transmission facilitates the evolution of cooperation.
+A spatial model is constructed and its results are compared to the well-mixed model.
 Comparisons are drawn with Hamilton's rule and the concepts of relatedness and assortment.
-%A spatial model is constructed and its results are compared to the well-mixed model.
-We show that assortment between cooperation and horizontal transmission facilitates the evolution of cooperation.
 % and increases the population mean fitness. 
@@
 
-Here we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
+In this paper we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
 \citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
@@
 \end{equation}
-Here $\varphi$ takes the role of `relatedness' ($r$ in Eq.~\ref{eq:hamilton_rule}) or `assortment' ($m$ in Eq.~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
+In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of `relatedness' ($r$ in Eq.~\ref{eq:hamilton_rule}) or `assortment' ($m$ in Eq.~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
 This shows that under a combination of genetic and vertical (parent-to-offspring) cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (\autoref{eq:hamilton_rule}).
@@
 Some of the analyses by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
-Importantly, \citet{woodcock2006significance} showed the significance of non-vertical transmission for the evolution of cooperation. In their model individuals play a prisoner's dilemma game.
-They do not link between interaction and transmission (i.e.
-no assortment), but their model demonstrates that it is possible to sustain altruistic behaviour via cultural transmission for a significant duration of time in the absence of any direct biological propensity favouring this behaviour.
 
-We therefore hypothesize that non-vertical cultural transmission can enhance the evolution of cooperation.
-To test this hypothesis we suggest a model in which behavioral changes are mediated by cultural transmission that can occur during social interactions.
-That is, if there exists assortative meeting in the choice of the social interaction partner, or assortative learning in choice of the cultural transmission partner.
-For example, if an individual interacts with a cooperative individual, it might learn that cooperation is an advantageous behavior and will be cooperative in the future. 
-Our cultural evolution models include both vertical and non-vertical transmission of cooperation, and we investigate these models using mathematical analysis and simulations.  
-Our results demonstrate that cultural transmission can facilitate the evolution of cooperation even when genetic transmission can not because it facilitates the generation of assortment, and that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a better understanding of its evolutionary dynamics.
+Here, we study cultural-evolution models of cooperation that include both vertical and non-vertical transmission. 
+We investigate these models using mathematical analysis and simulations.  
+In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
+For instance, when there is an association between the choice of partner for social interaction and the choice of partner for cultural transmission.
+As another example, when an individual interacts with an individual of a different phenotype, this exposure to a different phenotype may lead it to learn or convert its phenotype.
+Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot (partly because it facilitates the generation of assortment in the sense of~\citet{Fletcher2009assortment}).
+This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a better understanding of its evolutionary dynamics.
 
@@
 \section*{Discussion}
-We hypothesized that non-vertical transmission can explain the evolution of cooperation and evaluated this hypothesis using a deterministic discrete-time evolutionary model with fitnesses in the form of payoffs from a prisoner's dilemma game.
-
+We studied the evolution of cooperation under non-vertical transmission using deterministic discrete-time evolutionary models with fitnesses in the form of payoffs from a prisoner's dilemma game. 
 Under oblique and horizontal cultural transmission, a horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
-Under horizontal and vertical cultural transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the assortment between cooperation and transmission (Result~\autoref{result:vert_hori}).
-Under a combination of vertical, oblique, and horizontal transmission the dynamics are more complicated, but all outcomes can still occur, depending on parameter values (Result~\autoref{result:vert_obli_hori}).
-Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_B>T_A$) and the cost of cooperation and assortment ratio are intermediate (yellow areas \autoref{fig:results2}).
+Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the association between cooperation and transmission (Results~\autoref{result:vert_hori} and~\autoref{result:vert_obli_hori}).
+Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_B>T_A$) and both the cost of cooperation and social association are intermediate (yellow areas in \autoref{fig:results2}).
 % TODO figure for result 3
 % TODO something about v-hat
-
-\citet{Eshel1982} showed that with assortative meeting, namely, a probability $m$ that individuals interact  within their phenotypic group, cooperation can evolve if $c < b \cdot m$.
-\citet{Fletcher2009assortment} have further argued that a simple and general explanation for the evolution of altruism is given by assortment between individuals that carry an altruistic trait, and the altruistic behavior of others.
-They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate such assortment, and that one such major mechanism is population structure.
-Our results highlight another possibility for assortment, namely, individuals socially interacting at rate $\alpha$ with their horizontal transmission partners.
-This mechanism does not require population structure.
-Rather, it depends on the co-occurrence of two social processes: cultural transmission and cooperation.
-We show that high levels of assortment significantly increase the potential for evolution of cooperation (\autoref{fig:results2}).
-With enough assortment ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal bias against it ($T_B>T_A$, see Result~\autoref{result:vert_hori}).
-
-This study was partially inspired by the work of \citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors}, 
-who hypothesised that microbes that manipulate their hosts to act altruistically can be favored by selection, and may play a role in the evolution of cooperation.
-Indeed, it has been shown that microbes can mediate behavioral changes in their hosts~\citep{dobson1988population,poulin2010parasite}.
-Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
-Microbes can be transmitted \emph{horizontally} from one host to another during host interactions, and following horizontal transfer, the recipient host may carry microbes that are closely related to the microbes of the donor host,
-even when the two hosts are (genetically) unrelated~\citep{lewin2017microbes}. 
-Although this result can be described from a kin selection point-of-view, we are more interested in the assortment point-of-view:
-infection by behavior-determining microbes during interactions effectively generates assortment, as a cooperating donor can transmit to the recipient both the benefit of the cooperative behavior and behavior-determining microbe.
-Horizontal cultural transmission can similarly generate assortment between the cooperative phenotype and the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, which in our model occurs with rate $\alpha$.
-So, because non-vertical transmission can effectively generate assortment, we suggest a revision of the conclusion made by \citet{Fletcher2009assortment}\footnote{``what is necessary for the evolution of altruism is assortment between focal genotype and phenotypic help, rather than the assortment among genetic types often emphasized in kin selection theory.''}: what is necessary for the evolution of altruism is assortment between focal \emph{pheno-genotype} and phenotypic help.
 
@@
 
-An important implication of our results is that cooperation can evolve even without population structure, repeated interactions, or individual recognition.
-This highlights the potential importance of non-vertical cultural transmission for explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.
+\citet{woodcock2006significance} has previously argued the significance of non-vertical transmission for the evolution of cooperation.
+He executed simulations with prisoner's dilemma payoffs but without horizontal transmission or social association ($\alpha=0$).
+Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a significant duration of time.
+Our results provide strong evidence for his hypothesis that horizontal transmission could have an important role in the evolution of cooperation.
+
+To understand the role of horizontal transmission, we first discuss the role of \emph{assortment}.
+\citet{Eshel1982} showed that altruism can evolve when there is enough \emph{assortative meeting}, namely, a tendency for individuals to interact within their phenotypic group.
+\citet{Fletcher2009assortment} have further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group.
+They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate such assortment, like population structure, repeated interactions, and individual recognition.
+Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and partner for transmission.
+This mechanism does not require population structure, repeated interactions, or individual recognition.
+We show that high levels of such social association greatly increase the potential for evolution of cooperation (\autoref{fig:results2}).
+With enough social association ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_B>T_A$, see Result~\autoref{result:vert_hori}).
+
+How does non-vertical transmission generate assortment? 
+\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors}, 
+who suggested that microbes that manipulate their hosts to act altruistically can be favored by selection, and may help explain the evolution of cooperation. 
+%Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
+%Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others. 
+From the kin selection point-of-view, if microbes can be transmitted \emph{horizontally} from one host to another during host interactions, then following horizontal transmission the recipient host will carry microbes that are closely related to the microbes of the donor host,
+even when the two hosts are (genetically) unrelated. 
+However, we are more interested in the assortment point-of-view:
+infection by behavior-determining microbes during interactions effectively generates assortment because receipient of help may be infected by the behavior-determining microbe and therefore become a helper.
+Cultural horizontal transmission can similarly generate assortment between the cooperative phenotype and the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, which in our model occurs with probability $\alpha$.
+
+Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
+environment''~\citep{Fletcher2009assortment} is generated not because \emph{the helper is likely to be helped}, but rather because \emph{the helped is likely to become a helper}.
+These conclusions highlight the importance of non-vertical cultural transmission for explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.
 

### 2020-09-05 ms/main.tex
Another fix to result 3

@@
 	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
-  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_1 < c$ and $\hat\gamma_2 < c$; or 
+  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$; or 
 	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.

### 2020-09-07 ms/main.tex
coexistence figure updates

@@
   When the curves are below the dashed line, $\tilde'{p}<\tilde{p}$, then $\tilde{p}$ decreases.
-  The yellow curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
+  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
   The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
@@
 
-%%% Figure: coexistence map - without oblique transmission
+%%% Figure: coexistence map - with oblique transmission
 \begin{figure}[htb]

### 2020-09-07 ms/main.tex
Start using social association term instead of meeting assortment

@@
 \end{corollary}
-With perfect assortment horizontal transmission always co-occurs with the cooperative interaction.
+With perfect social association horizontal transmission always co-occurs with the cooperative interaction.
 The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
@@
 
-Given the previous two corollaries for no assortment and perfect assortment ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of assortment on the evolution of cooperation.
-We denote the assortment boundaries by
+Given the previous two corollaries for no association and perfect association ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of social association on the evolution of cooperation.
+We denote the social association boundaries by
 \begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting}
@@
 (\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
-(\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
+(\textbf{c})~the social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
 Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.

### 2020-09-08 ms/main.tex
added OLE spatial model result

@@
 where $\hat{p}=v\tilde{p}+(1-v)p$.
-%This is not a recursion-MF
 
@@
 
-\begin{corollary}[Symmetric horizontal transmission]
+\begin{corollary}[Symmetric horizontal transmission] \label{sec:sym_hor_trans}
 If $T=T_A=T_B$, then cooperation will take over the population if
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{With population structure}
+
+We constructed an additional model in which partner association emerges from the population structure.
+We model a non-overlapping population colonizing a 2D grid of size 100x100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
+Each individual is characterized by its phenotype which is either a cooperator, $A$, or a defector $B$.
+In each generation individuals interact with their neighbors, i.e.
+individuals that inhabit adjacent sites, in a prisoner’s dilemma game (\autoref{table:prisoner_payoff}) and in horizontal cultural transmission.
+As before, $T_A$ and $T_B$ are the probabilities to transmit the phenotypes $A$ and $B$ during horizontal transmission.
+At each generation, each individual is chosen to "initiate" interactions with probability 1/2.
+Initiators then interact with a random neighbor for a prisoners’ dilemma game and a random neighbor (with replacement) for horizontal cultural transmission (as both the game and the transmission are symmetrical, the expected number of each of these interactions per individual per generation is 1).
+Therefore, the effective partner association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/m$, where $m$ is the number of neighbors.
+On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
+
+The order of the interactions across the lattice on each generation is random.
+After all interactions take place, individual's fitness is determined by
+$w = 1 + b \cdot n_b - c \cdot n_c$,
+where $n_b$ is the number interactions of that individual with cooperative neighbors, and $n_c$ is the total number of interactions of that individual ($n_b \le n_c$).
+Then a new generation is generated.
+Each site is colonized by an offspring of one of the individuals that inhabit either this site or one of the neighboring sites.
+The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness in his neighborhood.
+Offspring then have the same phenotype as their parents.
+
+\autoref{fig:spatial} shows that the highest cooperation cost to benefit ratio ($c/b$) that permits the evolution of cooperation in simulations of the spatial model is roughly $\alpha \cdot T / (1-T)$, where $T=T_A=T_B$ is the horizontal transmission rate.
+This agrees with the condition we derived in Corollary~\ref{sec:sym_hor_trans} for a population without population structure.
+This demonstrates that the partner association parameter $\alpha$ can emerge from local interactions between individuals in a structured population.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % TODO something about v-hat
+
+We tested the applicability of our analytic results to a complex spatial stochastic model (\autoref{fig:spatial}).
+Indeed, our derived condition provide a good approximation to simulation results, demonstrating that association between cooperation and transmission can arise in a structured population simply because the choice of individuals for social interactions is small.
 
@@
 
+%%% Figure: Spatial model
+\begin{figure}[htb]
+  \centering
+    \includegraphics[scale=0.7]{spatial.pdf}
+  \caption{
+  \textbf{Evolution of cooperation in a spatial model.}
+  The proportion of cooperators after 10,000 generations is plotted (color coded) as function of the ration between the cost and benefit of cooperation ($c/b$) on the y-axis, and the horizontal transmission rate of both phenotypes $A$ and $B$ (without transmission bias, $T=T_A=T_B$) on the x-axis.
+The blue curve represents the condition for the evolution of cooperation in a well-mixed population with partner selection, $c/b<\alpha T / (1-T)$(\autoref{eq:equal_transmission}), where $\alpha=1/8$.
+  The difference between the results of the spatial model and the analytical condition are because in the spatial model selection is local (i.e.
+among neighbors, offspring are born to their parent's neighborhood) whereas in the well-mixed population model selection is global.
+  Here, population size is $10,000$ (100-by-100 grid); cost of cooperation, $c=0.05$. Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
+  }
+  \label{fig:spatial}
+\end{figure}
+
 %%%

### 2020-09-09 ms/main.tex
update spatial figure; formatting

@@
 We constructed an additional model in which partner association emerges from the population structure.
-We model a non-overlapping population colonizing a 2D grid of size 100x100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
+We model a non-overlapping population colonizing a 2D grid of size 100-by-100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
 Each individual is characterized by its phenotype which is either a cooperator, $A$, or a defector $B$.
 In each generation individuals interact with their neighbors, i.e.
-individuals that inhabit adjacent sites, in a prisoner’s dilemma game (\autoref{table:prisoner_payoff}) and in horizontal cultural transmission.
+individuals that inhabit adjacent sites, in a prisoner's dilemma game (\autoref{table:prisoner_payoff}) and in horizontal cultural transmission.
 As before, $T_A$ and $T_B$ are the probabilities to transmit the phenotypes $A$ and $B$ during horizontal transmission.
@@
   \textbf{Evolution of cooperation in a spatial model.}
-  The proportion of cooperators after 10,000 generations is plotted (color coded) as function of the ration between the cost and benefit of cooperation ($c/b$) on the y-axis, and the horizontal transmission rate of both phenotypes $A$ and $B$ (without transmission bias, $T=T_A=T_B$) on the x-axis.
-The blue curve represents the condition for the evolution of cooperation in a well-mixed population with partner selection, $c/b<\alpha T / (1-T)$(\autoref{eq:equal_transmission}), where $\alpha=1/8$.
-  The difference between the results of the spatial model and the analytical condition are because in the spatial model selection is local (i.e.
-among neighbors, offspring are born to their parent's neighborhood) whereas in the well-mixed population model selection is global.
-  Here, population size is $10,000$ (100-by-100 grid); cost of cooperation, $c=0.05$. Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the ratio between the cost and benefit of cooperation ($c/b$) on the y-axis, and the horizontal transmission rate (without transmission bias, $T=T_A=T_B$) on the x-axis.
+  The population evolves on a 100-by-100 grid. Selection, cooperation, and horizontal cultural transmission are all local between adjacent sites.
+  The black curve represents the condition for the evolution of cooperation in a well-mixed population with partner association, $c/b<\alpha T / (1-T)$, where $\alpha=1/8$; see \autoref{eq:equal_transmission}.
+  Note that in the structured population, selection is local, whereas in the unstructured population, selection is global. This can explain the small difference in the results.
+  Here, population size is $10,000$ (100-by-100 grid); cost of cooperation, $c=0.05$.
+50 simulations were executed per parameter set.
+Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
   }

### 2020-09-11 ms/main.tex
Another fix to result 3

@@
 It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
-The assortment rate $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
+The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
 Horizontal transmission is not always successful, as one partner may reject the other's phenotype.
@@
 
-\begin{corollary}[No assortment of transmission and cooperation]
-Without assortment ($\alpha=0$) and with horizontal bias for cooperation ($T_A>T_B$), then 
+\begin{corollary}[No social association of transmission and cooperation]
+Without association ($\alpha=0$) and with horizontal bias for cooperation ($T_A>T_B$), then 
 (1) if the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; 
@@
 
-\begin{corollary}[Perfect assortment of transmission and cooperation]
-With perfect assortment ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
+\begin{corollary}[Perfect social association of transmission and cooperation]
+With perfect social association ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
 The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
@@
 \item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
-  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $\hat\gamma_1 < c < \hat\gamma_2$; or
+  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_2$ and $c < \hat\gamma_1$; or
   if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 

### 2020-09-12 ms/main.tex
Move figures from my notebook to new notebook
fix some figures

@@
 \end{result}
+These conditions are illustrated in \autoref{fig:result3}.
 
 %This result illustrates the crucial role of vertical and oblique transmission: the same cost of cooperation $c$ can lead to remarkably different outcomes if the vertical transmission rate $v$ is below or above the threshold $\hat v$.
-% TODO example with figure
 
@@
 \centering
-\includegraphics{coexistence_without_oblique.pdf}
+\includegraphics[scale = 0.75]{coexistence_without_oblique.pdf}
 \caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
@@
 
-%%% Figure: Conditions for fixation
+%%% Figure: Boundaries figure - only vertical
 
@@
   \centering       
-  % TODO for some reason figs a and b have a lot of white space on their right side
-
-    \includegraphics[scale=0.75]{boundiries_alpha0.pdf}
-
-    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}
-
-    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
+    \includegraphics[scale=0.5]{Result2_zero_alpha.pdf}
+
+    \includegraphics[scale=0.5]{Result2__non_zero_alpha.pdf}
+
+    \includegraphics[scale=0.5]{Result2__alpha_on_y_axis.pdf}
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
@@
     \label{fig:results2}
+\end{figure}
+
+%%% Figure: Boundaries figure - vertical and oblique
+
+\begin{figure}[htb]
+  \centering       
+    \includegraphics[scale=0.5]{Result3_boundaries.pdf}
+    \caption{\textbf{Evolution of cooperation under vertical, oblique and horizontal cultural transmission.} 
+The figure shows the global fixation of cooperation (green), global fixation of defection (red) and stable coexistence of cooperation and defection (yellow).
+In all cases the horizontal bias ($T_A-T_B$) is negative meaning $T_B>T_A$.
+The vertical transmission rate $v$ is on the y-axis; the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are the solid and dashed lines. 
+Here, $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.}
+    \label{fig:result3}
 \end{figure}

### 2020-09-12 ms/main.tex
Add time figures to the notebook, add another figure to result 3

@@
     \includegraphics[scale=0.5]{Result3_boundaries.pdf}
+    \includegraphics[scale=0.5]{result3_positive_bias.pdf}
     \caption{\textbf{Evolution of cooperation under vertical, oblique and horizontal cultural transmission.} 
-The figure shows the global fixation of cooperation (green), global fixation of defection (red) and stable coexistence of cooperation and defection (yellow).
-In all cases the horizontal bias ($T_A-T_B$) is negative meaning $T_B>T_A$.
-The vertical transmission rate $v$ is on the y-axis; the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are the solid and dashed lines. 
-Here, $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.}
+The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
+In (\textbf{a}) the horizontal bias $T_A-T_B$ is negative, in (\textbf{b}) the horizontal bias is positive.
+The vertical transmission rate $v$ is on the x-axis; the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are the solid and dashed lines. 
+In (\textbf{a}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$ and (\textbf{b}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.}
     \label{fig:result3}

### 2020-09-13 ms/main.tex
formatting, remove pstar; replace partner assoc with social assoc

--- 2020-09-11 ms/main.tex
@@
 
-We constructed an additional model in which partner association emerges from the population structure.
+We constructed an additional model in which social association emerges from the population structure.
 We model a non-overlapping population colonizing a 2D grid of size 100-by-100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
@@
 Initiators then interact with a random neighbor for a prisoners’ dilemma game and a random neighbor (with replacement) for horizontal cultural transmission (as both the game and the transmission are symmetrical, the expected number of each of these interactions per individual per generation is 1).
-Therefore, the effective partner association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/m$, where $m$ is the number of neighbors.
+Therefore, the effective social association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/m$, where $m$ is the number of neighbors.
 On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
@@
 This agrees with the condition we derived in Corollary~\ref{sec:sym_hor_trans} for a population without population structure.
-This demonstrates that the partner association parameter $\alpha$ can emerge from local interactions between individuals in a structured population.
+This demonstrates that the social association parameter $\alpha$ can emerge from local interactions between individuals in a structured population.
 
@@
   \centering       
-  % TODO for some reason figs a and b have a lot of white space on their right side
-
-    \includegraphics[scale=0.75]{boundiries_alpha0.pdf}
-
-    \includegraphics[scale=0.75]{boundiries_non_zero_alpha.pdf}
-
-    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
+    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
+	~
+    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
+    ~
+    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}
+
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
@@
 In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
-(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
-(\textbf{c})~the social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
+(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
+(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
 Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
@@
     \label{fig:results2}
+\end{figure}
+
+%%% Figure: Boundaries figure - vertical and oblique
+
+\begin{figure}[htb]
+  \centering       
+    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
+    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
+    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
+The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
+The vertical transmission rate $v$ is on the x-axis.
+Horizontal transmission bias (\textbf{a}) for cooperation, $T_A>T_B$ and (\textbf{b}) for defection, $T_A<T_B$.
+Cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines. 
+(\textbf{a}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.
+(\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.
+	}
+    \label{fig:result3}
 \end{figure}
@@
   The population evolves on a 100-by-100 grid. Selection, cooperation, and horizontal cultural transmission are all local between adjacent sites.
-  The black curve represents the condition for the evolution of cooperation in a well-mixed population with partner association, $c/b<\alpha T / (1-T)$, where $\alpha=1/8$; see \autoref{eq:equal_transmission}.
+  The black curve represents the condition for the evolution of cooperation in a well-mixed population with social association, $c/b<\alpha T / (1-T)$, where $\alpha=1/8$; see \autoref{eq:equal_transmission}.
   Note that in the structured population, selection is local, whereas in the unstructured population, selection is global. This can explain the small difference in the results.

### 2020-09-14 ms/main.tex
remove some comments
revised intro a bit; revised and edited result 2; fixed result 3 and showed connection of beta to gamma

@@
 \begin{abstract}
-We construct models for the cultural evolution of cooperation in a well-mixed population with vertical, horizontal, and oblique transmission.
+We study the cultural evolution of cooperation under vertical, horizontal, and oblique transmission.
 Conditions are found for fixation and coexistence of cooperation and defection. 
-The results show that association between cooperation and horizontal transmission facilitates the evolution of cooperation.
-A spatial model is constructed and its results are compared to the well-mixed model.
+We find that the evolution of cooperation is facilitated by horizontal transmission, especially when there is an association between cooperation and transmission, and that the effect of oblique transmission depends on the bias in horizontal transmission.
+Interestingly, stable coexistence of cooperation and defection can occur.
+A spatial model is constructed and compared to results from an unstructured model.
 Comparisons are drawn with Hamilton's rule and the concepts of relatedness and assortment.
-% and increases the population mean fitness. 
+% population mean fitness?
 % TODO what about oblique?
@@
 Evolution of cooperative behavior remains an important conundrum in evolutionary biology.
+
 Since the work of  \citet{hamilton1964genetical} and \citet{axelrod1981evolution}, theories for the evolution of cooperative and altruistic behaviors have been intertwined often under the rubric of \emph{kin selection}.
-
 Kin selection theory posits that natural selection is more likely to favor cooperation between more closely related individuals.
-The importance of relatedness to the evolution of cooperation and altruism was demonstrated by \citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
-This relatedness coefficient $r$ measures a probability that an allele sampled from the cooperator is identical by descent to one at the same locus in the recipient.
+The importance of \emph{relatedness} to the evolution of cooperation and altruism was demonstrated by \citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
 This condition is  known as \emph{Hamilton's rule}:
 \begin{equation} \label{eq:hamilton_rule}
-c < b \cdot r.
-\end{equation}
+c < b \cdot r,
+\end{equation}
+where the relatedness coefficient $r$ measures the probability that an allele sampled from the cooperator is identical by descent to one at the same locus in the recipient.
 
@@
 where $b$ and $c$ are the benefit and cost of cooperation. 
-Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness $r$ in inequality~\ref{eq:hamilton_rule}.
-
-The role of assortment in the evolution of altruism was studied by \citet{Fletcher2009assortment} in a \emph{public goods} game.
-They found that for altruism to evolve, cooperative individuals must experience more cooperation, on average, than defecting individuals, and ``thus, the evolution of altruism requires (positive) assortment between focal \emph{cooperative} players and cooperative acts in their interaction environment.''
-This condition can be summarized by \citep[eq.~2.3]{Fletcher2009assortment}
+Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness coefficient $r$ in inequality~\ref{eq:hamilton_rule}.
+
+The role of assortment in the evolution of altruism was emphasized by \citet{Fletcher2009assortment}.
+They found that in a \emph{public-goods} game, altruism will evolve if cooperative individuals experience more cooperation, on average, than defecting individuals, and ``thus, the evolution of altruism requires (positive) assortment between focal \emph{cooperative} players and cooperative acts in their interaction environment.''
+With some change in parameters, this condition is summarized by \citep[eq.~2.3]{Fletcher2009assortment}
 \begin{equation} \label{eq:fletcher2009}
-c < b \cdot (e_C - e_D ) \,,
-\end{equation}
-where $e_C$ is the probability that a cooperator receives help, and $e_D$ is the probability that a defector receives help.\footnote{inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $e_C=r + p$, $e_D=p$ and $e_C=m + (1-m)p$, $e_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
+c < b \cdot (p_C - p_D ) \,,
+\end{equation}
+where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $e_C=r + p$, $e_D=p$ and $e_C=m + (1-m)p$, $e_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
+See \citet{Bijma2010assortment} for treatment of non-public-goods games.
 
@@
 \end{equation}
-In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of `relatedness' ($r$ in Eq.~\ref{eq:hamilton_rule}) or `assortment' ($m$ in Eq.~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
-This shows that under a combination of genetic and vertical (parent-to-offspring) cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (\autoref{eq:hamilton_rule}).
+In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
+This shows that under a combination of genetic and cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).
 
@@
 In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
-For instance, when there is an association between the choice of partner for social interaction and the choice of partner for cultural transmission.
+For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission.
 As another example, when an individual interacts with an individual of a different phenotype, this exposure to a different phenotype may lead it to learn or convert its phenotype.
-Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot (partly because it facilitates the generation of assortment in the sense of~\citet{Fletcher2009assortment}).
+Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can protect traits from the effect of natural selection \citep{ram2018evolution}.
 This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a better understanding of its evolutionary dynamics.
@@
 & = \tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \\
-& = v \tilde{p} + (1-v) p.
+& = v \tilde{p} + (1-v) p \;.
 \end{aligned}
@@
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between social partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
+It occurs between social interaction partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
 The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
@@
 where $\hat{p}=v\tilde{p}+(1-v)p$.
+\autoref{table:vars_params} summarized the model variables and parameters.
+
+%%% Table: variables and parameters
+\bigskip
+\begin{table}[h]
+\centering
+\begin{tabular}{lll}
+\toprule
+Symbol & Description & Values \\ \cmidrule(r){1-3}
+$A$ & Cooperator phenotype & \\
+$B$ & Defector phenotype & \\
+$p$ & Frequency of phenotype $A$ among adults & $[0,1]$ \\
+$\tilde p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
+$\hat p$ & Frequency of phenotype $A$ among juveniles & $[0,1]$ \\
+$v$ & Vertical transmission rate & $[0,1]$ \\
+$c$ & Cost of cooperation & $(0,1)$ \\
+$b$ & Benefit of cooperation & $c<b$ \\
+$\alpha$ & Social association & $[0,1]$ \\
+$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $[0,1]$ \\
+\\ \bottomrule
+\end{tabular}
+\caption{\textbf{Model variables and parameters.}
+}
+\label{table:vars_params}
+\end{table}
+\bigskip
+%%%
 
@@
 \begin{equation}  \label{eq:nextgen_parents_oblique_only}
-p' = p^2 (T_B-T_A) + p (1+T_A-T_B) ,
-\end{equation}
-
-which gives the following result.\\
+p' = p^2 (T_B-T_A) + p (1+T_A-T_B) \;.
+\end{equation}
+
+Solving for $p'>p$ we get the following result.\\
 
@@
 \begin{equation} \label{eq:oblique_only_result}
-T_A > T_B, 
-\end{equation}
-then $p'>p$, and the frequency of the cooperator phenotype among adults increases every generation.
+T_A > T_B \;,
+\end{equation}
+then the frequency of the cooperator phenotype among adults increases every generation, $p'>p$.
 \end{result}
 
-If $T_A = T_B$, then $p'=p$ and the population is static.
-Therefore, in the absence of vertical transmission, selection plays no role in the evolution of cooperation.
-Hence, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~{\autoref{fig:results}c).
+That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ are missing from \autoref{eq:nextgen_parents_oblique_only}).
+The dynamics are determined solely by differential horizontal transmission of the two phenotypes, that is, the relative tendency of each phenotype to be horizontally transmitted to peers (see~{\autoref{fig:results}c).
+Note that without bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
 
@@
 & + \tilde{p}(1-\tilde{p}) (1+b) [\tilde{p} (1-\alpha) + \alpha] T_A \\
-& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A .
+& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A \;.
 \end{aligned}
@@
 \begin{equation}
-\tilde{p}(1-\tilde{p})\big[(1+b)T_A + (1-c)(1-T_B)-1\big] = 0,
+\tilde{p}(1-\tilde{p})\big[(1+b)T_A + (1-c)(1-T_B)-1\big] = 0 \;,
 \end{equation}
@@
   \tilde{p}^2 (1+b-c) + \tilde{p}(1-\tilde{p}) \big[(1-c) (1 - T_B) + (1+b)T_A\big] 
-  > \bar{w}\tilde{p} .
+  > \bar{w}\tilde{p} \;.
 \end{equation}
@@
 \begin{equation} \label{eq:vert_hori_alpha1_condition_proof}
-  (1-c) (1 - T_B) + (1+b)T_A
-  > 1
+  (1-c) (1 - T_B) + (1+b)T_A > 1 \;.
 \end{equation}
@@
   & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-  & + (1-\tilde{p})^2 (1-\alpha) T_A .
+  & + (1-\tilde{p})^2 (1-\alpha) T_A \;.
 \end{aligned}
@@
 \begin{equation} \label{eq:vert_hori_global_condition}
-c(1-T_B) - b \alpha T_A - (T_A-T_B) < \tilde{p} \cdot b (1-\alpha) (T_A-T_B).
-\end{equation}
-
-Besides the fixation states $\tilde{p}=0$ and $\tilde{p}=1$, there may be an actual polymorphic equilibrium of $\tilde{p}'=\tilde{p}$ in Eq.\ \ref{eq:nextgen_parents_vertical_only}, namely 
+c(1-T_B) - b \alpha T_A - (T_A-T_B) < \tilde{p} \cdot b (1-\alpha) (T_A-T_B) \;.
+\end{equation}
+
+In addition to the the fixation states $\tilde{p}=0$ and $\tilde{p}=1$, there may be an actual polymorphic equilibrium of $\tilde{p}'=\tilde{p}$ in Eq.\ \ref{eq:nextgen_parents_vertical_only}, namely 
 \begin{equation} \label{eq:vert_hori_equilibrium}
@@
 Since all parameters are positive, we can apply
-inequality \ref{eq:vert_hori_global_condition} and see that for $\tilde{p}'>\tilde{p}$ we require that either 
+inequality \ref{eq:vert_hori_global_condition} and see that a requirement for $\tilde{p}'>\tilde{p}$ is that either 
 \begin{align} 
@@
 
-We define the initial frequency of the cooperator phenotype among parents, $\tilde{p}_0$, and the \emph{cost boundaries},
+We define the \emph{cost boundaries},
 \begin{equation} \label{eq:cost_boundaries}
@@
 \end{equation}
-Then, applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes in following result and corollaries.
+Then, applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes in the following result and corollaries.
 \\
@@
 \begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
-With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}):
+With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of cooperation will follow one of the following scenarios, depending on the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}):
 
@@
 \item \emph{Fixation of cooperation}:
-	if \emph{(i)} $T=T_A=T_B$ and $c < b \cdot \alpha \frac{T}{1-T}$; or
-	if \emph{(ii)} $T_A>T_B$ and $c<\gamma_1$; or
-	if \emph{(iii)} $T_A<T_B$ and $c<\gamma_2$.
+	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or
+	if \emph{(ii)} $T_A < T_B$ and $c < \gamma_2$.
 \item \emph{Fixation of defection}:
-	if \emph{(iv)} $T=T_A=T_B$ and $c > b \cdot \alpha \frac{T}{1-T}$; or
-	if \emph{(v)} $T_A>T_B$ and $\gamma_2<c$; or
-	if \emph{(vi)} $T_A<T_B$ and $\gamma_1<c$.
-\item \emph{Stable coexistence of both phenotypes at $\tilde{p}^*$}:
-	if \emph{(vii)} $T_A<T_B$ and $\gamma_2<c<\gamma_1$.
-\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}: 
-	if \emph{(viii)} $T_A>T_B$ and $\gamma_1<c<\gamma_2$.
+	if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or
+	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
+\item \emph{Stable coexistence}:
+	if \emph{(v)} $T_A<T_B$ and $\gamma_2 < c < \gamma_1$.
+\item \emph{Unstable coexistence}: 
+	if \emph{(vi)} $T_A>T_B$ and $\gamma_1 < c <\gamma_2$.
 \end{enumerate}
@@
 These conditions are illustrated in \autoref{fig:results2}.
-Note that cooperation and defection can coexist stably if there is horizontal bias for defection and the cost of cooperation is large but not too large.
-The recursion dynamic for this case is illustrated in \autoref{fig:coexistence_without_oblique}.
-
-Much of the literature on evolution of cooperation focuses on conditions for an initially rare cooperative phenotype to invade a population of defectors.
-The next corollary deals with such a condition, followed by a corollary that deals with symmetric horizontal transmission, i.e. $T_A=T_B$.
+
+Cooperation and defection can coexist stably at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:vert_hori_equilibrium}) if there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:results2}b.
+When unstable coexistence occurs, phenotype $A$ will fix if initially at a frequency $p>\tilde{p}^*$, and phenotype $B$ will fix if initially at a frequency $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+\autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:results2}a and \autoref{fig:results2}b.
+
+Much of the literature on evolution of cooperation focuses on conditions for  initially rare cooperative phenotype to invade a population of defectors.
+The next corollary deals with such a condition.
 \\
@@
 \begin{corollary}[Condition for cooperation to increase when initially rare]
-If the initial frequency of the cooperative phenotype is very close to zero, $\tilde{p}_0 \approx 0$, then this frequency will increase if 
+If the initial frequency of cooperation is very close to zero, $\tilde{p}_0 \approx 0$, then its frequency will increase if 
 \begin{equation} \label{eq:unequal_transmission_from_rarity}
 \begin{aligned}
-T_A>T_B \;\; \text{and} \;\; c < \gamma_1, \quad \text{or} \quad
-T_A<T_B \;\; \text{and} \;\; \gamma_2<c < \gamma_1. 
+c < \gamma_1 = \frac{b \alpha T_A + (T_A - T_B)}{1-T_B} \;.
 \end{aligned}
@@
 
-In general, these conditions cannot be formulated in the form of Hamilton's rule ($c<b\cdot r$) due to the horizontal transmission bias $T_A-T_B$.
-Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.\\
+Note that the right-hand side equals $\gamma_1$.
+This condition follows from combining the conditions for fixation of cooperation and for stable coexistence.
+
+In general, these conditions cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
+Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
+\\
 
@@
 \label{eq:equal_transmission}
-c < b \cdot \alpha \frac{T}{1-T}.
+c < b \cdot \alpha \frac{T}{1-T} \;.
 \end{equation}
 \end{corollary}
-Inequality \ref{eq:equal_transmission} is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:vert_hori_global_condition} and can be interpreted as a version of Hamilton's rule (inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the `effective relatedness' or `effective assortment', respectively.
-\autoref{fig:results}a demonstrates this condition. 
+Note that the right-hand side equals $\gamma_1$ when $T=T_A=T_B$.
+This condition is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:vert_hori_global_condition} and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+\autoref{fig:results}a illustrates this condition.
+
+The condition in inequality~\ref{eq:equal_transmission} demonstrates the importance of the social association $\alpha$. The following corollaries provide additional demonstrations.
 \\
 
-\begin{corollary}[No social association of transmission and cooperation]
-Without association ($\alpha=0$) and with horizontal bias for cooperation ($T_A>T_B$), then 
-(1) if the cost is low compared to the bias ($c<(T_A-T_B)/(1-T_B)$), then cooperation will fix from any positive frequency; 
-(2) if the cost is low compared to the benefit ($c<(1+b)(T_A-T_B)(1-T_B)$), then cooperation will fix if the initial frequency is high enough ($\tilde{p}_0 > \tilde{p}^*$).
-\end{corollary}
-
-\autoref{fig:results2}a illustrates these conditions, where
- the third equilibrium given by Eq.\ \ref{eq:vert_hori_equilibrium} becomes
-\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
-\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) },
-\end{equation} 
-and the cost boundaries are
-\begin{equation}\begin{aligned}
-\gamma_1(\alpha=0) = \frac{T_A - T_B}{1-T_B}, \quad
-\gamma_2(\alpha=0) = (1+b)\frac{T_A - T_B}{1-T_B}.
-\end{aligned}\end{equation}
-If $T_A>T_B$ then $0<\gamma_1(\alpha=0)<\gamma_2(\alpha=0)$.
-So either $c<\gamma_1(\alpha=0)$ or $\gamma_1(\alpha=0)<c<\gamma_2(\alpha=0)$ will allow fixation of cooperation, the latter only if the initial frequency is high enough.
-If $T_A<T_B$ then $\gamma_2(\alpha=0)<\gamma_1(\alpha=0)<0<c$,
-and defection will fix.
-%TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.
-\\
-
 \begin{corollary}[Perfect social association of transmission and cooperation]
-With perfect social association ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
-The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
+With perfect social association ($\alpha=1$), the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency, $\tilde{p}'>\tilde{p}$, if
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 \end{corollary}
-With perfect social association horizontal transmission always co-occurs with the cooperative interaction.
-The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
-
-In terms of the cost boundaries, inequality~\ref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$, and if $T_A>T_B$ then that suffices for fixation of cooperation.
+This condition is obtained from inequality \ref{eq:vert_hori_alpha1_condition_proof}, and the right-hand side equals $\gamma_1$ when $\alpha=1$ (\autoref{eq:cost_boundaries}).
+Perfect social association (horizontal transmission always occurs during the cooperative interaction) is also assumed in the model studied by \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
+
+%In terms of the cost boundaries, inequality~\ref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$, and if $T_A>T_B$ then that suffices for fixation of cooperation.
 If $T_B>T_A$ then $\gamma_2(\alpha=1)<0$ and again, inequality~\ref{eq:vert_hori_alpha1} is sufficient for increase in the frequency of $A$.
-Inequality~\ref{eq:vert_hori_alpha1} can be written as
-\begin{equation} \label{eq:vert_hori_alpha1_effective}
-1 - (1-c)(1-T_B) < (1+b) T_A ,
-\end{equation}
+Inequality~\ref{eq:vert_hori_alpha1} can also be written as
+$1 - (1-c)(1-T_B) < (1+b) T_A$,
 which provides an interesting interpretation for the success of cooperation. 
@@
 Therefore, $1 - (1-c)(1-T_B)$ is the probability that either the cooperator becomes a defector, or that it fails to reproduce.
-This is the \emph{effective cost of cooperation} from this interaction, while $(1+b) T_A$ is the probability that the defector becomes cooperative and reproduces, which is the \emph{effective benefit of cooperation} from this interaction.
-Thus, inequality~\ref{eq:vert_hori_alpha1} entails that cooperation can evolve if the effective cost of cooperation is less than the effective benefit.
+This is the \emph{effective cost of cooperation} from this interaction.
+Similarly, $(1+b) T_A$ is the probability that during an interaction between a cooperator and a defector, the defector becomes cooperative and reproduces, which is the \emph{effective benefit of cooperation} from this interaction.
+Thus, inequality~\ref{eq:vert_hori_alpha1} entails that cooperation can evolve if the effective cost of cooperation is less than the effective benefit during an interaction between a cooperator and a defector.
+\\
+
+\begin{corollary}[No social association of transmission and cooperation]
+Without social association ($\alpha=0$) cooperation can take over the population if there is horizontal transmission bias for cooperation, $T_A>T_B$, and if either
+\begin{equation}
+\label{eq:vert_hori_alpha0}
+c < \frac{T_A-T_B}{1-T_B}
+\quad \text{or} \quad
+\tilde{p}_0 > \tilde{p}^* = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B)} \;.
+\end{equation}
+\end{corollary}
+
+\autoref{fig:results2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in \autoref{eq:vert_hori_equilibrium} and \autoref{eq:cost_boundaries}.
+If there is horizontal transmission bias for cooperation ($T_A>T_B$) then cooperation can evolve from any initial frequency if the cost is low enough, $c<\gamma_1$ (green area below solid line).
+If the cost is not low enough, cooperation can also evolve if starting from high frequency and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
+
+We can interpret these condition as follows.
+First, when cooperators are rare, they will mostly interact with defectors.
+Therefore, for cooperation to increase in frequency and fix, the \emph{effective cost of cooperation} must be lower than the horizontal transmission of cooperation, $1-(1-c)(1-T_B) < T_A$, which is equivalent to the left condition in \autoref{eq:vert_hori_alpha0}.
+Second, if $T_A$ is not large enough, cooperation will fix if the initial frequency is higher than the threshold $\tilde{p}^*$; thus, this threshold must be below one, which entails $1-(1-c)(1-T_B) < T_A + b(T_A-T_B)$.
+That is, the effective cost of cooperation must be lower than the combined effect of horizontal transmission of cooperation, $T_A$, and the benefit of cooperation multiplied by the transmission bias, $b(T_A-T_B)$.
+\\
 
@@
 
-\begin{corollary}[Intermediate assortment of transmission and cooperation]
-The cooperative phenotype will increase from rarity if the assortment rate is high enough, or specifically if
+\begin{corollary}[Intermediate association of transmission and cooperation]
+Cooperation will increase from rarity if social association is high enough, or specifically if
   \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
@@
 \autoref{fig:results2}c demonstrates these conditions.
-With horizontal bias for cooperation ($T_A>T_B$; positive x-axis) cooperation fixes in the population from any initial positive frequency (green) if $\alpha$ (y-axis) is above the orange line ($a_1$), or if initially present at a high enough frequency (blue) if $\alpha$ is above the blue line ($a_2$).
-With horizontal bias for defection ($T_B>T_A$; negative x-axis) cooperation fixes if $\alpha$ is above the blue line ($a_2$), but can be maintained in coexistence with defection (yellow) if $\alpha$ is above the orange line ($a_1$).
-Without horizontal bias ($T_A=T_B$) fixation occurs if the assortment rate is high enough, $\alpha > \frac{c}{b} \cdot \frac{1-T}{T}$ (inequality~\ref{eq:equal_transmission}).
+With horizontal transmission bias for cooperation ($T_A>T_B$), cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
+Otherwise, cooperation can also fix if the horizontal bias is strong, the initial frequency is high, and social association is high, $a_1 < \alpha$ (blue area).
+With horizontal bias for defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area in negative x-axis), and can also increase in rarity and maintain a stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
+Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
 
@@
  \end{equation}
-since $c<b$ and $1>\alpha v$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
+since $c<b$ and $\alpha v < 1$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
 First, if $\beta_3<\beta_1$ then 
@@
 
-Similarly, if $T_B>T_A$, then
+Similarly, if $T_A<T_B$, then
 \begin{equation} \label{eq:beta1_rev}
@@
  \end{equation}
-since $c<b$ and $1>\alpha v$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
-First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A=B$ is the only locally stable legitimate equilibrium.
+since $c<b$ and $\alpha v < 1$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
+First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A$ is the only locally stable legitimate equilibrium.
 Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
@@
 \end{equation}
+
+Assume $T_A<T_B$.
+For $\beta_3<0$ we need $\hat\gamma_1<c$.
+For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
+Note that the expression in the square brackets is positive if and only if $v > \hat v$.
+So, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c$ or $v < \hat v$ and $c < \hat\gamma_2$.
+So, for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c < \hat\gamma_1$, or $v < \hat v$ and $c < \min(\hat\gamma_1, \hat\gamma_2)$; and 
+for $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\hat\gamma_2$ or $v < \hat v$ and $\hat\gamma_2<c$.
+However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\hat\gamma_2$.
+A similar analysis can be made when $T_A>T_B$.
 
@@
 \item \emph{Fixation of cooperation}: 
-	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \alpha \frac{T}{1-T}$; or
-	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
-	if \emph{(iii.a)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
-	if \emph{(iii.b)} $T_A<T_B$ and $v<\hat v$ and $\hat\gamma_2 < c$.
+	if \emph{(i)} $T_A \ge T_B$ and $c < \hat\gamma_1$; or 
+	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \hat\gamma_2$.
 \item \emph{Fixation of defection}: 
-	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \alpha \frac{T}{1-T}$; or 
-  if \emph{(v)} $T_A>T_B$ and $\hat\gamma_2 < c$; or 
-	if \emph{(vi)} $T_A<T_B$ and $\hat\gamma_1 < c$.
-\item \emph{Stable Coexistence of both phenotypes at $\hat{p}^*$}: 
-  if \emph{(vii.a)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_2$ and $c < \hat\gamma_1$; or
-  if \emph{(vii.b)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
-\item \emph{Unstable coexistence and fixation of either phenotype depending on initial frequency}:
-  if \emph{(viii)}  $T_A>T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
+    if \emph{(iii)} $T_A \ge T_B$ and $\hat\gamma_2 < c$; or 
+	if \emph{(iv)} $T_A < T_B$ and $\hat\gamma_1 < c$.
+\item \emph{Stable Coexistence}: 
+    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
+\item \emph{Unstable coexistence}:
+    if \emph{(vii)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
 \end{enumerate}
@@
 Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
-  % TODO missing text descriptions of conditions on (3)
   	}
@@
   \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
-  % TODO write all parameter values. T=? alpha=?
-  % TODO set colors the same as fig 3.
-  % TODO remove legends, increase fonts, explain in caption instead of legend.
   }

### 2020-09-14 ms/main.tex
revise result 3

@@
 
-Assume $T_A<T_B$.
+Now, assume $T_A<T_B$.
 For $\beta_3<0$ we need $\hat\gamma_1<c$.
@@
 \item \emph{Stable Coexistence}: 
-    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
+    if \emph{(v)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
 \item \emph{Unstable coexistence}:
-    if \emph{(vii)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
+    if \emph{(vi)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
 \end{enumerate}
@@
 
-%This result illustrates the crucial role of vertical and oblique transmission: the same cost of cooperation $c$ can lead to remarkably different outcomes if the vertical transmission rate $v$ is below or above the threshold $\hat v$.
+\emph{//additional corollaries//}
+
+%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
 
@@
 Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the association between cooperation and transmission (Results~\autoref{result:vert_hori} and~\autoref{result:vert_obli_hori}).
-Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_B>T_A$) and both the cost of cooperation and social association are intermediate (yellow areas in \autoref{fig:results2}).
+Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in \autoref{fig:results2}).
 % TODO figure for result 3
@@
 
-We tested the applicability of our analytic results to a complex spatial stochastic model (\autoref{fig:spatial}).
-Indeed, our derived condition provide a good approximation to simulation results, demonstrating that association between cooperation and transmission can arise in a structured population simply because the choice of individuals for social interactions is small.
+We tested the applicability of our analytic results to a complex spatial stochastic model.
+Our derived condition provide a good approximation to simulation results  (\autoref{fig:spatial}), demonstrating that association between cooperation and transmission can arise in a structured population simply because the choice of individuals for social interactions is small.
 
@@
 Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a significant duration of time.
-Our results provide strong evidence for his hypothesis that horizontal transmission could have an important role in the evolution of cooperation.
+Our results provide strong evidence for his hypothesis that horizontal transmission can have an important role in the evolution of cooperation.
 
@@
 \citet{Eshel1982} showed that altruism can evolve when there is enough \emph{assortative meeting}, namely, a tendency for individuals to interact within their phenotypic group.
-\citet{Fletcher2009assortment} have further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group.
+\citet{Fletcher2009assortment} have further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group; see also \citet{Bijma2010assortment}.
 They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate such assortment, like population structure, repeated interactions, and individual recognition.
@@
 We show that high levels of such social association greatly increase the potential for evolution of cooperation (\autoref{fig:results2}).
-With enough social association ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_B>T_A$, see Result~\autoref{result:vert_hori}).
+With enough social association ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$, see Result~\autoref{result:vert_hori}).
 

### 2020-09-20 ms/main.tex
Update the figure and fix merge issues
Add condition for result 3 - when v<v_hat
Add alpha vs v to result figures to the notebook

@@
 \autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:results2}a and \autoref{fig:results2}b.
-
-Much of the literature on evolution of cooperation focuses on conditions for  initially rare cooperative phenotype to invade a population of defectors.
-The next corollary deals with such a condition.
-\\
-
-\begin{corollary}[Condition for cooperation to increase when initially rare]
-If the initial frequency of cooperation is very close to zero, $\tilde{p}_0 \approx 0$, then its frequency will increase if 
-\begin{equation} \label{eq:unequal_transmission_from_rarity}
-\begin{aligned}
-c < \gamma_1 = \frac{b \alpha T_A + (T_A - T_B)}{1-T_B} \;.
-\end{aligned}
-\end{equation} 
-\end{corollary}
-
-Note that the right-hand side equals $\gamma_1$.
-This condition follows from combining the conditions for fixation of cooperation and for stable coexistence.
-
-In general, these conditions cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
-Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
-\\
 
@@
 \item \emph{Stable Coexistence}: 
-    if \emph{(v)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$. 
+    if \emph{(v)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$; or
+    if \emph{(vi)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_1$.
 \item \emph{Unstable coexistence}:
-    if \emph{(vi)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
+    if \emph{(vii)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
 \end{enumerate}
@@
 
-\emph{//additional corollaries//}
+Much of the literature on evolution of cooperation focuses on conditions for  initially rare cooperative phenotype to invade a population of defectors.
+The next corollary deals with such a condition.
+\begin{corollary}[Condition for cooperation to increase when initially rare]
+  If the initial frequency of cooperation is very close to zero, $\hat{p}_0 \approx 0$, then its frequency will increase if 
+  \begin{equation} \label{eq:unequal_transmission_from_rarity_general_case}
+  \begin{aligned}
+  c < \hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)} \;.
+  \end{aligned}
+  \end{equation} 
+  \end{corollary}
+
+Note that the right-hand side equals $\hat\gamma_1$.
+This condition follows from combining the conditions for fixation of cooperation and for stable coexistence.
+
+In general, these conditions cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
+Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
+\\
+\begin{corollary}[Necessity condition for fixation of cooperation.]
+  Fixation of cooperation is possible only when
+  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
+    \begin{aligned}
+      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
+    \end{aligned}
+    \end{equation} 
+\end{corollary}
+When there is horizontal transmission bias for cooperation, fixation can occured for every value of vertical transmission because $\hat{v}<0$.
+However, if the the horizontal bias favours defection, for fixation of cooperation to occur the vertical transmission must be higer than $\hat{v}$.
 
@@
     (\textbf{a}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.
-(\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.
-	}
+    (\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.}
     \label{fig:result3}

### 2020-09-20 ms/main.tex
Add alpha vs v graphs to the main file

@@
 
-\begin{corollary}[Intermediate association of transmission and cooperation]
+\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:Intermediate_association}
 Cooperation will increase from rarity if social association is high enough, or specifically if
@@
 \end{result}
-These conditions are illustrated in \autoref{fig:result3}.
+These conditions are illustrated in \autoref{fig:result3}a and \autoref{fig:result3}b.
 
@@
 However, if the the horizontal bias favours defection, for fixation of cooperation to occur the vertical transmission must be higer than $\hat{v}$.
+\\
+
+We already examine the effect of social association in the case of perfect vertical transmission ($v=1$). Now we'll move to the genral case where $0<v\leq 1$.
+We denote the social association boundaries of the general case by
+\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting_general_case}
+  \hat{a}_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
+  \hat{a}_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A}.
+\end{aligned}\end{equation}
+\emph{Corollary~\autoref{corollary:Intermediate_association}} is true for the general but with new boundaries coefficients $\hat{a}_1$, $\hat{a}_2$.
+\autoref{fig:result3}c and \autoref{fig:result3}d illustrate this result.
 
@@
     \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
+    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
+    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
     \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
@@
     Horizontal transmission bias (\textbf{a}) for cooperation, $T_A>T_B$ and (\textbf{b}) for defection, $T_A<T_B$.
-    Cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines. 
+    Cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines in figures \textbf{(a)}, \textbf{(b)}. 
+    Soical association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines in figures \textbf{(c)}, \textbf{(d)}.
     (\textbf{a}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.
-    (\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.}
+    (\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.
+    (\textbf{c}), $b=1.2$, $T_A=0.5$, $T_B = 0.4$, $c=0.5$.
+    (\textbf{d}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $c=0.5$.}
     \label{fig:result3}

### 2020-09-20 ms/main.tex
fix two typos - one of two, footnote

@@
 \end{equation}
-where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $e_C=r + p$, $e_D=p$ and $e_C=m + (1-m)p$, $e_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
+where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
 See \citet{Bijma2010assortment} for treatment of non-public-goods games.
@@
 
-Consider a very large population whose members are characterized by their phenotype $\phi$, which can be of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors.
+Consider a very large population whose members are characterized by their phenotype $\phi$, which can be one of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors.
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.

### 2020-09-20 ms/main.tex
Add unstable coexistence to figure 5

@@
   \includegraphics{coexistence_with_oblique.pdf}
-  \caption{\textbf{Stable coexistence between cooperation and defection with oblique transmission.}
-  The curve shows the frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ vs. the current generation $\hat{p}$ (\autoref{eq:horizontal}).
+  \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
+  The curves show the frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ vs. the current generation $\hat{p}$ (\autoref{eq:horizontal}).
   The dashed black line is $\hat{p}'=\hat{p}$.
-  The curve and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
+  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
   When $\hat{p} < \hat{p}^*$ then the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
   When $\hat{p} > \hat{p}^*$ then the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
-  Here,  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
+  The orange curve for wich the polymorphic equilibrium is stable is given by  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
+  The blue curve for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
   }

### 2020-09-20 ms/main.tex

@@
 \usepackage{chngcntr}
+%\usepackage{endfloat}
 
@@
 We find that the evolution of cooperation is facilitated by horizontal transmission, especially when there is an association between cooperation and transmission, and that the effect of oblique transmission depends on the bias in horizontal transmission.
-Interestingly, stable coexistence of cooperation and defection can occur.
+Stable coexistence of cooperation and defection can occur.
 A spatial model is constructed and compared to results from an unstructured model.
@@
 \end{equation}
-where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
+where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{Inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
 See \citet{Bijma2010assortment} for treatment of non-public-goods games.
@@
 \end{equation}
-In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is further reduced by $(1-\varphi)/\varphi$.
-This shows that under a combination of genetic and cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).
-
-Cultural transmission may be either viewed as vertical, horizontal or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
+In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
+This shows that under a combination of genetic and cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (\ref{eq:hamilton_rule}).
+
+Cultural transmission may be  viewed as vertical, horizontal or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
 from non-parental adults).
@@
 For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission.
-As another example, when an individual interacts with an individual of a different phenotype, this exposure to a different phenotype may lead it to learn or convert its phenotype.
+As another example, when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
 Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can protect traits from the effect of natural selection \citep{ram2018evolution}.
-This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a better understanding of its evolutionary dynamics.
+This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a broader understanding of its evolutionary dynamics.
 
@@
 
-Consider a very large population whose members are characterized by their phenotype $\phi$, which can be one of two types, $\phi=A$ for cooperators or $\phi=B$ for defectors.
+Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
@@
 \centering
+\caption{\textbf{Payoff matrix for prisoner's dilemma.}
+The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
+$b>c>0$.
+}
 \begin{tabular}{lll}
@@
 \end{tabular}
-\caption{\textbf{Payoff matrix for prisoner's dilemma.}
-The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
-$b>c>0$.
-}
 \label{table:prisoner_payoff}
@@
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between social interaction partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
-The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
-Horizontal transmission is not always successful, as one partner may reject the other's phenotype.
+It occurs between socially interacting partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
+%The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
+However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
 The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).
@@
 \begin{table}[]
+\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
 \begin{tabular}{@{}llllll@{}}
@@
 \end{tabular}
-\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
 \label{table:interactions}
@@
 \end{equation}
-where $\hat{p}=v\tilde{p}+(1-v)p$.
-\autoref{table:vars_params} summarized the model variables and parameters.
+%where $\hat{p}=v\tilde{p}+(1-v)p$.
+\autoref{table:vars_params} summarizes the model variables and parameters.
 
@@
 \centering
+\caption{\textbf{Model variables and parameters.}
+}
 \begin{tabular}{lll}
@@
 $b$ & Benefit of cooperation & $c<b$ \\
-$\alpha$ & Social association & $[0,1]$ \\
+$\alpha$ & Probability of social association & $[0,1]$ \\
 $T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $[0,1]$ \\
@@
 \end{tabular}
-\caption{\textbf{Model variables and parameters.}
-}
 \label{table:vars_params}
 \end{table}
-\bigskip
+%\bigskip
 %%%
@@
 \begin{equation}  \label{eq:nextgen_parents_oblique_only}
-p' = p^2 (T_B-T_A) + p (1+T_A-T_B) \;.
-\end{equation}
-
-Solving for $p'>p$ we get the following result.\\
+p' = p^2 (T_B-T_A) + p (1+T_A-T_B) \;,
+\end{equation}
+
+which gives the following result.\\
 
@@
 That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ are missing from \autoref{eq:nextgen_parents_oblique_only}).
-The dynamics are determined solely by differential horizontal transmission of the two phenotypes, that is, the relative tendency of each phenotype to be horizontally transmitted to peers (see~{\autoref{fig:results}c).
+The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers (see~{\autoref{fig:results}c).
 Note that without bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
@@
 Fixation of either cooperation, $\tilde{p}=1$, or defection, 
-$\tilde{p}=0$, are equilibria of Eq.\ \ref{eq:nextgen_parents_vertical_only}, that is, they solve $\tilde{p}'= \tilde{p}$.
-We therefore assume for the remainder of the analysis that $0<\tilde{p}<1$.
-
-If $\alpha=1$, then $\tilde{p}'= \tilde{p}$ is reduced to
+$\tilde{p}=0$, are equilibria of Eq.\ \ref{eq:nextgen_parents_vertical_only}, solving $\tilde{p}'= \tilde{p}$.
+We assume for the remainder of the analysis that $0<\tilde{p}<1$.
+
+If $\alpha=1$, then $\tilde{p}'= \tilde{p}$ reduces to
 \begin{equation}
@@
 and there are no additional equilibria.
-For cooperation to take over the population (for $\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$; that is,
+For cooperation to take over the population (i.e., for $\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$; that is,
 \begin{equation}
@@
 \begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
-With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of cooperation will follow one of the following scenarios, depending on the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}):
+With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of cooperation exhibits one of the following scenarios, depending on the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}):
 
@@
 Cooperation and defection can coexist stably at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:vert_hori_equilibrium}) if there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:results2}b.
-When unstable coexistence occurs, phenotype $A$ will fix if initially at a frequency $p>\tilde{p}^*$, and phenotype $B$ will fix if initially at a frequency $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
 \autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:results2}a and \autoref{fig:results2}b.
@@
 \begin{corollary}[Perfect social association of transmission and cooperation]
-With perfect social association ($\alpha=1$), the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency, $\tilde{p}'>\tilde{p}$, if
+With perfect social association ($\alpha=1$), the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 This condition is obtained from inequality \ref{eq:vert_hori_alpha1_condition_proof}, and the right-hand side equals $\gamma_1$ when $\alpha=1$ (\autoref{eq:cost_boundaries}).
-Perfect social association (horizontal transmission always occurs during the cooperative interaction) is also assumed in the model studied by \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).
+Perfect social association (horizontal transmission always occurs during the cooperative interaction) is also assumed in the model studied by \citet{lewin2017microbes}, and therefore this corollary is equivalent to the result in their eq.~1.
 
@@
 \begin{corollary}[No social association of transmission and cooperation]
-Without social association ($\alpha=0$) cooperation can take over the population if there is horizontal transmission bias for cooperation, $T_A>T_B$, and if either
+Without social association ($\alpha=0$), cooperation can take over the population if there is horizontal transmission bias for cooperation, $T_A>T_B$, and if either
 \begin{equation}
@@
 
-\autoref{fig:results2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in \autoref{eq:vert_hori_equilibrium} and \autoref{eq:cost_boundaries}.
+\autoref{fig:results2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:vert_hori_equilibrium} and \ref{eq:cost_boundaries}.
 If there is horizontal transmission bias for cooperation ($T_A>T_B$) then cooperation can evolve from any initial frequency if the cost is low enough, $c<\gamma_1$ (green area below solid line).
-If the cost is not low enough, cooperation can also evolve if starting from high frequency and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
+If the cost is not low enough, cooperation can also evolve if its initial frequency is high enough and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
 
@@
 First, when cooperators are rare, they will mostly interact with defectors.
-Therefore, for cooperation to increase in frequency and fix, the \emph{effective cost of cooperation} must be lower than the horizontal transmission of cooperation, $1-(1-c)(1-T_B) < T_A$, which is equivalent to the left condition in \autoref{eq:vert_hori_alpha0}.
+Therefore, for cooperation to increase in frequency and fix, the \emph{effective cost of cooperation} must be lower than the horizontal transmission of cooperation, $1-(1-c)(1-T_B) < T_A$, which is equivalent to the first of the two inequalities in \autoref{eq:vert_hori_alpha0}.
 Second, if $T_A$ is not large enough, cooperation will fix if the initial frequency is higher than the threshold $\tilde{p}^*$; thus, this threshold must be below one, which entails $1-(1-c)(1-T_B) < T_A + b(T_A-T_B)$.
@@
 \begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:Intermediate_association}
-Cooperation will increase from rarity if social association is high enough, or specifically if
+Cooperation will increase when rare if social association is high enough; specifically if
   \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
@@
 Otherwise, cooperation can also fix if the horizontal bias is strong, the initial frequency is high, and social association is high, $a_1 < \alpha$ (blue area).
-With horizontal bias for defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area in negative x-axis), and can also increase in rarity and maintain a stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
-Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+With horizontal bias favoring defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
+Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough; $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
 
@@
 
-With both vertical and oblique transmission, $0<v<1$, the recursion system is more complex,
+With both vertical and oblique transmission, $0<v<1$, the recursion system is more complex
 and we focus on local rather than on global stability.
-To proceed, we note that 
-Eq.\ \ref{eq:horizontal} can give $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
+To proceed,  note that 
+Eq.\ \ref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
 %Equation 4 does not give $\hat{p}$---MF
@@
 Eq.\ \ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}).
-We then determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
+Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}),
+determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
 %: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})=\bar{w}(\hat{p}'-\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
@@
 %We now turn to the general case where $T_A \neq T_B$. 
-We apply Eqs.\ \ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} to obtain the function $f(\hat{p})$ (see Appendix~\autoref{sec:appendixA}):
+Applying Eqs.\ \ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} gives the function $f(\hat{p})$ (see Appendix~\autoref{sec:appendixA}):
 
@@
 Clearly the only two equilibria are the fixations  $\hat{p} =  0$ and $\hat{p} = 1$.
-These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (Appendix~\autoref{sec:appendixB}), and
+These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\autoref{sec:appendixB}), where
 \begin{equation}
@@
 \end{equation}
-Therefore with symmetric horizontal transmission, fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary 1.1, namely Eq.\ \ref{eq:equal_transmission}.
+Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary 1.1, namely Eq.\ \ref{eq:equal_transmission}.
 
@@
 Second, if $\beta_1<\beta_3<0$ then 
-$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$, that is, both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
+$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$ so that both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
 Third, if $0<\beta_3$ then 
@@
 
-We define new cost boundaries, $\hat\gamma_1$ and $\hat\gamma_2$,
+Define new cost boundaries, $\hat\gamma_1$ and $\hat\gamma_2$,
 \begin{equation} \label{eq:cost_boundaries_v}
@@
 \end{equation}
-and define a vertical transmission threshold,
+and  a vertical transmission threshold,
 \begin{equation} \label{eq:v_threshold}
@@
 Now, assume $T_A<T_B$.
-For $\beta_3<0$ we need $\hat\gamma_1<c$.
-For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
+$\beta_3<0$ requires $\hat\gamma_1<c$,
+and for $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
 Note that the expression in the square brackets is positive if and only if $v > \hat v$.
-So, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c$ or $v < \hat v$ and $c < \hat\gamma_2$.
-So, for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c < \hat\gamma_1$, or $v < \hat v$ and $c < \min(\hat\gamma_1, \hat\gamma_2)$; and 
-for $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\hat\gamma_2$ or $v < \hat v$ and $\hat\gamma_2<c$.
+Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c$ or $v < \hat v$ and $c < \hat\gamma_2$,
+and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c < \hat\gamma_1$, or $v < \hat v$ and $c < \min(\hat\gamma_1, \hat\gamma_2)$.
+For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\hat\gamma_2$ or $v < \hat v$ and $\hat\gamma_2<c$.
 However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\hat\gamma_2$.
@@
 \begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) and the vertical transmission threshold $\hat v$ (\autoref{eq:v_threshold}) :
 
@@
 
-We constructed an additional model in which social association emerges from the population structure.
-We model a non-overlapping population colonizing a 2D grid of size 100-by-100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
-Each individual is characterized by its phenotype which is either a cooperator, $A$, or a defector $B$.
+Social association may also emerge from a population's structure.
+Consider a  population colonizing a 2D grid of size 100-by-100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
+Each individual is characterized by its phenotype which is either cooperator, $A$, or defector $B$.
 In each generation individuals interact with their neighbors, i.e.
-individuals that inhabit adjacent sites, in a prisoner's dilemma game (\autoref{table:prisoner_payoff}) and in horizontal cultural transmission.
-As before, $T_A$ and $T_B$ are the probabilities to transmit the phenotypes $A$ and $B$ during horizontal transmission.
-At each generation, each individual is chosen to "initiate" interactions with probability 1/2.
-Initiators then interact with a random neighbor for a prisoners’ dilemma game and a random neighbor (with replacement) for horizontal cultural transmission (as both the game and the transmission are symmetrical, the expected number of each of these interactions per individual per generation is 1).
+individuals that inhabit adjacent sites, in a prisoner's dilemma game (\autoref{table:prisoner_payoff}) and with horizontal cultural transmission.
+As before, $T_A$ and $T_B$ are the probabilities of transmitting phenotypes $A$ and $B$ during horizontal transmission.
+At each generation, each individual is chosen to "initiate" interactions with probability 1/2.\ %"with probability 1/2" not clear - MWF
+Initiators then interact with a random neighbor in a prisoners' dilemma game and a random neighbor (with replacement) for horizontal cultural transmission (as both the game and the transmission are symmetrical, the expected number of each of these interactions per individual per generation is 1).
 Therefore, the effective social association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/m$, where $m$ is the number of neighbors.
 On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
-
-The order of the interactions across the lattice on each generation is random.
-After all interactions take place, individual's fitness is determined by
+%How are A, B initialized on the grid? – MWF
+
+The order of the interactions across the lattice at each generation is random.
+After all interactions take place, and individual's fitness is determined by
 $w = 1 + b \cdot n_b - c \cdot n_c$,
-where $n_b$ is the number interactions of that individual with cooperative neighbors, and $n_c$ is the total number of interactions of that individual ($n_b \le n_c$).
+where $n_b$ is the number interactions of that individual with cooperative neighbors, and $n_c$ is the total number of interactions that that individual  had ($n_b \le n_c$).
 Then a new generation is generated.
 Each site is colonized by an offspring of one of the individuals that inhabit either this site or one of the neighboring sites.
-The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness in his neighborhood.
+The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness in its neighborhood.
 Offspring then have the same phenotype as their parents.
@@
 \autoref{fig:spatial} shows that the highest cooperation cost to benefit ratio ($c/b$) that permits the evolution of cooperation in simulations of the spatial model is roughly $\alpha \cdot T / (1-T)$, where $T=T_A=T_B$ is the horizontal transmission rate.
-This agrees with the condition we derived in Corollary~\ref{sec:sym_hor_trans} for a population without population structure.
-This demonstrates that the social association parameter $\alpha$ can emerge from local interactions between individuals in a structured population.
+This agrees with the condition we derived in Corollary~\ref{sec:sym_hor_trans} for a population without population structure, and
+this demonstrates that the social association parameter $\alpha$ can emerge from local interactions between individuals in a structured population.
 
@@
 We studied the evolution of cooperation under non-vertical transmission using deterministic discrete-time evolutionary models with fitnesses in the form of payoffs from a prisoner's dilemma game. 
-Under oblique and horizontal cultural transmission, a horizontal transmission bias for the cooperative phenotype was found to be sufficient and necessary for evolution of cooperation (Result~\autoref{result:obli_hori}).
+Under oblique and horizontal cultural transmission, horizontal transmission bias in favor of the cooperative phenotype was found to be necessary and sufficient for evolution of cooperation (Result~\autoref{result:obli_hori}).
 Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the association between cooperation and transmission (Results~\autoref{result:vert_hori} and~\autoref{result:vert_obli_hori}).
@@
 
-We tested the applicability of our analytic results to a complex spatial stochastic model.
-Our derived condition provide a good approximation to simulation results  (\autoref{fig:spatial}), demonstrating that association between cooperation and transmission can arise in a structured population simply because the choice of individuals for social interactions is small.
+We tested the applicability of our analytic results.
+Our derived analytic condition provided a good approximation to simulation results for a complex spatial stochastic model  (\autoref{fig:spatial}), demonstrating that association between cooperation and transmission can arise in a structured population simply because the choice of individuals for social interactions is very restricted.
 
@@
 Their results are very sensitive to this genetic modification: without it, the conditions for invasion of the altruistic phenotype reduce to Hamilton's rule.
-Further work is needed to include such genetic modification of cultural transmission to our model.
-
-\citet{woodcock2006significance} has previously argued the significance of non-vertical transmission for the evolution of cooperation.
+Further work is needed to incorporate such genetic modification of cultural transmission into our model.
+
+\citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation.
 He executed simulations with prisoner's dilemma payoffs but without horizontal transmission or social association ($\alpha=0$).
-Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a significant duration of time.
+Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
 Our results provide strong evidence for his hypothesis that horizontal transmission can have an important role in the evolution of cooperation.
@@
 \citet{Eshel1982} showed that altruism can evolve when there is enough \emph{assortative meeting}, namely, a tendency for individuals to interact within their phenotypic group.
-\citet{Fletcher2009assortment} have further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group; see also \citet{Bijma2010assortment}.
-They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate such assortment, like population structure, repeated interactions, and individual recognition.
+\citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
+They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
 Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and partner for transmission.
@@
 How does non-vertical transmission generate assortment? 
-\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors}, 
-who suggested that microbes that manipulate their hosts to act altruistically can be favored by selection, and may help explain the evolution of cooperation. 
+\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} 
+suggested that microbes that manipulate their hosts to act altruistically can be favored by selection, which may help to explain the evolution of cooperation. 
 %Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
 %Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others. 
-From the kin selection point-of-view, if microbes can be transmitted \emph{horizontally} from one host to another during host interactions, then following horizontal transmission the recipient host will carry microbes that are closely related to the microbes of the donor host,
+From the kin selection point-of-view, if microbes can be transmitted \emph{horizontally} from one host to another during host interactions, then following horizontal transmission the recipient host will carry microbes that are closely related to those of the donor host,
 even when the two hosts are (genetically) unrelated. 
-However, we are more interested in the assortment point-of-view:
-infection by behavior-determining microbes during interactions effectively generates assortment because receipient of help may be infected by the behavior-determining microbe and therefore become a helper.
+From the assortment point-of-view,
+infection by behavior-determining microbes during interactions effectively generates assortment because a recipient of help may be infected by a behavior-determining microbe and consequently become a helper.
 Cultural horizontal transmission can similarly generate assortment between the cooperative phenotype and the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, which in our model occurs with probability $\alpha$.
@@
 environment''~\citep{Fletcher2009assortment} is generated not because \emph{the helper is likely to be helped}, but rather because \emph{the helped is likely to become a helper}.
-These conclusions highlight the importance of non-vertical cultural transmission for explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.
+These conclusions highlight the importance of non-vertical cultural transmission in explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.
 
@@
 \end{equation}
-we substitute $p'$ using \autoref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ using \autoref{eq:nextgen_parents_simplified}, we have
+ substitute for $p'$ using \autoref{eq:nextgen_adults_slimpify} and for $\tilde{p}'$ using \autoref{eq:nextgen_parents_simplified}, we have
 \begin{equation}\label{eq:appendix_b_2}
@@
 where $\bar{w} = 1 + \hat{p}(b-c)$. 
-We define $f(\hat{p})$ as
+Define $g(\hat{p})$ as
 \begin{equation} \label{eq:appendix_define_f}
 \begin{aligned}
-      f(\hat{p}) &= \bar{w}(\hat{p}' - \hat{p})
-\end{aligned}
-\end{equation}
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we simplify \autoref{eq:appendix_define_f} to 
+      g(\hat{p}) &= \bar{w}(\hat{p}' - \hat{p})
+\end{aligned}
+\end{equation}
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics,  \autoref{eq:appendix_define_f} simplifies to 
 eqs.~\ref{eq:general_case_polynomial}-\ref{eq:polynomial_coefficients}.
@@
 
-Denote $f(p)=\lambda(p'-p)$, where $\lambda>0$, and assume $f(p^*)=0$; i.e., $p^*$ is an equilibrium.
+Let $f(p)=\lambda(p'-p)$, where $\lambda>0$, and assume $f(p^*)=0$; i.e., $p^*$ is an equilibrium.
 %HOW DO YOU KNOW $p^*\in(0,1)$?--MF
@@
 \end{aligned}\end{equation}
-Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any $0<p<\epsilon$, it is guaranteed that $0<p'<p$, that is, $p'$ is closer than $p$ to zero.
+Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any $0<p<\epsilon$, it is guaranteed that $0<p'<p$; that is, $p'$ is closer to zero than $p$.
 
@@
 \end{aligned}\end{equation}
-Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ it is guaranteed that $1-p'<1-p$, that is, $p'$ is closer than $p$ to one.
+Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
 \end{appendices}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 
@@
 \caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
-  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ vs. the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
+  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation, $\tilde{p}'$, vs.\ that in the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
   The dashed black line is $\tilde{p}'=\tilde{p}$.
   The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
-  When the curves are above the dashed line, $\tilde'{p}>\tilde{p}$, then $\tilde{p}$ increase.
-  When the curves are below the dashed line, $\tilde'{p}<\tilde{p}$, then $\tilde{p}$ decreases.
+  When the curves are above the dashed line, $\tilde{p}'>\tilde{p}$, and $\tilde{p}$ increases.
+  When the curves are below the dashed line, $\tilde{p}'<\tilde{p}$, and $\tilde{p}$ decreases.
   The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
@@
 \end{figure}
+
+\pagebreak
 
@@
 In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
-(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
-(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
+(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines, respectively. 
+(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines, respectively.
 Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
@@
 \end{figure}
+\pagebreak
 
@@
   \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
-  The curves show the frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ vs. the current generation $\hat{p}$ (\autoref{eq:horizontal}).
+  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
   The dashed black line is $\hat{p}'=\hat{p}$.
   The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
-  When $\hat{p} < \hat{p}^*$ then the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
-  When $\hat{p} > \hat{p}^*$ then the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
+  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
+  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
   The orange curve for wich the polymorphic equilibrium is stable is given by  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
@@
   \end{figure}
+\pagebreak
 
@@
   Here, population size is $10,000$ (100-by-100 grid); cost of cooperation, $c=0.05$.
-50 simulations were executed per parameter set.
+50 simulations were executed for each parameter set.
 Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.

### 2020-09-22 ms/main.tex
revise fig 4 legend

@@
   \includegraphics[scale=1]{figure1.pdf}
-  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
+  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{social association} parameter.
+  }
   \label{fig:horizontal}
@@
 unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
-    The vertical transmission rate $v$ is on the x-axis.
-    Horizontal transmission bias (\textbf{a}) for cooperation, $T_A>T_B$ and (\textbf{b}) for defection, $T_A<T_B$.
-    Cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines in figures \textbf{(a)}, \textbf{(b)}. 
-    Soical association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines in figures \textbf{(c)}, \textbf{(d)}.
-    (\textbf{a}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.
-    (\textbf{b}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.
-    (\textbf{c}), $b=1.2$, $T_A=0.5$, $T_B = 0.4$, $c=0.5$.
-    (\textbf{d}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $c=0.5$.}
+	In all cases the vertical transmission rate $v$ is on the x-axis.
+	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+    Horizontal transmission is biased in (\textbf{a,c}) for cooperation, $T_A>T_B$, and in (\textbf{b,d}) for defection, $T_A<T_B$.    
+    Here, $T_A = 0.5$, and
+    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
+    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
+    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
+    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
+    }
     \label{fig:result3}

### 2020-09-22 ms/main.tex
revise fig 5 legend

@@
   When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
-  The orange curve for wich the polymorphic equilibrium is stable is given by  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
-  The blue curve for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
+  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
+  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
   }

### 2020-09-23 ms/main.tex
formatting
revised result 3 corollaries

@@
 \autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:results2}a and \autoref{fig:results2}b.
+\\
 
@@
 \begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:Intermediate_association}
-Cooperation will increase when rare if social association is high enough; specifically if
+Cooperation will increase from rarity if social association is high enough, specifically if
   \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
@@
 \end{result}
-These conditions are illustrated in \autoref{fig:result3}a and \autoref{fig:result3}b.
+These conditions are illustrated in \autoref{fig:result3}ab.
 
@@
 The next corollary deals with such a condition.
-\begin{corollary}[Condition for cooperation to increase when initially rare]
+\\
+
+\begin{corollary}[Condition for cooperation to increase from rarity]
   If the initial frequency of cooperation is very close to zero, $\hat{p}_0 \approx 0$, then its frequency will increase if 
@@
 
-Note that the right-hand side equals $\hat\gamma_1$.
-This condition follows from combining the conditions for fixation of cooperation and for stable coexistence.
-
-In general, these conditions cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
+%Note that the right-hand side equals $\hat\gamma_1$.
+This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
+Importantly, increasing social association $\alpha$ increases maximum cost of cooperation $\hat\gamma_1$ that allows cooperation to increase from rarity (i.e.
+$\partial \hat\gamma_1 / \partial \alpha > 0$).
+
+In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
 Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
 \\
-\begin{corollary}[Necessity condition for fixation of cooperation.]
-  Fixation of cooperation is possible only when
+\begin{corollary}[Necessary condition for fixation of cooperation]
+  Fixation of cooperation is possible only if the vertical transmission rate is high enough,
   \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
@@
 \end{corollary}
-When there is horizontal transmission bias for cooperation, fixation can occured for every value of vertical transmission because $\hat{v}<0$.
-However, if the the horizontal bias favours defection, for fixation of cooperation to occur the vertical transmission must be higer than $\hat{v}$.
+%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
+Note that this condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
+When horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate, i.e. $\hat{v}<0$.
+In contrast, if the horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation, see \autoref{fig:result3}bd.
 \\
 
-We already examine the effect of social association in the case of perfect vertical transmission ($v=1$). Now we'll move to the genral case where $0<v\leq 1$.
-We denote the social association boundaries of the general case by
+In corollary~\autoref{corollary:Intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
+A more general case can be stated for $0 < v \leq 1$.
+Consider the social association boundaries 
 \begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting_general_case}
   \hat{a}_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
-  \hat{a}_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A}.
+  \hat{a}_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A} \;.
 \end{aligned}\end{equation}
-\emph{Corollary~\autoref{corollary:Intermediate_association}} is true for the general but with new boundaries coefficients $\hat{a}_1$, $\hat{a}_2$.
-\autoref{fig:result3}c and \autoref{fig:result3}d illustrate this result.
-
-%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
+Then the following applies.
+\\
+
+\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:Intermediate_association}
+Cooperation will increase from rarity if social association is high enough, specifically if
+  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
+    \begin{aligned}
+    T_A > T_B &\;\; \text{and} \;\; \hat a_2 < \alpha, \quad \text{or} \\
+    T_A < T_B &\;\; \text{and} \;\; \hat a_1 < \alpha \,.
+    \end{aligned}
+    \end{equation} 
+\end{corollary}
+\autoref{fig:result3}cd illustrates this conditions.
+
+Interestingly, when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$.
+Therefore, when there is horizontal transmission bias for cooperation, $T_A>T_B$, then vertical transmission hinders the evolution of cooperation ($\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$).
+In contrast, when there is horizontal transmission bias for defection, vertical transmission facilitates the evolution of cooperation ($\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$).
 

### 2020-09-24 ms/main.tex
reorder conditions in result 3

@@
 \item \emph{Stable Coexistence}: 
-    if \emph{(v)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$; or
-    if \emph{(vi)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_1$.
+    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_1$; or 
+    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$.
 \item \emph{Unstable coexistence}:

### 2020-09-29 ms/main.tex
Add analysis for T_A > T_B before result 3
moved tables to end; revised new section by DC; started new discussion par to summarize corollaries

@@
 
-%%% Table: payoff matrix
-\bigskip
-\begin{table}[h]
-\centering
-\caption{\textbf{Payoff matrix for prisoner's dilemma.}
-The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
-$b>c>0$.
-}
-\begin{tabular}{lll}
-\toprule
-           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
-$\phi_1=A$ & $1+b-c$ & $1-c$ \\
-$\phi_1=B$ & $1+b$   & $1$
-\\ \bottomrule
-\end{tabular}
-\label{table:prisoner_payoff}
-\end{table}
-\bigskip
-%%%
-
 Social interactions occur randomly:
@@
 
-%%% Table: interactions
-\bigskip
-\begin{table}[]
-\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
-\begin{tabular}{@{}llllll@{}}
-\toprule
-\multirow{2}{*}{Phenotype $\phi_1$} &
-  \multirow{2}{*}{Phenotype $\phi_2$} &
-  \multirow{2}{*}{Frequency} &
-  \multirow{2}{*}{Fitness of $\phi_1$} &
-  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
-    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
-$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
-$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
-\end{tabular}
-\label{table:interactions}
-\end{table}
-\bigskip
-%%%
-
 Therefore, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 \autoref{table:vars_params} summarizes the model variables and parameters.
-
-%%% Table: variables and parameters
-\bigskip
-\begin{table}[h]
-\centering
-\caption{\textbf{Model variables and parameters.}
-}
-\begin{tabular}{lll}
-\toprule
-Symbol & Description & Values \\ \cmidrule(r){1-3}
-$A$ & Cooperator phenotype & \\
-$B$ & Defector phenotype & \\
-$p$ & Frequency of phenotype $A$ among adults & $[0,1]$ \\
-$\tilde p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
-$\hat p$ & Frequency of phenotype $A$ among juveniles & $[0,1]$ \\
-$v$ & Vertical transmission rate & $[0,1]$ \\
-$c$ & Cost of cooperation & $(0,1)$ \\
-$b$ & Benefit of cooperation & $c<b$ \\
-$\alpha$ & Probability of social association & $[0,1]$ \\
-$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $[0,1]$ \\
-\\ \bottomrule
-\end{tabular}
-\label{table:vars_params}
-\end{table}
-%\bigskip
-%%%
 
@@
 
-These conditions are illustrated in \autoref{fig:results2}.
-
-Cooperation and defection can coexist stably at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:vert_hori_equilibrium}) if there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:results2}b.
+These conditions are illustrated in \autoref{fig:result2}.
+
+Cooperation and defection can coexist stably at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:vert_hori_equilibrium}) if there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:result2}b.
 When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:results2}a and \autoref{fig:results2}b.
+\autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
 \\
 
-\begin{corollary}[Symmetric horizontal transmission] \label{sec:sym_hor_trans}
+\begin{corollary}[Symmetric horizontal transmission] 
+\label{sec:cor_equal_transmission}
 If $T=T_A=T_B$, then cooperation will take over the population if
@@
 
-\autoref{fig:results2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:vert_hori_equilibrium} and \ref{eq:cost_boundaries}.
+\autoref{fig:result2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:vert_hori_equilibrium} and \ref{eq:cost_boundaries}.
 If there is horizontal transmission bias for cooperation ($T_A>T_B$) then cooperation can evolve from any initial frequency if the cost is low enough, $c<\gamma_1$ (green area below solid line).
@@
 
-\autoref{fig:results2}c demonstrates these conditions.
+\autoref{fig:result2}c demonstrates these conditions.
 With horizontal transmission bias for cooperation ($T_A>T_B$), cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
@@
 \end{equation}
-Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary 1.1, namely Eq.\ \ref{eq:equal_transmission}.
+Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{sec:cor_equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
 
@@
 
-Now, assume $T_A<T_B$.
+First, assume $T_A<T_B$.
 $\beta_3<0$ requires $\hat\gamma_1<c$,
@@
 However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\hat\gamma_2$.
-A similar analysis can be made when $T_A>T_B$.
+
+Second, when $T_A>T_B$
+$\beta_3>0$ requires $\hat\gamma_1 > c$. 
+For $\beta_1<\beta_3$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] < bv\alpha T_B + (1+b)(T_A-T_B)$.
+Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \hat\gamma_2 $ or $v < \hat v$ and $c > \hat\gamma_2$.
+But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \hat\gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
 
@@
 \begin{corollary}[Necessary condition for fixation of cooperation]
+\label{sec:cor_vhat}
   Fixation of cooperation is possible only if the vertical transmission rate is high enough,
@@
 Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the association between cooperation and transmission (Results~\autoref{result:vert_hori} and~\autoref{result:vert_obli_hori}).
-Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in \autoref{fig:results2}).
-% TODO figure for result 3
-% TODO something about v-hat
-
-We tested the applicability of our analytic results.
-Our derived analytic condition provided a good approximation to simulation results for a complex spatial stochastic model  (\autoref{fig:spatial}), demonstrating that association between cooperation and transmission can arise in a structured population simply because the choice of individuals for social interactions is very restricted.
+Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2}-\ref{fig:result3}).
+
+We find that increasing social association ($\alpha$) increases the opportunity for evolution of cooperation (corollary X, \autoref{fig:result2}c and \autoref{fig:result3}cd). 
+Similarly, a horizontal transmission bias for cooperation ($T_A-T_B$) will also facilitate its evolution (corollary X, \autoref{fig:result2}}.
+The situation with vertical/oblique transmission ($v$) is more complex. 
+When there is horizontal transmission bias for cooperation ($T_A>T_B$), increasing the rate of oblique transmission ($1-v$) will facilitate the evolution of cooperation (\autoref{fig:result3}ac).
+However, when the bias if for defection ($T_A<T_B$), high rates of vertical transmission ($v$) are advantageous for cooperation.
+Nevertheless, to reach fixation of cooperation in the population, there must be a sufficient rate of vertical transmission ($v>\hat v$, Corollary~\autoref{sec:cor_vhat}).
+% TODO carry on summarizing corollaries here
+
+Our analytic conditions derived for a deterministic well-mixed model provides a good approximation to results of simulations of a complex spatial stochastic model  (\autoref{fig:spatial}).
+In this spatial model, individuals can only interact with and transmit to their neighbors on a grid.
+This demonstrates that social association between cooperation and transmission can arise in a structured population in which interactions are local.
 
@@
 This mechanism does not require population structure, repeated interactions, or individual recognition.
-We show that high levels of such social association greatly increase the potential for evolution of cooperation (\autoref{fig:results2}).
+We show that high levels of such social association greatly increase the potential for evolution of cooperation (\autoref{fig:result2}).
 With enough social association ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$, see Result~\autoref{result:vert_hori}).
@@
 
+\section*{Tables}
+
+%%% Table: payoff matrix
+\bigskip
+\begin{table}[h]
+\centering
+\caption{\textbf{Payoff matrix for prisoner's dilemma.}}
+\begin{tabular}{lll}
+\toprule
+           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
+$\phi_1=A$ & $1+b-c$ & $1-c$ \\
+$\phi_1=B$ & $1+b$   & $1$
+\\ \bottomrule
+\end{tabular}
+\label{table:prisoner_payoff}
+\caption*{
+The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
+$0<b<c$.
+}
+\end{table}
+\bigskip
+%%%
+
+%%% Table: interactions
+\bigskip
+\begin{table}[h]
+\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
+\begin{tabular}{@{}llllll@{}}
+\toprule
+\multirow{2}{*}{Phenotype $\phi_1$} &
+  \multirow{2}{*}{Phenotype $\phi_2$} &
+  \multirow{2}{*}{Frequency} &
+  \multirow{2}{*}{Fitness of $\phi_1$} &
+  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
+    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
+$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
+$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
+\end{tabular}
+\label{table:interactions}
+\end{table}
+\bigskip
+%%%
+
+%%% Table: variables and parameters
+\bigskip
+\begin{table}[h]
+\centering
+\caption{\textbf{Model variables and parameters.}
+}
+\begin{tabular}{lll}
+\toprule
+Symbol & Description & Values \\ \cmidrule(r){1-3}
+$A$ & Cooperator phenotype & \\
+$B$ & Defector phenotype & \\
+$p$ & Frequency of phenotype $A$ among adults & $[0,1]$ \\
+$\tilde p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
+$\hat p$ & Frequency of phenotype $A$ among juveniles & $[0,1]$ \\
+$v$ & Vertical transmission rate & $[0,1]$ \\
+$c$ & Cost of cooperation & $(0,1)$ \\
+$b$ & Benefit of cooperation & $c<b$ \\
+$\alpha$ & Probability of social association & $[0,1]$ \\
+$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $[0,1]$ \\
+\\ \bottomrule
+\end{tabular}
+\label{table:vars_params}
+\end{table}
+%\bigskip
+%%%
+
+\newpage
+
 \section*{Figures}
 %%% Figure: model illustration
-\begin{figure}[thb]
+\begin{figure}[h]
   \centering
@@
 %%% Figure: coexistence map - without oblique transmission
-\begin{figure}[htb]
+\begin{figure}[h]
 \centering
-\includegraphics[scale = 0.75]{coexistence_without_oblique.pdf}
+\includegraphics[scale = 0.55]{coexistence_without_oblique.pdf}
 \caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
@@
 
-\pagebreak
-
 %%% Figure: Boundaries figure - only vertical
 
-\begin{figure}[htb]
+\begin{figure}[h]
   \centering       
@@
   	}
-    \label{fig:results2}
+    \label{fig:result2}
 \end{figure}
-\pagebreak
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[h]
   \centering       
@@
 \end{figure}
-\pagebreak
 
 %%% Figure: coexistence map - with oblique transmission
-\begin{figure}[htb]
+\begin{figure}[h]
   \centering
-  \includegraphics{coexistence_with_oblique.pdf}
+  \includegraphics[scale=0.55]{coexistence_with_oblique.pdf}
   \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
@@
   \end{figure}
-\pagebreak
 
 %%% Figure: frequency dynamics
-\begin{figure}[htb]
+\begin{figure}[h]
   \centering
@@
 \end{figure}
-\pagebreak
 
 %%% Figure: Spatial model
-\begin{figure}[htb]
+\begin{figure}[h]
   \centering

### 2020-09-29 ms/main.tex
sec:cor -> corollary; more small revisions

@@
 \begin{corollary}[Symmetric horizontal transmission] 
-\label{sec:cor_equal_transmission}
+\label{corollary:equal_transmission}
 If $T=T_A=T_B$, then cooperation will take over the population if
@@
 
-\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:Intermediate_association}
+\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:intermediate_association}
 Cooperation will increase from rarity if social association is high enough, specifically if
@@
 \end{equation}
-Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{sec:cor_equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
+Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{corollary:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
 
@@
 \begin{corollary}[Necessary condition for fixation of cooperation]
-\label{sec:cor_vhat}
+\label{corollary:vhat}
   Fixation of cooperation is possible only if the vertical transmission rate is high enough,
@@
 
-In corollary~\autoref{corollary:Intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
+In Corollary~\autoref{corollary:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
 A more general case can be stated for $0 < v \leq 1$.
@@
 
-\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:Intermediate_association}
+\begin{corollary}[Intermediate association of transmission and cooperation]
 Cooperation will increase from rarity if social association is high enough, specifically if
@@
 We find that increasing social association ($\alpha$) increases the opportunity for evolution of cooperation (corollary X, \autoref{fig:result2}c and \autoref{fig:result3}cd). 
-Similarly, a horizontal transmission bias for cooperation ($T_A-T_B$) will also facilitate its evolution (corollary X, \autoref{fig:result2}}.
-The situation with vertical/oblique transmission ($v$) is more complex. 
+Similarly, a horizontal transmission bias for cooperation ($T_A-T_B$) will also facilitate its evolution (corollary X, \autoref{fig:result2}).
+The effect of vertical/oblique transmission is more complex. 
 When there is horizontal transmission bias for cooperation ($T_A>T_B$), increasing the rate of oblique transmission ($1-v$) will facilitate the evolution of cooperation (\autoref{fig:result3}ac).
-However, when the bias if for defection ($T_A<T_B$), high rates of vertical transmission ($v$) are advantageous for cooperation.
-Nevertheless, to reach fixation of cooperation in the population, there must be a sufficient rate of vertical transmission ($v>\hat v$, Corollary~\autoref{sec:cor_vhat}).
+However, when the bias is for defection ($T_A<T_B$), high rates of vertical transmission ($v$) are advantageous for cooperation.
+Nevertheless, to reach fixation of cooperation in the population, there must be a sufficient rate of vertical transmission ($v>\hat v$, Corollary~\autoref{corollary:vhat}).
 % TODO carry on summarizing corollaries here
 
-Our analytic conditions derived for a deterministic well-mixed model provides a good approximation to results of simulations of a complex spatial stochastic model  (\autoref{fig:spatial}).
-In this spatial model, individuals can only interact with and transmit to their neighbors on a grid.
-This demonstrates that social association between cooperation and transmission can arise in a structured population in which interactions are local.
+The results that we derived for a deterministic well-mixed model provide a good approximation to results of simulations of a complex stochastic spatial model  (\autoref{fig:spatial}).
+In this spatial model, individuals can only interact with and transmit to their neighbors.
+This model demonstrates that social association between cooperation and transmission can arise in a structured population in which both types of interactions are local.
 

### 2020-09-29 ms/main.tex
revised corollaries and derivatives on the boundaries; finished summarizing corollaries in discussion; revised spatial model section, figures, and conclusions

@@
 
+\begin{corollary}[No social association of transmission and cooperation]
+\label{corollary:alpha0}
+Without social association ($\alpha=0$), cooperation can take over the population if there is horizontal transmission bias for cooperation, $T_A>T_B$, and if either
+\begin{equation}
+\label{eq:vert_hori_alpha0}
+c < \frac{T_A-T_B}{1-T_B}
+\quad \text{or} \quad
+\tilde{p}_0 > \tilde{p}^* = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B)} \;.
+\end{equation}
+\end{corollary}
+
+\autoref{fig:result2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:vert_hori_equilibrium} and \ref{eq:cost_boundaries}.
+If there is horizontal transmission bias for cooperation ($T_A>T_B$) then cooperation can evolve from any initial frequency if the cost is low enough, $c<\gamma_1$ (green area below solid line).
+If the cost is not low enough, cooperation can also evolve if its initial frequency is high enough and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
+
+We can interpret these condition as follows.
+First, when cooperators are rare, they will mostly interact with defectors.
+Therefore, for cooperation to increase in frequency and fix, the \emph{effective cost of cooperation} must be lower than the horizontal transmission of cooperation, $1-(1-c)(1-T_B) < T_A$, which is equivalent to the first of the two inequalities in \autoref{eq:vert_hori_alpha0}.
+Second, if $T_A$ is not large enough, cooperation will fix if the initial frequency is higher than the threshold $\tilde{p}^*$; thus, this threshold must be below one, which entails $1-(1-c)(1-T_B) < T_A + b(T_A-T_B)$.
+That is, the effective cost of cooperation must be lower than the combined effect of horizontal transmission of cooperation, $T_A$, and the benefit of cooperation multiplied by the transmission bias, $b(T_A-T_B)$.
+\\
+
 \begin{corollary}[Perfect social association of transmission and cooperation]
+\label{corollary:alpha1}
 With perfect social association ($\alpha=1$), the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if
@@
 Thus, inequality~\ref{eq:vert_hori_alpha1} entails that cooperation can evolve if the effective cost of cooperation is less than the effective benefit during an interaction between a cooperator and a defector.
-\\
-
-\begin{corollary}[No social association of transmission and cooperation]
-Without social association ($\alpha=0$), cooperation can take over the population if there is horizontal transmission bias for cooperation, $T_A>T_B$, and if either
-\begin{equation}
-\label{eq:vert_hori_alpha0}
-c < \frac{T_A-T_B}{1-T_B}
-\quad \text{or} \quad
-\tilde{p}_0 > \tilde{p}^* = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B)} \;.
-\end{equation}
-\end{corollary}
-
-\autoref{fig:result2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:vert_hori_equilibrium} and \ref{eq:cost_boundaries}.
-If there is horizontal transmission bias for cooperation ($T_A>T_B$) then cooperation can evolve from any initial frequency if the cost is low enough, $c<\gamma_1$ (green area below solid line).
-If the cost is not low enough, cooperation can also evolve if its initial frequency is high enough and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
-
-We can interpret these condition as follows.
-First, when cooperators are rare, they will mostly interact with defectors.
-Therefore, for cooperation to increase in frequency and fix, the \emph{effective cost of cooperation} must be lower than the horizontal transmission of cooperation, $1-(1-c)(1-T_B) < T_A$, which is equivalent to the first of the two inequalities in \autoref{eq:vert_hori_alpha0}.
-Second, if $T_A$ is not large enough, cooperation will fix if the initial frequency is higher than the threshold $\tilde{p}^*$; thus, this threshold must be below one, which entails $1-(1-c)(1-T_B) < T_A + b(T_A-T_B)$.
-That is, the effective cost of cooperation must be lower than the combined effect of horizontal transmission of cooperation, $T_A$, and the benefit of cooperation multiplied by the transmission bias, $b(T_A-T_B)$.
 \\
@@
 \begin{corollary}[Condition for cooperation to increase from rarity]
+\label{corollary:rarity}
   If the initial frequency of cooperation is very close to zero, $\hat{p}_0 \approx 0$, then its frequency will increase if 
@@
 This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
-Importantly, increasing social association $\alpha$ increases maximum cost of cooperation $\hat\gamma_1$ that allows cooperation to increase from rarity (i.e.
-$\partial \hat\gamma_1 / \partial \alpha > 0$).
+Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \hat\gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
+Similarly, increasing the horizontal transmission of cooperation increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), making it easier for cooperation to evolve.
+However, increasing the horizontal transmission of defection can either increase or decrease the boundary, making it easier or harder for cooperation to evolve, respectively, depending if $T_A$ is high or low (i.e.
+if $T_A>1/(1+bv\alpha)$ or below).
+%($\text{sign}\big(\partial \hat\gamma_1 / \partial T_B \big)= \text{sign}\big(b v \alpha T_A - (1-T_A)\big)$).
 
@@
 \end{aligned}\end{equation}
+Note that when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$.
+Similarly, $\partial \hat a_1 / \partial T_A < 0$, $\partial \hat a_2 / \partial T_A < 0$, $\partial \hat a_2 / \partial T_B > 0$, and $\text{sign}(\partial \hat a_1 / \partial T_B) = \text{sign}\big(T_A (1+b-c) - (1-T_A)cv\big)$.
+
 Then the following applies.
@@
 \begin{corollary}[Intermediate association of transmission and cooperation]
+\label{corollary:intermediate_association_res3}
 Cooperation will increase from rarity if social association is high enough, specifically if
@@
 
-Interestingly, when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$.
-Therefore, when there is horizontal transmission bias for cooperation, $T_A>T_B$, then vertical transmission hinders the evolution of cooperation ($\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$).
-In contrast, when there is horizontal transmission bias for defection, vertical transmission facilitates the evolution of cooperation ($\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$).
+Note that increasing the horizontal transmission of cooperation, $T_A$, decreases both boundaries ($\partial \hat a_1 / \partial T_A, \partial \hat a_2 / \partial T_A < 0$), thus facilitating evolution of cooperation.
+Increasing the horizontal transmission of defection, increases one boundary, ($\partial \hat a_2 / \partial T_B > 0$).
+So, if there is horizontal bias for cooperation ($T_A>T_B$), decreasing that bias will make it harder for cooperation to evolve.
+However, if there is horizontal bias for defection ($T_A<T_B$) then the effect of further increasing the horizontal transmission of defection, $T_B$, can either increase or decrease the threshold $\hat\alpha_1$, making it harder or easier for cooperation to evolve, respectively, depending if horizontal transmission of cooperation ($T_A$) is high or low (i.e.
+if $T_A > cv/(1+b-c+cv)$ or below).
+
+Interestingly, when there is horizontal transmission bias for cooperation ($T_A>T_B$), then vertical transmission hinders the evolution of cooperation ($\partial \hat a_2 / \partial v > 0$).
+In contrast, when there is horizontal transmission bias for defection ($T_A<T_B$), vertical transmission facilitates the evolution of cooperation ($\partial \hat a_1 / \partial v < 0$).
+\\
 
@@
 where $n_b$ is the number interactions of that individual with cooperative neighbors, and $n_c$ is the total number of interactions that that individual  had ($n_b \le n_c$).
-Then a new generation is generated.
-Each site is colonized by an offspring of one of the individuals that inhabit either this site or one of the neighboring sites.
-The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness in its neighborhood.
+Then a new generation is generated, and sites can be settled by offspring of any parent, not just neighbor parents.
+Thus, selection is global, rather than local, in accordance with our deterministic model.
+The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness of all potential parents.
 Offspring then have the same phenotype as their parents.
 
-\autoref{fig:spatial} shows that the highest cooperation cost to benefit ratio ($c/b$) that permits the evolution of cooperation in simulations of the spatial model is roughly $\alpha \cdot T / (1-T)$, where $T=T_A=T_B$ is the horizontal transmission rate.
-This agrees with the condition we derived in Corollary~\ref{sec:sym_hor_trans} for a population without population structure, and
-this demonstrates that the social association parameter $\alpha$ can emerge from local interactions between individuals in a structured population.
+\autoref{fig:spatial} shows that the highest cost of cooperation  ($c$) that permits the evolution of cooperation in simulations of the spatial model roughly agrees with the conditions derived in Result 2.
+Simulating a spatial model with local selection (i.e.
+sites can only be settled by offspring of neighbor parents) had only a minor affect, eliminating the stable coexistence.
+
+This comparison between the deterministic well-mixed model and the stochastic spatial model demonstrates that the derived conditions can be useful for predicting the dynamics of complex scenarios. 
+Moreover, our spatial model shows how social association ($\alpha$) can emerge from local interactions between individuals in a structured population.
 
@@
 Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the association between cooperation and transmission (Results~\autoref{result:vert_hori} and~\autoref{result:vert_obli_hori}).
+Importantly, cooperation can increase from rarity (i.e. invade a population of defectors) if and only if (inequality~\ref{eq:unequal_transmission_from_rarity_general_case}),
+\begin{equation}
+c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;,
+\end{equation}
+that is, if the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
 Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2}-\ref{fig:result3}).
 
-We find that increasing social association ($\alpha$) increases the opportunity for evolution of cooperation (corollary X, \autoref{fig:result2}c and \autoref{fig:result3}cd). 
-Similarly, a horizontal transmission bias for cooperation ($T_A-T_B$) will also facilitate its evolution (corollary X, \autoref{fig:result2}).
-The effect of vertical/oblique transmission is more complex. 
+We find that increasing social association ($\alpha$) increases the opportunity for evolution of cooperation (Corollaries \ref{corollary:intermediate_association} and \ref{corollary:intermediate_association_res3}, Figures~\ref{fig:result2}c and \ref{fig:result3}cd).
+Without social association, the benefit of cooperation cannot facilitate its evolution; cooperation can only succeed under horizontal transmission bias ($T_A>T_B$, Corollary~\ref{corollary:alpha0}). 
+Indeed, horizontal transmission plays a major role in the evolution of cooperation.
+Mostly, increasing the transmission of cooperation ($T_A$) or decreasing the transmission of defection ($T_B$) facilitates the evolution of cooperation (Corollaries~\ref{corollary:rarity} and~\ref{corollary:intermediate_association_res3}, \autoref{fig:result2}).
+However, in specific cases increasing the transmission of defection can be advantageous for cooperation (Corollaries~\ref{corollary:rarity} and~\ref{corollary:intermediate_association_res3}).
+The effect of oblique transmission is more complex (Corollary~\ref{corollary:intermediate_association_res3}). 
 When there is horizontal transmission bias for cooperation ($T_A>T_B$), increasing the rate of oblique transmission ($1-v$) will facilitate the evolution of cooperation (\autoref{fig:result3}ac).
-However, when the bias is for defection ($T_A<T_B$), high rates of vertical transmission ($v$) are advantageous for cooperation.
-Nevertheless, to reach fixation of cooperation in the population, there must be a sufficient rate of vertical transmission ($v>\hat v$, Corollary~\autoref{corollary:vhat}).
-% TODO carry on summarizing corollaries here
-
-The results that we derived for a deterministic well-mixed model provide a good approximation to results of simulations of a complex stochastic spatial model  (\autoref{fig:spatial}).
+In contrast, when the bias is for defection ($T_A<T_B$), high rates of vertical transmission ($v$) are advantageous for cooperation, and there must be sufficient rate of vertical transmission ($v>\hat v$, Corollary~\autoref{corollary:vhat}, \autoref{fig:result3}bd) for cooperation to fix in the population.
+
+The conditions derived from our deterministic well-mixed model provide a good approximation to results of simulations of a complex stochastic spatial model  (\autoref{fig:spatial}).
 In this spatial model, individuals can only interact with and transmit to their neighbors.
@@
   \centering
-    \includegraphics[scale=0.7]{spatial.pdf}
+    \includegraphics[scale=0.5]{spatial1.png}
+    ~
+    \includegraphics[scale=0.5]{spatial2.png} \\
   \caption{
   \textbf{Evolution of cooperation in a spatial model.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the ratio between the cost and benefit of cooperation ($c/b$) on the y-axis, and the horizontal transmission rate (without transmission bias, $T=T_A=T_B$) on the x-axis.
-  The population evolves on a 100-by-100 grid. Selection, cooperation, and horizontal cultural transmission are all local between adjacent sites.
-  The black curve represents the condition for the evolution of cooperation in a well-mixed population with social association, $c/b<\alpha T / (1-T)$, where $\alpha=1/8$; see \autoref{eq:equal_transmission}.
-  Note that in the structured population, selection is local, whereas in the unstructured population, selection is global. This can explain the small difference in the results.
-  Here, population size is $10,000$ (100-by-100 grid); cost of cooperation, $c=0.05$.
-50 simulations were executed for each parameter set.
-Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
+  The population evolves on a 100-by-100 grid. Cooperation and horizontal cultural transmission are all local between adjacent sites, and each site had 8 neighbors.
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
+  Here, population size is $10,000$ (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
+  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$. \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
   }

### 2020-09-30 ms/main.tex
small changes and added TODOs during talking with DC

@@
 Eq.\ \ref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
-%Equation 4 does not give $\hat{p}$---MF
+%TODO Equation 4 does not give $\hat{p}$---MWF
 Eq.\ \ref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
@@
 %($\text{sign}\big(\partial \hat\gamma_1 / \partial T_B \big)= \text{sign}\big(b v \alpha T_A - (1-T_A)\big)$).
+%TODO talk about partial gamma 1 / partial v = -(TA-TB)(1-TB)
 
@@
 Similarly, $\partial \hat a_1 / \partial T_A < 0$, $\partial \hat a_2 / \partial T_A < 0$, $\partial \hat a_2 / \partial T_B > 0$, and $\text{sign}(\partial \hat a_1 / \partial T_B) = \text{sign}\big(T_A (1+b-c) - (1-T_A)cv\big)$.
+%TODO remove derivatives of a1
 
@@
 \autoref{fig:result3}cd illustrates this conditions.
+%TODO fix for increasing from rarity, only using a2
 
@@
 So, if there is horizontal bias for cooperation ($T_A>T_B$), decreasing that bias will make it harder for cooperation to evolve.
-However, if there is horizontal bias for defection ($T_A<T_B$) then the effect of further increasing the horizontal transmission of defection, $T_B$, can either increase or decrease the threshold $\hat\alpha_1$, making it harder or easier for cooperation to evolve, respectively, depending if horizontal transmission of cooperation ($T_A$) is high or low (i.e.
-if $T_A > cv/(1+b-c+cv)$ or below).
 
@@
 \\
+%TODO switch corollary 7 and 6
 
@@
 As before, $T_A$ and $T_B$ are the probabilities of transmitting phenotypes $A$ and $B$ during horizontal transmission.
-At each generation, each individual is chosen to "initiate" interactions with probability 1/2.\ %"with probability 1/2" not clear - MWF
+At each generation, each individual is chosen to "initiate" interactions with probability 1/2.\ %TODO "with probability 1/2" not clear - MWF
 Initiators then interact with a random neighbor in a prisoners' dilemma game and a random neighbor (with replacement) for horizontal cultural transmission (as both the game and the transmission are symmetrical, the expected number of each of these interactions per individual per generation is 1).
@@
 On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
-%How are A, B initialized on the grid? – MWF
+%TODO How are A, B initialized on the grid? – MWF
 
@@
 Let $f(p)=\lambda(p'-p)$, where $\lambda>0$, and assume $f(p^*)=0$; i.e., $p^*$ is an equilibrium.
-%HOW DO YOU KNOW $p^*\in(0,1)$?--MF
+%TODO HOW DO YOU KNOW $p^*\in(0,1)$?--MWF
 We want a condition for $|p'-p^*| < |p-p^*|$.
@@
 \end{figure}
+%TODO add panel d?
 

### 2020-10-03 ms/main.tex
Fix corollaries 4 & 6 and reorder them

@@
 
-With only oblique and horizontal transmission, i.e.
-$v = 0$, Eq.\ \ref{eq:horizontal} becomes $\hat{p}=p$ and Eq.\ \ref{eq:nextgen_adults_slimpify} becomes % TODO check this, I changed the ref from nextgen_parents_simplified to nextgen_adults_slimpify
+With only oblique and horizontal transmission, i.e. $v = 0$, Eq.\ \ref{eq:horizontal} becomes $\hat{p}=p$ and Eq.\ \ref{eq:nextgen_adults_slimpify} becomes 
 \begin{equation}  \label{eq:nextgen_parents_oblique_only}
@@
     \begin{aligned}
-    T_A > T_B &\;\; \text{and} \;\; a_2 < \alpha, \quad \text{or} \\
-    T_A < T_B &\;\; \text{and} \;\; a_1 < \alpha \,.
+     a_2 < \alpha
     \end{aligned}
@@
 With horizontal transmission bias for cooperation ($T_A>T_B$), cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
-Otherwise, cooperation can also fix if the horizontal bias is strong, the initial frequency is high, and social association is high, $a_1 < \alpha$ (blue area).
 With horizontal bias favoring defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
@@
 \\
-\begin{corollary}[Necessary condition for fixation of cooperation]
-\label{corollary:vhat}
-  Fixation of cooperation is possible only if the vertical transmission rate is high enough,
-  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
-    \begin{aligned}
-      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
-    \end{aligned}
-    \end{equation} 
-\end{corollary}
-%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
-Note that this condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
-When horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate, i.e. $\hat{v}<0$.
-In contrast, if the horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation, see \autoref{fig:result3}bd.
-\\
 
@@
 \end{aligned}\end{equation}
-Note that when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$.
-Similarly, $\partial \hat a_1 / \partial T_A < 0$, $\partial \hat a_2 / \partial T_A < 0$, $\partial \hat a_2 / \partial T_B > 0$, and $\text{sign}(\partial \hat a_1 / \partial T_B) = \text{sign}\big(T_A (1+b-c) - (1-T_A)cv\big)$.
-%TODO remove derivatives of a1
 
@@
     \begin{aligned}
-    T_A > T_B &\;\; \text{and} \;\; \hat a_2 < \alpha, \quad \text{or} \\
-    T_A < T_B &\;\; \text{and} \;\; \hat a_1 < \alpha \,.
+     \hat a_2 < \alpha.
     \end{aligned}
@@
 \autoref{fig:result3}cd illustrates this conditions.
-%TODO fix for increasing from rarity, only using a2
-
-Note that increasing the horizontal transmission of cooperation, $T_A$, decreases both boundaries ($\partial \hat a_1 / \partial T_A, \partial \hat a_2 / \partial T_A < 0$), thus facilitating evolution of cooperation.
-Increasing the horizontal transmission of defection, increases one boundary, ($\partial \hat a_2 / \partial T_B > 0$).
-So, if there is horizontal bias for cooperation ($T_A>T_B$), decreasing that bias will make it harder for cooperation to evolve.
-
-Interestingly, when there is horizontal transmission bias for cooperation ($T_A>T_B$), then vertical transmission hinders the evolution of cooperation ($\partial \hat a_2 / \partial v > 0$).
-In contrast, when there is horizontal transmission bias for defection ($T_A<T_B$), vertical transmission facilitates the evolution of cooperation ($\partial \hat a_1 / \partial v < 0$).
-\\
-%TODO switch corollary 7 and 6
+
+Note that when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$.
+When $T_A>T_B$ and the vertical transmission $v$ increases the boundary $\hat{a}_2$ also increases
+and therefore, a greater value of social association is required for fixation of cooperation from rarity. When $T_B>T_A$ decreasing of $v$ increases the boundary $\hat{a}_2$ 
+and therefore, a greater value of social association is required for fixation of cooperation from rarity.
+\\
+
+\begin{corollary}[Necessary condition for fixation of cooperation]
+\label{corollary:vhat}
+  Fixation of cooperation is possible only if the vertical transmission rate is high enough,
+  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
+    \begin{aligned}
+      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
+    \end{aligned}
+    \end{equation} 
+\end{corollary}
+%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
+Note that this condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
+When horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate, i.e. $\hat{v}<0$.
+In contrast, if the horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation, see \autoref{fig:result3}bd.
+\\
 
@@
   \centering
-    \includegraphics[scale=0.5]{spatial1.png}
+%   \includegraphics[scale=0.5]{spatial1.png}
     ~
-    \includegraphics[scale=0.5]{spatial2.png} \\
+ %   \includegraphics[scale=0.5]{spatial2.png} \\
   \caption{

### 2020-10-04 ms/main.tex
Explain how the grid in initialized in the spital model
small phrasing changes

@@
 Consider a  population colonizing a 2D grid of size 100-by-100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
-Each individual is characterized by its phenotype which is either cooperator, $A$, or defector $B$.
+Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
+At the beginning, each cell in the grid is randomly colonized with either a cooperator or a defector, with equal probability.
 In each generation individuals interact with their neighbors, i.e.
@@
 As before, $T_A$ and $T_B$ are the probabilities of transmitting phenotypes $A$ and $B$ during horizontal transmission.
-At each generation, each individual is chosen to "initiate" interactions with probability 1/2.\ %TODO "with probability 1/2" not clear - MWF
+At each generation, half of the individuals are randomly chosen to "initiate" interactions.
 Initiators then interact with a random neighbor in a prisoners' dilemma game and a random neighbor (with replacement) for horizontal cultural transmission (as both the game and the transmission are symmetrical, the expected number of each of these interactions per individual per generation is 1).
@@
 On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
-%TODO How are A, B initialized on the grid? – MWF
 
@@
 \autoref{fig:spatial} shows that the highest cost of cooperation ($c$) that permits the evolution of cooperation in simulations of the spatial model roughly agrees with the conditions derived in Result 2.
-Simulating a spatial model with local selection (i.e.
-sites can only be settled by offspring of neighbor parents) had only a minor affect, eliminating the stable coexistence.
+Simulating a spatial model with local selection (i.e. sites can only be settled by offspring of neighbor parents) had only a minor affect, eliminating the stable coexistence.
 

### 2020-10-04 ms/main.tex
minor fixes and formatting in corolarries

@@
 \begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:intermediate_association}
-Cooperation will increase from rarity if social association is high enough, specifically if
-  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
-    \begin{aligned}
-     a_2 < \alpha
-    \end{aligned}
-    \end{equation} 
+Cooperation will increase from rarity if social association is high enough, specifically if $a_2 < \alpha$.
 \end{corollary}
@@
 To proceed,  note that 
-Eq.\ \ref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
-%TODO Equation 4 does not give $\hat{p}$---MWF
-Eq.\ \ref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
-Eq.\ \ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
+\autoref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
+\autoref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
+\autoref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
+%TODO cleanup 
 Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}),
@@
 \label{corollary:intermediate_association_res3}
-Cooperation will increase from rarity if social association is high enough, specifically if
-  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
-    \begin{aligned}
-     \hat a_2 < \alpha.
-    \end{aligned}
-    \end{equation} 
+Cooperation will increase from rarity if social association is high enough, specifically if $\hat a_2 < \alpha$.
 \end{corollary}
@@
 Note that when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$.
-When $T_A>T_B$ and the vertical transmission $v$ increases the boundary $\hat{a}_2$ also increases
-and therefore, a greater value of social association is required for fixation of cooperation from rarity. When $T_B>T_A$ decreasing of $v$ increases the boundary $\hat{a}_2$ 
-and therefore, a greater value of social association is required for fixation of cooperation from rarity.
+When $T_A>T_B$ and the vertical transmission $v$ increases the boundary $\hat{a}_2$ also increases and therefore, a greater value of social association is required for fixation of cooperation from rarity.
+When $T_B>T_A$ decreasing the vertical transmission rate, $v$, increases the boundary $\hat{a}_2$.
+Therefore, a greater value of social association is required for fixation of cooperation from rarity.
 \\

### 2020-10-04 ms/main.tex
Fix some of the issues discussed today

@@
 
-%Note that the right-hand side equals $\hat\gamma_1$.
 This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
@@
 if $T_A>1/(1+bv\alpha)$ or below).
+%TODO I think the boundary on TA should be (2TB-1)/(alpha*b*v+1). DC
+Increasing the vertical transmission $v$ can either increase or decrease the boundary since $\partial \hat\gamma_1 / \partial v = \frac{(1-T_B)(T_B-T_a)}{v^2(1-T_B)^2}$ which can be both positive and negative depending on the sign of $T_B-T_A$.
+When $T_B>T_A$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the boundary on the cost increases making it easier for cooperation to evolve from rarity.
+Similarly, when $T_A > T_B$ we get $\partial \hat\gamma_1 / \partial v <0$ and therefore, as the vertical transmission increases the boundary on the cost decreases making it harder for cooperation to evolve from rarity.
+We got that when $T_A>T_B$ vertical transmission is interfering cooperation to evolve by decreasing the maximum cost that the cooperates can pay and stil evolve from rairty. 
+%TODO Is the last sentence requried ? Should we mention here we already saw result 1 - when $T_A > T_B$ we will have global fixation of cooperation
+
 %($\text{sign}\big(\partial \hat\gamma_1 / \partial T_B \big)= \text{sign}\big(b v \alpha T_A - (1-T_A)\big)$).
 %TODO talk about partial gamma 1 / partial v = -(TA-TB)(1-TB)
+%TODO - do we need the command above ? DC
 
@@
 
-Note that when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$.
-When $T_A>T_B$ and the vertical transmission $v$ increases the boundary $\hat{a}_2$ also increases and therefore, a greater value of social association is required for fixation of cooperation from rarity.
-When $T_B>T_A$ decreasing the vertical transmission rate, $v$, increases the boundary $\hat{a}_2$.
-Therefore, a greater value of social association is required for fixation of cooperation from rarity.
+Note that $\partial \hat a_2 / \partial v = b T_A (T_A-T_B)$.
+$\partial \hat a_2 / \partial v > 0$ when $T_A > T_B$ and therefore, as the vertical transmission $v$ \emph{increases} a greater value of social association is required for fixation of cooperation from rarity.
+Similarly, when $T_B>T_A$ $T_A > T_B$ we get $\partial \hat a_2 / \partial v < 0$ and therefore, as $v$ \emph{decreases} a greater value of social association is required for fixation of cooperation from rarity.
 \\
@@
 
-Let $f(p)=\lambda(p'-p)$, where $\lambda>0$, and assume $f(p^*)=0$; i.e., $p^*$ is an equilibrium.
-%TODO HOW DO YOU KNOW $p^*\in(0,1)$?--MWF
-We want a condition for $|p'-p^*| < |p-p^*|$.
+Let $f(p)=\lambda(p'-p)$, where $\lambda>0$, and we know that $f(0)=0$ and $f(1)=0$ since 0,1 are equilibrium.
 

### 2020-10-07 ms/main.tex
Add Ohad's graph and some todo to discuss with Yoav
update todos

@@
 \autoref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-%TODO cleanup 
+%TODO YR cleanup  
 Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}),
@@
 if $T_A>1/(1+bv\alpha)$ or below).
+% TODO write sign(dgamma1/dTB) = sign(???)
 %TODO I think the boundary on TA should be (2TB-1)/(alpha*b*v+1). DC
-Increasing the vertical transmission $v$ can either increase or decrease the boundary since $\partial \hat\gamma_1 / \partial v = \frac{(1-T_B)(T_B-T_a)}{v^2(1-T_B)^2}$ which can be both positive and negative depending on the sign of $T_B-T_A$.
-When $T_B>T_A$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the boundary on the cost increases making it easier for cooperation to evolve from rarity.
+
+Increasing the vertical transmission $v$ can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$ (because $\text{sign}(\partial \hat\gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.)
+When $T_A<T_B$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the boundary on the cost increases making it easier for cooperation to evolve from rarity.
 Similarly, when $T_A > T_B$ we get $\partial \hat\gamma_1 / \partial v <0$ and therefore, as the vertical transmission increases the boundary on the cost decreases making it harder for cooperation to evolve from rarity.
 We got that when $T_A>T_B$ vertical transmission is interfering cooperation to evolve by decreasing the maximum cost that the cooperates can pay and stil evolve from rairty. 
-%TODO Is the last sentence requried ? Should we mention here we already saw result 1 - when $T_A > T_B$ we will have global fixation of cooperation
-
-%($\text{sign}\big(\partial \hat\gamma_1 / \partial T_B \big)= \text{sign}\big(b v \alpha T_A - (1-T_A)\big)$).
-%TODO talk about partial gamma 1 / partial v = -(TA-TB)(1-TB)
-%TODO - do we need the command above ? DC
+% TODO YR revise; note that without vertical transmission TA-TB determines the outcome
 
@@
 $\partial \hat a_2 / \partial v > 0$ when $T_A > T_B$ and therefore, as the vertical transmission $v$ \emph{increases} a greater value of social association is required for fixation of cooperation from rarity.
+%TODO YR revise
 Similarly, when $T_B>T_A$ $T_A > T_B$ we get $\partial \hat a_2 / \partial v < 0$ and therefore, as $v$ \emph{decreases} a greater value of social association is required for fixation of cooperation from rarity.
@@
 %Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
-Note that this condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
+This condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
 When horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate, i.e. $\hat{v}<0$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{With population structure}
+\subsection*{With Population Structure}
 
@@
 \section*{Acknowledgements}
-We thank Lilach Hadany and Ayelet Shavit for discussions and comments.
+We thank Lilach Hadany, Ayelet Shavit, and Kaleda Krebs Denton for discussions and comments.
 This work was supported in part by
@@
   \centering
-%   \includegraphics[scale=0.5]{spatial1.png}
+   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
     ~
- %   \includegraphics[scale=0.5]{spatial2.png} \\
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
   \caption{
@@
   The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
-  The population evolves on a 100-by-100 grid. Cooperation and horizontal cultural transmission are all local between adjacent sites, and each site had 8 neighbors.
+  The population evolves on a 100-by-100 grid.
+  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
+  Selection operates globally (see Fig X for results from a model with local selection).
   The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
-  Here, population size is $10,000$ (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
-  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$. \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
+  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
   }
@@
 
+% TODO add figure of fluctuations in spatial model
+% TODO add figure of local selection in spatial model
+
 %%%

### 2020-10-09 ms/main.tex
Handle Corollary 5 - derivative by T_B

@@
 Similarly, increasing the horizontal transmission of cooperation increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), making it easier for cooperation to evolve.
-However, increasing the horizontal transmission of defection can either increase or decrease the boundary, making it easier or harder for cooperation to evolve, respectively, depending if $T_A$ is high or low (i.e.
-if $T_A>1/(1+bv\alpha)$ or below).
-% TODO write sign(dgamma1/dTB) = sign(???)
-%TODO I think the boundary on TA should be (2TB-1)/(alpha*b*v+1). DC
+However, increasing the horizontal transmission of defection can either increase or decrease the boundary, making it easier or harder for cooperation to evolve, respectively,
+depending if $T_A$ is high or low.
+Since $sign(\partial\gamma_1/\partial T_B) = sign(vb \alpha T_A+T_A-1)$ it will be easier to cooperation to evolve if $T_A > \frac{1}{1+\alpha b v}$ and harder otherwise.
 

### 2020-10-09 ms/main.tex
Handle Corollary 5 - derivative by T_B - fix

--- 2020-10-07 ms/main.tex
@@
 Similarly, increasing the horizontal transmission of cooperation increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), making it easier for cooperation to evolve.
-However, increasing the horizontal transmission of defection can either increase or decrease the boundary, making it easier or harder for cooperation to evolve, respectively, depending if $T_A$ is high or low (i.e.
-if $T_A>1/(1+bv\alpha)$ or below).
-% TODO write sign(dgamma1/dTB) = sign(???)
-%TODO I think the boundary on TA should be (2TB-1)/(alpha*b*v+1). DC
+However, increasing the horizontal transmission of defection can either increase or decrease the boundary depending on $sign(\partial\gamma_1/\partial T_B) = sign(vb \alpha T_A+T_A-1)$. 
+Therefore, increasing $T_B$ increases the boundary when $T_A > \frac{1}{1+\alpha b v}$ but when this applies we get that $\hat\gamma_1 > 1$ which guarantees cooperation will evolve from rairty since $c<1$.
+When $T_A < \frac{1}{1+\alpha b v}$ increasing $T_B$ decreases the boundary.
 

### 2020-10-09 ms/main.tex
Add spaitl model with local selection figure

@@
 
-%%% Figure: Spatial model
+%%% Figure: Spatial model - global selection
 \begin{figure}[h]
@@
   Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
-  Selection operates globally (see Fig X for results from a model with local selection).
+  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
   The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
@@
 
+%%% Figure: Spatial model - local selection
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
+    ~
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
+  \caption{
+  \textbf{Evolution of cooperation in a spatial model and local selection.}
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
+  The population evolves on a 100-by-100 grid.
+  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
+  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
+  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
+  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  }
+  \label{fig:spatial_local_selection}
+\end{figure}
+
 % TODO add figure of fluctuations in spatial model
-% TODO add figure of local selection in spatial model
 

### 2020-10-09 ms/main.tex
Add Fluctuations in spatial model figure

@@
   Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in ()\textbf{a}) \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
   Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
-  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
   }
@@
   Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in (left) \autoref{eq:equal_transmission} and (right) \label{eq:cost_boundaries}.
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
   Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
-  \textbf{(left)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(right)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
   }
@@
 
-% TODO add figure of fluctuations in spatial model
+% Fluctuations in spatial model
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
+   \caption{
+    \textbf{Coexistence of both phenotypes in spatial model.}
+    The dyanmics of the frequancy of cooperators (green) and the frequency of defactors in the spatial model. 
+    Both groups has the same initial frequency (0.5) and there are no fixation of one of the groups through the simulation.
+    The frequency of cooperators oscillate around the initial frequency. Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
+    horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
+    }
+    \label{fig:spatial_fluctuations}
+  \end{figure}
+  %TODO: edit this caption. DC
 

### 2020-10-09 ms/main.tex
Add refernce to Fluctuations in spatial model figure in the text

@@
 \autoref{fig:spatial} shows that the highest cost of cooperation ($c$) that permits the evolution of cooperation in simulations of the spatial model roughly agrees with the conditions derived in Result 2.
+An example for stable coexistence is shown in \autoref{fig:spatial_fluctuations}.
 Simulating a spatial model with local selection (i.e. sites can only be settled by offspring of neighbor parents) had only a minor affect, eliminating the stable coexistence.
@@
    \caption{
-    \textbf{Coexistence of both phenotypes in spatial model.}
+    \textbf{Stable coexistence of both phenotypes in spatial model.}
     The dyanmics of the frequancy of cooperators (green) and the frequency of defactors in the spatial model. 
     Both groups has the same initial frequency (0.5) and there are no fixation of one of the groups through the simulation.
-    The frequency of cooperators oscillate around the initial frequency. Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
+    The frequency of cooperators oscillate around the initial frequency.
+Here, population size is 10,000 (100-by-100 grid), selection operates globally, benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
     horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.

### 2020-10-10 ms/main.tex
Add equations for invasion

@@
 When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
+\autoref{fig:coexistence_recursive}a shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
 \\
@@
 
+\subsection*{Invasion analysis}
+
+In this section we assume perfect vertical transmission and stable coexistence of both cooperates and defector around equilibrium $p^*$.
+We saw in result 2 that such situation is possible if there is horizontal bias for defection, $T_B > T_A$ and $\gamma_2 < c < \gamma_1$ 
+where c is the cost and $\gamma_1$, $\gamma_2$ is defined in \autoref{eq:cost_boundaries}. The equilibrium $p^*$ is define in \autoref{eq:vert_hori_equilibrium}.
+
+Even though we describe a stable system, in which the frequency of each phenotype does not change, 
+it is safe to assume that in reality there are changes that can cause a change in the system parameters. 
+For example, a reduction in the cost $c$ that cooperator "pays" for its cooperation will favor cooperation. 
+We would like to make invasion analysis for invasion of new kind of individual with different soical association.
+For simplicity, we denote the orignal soical association with $\alpha_1$, and the new social association with $\alpha_2$. 
+We assume that $\alpha_2 > \alpha_1$.
+
+Before we start the invasion analysis let's examine if mean fitness increases if social association $\alpha$ increases. 
+From \autoref{eq:mean_fitness} we know that the mean fitness $\bar{w} = 1 + \hat{p}(b-c)$. In our case $\hat{p} = \hat{p}^*$ the equilibrium.
+Therefore, we get that the mean fitness in our scenario is
+\begin{equation} \label{eq:mean_fitness_stable_coexistence}
+  \bar{w} = 1 + (b-c)\cdot \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B)}.
+\end{equation} 
+We are interested in the sign of derivative $\bar{w}$ by $alpha$ which is the same as the derivative of $\hat{p}^*$ since $b>c$.
+\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
+  \begin{aligned}
+  \frac{d\hat{p}^*}{d\alpha} & =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \\
+  &= \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2}
+  \end{aligned}
+\end{equation} 
+Since the denominator is always positive the derivative of mean fitness by alpha will be positive if the numerator is positive for every alpha.
+We get the numerator is positive if
+\begin{equation} \label{eq:mean_fitness_numerator_condition}
+  \begin{aligned}
+  &  0 < b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2  \\
+  & c(1-T_B) < b(T_A-T_B) + (T_A-T_B)  \\
+  & c < \frac{b(T_A-T_B) + (T_A-T_B)}{(1-T_B)}.
+  \end{aligned}
+\end{equation} 
+\autoref{eq:mean_fitness_numerator_condition} is always true for stable coexistence because we know from Result2 
+that the condition for coexistence is $c<\gamma_1$ and $ \gamma_1 \leq \frac{b(T_A-T_B) + (T_A-T_B)}{(1-T_B)}$. 
+Therefore, the mean fitness increases as social association $\alpha$ increases.
+
+In case of invasion we will have 4 types, each type has unique combination of phenotype(A/B) and soical association value ($\alpha_1$/$\alpha_2$).
+Let's define their frequencies:
+\begin{enumerate}
+  \item $\hat{p}_1$ is the frequency of juveniles in next generation with phenotype A and probability of sical association $\alpha_1$
+  \item $\hat{p}_2$ is the frequency of juveniles in next generation with phenotype B and probability of sical association $\alpha_1$
+  \item $\hat{p}_3$ is the frequency of juveniles in next generation with phenotype A and probability of sical association $\alpha_2$
+  \item $\hat{p}_4$ is the frequency of juveniles in next generation with phenotype B and probability of sical association $\alpha_2$
+\end{enumerate}
+
+\begin{equation} \label{eq:next_gen_p_1}
+  \begin{aligned}
+  \bar{w}\hat{p}_1' & = \hat{p}_1(\hat{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_1)(\hat{p}_2 + \hat{p}_4)T_B) \\
+  &+ \hat{p}_1(\hat{p}_2 + \hat{p}_4)(1-c)(1-\alpha_1T_B(\hat{p_1}+\hat{p}_3) - T_B(\hat{p}_2+\hat{p}_4)) \\
+  &+ \hat{p}_2(\hat{p}_1 + \hat{p}_3)(1+b)T_A(\hat{p}_1 + \hat{p}_3 + \alpha_1(\hat{p}_2 + \hat{p_4})) \\
+  &+ \hat{p}_2(\hat{p}_2 + \hat{p}_4)(\hat{p}_1 + \hat{p}_3)(1-\alpha_1)T_A 
+  \end{aligned}
+\end{equation}
+Where the mean fitness $\bar{w} = 1 + (b-c)\cdot(\hat{p}_1 + \hat{p}_3)$. The equations describing $\hat{p}_2'$, $\hat{p}_3'$, $\hat{p}_4'$ is in \autoref{sec:appendixC}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{} \label{sec:appendixC}
+
+\begin{equation} \label{eq:next_gen_p_2}
+  \begin{aligned}
+  \bar{w}\hat{p}_2' & = \hat{p}_2(\hat{p}_2+\hat{p_4})(1 - (1-\alpha_1)(\hat{p}_1 + \hat{p}_3)T_A) \\
+  &+ \hat{p}_2(\hat{p}_1 + \hat{p}_3)(1+b)(1-\alpha_1T_A(\hat{p}_2 + \hat{p}_4)-T_A(\hat{p}_1 + \hat{p}_3))\\
+  &+ \hat{p}_1(\hat{p}_2 + \hat{p}_4)(1-c)(\alpha_1T_B + (1-\alpha_1)(\hat{p}_2+\hat{p}_4)T_B) \\
+  &+ \hat{p}_1(\hat{p}_1 + \hat{p}_3)(1-\alpha_1)(\hat{p}_2+\hat{p}_4)T_B 
+  \end{aligned}
+\end{equation}
+
+\begin{equation} \label{eq:next_gen_p_3}
+  \begin{aligned}
+  \bar{w}\hat{p}_3' & = \hat{p}_3(\hat{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_2)(\hat{p}_2 + \hat{p}_4)T_B) \\
+  &+ \hat{p}_3(\hat{p}_2 + \hat{p}_4)(1-c)(1-\alpha_2T_B(\hat{p_1}+\hat{p}_3) - T_B(\hat{p}_2+\hat{p}_4)) \\
+  &+ \hat{p}_4(\hat{p}_1 + \hat{p}_3)(1+b)T_A(\hat{p}_1 + \hat{p}_3 + \alpha_2(\hat{p}_2 + \hat{p_4})) \\
+  &+ \hat{p}_4(\hat{p}_2 + \hat{p}_4)(\hat{p}_1 + \hat{p}_3)(1-\alpha_2)T_A 
+  \end{aligned}
+\end{equation}
+
+\begin{equation} \label{eq:next_gen_p_4}
+  \begin{aligned}
+  \bar{w}\hat{p}_4' & = \hat{p}_4(\hat{p}_2+\hat{p_4})(1 - (1-\alpha_2)(\hat{p}_1 + \hat{p}_3)T_A) \\
+  &+ \hat{p}_4(\hat{p}_1 + \hat{p}_3)(1+b)(1-\alpha_2T_A(\hat{p}_2 + \hat{p}_4)-T_A(\hat{p}_1 + \hat{p}_3))\\
+  &+ \hat{p}_3(\hat{p}_2 + \hat{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\hat{p}_2+\hat{p}_4)T_B) \\
+  &+ \hat{p}_3(\hat{p}_1 + \hat{p}_3)(1-\alpha_2)(\hat{p}_2+\hat{p}_4)T_B 
+  \end{aligned}
+\end{equation}
+
 \end{appendices}
@@
 
-%%% Figure: coexistence map - without oblique transmission
-\begin{figure}[h]
-\centering
-\includegraphics[scale = 0.55]{coexistence_without_oblique.pdf}
-\caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
-  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation, $\tilde{p}'$, vs.\ that in the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
-  The dashed black line is $\tilde{p}'=\tilde{p}$.
-  The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
-  When the curves are above the dashed line, $\tilde{p}'>\tilde{p}$, and $\tilde{p}$ increases.
-  When the curves are below the dashed line, $\tilde{p}'<\tilde{p}$, and $\tilde{p}$ decreases.
-  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
-  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
-  In both cases there is no oblique transmission, $v=1$; see \autoref{fig:coexistence_with_oblique} for $v<1$.
-  }
-\label{fig:coexistence_without_oblique}
-\end{figure}
-
 %%% Figure: Boundaries figure - only vertical
@@
 
-%%% Figure: coexistence map - with oblique transmission
+%%% Figure: coexistence map
 \begin{figure}[h]
   \centering
-  \includegraphics[scale=0.55]{coexistence_with_oblique.pdf}
-  \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
+    \includegraphics[scale=0.45]{coexistence_without_oblique.pdf}~
+    \includegraphics[scale=0.45]{coexistence_with_oblique.pdf}
+  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
   The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
@@
   When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
-  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
+  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.\\
+  \textbf{(a)} There is no oblique transmission, $v=1$.
+  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries}).
+  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.\\
+  \textbf{(b)} Oblique transmission exists. 
   The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
-  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
-  }
-  \label{fig:coexistence_with_oblique}
+  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
+  }
+  \label{fig:coexistence_recursive}
   \end{figure}
@@
   \centering
-    \includegraphics[scale=0.7]{Time_Figure_Equal_Horizontal.pdf}
-    \includegraphics[scale=0.7]{Time_Figure_Only_Vertical_No_Alpha.pdf}
-    \includegraphics[scale=0.7]{Time_Figure_No_Vertical.pdf}
+    \includegraphics[scale=0.45]{Time_Figure_Equal_Horizontal.pdf}
+    ~\\
+    \includegraphics[scale=0.45]{Time_Figure_Only_Vertical_No_Alpha.pdf}
+    ~\\
+    \includegraphics[scale=0.45]{Time_Figure_No_Vertical.pdf}
   \caption{
@@
   Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in ()\textbf{a}) \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
@@
     \textbf{Stable coexistence of both phenotypes in spatial model.}
-    The dyanmics of the frequancy of cooperators (green) and the frequency of defactors in the spatial model. 
-    Both groups has the same initial frequency (0.5) and there are no fixation of one of the groups through the simulation.
-    The frequency of cooperators oscillate around the initial frequency.
-Here, population size is 10,000 (100-by-100 grid), selection operates globally, benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
-    horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
+    The frequancy of cooperators (green) and defactors (red) in the spatial model. 
+    Both phenotypes have initial frequency of 50 precent. The figure shows that there are no fixation of nither phenotype through out the simulation.
+    The frequency of both cooperators and defactors oscillates around the initial frequency. Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
+    benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$, horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
     }

### 2020-10-14 ms/main.tex
typos

--- 2020-10-09 ms/main.tex
@@
   The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
-  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
+  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
   }

### 2020-10-17 ms/main.tex
Unify figure 2,5 to figure 4

@@
 
-%%% Figure: coexistence map - with oblique transmission
+%%% Figure: coexistence map
 \begin{figure}[h]
   \centering
-  \includegraphics[scale=0.55]{coexistence_with_oblique.pdf}
-  \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
+    \includegraphics[scale=0.5]{coexistence_without_oblique.pdf}~
+    \includegraphics[scale=0.5]{coexistence_with_oblique.pdf}
+  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
   The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
@@
   When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
-  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
+  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.\\
+  \textbf{(a)} There is no oblique transmission, $v=1$.
+  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries}).
+  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.\\
+  \textbf{(b)} Oblique transmission exists. 
   The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
@@
   }
-  \label{fig:coexistence_with_oblique}
+  \label{fig:coexistence_recursive}
   \end{figure}

### 2020-10-17 ms/main.tex
Fix more graphs

@@
   \centering
-    \includegraphics[scale=0.5]{coexistence_without_oblique.pdf}~
-    \includegraphics[scale=0.5]{coexistence_with_oblique.pdf}
+    \includegraphics[scale=0.45]{coexistence_without_oblique.pdf}~
+    \includegraphics[scale=0.45]{coexistence_with_oblique.pdf}
   \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}

### 2020-10-18 ms/main.tex
haldane cite; sagol affil to YR

@@
 \author[3]{Marcus W. Feldman}
-\author[1,4,*]{Yoav Ram}
+\author[1,4,5,*]{Yoav Ram}
 
@@
 \affil[4]{School of Zoology, Tel Aviv University, Tel Aviv, Israel}
+\affil[5]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
 \affil[*]{Corresponding author: yoav@yoavram.com}
@@
 Nevertheless, cooperative behavior appears to occur in many non-human animals~\citep{dugatkin1997cooperation}, including primates~\citep{jaeggi2013natural},  rats~\citep{rice1962altruism}, birds~\citep{stacey1990cooperative,krams2008experimental}, and lizards~\citep{sinervo2006self}.
-Evolution of cooperative behavior remains an important conundrum in evolutionary biology.
+Evolution of cooperative behavior remains an important conundrum in evolutionary biology~\citep[Appendix]{Haldane1932book}.
 
@@
 As another example, when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can protect traits from the effect of natural selection \citep{ram2018evolution}.
+Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can diminish the effect of natural selection \citep{ram2018evolution}.
 This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a broader understanding of its evolutionary dynamics.

### 2020-10-18 ms/main.tex
edit result 2; merge appendix A back to results

@@
 \end{corollary}
-Note that the right-hand side equals $\gamma_1$ when $T=T_A=T_B$.
 This condition is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:vert_hori_global_condition} and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-\autoref{fig:results}a illustrates this condition.
+\autoref{fig:results}a illustrates this condition. Note that the right-hand side equals $\gamma_1$ when $T=T_A=T_B$.
 
@@
 If there is horizontal transmission bias for cooperation ($T_A>T_B$) then cooperation can evolve from any initial frequency if the cost is low enough, $c<\gamma_1$ (green area below solid line).
-If the cost is not low enough, cooperation can also evolve if its initial frequency is high enough and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
-
-We can interpret these condition as follows.
-First, when cooperators are rare, they will mostly interact with defectors.
+If the cost is not low enough, cooperation can still evolve if its initial frequency is high enough and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
+
+We can interpret these condition as follows. First, when cooperators are rare, they will mostly interact with defectors.
 Therefore, for cooperation to increase in frequency and fix, the \emph{effective cost of cooperation} must be lower than the horizontal transmission of cooperation, $1-(1-c)(1-T_B) < T_A$, which is equivalent to the first of the two inequalities in \autoref{eq:vert_hori_alpha0}.
@@
 This condition is obtained from inequality \ref{eq:vert_hori_alpha1_condition_proof}, and the right-hand side equals $\gamma_1$ when $\alpha=1$ (\autoref{eq:cost_boundaries}).
-Perfect social association (horizontal transmission always occurs during the cooperative interaction) is also assumed in the model studied by \citet{lewin2017microbes}, and therefore this corollary is equivalent to the result in their eq.~1.
+Perfect social association (horizontal transmission always occurs during the social interaction) is also assumed in the model studied by \citet{lewin2017microbes}, and therefore this corollary is equivalent to their eq.~1.
 
@@
 With horizontal bias favoring defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
-Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough; $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
 
@@
 and we focus on local rather than on global stability.
-To proceed,  note that 
-\autoref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
-\autoref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
-\autoref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-%TODO YR cleanup  
-Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}),
+In the following, we find an equation for the frequency of phenotype $A$ among juveniles in the next generation $\hat{p}'$ as a function of the frequency in the current generation,
 determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
-%: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})=\bar{w}(\hat{p}'-\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
-
-%We start with the simple case of symmetrical horizontal transmission, $T=T_A=T_B$ and apply \autoref{eq:horizontal}, \autoref{eq:nextgen_adults_slimpify}, and \autoref{eq:nextgen_parents_simplified} to obtain
-%\begin{equation} \label{eq:equal_horizontal_transmission}
-%\begin{aligned}
-%  f(\hat{p}) &= 
-%  \bar{w}(\hat{p}' - \hat{p}) = \\
-%  &\hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big].\end{aligned}
-%\end{equation}
-%A detailed explain of how we get eq.~\ref{eq:equal_horizontal_transmission} can be found in appendix B.
-%The equilibria are solutions of $f(\hat{p})=0$, or $\hat{p}' = \hat{p}$.
-%It is easy to verify that fixation of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$, is an equilibrium.
-%Since the derivative of $f'(\hat{p}$ is 
-%\begin{equation}
-%f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big],
-%\end{equation}
-%then the condition for local stability of $\hat{p}=1$ is
-%\begin{equation} \label{eq:derivative_of_phattag-phat}
-%	f'(1) =	-\alpha bvT + cv(1-T) < 0,
-%\end{equation}
-%which gives the following result.
-%
-%\textbf{Result 3: Oblique and vertical transmission with symmetric horizontal transmission.}
-%If horizontal transmission is symmetric, $T = T_A = T_B$, and if
-%\begin{equation} \label{eq:oblique_and_vertic_result2}
-%  %\frac{b}{c}>\frac{1-T}{\alpha T}
-%	c < b \cdot \frac{\alpha T}{1-T},
-%\end{equation}
-%then fixation of the cooperator phenotype $A$ is locally stable.
-%The same condition was given in Corollary 1.1, \autoref{eq:equal_transmission}.
-
-%We now turn to the general case where $T_A \neq T_B$. 
-Applying Eqs.\ \ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} gives the function $f(\hat{p})$ (see Appendix~\autoref{sec:appendixA}):
-
+
+Starting from \autoref{eq:horizontal}, we substitute \autoref{eq:nextgen_adults_slimpify} for $p'$ and  \autoref{eq:nextgen_parents_simplified} for $\tilde{p}'$.
+We therefore have
+\begin{equation}
+  \begin{aligned}
+  \hat{p}'  = & \frac{v}{\bar{w}}\left\{\hat{p}^2(1+b-c)\left[1-(1-\hat{p})(1-\alpha)T_B)\right]\right\} \\
+  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1-c)\left[ \hat{p}(1-\alpha)T_B + 1 - T_B \right] \right\} \\
+  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1+b)\left[\hat{p}(1-\alpha) + \alpha \right]T_A \right\} \\
+  & + \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \\
+  & + (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B),
+\end{aligned}
+\end{equation}
+where $\bar{w} = 1 + \hat{p}(b-c)$. 
+We define $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics,  this simplifies to
 \begin{equation} \label{eq:general_case_polynomial}
@@
 
-If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$, 
-and $f(\hat{p})$ becomes a quadratic polynomial:
+If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$. 
+Thus, $f(\hat{p})$ becomes a quadratic polynomial,
 \begin{equation} \label{eq:equal_horizontal_transmission}
@@
 Clearly the only two equilibria are the fixations  $\hat{p} =  0$ and $\hat{p} = 1$.
-These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\autoref{sec:appendixB}), where
-\begin{equation}
-f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big],
-\end{equation}
-with
+These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\autoref{sec:appendixA}), where
+$f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big]$, so that
 \begin{equation} \label{eq:derivative_of_phattag-phat}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{} \label{sec:appendixA}
-We want to find the frequency of juveniles with phenotype $A$ in next generation $\hat{p}'$ as a function of frequency
-of juveniles with phenotype $A$ in the current generation $\hat{p}$.
-Starting from \autoref{eq:horizontal},
-\begin{equation}\label{eq:appendix_b_1}
-  \hat{p}' = v \tilde{p}' + (1-v) p',
-\end{equation}
- substitute for $p'$ using \autoref{eq:nextgen_adults_slimpify} and for $\tilde{p}'$ using \autoref{eq:nextgen_parents_simplified}, we have
-\begin{equation}\label{eq:appendix_b_2}
-  \begin{aligned}
-  \hat{p}'  = & \frac{v}{\bar{w}}\left\{\hat{p}^2(1+b-c)\left[1-(1-\hat{p})(1-\alpha)T_B)\right]\right\} \\
-  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1-c)\left[ \hat{p}(1-\alpha)T_B + 1 - T_B \right] \right\} \\
-  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1+b)\left[\hat{p}(1-\alpha) + \alpha \right]T_A \right\} \\
-  & + \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \\
-  & + (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B),
-\end{aligned}
-\end{equation}
-where $\bar{w} = 1 + \hat{p}(b-c)$. 
-Define $g(\hat{p})$ as
-\begin{equation} \label{eq:appendix_define_f}
-\begin{aligned}
-      g(\hat{p}) &= \bar{w}(\hat{p}' - \hat{p})
-\end{aligned}
-\end{equation}
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics,  \autoref{eq:appendix_define_f} simplifies to 
-eqs.~\ref{eq:general_case_polynomial}-\ref{eq:polynomial_coefficients}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{} \label{sec:appendixB}
 

### 2020-10-18 ms/main.tex
revise result 3 and spatial model

@@
 This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
+In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
+
 Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \hat\gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
-Similarly, increasing the horizontal transmission of cooperation increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), making it easier for cooperation to evolve.
-However, increasing the horizontal transmission of defection can either increase or decrease the boundary depending on $sign(\partial\gamma_1/\partial T_B) = sign(vb \alpha T_A+T_A-1)$. 
-Therefore, increasing $T_B$ increases the boundary when $T_A > \frac{1}{1+\alpha b v}$ but when this applies we get that $\hat\gamma_1 > 1$ which guarantees cooperation will evolve from rairty since $c<1$.
-When $T_A < \frac{1}{1+\alpha b v}$ increasing $T_B$ decreases the boundary.
-
-Increasing the vertical transmission $v$ can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$ (because $\text{sign}(\partial \hat\gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.)
-When $T_A<T_B$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the boundary on the cost increases making it easier for cooperation to evolve from rarity.
-Similarly, when $T_A > T_B$ we get $\partial \hat\gamma_1 / \partial v <0$ and therefore, as the vertical transmission increases the boundary on the cost decreases making it harder for cooperation to evolve from rarity.
-We got that when $T_A>T_B$ vertical transmission is interfering cooperation to evolve by decreasing the maximum cost that the cooperates can pay and stil evolve from rairty. 
-% TODO YR revise; note that without vertical transmission TA-TB determines the outcome
-
-In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
-Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
-\\
+Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation.
+However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost boundary, but it increases the cost boundary when it is already above one ($c<1<\hat\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\hat\gamma_1>1/v$.
+Therefore, increasing $T_B$ decreases the cost boundary and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
+
+Increasing the vertical transmission $v$ can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \hat\gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
+When $T_A<T_B$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the cost boundary increases, making it easier for cooperation to evolve from rarity.
+In contrast, when $T_A > T_B$ we get $\partial \hat\gamma_1 / \partial v <0$ and therefore, as the vertical transmission increases the cost boundary decreases making it harder for cooperation to evolve from rarity.
 
@@
 \end{corollary}
-\autoref{fig:result3}cd illustrates this conditions.
-
-Note that $\partial \hat a_2 / \partial v = b T_A (T_A-T_B)$.
-$\partial \hat a_2 / \partial v > 0$ when $T_A > T_B$ and therefore, as the vertical transmission $v$ \emph{increases} a greater value of social association is required for fixation of cooperation from rarity.
-%TODO YR revise
-Similarly, when $T_B>T_A$ $T_A > T_B$ we get $\partial \hat a_2 / \partial v < 0$ and therefore, as $v$ \emph{decreases} a greater value of social association is required for fixation of cooperation from rarity.
+\autoref{fig:result3}cd illustrates this condition.
+Interestingly, the effect of vertical transmission on this condition depends on the horizontal transmission bias, $\partial \hat a_2 / \partial v = b T_A (T_A-T_B)$. 
+That is, with horizontal bias for cooperation, $T_A>T_B$, the boundary increases with the rate of vertical transmission, impeding the evolution of cooperation.
+In contrast, with horizontal bias for defection, $T_A<T_B$, the boundary decreases with the rate of vertical transmission, facilitating the evolution of cooperation. 
+These effects of vertical transmission are demonstrated in \autoref{fig:result3}cd.
 \\
@@
 Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
-At the beginning, each cell in the grid is randomly colonized with either a cooperator or a defector, with equal probability.
-In each generation individuals interact with their neighbors, i.e.
-individuals that inhabit adjacent sites, in a prisoner's dilemma game (\autoref{table:prisoner_payoff}) and with horizontal cultural transmission.
-As before, $T_A$ and $T_B$ are the probabilities of transmitting phenotypes $A$ and $B$ during horizontal transmission.
-At each generation, half of the individuals are randomly chosen to "initiate" interactions.
-Initiators then interact with a random neighbor in a prisoners' dilemma game and a random neighbor (with replacement) for horizontal cultural transmission (as both the game and the transmission are symmetrical, the expected number of each of these interactions per individual per generation is 1).
-Therefore, the effective social association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/m$, where $m$ is the number of neighbors.
+Initially, each site in the grid is randomly colonized with either a cooperator or a defector, with equal probability.
+%In each generation individuals interact with their neighbors, i.e.
+individuals that inhabit adjacent sites, in a prisoner's dilemma game (\autoref{table:prisoner_payoff}) and in horizontal cultural transmission (\autoref{fig:horizontal}).
+%As before, $T_A$ and $T_B$ are the probabilities of transmitting phenotypes $A$ and $B$ during horizontal transmission.
+In each generation, half of the individuals are randomly chosen to "initiate" interactions.
+Initiators then interact with a random neighbor (i.e.
+individual in an adjacent site) in a prisoners' dilemma game (\autoref{table:prisoner_payoff}) and a random neighbor (with replacement) in horizontal cultural transmission (\autoref{fig:horizontal}).
+The expected number of each of these interactions per individual per generation is one.
+The effective social association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/m$, where $m$ is the number of neighbors.
 On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
-
-The order of the interactions across the lattice at each generation is random.
-After all interactions take place, and individual's fitness is determined by
+As before, $T_A$ and $T_B$ are the probability to successfully transmitting phenotypes $A$ and $B$ during horizontal transmission, respectively.
+
+The order the interactions across the grid at each generation is random.
+After all interactions take place, individual fitness is determined by
 $w = 1 + b \cdot n_b - c \cdot n_c$,
@@
 The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness of all potential parents.
-Offspring then have the same phenotype as their parents.
-
-\autoref{fig:spatial} shows that the highest cost of cooperation ($c$) that permits the evolution of cooperation in simulations of the spatial model roughly agrees with the conditions derived in Result 2.
+Offspring then have the same phenotype as their parents ($v=1$).
+
+\autoref{fig:spatial} shows that the highest cost of cooperation ($c$) that permits the evolution of cooperation in simulations of the spatial model agrees with the conditions derived in Result~2.
 An example for stable coexistence is shown in \autoref{fig:spatial_fluctuations}.
-Simulating a spatial model with local selection (i.e. sites can only be settled by offspring of neighbor parents) had only a minor affect, eliminating the stable coexistence.
+Simulating a spatial model with local selection (i.e.
+sites can only be settled by offspring of neighbor parents) had only a minor effect on the agreement with Result~2 (\autoref{fig:spatial_local_selection}).
 
@@
   \caption{
-  \textbf{Evolution of cooperation in a spatial model and local selection.}
+  \textbf{Evolution of cooperation in a spatial model with local selection.}
   The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
@@
    \caption{
-    \textbf{Stable coexistence of both phenotypes in spatial model.}
-    The frequancy of cooperators (green) and defactors (red) in the spatial model. 
-    Both phenotypes have initial frequency of 50 precent. The figure shows that there are no fixation of nither phenotype through out the simulation.
-    The frequency of both cooperators and defactors oscillates around the initial frequency. Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
-    benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$, horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
+    \textbf{Stable coexistence of both phenotypes in a spatial model.}
+    The frequency of cooperators (green) and defectors (red) in a spatial model. 
+    Both phenotypes start at 50\% frequency.
+    The figure shows that neither phenotype is fixed throughout the simulation, maintaining a stochastic coexistence.
+    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
+    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
     }

### 2020-10-18 ms/main.tex
revise modifier model section

--- 2020-10-18 ms/main.tex
@@
 \author[3]{Marcus W. Feldman}
-\author[1,4,5,*]{Yoav Ram}
+\author[1,4,*]{Yoav Ram}
 
@@
 \affil[4]{School of Zoology, Tel Aviv University, Tel Aviv, Israel}
-\affil[5]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
 \affil[*]{Corresponding author: yoav@yoavram.com}
@@
 Nevertheless, cooperative behavior appears to occur in many non-human animals~\citep{dugatkin1997cooperation}, including primates~\citep{jaeggi2013natural},  rats~\citep{rice1962altruism}, birds~\citep{stacey1990cooperative,krams2008experimental}, and lizards~\citep{sinervo2006self}.
-Evolution of cooperative behavior remains an important conundrum in evolutionary biology~\citep[Appendix]{Haldane1932book}.
+Evolution of cooperative behavior remains an important conundrum in evolutionary biology.
 
@@
 As another example, when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can diminish the effect of natural selection \citep{ram2018evolution}.
+Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can protect traits from the effect of natural selection \citep{ram2018evolution}.
 This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a broader understanding of its evolutionary dynamics.
@@
 
+\subsection*{Modifier model}
+
+We now analyze the evolution of social association under perfect vertical transmission, $v=1$.
+We assume a population at a stable coexistence of the two phenotypes, cooperation $A$ and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
+\autoref{eq:vert_hori_equilibrium}).
+Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries})
+
+The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$ (\autoref{eq:mean_fitness}), which is increasing in $\tilde{p}^*$. 
+Therefore, to determine the effect of increasing $\alpha$ on the stable population mean fitness, we must analyze its effect on $\tilde{p}^*$, 
+\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
+  \frac{\partial \tilde{p}^*}{\partial \alpha} 
+%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
+%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
+  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
+\end{equation} 
+Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
+\begin{equation}
+c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
+\end{equation} 
+Therefore, $b T_A - c(1-T_B) - (T_B-T_A)>0$, and since $T_A<T_B$, the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive, and the population mean fitness increases as social association $\alpha$ increases.
+
+Therefore, if a modifier allele that increases social association invades the population, the population mean fitness will increase. But can such a modifier allele invade the population?
+We assume that social association is determined by a genetically transmitted locus with alleles $m$ and $M$, which induce association probabilities $\alpha_1$ and $\alpha_2$, respectively.
+
+We define the frequencies of the pheno-genotypes $Am$, $Bm$, $AM$, and $BM$ as $\hat{p}_1$, $\hat{p}_2$, $\hat{p}_3$, and $\hat{p}_4$, respectively. 
+Then the following recursion system defines the frequencies of the pheno-genotypes in the next generation,
+\begin{equation} \label{eq:next_gen_p_1}
+  \begin{aligned}
+	% p1
+  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\hat{p_1}+\tilde{p}_3) - T_B(\tilde{p}_2+\tilde{p}_4)) \\
+  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \hat{p_4})) \\
+  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A 
+\\
+	% p2
+  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\hat{p_4})(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
+  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
+  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1T_B + (1-\alpha_1)(\tilde{p}_2+\tilde{p}_4)T_B) \\
+  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)(\tilde{p}_2+\tilde{p}_4)T_B 
+\\
+	% p3
+  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\hat{p_1}+\tilde{p}_3) - T_B(\tilde{p}_2+\tilde{p}_4)) \\
+  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \hat{p_4})) \\
+  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A 
+\\
+	% p4
+  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2+\hat{p_4})(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
+  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
+  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2+\tilde{p}_4)T_B) \\
+  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)(\tilde{p}_2+\tilde{p}_4)T_B \;,
+  \end{aligned}
+\end{equation}
+where $\bar{w} = 1 + (b-c)\cdot(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.
+
+Denote this system by $\bar{w} \vec{\tilde{p}} = f(\vec{\tilde{p}})$, where $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+We are interested in the invasion of allele $M$ to a population at equilibrium with allele $m$, that is, with equilibrium frequencies $\vec{\tilde{p}}^*=(\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, with $\tilde{p}^*$ defined in
+\autoref{eq:vert_hori_equilibrium}.
+The success of the invasion of allele $M$ is determined by the external stability matrix $\mathbf{L}^*_{ex}$~\citep{Liberman1988}, which is derived from \autoref{eq:next_gen_p_1} as
+\begin{equation}
+\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{bmatrix}
+	 \frac{\partial \tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
+	 \frac{\partial \tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
+	 \frac{\partial \tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
+	 \frac{\partial \tilde{p}_4'}{\partial \tilde{p}_4} (\vec{\tilde{p}}^*)
+\end{bmatrix} \;.
+\end{equation}
+If the leading eigenvalue of $\mathbf{L}^*_{ex}$ is less than 1, then the equilibrium $\vec{\tilde{p}}$ is locally stable and allele $M$ cannot invade the population of allele $m$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
+
 \end{appendices}

### 2020-10-20 ms/main.tex
Add partial derivatives
revised external stability primer

@@
 
-\subsection*{Modifier model}
+\subsection*{Modifiers of social association}
 
@@
 
-Therefore, if a modifier allele that increases social association invades the population, the population mean fitness will increase. But can such a modifier allele invade the population?
-We assume that social association is determined by a genetically transmitted locus with alleles $m$ and $M$, which induce association probabilities $\alpha_1$ and $\alpha_2$, respectively.
-
-We define the frequencies of the pheno-genotypes $Am$, $Bm$, $AM$, and $BM$ as $\hat{p}_1$, $\hat{p}_2$, $\hat{p}_3$, and $\hat{p}_4$, respectively. 
+Therefore, if the social association increases, the population mean fitness will increase.
+But can an allele that increases the social association evolve? 
+To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988}.
+The function of this modifier locus is to determine the social association.
+It has no direct effect on fitness.
+We assume that the modifier locus has two alleles, $M$ and $m$, which induce association probabilities $\alpha_1$ and $\alpha_2$, respectively, and that initially only $M$ is present.
+Suppose that the population evolves to a stable equilibrium when only $M$ is present; we check the local stability of this equilibrium to the introduction of the allele $m$ at the modifier locus.
+This is called ``external stability''; For more details on external stability, see \citet{Altenberg2017}.
+
+We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
 Then the following recursion system defines the frequencies of the pheno-genotypes in the next generation,
@@
 	% p1
-  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\hat{p_1}+\tilde{p}_3) - T_B(\tilde{p}_2+\tilde{p}_4)) \\
-  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \hat{p_4})) \\
+  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
+  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) \\
   &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A 
@@
 	% p2
-  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\hat{p_4})(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
-  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
-  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1T_B + (1-\alpha_1)(\tilde{p}_2+\tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)(\tilde{p}_2+\tilde{p}_4)T_B 
+  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
+  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3))\\
+  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B 
 \\
 	% p3
-  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\hat{p_1}+\tilde{p}_3) - T_B(\tilde{p}_2+\tilde{p}_4)) \\
-  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \hat{p_4})) \\
+  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
+  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) \\
   &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A 
@@
 	% p4
-  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2+\hat{p_4})(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
+  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
   &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
-  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2+\tilde{p}_4)T_B) \\
-  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)(\tilde{p}_2+\tilde{p}_4)T_B \;,
-  \end{aligned}
-\end{equation}
-where $\bar{w} = 1 + (b-c)\cdot(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.
-
-Denote this system by $\bar{w} \vec{\tilde{p}} = f(\vec{\tilde{p}})$, where $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-We are interested in the invasion of allele $M$ to a population at equilibrium with allele $m$, that is, with equilibrium frequencies $\vec{\tilde{p}}^*=(\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, with $\tilde{p}^*$ defined in
-\autoref{eq:vert_hori_equilibrium}.
-The success of the invasion of allele $M$ is determined by the external stability matrix $\mathbf{L}^*_{ex}$~\citep{Liberman1988}, which is derived from \autoref{eq:next_gen_p_1} as
+  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
+  \end{aligned}
+\end{equation}
+%which we can write as 
+%\begin{equation}
+%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
+%\end{equation}
+where $\bar{w} = 1 + (b-c)\cdot(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+
+The local stability of $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, the equilibrium when only allele $M$ is present (see \autoref{eq:vert_hori_equilibrium}), to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
+The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
+Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e.
+locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of
+$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, which is derived from \autoref{eq:next_gen_p_1} as
 \begin{equation}
@@
 \end{equation}
-If the leading eigenvalue of $\mathbf{L}^*_{ex}$ is less than 1, then the equilibrium $\vec{\tilde{p}}$ is locally stable and allele $M$ cannot invade the population of allele $m$.
+If the eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}}$ is externally stable and allele $m$ cannot invade the population of allele $M$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection*{With Population Structure}

### 2020-10-20 ms/main.tex

@@
 
-Therefore, if the social association increases, the population mean fitness will increase.
+We found that if the social association increases, the population mean fitness will increase.
 But can an allele that increases the social association evolve? 
@@
 We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
-Then the following recursion system defines the frequencies of the pheno-genotypes in the next generation,
+The frequencies of the pheno-genotypes in the next generation are defined by the recursion system 
 \begin{equation} \label{eq:next_gen_p_1}
@@
 
+%\begin{equation} \label{eq:partial_derivatives}
+%  \begin{aligned}
+%  &\frac{\partial\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b(\tilde{p}^*-(1-\alpha_2)T_B(\tilde{p}^*-\tilde{p}^{*2}))+(1-c)(1-\tilde{p}^*T_B-T_B)\\
+%  &\frac{\partial\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = bT_A\tilde{p}^*(\tilde{p}^*+\alpha_2(1-\tilde{p}^*))+\tilde{p}^*T_A)\\
+%  &\frac{\partial\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = T_B(1-\tilde{p}^*)-cT_B(\alpha_2+(1-\alpha_2)(1-\tilde{p}^*))\\
+%  &\frac{\partial\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1-\tilde{p}^*T_A+ b\tilde{p}^*(1-\alpha_2T_A(1-\tilde{p}^*)-T_A\tilde{p}^*)\\
+%  \end{aligned}
+%\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection*{With Population Structure}

### 2020-10-20 ms/main.tex
Create new sympy.ipynb file with typical poly equation

--- 2020-10-20 ms/main.tex
@@
 
+\begin{equation} \label{eq:partial_derivatives}
+  \begin{aligned}
+  &\frac{\partial\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b(\tilde{p}^*-(1-\alpha_2)T_B(\tilde{p}^*-\tilde{p}^{*2}))+(1-c)(1+\tilde{p}^*T_B-T_B)\\
+  &\frac{\partial\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = bT_A\tilde{p}^*(\tilde{p}^*+\alpha_2(1-\tilde{p}^*))+\tilde{p}^*T_A\\
+  &\frac{\partial\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = T_B(1-\tilde{p}^*)-cT_B(1-\tilde{p}^*)(\alpha_2+(1-\alpha_2)(1-\tilde{p}^*))\\
+  &\frac{\partial\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1-\tilde{p}^*T_A+ b\tilde{p}^*(1-\alpha_2T_A(1-\tilde{p}^*)-T_A\tilde{p}^*)\\
+  \end{aligned}
+\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection*{With Population Structure}

### 2020-10-21 ms/main.tex
major reogranization of results, not finished yet

--- 2020-10-20 ms/main.tex
@@
 %where $\hat{p}=v\tilde{p}+(1-v)p$.
+
+Finally, we find an equation for the frequency of phenotype $A$ among juveniles in the next generation $\hat{p}'$ as a function of the frequency in the current generation.
+Starting from \autoref{eq:horizontal}, we substitute \autoref{eq:nextgen_adults_slimpify} for $p'$ and  \autoref{eq:nextgen_parents_simplified} for $\tilde{p}'$.
+We therefore have
+\begin{equation} \label{eq:nextgen_juveniles}
+  \begin{aligned}
+  \hat{p}'  = & \frac{v}{\bar{w}}\left\{\hat{p}^2(1+b-c)\left[1-(1-\hat{p})(1-\alpha)T_B)\right]\right\} \\
+  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1-c)\left[ \hat{p}(1-\alpha)T_B + 1 - T_B \right] \right\} \\
+  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1+b)\left[\hat{p}(1-\alpha) + \alpha \right]T_A \right\} \\
+  & + \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \\
+  & + (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B),
+\end{aligned}
+\end{equation}
+where $\bar{w} = 1 + \hat{p}(b-c)$.
+
 \autoref{table:vars_params} summarizes the model variables and parameters.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Oblique and Horizontal Transmission}
-
-With only oblique and horizontal transmission, i.e. $v = 0$, Eq.\ \ref{eq:horizontal} becomes $\hat{p}=p$ and Eq.\ \ref{eq:nextgen_adults_slimpify} becomes 
-\begin{equation}  \label{eq:nextgen_parents_oblique_only}
-p' = p^2 (T_B-T_A) + p (1+T_A-T_B) \;,
-\end{equation}
-
-which gives the following result.\\
-
-\begin{result}[Oblique and horizontal transmission of cooperation] \label{result:obli_hori}
-Without vertical transmission ($v=0$), if there is a horizontal transmission bias in favor of cooperation, namely
-\begin{equation} \label{eq:oblique_only_result}
-T_A > T_B \;,
-\end{equation}
-then the frequency of the cooperator phenotype among adults increases every generation, $p'>p$.
-\end{result}
-
-That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ are missing from \autoref{eq:nextgen_parents_oblique_only}).
-The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers (see~{\autoref{fig:results}c).
-Note that without bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Vertical and Horizontal Transmission}
-
-With only vertical and horizontal transmission, i.e. $v=1$, Eq.\ \ref{eq:horizontal} becomes
-$\hat{p} =  \tilde{p}$,
-and Eq.\ \ref{eq:nextgen_parents_simplified} for the frequency of the cooperative phenotype among parents in the next generation $\tilde{p}'$ can be written as
-\begin{equation} \label{eq:nextgen_parents_vertical_only} 
-\begin{aligned}
-\bar{w} \tilde{p}' 
-& = \tilde{p}^2 (1+b-c) [1 - (1-\tilde{p}) (1-\alpha) T_B] \\
-& + \tilde{p}(1-\tilde{p}) (1-c) [\tilde{p} (1-\alpha) T_B + 1 - T_B] \\
-& + \tilde{p}(1-\tilde{p}) (1+b) [\tilde{p} (1-\alpha) + \alpha] T_A \\
-& + (1-\tilde{p})^2 \tilde{p} (1-\alpha) T_A \;.
-\end{aligned}
-\end{equation}
-
-Fixation of either cooperation, $\tilde{p}=1$, or defection, 
-$\tilde{p}=0$, are equilibria of Eq.\ \ref{eq:nextgen_parents_vertical_only}, solving $\tilde{p}'= \tilde{p}$.
-We assume for the remainder of the analysis that $0<\tilde{p}<1$.
-
-If $\alpha=1$, then $\tilde{p}'= \tilde{p}$ reduces to
-\begin{equation}
-\tilde{p}(1-\tilde{p})\big[(1+b)T_A + (1-c)(1-T_B)-1\big] = 0 \;,
-\end{equation}
-and there are no additional equilibria.
-For cooperation to take over the population (i.e., for $\tilde{p}=1$ to be globally stable) we require $\tilde{p}'>\tilde{p}$; that is,
-\begin{equation}
-  \tilde{p}^2 (1+b-c) + \tilde{p}(1-\tilde{p}) \big[(1-c) (1 - T_B) + (1+b)T_A\big] 
-  > \bar{w}\tilde{p} \;.
-\end{equation}
-Factoring out $\tilde{p}(1-\tilde{p})$ and setting $\bar{w} = 1 + \tilde{p}(b-c)$, we find that $\hat{p}'>\hat{p}$ if
-%\begin{equation}
-%  (1-\tilde{p}) \big[(1-c) (1 - T_B) + (1+b)T_A\big] 
-%  > 1 -\tilde{p} .
-%\end{equation}
-%Dividing by $(1-\tilde{p})$ we find that $\tilde{p}'>\tilde{p}$ if 
-\begin{equation} \label{eq:vert_hori_alpha1_condition_proof}
-  (1-c) (1 - T_B) + (1+b)T_A > 1 \;.
-\end{equation}
-\\
-
-If $\alpha<1$, divide both sides of Eq.\ \ref{eq:nextgen_parents_vertical_only} by $\tilde{p}$ and set $\bar{w} = 1 + \tilde{p}(b-c)$. Then $\tilde{p}'>\tilde{p}$ if
-\begin{equation}
-\begin{aligned} 
-  1 + \tilde{p}(b-c) < 
-  & \, \tilde{p}(1+b-c) (1 - (1-\tilde{p}) (1-\alpha) T_B) \\
-  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
-  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-  & + (1-\tilde{p})^2 (1-\alpha) T_A \;.
-\end{aligned}
-\end{equation}
-%Rearranging, we get
-%\begin{equation} 
-%\begin{aligned} 
-%  1 - \tilde{p} < 
-%  & - \tilde{p}(1+b-c)(1-\tilde{p}) (1-\alpha) T_B \\
-%  & + (1-\tilde{p}) (1-c) (\tilde{p} (1-\alpha) T_B + 1 - T_B) \\
-%  & + (1-\tilde{p}) (1+b) (\tilde{p} (1-\alpha) + \alpha) T_A \\
-%  & + (1-\tilde{p})^2 (1-\alpha) T_A .
-%\end{aligned}
-%\end{equation}
-%Diving by $(1-\tilde{p})$ and rearranging so that free terms are on the left and terms with $\tilde{p}$ are on the right, we have
-%\begin{equation} 
-%\begin{aligned} 
-%  &1 - (1-\alpha) T_A - (1+b) \alpha T_A - (1 - T_B)(1-c)  < \\
-%   &\tilde{p}[ - (1+b-c) (1-\alpha) T_B 
-%   + (1-c) (1-\alpha) T_B
-%   + (1+b) (1-\alpha) T_A 
-%   - (1-\alpha) T_A].
-%\end{aligned}
-%\end{equation}
-Simplifying, we find that $\tilde{p}'>\tilde{p}$ if and only if
-\begin{equation} \label{eq:vert_hori_global_condition}
-c(1-T_B) - b \alpha T_A - (T_A-T_B) < \tilde{p} \cdot b (1-\alpha) (T_A-T_B) \;.
-\end{equation}
-
-In addition to the the fixation states $\tilde{p}=0$ and $\tilde{p}=1$, there may be an actual polymorphic equilibrium of $\tilde{p}'=\tilde{p}$ in Eq.\ \ref{eq:nextgen_parents_vertical_only}, namely 
-\begin{equation} \label{eq:vert_hori_equilibrium}
-  \tilde{p}^* = 
-  \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B)} ,
-\end{equation} 
-which is legitimate if $0<\tilde{p}^*<1$.
-
-Since all parameters are positive, we can apply
-inequality \ref{eq:vert_hori_global_condition} and see that a requirement for $\tilde{p}'>\tilde{p}$ is that either 
-\begin{align} 
-\label{eq:vert_hori_global_condition1}
-T_A > T_B \quad&\text{and}\quad \tilde{p}>\tilde{p}^*,  \quad \text{or} \\
-\label{eq:vert_hori_global_condition2}
-T_A <T_B \quad&\text{and}\quad \tilde{p}<\tilde{p}^* .
-\end{align}
-
-We define the \emph{cost boundaries},
-\begin{equation} \label{eq:cost_boundaries}
-\begin{aligned}
-\gamma_1 = \frac{b \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
-\gamma_2 = \frac{b \alpha T_B + (1+b) (T_A - T_B)}{1-T_B}.
-\end{aligned}
-\end{equation}
-Then, applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we  summarize the possible outcomes in the following result and corollaries.
-\\
-
-\begin{result}[Vertical and horizontal transmission of cooperation] \label{result:vert_hori}
-With vertical and horizontal but without oblique transmission ($v=1$), the cultural evolution of cooperation exhibits one of the following scenarios, depending on the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}):
-
-%\begin{enumerate} % p* version
-%\item Fixation of cooperation,
-%	if $T_A>T_B$ and $0<\tilde{p}^*$, or
-%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0>\tilde{p}^*$, or
-%	if $T_A<T_B$ and $1<\tilde{p}^*$.
-%\item Global fixation of defection,
-%	if $T_A>T_B$ and $\tilde{p}^*>1$, or
-%	if $T_A>T_B$ and $0<\tilde{p}^*<1$, and $\tilde{p}_0<\tilde{p}^*$, or
-%	if $T_A<T_B$ and $\tilde{p}^*<0$
-%\item Co-existence of both phenotypes at $\tilde{p}^*$, 
-%	if $T_A<T_B$ and $0<\tilde{p}^*<1$.
-%\end{enumerate}
-\begin{enumerate} % gamma version
-\item \emph{Fixation of cooperation}:
-	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or
-	if \emph{(ii)} $T_A < T_B$ and $c < \gamma_2$.
-\item \emph{Fixation of defection}:
-	if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or
-	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
-\item \emph{Stable coexistence}:
-	if \emph{(v)} $T_A<T_B$ and $\gamma_2 < c < \gamma_1$.
-\item \emph{Unstable coexistence}: 
-	if \emph{(vi)} $T_A>T_B$ and $\gamma_1 < c <\gamma_2$.
-\end{enumerate}
-\end{result}
-
-These conditions are illustrated in \autoref{fig:result2}.
-
-Cooperation and defection can coexist stably at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:vert_hori_equilibrium}) if there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:result2}b.
-When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:coexistence_recursive}a shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
-\\
-
-\begin{corollary}[Symmetric horizontal transmission] 
-\label{corollary:equal_transmission}
-If $T=T_A=T_B$, then cooperation will take over the population if
-\begin{equation}
-\label{eq:equal_transmission}
-c < b \cdot \alpha \frac{T}{1-T} \;.
-\end{equation}
-\end{corollary}
-Note that the right-hand side equals $\gamma_1$ when $T=T_A=T_B$.
-This condition is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:vert_hori_global_condition} and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-\autoref{fig:results}a illustrates this condition.
-
-The condition in inequality~\ref{eq:equal_transmission} demonstrates the importance of the social association $\alpha$. The following corollaries provide additional demonstrations.
-\\
-
-\begin{corollary}[No social association of transmission and cooperation]
-\label{corollary:alpha0}
-Without social association ($\alpha=0$), cooperation can take over the population if there is horizontal transmission bias for cooperation, $T_A>T_B$, and if either
-\begin{equation}
-\label{eq:vert_hori_alpha0}
-c < \frac{T_A-T_B}{1-T_B}
-\quad \text{or} \quad
-\tilde{p}_0 > \tilde{p}^* = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B)} \;.
-\end{equation}
-\end{corollary}
-
-\autoref{fig:result2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:vert_hori_equilibrium} and \ref{eq:cost_boundaries}.
-If there is horizontal transmission bias for cooperation ($T_A>T_B$) then cooperation can evolve from any initial frequency if the cost is low enough, $c<\gamma_1$ (green area below solid line).
-If the cost is not low enough, cooperation can also evolve if its initial frequency is high enough and the cost is not too high, $c<\gamma_2$ (blue area between solid and dashed lines).
-
-We can interpret these condition as follows.
-First, when cooperators are rare, they will mostly interact with defectors.
-Therefore, for cooperation to increase in frequency and fix, the \emph{effective cost of cooperation} must be lower than the horizontal transmission of cooperation, $1-(1-c)(1-T_B) < T_A$, which is equivalent to the first of the two inequalities in \autoref{eq:vert_hori_alpha0}.
-Second, if $T_A$ is not large enough, cooperation will fix if the initial frequency is higher than the threshold $\tilde{p}^*$; thus, this threshold must be below one, which entails $1-(1-c)(1-T_B) < T_A + b(T_A-T_B)$.
-That is, the effective cost of cooperation must be lower than the combined effect of horizontal transmission of cooperation, $T_A$, and the benefit of cooperation multiplied by the transmission bias, $b(T_A-T_B)$.
-\\
-
-\begin{corollary}[Perfect social association of transmission and cooperation]
-\label{corollary:alpha1}
-With perfect social association ($\alpha=1$), the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if
-\begin{equation}\label{eq:vert_hori_alpha1}
-c < \frac{b \cdot T_A + (T_A - T_B)}{1-T_B}.
-\end{equation}
-\end{corollary}
-This condition is obtained from inequality \ref{eq:vert_hori_alpha1_condition_proof}, and the right-hand side equals $\gamma_1$ when $\alpha=1$ (\autoref{eq:cost_boundaries}).
-Perfect social association (horizontal transmission always occurs during the cooperative interaction) is also assumed in the model studied by \citet{lewin2017microbes}, and therefore this corollary is equivalent to the result in their eq.~1.
-
-%In terms of the cost boundaries, inequality~\ref{eq:vert_hori_alpha1} is equivalent to $c<\gamma_1$, and if $T_A>T_B$ then that suffices for fixation of cooperation.
-If $T_B>T_A$ then $\gamma_2(\alpha=1)<0$ and again, inequality~\ref{eq:vert_hori_alpha1} is sufficient for increase in the frequency of $A$.
-Inequality~\ref{eq:vert_hori_alpha1} can also be written as
-$1 - (1-c)(1-T_B) < (1+b) T_A$,
-which provides an interesting interpretation for the success of cooperation. 
-In the interaction between a cooperator and a defector, $(1-c)(1-T_B)$ is the probability that the cooperator remains cooperative and also reproduces. 
-Therefore, $1 - (1-c)(1-T_B)$ is the probability that either the cooperator becomes a defector, or that it fails to reproduce.
-This is the \emph{effective cost of cooperation} from this interaction.
-Similarly, $(1+b) T_A$ is the probability that during an interaction between a cooperator and a defector, the defector becomes cooperative and reproduces, which is the \emph{effective benefit of cooperation} from this interaction.
-Thus, inequality~\ref{eq:vert_hori_alpha1} entails that cooperation can evolve if the effective cost of cooperation is less than the effective benefit during an interaction between a cooperator and a defector.
-\\
-
-Given the previous two corollaries for no association and perfect association ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of social association on the evolution of cooperation.
-We denote the social association boundaries by
-\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting}
-  a_1 = \frac{c(1-T_B)-(1+b)(T_A-T_B)}{b\cdot T_B}, \quad
-  a_2 = \frac{c(1-T_B)-(T_A-T_B)}{b\cdot T_A}.
-\end{aligned}\end{equation}
-Applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we have the following corollary.
-\\
-
-\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:intermediate_association}
-Cooperation will increase from rarity if social association is high enough, specifically if $a_2 < \alpha$.
-\end{corollary}
-
-\autoref{fig:result2}c demonstrates these conditions.
-With horizontal transmission bias for cooperation ($T_A>T_B$), cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
-With horizontal bias favoring defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
-Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough; $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{With Vertical and Oblique Transmission}
-
-With both vertical and oblique transmission, $0<v<1$, the recursion system is more complex
-and we focus on local rather than on global stability.
-To proceed,  note that 
-\autoref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
-\autoref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
-\autoref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
-%TODO YR cleanup  
-Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}),
-determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
-%: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})=\bar{w}(\hat{p}'-\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.
-
-%We start with the simple case of symmetrical horizontal transmission, $T=T_A=T_B$ and apply \autoref{eq:horizontal}, \autoref{eq:nextgen_adults_slimpify}, and \autoref{eq:nextgen_parents_simplified} to obtain
-%\begin{equation} \label{eq:equal_horizontal_transmission}
-%\begin{aligned}
-%  f(\hat{p}) &= 
-%  \bar{w}(\hat{p}' - \hat{p}) = \\
-%  &\hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big].\end{aligned}
-%\end{equation}
-%A detailed explain of how we get eq.~\ref{eq:equal_horizontal_transmission} can be found in appendix B.
-%The equilibria are solutions of $f(\hat{p})=0$, or $\hat{p}' = \hat{p}$.
-%It is easy to verify that fixation of either phenotype, $\hat{p} =  0$ and $\hat{p} = 1$, is an equilibrium.
-%Since the derivative of $f'(\hat{p}$ is 
-%\begin{equation}
-%f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big],
-%\end{equation}
-%then the condition for local stability of $\hat{p}=1$ is
-%\begin{equation} \label{eq:derivative_of_phattag-phat}
-%	f'(1) =	-\alpha bvT + cv(1-T) < 0,
-%\end{equation}
-%which gives the following result.
-%
-%\textbf{Result 3: Oblique and vertical transmission with symmetric horizontal transmission.}
-%If horizontal transmission is symmetric, $T = T_A = T_B$, and if
-%\begin{equation} \label{eq:oblique_and_vertic_result2}
-%  %\frac{b}{c}>\frac{1-T}{\alpha T}
-%	c < b \cdot \frac{\alpha T}{1-T},
-%\end{equation}
-%then fixation of the cooperator phenotype $A$ is locally stable.
-%The same condition was given in Corollary 1.1, \autoref{eq:equal_transmission}.
-
-%We now turn to the general case where $T_A \neq T_B$. 
-Applying Eqs.\ \ref{eq:horizontal}, \ref{eq:nextgen_adults_slimpify}, and \ref{eq:nextgen_parents_simplified} gives the function $f(\hat{p})$ (see Appendix~\autoref{sec:appendixA}):
-
+In the following sections, we determine the equilibria of the model, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
+We then analyze the evolution of a modifier of the social association to determine the evolution of social association.
+Finally, we demonstrate the application of the conditions derived in the previous sections to predict the outcomes of stochastic simulations in a spatial model.
+
+\subsection*{Equilibria and Stability}
+
+To determine the equilibria in our model, we analyze the fixed points of \autoref{eq:nextgen_juveniles}.
+We define $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics,  this simplifies to
 \begin{equation} \label{eq:general_case_polynomial}
@@
 \end{equation}
-Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{corollary:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
+%Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{corollary:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
 
@@
 $\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
-\begin{equation} \label{eq:oblique_and_vertic_result}
+\begin{equation} \label{eq:general_equilibrium}
   \hat{p}^* =  
@@
 
-Define new cost boundaries, $\hat\gamma_1$ and $\hat\gamma_2$,
-\begin{equation} \label{eq:cost_boundaries_v}
+We define the \emph{cost boundaries}, $\hat\gamma_1$ and $\hat\gamma_2$,
+\begin{equation} \label{eq:cost_boundaries}
 \begin{aligned}
@@
 \end{equation}
-and  a vertical transmission threshold,
+and the \emph{vertical transmission threshold}, $\hat v$,
 \begin{equation} \label{eq:v_threshold}
@@
 
-The following result summarizes the possible outcomes.
+The following result summarizes the possible outcomes of the model (\autoref{eq:nextgen_juveniles}).
 \\
 
-\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) and the vertical transmission threshold $\hat v$ (\autoref{eq:v_threshold}) :
+\begin{result}[Equilibria and stability] \label{result:vert_obli_hori}
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ and the vertical transmission threshold $\hat v$ (Eqs.~\ref{eq:cost_boundaries}-\ref{eq:v_threshold}) :
 
@@
 	if \emph{(iv)} $T_A < T_B$ and $\hat\gamma_1 < c$.
-\item \emph{Stable Coexistence}: 
+\item \emph{Stable coexistence}: 
     if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_1$; or 
@@
 Much of the literature on evolution of cooperation focuses on conditions for  initially rare cooperative phenotype to invade a population of defectors.
-The next corollary deals with such a condition.
+The next remarks deal with such conditions. The first introduces a condition on the cost of cooperation, $c$, and the second on the social association, $\alpha$.
 \\
 
-\begin{corollary}[Condition for cooperation to increase from rarity]
+\begin{remark}[Condition for cooperation to increase from rarity: cost of cooperation]
 \label{corollary:rarity}
@@
 \begin{equation} \label{eq:unequal_transmission_from_rarity_general_case}
-  \begin{aligned}
 c < \hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)} \;.
-  \end{aligned}
-  \end{equation} 
-  \end{corollary}
+\end{equation} 
+\end{remark}
 
 This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
+In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
+
 Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \hat\gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
-Similarly, increasing the horizontal transmission of cooperation increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), making it easier for cooperation to evolve.
-However, increasing the horizontal transmission of defection can either increase or decrease the boundary depending on $sign(\partial\gamma_1/\partial T_B) = sign(vb \alpha T_A+T_A-1)$. 
-Therefore, increasing $T_B$ increases the boundary when $T_A > \frac{1}{1+\alpha b v}$ but when this applies we get that $\hat\gamma_1 > 1$ which guarantees cooperation will evolve from rairty since $c<1$.
-When $T_A < \frac{1}{1+\alpha b v}$ increasing $T_B$ decreases the boundary.
-
-Increasing the vertical transmission $v$ can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$ (because $\text{sign}(\partial \hat\gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.)
-When $T_A<T_B$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the boundary on the cost increases making it easier for cooperation to evolve from rarity.
-Similarly, when $T_A > T_B$ we get $\partial \hat\gamma_1 / \partial v <0$ and therefore, as the vertical transmission increases the boundary on the cost decreases making it harder for cooperation to evolve from rarity.
-We got that when $T_A>T_B$ vertical transmission is interfering cooperation to evolve by decreasing the maximum cost that the cooperates can pay and stil evolve from rairty. 
-% TODO YR revise; note that without vertical transmission TA-TB determines the outcome
-
-In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
-Without horizontal transmission bias, i.e., with $T=T_A=T_B$, these conditions reduce to a form of Hamilton's rule.
+Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation.
+However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost boundary, but it increases the cost boundary when it is already above one ($c<1<\hat\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\hat\gamma_1>1/v$.
+Therefore, increasing $T_B$ decreases the cost boundary and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
+
+Increasing the vertical transmission $v$ can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \hat\gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
+When $T_A<T_B$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the cost boundary increases, making it easier for cooperation to evolve from rarity.
+In contrast, when $T_A > T_B$ we get $\partial \hat\gamma_1 / \partial v <0$ and therefore, as the vertical transmission increases the cost boundary decreases making it harder for cooperation to evolve from rarity.
+
+When there is no horizontal transmission bias, $T_A=T_B$, the next remark applies.
 \\
 
-In Corollary~\autoref{corollary:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
-A more general case can be stated for $0 < v \leq 1$.
-Consider the social association boundaries 
+\begin{remark}[Symmetric horizontal transmission] 
+\label{corollary:equal_transmission}
+If $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if
+\begin{equation}
+\label{eq:equal_transmission}
+c < b v \cdot \frac{\alpha T}{1-T} \;.
+\end{equation}
+\end{remark}
+This condition is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:unequal_transmission_from_rarity_general_case} and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+\autoref{fig:results}a illustrates this condition for $v=1$. Note that the right-hand side equals $\hat\gamma_1$ when $T=T_A=T_B$.
+
+%In Corollary~\autoref{corollary:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
+%A more general case can be stated for $0 < v \leq 1$.
+In the next remarks we examine the effect of social association on the evolution of cooperation.
+\\
+
+\begin{remark}[No social association]
+\label{corollary:alpha0}
+Without social association ($\alpha=0$), cooperation can increase from rarity, and go to fixation, if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
+\begin{equation}
+\label{eq:vert_hori_alpha0}
+c < \frac{T_A - T_B}{v(1-T_B)} \;.
+\end{equation}
+\end{remark}
+
+\autoref{fig:result2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:unequal_transmission_from_rarity_general_case} and \ref{eq:cost_boundaries}.
+Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of social association. The outcome is determined only by  cultural transmission.
+\\
+
+\begin{remark}[Perfect social association]
+\label{corollary:alpha1}
+With perfect social association ($\alpha=1$), cooperation will increase from rarity if
+\begin{equation}\label{eq:vert_hori_alpha1}
+c < \frac{b v T_A + (T_A - T_B)}{v(1-T_B)} \;.
+\end{equation}
+\end{remark}
+This condition is obtained by setting $\alpha=1$ in Eqs.\ \ref{eq:unequal_transmission_from_rarity_general_case} and \ref{eq:cost_boundaries}.
+
+Moreover, without oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality \ref{eq:vert_hori_alpha1} applies.
+This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}, and therefore when $v=1$, this remark is equivalent to their eq.~1.
+
+Given the previous two remarks for no association and perfect association ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of social association on the evolution of cooperation.
+Consider the \emph{social association boundaries}, $\hat{a}_1$ and $\hat{a}_2$,
 \begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting_general_case}
@@
 \end{aligned}\end{equation}
-
 Then the following applies.
@@
 
-\begin{corollary}[Intermediate association of transmission and cooperation]
+\begin{remark}[Condition for cooperation to increase from rarity: social association]
 \label{corollary:intermediate_association_res3}
 Cooperation will increase from rarity if social association is high enough, specifically if $\hat a_2 < \alpha$.
-\end{corollary}
-\autoref{fig:result3}cd illustrates this conditions.
-
-Note that $\partial \hat a_2 / \partial v = b T_A (T_A-T_B)$.
-$\partial \hat a_2 / \partial v > 0$ when $T_A > T_B$ and therefore, as the vertical transmission $v$ \emph{increases} a greater value of social association is required for fixation of cooperation from rarity.
-%TODO YR revise
-Similarly, when $T_B>T_A$ $T_A > T_B$ we get $\partial \hat a_2 / \partial v < 0$ and therefore, as $v$ \emph{decreases} a greater value of social association is required for fixation of cooperation from rarity.
+\end{remark}
+\autoref{fig:result3}cd illustrates this condition.
+\autoref{fig:result2}c demonstrates these conditions.
+With horizontal transmission bias for cooperation ($T_A>T_B$), cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
+With horizontal bias favoring defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
+Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+
+Interestingly, the effect of vertical transmission on this condition depends on the horizontal transmission bias, $\partial \hat a_2 / \partial v = b T_A (T_A-T_B)$. 
+That is, with horizontal bias for cooperation, $T_A>T_B$, the boundary increases with the rate of vertical transmission, impeding the evolution of cooperation.
+In contrast, with horizontal bias for defection, $T_A<T_B$, the boundary decreases with the rate of vertical transmission, facilitating the evolution of cooperation.
+
+These effects of vertical and oblique transmission are demonstrated in \autoref{fig:result3}cd. 
+The next remarks further inspect the roles of vertical and oblique transmission in the evolution of cooperation.
 \\
 
-\begin{corollary}[Necessary condition for fixation of cooperation]
+\begin{remark}[Necessary condition for fixation of cooperation: vertical transmission rate]
 \label{corollary:vhat}
@@
     \end{equation} 
-\end{corollary}
+\end{remark}
 %Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
 This condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
-When horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate, i.e. $\hat{v}<0$.
-In contrast, if the horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation, see \autoref{fig:result3}bd.
+If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
+In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough~(\autoref{eq:fixation_of_cooperation_vertical_transmission_condition}): in this case oblique transmission can prevent fixation of cooperation (see \autoref{fig:result3}bd).
+
+With only oblique and horizontal transmission, i.e. $v = 0$, Eq.\ \ref{eq:horizontal} becomes $\hat{p}=p$ and Eq.\ \ref{eq:nextgen_adults_slimpify} becomes 
+\begin{equation}  \label{eq:nextgen_parents_oblique_only}
+p' = p^2 (T_B-T_A) + p (1+T_A-T_B) \;,
+\end{equation}
+which gives the following result.\\
+
+\begin{remark}[Condition for global fixation of cooperation: oblique and horizontal transmission] \label{result:obli_hori}
+Without vertical transmission ($v=0$), the frequency of the cooperator phenotype among adults increases every generation, $p'>p$ if there is a horizontal transmission bias in favor of cooperation, namely
+\begin{equation} \label{eq:oblique_only_result}
+T_A > T_B \;.
+\end{equation}
+\end{remark}
+
+That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ are missing from \autoref{eq:nextgen_parents_oblique_only}).
+The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers (see~{\autoref{fig:results}c).
+Note that without bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
+
+Finally, the last remark focuses on the coexistence of cooperation and defection.
 \\
 
-\subsection*{Modifiers of social association}
-
-We now analyze the evolution of social association under perfect vertical transmission, $v=1$.
-We assume a population at a stable coexistence of the two phenotypes, cooperation $A$ and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
-\autoref{eq:vert_hori_equilibrium}).
-Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries})
-
-The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$ (\autoref{eq:mean_fitness}), which is increasing in $\tilde{p}^*$. 
-Therefore, to determine the effect of increasing $\alpha$ on the stable population mean fitness, we must analyze its effect on $\tilde{p}^*$, 
-\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
-  \frac{\partial \tilde{p}^*}{\partial \alpha} 
-%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
-%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
-  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
-\end{equation} 
-Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
-\begin{equation}
-c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
-\end{equation} 
-Therefore, $b T_A - c(1-T_B) - (T_B-T_A)>0$, and since $T_A<T_B$, the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive, and the population mean fitness increases as social association $\alpha$ increases.
-
-Therefore, if the social association increases, the population mean fitness will increase.
-But can an allele that increases the social association evolve? 
-To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988}.
-The function of this modifier locus is to determine the social association.
-It has no direct effect on fitness.
-We assume that the modifier locus has two alleles, $M$ and $m$, which induce association probabilities $\alpha_1$ and $\alpha_2$, respectively, and that initially only $M$ is present.
-Suppose that the population evolves to a stable equilibrium when only $M$ is present; we check the local stability of this equilibrium to the introduction of the allele $m$ at the modifier locus.
-This is called ``external stability''; For more details on external stability, see \citet{Altenberg2017}.
-
-We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
-Then the following recursion system defines the frequencies of the pheno-genotypes in the next generation,
-\begin{equation} \label{eq:next_gen_p_1}
-  \begin{aligned}
-	% p1
-  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A 
-\\
-	% p2
-  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
-  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3))\\
-  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B 
-\\
-	% p3
-  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A 
-\\
-	% p4
-  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
-  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
-  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
-  \end{aligned}
-\end{equation}
-%which we can write as 
-%\begin{equation}
-%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
-%\end{equation}
-where $\bar{w} = 1 + (b-c)\cdot(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-
-The local stability of $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, the equilibrium when only allele $M$ is present (see \autoref{eq:vert_hori_equilibrium}), to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
-$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e.
-locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, which is derived from \autoref{eq:next_gen_p_1} as
-\begin{equation}
-\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{bmatrix}
-	 \frac{\partial \tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-	 \frac{\partial \tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
-	 \frac{\partial \tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-	 \frac{\partial \tilde{p}_4'}{\partial \tilde{p}_4} (\vec{\tilde{p}}^*)
-\end{bmatrix} \;.
-\end{equation}
-If the eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}}$ is externally stable and allele $m$ cannot invade the population of allele $M$.
+\begin{remark}[Coexistence of cooperation and defection]
+Cooperation and defection can coexist at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:general_equilibrium}). 
+When it occurs, the coexistence is stable if there is horizontal transmission bias for defection, $T_A<T_B$, and unstable if there is horizontal bias for cooperation, $T_A>T_B$.
+\end{remark}
+
+% TODO - revise the next paragraph
+If there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:result2}b.
+When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+\autoref{fig:coexistence_recursive}a shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
+
+% TODO - consider adding v=1 case?
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection*{With Population Structure}
@@
 Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
-
 \end{appendices}
@@
 	In all cases the vertical transmission rate $v$ is on the x-axis.
-	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are represented by the solid and dashed lines, respectively.
+	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries}) are represented by the solid and dashed lines, respectively.
     (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.

### 2020-10-24 ms/main.tex
Proof that if alpha2>alpha1 then invasion is successful
Add results to tex file

--- 2020-10-20 ms/main.tex
@@
   &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B 
+  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B 
 \\
@@
   &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
+  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
   \end{aligned}
@@
 \mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{bmatrix}
-	 \frac{\partial \tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-	 \frac{\partial \tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
-	 \frac{\partial \tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-	 \frac{\partial \tilde{p}_4'}{\partial \tilde{p}_4} (\vec{\tilde{p}}^*)
+	 \frac{\partial \bar{w} \tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
+	 \frac{\partial \bar{w}  \tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
+	 \frac{\partial \bar{w}  \tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
+	 \frac{\partial \bar{w}  \tilde{p}_4'}{\partial \tilde{p}_4} (\vec{\tilde{p}}^*)
 \end{bmatrix} \;.
@@
   \begin{aligned}
-  &\frac{\partial\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b(\tilde{p}^*-(1-\alpha_2)T_B(\tilde{p}^*-\tilde{p}^{*2}))+(1-c)(1+\tilde{p}^*T_B-T_B)\\
-  &\frac{\partial\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = bT_A\tilde{p}^*(\tilde{p}^*+\alpha_2(1-\tilde{p}^*))+\tilde{p}^*T_A\\
-  &\frac{\partial\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = T_B(1-\tilde{p}^*)-cT_B(1-\tilde{p}^*)(\alpha_2+(1-\alpha_2)(1-\tilde{p}^*))\\
-  &\frac{\partial\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1-\tilde{p}^*T_A+ b\tilde{p}^*(1-\alpha_2T_A(1-\tilde{p}^*)-T_A\tilde{p}^*)\\
-  \end{aligned}
-\end{equation}
+  &D_{33} = \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b(\tilde{p}^*-(1-\alpha_2)T_B(\tilde{p}^*-\tilde{p}^{*2}))+(1-c)(1+\tilde{p}^*T_B-T_B)\\
+  &D_{34} = \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = bT_A\tilde{p}^*(\tilde{p}^*+\alpha_2(1-\tilde{p}^*))+\tilde{p}^*T_A\\
+  &D_{43} =\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1-\tilde{p}^*)(1-c)T_B+b\tilde{p}^*(1-\alpha_2)(1-\tilde{p}^*)T_B\\
+  &D_{44} =\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1-\tilde{p}^*T_A+ b\tilde{p}^*(1-\alpha_2T_A(1-\tilde{p}^*)-T_A\tilde{p}^*)\\
+  \end{aligned}
+\end{equation}
+Looking on the greater eigenvalue of $\mathbf{L}^*_{ex}$ $\lambda_1$:
+\begin{equation} \label{eq:eigenvalues}
+  \lambda_1 = \frac{D_{33} + D_{44} + \sqrt{(D_{33}+D_{44})^2-4*(D_{33}+D_{44}-D_{43}D_{34})}}{2} 
+\end{equation}
+Using SymPy \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics we get that $\lambda_1 > 1$ when:
+\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
+ \alpha_2 > \frac{b\tilde{p}^*(T_B-T_A) + T_B - T_A  + c (1-T_B)}{b*(T_A(1-\tilde{p}^*) + T_B\tilde{p}^*)}
+\end{equation}
+Using \autoref{eq:vert_hori_equilibrium} we get that $\lambda_1 > 1$ when:
+\begin{equation} \label{eq:eigenvalues_greater_than_1_final_condition}
+  \alpha_2 > \alpha_1
+ \end{equation}
+ % TODO: make this result
 

### 2020-10-25 ms/main.tex
revised and verified modifier model

@@
 
-\subsection*{Modifiers of social association}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Evolution of social association}
 
 We now analyze the evolution of social association under perfect vertical transmission, $v=1$.
-We assume a population at a stable coexistence of the two phenotypes, cooperation $A$ and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
+We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
 \autoref{eq:vert_hori_equilibrium}).
@@
 \end{equation} 
-Therefore, $b T_A - c(1-T_B) - (T_B-T_A)>0$, and since $T_A<T_B$, the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive, and the population mean fitness increases as social association $\alpha$ increases.
-
-We found that if the social association increases, the population mean fitness will increase.
-But can an allele that increases the social association evolve? 
-To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988}.
-The function of this modifier locus is to determine the social association.
-It has no direct effect on fitness.
-We assume that the modifier locus has two alleles, $M$ and $m$, which induce association probabilities $\alpha_1$ and $\alpha_2$, respectively, and that initially only $M$ is present.
-Suppose that the population evolves to a stable equilibrium when only $M$ is present; we check the local stability of this equilibrium to the introduction of the allele $m$ at the modifier locus.
-This is called ``external stability''; For more details on external stability, see \citet{Altenberg2017}.
+Therefore, the numerator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is positive.
+Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is also positive, and hence the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive.
+Thus, the population mean fitness increases as social association $\alpha$ increases.
+
+We found that if social association increases, the population mean fitness also increases.
+But can an allele that increases social association evolve? 
+To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988} that determines social association, but has no direct effect on fitness.
+We assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
+Suppose that the population evolves to a stable equilibrium when only allele $M$ is present; we check the local stability of this equilibrium to the introduction of allele $m$ at the modifier locus; This is called ``external stability'', see \citet{Altenberg2017}.
 
@@
   &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A 
+  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A \;,
 \\
@@
   &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B 
+  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B \;, 
 \\
@@
   &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A 
+  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A \;, 
 \\
@@
 %\end{equation}
-where $\bar{w} = 1 + (b-c)\cdot(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-
-The local stability of $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, the equilibrium when only allele $M$ is present (see \autoref{eq:vert_hori_equilibrium}), to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+where $\bar{w} = 1 + (b-c)(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+
+The equilibrium when only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
+\begin{equation} \label{eq:p_tilde_star_alpha_1}
+\tilde{p}^*=
+\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)},
+\end{equation}
+which we get by setting $\alpha=\alpha_1$ in \autoref{eq:vert_hori_equilibrium}.
+Its local stability to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
 $\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
 The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e.
-locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, which is derived from \autoref{eq:next_gen_p_1} as
+Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, 
 \begin{equation}
-\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{bmatrix}
-	 \frac{\partial \bar{w} \tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-	 \frac{\partial \bar{w}  \tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
-	 \frac{\partial \bar{w}  \tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-	 \frac{\partial \bar{w}  \tilde{p}_4'}{\partial \tilde{p}_4} (\vec{\tilde{p}}^*)
-\end{bmatrix} \;.
-\end{equation}
-If the eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}}$ is externally stable and allele $m$ cannot invade the population of allele $M$.
-
+\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{pmatrix}
+	 X &
+	 Y \\
+	 Z &
+	 Q 
+\end{pmatrix} \;.
+\end{equation}
+
+The elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1},
 \begin{equation} \label{eq:partial_derivatives}
   \begin{aligned}
-  &D_{33} = \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b(\tilde{p}^*-(1-\alpha_2)T_B(\tilde{p}^*-\tilde{p}^{*2}))+(1-c)(1+\tilde{p}^*T_B-T_B)\\
-  &D_{34} = \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = bT_A\tilde{p}^*(\tilde{p}^*+\alpha_2(1-\tilde{p}^*))+\tilde{p}^*T_A\\
-  &D_{43} =\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1-\tilde{p}^*)(1-c)T_B+b\tilde{p}^*(1-\alpha_2)(1-\tilde{p}^*)T_B\\
-  &D_{44} =\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1-\tilde{p}^*T_A+ b\tilde{p}^*(1-\alpha_2T_A(1-\tilde{p}^*)-T_A\tilde{p}^*)\\
-  \end{aligned}
-\end{equation}
-Looking on the greater eigenvalue of $\mathbf{L}^*_{ex}$ $\lambda_1$:
+%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
+  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
+%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
+  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
+% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
+  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - c) T_B (1 - \tilde{p}^*) + b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) \;,\\
+%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
+  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - T_A \tilde{p}^* + b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* \;.
+  \end{aligned}
+\end{equation}
+
+If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
+These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
 \begin{equation} \label{eq:eigenvalues}
-  \lambda_1 = \frac{D_{33} + D_{44} + \sqrt{(D_{33}+D_{44})^2-4*(D_{33}+D_{44}-D_{43}D_{34})}}{2} 
-\end{equation}
-Using SymPy \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics we get that $\lambda_1 > 1$ when:
+  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
+\end{equation}
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
 \begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
- \alpha_2 > \frac{b\tilde{p}^*(T_B-T_A) + T_B - T_A  + c (1-T_B)}{b*(T_A(1-\tilde{p}^*) + T_B\tilde{p}^*)}
-\end{equation}
-Using \autoref{eq:vert_hori_equilibrium} we get that $\lambda_1 > 1$ when:
-\begin{equation} \label{eq:eigenvalues_greater_than_1_final_condition}
-  \alpha_2 > \alpha_1
- \end{equation}
- % TODO: make this result
+\begin{aligned}
+ \alpha_2 > 
+ \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
+% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
+% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
+%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
+%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
+\alpha_1 \;,
+\end{aligned}
+\end{equation}
+which gives the following result.
+\\
+
+\begin{result}[Evolution of social association] 
+In a population at a stable coexistence between cooperation and defection, a modifier allele can successfully invade the population if it increases the social association.
+Such an invasion will, in turn, increase the population mean fitness.
+\end{result}
 

### 2020-10-25 ms/main.tex
format multiline eqs

--- 2020-10-21 ms/main.tex
@@
 \let\vec\mathbf
-\newcommand{\matrx}[1]{{\left[ \stackrel{}{#1}\right]}}
+\newcommand{\matrx}[1]{{\Big[ \stackrel{}{#1}\Big]}}
 \newcommand{\diag}[1]{\mbox{diag}\matrx{#1}}
@@
 \begin{aligned}
-\hat{p}
-& = \tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \\
-& = v \tilde{p} + (1-v) p \;.
+\hat{p} =
+& \tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] = \\
+& v \tilde{p} + (1-v) p \;.
 \end{aligned}
@@
 \begin{aligned}
-p'
-& = \hat{p}^2 [\alpha + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
-& + \hat{p}(1-\hat{p}) [\alpha(1-T_B) + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
-& + (1-\hat{p})\hat{p} [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
-& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A] \;,
+p' = 
+& \hat{p}^2 \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
+& \hat{p}(1-\hat{p}) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
+& (1-\hat{p})\hat{p} \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] + \\
+& (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
 \end{aligned}
@@
 \begin{equation}\label{eq:nextgen_adults_slimpify}
-p' = \hat{p}^2(T_B-T_A) + \hat{p}(1+T_A-T_B) .
+p' = \hat{p}^2(T_B-T_A) + \hat{p}(1+T_A-T_B) \;.
 \end{equation}
@@
 \begin{aligned}
-\bar{w} \tilde{p}'
-& = \hat{p}^2 (1+b-c) [\alpha + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
-& + \hat{p}(1-\hat{p}) (1-c) [\alpha(1-T_B) + (1-\alpha)(\hat{p} + (1-\hat{p})(1-T_B))] \\
-& + (1-\hat{p})\hat{p} (1+b) [\alpha T_A + (1-\alpha) \hat{p} T_A ] \\
-& + (1-\hat{p})^2 [(1-\alpha) \hat{p} T_A] \;,
+\bar{w} \tilde{p}' =
+& \hat{p}^2 (1+b-c) \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
+& \hat{p}(1-\hat{p}) (1-c) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
+& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] + \\
+& (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
 \end{aligned}
@@
 \begin{aligned}
-\bar{w} \tilde{p}'
-& = \hat{p}^2 (1+b-c) \big(1-(1-\hat{p})(1-\alpha)T_B)\big) \\
-& + \hat{p}(1-\hat{p}) (1-c) \big(\hat{p}(1-\alpha)T_B+1-T_B\big) \\
-& + (1-\hat{p})\hat{p} (1+b) \big(\hat{p}(1-\alpha) + \alpha\big) T_A \\
-& + (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
+\bar{w} \tilde{p}' =
+& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] + \\
+& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] + \\
+& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A + \\
+& (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
 \end{aligned}
@@
 \begin{aligned}
-  \hat{p}'  = & \frac{v}{\bar{w}}\left\{\hat{p}^2(1+b-c)\left[1-(1-\hat{p})(1-\alpha)T_B)\right]\right\} \\
-  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1-c)\left[ \hat{p}(1-\alpha)T_B + 1 - T_B \right] \right\} \\
-  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1+b)\left[\hat{p}(1-\alpha) + \alpha \right]T_A \right\} \\
-  & + \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \\
-  & + (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B),
+\hat{p}' =
+& \frac{v}{\bar{w}}\Big[\hat{p}^2(1+b-c)\Big[1-(1-\hat{p})(1-\alpha)T_B)\Big]\Big] + \\
+& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1-c)\big( \hat{p}(1-\alpha)T_B + 1 - T_B \big) \Big] + \\
+& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1+b)\big(\hat{p}(1-\alpha) + \alpha \big) T_A \Big] + \\
+& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A + \\
+& (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B) \;,
 \end{aligned}
@@
 We show that high levels of such social association greatly increase the potential for evolution of cooperation (\autoref{fig:result2}).
-With enough social association ($\alpha > \big(c(1-T_B) + (T_B-T_A)\big) / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$, see Result~\autoref{result:vert_hori}).
+With enough social association ($\alpha > \Big[c(1-T_B) + (T_B-T_A)\Big] / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$, see Result~\autoref{result:vert_hori}).
 
@@
 1-p' &< 1-p  \Leftrightarrow \\
-\frac{f'(1)(p-1) + O\big((p-1)^2\big)}{p-1} &< 0 \Leftrightarrow \\
+\frac{f'(1)(p-1) + O\Big[(p-1)^2\Big]}{p-1} &< 0 \Leftrightarrow \\
 f'(1) - O(1-p) &< 0.

### 2020-10-25 ms/main.tex
format multiline eqs; results overview

@@
 In the following sections, we determine the equilibria of the model, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
-We then analyze the evolution of a modifier of the social association to determine the evolution of social association.
-Finally, we demonstrate the application of the conditions derived in the previous sections to predict the outcomes of stochastic simulations in a spatial model.
+We then analyze the evolution of a modifier of social association.
+Finally, we demonstrate the application of the conditions derived in the previous sections to predict the outcomes of stochastic simulations in a structured population.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{With Population Structure}
+\subsection*{Population Structure}
 

### 2020-10-25 ms/main.tex

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Evolution of social association}
+
+We now analyze the evolution of social association under perfect vertical transmission, $v=1$.
+We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
+\autoref{eq:vert_hori_equilibrium}).
+Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries})
+
+The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$ (\autoref{eq:mean_fitness}), which is increasing in $\tilde{p}^*$. 
+Therefore, to determine the effect of increasing $\alpha$ on the stable population mean fitness, we must analyze its effect on $\tilde{p}^*$, 
+\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
+  \frac{\partial \tilde{p}^*}{\partial \alpha} 
+%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
+%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
+  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
+\end{equation} 
+Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
+\begin{equation}
+c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
+\end{equation} 
+Therefore, the numerator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is positive.
+Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is also positive, and hence the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive.
+Thus, the population mean fitness increases as social association $\alpha$ increases.
+
+We found that if social association increases, the population mean fitness also increases.
+But can an allele that increases social association evolve? 
+To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988} that determines social association, but has no direct effect on fitness.
+We assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
+Suppose that the population evolves to a stable equilibrium when only allele $M$ is present; we check the local stability of this equilibrium to the introduction of allele $m$ at the modifier locus; This is called ``external stability'', see \citet{Altenberg2017}.
+
+We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
+The frequencies of the pheno-genotypes in the next generation are defined by the recursion system 
+\begin{equation} \label{eq:next_gen_p_1}
+  \begin{aligned}
+	% p1
+  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
+  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) \\
+  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A \;,
+\\
+	% p2
+  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
+  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3))\\
+  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B \;, 
+\\
+	% p3
+  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
+  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) \\
+  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A \;, 
+\\
+	% p4
+  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
+  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
+  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
+  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
+  \end{aligned}
+\end{equation}
+%which we can write as 
+%\begin{equation}
+%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
+%\end{equation}
+where $\bar{w} = 1 + (b-c)(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+
+The equilibrium when only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
+\begin{equation} \label{eq:p_tilde_star_alpha_1}
+\tilde{p}^*=
+\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)},
+\end{equation}
+which we get by setting $\alpha=\alpha_1$ in \autoref{eq:vert_hori_equilibrium}.
+Its local stability to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
+The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
+Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, 
+\begin{equation}
+\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{pmatrix}
+	 X &
+	 Y \\
+	 Z &
+	 Q 
+\end{pmatrix} \;.
+\end{equation}
+
+The elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1},
+\begin{equation} \label{eq:partial_derivatives}
+  \begin{aligned}
+%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
+  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
+%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
+  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
+% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
+  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - c) T_B (1 - \tilde{p}^*) + b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) \;,\\
+%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
+  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - T_A \tilde{p}^* + b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* \;.
+  \end{aligned}
+\end{equation}
+
+If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
+These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
+\begin{equation} \label{eq:eigenvalues}
+  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
+\end{equation}
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
+\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
+\begin{aligned}
+ \alpha_2 > 
+ \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
+% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
+% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
+%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
+%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
+\alpha_1 \;,
+\end{aligned}
+\end{equation}
+which gives the following result.
+\\
+
+\begin{result}[Evolution of social association] 
+In a population at a stable coexistence between cooperation and defection, a modifier allele can successfully invade the population if it increases the social association.
+Such an invasion will, in turn, increase the population mean fitness.
+\end{result}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-10-25 ms/main.tex
revised results and discussion

@@
 \begin{abstract}
-We study the cultural evolution of cooperation under vertical, horizontal, and oblique transmission.
+We study the cultural evolution of cooperation under vertical and non-vertical cultural transmission.
 Conditions are found for fixation and coexistence of cooperation and defection. 
-We find that the evolution of cooperation is facilitated by horizontal transmission, especially when there is an association between cooperation and transmission, and that the effect of oblique transmission depends on the bias in horizontal transmission.
-Stable coexistence of cooperation and defection can occur.
-A spatial model is constructed and compared to results from an unstructured model.
+The evolution of cooperation is facilitated by horizontal transmission and by an association between social interactions and horizontal transmission.
+The effect of oblique transmission depends on the horizontal transmission bias.
+A stable coexistence between cooperation and defection can occur.
+When it does, selection favors the evolution of higher association between social interactions and horizontal transmission, which leads to an increased frequency of cooperation and higher population mean fitness.
+The derived conditions are compared to outcomes of stochastic simulations of structured populations.
 Comparisons are drawn with Hamilton's rule and the concepts of relatedness and assortment.
-% population mean fitness?
-% TODO what about oblique?
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% Introduction
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Models
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% Results
@@
 
-In the following sections, we determine the equilibria of the model, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
+In the following sections, we determine the equilibria of the model in \autoref{eq:nextgen_juveniles}, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
 We then analyze the evolution of a modifier of social association.
-Finally, we demonstrate the application of the conditions derived in the previous sections to predict the outcomes of stochastic simulations in a structured population.
-
-\subsection*{Equilibria and Stability}
+Finally, we compare derived conditions to outcomes of stochastic simulations with a structured population.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Evolution of cooperation}
 
@@
 We define $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics,  this simplifies to
+Then, using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, this simplifies to
 \begin{equation} \label{eq:general_case_polynomial}
-  f(\hat{p}) = \bar{w}(\hat{p}'-\hat{p}) =
-  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p},
+\begin{aligned}
+  f(\hat{p}) &= \bar{w}(\hat{p}'-\hat{p}) =
+  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p} \;,
+\end{aligned}
 \end{equation}
@@
 \begin{aligned}
-\beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) , \\
-\beta_2 &= -\beta_1 -\beta_3 ,  \\
-\beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) .
+  \beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \;, \\
+  \beta_2 &= -\beta_1 -\beta_3 \;, \\
+  \beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \;.
 \end{aligned}
@@
 \begin{equation} \label{eq:equal_horizontal_transmission}
-  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big].
+  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big] \;.
 \end{equation}
@@
 \begin{aligned}
-	f'(0) &=	\alpha bvT - cv(1-T), \\
-	f'(1) &=	-\alpha bvT + cv(1-T).
+	f'(0) &=	\alpha bvT - cv(1-T) \;, \\
+	f'(1) &=	-\alpha bvT + cv(1-T) \;.
 \end{aligned}
 \end{equation}
-%Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{corollary:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
+%Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{remark:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
 
@@
   \hat{p}^* =  
-  \frac{\beta_3}{\beta_1}.
+  \frac{\beta_3}{\beta_1} =
+  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
 \end{equation}
@@
    \beta_1 < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) < 0 ,
+   = (1-\alpha v)(c-b)(T_A-T_B) < 0 \;,
  \end{equation}
@@
    \beta_1 > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) > 0,
+   = (1-\alpha v)(c-b)(T_A-T_B) > 0 \;,
  \end{equation}
@@
 
-We define the \emph{cost boundaries}, $\hat\gamma_1$ and $\hat\gamma_2$,
-\begin{equation} \label{eq:cost_boundaries}
-\begin{aligned}
-\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
-\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
-\end{aligned}
-\end{equation}
-and the \emph{vertical transmission threshold}, $\hat v$,
-\begin{equation} \label{eq:v_threshold}
-\hat v = \frac{T_B - T_A}{1-T_A} \,.
+To present this analysis in terms of conditions on the cost of cooperation $c$, we define the cost boundaries, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
+
+\begin{equation} \label{eq:cost_boundaries_v_threshold} 
+\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
+\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}, \quad
+\hat v = \frac{T_B - T_A}{1-T_A} \;.
 \end{equation}
@@
 First, assume $T_A<T_B$.
-$\beta_3<0$ requires $\hat\gamma_1<c$,
-and for $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
+$\beta_3<0$ requires $\gamma_1<c$.
+For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
 Note that the expression in the square brackets is positive if and only if $v > \hat v$.
-Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c$ or $v < \hat v$ and $c < \hat\gamma_2$,
-and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\hat\gamma_2 < c < \hat\gamma_1$, or $v < \hat v$ and $c < \min(\hat\gamma_1, \hat\gamma_2)$.
-For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\hat\gamma_2$ or $v < \hat v$ and $\hat\gamma_2<c$.
-However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\hat\gamma_2$.
-
-Second, when $T_A>T_B$
-$\beta_3>0$ requires $\hat\gamma_1 > c$. 
+Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c$ or $v < \hat v$ and $c < \gamma_2$,
+and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c < \gamma_1$, or $v < \hat v$ and $c < \min(\gamma_1, \gamma_2)$.
+For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\gamma_2$ or $v < \hat v$ and $\gamma_2<c$.
+However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\gamma_2$.
+
+Second, assume $T_A>T_B$.
+$\beta_3>0$ requires $\gamma_1 > c$. 
 For $\beta_1<\beta_3$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] < bv\alpha T_B + (1+b)(T_A-T_B)$.
-Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \hat\gamma_2 $ or $v < \hat v$ and $c > \hat\gamma_2$.
-But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \hat\gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
+Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \gamma_2 $ or $v < \hat v$ and $c > \gamma_2$.
+But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{result}[Equilibria and stability] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ and the vertical transmission threshold $\hat v$ (Eqs.~\ref{eq:cost_boundaries}-\ref{eq:v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_boundaries_v_threshold}) :
 
@@
 \item \emph{Fixation of cooperation}: 
-	if \emph{(i)} $T_A \ge T_B$ and $c < \hat\gamma_1$; or 
-	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \hat\gamma_2$.
+	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or 
+	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \gamma_2$.
 \item \emph{Fixation of defection}: 
-    if \emph{(iii)} $T_A \ge T_B$ and $\hat\gamma_2 < c$; or 
-	if \emph{(iv)} $T_A < T_B$ and $\hat\gamma_1 < c$.
+    if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or 
+	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
 \item \emph{Stable coexistence}: 
-    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_1$; or 
-    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$.
+    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
+    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
 \item \emph{Unstable coexistence}:
-    if \emph{(vii)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
+    if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
 \end{enumerate}
@@
 
-Much of the literature on evolution of cooperation focuses on conditions for  initially rare cooperative phenotype to invade a population of defectors.
-The next remarks deal with such conditions. The first introduces a condition on the cost of cooperation, $c$, and the second on the social association, $\alpha$.
-\\
-
+Much of the literature on evolution of cooperation focuses on conditions for  an initially rare cooperative phenotype to invade a population of defectors.
+The following remarks on such a condition.
+\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{remark}[Condition for cooperation to increase from rarity: cost of cooperation]
-\label{corollary:rarity}
-If the initial frequency of cooperation is very close to zero, $\hat{p}_0 \approx 0$, then its frequency will increase if 
+\label{remark:rarity}
+If the initial frequency of cooperation is very close to zero, then its frequency will increase if the cost of cooperation is low enough,
 \begin{equation} \label{eq:unequal_transmission_from_rarity_general_case}
-c < \hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)} \;.
+c < \gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)} \;.
 \end{equation} 
@@
 
-This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
-In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias $T_A-T_B$.
-
-Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \hat\gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
-Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation.
-However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost boundary, but it increases the cost boundary when it is already above one ($c<1<\hat\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\hat\gamma_1>1/v$.
+This unites the conditions for fixation of cooperation and for stable coexistence, which both lead to instability of the fixation state associated with defection, $\hat{p}=0$.
+
+Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
+Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the boundary ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation.
+However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost boundary, but it increases the cost boundary when it is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
 Therefore, increasing $T_B$ decreases the cost boundary and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
 
-Increasing the vertical transmission $v$ can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \hat\gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
-When $T_A<T_B$ we get $\partial \hat\gamma_1 / \partial v >0$ and therefore, as the vertical transmission increases the cost boundary increases, making it easier for cooperation to evolve from rarity.
-In contrast, when $T_A > T_B$ we get $\partial \hat\gamma_1 / \partial v <0$ and therefore, as the vertical transmission increases the cost boundary decreases making it harder for cooperation to evolve from rarity.
-
+Increasing the vertical transmission rate, $v$, can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
+When $T_A<T_B$ we get $\partial \gamma_1 / \partial v >0$, and therefore as the vertical transmission rate increases, the cost boundary increases, making it easier for cooperation to evolve from rarity.
+In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost boundary decreases, making it harder for cooperation to evolve from rarity.
+
+In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias term, $T_A-T_B$.
 When there is no horizontal transmission bias, $T_A=T_B$, the next remark applies.
@@
 
-\begin{remark}[Symmetric horizontal transmission] 
-\label{corollary:equal_transmission}
-If $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{remark}[Unbiased horizontal transmission] 
+\label{remark:equal_transmission}
+If horizontal transmission is unbiased, $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if the cost is low enough,
 \begin{equation}
 \label{eq:equal_transmission}
-c < b v \cdot \frac{\alpha T}{1-T} \;.
+c < b \cdot \frac{v \alpha T}{1-T} \;.
 \end{equation}
@@
 This condition is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:unequal_transmission_from_rarity_general_case} and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-\autoref{fig:results}a illustrates this condition for $v=1$. Note that the right-hand side equals $\hat\gamma_1$ when $T=T_A=T_B$.
-
-%In Corollary~\autoref{corollary:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
+\autoref{fig:results}a illustrates this condition for $v=1$. Note that the right-hand side equals $\gamma_1$ when $T=T_A=T_B$.
+
+%In Corollary~\autoref{remark:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
 %A more general case can be stated for $0 < v \leq 1$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{remark}[No social association]
-\label{corollary:alpha0}
-Without social association ($\alpha=0$), cooperation can increase from rarity, and go to fixation, if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
+\label{remark:alpha0}
+Without social association ($\alpha=0$), cooperation will increase from rarity if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
 \begin{equation}
@@
 
-\autoref{fig:result2}a illustrates these conditions, which are obtained by setting $\alpha=0$ in Eqs.\ \ref{eq:unequal_transmission_from_rarity_general_case} and \ref{eq:cost_boundaries}.
-Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of social association. The outcome is determined only by  cultural transmission.
-\\
-
+\autoref{fig:result2}a illustrates this condition, which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
+Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of social association, and the outcome is determined only by  cultural transmission.
+\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{remark}[Perfect social association]
-\label{corollary:alpha1}
+\label{remark:alpha1}
 With perfect social association ($\alpha=1$), cooperation will increase from rarity if
@@
 \end{remark}
-This condition is obtained by setting $\alpha=1$ in Eqs.\ \ref{eq:unequal_transmission_from_rarity_general_case} and \ref{eq:cost_boundaries}.
+This condition is obtained by setting $\alpha=1$ in inequality~\ \ref{eq:unequal_transmission_from_rarity_general_case}.
 
@@
 Given the previous two remarks for no association and perfect association ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of social association on the evolution of cooperation.
-Consider the \emph{social association boundaries}, $\hat{a}_1$ and $\hat{a}_2$,
-\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting_general_case}
-  \hat{a}_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
-  \hat{a}_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A} \;.
-\end{aligned}\end{equation}
+Consider the social association boundaries, $a_1$ and $a_2$,
+\begin{equation} \label{eq:boundries_assortative_meeting_general_case}
+  a_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
+  a_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A} \;.
+\end{equation}
 Then the following applies.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{remark}[Condition for cooperation to increase from rarity: social association]
-\label{corollary:intermediate_association_res3}
-Cooperation will increase from rarity if social association is high enough, specifically if $\hat a_2 < \alpha$.
+\label{remark:intermediate_association_res3}
+Cooperation will increase from rarity if social association is high enough, specifically if $a_2 < \alpha$.
 \end{remark}
-\autoref{fig:result3}cd illustrates this condition.
-\autoref{fig:result2}c demonstrates these conditions.
-With horizontal transmission bias for cooperation ($T_A>T_B$), cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
-With horizontal bias favoring defection ($T_A<T_B$), cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
-Without horizontal bias ($T_A=T_B$) fixation of cooperation occurs if social association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
-
-Interestingly, the effect of vertical transmission on this condition depends on the horizontal transmission bias, $\partial \hat a_2 / \partial v = b T_A (T_A-T_B)$. 
-That is, with horizontal bias for cooperation, $T_A>T_B$, the boundary increases with the rate of vertical transmission, impeding the evolution of cooperation.
-In contrast, with horizontal bias for defection, $T_A<T_B$, the boundary decreases with the rate of vertical transmission, facilitating the evolution of cooperation.
-
-These effects of vertical and oblique transmission are demonstrated in \autoref{fig:result3}cd. 
+Figures~\ref{fig:result2}c and \ref{fig:result3}cd illustrate this condition.
+With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
+With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
+Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if social association is high enough, $\frac{c}{b \cdot v} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+
+Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on this condition depends on the horizontal transmission bias.
+That is, with horizontal bias for cooperation, $T_A>T_B$, evolution of cooperation is facilitated by oblique transmission, whereas with horizontal bias for defection, $T_A<T_B$, evolution of cooperation is facilitated by vertical transmission.
+This is demonstrated in \autoref{fig:result3}cd.
+
 The next remarks further inspect the roles of vertical and oblique transmission in the evolution of cooperation.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{remark}[Necessary condition for fixation of cooperation: vertical transmission rate]
-\label{corollary:vhat}
+\label{remark:vhat}
   Fixation of cooperation is possible only if the vertical transmission rate is high enough,
@@
 \end{remark}
-%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \hat\gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
+%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
 This condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
 If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
-In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough~(\autoref{eq:fixation_of_cooperation_vertical_transmission_condition}): in this case oblique transmission can prevent fixation of cooperation (see \autoref{fig:result3}bd).
-
-With only oblique and horizontal transmission, i.e. $v = 0$, Eq.\ \ref{eq:horizontal} becomes $\hat{p}=p$ and Eq.\ \ref{eq:nextgen_adults_slimpify} becomes 
-\begin{equation}  \label{eq:nextgen_parents_oblique_only}
-p' = p^2 (T_B-T_A) + p (1+T_A-T_B) \;,
-\end{equation}
-which gives the following result.\\
-
+In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see \autoref{fig:result3}bd).
+
+Without oblique transmission, the following applies.
+\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{remark}[Condition for cooperation to increase from rarity: vertical and horizontal transmission]
+\label{remark:vert_hori}
+Without oblique transmission ($v=1$) cooperation will increase from rarity if
+\begin{equation} \label{eq:vert_hori}
+c < \frac{b \alpha T_A + (T_A - T_B)}{1-T_B} \;,
+\end{equation} 
+which can also be written as
+\begin{equation} \label{eq:vert_hori_alpha}
+\frac{c (1-T_B)-(T_A-T_B)}{b T_A} < \alpha \;.
+\end{equation}
+\end{remark}
+
+These conditions is obtained by setting $v=1$ in inequalities~\ref{eq:unequal_transmission_from_rarity_general_case} and \ref{eq:boundries_assortative_meeting_general_case}
+
+Without vertical transmission we have the following result.
+\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{remark}[Condition for global fixation of cooperation: oblique and horizontal transmission] \label{result:obli_hori}
@@
 
-That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ are missing from \autoref{eq:nextgen_parents_oblique_only}).
-The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers (see~{\autoref{fig:results}c).
+This condition is found by setting $v = 0$ in \autoref{eq:horizontal}, which becomes $\hat{p}=p$, and then \autoref{eq:nextgen_adults_slimpify} becomes 
+$p' = p^2 (T_B-T_A) + p (1+T_A-T_B)$. 
+That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ do not affect $p'$).
+The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers.
 Note that without bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{remark}[Coexistence of cooperation and defection]
@@
 
-% TODO - revise the next paragraph
-If there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:result2}b.
-When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:coexistence_recursive}a shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
-
-% TODO - consider adding v=1 case?
+See yellow and blue area in \autoref{fig:result2} and \autoref{fig:result3} for cases of stable and unstable coexistence, respectively.
+When unstable coexistence occurs, cooperation will fix if its initial frequency is $p>\tilde{p}^*$, and defection will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+\autoref{fig:coexistence_recursive}a shows the mapping $\tilde p \to \tilde p'$.
 
@@
 We now analyze the evolution of social association under perfect vertical transmission, $v=1$.
-We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
-\autoref{eq:vert_hori_equilibrium}).
-Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries})
-
-The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$ (\autoref{eq:mean_fitness}), which is increasing in $\tilde{p}^*$. 
+We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (\autoref{eq:general_equilibrium}).
+Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries_v_threshold})
+
+The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$, which is increasing in $\tilde{p}^*$. 
 Therefore, to determine the effect of increasing $\alpha$ on the stable population mean fitness, we must analyze its effect on $\tilde{p}^*$, 
@@
 \end{equation}
-which we get by setting $\alpha=\alpha_1$ in \autoref{eq:vert_hori_equilibrium}.
-Its local stability to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+which we get by setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
+The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
 $\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{result}[Evolution of social association] 
+\label{result:evol_social_association}
 In a population at a stable coexistence between cooperation and defection, a modifier allele can successfully invade the population if it increases the social association.
-Such an invasion will, in turn, increase the population mean fitness.
+Such an invasion will, in turn, increase the frequency of cooperator as well as the population mean fitness.
 \end{result}
 
+Let us assume that modifier alleles with increased and decreased social association can appear in the population from time to time.
+Then, this results suggests that social association will continue to (slowly) increase as long as cooperation and defection coexist.
+This coexistence requires $a_2 < \alpha < a_1$ (\autoref{fig:result2}c), and so this process will proceed until $\alpha=a_1$ and cooperation takes over the population.
+%TODO - This process is demonstrated in \autoref{fig:evolution_alpha}.
+\\
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Population Structure}
-
-Social association may also emerge from a population's structure.
+\subsection*{Population structure}
+
+Social association may also emerge from population structure.
 Consider a  population colonizing a 2D grid of size 100-by-100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
@@
 On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
-As before, $T_A$ and $T_B$ are the probability to successfully transmitting phenotypes $A$ and $B$ during horizontal transmission, respectively.
+As before, $T_A$ and $T_B$ are the probability for successful horizontal transmission of phenotypes $A$ and $B$, respectively.
 
@@
 where $n_b$ is the number interactions of that individual with cooperative neighbors, and $n_c$ is the total number of interactions that that individual  had ($n_b \le n_c$).
-Then a new generation is generated, and sites can be settled by offspring of any parent, not just neighbor parents.
+Then, a new generation is generated, and sites can be settled by offspring of any parent, not just neighbor parents.
 Thus, selection is global, rather than local, in accordance with our deterministic model.
 The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness of all potential parents.
-Offspring then have the same phenotype as their parents ($v=1$).
-
-\autoref{fig:spatial} shows that the highest cost of cooperation ($c$) that permits the evolution of cooperation in simulations of the spatial model agrees with the conditions derived in Result~2.
+Offspring then have the same phenotype as their parents (i.e. $v=1$).
+
+The outcomes of stochastic simulations with a structured population are shown in \autoref{fig:spatial}.
+The figure demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for a model without population structure or stochasticity.
 An example for stable coexistence is shown in \autoref{fig:spatial_fluctuations}.
-Simulating a spatial model with local selection (i.e.
-sites can only be settled by offspring of neighbor parents) had only a minor effect on the agreement with Result~2 (\autoref{fig:spatial_local_selection}).
-
-This comparison between the deterministic well-mixed model and the stochastic spatial model demonstrates that the derived conditions can be useful for predicting the dynamics of complex scenarios. 
-Moreover, our spatial model shows how social association ($\alpha$) can emerge from local interactions between individuals in a structured population.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Simulating a structured population with local selection (i.e.
+sites can only be settled by offspring of neighbor parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+
+These comparisons between the deterministic unstructured model and the stochastic structured model show that the derived conditions can be useful for predicting the dynamics of complex scenarios. 
+Moreover, our structured populations demonstrate how social association ($\alpha$) can emerge from local interactions between individuals.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Discussion
@@
 We studied the evolution of cooperation under non-vertical transmission using deterministic discrete-time evolutionary models with fitnesses in the form of payoffs from a prisoner's dilemma game. 
-Under oblique and horizontal cultural transmission, horizontal transmission bias in favor of the cooperative phenotype was found to be necessary and sufficient for evolution of cooperation (Result~\autoref{result:obli_hori}).
-Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist at a stable polymorphism, depending on the relationship between the cost and benefit of cooperation, the horizontal bias, and the association between cooperation and transmission (Results~\autoref{result:vert_hori} and~\autoref{result:vert_obli_hori}).
+Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\autoref{result:vert_obli_hori}).
 Importantly, cooperation can increase from rarity (i.e. invade a population of defectors) if and only if (inequality~\ref{eq:unequal_transmission_from_rarity_general_case}),
 \begin{equation}
-c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;,
-\end{equation}
-that is, if the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
-Remarkably, stable coexistence between cooperation and defection can be maintained if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2}-\ref{fig:result3}).
-
-We find that increasing social association ($\alpha$) increases the opportunity for evolution of cooperation (Corollaries \ref{corollary:intermediate_association} and \ref{corollary:intermediate_association_res3}, Figures~\ref{fig:result2}c and \ref{fig:result3}cd).
-Without social association, the benefit of cooperation cannot facilitate its evolution; cooperation can only succeed under horizontal transmission bias ($T_A>T_B$, Corollary~\ref{corollary:alpha0}). 
-Indeed, horizontal transmission plays a major role in the evolution of cooperation.
-Mostly, increasing the transmission of cooperation ($T_A$) or decreasing the transmission of defection ($T_B$) facilitates the evolution of cooperation (Corollaries~\ref{corollary:rarity} and~\ref{corollary:intermediate_association_res3}, \autoref{fig:result2}).
-However, in specific cases increasing the transmission of defection can be advantageous for cooperation (Corollaries~\ref{corollary:rarity} and~\ref{corollary:intermediate_association_res3}).
-The effect of oblique transmission is more complex (Corollary~\ref{corollary:intermediate_association_res3}). 
-When there is horizontal transmission bias for cooperation ($T_A>T_B$), increasing the rate of oblique transmission ($1-v$) will facilitate the evolution of cooperation (\autoref{fig:result3}ac).
-In contrast, when the bias is for defection ($T_A<T_B$), high rates of vertical transmission ($v$) are advantageous for cooperation, and there must be sufficient rate of vertical transmission ($v>\hat v$, Corollary~\autoref{corollary:vhat}, \autoref{fig:result3}bd) for cooperation to fix in the population.
-
-The conditions derived from our deterministic well-mixed model provide a good approximation to results of simulations of a complex stochastic spatial model  (\autoref{fig:spatial}).
-In this spatial model, individuals can only interact with and transmit to their neighbors.
-This model demonstrates that social association between cooperation and transmission can arise in a structured population in which both types of interactions are local.
+c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;.
+\end{equation}
+That is, if the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
+This condition cannot be formulates in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission.
+
+Remarkably, stable coexistence between cooperation and defection can be stable if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2}-\ref{fig:result3}).
+
+We find that higher social association $\alpha$ leads to evolution of higher frequencies of cooperation (Remark~\autoref{remark:intermediate_association_res3}, Figures~\ref{fig:result2}c and \ref{fig:result3}cd), and that when both cooperation and defection coexist, higher social association is expected to evolve (Result~\ref{result:evol_social_association}).
+Without social association, the benefit of cooperation cannot facilitate its evolution; cooperation can only succeed under horizontal transmission bias ($T_A>T_B$, Remark~\ref{remark:alpha0}).
+
+Indeed, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation (Remarks~\ref{remark:rarity} and~\ref{remark:intermediate_association_res3}, Figures~\ref{fig:result2}-\ref{fig:result3}).
+The effect of oblique transmission is more complex (Corollary~\ref{remark:intermediate_association_res3}). 
+When there is horizontal transmission bias for cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation (\autoref{fig:result3}ac).
+In contrast, when the bias is for defection, $T_A<T_B$, high rates of vertical transmission, $v$, are advantageous for cooperation, and there must be sufficient rate of vertical transmission for cooperation to fix in the population ($v>\hat v$, see Remark~\autoref{remark:vhat}, \autoref{fig:result3}bd).
+
+The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with structured populations, in which individuals can only interact with and transmit to their neighbors (\autoref{fig:spatial}).
+In these structured populations social association arises due to both social interactions and horizontal cultural transmission being local.
 
@@
 
-To understand the role of horizontal transmission, we first discuss the role of \emph{assortment}.
+To understand the role of horizontal transmission, we first review the role of \emph{assortment}.
 \citet{Eshel1982} showed that altruism can evolve when there is enough \emph{assortative meeting}, namely, a tendency for individuals to interact within their phenotypic group.
@@
 This mechanism does not require population structure, repeated interactions, or individual recognition.
-We show that high levels of such social association greatly increase the potential for evolution of cooperation (\autoref{fig:result2}).
-With enough social association ($\alpha > \Big[c(1-T_B) + (T_B-T_A)\Big] / b T_A$), cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$, see Result~\autoref{result:vert_hori}).
+We show that high levels of such social association greatly increase the potential for evolution of cooperation (Figures~\ref{fig:result2}-\ref{fig:result3}).
+With enough social association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$, see Remark~\ref{remark:intermediate_association_res3}).
 
@@
 infection by behavior-determining microbes during interactions effectively generates assortment because a recipient of help may be infected by a behavior-determining microbe and consequently become a helper.
-Cultural horizontal transmission can similarly generate assortment between the cooperative phenotype and the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, which in our model occurs with probability $\alpha$.
-
+Cultural horizontal transmission can similarly generate assortment between the cooperative phenotype and the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
+when there is social association, because the recipient of help may be also the recipient of the cultural trait for cooperation.
 Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
 environment''~\citep{Fletcher2009assortment} is generated not because \emph{the helper is likely to be helped}, but rather because \emph{the helped is likely to become a helper}.
+
 These conclusions highlight the importance of non-vertical cultural transmission in explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % \pagebreak
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Appendices
@@
 
-Let $f(p)=\lambda(p'-p)$, where $\lambda>0$, and we know that $f(0)=0$ and $f(1)=0$ since 0,1 are equilibrium.
-
-If $p>p^*=0$, we want a condition for $p'<p$, or
-$\frac{p'}{p}<1$, or
-$\lambda \frac{p'-p}{p} < 0$, or
-$\frac{f(p)}{p} < 0$.
+Let $f(p)=\lambda \cdot (p'-p)$, where $\lambda>0$, and $0$ and $1$ are equilibria, that is, $f(0)=0$ and $f(1)=0$.
+
+Set $p>p^*=0$.
 Using a linear approximation for $f(p)$ near $0$, we have
-\begin{equation}\begin{aligned}
-p' &< p \Leftrightarrow \\
-\frac{f'(0) \cdot p + O(p^2)}{p} &< 0 \Leftrightarrow \\
-f'(0) + O(p) &< 0.
-\end{aligned}\end{equation}
+\begin{equation}
+p' < p \Leftrightarrow 
+f(p)/p < 0 \Leftrightarrow 
+\frac{f'(0) \cdot p + O(p^2)}{p} < 0 \Leftrightarrow 
+f'(0) + O(p) < 0 \;.
+\end{equation}
 Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any $0<p<\epsilon$, it is guaranteed that $0<p'<p$; that is, $p'$ is closer to zero than $p$.
 
-If $p<p^*=1$, we want a condition for $1-p' < 1-p$, or
-$\frac{1-p'}{1-p}<1$, or
-$\lambda \frac{-(p'-p)}{1-p} < 0$, or
-$-\frac{f(p)}{1-p} < 0$.
+Set $p<p^*=1$
 Using a linear approximation for $f(p)$ near $1$, we have
-\begin{equation}\begin{aligned}
-1-p' &< 1-p  \Leftrightarrow \\
-\frac{f'(1)(p-1) + O\Big[(p-1)^2\Big]}{p-1} &< 0 \Leftrightarrow \\
-f'(1) - O(1-p) &< 0.
-\end{aligned}\end{equation}
+\begin{equation}
+1-p' < 1-p  \Leftrightarrow 
+-\frac{f(p)}{1-p} < 0 \Leftrightarrow 
+\frac{f'(1)(p-1) + O\big((p-1)^2\big)}{p-1} < 0 \Leftrightarrow 
+f'(1) - O(1-p) < 0 \;.
+\end{equation}
 Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Bibliography
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
-(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines, respectively. 
+(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are the solid and dashed lines, respectively. 
 (\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines, respectively.
@@
 	In all cases the vertical transmission rate $v$ is on the x-axis.
-	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $\hat{a}_1$ and $\hat{a}_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
     Horizontal transmission is biased in (\textbf{a,c}) for cooperation, $T_A>T_B$, and in (\textbf{b,d}) for defection, $T_A<T_B$.    
@@
   \textbf{(a)} There is no oblique transmission, $v=1$.
-  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries}).
+  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries_v_threshold}).
   The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.\\
@@
   \caption{
-  \textbf{Evolution of cooperation in a spatial model.}
+  \textbf{Evolution of cooperation in a structured population.}
   The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
@@
   Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
@@
   \caption{
-  \textbf{Evolution of cooperation in a spatial model with local selection.}
+  \textbf{Evolution of cooperation in a structured population with local selection.}
   The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
@@
   Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
@@
    \caption{
-    \textbf{Stable coexistence of both phenotypes in a spatial model.}
-    The frequency of cooperators (green) and defectors (red) in a spatial model. 
+    \textbf{Stable coexistence of both phenotypes in a structured population.}
+    The frequency of cooperators (green) and defectors (red) in a structured finite population.
     Both phenotypes start at 50\% frequency.
-    The figure shows that neither phenotype is fixed throughout the simulation, maintaining a stochastic coexistence.
+    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
     Here, population size is 10,000 (100-by-100 grid), selection operates globally, 

### 2020-10-25 ms/main.tex
refactored analysis to appendices

@@
 
-To determine the equilibria in our model, we analyze the fixed points of \autoref{eq:nextgen_juveniles}.
-We define $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
-Then, using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, this simplifies to
-\begin{equation} \label{eq:general_case_polynomial}
-\begin{aligned}
-  f(\hat{p}) &= \bar{w}(\hat{p}'-\hat{p}) =
-  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p} \;,
-\end{aligned}
-\end{equation}
-where 
-\begin{equation} \label{eq:polynomial_coefficients}
-\begin{aligned}
-  \beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \;, \\
-  \beta_2 &= -\beta_1 -\beta_3 \;, \\
-  \beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \;.
-\end{aligned}
-\end{equation}
-
-If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$. 
-Thus, $f(\hat{p})$ becomes a quadratic polynomial,
-\begin{equation} \label{eq:equal_horizontal_transmission}
-  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big] \;.
-\end{equation}
-Clearly the only two equilibria are the fixations  $\hat{p} =  0$ and $\hat{p} = 1$.
-These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\autoref{sec:appendixA}), where
-$f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big]$, so that
-\begin{equation} \label{eq:derivative_of_phattag-phat}
-\begin{aligned}
-	f'(0) &=	\alpha bvT - cv(1-T) \;, \\
-	f'(1) &=	-\alpha bvT + cv(1-T) \;.
-\end{aligned}
-\end{equation}
-%Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{remark:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
-
-In the general case where $T_A \neq T_B$, the coefficient $\beta_1$ is not necessarily zero, and $f(\hat{p})$ is a cubic polynomial.
-Therefore, three equilibria may exist, two of which are
-$\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
+We determined the equilibria of our model, i.e. the fixed points of \autoref{eq:nextgen_juveniles}, and their local stability.
+The equilibria are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
 \begin{equation} \label{eq:general_equilibrium}
   \hat{p}^* =  
-  \frac{\beta_3}{\beta_1} =
   \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
@@
 
-Note that the sign of the  cubic (Eq.\ \ref{eq:general_case_polynomial}) at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
-If $T_A>T_B$, then 
-\begin{equation} \label{eq:beta1}
-   \beta_1 < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) < 0 \;,
- \end{equation}
-since $c<b$ and $\alpha v < 1$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
-First, if $\beta_3<\beta_1$ then 
-$1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e. between 0 and 1) equilibrium.
-Second, if $\beta_1<\beta_3<0$ then 
-$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$ so that both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
-Third, if $0<\beta_3$ then 
-$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$; that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
-
-Similarly, if $T_A<T_B$, then
-\begin{equation} \label{eq:beta1_rev}
-   \beta_1 > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) > 0 \;,
- \end{equation}
-since $c<b$ and $\alpha v < 1$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
-First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A$ is the only locally stable legitimate equilibrium.
-Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
-
-To present this analysis in terms of conditions on the cost of cooperation $c$, we define the cost boundaries, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
-
+To find conditions on the cost of cooperation, $c$, we define the following cost boundaries, $\gamma_1$ and $\gamma_2$, vertical transmission threshold, $\hat v$,
 \begin{equation} \label{eq:cost_boundaries_v_threshold} 
@@
 
-First, assume $T_A<T_B$.
-$\beta_3<0$ requires $\gamma_1<c$.
-For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
-Note that the expression in the square brackets is positive if and only if $v > \hat v$.
-Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c$ or $v < \hat v$ and $c < \gamma_2$,
-and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c < \gamma_1$, or $v < \hat v$ and $c < \min(\gamma_1, \gamma_2)$.
-For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\gamma_2$ or $v < \hat v$ and $\gamma_2<c$.
-However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\gamma_2$.
-
-Second, assume $T_A>T_B$.
-$\beta_3>0$ requires $\gamma_1 > c$. 
-For $\beta_1<\beta_3$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] < bv\alpha T_B + (1+b)(T_A-T_B)$.
-Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \gamma_2 $ or $v < \hat v$ and $c > \gamma_2$.
-But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
-
-The following result summarizes the possible outcomes of the model (\autoref{eq:nextgen_juveniles}).
+The full analysis is given in Appendix~\ref{sec:appendixB}.
+The following result summarizes the possible outcomes.
 \\
@@
 With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_boundaries_v_threshold}) :
-
-% in beta
-%\begin{enumerate}
-%\item \emph{Fixation of cooperation}: 
-%	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-%	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
-%	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
-%\item \emph{Fixation of the defection}: 
-%	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-%	if \emph{(v)} $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
-%	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
-%\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
-%	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
-%\item \emph{Fixation of either phenotype depending on initial frequency}:
-%	if \emph{(viii)}  $T_A>T_B$ and $\beta_1<\beta_3<0$.
-%\end{enumerate}
 
@@
 We now analyze the evolution of social association under perfect vertical transmission, $v=1$. 
-We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (\autoref{eq:general_equilibrium}).
+We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
 Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries_v_threshold})
 
-The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$, which is increasing in $\tilde{p}^*$. 
-Therefore, to determine the effect of increasing $\alpha$ on the stable population mean fitness, we must analyze its effect on $\tilde{p}^*$, 
-\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
-  \frac{\partial \tilde{p}^*}{\partial \alpha} 
-%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
-%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
-  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
-\end{equation} 
-Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
-\begin{equation}
-c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
-\end{equation} 
-Therefore, the numerator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is positive.
-Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is also positive, and hence the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive.
-Thus, the population mean fitness increases as social association $\alpha$ increases.
-
-We found that if social association increases, the population mean fitness also increases.
+The stable population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$. 
+In turn, $\hat{p}^*$ is also increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
+Therefore, if social association increases, the population mean fitness also increases.
 But can an allele that increases social association evolve? 
 To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988} that determines social association, but has no direct effect on fitness.
-We assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
-Suppose that the population evolves to a stable equilibrium when only allele $M$ is present; we check the local stability of this equilibrium to the introduction of allele $m$ at the modifier locus; This is called ``external stability'', see \citet{Altenberg2017}.
-
-We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
-The frequencies of the pheno-genotypes in the next generation are defined by the recursion system 
-\begin{equation} \label{eq:next_gen_p_1}
-  \begin{aligned}
-	% p1
-  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A \;,
-\\
-	% p2
-  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
-  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3))\\
-  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B \;, 
-\\
-	% p3
-  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) \\
-  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A \;, 
-\\
-	% p4
-  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
-  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
-  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
-  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
-  \end{aligned}
-\end{equation}
-%which we can write as 
-%\begin{equation}
-%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
-%\end{equation}
-where $\bar{w} = 1 + (b-c)(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-
-The equilibrium when only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
-\begin{equation} \label{eq:p_tilde_star_alpha_1}
-\tilde{p}^*=
-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)},
-\end{equation}
-which we get by setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
-The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
-$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, 
-\begin{equation}
-\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{pmatrix}
-	 X &
-	 Y \\
-	 Z &
-	 Q 
-\end{pmatrix} \;.
-\end{equation}
-
-The elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1},
-\begin{equation} \label{eq:partial_derivatives}
-  \begin{aligned}
-%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
-  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
-%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
-  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
-% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
-  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - c) T_B (1 - \tilde{p}^*) + b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) \;,\\
-%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
-  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - T_A \tilde{p}^* + b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* \;.
-  \end{aligned}
-\end{equation}
-
-If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
-These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
-\begin{equation} \label{eq:eigenvalues}
-  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
-\end{equation}
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
-\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
-\begin{aligned}
- \alpha_2 > 
- \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
-% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
-% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
-%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
-%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
-\alpha_1 \;,
-\end{aligned}
-\end{equation}
-which gives the following result.
+Assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
+Suppose that the population evolves to a stable equilibrium when only allele $M$ is present.
+We check the local stability of this equilibrium to the invasion of the modifier allele $m$; this stablity is called ``external stability'', see \citet{Altenberg2017}.
+
+The full analysis is given in Appendix~\ref{sec:appendixD}, and following result summarizes the outcomes of such invasions.
 \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{} \label{sec:appendixA}
+\section{Local stability criterion} \label{sec:appendixA}
 
@@
 Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Equilibria and stability} \label{sec:appendixB}
+
+We define $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
+Then, using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, this simplifies to
+\begin{equation} \label{eq:general_case_polynomial}
+\begin{aligned}
+  f(\hat{p}) &= \bar{w}(\hat{p}'-\hat{p}) =
+  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p} \;,
+\end{aligned}
+\end{equation}
+where 
+\begin{equation} \label{eq:polynomial_coefficients}
+\begin{aligned}
+  \beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \;, \\
+  \beta_2 &= -\beta_1 -\beta_3 \;, \\
+  \beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \;.
+\end{aligned}
+\end{equation}
+
+If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$. 
+Thus, $f(\hat{p})$ becomes a quadratic polynomial,
+\begin{equation} \label{eq:equal_horizontal_transmission}
+  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big] \;.
+\end{equation}
+Clearly the only two equilibria are the fixations  $\hat{p} =  0$ and $\hat{p} = 1$.
+These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\autoref{sec:appendixA}), where
+$f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big]$, so that
+\begin{equation} \label{eq:derivative_of_phattag-phat}
+\begin{aligned}
+	f'(0) &=	\alpha bvT - cv(1-T) \;, \\
+	f'(1) &=	-\alpha bvT + cv(1-T) \;.
+\end{aligned}
+\end{equation}
+%Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{remark:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
+
+In the general case where $T_A \neq T_B$, the coefficient $\beta_1$ is not necessarily zero, and $f(\hat{p})$ is a cubic polynomial.
+Therefore, three equilibria may exist, two of which are
+$\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
+\begin{equation} \label{eq:general_equilibrium_appendix}
+  \hat{p}^* =  
+  \frac{\beta_3}{\beta_1} =
+  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
+\end{equation}
+
+Note that the sign of the  cubic (Eq.\ \ref{eq:general_case_polynomial}) at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
+If $T_A>T_B$, then 
+\begin{equation} \label{eq:beta1}
+   \beta_1 < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   = (1-\alpha v)(c-b)(T_A-T_B) < 0 \;,
+ \end{equation}
+since $c<b$ and $\alpha v < 1$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
+First, if $\beta_3<\beta_1$ then 
+$1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e. between 0 and 1) equilibrium.
+Second, if $\beta_1<\beta_3<0$ then 
+$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$ so that both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
+Third, if $0<\beta_3$ then 
+$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$; that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+
+Similarly, if $T_A<T_B$, then
+\begin{equation} \label{eq:beta1_rev}
+   \beta_1 > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   = (1-\alpha v)(c-b)(T_A-T_B) > 0 \;,
+ \end{equation}
+since $c<b$ and $\alpha v < 1$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
+First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A$ is the only locally stable legitimate equilibrium.
+Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
+Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+
+This analysis can be summarized with the following conditions:
+% in beta
+\begin{enumerate}
+\item \emph{Fixation of cooperation}: 
+	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
+	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
+	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
+\item \emph{Fixation of the defection}: 
+	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
+	if \emph{(v)} $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
+	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
+\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
+	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+\item \emph{Fixation of either phenotype depending on initial frequency}:
+	if \emph{(viii)}  $T_A>T_B$ and $\beta_1<\beta_3<0$.
+\end{enumerate}
+
+We now proceed to use the cost boundaries, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$ (\autoref{eq:cost_boundaries_v_threshold}).
+First, assume $T_A<T_B$.
+$\beta_3<0$ requires $\gamma_1<c$.
+For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
+Note that the expression in the square brackets is positive if and only if $v > \hat v$.
+Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c$ or $v < \hat v$ and $c < \gamma_2$,
+and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c < \gamma_1$, or $v < \hat v$ and $c < \min(\gamma_1, \gamma_2)$.
+For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\gamma_2$ or $v < \hat v$ and $\gamma_2<c$.
+However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\gamma_2$.
+
+Second, assume $T_A>T_B$.
+$\beta_3>0$ requires $\gamma_1 > c$. 
+For $\beta_1<\beta_3$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] < bv\alpha T_B + (1+b)(T_A-T_B)$.
+Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \gamma_2 $ or $v < \hat v$ and $c > \gamma_2$.
+But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
+
+This analysis is summarized in Result~\ref{result:vert_obli_hori}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Effect of social association on mean fitness} \label{sec:appendixC}
+
+To determine the effect of increasing $\alpha$ on the stable population mean fitness, $\bar{w}^*=1+(b-c)\hat{p}^*$, we must analyze its effect on $\hat{p}^*$, 
+\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
+  \frac{\partial \hat{p}^*}{\partial \alpha} 
+%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
+%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
+  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
+\end{equation} 
+Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
+\begin{equation}
+c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
+\end{equation} 
+Therefore, the numerator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is positive.
+Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is also positive, and hence the derivative $\partial \hat{p}^* / \partial \alpha$ is positive.
+Thus, the population mean fitness increases as social association $\alpha$ increases.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{External stability of $\tilde{p}^*$} \label{sec:appendixD}
+
+We assume here that $v=1$, i.e. no oblique transmission, and therefore $\hat{p}=\tilde{p}$.
+We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
+The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
+\begin{equation} \label{eq:next_gen_p_1}
+  \begin{aligned}
+	% p1
+  \bar{w}\tilde{p}_1' = 
+  & \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
+  & \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) + \\
+  & \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) + \\
+  & \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A \;,
+\\
+	% p2
+  \bar{w}\tilde{p}_2' = 
+  & \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) + \\
+  & \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3)) + \\
+  & \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
+  & \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B \;, 
+\\
+	% p3
+  \bar{w}\tilde{p}_3' =
+  & \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
+  & \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) + \\
+  & \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) + \\
+  & \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A \;, 
+\\
+	% p4
+  \bar{w}\tilde{p}_4' =
+  & \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) + \\
+  & \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3)) + \\
+  & \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
+  & \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
+  \end{aligned}
+\end{equation}
+%which we can write as 
+%\begin{equation}
+%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
+%\end{equation}
+where $\bar{w} = 1 + (b-c)(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+
+The equilibrium when only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
+\begin{equation} \label{eq:p_tilde_star_alpha_1}
+\tilde{p}^*=
+\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)},
+\end{equation}
+which we get by setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
+The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
+The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
+Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, 
+\begin{equation}
+\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{pmatrix}
+	 X &
+	 Y \\
+	 Z &
+	 Q 
+\end{pmatrix} \;.
+\end{equation}
+
+The elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1},
+\begin{equation} \label{eq:partial_derivatives}
+  \begin{aligned}
+%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
+  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
+%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
+  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
+% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
+  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - c) T_B (1 - \tilde{p}^*) + b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) \;,\\
+%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
+  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - T_A \tilde{p}^* + b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* \;.
+  \end{aligned}
+\end{equation}
+
+If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
+These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
+\begin{equation} \label{eq:eigenvalues}
+  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
+\end{equation}
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
+\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
+\begin{aligned}
+ \alpha_2 > 
+ \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
+% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
+% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
+%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
+%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
+\alpha_1 \;.
+\end{aligned}
+\end{equation}
 
@@
 $A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
-$0<b<c$.
+$0<c<1$ and $c<b$.
 }
@@
 
+%%% Figure: Spatial model - global selection
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
+    ~
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
+  \caption{
+  \textbf{Evolution of cooperation in a structured population.}
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
+  The population evolves on a 100-by-100 grid.
+  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
+  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
+  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  }
+  \label{fig:spatial}
+\end{figure}
+
+%%% Figure: Spatial model - local selection
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
+    ~
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
+  \caption{
+  \textbf{Evolution of cooperation in a structured population with local selection.}
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
+  The population evolves on a 100-by-100 grid.
+  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
+  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
+  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
+  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  }
+  \label{fig:spatial_local_selection}
+\end{figure}
+
+% Fluctuations in spatial model
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
+   \caption{
+    \textbf{Stable coexistence of both phenotypes in a structured population.}
+    The frequency of cooperators (green) and defectors (red) in a structured finite population.
+    Both phenotypes start at 50\% frequency.
+    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
+    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
+    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
+    }
+    \label{fig:spatial_fluctuations}
+  \end{figure}
+
 %%% Figure: coexistence map
@@
 
-%%% Figure: Spatial model - global selection
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
-    ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
-  \caption{
-  \textbf{Evolution of cooperation in a structured population.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
-  The population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
-  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
-  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
-  }
-  \label{fig:spatial}
-\end{figure}
-
-%%% Figure: Spatial model - local selection
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
-    ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
-  \caption{
-  \textbf{Evolution of cooperation in a structured population with local selection.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
-  The population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
-  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
-  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
-  }
-  \label{fig:spatial_local_selection}
-\end{figure}
-
-% Fluctuations in spatial model
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
-   \caption{
-    \textbf{Stable coexistence of both phenotypes in a structured population.}
-    The frequency of cooperators (green) and defectors (red) in a structured finite population.
-    Both phenotypes start at 50\% frequency.
-    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
-    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
-    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
-    }
-    \label{fig:spatial_fluctuations}
-  \end{figure}
-  %TODO: edit this caption. DC
-
 %%%

### 2020-10-25 ms/main.tex
formatting

@@
 where fitness values are taken from \autoref{table:prisoner_payoff} and \autoref{table:interactions}, and the population mean fitness is
-\begin{equation} \label{eq:mean_fitness}
-\bar{w} =  1 + \hat{p}(b-c).
-\end{equation}
-
+%\begin{equation} \label{eq:mean_fitness}
+$\bar{w} =  1 + \hat{p}(b-c)$.
+%\end{equation}
 \autoref{eq:nextgen_parents} can be simplified to
@@
 %where $\hat{p}=v\tilde{p}+(1-v)p$.
-
 Finally, we find an equation for the frequency of phenotype $A$ among juveniles in the next generation $\hat{p}'$ as a function of the frequency in the current generation.
@@
 & \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A + \\
-& (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B) \;,
+& (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B) \;.
 \end{aligned}
 \end{equation}
-where $\bar{w} = 1 + \hat{p}(b-c)$.
-
 \autoref{table:vars_params} summarizes the model variables and parameters.
@@
 
-\begin{figure}[h]
+\begin{figure}[p]
   \centering       
@@
 (\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are the solid and dashed lines, respectively. 
-(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines, respectively.
+(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
 Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
@@
 %%% Figure: Spatial model - global selection
-\begin{figure}[h]
+\begin{figure}[p]
   \centering
@@
 \end{figure}
+
+% Fluctuations in spatial model
+\begin{figure}[p]
+  \centering
+   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
+   \caption{
+    \textbf{Stable coexistence of both phenotypes in a structured population.}
+    The frequency of cooperators (green) and defectors (red) in a structured finite population.
+    Both phenotypes start at 50\% frequency.
+    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
+    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
+    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
+    }
+    \label{fig:spatial_fluctuations}
+  \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section*{Supplementary Material}
+\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
 
@@
 
-% Fluctuations in spatial model
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
-   \caption{
-    \textbf{Stable coexistence of both phenotypes in a structured population.}
-    The frequency of cooperators (green) and defectors (red) in a structured finite population.
-    Both phenotypes start at 50\% frequency.
-    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
-    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
-    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
-    }
-    \label{fig:spatial_fluctuations}
-  \end{figure}
-
 %%% Figure: coexistence map
-\begin{figure}[h]
+\begin{figure}[p]
   \centering
@@
   When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
-  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.\\
+  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
   \textbf{(a)} There is no oblique transmission, $v=1$.
   The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries_v_threshold}).
-  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.\\
+  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
   \textbf{(b)} Oblique transmission exists. 
@@
 %%% Figure: frequency dynamics
-\begin{figure}[h]
+\begin{figure}[p]
   \centering

### 2020-10-25 ms/main.tex
added zefferman citation

@@
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
-Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance, % TODO cite Zefferman Behav Ecol 2016
-the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
+Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
 

### 2020-10-27 ms/main.tex
Add another sub figure to fig5

@@
   \centering
-   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
+   \includegraphics[scale=0.75]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf}~\\
+   \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
    \caption{
     \textbf{Stable coexistence of both phenotypes in a structured population.}
-    The frequency of cooperators (green) and defectors (red) in a structured finite population.
+    Figure \textbf{(a)} emphasizes the coexistence shown in \autoref{fig:spatial}b in a structured finite population. 
+    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
     Both phenotypes start at 50\% frequency.
@@
     }
+    %TODO: revisit this caption.
     \label{fig:spatial_fluctuations}

### 2020-10-28 ms/main.tex
Fix characteristic polynomial

@@
 If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
-These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
+These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda \frac{(X+Q)}{\bar{w}} + \frac{XQ - YZ}{\bar{w}^2}$; the leading eigenvalue $\lambda_1$ is the largest of them,
 \begin{equation} \label{eq:eigenvalues}
-  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
+  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2\bar{w}} \;.
 \end{equation}

### 2020-10-31 ms/main.tex
sympy + notebook - add more condition to the proof

--- 2020-10-27 ms/main.tex
@@
 If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
-These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
-\begin{equation} \label{eq:eigenvalues}
-  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
-\end{equation}
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
-\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
-\begin{aligned}
- \alpha_2 > 
- \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
-% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
-% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
-%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
-%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
-\alpha_1 \;.
-\end{aligned}
-\end{equation}
-
+These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda \frac{(X+Q)}{\bar{w}} + \frac{XQ - YZ}{\bar{w}^2}$; At $\lambda = 1$ the characteristic polynomial is equal to:
+\begin{equation} \label{eq:characteristic_at_1}
+  1-\frac{X+Q}{\bar{w}} + \frac{XQ-YZ}{\bar{w}^2}.
+\end{equation}
+This polynomial has at least one real root since 
+\begin{equation} \label{eq:delta}
+  \Delta = \frac{(X+Q)^2}{\bar{w}^2}-\frac{4XQ-4YZ}{\bar{w}^2}=\frac{(X-Q)^2+4YZ}{\bar{w}^2} > 0.
+\end{equation}
+Since the characteristic polynomial is second order polynomial with leading positive coefficient, if the value at 1 is greater than zero, we know that both roots can be either greater or smaller than 1.
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that the characteristic polynomial is positive at $\lambda = 1$ if 
+\begin{equation} \label{eq:both_roots_greater_or_smaller_than_1_condition}
+\begin{aligned}
+ \alpha_2 < \alpha_1 \;.
+\end{aligned}
+\end{equation}
+Now we know when all the roots are either smaller or greather than 1. We would like to know when all the roots are smaller than 1.
+All the roots are smaller than 1 when the slope at 1 is positive. 
+Using SymPy we get that the slope is positive when:
+\begin{equation} \label{eq:eigenvalues_smaller_than_1_condition}
+  \begin{aligned}
+   c < &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \\
+   OR \\
+   c > &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \, AND\, c<\frac{-g}{h}
+  \end{aligned}
+  \end{equation}
 \end{appendices}

### 2020-11-07 ms/main.tex
Fix figure S2

@@
     ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
+    \includegraphics[scale=0.56]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf} \\
+    ~
+    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
@@
 % Fluctuations in spatial model
-\begin{figure}[p]
-  \centering
-   \includegraphics[scale=0.75]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf}~\\
-   \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
-   \caption{
-    \textbf{Stable coexistence of both phenotypes in a structured population.}
-    Figure \textbf{(a)} emphasizes the coexistence shown in \autoref{fig:spatial}b in a structured finite population. 
-    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
-    Both phenotypes start at 50\% frequency.
-    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
-    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
-    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
-    }
-    %TODO: revisit this caption.
-    \label{fig:spatial_fluctuations}
-  \end{figure}
+%\begin{figure}[p]
+%  \centering
+%   \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
+%   \caption{
+%    \textbf{Stable coexistence of both phenotypes in a structured population.}
+%    Figure \textbf{(a)} emphasizes the coexistence shown in \autoref{fig:spatial}b in a structured finite population. 
+%    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
+%    Both phenotypes start at 50\% frequency.
+%    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
+%    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
+%    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
+%    }
+%    %TODO: revisit this caption.
+%    \label{fig:spatial_fluctuations}
+%  \end{figure}
 
@@
   \centering
-    \includegraphics[scale=0.45]{coexistence_without_oblique.pdf}~
-    \includegraphics[scale=0.45]{coexistence_with_oblique.pdf}
+    \includegraphics[scale=0.4]{coexistence_without_oblique.eps}
+    \includegraphics[scale=0.4]{coexistence_with_oblique.eps}
   \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
-  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
-  The dashed black line is $\hat{p}'=\hat{p}$.
-  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
-  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
-  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
+  The curves show the diffrence of $\hat{p}'-\hat{p}$ vs $\hat{p}$ where $\hat{p}'$ abd $\hat{p}$ are the frequency of the cooperative phenotype $A$ among juveniles in the next generation and current generations (\autoref{eq:horizontal}).
+  The dashed black line is $\hat{p}'-\hat{p}=0$.
+  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (red circle).
+  When $\hat{p}' - \hat{p} > 0 $,  $\hat{p}$ increases towards $\hat{p}^*$.
+  When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
   \textbf{(a)} There is no oblique transmission, $v=1$.

### 2020-11-07 ms/main.tex
Add figure 5

@@
 
+%%% Figure: invasion
+\begin{figure}[b]
+  \centering
+   \includegraphics[scale=0.4]{Frequency_of_invadors.eps}
+    ~
+    \includegraphics[scale=0.4]{Frequency_of_cooperation_after_invasion.eps}\\ 
+  \caption{
+  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable coexistence of cooperators and defactors with soical association $\alpha_1$. 
+  The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
+  \textbf{(a)} describes the frequency of the invadors. 
+  \textbf{(b)} describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency $\hat{p}_2^*$ which described by the black dashed line. 
+  $\hat{p}_2^*$ is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
+  In this case $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
+  }
+  \label{fig:invasion}
+\end{figure}
+
 % Fluctuations in spatial model

### 2020-11-07 ms/main.tex
Add yoav work in App. D

@@
 The figure demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for a model without population structure or stochasticity.
-An example for stable coexistence is shown in \autoref{fig:spatial_fluctuations}.
+An example for stable coexistence is shown in \autoref{fig:spatial}c.
 Simulating a structured population with local selection (i.e.
@@
 We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
-The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
+The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, where $x=\tilde{p}_1+\tilde{p}_3$ is the cooperator frequency, 
 \begin{equation} \label{eq:next_gen_p_1}
@@
   \bar{w}\tilde{p}_1' = 
-  & \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
-  & \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) + \\
-  & \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) + \\
-  & \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A \;,
+  & \tilde{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) + \\
+  & \tilde{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) + \\
+  & \tilde{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) + \\
+  & \tilde{p}_2(1-x)x(1-\alpha_1)T_A \;,
 \\
@@
   \bar{w}\tilde{p}_2' = 
-  & \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) + \\
-  & \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3)) + \\
-  & \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
-  & \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B \;, 
+  & \tilde{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \\
+  & \tilde{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) + \\
+  & \tilde{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) + \\
+& \tilde{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;, 
 \\
@@
   \bar{w}\tilde{p}_3' =
-  & \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
-  & \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) + \\
-  & \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) + \\
-  & \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A \;, 
+  & \tilde{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) + \\
+  & \tilde{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) + \\
+  & \tilde{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) + \\
+  & \tilde{p}_4(1-x) x (1-\alpha_2)T_A \;, 
 \\
@@
   \bar{w}\tilde{p}_4' =
-  & \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) + \\
-  & \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3)) + \\
-  & \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) + \\
-  & \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
+  & \tilde{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B + \\
+  & \tilde{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) + \\
+  & \tilde{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) + \\
+  & \tilde{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \;,
   \end{aligned}
@@
 %\end{equation}
-where $\bar{w} = 1 + (b-c)(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+where $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
 
@@
 \begin{equation}
-\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{pmatrix}
+\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{bmatrix}
 	 X &
@@
 	 Q 
-\end{pmatrix} \;.
+\end{bmatrix} \;.
 \end{equation}
@@
 %  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
-  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
+  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
+  b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
 %  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
-  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
+  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
+  b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
 % Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
-  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - c) T_B (1 - \tilde{p}^*) + b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) \;,\\
+  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
+  b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) + (1 - c) T_B (1 - \tilde{p}^*) \;,\\
 %  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
-  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - T_A \tilde{p}^* + b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* \;.
+  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
+  b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* + 1 - T_A \tilde{p}^* \;.
+  \end{aligned}
+\end{equation}
+
+Reorganizing these equations, we get,
+\begin{equation} 
+  \begin{aligned}
+  	&\bar{w}^* L^*_{ex} = \\
+	&\begin{bmatrix}
+		(1+b \tilde{p}^* -c)(1-T_B(1-\tilde{p}^*)) + b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) & 
+		(1+b \tilde{p}^*) T_A \tilde{p}^* + b \tilde{p}^* \alpha_2 T_A(1-\tilde{p}^*) \\
+		(1+b \tilde{p}^* - c) T_B(1-\tilde{p}^*) - b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) &
+		(1+b \tilde{p}^*) (1-T_A \tilde{p}^*) - b \tilde{p}^* \alpha_2 T_A (1-\tilde{p}^*) \\
+  	\end{bmatrix} \;,
+  \end{aligned}
+\end{equation}
+which can be rearranges as
+\begin{equation} 
+  \begin{aligned}
+  	\bar{w}^* L^*_{ex} = 
+	\Big[
+	\ci 
+	-\vec{T}	
+	\cdot
+	\vec{P}
+	\Big] 
+	\cdot
+	\begin{bmatrix}
+	1+b\tilde{p}^*-c & 0 \\ 0 & 1+b\tilde{p}^*
+	\end{bmatrix}
+	+ 
+	\alpha_2 \cdot b \cdot \tilde{p}^* (1-\tilde{p}^*)
+	\cdot \vec{T} \;,
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} 
+\begin{aligned}
+\vec{T} &= \begin{bmatrix}
+	T_B & T_A \\ -T_B & -T_A
+\end{bmatrix} \;,
+\vec{P} &= \begin{bmatrix}
+	1-\tilde{p}^* & 0 \\ 0 & -\tilde{p}^*
+\end{bmatrix} \;.
 \end{aligned}

### 2020-11-08 ms/main.tex
revise app D

@@
 We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
-The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, where $x=\tilde{p}_1+\tilde{p}_3$ is the cooperator frequency, 
+The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
 \begin{equation} \label{eq:next_gen_p_1}
@@
 %\end{equation}
-where $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+where $x=\tilde{p}_1+\tilde{p}_3$ is the cooperator frequency, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
 
@@
 \begin{equation}
-\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{bmatrix}
+\begin{aligned}
+&\mathbf{L}^*_{ex} = 
+ \frac{1}{\bar{w}^*} \begin{bmatrix}
 	 X &
@@
 	 Q 
-\end{bmatrix} \;.
-\end{equation}
-
-The elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1},
-\begin{equation} \label{eq:partial_derivatives}
-  \begin{aligned}
-%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
-  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
-  b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
-%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
-  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
-  b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
-% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
-  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
-  b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) + (1 - c) T_B (1 - \tilde{p}^*) \;,\\
-%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
-  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
-  b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* + 1 - T_A \tilde{p}^* \;.
-  \end{aligned}
-\end{equation}
-
-Reorganizing these equations, we get,
-\begin{equation} 
-  \begin{aligned}
-  	&\bar{w}^* L^*_{ex} = \\
-	&\begin{bmatrix}
+\end{bmatrix} = \\
+& \frac{1}{\bar{w}^*} \begin{bmatrix}
+\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
+\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
+\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
+\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) 
+\end{bmatrix} = \\
+& \frac{1}{\bar{w}^*} \begin{bmatrix}
 		(1+b \tilde{p}^* -c)(1-T_B(1-\tilde{p}^*)) + b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) & 
@@
 \end{equation}
-which can be rearranges as
-\begin{equation} 
-  \begin{aligned}
-  	\bar{w}^* L^*_{ex} = 
-	\Big[
-	\ci 
-	-\vec{T}	
-	\cdot
-	\vec{P}
-	\Big] 
-	\cdot
-	\begin{bmatrix}
-	1+b\tilde{p}^*-c & 0 \\ 0 & 1+b\tilde{p}^*
-	\end{bmatrix}
-	+ 
-	\alpha_2 \cdot b \cdot \tilde{p}^* (1-\tilde{p}^*)
-	\cdot \vec{T} \;,
-  \end{aligned}
-\end{equation}
-where
-\begin{equation} 
-\begin{aligned}
-\vec{T} &= \begin{bmatrix}
-	T_B & T_A \\ -T_B & -T_A
-\end{bmatrix} \;,
-\vec{P} &= \begin{bmatrix}
-	1-\tilde{p}^* & 0 \\ 0 & -\tilde{p}^*
-\end{bmatrix} \;.
-\end{aligned}
-\end{equation}
-
-If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
-These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda \frac{(X+Q)}{\bar{w}} + \frac{XQ - YZ}{\bar{w}^2}$; At $\lambda = 1$ the characteristic polynomial is equal to:
-\begin{equation} \label{eq:characteristic_at_1}
-  1-\frac{X+Q}{\bar{w}} + \frac{XQ-YZ}{\bar{w}^2}.
-\end{equation}
-This polynomial has at least one real root since 
-\begin{equation} \label{eq:delta}
-  \Delta = \frac{(X+Q)^2}{\bar{w}^2}-\frac{4XQ-4YZ}{\bar{w}^2}=\frac{(X-Q)^2+4YZ}{\bar{w}^2} > 0.
-\end{equation}
-Since the characteristic polynomial is second order polynomial with leading positive coefficient, if the value at 1 is greater than zero, we know that both roots can be either greater or smaller than 1.
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that the characteristic polynomial is positive at $\lambda = 1$ if 
-\begin{equation} \label{eq:both_roots_greater_or_smaller_than_1_condition}
-\begin{aligned}
- \alpha_2 < \alpha_1 \;.
-\end{aligned}
-\end{equation}
-Now we know when all the roots are either smaller or greather than 1. We would like to know when all the roots are smaller than 1.
-All the roots are smaller than 1 when the slope at 1 is positive. 
-Using SymPy we get that the slope is positive when:
-\begin{equation} \label{eq:eigenvalues_smaller_than_1_condition}
-  \begin{aligned}
-   c < &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \\
-   OR \\
-   c > &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \, AND\, c<\frac{-g}{h}
-  \end{aligned}
-  \end{equation}
+
+where the elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1}.
+%\begin{equation} \label{eq:partial_derivatives}
+%  \begin{aligned}
+%%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
+%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
+%  b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
+%%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
+%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
+%  b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
+%% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
+%  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
+%  b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) + (1 - c) T_B (1 - \tilde{p}^*) \;,\\
+%%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
+%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
+%  b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* + 1 - T_A \tilde{p}^* \;.
+%  \end{aligned}
+%\end{equation}
+
+Note that $\mathbf{L}^*_{ex}$ is positive, and due to the Perron-Frobenius theorem, its leading eigenvalue is real and positive.
+If the leading eigenvalue is less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
+The eigenvalues of $\mathbf{L}^*_{ex}$ are the roots of the characteristic polynomial 
+\begin{equation}\label{char_poly}
+R(\lambda) = 
+\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;.
+\end{equation}
+%At $\lambda = 1$ the characteristic polynomial is equal to:
+%\begin{equation} \label{eq:characteristic_at_1}
+%  1-\frac{X+Q}{\bar{w}} + \frac{XQ-YZ}{\bar{w}^2}.
+%\end{equation}
+%Because the discriminant of $R(\lambda)$ is positive, 
+%\begin{equation} \label{eq:delta}
+%  \Delta = 
+%  %\frac{(X+Q)^2}{\bar{w}^2}-\frac{4XQ-4YZ}{\bar{w}^2}=
+%  \frac{(X-Q)^2+4YZ}{\bar{w}^2} > 0 \;,
+%\end{equation}
+%it has two real roots.
+
+The characteristic polynomial $R(\lambda)$ is a quadratic with a positive leading coefficient. Therefore, $R(\infty)=R(-\infty)>0$.
+Hence, the leading eigenvalue is greater than one, implying external stability, if and only if $R(1)>0$ and $R'(1)>0$.
+Thus, a sufficient condition for instability is $R(1)<0$.
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $R(1)<0$ if and only if $\alpha_2 < \alpha_1$.
+That is, if the social association $\alpha_2$ of the invading modifier allele $m$ is less than $\alpha_1$ of the resident $M$, then invasion will be successful.
+
+Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
+
+%Now we know when all the roots are either smaller or greather than 1. We would like to know when all the roots are smaller than 1.
+%All the roots are smaller than 1 when the slope at 1 is positive. 
+%Using SymPy we get that the slope is positive when:
+%\begin{equation} \label{eq:eigenvalues_smaller_than_1_condition}
+%  \begin{aligned}
+%   c < &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \\
+%   OR \\
+%   c > &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \, AND\, c<\frac{-g}{h}
+%  \end{aligned}
+%\end{equation}
+
 \end{appendices}

### 2020-11-08 ms/main.tex
small change
Fix figure 5

@@
     ~
-    \includegraphics[scale=0.56]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf} \\
+    \includegraphics[scale=0.45]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_B}.pdf} \\
     ~
@@
   \centering
-   \includegraphics[scale=0.4]{Frequency_of_invadors.eps}
-    ~
-    \includegraphics[scale=0.4]{Frequency_of_cooperation_after_invasion.eps}\\ 
+   \includegraphics[scale=0.5]{Frequency_of_invadors.eps}
   \caption{
@@
   The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
-  \textbf{(a)} describes the frequency of the invadors. 
-  \textbf{(b)} describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency $\hat{p}_2^*$ which described by the black dashed line. 
-  $\hat{p}_2^*$ is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
+  The blue curve describes the frequency of the invadors, starting from initial frequency of 1\%.
+  The orange curve describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency which is described by the black dashed line. 
+  The frequency of cooperators after the fixation of the invadors is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
   In this case $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.

### 2020-11-10 ms/main.tex
fixed result 2 - reduction principle - and its proof in app D

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}[Evolution of social association] 
+\begin{result}[Reduction principle for social association] 
 \label{result:evol_social_association}
-In a population at a stable coexistence between cooperation and defection, a modifier allele can successfully invade the population if it increases the social association.
-Such an invasion will, in turn, increase the frequency of cooperator as well as the population mean fitness.
+Under perfect vertical transmission ($v=1$), in a population at a stable coexistence between cooperation and defection, a modifier allele can successfully invade the population if it decreases the social association $\alpha$.
 \end{result}
 
-Let us assume that modifier alleles with increased and decreased social association can appear in the population from time to time.
-Then, this results suggests that social association will continue to (slowly) increase as long as cooperation and defection coexist.
-This coexistence requires $a_2 < \alpha < a_1$ (\autoref{fig:result2}c), and so this process will proceed until $\alpha=a_1$ and cooperation takes over the population.
-%TODO - This process is demonstrated in \autoref{fig:evolution_alpha}.
+Note that this reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
+Furthermore, if we assume that modifier alleles with decreased social association appear and invade the population from time to time, then, social association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
+This evolution will proceed as long as stable polymorphism occurs, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}
+, \autoref{fig:result2}c). 
+Thus, we can expect social association to eventually drop to $a_2$, the frequency of cooperation to drop to zero, and the population mean fitness to drop to one.
 \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{External stability of $\tilde{p}^*$} \label{sec:appendixD}
+\section{Reduction principle} \label{sec:appendixD}
 
@@
 %\end{equation}
-where $x=\tilde{p}_1+\tilde{p}_3$ is the cooperator frequency, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
+where $x=\tilde{p}_1+\tilde{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
 
@@
 which we get by setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
+When $v=1$, this equilibrium is polymorphic ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\autoref{result:vert_obli_hori}).
+
 The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
 $\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, 
-\begin{equation}
+The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1} as
+\begin{equation} \label{eq:external_stability_matrix}
 \begin{aligned}
@@
 	 Q 
-\end{bmatrix} = \\
-& \frac{1}{\bar{w}^*} \begin{bmatrix}
+\end{bmatrix} = 
+\frac{1}{\bar{w}^*} \begin{bmatrix}
 \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
@@
 		(1+b \tilde{p}^*) (1-T_A \tilde{p}^*) - b \tilde{p}^* \alpha_2 T_A (1-\tilde{p}^*) \\
-  	\end{bmatrix} \;,
-\end{aligned}
-\end{equation}
-
-where the elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1}.
+  	\end{bmatrix} \;.
+\end{aligned}
+\end{equation}
+
 %\begin{equation} \label{eq:partial_derivatives}
@@
 
-Note that $\mathbf{L}^*_{ex}$ is positive, and due to the Perron-Frobenius theorem, its leading eigenvalue is real and positive.
-If the leading eigenvalue is less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
-The eigenvalues of $\mathbf{L}^*_{ex}$ are the roots of the characteristic polynomial 
+Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$.
+This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\mathbf{L}^*_{ex}$ is real and positive.
+Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
+The eigenvalues of $\mathbf{L}^*_{ex}$ are the roots of the characteristic polynomial, 
 \begin{equation}\label{char_poly}
 R(\lambda) = 
-\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;.
-\end{equation}
+\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;,
+\end{equation}
+where $X$, $Y$, $Z$, and $Q$ are defined in \autoref{eq:external_stability_matrix}.
 %At $\lambda = 1$ the characteristic polynomial is equal to:
@@
 %it has two real roots.
-
-The characteristic polynomial $R(\lambda)$ is a quadratic with a positive leading coefficient. Therefore, $R(\infty)=R(-\infty)>0$.
-Hence, the leading eigenvalue is greater than one, implying external stability, if and only if $R(1)>0$ and $R'(1)>0$.
-Thus, a sufficient condition for instability is $R(1)<0$.
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $R(1)<0$ if and only if $\alpha_2 < \alpha_1$.
-That is, if the social association $\alpha_2$ of the invading modifier allele $m$ is less than $\alpha_1$ of the resident $M$, then invasion will be successful.
+The characteristic polynomial $R(\lambda)$ is a quadratic with a positive leading coefficient.
+Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
+Thus, a sufficient condition for external instability of $\vec{\tilde{p}^*}$ is
+\begin{equation} \label{eq:R1_negative}
+\begin{aligned}
+R(1) < 0 \Leftrightarrow 
+1 - \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} < 0 \Leftrightarrow 
+\bar{w^*}^2 - \bar{w^*} (X+Q) + XQ - YZ < 0 \;.
+\end{aligned}
+\end{equation}
+Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that inequality~\ref{eq:R1_negative} is true if and only if
+\begin{equation} \label{eq:alpha2_alpha1_intermediate}
+\begin{aligned}
+\alpha_2 \big(b T_{A} + (T_A-T_B) - c(1-T_B)\big) <
+\alpha_1 \big(b T_{A} + (T_A-T_B) - c(1-T_B)\big) \;.
+\end{aligned}
+\end{equation}
+We assumed $c<\gamma_1$, that is,
+\begin{equation} \label{eq:c_gamma1_utility}
+\begin{aligned}
+c < \gamma_1 = \frac{b \alpha_1 T_A + (T_A-T_B)}{1-T_B} \Leftrightarrow \\
+%c(1-T_B) < b \alpha_1 T_A + (T_A-T_B) \Leftrightarrow \\
+0 < b \alpha_1 T_A + (T_A-T_B) - c(1-T_B) \Rightarrow \\
+0 < b T_A + (T_A-T_B) - c(1-T_B) \;,
+\end{aligned}
+\end{equation}
+since $0 \le \alpha_1 \le 1$.
+Therefore, combining inequalities \ref{eq:R1_negative}, \ref{eq:alpha2_alpha1_intermediate}, and \ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_2 < \alpha_1$.
+This is a sufficient condition for external instability, so, if the social association $\alpha_2$ of the invading modifier allele $m$ is less than $\alpha_1$ of the resident $M$, then invasion will be successful.
 

### 2020-11-10 ms/main.tex
Fix figure 4

@@
   \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
+   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
     ~
-    \includegraphics[scale=0.45]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_B}.pdf} \\
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} \\
     ~
-    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
+    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
   \caption{
   \textbf{Evolution of cooperation in a structured population.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
+  Figures \textbf{(a)} and \textbf{(b)} describes the expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel \textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of the right panel \textbf{(b)}.
   The population evolves on a 100-by-100 grid.
@@
   The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
+  Figure \textbf{(b)} emphasizes an area in which neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence. 
+  Figure \textbf{(c)} describes the frequency of cooperators and defactors over time
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
@@
   \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
   }
@@
 \end{figure}
+%TODO: could you revisit figure 4 caption ? I didn't know how to describe the x sign in figure b. DC
 

### 2020-11-10 ms/main.tex
Add mean fitness graph

@@
   \centering
-   \includegraphics[scale=0.5]{Frequency_of_invadors.eps}
+   \includegraphics[scale=0.5]{Frequency_of_invadors.eps}~
+   \includegraphics[scale=0.5]{mean_fitness_of_invadors.eps}
   \caption{
@@
   The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
-  The blue curve describes the frequency of the invadors, starting from initial frequency of 1\%.
+  \textbf{(a)} The blue curve describes the frequency of the invadors, starting from initial frequency of 1\%.
   The orange curve describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency which is described by the black dashed line. 
-  The frequency of cooperators after the fixation of the invadors is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
-  In this case $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
+  The frequency of cooperators after the fixation of the invadors is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.\\
+  \textbf{(b)} describes the mean fitness as a function of time (generations). 
+  As the frequency of the invadors increases the mean fitness decreases. \\
+  In both panels $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
   }
@@
 \end{figure}
+%TDODO: revisit this caption
 

### 2020-11-11 ms/main.tex
formatting

@@
 But can an allele that increases social association evolve?
+
 To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988} that determines social association, but has no direct effect on fitness.
-Assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
+We assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
 Suppose that the population evolves to a stable equilibrium when only allele $M$ is present.
 We check the local stability of this equilibrium to the invasion of the modifier allele $m$; this stablity is called ``external stability'', see \citet{Altenberg2017}.
-
-The full analysis is given in Appendix~\ref{sec:appendixD}, and following result summarizes the outcomes of such invasions.
+The full analysis is given in Appendix~\ref{sec:appendixD}, and the following result summarizes the outcomes of such invasions.
 \\
@@
 Note that this reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we assume that modifier alleles with decreased social association appear and invade the population from time to time, then, social association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
-This evolution will proceed as long as stable polymorphism occurs, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}
-, \autoref{fig:result2}c). 
+Furthermore, if we assume that modifier alleles with decreased social association appear and invade the population from time to time, then, the social association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
+This evolution will proceed as long as stable polymorphism occurs, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:result2}c).
 Thus, we can expect social association to eventually drop to $a_2$, the frequency of cooperation to drop to zero, and the population mean fitness to drop to one.
-\\
 

### 2020-11-11 ms/main.tex
MWF changes

@@
 We study the cultural evolution of cooperation under vertical and non-vertical cultural transmission.
-Conditions are found for fixation and coexistence of cooperation and defection. 
+Conditions are found for fixation and polymorphism of cooperation and defection. 
 The evolution of cooperation is facilitated by horizontal transmission and by an association between social interactions and horizontal transmission.
 The effect of oblique transmission depends on the horizontal transmission bias.
-A stable coexistence between cooperation and defection can occur.
+Stable polymorphism of cooperation and defection can occur.
 When it does, selection favors the evolution of higher association between social interactions and horizontal transmission, which leads to an increased frequency of cooperation and higher population mean fitness.
@@
 where $b$ and $c$ are the benefit and cost of cooperation. 
-Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness coefficient $r$ in inequality~\ref{eq:hamilton_rule}.
+%Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness coefficient $r$ in inequality~\ref{eq:hamilton_rule}.
 
@@
 \end{equation}
-where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{Inequality~\ref{eq:fletcher2009} generalizes inequality~\ref{eq:hamilton_rule} and inequality~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
-See \citet{Bijma2010assortment} for treatment of non-public-goods games.
+where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{Inequality~\ref{eq:fletcher2009} generalizes inequalities~\ref{eq:hamilton_rule} and~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
+\citet{Bijma2010assortment} gave a result related to inequality~\ref{eq:fletcher2009} for other types of games.
 
 In this paper we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
-\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission.
-They demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
+\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
 \begin{equation} \label{eq:feldman1985}
@@
 Here, we study cultural-evolution models of cooperation that include both vertical and non-vertical transmission. 
-We investigate these models using mathematical analysis and simulations.  
+%We investigate these models using mathematical analysis and simulations.  
 In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
@@
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
-Following~\citet{ram2018evolution}, given that the parent phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
+Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
 
@@
 However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
-The probability for successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).
+The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).
 
@@
 %where $\hat{p}=v\tilde{p}+(1-v)p$.
-Finally, we find an equation for the frequency of phenotype $A$ among juveniles in the next generation $\hat{p}'$ as a function of the frequency in the current generation.
-Starting from \autoref{eq:horizontal}, we substitute \autoref{eq:nextgen_adults_slimpify} for $p'$ and  \autoref{eq:nextgen_parents_simplified} for $\tilde{p}'$.
-We therefore have
+Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute \autoref{eq:nextgen_adults_slimpify} for $p'$ and \autoref{eq:nextgen_parents_simplified} for $\tilde{p}'$ and obtain
 \begin{equation} \label{eq:nextgen_juveniles}
@@
 \end{equation}
-\autoref{table:vars_params} summarizes the model variables and parameters.
+\autoref{table:vars_params} lists the model variables and parameters.
 
@@
 
-We determined the equilibria of our model, i.e. the fixed points of \autoref{eq:nextgen_juveniles}, and their local stability.
-The equilibria are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
+The equilibria of our model, i.e. the fixed points of \autoref{eq:nextgen_juveniles}, are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
 \begin{equation} \label{eq:general_equilibrium}
@@
 
-To find conditions on the cost of cooperation, $c$, we define the following cost boundaries, $\gamma_1$ and $\gamma_2$, vertical transmission threshold, $\hat v$,
-\begin{equation} \label{eq:cost_boundaries_v_threshold} 
+To find conditions on the cost of cooperation, $c$, define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
+\begin{equation} \label{eq:cost_thresholds_v_threshold} 
 \gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
@@
 \begin{result}[Equilibria and stability] \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_boundaries_v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
 
@@
 	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
-\item \emph{Stable coexistence}: 
+\item \emph{Stable polymorphism}: 
     if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
     if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
-\item \emph{Unstable coexistence}:
+\item \emph{Unstable polymorphism}:
     if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
@@
 \end{result}
-These conditions are illustrated in \autoref{fig:result3}ab.
+These conditions are illustrated in \autoref{fig:result3}a and \autoref{fig:result3}b.
 
 Much of the literature on evolution of cooperation focuses on conditions for  an initially rare cooperative phenotype to invade a population of defectors.
-The following remarks on such a condition.
+The following remarks address this condition.
 \\
@@
 
-This unites the conditions for fixation of cooperation and for stable coexistence, which both lead to instability of the fixation state associated with defection, $\hat{p}=0$.
-
-Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
-Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the boundary ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation.
-However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost boundary, but it increases the cost boundary when it is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
-Therefore, increasing $T_B$ decreases the cost boundary and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
-
-Increasing the vertical transmission rate, $v$, can either increase or decrease the boundary, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
-When $T_A<T_B$ we get $\partial \gamma_1 / \partial v >0$, and therefore as the vertical transmission rate increases, the cost boundary increases, making it easier for cooperation to evolve from rarity.
-In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost boundary decreases, making it harder for cooperation to evolve from rarity.
-
-In general, this condition cannot be formulated in the form of Hamilton's rule due to the horizontal transmission bias term, $T_A-T_B$.
+This unites the conditions for fixation of cooperation and for stable polymorphism, both of which lead to instability of the fixation state associated with defection, $\hat{p}=0$.
+
+Importantly, increasing social association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
+Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation.
+However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost threshold, but it increases the cost threshold when it is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
+Therefore, increasing $T_B$ decreases the cost threshold and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
+
+Increasing the vertical transmission rate, $v$, can either increase or decrease the cost threshold, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
+When $T_A<T_B$ we get $\partial \gamma_1 / \partial v >0$, and therefore as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to evolve from rarity.
+In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to evolve from rarity.
+
+In general, this condition cannot be formulated in the form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
 When there is no horizontal transmission bias, $T_A=T_B$, the next remark applies.
@@
 \end{remark}
-This condition is obtained by setting $T=T_A=T_B$ in inequality \ref{eq:unequal_transmission_from_rarity_general_case} and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+This condition is obtained by setting $T=T_A=T_B$ in inequality (\ref{eq:unequal_transmission_from_rarity_general_case}) and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~(\ref{eq:fletcher2009}), where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
 \autoref{fig:results}a illustrates this condition for $v=1$. Note that the right-hand side equals $\gamma_1$ when $T=T_A=T_B$.
 
-%In Corollary~\autoref{remark:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
+%In Corollary~\ref{remark:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
 %A more general case can be stated for $0 < v \leq 1$.
@@
 \label{remark:alpha0}
-Without social association ($\alpha=0$), cooperation will increase from rarity if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
+Without social association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
 \begin{equation}
@@
 
-\autoref{fig:result2}a illustrates this condition, which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
+\autoref{fig:result2}a illustrates this condition, which is obtained by setting $\alpha=0$ in inequality~(\ref{eq:unequal_transmission_from_rarity_general_case}).
 Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of social association, and the outcome is determined only by  cultural transmission.
@@
 \label{remark:alpha1}
-With perfect social association ($\alpha=1$), cooperation will increase from rarity if
+With perfect social association ($\alpha=1$), cooperation will increase when it is rare if
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 \end{remark}
-This condition is obtained by setting $\alpha=1$ in inequality~\ \ref{eq:unequal_transmission_from_rarity_general_case}.
-
-Moreover, without oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality \ref{eq:vert_hori_alpha1} applies.
-This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}, and therefore when $v=1$, this remark is equivalent to their eq.~1.
-
-Given the previous two remarks for no association and perfect association ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of social association on the evolution of cooperation.
-Consider the social association boundaries, $a_1$ and $a_2$,
+This condition is obtained by setting $\alpha=1$ in inequality~\ (\ref{eq:unequal_transmission_from_rarity_general_case}).
+% TODO fig 2b?
+
+In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality \ref{eq:vert_hori_alpha1} applies.
+This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}, and therefore when $v=1$, this remark is equivalent to their eq.~(1).
+
+In light of Remarks~\ref{remark:alpha0} and \ref{remark:alpha1}, it is interesting to examine the general effect of social association on the evolution of cooperation.
+Define the social association thresholds, $a_1$ and $a_2$, as 
 \begin{equation} \label{eq:boundries_assortative_meeting_general_case}
@@
 \label{remark:intermediate_association_res3}
-Cooperation will increase from rarity if social association is high enough, specifically if $a_2 < \alpha$.
+Cooperation will increase when rare if social association is high enough, specifically if $a_2 < \alpha$.
 \end{remark}
-Figures~\ref{fig:result2}c and \ref{fig:result3}cd illustrate this condition.
+Figures~\ref{fig:result2}c, \ref{fig:result3}c, and \ref{fig:result3}d illustrate this condition.
 With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
-With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable coexistence with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
+With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
 Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if social association is high enough, $\frac{c}{b \cdot v} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
 
-Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on this condition depends on the horizontal transmission bias.
+Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on $a_1$ and $a_2$ depends on the horizontal transmission bias.
 That is, with horizontal bias for cooperation, $T_A>T_B$, evolution of cooperation is facilitated by oblique transmission, whereas with horizontal bias for defection, $T_A<T_B$, evolution of cooperation is facilitated by vertical transmission.
-This is demonstrated in \autoref{fig:result3}cd.
-
-The next remarks further inspect the roles of vertical and oblique transmission in the evolution of cooperation.
+This is demonstrated in Figures~\ref{fig:result3}c and~\ref{fig:result3}d.
+
+The next remarks explain the roles of vertical and oblique transmission in the evolution of cooperation.
 \\
@@
 %Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
-This condition does not guarantee fixation of cooperation. Rather, if this condition does not apply then cooperation cannot fix.
+This condition does not guarantee fixation of cooperation; rather, if this condition does not apply then cooperation cannot fix.
 If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
-In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see \autoref{fig:result3}bd).
-
-Without oblique transmission, the following applies.
+In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see Figures~\ref{fig:result3}b and \autoref{fig:result3}d).
+
+With only vertical transmission ($v=1$), the following applies.
 \\
@@
 \label{remark:vert_hori}
-Without oblique transmission ($v=1$) cooperation will increase from rarity if
+In the absence of oblique transmission ($v=1$) cooperation will increase when rare if
 \begin{equation} \label{eq:vert_hori}
@@
 
-These conditions is obtained by setting $v=1$ in inequalities~\ref{eq:unequal_transmission_from_rarity_general_case} and \ref{eq:boundries_assortative_meeting_general_case}
-
-Without vertical transmission we have the following result.
+These conditions are obtained by setting $v=1$ in inequalities~(\ref{eq:unequal_transmission_from_rarity_general_case}) and (\ref{eq:boundries_assortative_meeting_general_case}).
+
+In the absence of vertical transmission ($v=0$) we have the following.
 \\
@@
 \begin{remark}[Condition for global fixation of cooperation: oblique and horizontal transmission] \label{result:obli_hori}
-Without vertical transmission ($v=0$), the frequency of the cooperator phenotype among adults increases every generation, $p'>p$ if there is a horizontal transmission bias in favor of cooperation, namely
+In the absence of vertical transmission ($v=0$), the frequency of the cooperator phenotype among adults increases every generation, i.e.
+$p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely
 \begin{equation} \label{eq:oblique_only_result}
@@
 The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers.
-Note that without bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
-
-Finally, the last remark focuses on the coexistence of cooperation and defection.
+Note that with no bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
+
+Finally, the last remark focuses on the polymorphism of cooperation and defection.
 \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Coexistence of cooperation and defection]
+\begin{remark}[polymorphism of cooperation and defection]
 Cooperation and defection can coexist at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:general_equilibrium}). 
-When it occurs, the coexistence is stable if there is horizontal transmission bias for defection, $T_A<T_B$, and unstable if there is horizontal bias for cooperation, $T_A>T_B$.
+When it is feasible, this equilibrium is stable if there is horizontal transmission bias for defection, $T_A<T_B$, and unstable if there is horizontal bias for cooperation, $T_A>T_B$.
 \end{remark}
 
-See yellow and blue area in \autoref{fig:result2} and \autoref{fig:result3} for cases of stable and unstable coexistence, respectively.
-When unstable coexistence occurs, cooperation will fix if its initial frequency is $p>\tilde{p}^*$, and defection will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:coexistence_recursive}a shows the mapping $\tilde p \to \tilde p'$.
+The yellow and blue areas in Figures~\ref{fig:result2} and \ref{fig:result3} show cases of stable and unstable polymorphism, respectively.
+When $\tilde{p}^*$ is unstable, cooperation will fix if its initial frequency is $p>\tilde{p}^*$, and defection will fix $p<\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+\autoref{fig:polymorphism_recursive}a shows the mapping $\tilde p \to \tilde p'$.
 
@@
 
-We now analyze the evolution of social association under perfect vertical transmission, $v=1$. 
-We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
-Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries_v_threshold})
-
-The stable population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$. 
-In turn, $\hat{p}^*$ is also increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
+We now focus on the evolution of social association under perfect vertical transmission, $v=1$ assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
+Note that for stable polymorphism to occur, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold})
+
+The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
 Therefore, if social association increases, the population mean fitness also increases.
@@
 To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988} that determines social association, but has no direct effect on fitness.
-We assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
-Suppose that the population evolves to a stable equilibrium when only allele $M$ is present.
-We check the local stability of this equilibrium to the invasion of the modifier allele $m$; this stablity is called ``external stability'', see \citet{Altenberg2017}.
-The full analysis is given in Appendix~\ref{sec:appendixD}, and the following result summarizes the outcomes of such invasions.
+The modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
+Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$ where when only allele $M$ is present.
+We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'', see \citet{Altenberg2017}.
+The full analysis is given in Appendix~\ref{sec:appendixD}, and the following result summarizes the condition for this.
 \\
@@
 \label{result:evol_social_association}
-Under perfect vertical transmission ($v=1$), in a population at a stable coexistence between cooperation and defection, a modifier allele can successfully invade the population if it decreases the social association $\alpha$.
+From a stable polymorphism between cooperation and defection, a modifier allele can successfully invade the population if it decreases the social association $\alpha$.
 \end{result}
@@
 Social association may also emerge from population structure.
-Consider a  population colonizing a 2D grid of size 100-by-100, where each site is inhabited by one individual, similarly to \citet{lewin2020rockpaperscissors}.
+Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
 Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
-Initially, each site in the grid is randomly colonized with either a cooperator or a defector, with equal probability.
-%In each generation individuals interact with their neighbors, i.e.
-individuals that inhabit adjacent sites, in a prisoner's dilemma game (\autoref{table:prisoner_payoff}) and in horizontal cultural transmission (\autoref{fig:horizontal}).
-%As before, $T_A$ and $T_B$ are the probabilities of transmitting phenotypes $A$ and $B$ during horizontal transmission.
+Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
 In each generation, half of the individuals are randomly chosen to "initiate" interactions.
 Initiators then interact with a random neighbor (i.e.
-individual in an adjacent site) in a prisoners' dilemma game (\autoref{table:prisoner_payoff}) and a random neighbor (with replacement) in horizontal cultural transmission (\autoref{fig:horizontal}).
+individual in a neighboring site) in a prisoners' dilemma game (\autoref{table:prisoner_payoff}) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:horizontal}).
 The expected number of each of these interactions per individual per generation is one.
@@
 The order the interactions across the grid at each generation is random.
-After all interactions take place, individual fitness is determined by
+After all interactions take place, an individual's fitness is determined by
 $w = 1 + b \cdot n_b - c \cdot n_c$,
@@
 
-The outcomes of stochastic simulations with a structured population are shown in \autoref{fig:spatial}.
-The figure demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for a model without population structure or stochasticity.
-An example for stable coexistence is shown in \autoref{fig:spatial}c.
-Simulating a structured population with local selection (i.e.
-sites can only be settled by offspring of neighbor parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
-
-These comparisons between the deterministic unstructured model and the stochastic structured model show that the derived conditions can be useful for predicting the dynamics of complex scenarios. 
-Moreover, our structured populations demonstrate how social association ($\alpha$) can emerge from local interactions between individuals.
+The outcomes of stochastic simulations with a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for a model without population structure or stochasticity.
+An example of a case with stable polymorphism is shown in \autoref{fig:spatial}.
+Changing the simulation so that the population is structured to allow local selection (i.e.
+sites could only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+
+These comparisons between the deterministic unstructured model and the stochastic structured model show that the derived conditions can be useful for predicting the dynamics under complex scenarios. 
+Moreover, our structured populations demonstrate how our parameter for social association ($\alpha$) can represent local interactions between individuals.
 
@@
 \section*{Discussion}
-We studied the evolution of cooperation under non-vertical transmission using deterministic discrete-time evolutionary models with fitnesses in the form of payoffs from a prisoner's dilemma game. 
-Under a combination of vertical, oblique, and horizontal transmission, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\autoref{result:vert_obli_hori}).
-Importantly, cooperation can increase from rarity (i.e. invade a population of defectors) if and only if (inequality~\ref{eq:unequal_transmission_from_rarity_general_case}),
+Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of payoffs from a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}).
+Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if (inequality~\ref{eq:unequal_transmission_from_rarity_general_case}),
 \begin{equation}
-c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;.
-\end{equation}
-That is, if the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
-This condition cannot be formulates in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission.
-
-Remarkably, stable coexistence between cooperation and defection can be stable if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2}-\ref{fig:result3}).
-
-We find that higher social association $\alpha$ leads to evolution of higher frequencies of cooperation (Remark~\autoref{remark:intermediate_association_res3}, Figures~\ref{fig:result2}c and \ref{fig:result3}cd), and that when both cooperation and defection coexist, higher social association is expected to evolve (Result~\ref{result:evol_social_association}).
-Without social association, the benefit of cooperation cannot facilitate its evolution; cooperation can only succeed under horizontal transmission bias ($T_A>T_B$, Remark~\ref{remark:alpha0}).
-
-Indeed, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation (Remarks~\ref{remark:rarity} and~\ref{remark:intermediate_association_res3}, Figures~\ref{fig:result2}-\ref{fig:result3}).
-The effect of oblique transmission is more complex (Corollary~\ref{remark:intermediate_association_res3}). 
-When there is horizontal transmission bias for cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation (\autoref{fig:result3}ac).
-In contrast, when the bias is for defection, $T_A<T_B$, high rates of vertical transmission, $v$, are advantageous for cooperation, and there must be sufficient rate of vertical transmission for cooperation to fix in the population ($v>\hat v$, see Remark~\autoref{remark:vhat}, \autoref{fig:result3}bd).
-
-The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with structured populations, in which individuals can only interact with and transmit to their neighbors (\autoref{fig:spatial}).
+c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;,
+\end{equation}
+namely, if the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
+This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission.
+
+Remarkably, stable polymorphism between cooperation and defection can be stable if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2} and~\ref{fig:result3}).
+
+We find that stronger social association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
+Nevertheless, when cooperation and defection coexist, social association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness.
+Without social association, the benefit of cooperation cannot facilitate its evolution; cooperation can only succeed if horizontal transmission is biased in its favor.
+
+Horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
+However, the effect of oblique transmission is more complicated.
+When there is horizontal transmission bias for cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation.
+In contrast, when the bias is in favor of defection, $T_A<T_B$, high rates of vertical transmission, $v$, are advantageous for cooperation, and the rate of vertical transmission must be high enough ($v>\hat v$) for cooperation to fix in the population.
+
+The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with population structurein which individuals can only interact with and transmit to their neighbors.
 In these structured populations social association arises due to both social interactions and horizontal cultural transmission being local.
@@
 \citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation.
-He executed simulations with prisoner's dilemma payoffs but without horizontal transmission or social association ($\alpha=0$).
+He carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or social association ($\alpha=0$).
 Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
-Our results provide strong evidence for his hypothesis that horizontal transmission can have an important role in the evolution of cooperation.
+Our results provide strong evidence for his hypothesis that horizontal transmission can play an important role in the evolution of cooperation.
 
 To understand the role of horizontal transmission, we first review the role of \emph{assortment}.
-\citet{Eshel1982} showed that altruism can evolve when there is enough \emph{assortative meeting}, namely, a tendency for individuals to interact within their phenotypic group.
+\citet{Eshel1982} showed that altruism can evolve when there is enough \emph{assortative meeting}, namely, a tendency for individuals to interact with others of their own phenotype.
 \citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
 They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
-Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and partner for transmission.
+Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.
 This mechanism does not require population structure, repeated interactions, or individual recognition.
-We show that high levels of such social association greatly increase the potential for evolution of cooperation (Figures~\ref{fig:result2}-\ref{fig:result3}).
-With enough social association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$, see Remark~\ref{remark:intermediate_association_res3}).
+We show that high levels of such social association greatly increase the potential for evolution of cooperation.
+With enough social association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$).
 
@@
 infection by behavior-determining microbes during interactions effectively generates assortment because a recipient of help may be infected by a behavior-determining microbe and consequently become a helper.
-Cultural horizontal transmission can similarly generate assortment between the cooperative phenotype and the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
-when there is social association, because the recipient of help may be also the recipient of the cultural trait for cooperation.
+Cultural horizontal transmission can similarly generate assortment between cooperators and enhance benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
+when there is social association; the recipient of help may also be the recipient of the cultural trait for cooperation.
 Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
 environment''~\citep{Fletcher2009assortment} is generated not because \emph{the helper is likely to be helped}, but rather because \emph{the helped is likely to become a helper}.
-
-These conclusions highlight the importance of non-vertical cultural transmission in explaining complex evolutionary phenomena, and  furthers our understating of the cultural evolution of cooperation.
-
-% Javarone MA, Atzeni AE, Galam S. Emergence of Cooperation in the Prisoner ’ s Dilemma Driven by Conformity. 2:155-163. doi:10.1007/978-3-319-16549-3
 
@@
 \end{equation}
-Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any $0<p<\epsilon$, it is guaranteed that $0<p'<p$; that is, $p'$ is closer to zero than $p$.
+Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any local perturbation $0<p<\epsilon$, it is guaranteed that $0<p'<p$; that is, $p'$ is closer to zero than $p$.
 
@@
 
-We define $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
+Let $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
 Then, using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, this simplifies to
@@
 
-If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$. 
-Thus, $f(\hat{p})$ becomes a quadratic polynomial,
+If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$, and $f(\hat{p})$ becomes a quadratic polynomial,
 \begin{equation} \label{eq:equal_horizontal_transmission}
@@
 \end{equation}
-Clearly the only two equilibria are the fixations  $\hat{p} =  0$ and $\hat{p} = 1$.
-These equilibria are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\autoref{sec:appendixA}), where
+Clearly the only two equilibria are the fixations $\hat{p} =  0$ and $\hat{p} = 1$, which are are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\ref{sec:appendixA}), where
 $f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big]$, so that
@@
 First, if $\beta_3<\beta_1$ then 
-$1<\hat{p}^*$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable legitimate (i.e. between 0 and 1) equilibrium.
+$1<\hat{p}^*$. Also, $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable feasible equilibrium.
 Second, if $\beta_1<\beta_3<0$ then 
@@
 Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable feasible equilibrium.
 
@@
 	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
-\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
+\item \emph{polymorphism of both phenotypes at $\hat{p}^*$}: 
 	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
@@
 
-We now proceed to use the cost boundaries, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$ (\autoref{eq:cost_boundaries_v_threshold}).
+We now proceed to use the cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}).
 First, assume $T_A<T_B$.
@@
 To determine the effect of increasing $\alpha$ on the stable population mean fitness, $\bar{w}^*=1+(b-c)\hat{p}^*$, we must analyze its effect on $\hat{p}^*$, 
-\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
+\begin{equation} \label{eq:mean_fitness_stable_polymorphism_derivative}
   \frac{\partial \hat{p}^*}{\partial \alpha} 
@@
 \end{equation} 
-Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
+Note that stable polymorphism implies $c<\gamma_1$, and because $\alpha<1$, we have
 \begin{equation}
@@
 \end{equation} 
-Therefore, the numerator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is positive.
-Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is also positive, and hence the derivative $\partial \hat{p}^* / \partial \alpha$ is positive.
+Therefore, the numerator in \autoref{eq:mean_fitness_stable_polymorphism_derivative} is positive.
+Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_polymorphism_derivative} is also positive, and hence the derivative $\partial \hat{p}^* / \partial \alpha$ is positive.
 Thus, the population mean fitness increases as social association $\alpha$ increases.
@@
 We assume here that $v=1$, i.e. no oblique transmission, and therefore $\hat{p}=\tilde{p}$.
-We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
+Denote the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ by $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
 The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
@@
 
-The equilibrium when only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
+The equilibrium where only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
 \begin{equation} \label{eq:p_tilde_star_alpha_1}
@@
 which we get by setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
-When $v=1$, this equilibrium is polymorphic ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\autoref{result:vert_obli_hori}).
+When $v=1$, this equilibrium is polymorphic ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
 
@@
 
-%%% Figure: Boundaries figure - only vertical
+%%% Figure: thresholds figure - only vertical
 
@@
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
-The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
-unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
+The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
 In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
-(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are the solid and dashed lines, respectively. 
-(\textbf{c})~social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
+(\textbf{c})~social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
 Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
@@
 
-%%% Figure: Boundaries figure - vertical and oblique
+%%% Figure: thresholds figure - vertical and oblique
 
@@
     \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
-    The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
-unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
+    The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
 	In all cases the vertical transmission rate $v$ is on the x-axis.
-	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries_v_threshold}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
     Horizontal transmission is biased in (\textbf{a,c}) for cooperation, $T_A>T_B$, and in (\textbf{b,d}) for defection, $T_A<T_B$.    
@@
   \textbf{Evolution of cooperation in a structured population.}
-  Figures \textbf{(a)} and \textbf{(b)} describes the expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel \textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of the right panel \textbf{(b)}.
+	The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel \textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of the right panel \textbf{(b)}.
   The population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
+  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
   Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
-  Figure \textbf{(b)} emphasizes an area in which neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence. 
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_thresholds_v_threshold}.
+  Figure \textbf{(b)} emphasizes an area in which neither phenotype is fixed throughout the simulation, maintaining stochastic polymorphism. 
   Figure \textbf{(c)} describes the frequency of cooperators and defactors over time
@@
   \caption{
-  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable coexistence of cooperators and defactors with soical association $\alpha_1$. 
+  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable polymorphism of cooperators and defactors with soical association $\alpha_1$. 
   The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
@@
 %   \caption{
-%    \textbf{Stable coexistence of both phenotypes in a structured population.}
-%    Figure \textbf{(a)} emphasizes the coexistence shown in \autoref{fig:spatial}b in a structured finite population. 
+%    \textbf{Stable polymorphism of both phenotypes in a structured population.}
+%    Figure \textbf{(a)} emphasizes the polymorphism shown in \autoref{fig:spatial}b in a structured finite population. 
 %    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
 %    Both phenotypes start at 50\% frequency.
-%    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence.
+%    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic polymorphism.
 %    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
@@
   The population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
+  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
   Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_thresholds_v_threshold}.
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
@@
 
-%%% Figure: coexistence map
+%%% Figure: polymorphism map
 \begin{figure}[p]
@@
     \includegraphics[scale=0.4]{coexistence_with_oblique.eps}
-  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
-  The curves show the diffrence of $\hat{p}'-\hat{p}$ vs $\hat{p}$ where $\hat{p}'$ abd $\hat{p}$ are the frequency of the cooperative phenotype $A$ among juveniles in the next generation and current generations (\autoref{eq:horizontal}).
+  \caption{\textbf{Stable and unstable polymorphism of cooperation and defection.}
+  The curves show the difference of $\hat{p}'-\hat{p}$ vs $\hat{p}$ where $\hat{p}'$ abd $\hat{p}$ are the frequency of the cooperative phenotype $A$ among juveniles in the next generation and current generations (\autoref{eq:horizontal}).
   The dashed black line is $\hat{p}'-\hat{p}=0$.
@@
   \textbf{(a)} There is no oblique transmission, $v=1$.
-  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries_v_threshold}).
+  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}).
   The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
@@
   }
-  \label{fig:coexistence_recursive}
+  \label{fig:polymorphism_recursive}
   \end{figure}
@@
   \textbf{Dynamics of the frequency of cooperation.}
-  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
-  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
+  The frequency $\tilde{p}$ of cooperator parents in \textbf{(a-b)} and the frequency $p$ of adults cooperators in \textbf{(c)}.
+  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable polymorphism of cooperators and defectors (yellow).
   \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.

### 2020-11-11 ms/main.tex
revise abstract

@@
 We study the cultural evolution of cooperation under vertical and non-vertical cultural transmission.
-Conditions are found for fixation and polymorphism of cooperation and defection. 
+Conditions are found for fixation and coexistence of cooperation and defection. 
 The evolution of cooperation is facilitated by horizontal transmission and by an association between social interactions and horizontal transmission.
@@
 Stable polymorphism of cooperation and defection can occur.
-When it does, selection favors the evolution of higher association between social interactions and horizontal transmission, which leads to an increased frequency of cooperation and higher population mean fitness.
+When it does, selection will reduce the association between social interactions and horizontal transmission, which leads to a decreased frequency of cooperation and lower population mean fitness.
 The derived conditions are compared to outcomes of stochastic simulations of structured populations.

### 2020-11-11 ms/main.tex
formatting
formatting more

@@
 \hat{p} =
-& \tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] = \\
+& \tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \;= \\
 & v \tilde{p} + (1-v) p \;.
@@
 p' = 
-& \hat{p}^2 \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
-& \hat{p}(1-\hat{p}) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
-& (1-\hat{p})\hat{p} \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] + \\
+& \hat{p}^2 \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
+& \hat{p}(1-\hat{p}) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
+& (1-\hat{p})\hat{p} \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+ \\
 & (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
@@
 \bar{w} \tilde{p}' =
-& \hat{p}^2 (1+b-c) \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
-& \hat{p}(1-\hat{p}) (1-c) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] + \\
-& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] + \\
+& \hat{p}^2 (1+b-c) \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
+& \hat{p}(1-\hat{p}) (1-c) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
+& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+ \\
 & (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
@@
 \bar{w} \tilde{p}' =
-& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] + \\
-& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] + \\
-& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A + \\
+& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] \;+ \\
+& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] \;+ \\
+& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A \;+ \\
 & (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
@@
 \hat{p}' =
-& \frac{v}{\bar{w}}\Big[\hat{p}^2(1+b-c)\Big[1-(1-\hat{p})(1-\alpha)T_B)\Big]\Big] + \\
-& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1-c)\big( \hat{p}(1-\alpha)T_B + 1 - T_B \big) \Big] + \\
-& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1+b)\big(\hat{p}(1-\alpha) + \alpha \big) T_A \Big] + \\
-& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A + \\
-& (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B) \;.
+& \frac{v}{\bar{w}}\Big[\hat{p}^2(1+b-c)\Big(1-(1-\hat{p})(1-\alpha)T_B)\Big)\Big] \;+ \\
+& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1-c)\big( \hat{p}(1-\alpha)T_B + 1 - T_B \big) \Big] \;+ \\
+& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1+b)\big(\hat{p}(1-\alpha) + \alpha \big) T_A \Big] \;+ \\
+& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \;+ \\
+& (1-v)\hat{p}^2(T_B-T_A) \;+ \\
+& (1-v)\hat{p}(1+T_A-T_B) \;.
 \end{aligned}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[polymorphism of cooperation and defection]
+\begin{remark}[Polymorphism of cooperation and defection]
 Cooperation and defection can coexist at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:general_equilibrium}). 
@@
 namely, if the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
-This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission.
-
-Remarkably, stable polymorphism between cooperation and defection can be stable if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2} and~\ref{fig:result3}).
+This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
+Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2} and~\ref{fig:result3}).
 
 We find that stronger social association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, social association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness.
+Nevertheless, when cooperation and defection coexist, social association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}).
 Without social association, the benefit of cooperation cannot facilitate its evolution; cooperation can only succeed if horizontal transmission is biased in its favor.
@@
 
-The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with population structurein which individuals can only interact with and transmit to their neighbors.
+The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
 In these structured populations social association arises due to both social interactions and horizontal cultural transmission being local.
@@
 Further work is needed to incorporate such genetic modification of cultural transmission into our model.
-
 \citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation.
@@
   \bar{w}\tilde{p}_1' = 
-  & \tilde{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) + \\
-  & \tilde{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) + \\
-  & \tilde{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) + \\
+  & \tilde{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) \;+ \\
+  & \tilde{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) \;+ \\
+  & \tilde{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) \;+ \\
   & \tilde{p}_2(1-x)x(1-\alpha_1)T_A \;,
@@
   \bar{w}\tilde{p}_2' = 
-  & \tilde{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \\
-  & \tilde{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) + \\
-  & \tilde{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) + \\
+  & \tilde{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \;+ \\
+  & \tilde{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) \;+ \\
+  & \tilde{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) \;+ \\
 & \tilde{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;, 
@@
   \bar{w}\tilde{p}_3' =
-  & \tilde{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) + \\
-  & \tilde{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) + \\
-  & \tilde{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) + \\
+  & \tilde{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) \;+ \\
+  & \tilde{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) \;+ \\
+  & \tilde{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) \;+ \\
   & \tilde{p}_4(1-x) x (1-\alpha_2)T_A \;, 
@@
   \bar{w}\tilde{p}_4' =
-  & \tilde{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B + \\
-  & \tilde{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) + \\
-  & \tilde{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) + \\
+  & \tilde{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B \;+ \\
+  & \tilde{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) \;+ \\
+  & \tilde{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) \;+ \\
   & \tilde{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \;,
@@
 \tilde{p}^*=
-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)},
+\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)} \;,
 \end{equation}
@@
 \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) 
-\end{bmatrix} = \\
+\end{bmatrix} \;= \\
 & \frac{1}{\bar{w}^*} \begin{bmatrix}
@@
 \begin{aligned}
-c < \gamma_1 = \frac{b \alpha_1 T_A + (T_A-T_B)}{1-T_B} \Leftrightarrow \\
+c &< \gamma_1 = \frac{b \alpha_1 T_A + (T_A-T_B)}{1-T_B} \; \Leftrightarrow \\
 %c(1-T_B) < b \alpha_1 T_A + (T_A-T_B) \Leftrightarrow \\
-0 < b \alpha_1 T_A + (T_A-T_B) - c(1-T_B) \Rightarrow \\
-0 < b T_A + (T_A-T_B) - c(1-T_B) \;,
+0 &< b \alpha_1 T_A + (T_A-T_B) - c(1-T_B) \; \Rightarrow \\
+0 &< b T_A + (T_A-T_B) - c(1-T_B) \;,
 \end{aligned}

### 2020-11-11 ms/main.tex
invasion figure

@@
 \newpage
+
+%%%%%%%%%% Tables %%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Figures}
@@
 In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
-(\textbf{a-b})~The cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
-(\textbf{c})~social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
-Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
+(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
+(\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+Here, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
   	}
@@
 	In all cases the vertical transmission rate $v$ is on the x-axis.
-	(\textbf{a-b}) The cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d}) The social association $\alpha$ is on the y-axis and the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
-    Horizontal transmission is biased in (\textbf{a,c}) for cooperation, $T_A>T_B$, and in (\textbf{b,d}) for defection, $T_A<T_B$.    
+	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d})~Social association $\alpha$ is on the y-axis and the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+    Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
     Here, $T_A = 0.5$, and
@@
    \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
+    ~\\
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
     ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} \\
-    ~
-    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
+    \includegraphics[scale=0.5]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
   \caption{
   \textbf{Evolution of cooperation in a structured population.}
-	The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel \textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of the right panel \textbf{(b)}.
-  The population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
+	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~(a), or the transmission bias, $T_A-T_B$, on the x-axis of panel~(b).
+  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \autoref{eq:equal_transmission} for  panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for~(b).
+	\textbf{(b)}~The inset focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
+  \textbf{(c)}~Frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~(b).
+  In all cases, the population evolves on a 100-by-100 grid.
+  Cooperation and horizontal transmission are both local between neighboring sites, and each site has 8 neighbors.
   Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_thresholds_v_threshold}.
-  Figure \textbf{(b)} emphasizes an area in which neither phenotype is fixed throughout the simulation, maintaining stochastic polymorphism. 
-  Figure \textbf{(c)} describes the frequency of cooperators and defactors over time
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
-  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
+  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$;
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
+  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$;
   \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
@@
 %%% Figure: invasion
-\begin{figure}[b]
+\begin{figure}[p]
   \centering
-   \includegraphics[scale=0.5]{Frequency_of_invadors.eps}~
-   \includegraphics[scale=0.5]{mean_fitness_of_invadors.eps}
+   \includegraphics[scale=0.5]{Figures/invasion.eps}
   \caption{
-  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable polymorphism of cooperators and defactors with soical association $\alpha_1$. 
-  The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
-  \textbf{(a)} The blue curve describes the frequency of the invadors, starting from initial frequency of 1\%.
-  The orange curve describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency which is described by the black dashed line. 
-  The frequency of cooperators after the fixation of the invadors is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.\\
-  \textbf{(b)} describes the mean fitness as a function of time (generations). 
-  As the frequency of the invadors increases the mean fitness decreases. \\
-  In both panels $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
+  \textbf{Reduction principle for social association.} 
+  Consecutive fixation of modifier alleles that reduce social association in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
+  When a modifier allele fixes (frequency > 99.95\%), a new modifier allele that reduces social association by 5\% is introduced.
+\textbf{(a)} The frequency of the cooperative phenotype $A$ in the population over time.
+\textbf{(b)} The frequency of the invading modifier allele $m$ over time.
+\textbf{(c)} The population mean fitness over time.
+Invading alleles are introduced at frequency 0.5\%.
+  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial social association $\alpha_1=0.7$.  
   }
@@
 \end{figure}
-%TDODO: revisit this caption
 

### 2020-11-15 ms/main.tex
A
faculty added

@@
 \affil[1]{School of Computer Science, Interdisciplinary Center Herzliya, Herzliya, Israel}
-\affil[2]{School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv, Israel}
+\affil[2]{School of Plant Sciences and Food Security, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
 \affil[3]{Department of Biology, Stanford University, Stanford, CA}
-\affil[4]{School of Zoology, Tel Aviv University, Tel Aviv, Israel}
+\affil[4]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
 \affil[5]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}

### 2020-11-16 ms/main.tex
fix figs
mwf added

@@
 \begin{abstract}
-We study the cultural evolution of cooperation under vertical and non-vertical cultural transmission.
-Conditions are found for fixation and coexistence of cooperation and defection. 
+Cultural evolution of cooperation under vertical and non-vertical cultural transmission is studied, and conditions are found for fixation and coexistence of cooperation and defection. 
 The evolution of cooperation is facilitated by horizontal transmission and by an association between social interactions and horizontal transmission.
 The effect of oblique transmission depends on the horizontal transmission bias.
-Stable polymorphism of cooperation and defection can occur.
-When it does, selection will reduce the association between social interactions and horizontal transmission, which leads to a decreased frequency of cooperation and lower population mean fitness.
-The derived conditions are compared to outcomes of stochastic simulations of structured populations.
-Comparisons are drawn with Hamilton's rule and the concepts of relatedness and assortment.
+Stable polymorphism of cooperation and defection can occur, and
+when it does, reduced association between social interactions and horizontal transmission evolves, which leads to a decreased frequency of cooperation and lower population mean fitness.
+The deterministic conditions are compared to outcomes of stochastic simulations of structured populations.
+Parallels are drawn with Hamilton's rule incorporating assortment and effective relatedness.
 \end{abstract}
@@
 Such assortative meeting may be due, for example, to population structure or active partner choice.
-In their model, cooperative behavior can evolve if\footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the righthand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
-} 
+In their model, cooperative behavior can evolve if
 \citep[eq.~3.2]{Eshel1982}
@@
 \end{equation}
-where $b$ and $c$ are the benefit and cost of cooperation. 
+where $b$ and $c$ are the benefit and cost of cooperation\footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the right hand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
+}. 
 %Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness coefficient $r$ in inequality~\ref{eq:hamilton_rule}.
@@
 where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{Inequality~\ref{eq:fletcher2009} generalizes inequalities~\ref{eq:hamilton_rule} and~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
-\citet{Bijma2010assortment} gave a result related to inequality~\ref{eq:fletcher2009} for other types of games.
+\citet{Bijma2010assortment} obtained a result related to inequality~\ref{eq:fletcher2009} for other types of games.
 
@@
 
-Cultural transmission may be  viewed as vertical, horizontal or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
+Cultural transmission may be  modeled as vertical, horizontal, or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
 from non-parental adults).
@@
 
-Here, we study cultural-evolution models of cooperation that include both vertical and non-vertical transmission. 
+Here, we study models for the cultural evolution of cooperation that include both vertical and non-vertical transmission. 
 %We investigate these models using mathematical analysis and simulations.  
 In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
-For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission.
-As another example, when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
+For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission,
+or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
 Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can diminish the effect of natural selection \citep{ram2018evolution}.
@@
 two juvenile individuals with phenotype $A$ interact with probability $\hat{p}^2$, two juveniles with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two juveniles with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
-
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
@@
 The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).
-
-Therefore, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
+Then, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
 \begin{equation}\label{eq:nextgen_adults}
@@
 %where $\hat{p}=v\tilde{p}+(1-v)p$.
-Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute \autoref{eq:nextgen_adults_slimpify} for $p'$ and \autoref{eq:nextgen_parents_simplified} for $\tilde{p}'$ and obtain
+Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ from \autoref{eq:nextgen_parents_simplified} and obtain
 \begin{equation} \label{eq:nextgen_juveniles}
@@
 %%% Results
-\section*{Results}
+\section*{Results \textcolor{red}{You still need to change the order of Figs.\ 2 and 3 and the references to them in the text}}
 
@@
 
-The equilibria of our model, i.e. the fixed points of \autoref{eq:nextgen_juveniles}, are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
+The fixed points (equilibria) of  the recursion (\ref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
 \begin{equation} \label{eq:general_equilibrium}
@@
 
-To find conditions on the cost of cooperation, $c$, define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
+Define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
 \begin{equation} \label{eq:cost_thresholds_v_threshold} 
@@
 
-The full analysis is given in Appendix~\ref{sec:appendixB}.
-The following result summarizes the possible outcomes.
+Then we have the following result.
 \\
@@
 \end{result}
-These conditions are illustrated in \autoref{fig:result3}a and \autoref{fig:result3}b.
+These conditions are illustrated in \autoref{fig:result3}a and \autoref{fig:result3}b, and full analysis is in Appendix~\ref{sec:appendixB}. \textcolor{red}{[NOTE: Fig.\ 3 should be Fig.\ 2]}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Condition for cooperation to increase from rarity: cost of cooperation]
+\begin{remark}[Condition on $c$ for cooperation to increase when rare, i.e., $\hat{p}'>p$ near $p=0$]
 \label{remark:rarity}
@@
 
-This unites the conditions for fixation of cooperation and for stable polymorphism, both of which lead to instability of the fixation state associated with defection, $\hat{p}=0$.
+This unites the conditions for fixation of cooperation and for stable polymorphism, both of which entail instability of the state where defection is fixed, $\hat{p}=0$.
 
@@
 Increasing the vertical transmission rate, $v$, can either increase or decrease the cost threshold, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
-When $T_A<T_B$ we get $\partial \gamma_1 / \partial v >0$, and therefore as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to evolve from rarity.
-In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to evolve from rarity.
+When $T_A<T_B$ we have $\partial \gamma_1 / \partial v >0$, and as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to increase when rare. 
+In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to increase when rare.
 
 In general, this condition cannot be formulated in the form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
-When there is no horizontal transmission bias, $T_A=T_B$, the next remark applies.
-\\
+When there is no horizontal transmission bias, $T_A=T_B$, the following applies.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Unbiased horizontal transmission] 
-\label{remark:equal_transmission}
-If horizontal transmission is unbiased, $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if the cost is low enough,
+From Result (\ref{remark:rarity}) and inequality (\ref{eq:unequal_transmission_from_rarity_general_case}), if horizontal transmission is unbiased, $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if the cost is low enough,
 \begin{equation}
@@
 \end{equation}
-\end{remark}
-This condition is obtained by setting $T=T_A=T_B$ in inequality (\ref{eq:unequal_transmission_from_rarity_general_case}) and can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~(\ref{eq:fletcher2009}), where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-\autoref{fig:results}a illustrates this condition for $v=1$. Note that the right-hand side equals $\gamma_1$ when $T=T_A=T_B$.
+This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~(\ref{eq:fletcher2009}), where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+\autoref{fig:results}a illustrates this condition for $v=1$. Note that the right-hand side of (\ref{eq:equal_transmission}) equals $\gamma_1$ when $T=T_A=T_B$.
 
@@
 %A more general case can be stated for $0 < v \leq 1$.
-In the next remarks we examine the effect of social association on the evolution of cooperation.
-\\
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[No social association]
-\label{remark:alpha0}
-Without social association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
+From inequality (\ref{eq:unequal_transmission_from_rarity_general_case}), without social association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
 \begin{equation}
@@
 \end{equation}
-\end{remark}
 
@@
 Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of social association, and the outcome is determined only by  cultural transmission.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Perfect social association]
-\label{remark:alpha1}
-With perfect social association ($\alpha=1$), cooperation will increase when it is rare if
+Further, inequality (\ref{eq:unequal_transmission_from_rarity_general_case}) shows that
+with perfect social association ($\alpha=1$), cooperation will increase when rare if
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 \end{equation}
-\end{remark}
-This condition is obtained by setting $\alpha=1$ in inequality~\ (\ref{eq:unequal_transmission_from_rarity_general_case}).
 % TODO fig 2b?
@@
 In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality \ref{eq:vert_hori_alpha1} applies.
-This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}, and therefore when $v=1$, this remark is equivalent to their eq.~(1).
-
-In light of Remarks~\ref{remark:alpha0} and \ref{remark:alpha1}, it is interesting to examine the general effect of social association on the evolution of cooperation.
-Define the social association thresholds, $a_1$ and $a_2$, as 
+This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~(1).
+
+It is interesting to examine the general effect of social association $\alpha$ on the evolution of cooperation.
+Define social association thresholds, $a_1$ and $a_2$, as 
 \begin{equation} \label{eq:boundries_assortative_meeting_general_case}
@@
 \end{equation}
-Then the following applies.
-\\
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Condition for cooperation to increase from rarity: social association]
+\begin{remark}[Condition on social association $\alpha$ for cooperation to increase when it is rare]
 \label{remark:intermediate_association_res3}
@@
 Figures~\ref{fig:result2}c, \ref{fig:result3}c, and \ref{fig:result3}d illustrate this condition.
-With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in positive x-axis). 
-With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism with defection if social association is intermediate, $a_2<\alpha$ (yellow area).
+With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in the figures). 
+With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism if social association is intermediate, $a_2<\alpha$ (yellow area).
 Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if social association is high enough, $\frac{c}{b \cdot v} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Necessary condition for fixation of cooperation: vertical transmission rate]
+\begin{remark}[Necessary condition on the vertical transmission rate for fixation of cooperation]
 \label{remark:vhat}
@@
 
-With only vertical transmission ($v=1$), the following applies.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Condition for cooperation to increase from rarity: vertical and horizontal transmission]
-\label{remark:vert_hori}
-In the absence of oblique transmission ($v=1$) cooperation will increase when rare if
+With only vertical transmission ($v=1$), inequality (\ref{eq:unequal_transmission_from_rarity_general_case}) entails that cooperation will increase when rare if
 \begin{equation} \label{eq:vert_hori}
@@
 \end{equation}
-\end{remark}
-
-These conditions are obtained by setting $v=1$ in inequalities~(\ref{eq:unequal_transmission_from_rarity_general_case}) and (\ref{eq:boundries_assortative_meeting_general_case}).
-
-In the absence of vertical transmission ($v=0$) we have the following.
-\\
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Condition for global fixation of cooperation: oblique and horizontal transmission] \label{result:obli_hori}
-In the absence of vertical transmission ($v=0$), the frequency of the cooperator phenotype among adults increases every generation, i.e.
-$p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely
-\begin{equation} \label{eq:oblique_only_result}
-T_A > T_B \;.
-\end{equation}
-\end{remark}
-
-This condition is found by setting $v = 0$ in \autoref{eq:horizontal}, which becomes $\hat{p}=p$, and then \autoref{eq:nextgen_adults_slimpify} becomes 
-$p' = p^2 (T_B-T_A) + p (1+T_A-T_B)$. 
-That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ do not affect $p'$).
+In the absence of vertical transmission ($v=0$), from recursion (\ref{eq:nextgen_juveniles}) we see that the frequency of the cooperator phenotype among adults increases every generation, i.e.
+$p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely $T_A > T_B$.
+That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e., $b$ and $c$ do not affect $\hat p'$).
 The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers.
-Note that with no bias in horizontal transmission, $T_A = T_B$, phenotype frequencies are static, $p'=p$.
-
-Finally, the last remark focuses on the polymorphism of cooperation and defection.
-\\
+With no bias in horizontal transmission, $T_A = T_B$, phenotype frequencies do not change, $\hat p'=\hat p$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Polymorphism of cooperation and defection]
 Cooperation and defection can coexist at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:general_equilibrium}). 
-When it is feasible, this equilibrium is stable if there is horizontal transmission bias for defection, $T_A<T_B$, and unstable if there is horizontal bias for cooperation, $T_A>T_B$.
-\end{remark}
-
+When it is feasible, this equilibrium is stable or unstable under the conditions of Result \ref{result:vert_obli_hori}, parts 3 and 4, respectively.
 The yellow and blue areas in Figures~\ref{fig:result2} and \ref{fig:result3} show cases of stable and unstable polymorphism, respectively.
@@
 We now focus on the evolution of social association under perfect vertical transmission, $v=1$ assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
-Note that for stable polymorphism to occur, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold})
-
+Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}).
 The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
@@
 
-To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988} that determines social association, but has no direct effect on fitness.
+To answer this question, we extend our model to include a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines social association, but has no direct effect on fitness.
 The modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
-Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$ where when only allele $M$ is present.
-We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'', see \citet{Altenberg2017}.
-The full analysis is given in Appendix~\ref{sec:appendixD}, and the following result summarizes the condition for this.
-\\
+Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
+We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain
 
@@
 
+The full analysis is in Appendix~\ref{sec:appendixD}.
 Note that this reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
 Furthermore, if we assume that modifier alleles with decreased social association appear and invade the population from time to time, then, the social association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
-This evolution will proceed as long as stable polymorphism occurs, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:result2}c).
-Thus, we can expect social association to eventually drop to $a_2$, the frequency of cooperation to drop to zero, and the population mean fitness to drop to one.
+This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:result2}c).
+Thus, we can expect social association to eventually approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one.
 
@@
 Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
-In each generation, half of the individuals are randomly chosen to "initiate" interactions.
-Initiators then interact with a random neighbor (i.e.
+In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
+initiators interact with a random neighbor (i.e.
 individual in a neighboring site) in a prisoners' dilemma game (\autoref{table:prisoner_payoff}) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:horizontal}).
@@
 On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
-As before, $T_A$ and $T_B$ are the probability for successful horizontal transmission of phenotypes $A$ and $B$, respectively.
-
-The order the interactions across the grid at each generation is random.
+As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
+
+The order of the interactions across the grid at each generation is random.
 After all interactions take place, an individual's fitness is determined by
 $w = 1 + b \cdot n_b - c \cdot n_c$,
-where $n_b$ is the number interactions of that individual with cooperative neighbors, and $n_c$ is the total number of interactions that that individual  had ($n_b \le n_c$).
-Then, a new generation is generated, and sites can be settled by offspring of any parent, not just neighbor parents.
+where $n_b$ is the number of interactions that individual had with cooperative neighbors, and $n_c$ is the total number of interactions that that individual  had ($n_b \le n_c$).
+Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
 Thus, selection is global, rather than local, in accordance with our deterministic model.
 The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness of all potential parents.
-Offspring then have the same phenotype as their parents (i.e. $v=1$).
-
-The outcomes of stochastic simulations with a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for a model without population structure or stochasticity.
+Offspring are assumed to have the same phenotype as their parents (i.e. $v=1$).
+
+The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
 An example of a case with stable polymorphism is shown in \autoref{fig:spatial}.
-Changing the simulation so that the population is structured to allow local selection (i.e.
-sites could only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
-
-These comparisons between the deterministic unstructured model and the stochastic structured model show that the derived conditions can be useful for predicting the dynamics under complex scenarios. 
-Moreover, our structured populations demonstrate how our parameter for social association ($\alpha$) can represent local interactions between individuals.
+Changing the simulation so that the population is structured to allow local selection (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+
+These comparisons between the deterministic unstructured model and the stochastic structured model show that the conditions derived for the deterministic model can be useful for predicting the dynamics under complex scenarios.
+Moreover, this structured population model demonstrates that our parameter for social association ($\alpha$) can represent local interactions between individuals.
 
@@
 \section*{Discussion}
-Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of payoffs from a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}).
-Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if (inequality~\ref{eq:unequal_transmission_from_rarity_general_case}),
+Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}).
+Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~(\ref{eq:unequal_transmission_from_rarity_general_case}),
 \begin{equation}
@@
 \end{equation}
-namely, if the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
+namely, the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
 This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
-Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased for defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2} and~\ref{fig:result3}).
+Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2} and~\ref{fig:result3}).
 
@@
 
-Horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
+In our model, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
 However, the effect of oblique transmission is more complicated.
-When there is horizontal transmission bias for cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation.
-In contrast, when the bias is in favor of defection, $T_A<T_B$, high rates of vertical transmission, $v$, are advantageous for cooperation, and the rate of vertical transmission must be high enough ($v>\hat v$) for cooperation to fix in the population.
+When there is horizontal transmission bias in favor of cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation.
+In contrast, when the bias is in favor of defection, $T_A<T_B$, higher rates of vertical transmission, $v$, are advantageous for cooperation, and the rate of vertical transmission must be high enough ($v>\hat v$) for cooperation to fix in the population.
 
@@
 Further work is needed to incorporate such genetic modification of cultural transmission into our model.
-\citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation.
-He carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or social association ($\alpha=0$).
+\citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation and
+carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or social association ($\alpha=0$).
 Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
@@
 To understand the role of horizontal transmission, we first review the role of \emph{assortment}.
-\citet{Eshel1982} showed that altruism can evolve when there is enough \emph{assortative meeting}, namely, a tendency for individuals to interact with others of their own phenotype.
+\citet{Eshel1982} showed that altruism can evolve when the tendency for \emph{assortative meeting}, i.e., for individuals to interact with others of their own phenotype, is strong enough.
 \citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
-They therefore suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
+They suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
 Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.
@@
 
-This analysis can be summarized with the following conditions:
+This analysis can be summarized as follows:
 % in beta
@@
 \end{equation}
-which we get by setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
-When $v=1$, this equilibrium is polymorphic ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
+setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
+When $v=1$, $\tilde p^*$ is a feasible polymorphism ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
 
 The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
-$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
+$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
 The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1} as

### 2020-11-16 ms/main.tex
reorder figs; revised text

@@
 In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
-This shows that under a combination of genetic and cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (\ref{eq:hamilton_rule}).
+This shows that under a combination of genetic and cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).
 
@@
 Social interactions occur randomly:
-two juvenile individuals with phenotype $A$ interact with probability $\hat{p}^2$, two juveniles with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two juveniles with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
+two juvenile individuals with phenotype $A$ interact with probability~$\hat{p}^2$, two juveniles with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two juveniles with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between socially interacting partners with probability $\alpha$, or between a random pair with probability $1-\alpha$ (see~\autoref{fig:horizontal}).
+It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:horizontal}).
 %The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
@@
 %%% Results
-\section*{Results \textcolor{red}{You still need to change the order of Figs.\ 2 and 3 and the references to them in the text}}
+\section*{Results}
 
@@
 
-The fixed points (equilibria) of  the recursion (\ref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
+The fixed points (equilibria) of  the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
 \begin{equation} \label{eq:general_equilibrium}
@@
 \end{result}
-These conditions are illustrated in \autoref{fig:result3}a and \autoref{fig:result3}b, and full analysis is in Appendix~\ref{sec:appendixB}. \textcolor{red}{[NOTE: Fig.\ 3 should be Fig.\ 2]}
+These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and full analysis is in Appendix~\ref{sec:appendixB}.
 
@@
 Importantly, increasing social association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
-Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation.
+Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
 However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost threshold, but it increases the cost threshold when it is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
@@
 Increasing the vertical transmission rate, $v$, can either increase or decrease the cost threshold, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
-When $T_A<T_B$ we have $\partial \gamma_1 / \partial v >0$, and as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to increase when rare. 
-In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to increase when rare.
+When $T_A<T_B$ we have $\partial \gamma_1 / \partial v >0$, and as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to increase when rare (\autoref{fig:equilibria}b).
+In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to increase when rare (\autoref{fig:equilibria}a).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-From Result (\ref{remark:rarity}) and inequality (\ref{eq:unequal_transmission_from_rarity_general_case}), if horizontal transmission is unbiased, $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if the cost is low enough,
+From Result \ref{result:vert_obli_hori} and inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, if horizontal transmission is unbiased, $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if the cost is low enough,
 \begin{equation}
@@
 \end{equation}
-This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~(\ref{eq:fletcher2009}), where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-\autoref{fig:results}a illustrates this condition for $v=1$. Note that the right-hand side of (\ref{eq:equal_transmission}) equals $\gamma_1$ when $T=T_A=T_B$.
-
-%In Corollary~\ref{remark:intermediate_association}, we examined the effect of social association on evolution of cooperation in the case of perfect vertical transmission ($v=1$).
-%A more general case can be stated for $0 < v \leq 1$.
+This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+\autoref{fig:results}a illustrates this condition for $v=1$.
+Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-From inequality (\ref{eq:unequal_transmission_from_rarity_general_case}), without social association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
+From inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, without social association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
 \begin{equation}
@@
 
-\autoref{fig:result2}a illustrates this condition, which is obtained by setting $\alpha=0$ in inequality~(\ref{eq:unequal_transmission_from_rarity_general_case}).
+\autoref{fig:equilibria_v1}a illustrates this condition (for $v=1$), which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
 Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of social association, and the outcome is determined only by  cultural transmission.
-Further, inequality (\ref{eq:unequal_transmission_from_rarity_general_case}) shows that
-with perfect social association ($\alpha=1$), cooperation will increase when rare if
+Further, inequality~\ref{eq:unequal_transmission_from_rarity_general_case} shows that with perfect social association ($\alpha=1$), cooperation will increase when rare if
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 
-In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality \ref{eq:vert_hori_alpha1} applies.
-This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~(1).
+In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
+This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
 
 It is interesting to examine the general effect of social association $\alpha$ on the evolution of cooperation.
-Define social association thresholds, $a_1$ and $a_2$, as 
+Define the social association thresholds, $a_1$ and $a_2$, as 
 \begin{equation} \label{eq:boundries_assortative_meeting_general_case}
@@
 \end{remark}
-Figures~\ref{fig:result2}c, \ref{fig:result3}c, and \ref{fig:result3}d illustrate this condition.
+Figures~\ref{fig:equilibria}c and \ref{fig:equilibria}d illustrate this condition.
 With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in the figures). 
-With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism if social association is intermediate, $a_2<\alpha$ (yellow area).
+With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism if social association is intermediate, $a_2<\alpha<a_1$ (yellow area).
 Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if social association is high enough, $\frac{c}{b \cdot v} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
@@
 That is, with horizontal bias for cooperation, $T_A>T_B$, evolution of cooperation is facilitated by oblique transmission, whereas with horizontal bias for defection, $T_A<T_B$, evolution of cooperation is facilitated by vertical transmission.
-This is demonstrated in Figures~\ref{fig:result3}c and~\ref{fig:result3}d.
-
-The next remarks explain the roles of vertical and oblique transmission in the evolution of cooperation.
+This is demonstrated in Figures~\ref{fig:equilibria}c and~\ref{fig:equilibria}d.
 \\
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Necessary condition on the vertical transmission rate for fixation of cooperation]
-\label{remark:vhat}
+Next, we look at the roles of vertical and oblique transmission in the evolution of cooperation.
+%\begin{remark}[Necessary condition on the vertical transmission rate for fixation of cooperation]
 Fixation of cooperation is possible only if the vertical transmission rate is high enough,
@@
     \end{equation} 
-\end{remark}
-%Note that $\sigma \frac{\partial \gamma_1}{\partial v} = \sigma (T_B-T_A)$ and $\sigma \frac{\partial \gamma_2}{\partial v} = \sigma (T_A-T_B)(b \alpha T_B - (1+b)(1-T_A))$
 This condition does not guarantee fixation of cooperation; rather, if this condition does not apply then cooperation cannot fix.
 If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
-In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see Figures~\ref{fig:result3}b and \autoref{fig:result3}d).
-
-With only vertical transmission ($v=1$), inequality (\ref{eq:unequal_transmission_from_rarity_general_case}) entails that cooperation will increase when rare if
+In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see Figures~\ref{fig:equilibria}b and \ref{fig:equilibria}d).
+
+With only vertical transmission ($v=1$), inequality~\ref{eq:unequal_transmission_from_rarity_general_case} entails that cooperation will increase when rare if
 \begin{equation} \label{eq:vert_hori}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the absence of vertical transmission ($v=0$), from recursion (\ref{eq:nextgen_juveniles}) we see that the frequency of the cooperator phenotype among adults increases every generation, i.e.
+In the absence of vertical transmission ($v=0$), from recursion~\ref{eq:nextgen_juveniles} we see that the frequency of the cooperator phenotype among adults increases every generation, i.e.
 $p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely $T_A > T_B$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cooperation and defection can coexist at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:general_equilibrium}). 
+Cooperation and defection can coexist at frequencies $\hat{p}^*$ and $1-\hat{p}^*$ (\autoref{eq:general_equilibrium}). 
 When it is feasible, this equilibrium is stable or unstable under the conditions of Result \ref{result:vert_obli_hori}, parts 3 and 4, respectively.
-The yellow and blue areas in Figures~\ref{fig:result2} and \ref{fig:result3} show cases of stable and unstable polymorphism, respectively.
-When $\tilde{p}^*$ is unstable, cooperation will fix if its initial frequency is $p>\tilde{p}^*$, and defection will fix $p<\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:polymorphism_recursive}a shows the mapping $\tilde p \to \tilde p'$.
+The yellow and blue areas in Figures~\ref{fig:equilibria_v1} and \ref{fig:equilibria} show cases of stable and unstable polymorphism, respectively.
+When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+\autoref{fig:polymorphism_recursive} shows the mapping $\hat{p} \to \hat{p}'-\hat{p}$.
 
@@
 
-We now focus on the evolution of social association under perfect vertical transmission, $v=1$ assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
-Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}).
+We now focus on the evolution of social association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
+Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}), see \autoref{fig:equilibria_v1}b.
 The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
@@
 Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
-We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain
+We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain the following result.
+\\
 
@@
 Note that this reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we assume that modifier alleles with decreased social association appear and invade the population from time to time, then, the social association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
-This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:result2}c).
-Thus, we can expect social association to eventually approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one.
+Furthermore, if we assume that modifier alleles with decreased social association appear and invade the population from time to time, then social association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
+This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c).
+Thus, we can expect social association to eventually approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
 
@@
 The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
-An example of a case with stable polymorphism is shown in \autoref{fig:spatial}.
+An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
 Changing the simulation so that the population is structured to allow local selection (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
@@
 \section*{Discussion}
-Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}).
-Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~(\ref{eq:unequal_transmission_from_rarity_general_case}),
+Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
+Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~\ref{eq:unequal_transmission_from_rarity_general_case},
 \begin{equation}
@@
 This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
-Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:result2} and~\ref{fig:result3}).
+Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
 
 We find that stronger social association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, social association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}).
-Without social association, the benefit of cooperation cannot facilitate its evolution; cooperation can only succeed if horizontal transmission is biased in its favor.
-
-In our model, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
+Nevertheless, when cooperation and defection coexist, social association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
+Without social association, the benefit of cooperation cannot facilitate its evolution, and cooperation can only succeed if horizontal transmission is biased in its favor.
+
+Indeed, in our model, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
 However, the effect of oblique transmission is more complicated.
@@
 The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
-In these structured populations social association arises due to both social interactions and horizontal cultural transmission being local.
+In these structured populations social association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
 
@@
 Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.
-This mechanism does not require population structure, repeated interactions, or individual recognition.
+This mechanism does not require repeated interactions, population structure, or individual recognition.
 We show that high levels of such social association greatly increase the potential for evolution of cooperation.
@@
 infection by behavior-determining microbes during interactions effectively generates assortment because a recipient of help may be infected by a behavior-determining microbe and consequently become a helper.
-Cultural horizontal transmission can similarly generate assortment between cooperators and enhance benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
-when there is social association; the recipient of help may also be the recipient of the cultural trait for cooperation.
+Cultural horizontal transmission can similarly generate assortment between cooperators and enhance the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
+when there is social association, so that the recipient of help may also be the recipient of the cultural trait for cooperation.
 Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
-environment''~\citep{Fletcher2009assortment} is generated not because \emph{the helper is likely to be helped}, but rather because \emph{the helped is likely to become a helper}.
+environment''~\citep{Fletcher2009assortment} is generated not because the helper is likely to be helped, but rather because the helped is likely to become a helper.
 
@@
 Therefore, combining inequalities \ref{eq:R1_negative}, \ref{eq:alpha2_alpha1_intermediate}, and \ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_2 < \alpha_1$.
-This is a sufficient condition for external instability, so, if the social association $\alpha_2$ of the invading modifier allele $m$ is less than $\alpha_1$ of the resident $M$, then invasion will be successful.
+This is a sufficient condition for external instability.
+So, if $\alpha_2$, the social association of the invading modifier allele $m$, is less than $\alpha_1$, the social association of the resident allele $M$, then invasion will be successful.
 
 Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-
-%Now we know when all the roots are either smaller or greather than 1. We would like to know when all the roots are smaller than 1.
-%All the roots are smaller than 1 when the slope at 1 is positive. 
-%Using SymPy we get that the slope is positive when:
-%\begin{equation} \label{eq:eigenvalues_smaller_than_1_condition}
-%  \begin{aligned}
-%   c < &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \\
-%   OR \\
-%   c > &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \, AND\, c<\frac{-g}{h}
-%  \end{aligned}
-%\end{equation}
+However, we numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_2<\alpha_1$.
 
@@
 
-%%% Figure: thresholds figure - only vertical
-
-\begin{figure}[p]
-  \centering       
-    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
-	~
-    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
-    ~
-    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}
-
-    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
-The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
-unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
-(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
-(\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
-Here, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
-  	}
-    \label{fig:result2}
-\end{figure}
-%TODO add panel d?
-
 %%% Figure: thresholds figure - vertical and oblique
@@
     }
-    \label{fig:result3}
+    \label{fig:equilibria}
+\end{figure}
+
+%%% Figure: thresholds figure - only vertical
+
+\begin{figure}[p]
+  \centering       
+    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
+	~
+    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
+    ~
+    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
+The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
+In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
+(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
+(\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+Here, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
+  	}
+    \label{fig:equilibria_v1}
+\end{figure}
+%TODO add panel d?
+
+%%% Figure: invasion
+\begin{figure}[p]
+  \centering
+   \includegraphics[scale=0.5]{Figures/invasion.eps}
+  \caption{
+  \textbf{Reduction principle for social association.} 
+  Consecutive fixation of modifier alleles that reduce social association in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
+  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces social association by 5\% is introduced (at initial frequency 0.5\%).
+  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
+  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
+  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
+  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial social association $\alpha_1=0.7$, lower social association threshold $a_2=0.605$.  
+  }
+  \label{fig:invasion}
 \end{figure}
@@
   \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
-    ~\\
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
+	\includegraphics[width=0.3\textwidth]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
     ~
-    \includegraphics[scale=0.5]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
+	\includegraphics[width=0.3\textwidth]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
+    ~
+    \includegraphics[width=0.36\textwidth]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
   \caption{
@@
 	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~(a), or the transmission bias, $T_A-T_B$, on the x-axis of panel~(b).
-  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \autoref{eq:equal_transmission} for  panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for~(b).
-	\textbf{(b)}~The inset focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
-  \textbf{(c)}~Frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~(b).
+  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for  panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for~(b).
+	The inset in panel~(b) focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
+	This stochastic polymorphism is illustrated in panel (c), which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~(b).
   In all cases, the population evolves on a 100-by-100 grid.
@@
 \end{figure}
-%TODO: could you revisit figure 4 caption ? I didn't know how to describe the x sign in figure b. DC
-
-%%% Figure: invasion
-\begin{figure}[p]
-  \centering
-   \includegraphics[scale=0.5]{Figures/invasion.eps}
-  \caption{
-  \textbf{Reduction principle for social association.} 
-  Consecutive fixation of modifier alleles that reduce social association in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
-  When a modifier allele fixes (frequency > 99.95\%), a new modifier allele that reduces social association by 5\% is introduced.
-\textbf{(a)} The frequency of the cooperative phenotype $A$ in the population over time.
-\textbf{(b)} The frequency of the invading modifier allele $m$ over time.
-\textbf{(c)} The population mean fitness over time.
-Invading alleles are introduced at frequency 0.5\%.
-  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial social association $\alpha_1=0.7$.  
-  }
-  \label{fig:invasion}
-\end{figure}
-
-% Fluctuations in spatial model
-%\begin{figure}[p]
-%  \centering
-%   \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
-%   \caption{
-%    \textbf{Stable polymorphism of both phenotypes in a structured population.}
-%    Figure \textbf{(a)} emphasizes the polymorphism shown in \autoref{fig:spatial}b in a structured finite population. 
-%    Figure \textbf{(b)} is a further zoom in which shows the frequency of cooperators (green) and defectors (red).
-%    Both phenotypes start at 50\% frequency.
-%    The figure shows that neither phenotype is fixed throughout the simulation, maintaining stochastic polymorphism.
-%    Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
-%    benefit and cost of cooperation $b=1.3$ and $c=0.02$, perfect vertical transmission $v=1$, horizontal transmission rates $T_A = 0.4 < T_B = 0.435$.
-%    }
-%    %TODO: revisit this caption.
-%    \label{fig:spatial_fluctuations}
-%  \end{figure}
 
@@
 \newpage
-\section*{Supplementary Material}
+%\section*{Supplementary Material}
 \beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
-
-%%% Figure: Spatial model - local selection
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
-    ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
-  \caption{
-  \textbf{Evolution of cooperation in a structured population with local selection.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
-  The population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
-  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_thresholds_v_threshold}.
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
-  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
-  }
-  \label{fig:spatial_local_selection}
-\end{figure}
 
@@
   \caption{\textbf{Stable and unstable polymorphism of cooperation and defection.}
-  The curves show the difference of $\hat{p}'-\hat{p}$ vs $\hat{p}$ where $\hat{p}'$ abd $\hat{p}$ are the frequency of the cooperative phenotype $A$ among juveniles in the next generation and current generations (\autoref{eq:horizontal}).
+  The curves show the change in cooperators frequency, $\hat{p}'-\hat{p}$, as a function of the current frequency of cooperators among juveniles, $\hat{p}$ (\autoref{eq:nextgen_juveniles}).
   The dashed black line is $\hat{p}'-\hat{p}=0$.
-  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (red circle).
-  When $\hat{p}' - \hat{p} > 0 $,  $\hat{p}$ increases towards $\hat{p}^*$.
-  When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
-  \textbf{(a)} There is no oblique transmission, $v=1$.
-  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}).
-  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
-  \textbf{(b)} Oblique transmission exists. 
-  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
-  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
+  The curves and the dashed line intersect at the polymorphic equilibrium $\hat{p}^*$ (red circle).
+  %When $\hat{p}' - \hat{p} > 0 $,  $\hat{p}$ increases towards $\hat{p}^*$.
+  %When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
+  \textbf{(a)} Without oblique transmission, $v=1$.
+  A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$.
+  An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$.
+  \textbf{(b)} With oblique transmission. 
+  A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$.
+  An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$.
   }
@@
 
+%%% Figure: Spatial model - local selection
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
+    ~
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
+  \caption{
+  \textbf{Evolution of cooperation in a structured population with local selection.}
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel (a), or the transmission bias $T_A-T_B$ on the x-axis of panel (b).
+  The population evolves on a 100-by-100 grid.
+  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
+  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for panel (b).
+  The population evolves on a 100-by-100 grid.
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
+  50 simulations were executed for each parameter set.
+  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$;
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
+  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$;
+  }
+  \label{fig:spatial_local_selection}
+\end{figure}
+
 %%%

### 2020-11-18 ms/main.tex
minor changes

@@
 \citet{Eshel1982} studied a related model for the evolution of cooperative behavior.
-Their model included \emph{assortative meeting}, or non-random encounters, where a fraction $m$ of individuals in the population each interact with an individual of the same phenotype, and a fraction $1-m$ interacts  with a randomly chosen individual.
+Their model included \emph{assortative meeting}, or non-random encounters, where a fraction $m$ of individuals in the population each interact specifically with an individual of the same phenotype, and a fraction $1-m$ interacts  with a randomly chosen individual.
 Such assortative meeting may be due, for example, to population structure or active partner choice.
@@
 In this paper we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
-\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
+\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission with kin selection and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
 \begin{equation} \label{eq:feldman1985}
@@
 or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because non-vertical transmission can diminish the effect of natural selection \citep{ram2018evolution}.
+Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
 This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a broader understanding of its evolutionary dynamics.
@@
 Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
-However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost threshold, but it increases the cost threshold when it is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
+However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost threshold, but it increases the cost threshold when the threshold is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
 Therefore, increasing $T_B$ decreases the cost threshold and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
@@
 \label{eq:equal_transmission}
-c < b \cdot \frac{v \alpha T}{1-T} \;.
-\end{equation}
-This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $v \alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-\autoref{fig:results}a illustrates this condition for $v=1$.
+c < b \cdot \frac{\alpha T}{1-T} \;,
+\end{equation}
+and regardless of the vertical transmission rate, $v$.
+This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+\autoref{fig:results}a illustrates this condition.
 Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.
@@
 \end{equation}
-% TODO fig 2b?
 
@@
 $\alpha$ & Probability of social association & $[0,1]$ \\
-$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $[0,1]$ \\
+$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $(0,1)$ \\
 \\ \bottomrule
@@
 %TODO add panel d?
+% maybe show cost vs alpha ?
 

### 2020-11-18 ms/main.tex
morrison

@@
 the Israel Science Foundation 552/19 (YR),
-and Minerva Stiftung Center for Lab Evolution (YR).
-% TODO funding for other authors?
-}
+Minerva Stiftung Center for Lab Evolution (YR),
+and the Morrison Institute for Population and Resources Studies at Stanford University (MWF).
 

### 2020-11-19 ms/main.tex
OLE comments; change biblio format to rsnat

--- 2020-11-18 ms/main.tex
@@
 % NatBib
-\usepackage[round,colon]{natbib}
+\usepackage[numbers,square,comma,sort]{natbib}
 
@@
 Cooperative behavior can reduce an individual's fitness and increase the fitness of its conspecifics or competitors~\citep{axelrod1981evolution}.
-Nevertheless, cooperative behavior appears to occur in many non-human animals~\citep{dugatkin1997cooperation}, including primates~\citep{jaeggi2013natural},  rats~\citep{rice1962altruism}, birds~\citep{stacey1990cooperative,krams2008experimental}, and lizards~\citep{sinervo2006self}.
-Evolution of cooperative behavior remains an important conundrum in evolutionary biology~\citep[Appendix]{Haldane1932book}.
+Nevertheless, cooperative behavior appears to occur in many animals~\citep{dugatkin1997cooperation}, including humans, primates~\citep{jaeggi2013natural},  rats~\citep{rice1962altruism}, birds~\citep{stacey1990cooperative,krams2008experimental}, and lizards~\citep{sinervo2006self}.
+Evolution of cooperative behavior has been an important focus of research in evolutionary theory since at least the 1930s~\citep[Appendix]{Haldane1932book}.
 
@@
 
-In this paper we study the evolution of a cooperative behavior that is subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
+Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
 \citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission with kin selection and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
@@
 In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
-This shows that under a combination of genetic and cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).
+This shows that under a cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).
 
@@
 Evolution under either of these transmission models can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior (the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by microbes that manipulate their host's behavior.)
-Some of the analyses by \citet{lewin2017microbes} can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
+Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior, the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by host-associated microbes.
+Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
 
@@
 or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
+Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
 This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a broader understanding of its evolutionary dynamics.
@@
 
-Not all adults become parents due to natural selection, and we denote the frequency of phenotype $A$ among parents by $\tilde{p}$.
+Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\tilde{p}$.
 Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
@@
 \end{result}
-These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and full analysis is in Appendix~\ref{sec:appendixB}.
+These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the full analysis is in Appendix~\ref{sec:appendixB}.
 
@@
 In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
-This is similar to case of microbe-associated cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
+This is similar to case of microbe-induced cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
 
@@
     \end{equation} 
-This condition does not guarantee fixation of cooperation; rather, if this condition does not apply then cooperation cannot fix.
+This condition is necessary for fixation of cooperation, but it is not sufficient.
 If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
@@
 $w = 1 + b \cdot n_b - c \cdot n_c$,
-where $n_b$ is the number of interactions that individual had with cooperative neighbors, and $n_c$ is the total number of interactions that that individual  had ($n_b \le n_c$).
+where $n_b$ is the number of interactions that individual had with cooperative neighbors,
+and $n_c$ is the number of interactions in which that individual cooperated (note that the phenotype may change between consecutive interactions due to horizontal transmission).
 Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
-Thus, selection is global, rather than local, in accordance with our deterministic model.
-The parent is randomly drawn with probability proportional to its fitness, divided by the average fitness of all potential parents.
+Selection is global, rather than local, in accordance with our deterministic model:
+The parent is randomly drawn with probability proportional to its fitness, divided by the sum of the fitness values of all potential parents.
 Offspring are assumed to have the same phenotype as their parents (i.e. $v=1$).
@@
 An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
-Changing the simulation so that the population is structured to allow local selection (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+Changing the simulation so that selection is local (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
 
@@
 \citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} 
-suggested that microbes that manipulate their hosts to act altruistically can be favored by selection, which may help to explain the evolution of cooperation. 
+suggested that microbes that induce their hosts to act altruistically can be favored by selection, which may help to explain the evolution of cooperation. 
 %Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
@@
 This work was supported in part by
+the Clore Foundation Scholars Programme (OLE),
+the Morrison Institute for Population and Resources Studies at Stanford University (MWF),
 the Israel Science Foundation 552/19 (YR),
 and Minerva Stiftung Center for Lab Evolution (YR).
-% TODO funding for other authors?
-}
 
@@
 % Bibliography
-\bibliographystyle{plainnat}
+\bibliographystyle{rsnat}
 \bibliography{bib}

### 2020-11-21 ms/main.tex
todo
Add panel D

--- 2020-11-18 ms/main.tex
@@
     ~
-    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
-The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
+    ~
+    \includegraphics[width=0.45\textwidth]{coexistence_without_oblique.eps}
+    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
+    Figures \textbf{(a)-(c)} shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
 unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
+    In figures \textbf{(a)-(c)} the horizontal bias ($T_A-T_B$) is on the x-axis.
     (\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
     (\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
-Here, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
+    Here in figures \textbf{(a)-(c)}, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
+    In figure \textbf{(d)} shows stable and unstable polymorphism of cooperation and defection.
+    The curves show the change in cooperators frequency, $\hat{p}'-\hat{p}$, as a function of the current frequency of cooperators among juveniles, $\hat{p}$ (\autoref{eq:nextgen_juveniles}).
+    A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$.
+    An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$.
   	}
@@
   \centering
-    \includegraphics[scale=0.4]{coexistence_without_oblique.eps}
-    \includegraphics[scale=0.4]{coexistence_with_oblique.eps}
+   % \includegraphics[scale=0.4]{coexistence_without_oblique.eps}
+    \includegraphics[scale=0.6]{coexistence_with_oblique.eps}
   \caption{\textbf{Stable and unstable polymorphism of cooperation and defection.}
@@
   %When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
-  \textbf{(a)} Without oblique transmission, $v=1$.
-  A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$.
-  An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$.
-  \textbf{(b)} With oblique transmission. 
   A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$.

### 2020-11-22 ms/main.tex
revised fig 2

@@
     \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
-    The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
 unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
@@
     ~
-    \includegraphics[width=0.45\textwidth]{coexistence_without_oblique.eps}
+    \includegraphics[width=0.48\textwidth]{coexistence_without_oblique.eps}
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
-    Figures \textbf{(a)-(c)} shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
 unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-    In figures \textbf{(a)-(c)} the horizontal bias ($T_A-T_B$) is on the x-axis.
-    (\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
-    (\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
-    Here in figures \textbf{(a)-(c)}, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
-    In figure \textbf{(d)} shows stable and unstable polymorphism of cooperation and defection.
-    The curves show the change in cooperators frequency, $\hat{p}'-\hat{p}$, as a function of the current frequency of cooperators among juveniles, $\hat{p}$ (\autoref{eq:nextgen_juveniles}).
-    A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$.
-    An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$.
+    (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
+    In panels (a) and (b), the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
+	In panel (c), social association $\alpha$ is on the y-axis and the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+    Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
+    \textbf{(d)} Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
+    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$).
+    The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
+    Markers show the three equilibria.
   	}
@@
 \end{figure}
-%TODO add panel d?
-% maybe show cost vs alpha ?
-
-%%% Figure: invasion
+
+%%% Figure: Invasion
 \begin{figure}[p]

### 2020-11-22 ms/main.tex

--- 2020-11-19 ms/main.tex
@@
 \pagebreak
+
+% TODO change "scoail association" to "interaction-transmission association"
 
@@
     ~
-    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
-The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
+    ~
+    \includegraphics[width=0.48\textwidth]{coexistence_without_oblique.eps}
+    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
+    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
 unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
-(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
-(\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
-Here, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
+    (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
+    In panels (a) and (b), the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
+	In panel (c), social association $\alpha$ is on the y-axis and the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+    Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
+    \textbf{(d)} Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
+    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$).
+    The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
+    Markers show the three equilibria.
   	}

### 2020-11-22 ms/main.tex
revise fig 1 based on OLE illustration

@@
 Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
-An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$.
+An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}a).
 Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
@@
 Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
-\autoref{table:prisoner_payoff} shows the payoff matrix, i.e.
+\autoref{fig:illustration}a shows the payoff matrix, i.e.
 the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
@@
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:horizontal}).
+It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}b).
 %The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
 However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
-The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}).
+The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}c).
 Then, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 \end{equation}
-where fitness values are taken from \autoref{table:prisoner_payoff} and \autoref{table:interactions}, and the population mean fitness is
+where fitness values are taken from \autoref{fig:illustration}a and \autoref{table:interactions}, and the population mean fitness is
 %\begin{equation} \label{eq:mean_fitness}
@@
 With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism if social association is intermediate, $a_2<\alpha<a_1$ (yellow area).
-Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if social association is high enough, $\frac{c}{b \cdot v} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if social association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
 
@@
 The yellow and blue areas in Figures~\ref{fig:equilibria_v1} and \ref{fig:equilibria} show cases of stable and unstable polymorphism, respectively.
-When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:polymorphism_recursive} shows the mapping $\hat{p} \to \hat{p}'-\hat{p}$.
+When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$.
+$\hat{p}^*$ is unstable when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+\autoref{fig:equilibria_v1}d shows the mapping $\hat{p} \to \hat{p}'-\hat{p}$.
 
@@
 Therefore, if social association increases, the population mean fitness also increases.
-But can an allele that increases social association evolve?
+But can this population-level advantage lead to the evolution of social association?
 
@@
 The expected number of each of these interactions per individual per generation is one.
-The effective social association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/m$, where $m$ is the number of neighbors.
-On an infinite grid, $m=8$, but on a finite grid $m$ can be lower in edge neighborhoods close to the grid border.
+The effective social association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
+On an infinite grid, $M=8$, but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
 As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
@@
 Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
-Our results provide strong evidence for his hypothesis that horizontal transmission can play an important role in the evolution of cooperation.
+He further hypothesized that horizontal transmission can play an important role in the evolution of cooperation, and our results provide strong evidence for this hypothesis.
 
@@
 the Morrison Institute for Population and Resources Studies at Stanford University (MWF),
-the Israel Science Foundation 552/19 (YR),
+Israel Science Foundation (YR 552/19),
 and Minerva Stiftung Center for Lab Evolution (YR).
@@
 
-%%% Table: payoff matrix
-\bigskip
-\begin{table}[h]
-\centering
-\caption{\textbf{Payoff matrix for prisoner's dilemma.}}
-\begin{tabular}{lll}
-\toprule
-           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
-$\phi_1=A$ & $1+b-c$ & $1-c$ \\
-$\phi_1=B$ & $1+b$   & $1$
-\\ \bottomrule
-\end{tabular}
-\label{table:prisoner_payoff}
-\caption*{
-The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+%%%% Table: payoff matrix
+%\bigskip
+%\begin{table}[h]
+%\centering
+%\caption{\textbf{Payoff matrix for prisoner's dilemma.}}
+%\begin{tabular}{lll}
+%\toprule
+%           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
+%$\phi_1=A$ & $1+b-c$ & $1-c$ \\
+%$\phi_1=B$ & $1+b$   & $1$
+%\\ \bottomrule
+%\end{tabular}
+%\label{table:prisoner_payoff}
+%\caption*{
+%The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
 $A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
 $0<c<1$ and $c<b$.
-}
-\end{table}
-\bigskip
-%%%
+%}
+%\end{table}
+%\bigskip
+%%%%
 
@@
   \centering
-  \includegraphics[scale=1]{figure1.pdf}
+  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
   \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{social association} parameter.
   }
-  \label{fig:horizontal}
+  \label{fig:illustration}
 \end{figure}
@@
 
-%%% Figure: polymorphism map
-\begin{figure}[p]
-  \centering
-   % \includegraphics[scale=0.4]{coexistence_without_oblique.eps}
-    \includegraphics[scale=0.6]{coexistence_with_oblique.eps}
-  \caption{\textbf{Stable and unstable polymorphism of cooperation and defection.}
-  The curves show the change in cooperators frequency, $\hat{p}'-\hat{p}$, as a function of the current frequency of cooperators among juveniles, $\hat{p}$ (\autoref{eq:nextgen_juveniles}).
-  The dashed black line is $\hat{p}'-\hat{p}=0$.
-  The curves and the dashed line intersect at the polymorphic equilibrium $\hat{p}^*$ (red circle).
-  %When $\hat{p}' - \hat{p} > 0 $,  $\hat{p}$ increases towards $\hat{p}^*$.
-  %When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
-  A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$.
-  An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$.
-  }
-  \label{fig:polymorphism_recursive}
-  \end{figure}
-
 %%% Figure: frequency dynamics

### 2020-11-22 ms/main.tex
interaction-transmission association

@@
 It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}b).
-%The social association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
+%The interaction-transmission association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
 However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
@@
 In the following sections, we determine the equilibria of the model in \autoref{eq:nextgen_juveniles}, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
-We then analyze the evolution of a modifier of social association.
+We then analyze the evolution of a modifier of interaction-transmission association.
 Finally, we compare derived conditions to outcomes of stochastic simulations with a structured population.
@@
 
-Importantly, increasing social association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
+Importantly, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
 Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-From inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, without social association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
+From inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, without interaction-transmission association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
 \begin{equation}
@@
 \autoref{fig:equilibria_v1}a illustrates this condition (for $v=1$), which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
-Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of social association, and the outcome is determined only by  cultural transmission.
-Further, inequality~\ref{eq:unequal_transmission_from_rarity_general_case} shows that with perfect social association ($\alpha=1$), cooperation will increase when rare if
+Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of interaction-transmission association, and the outcome is determined only by  cultural transmission.
+Further, inequality~\ref{eq:unequal_transmission_from_rarity_general_case} shows that with perfect interaction-transmission association ($\alpha=1$), cooperation will increase when rare if
 \begin{equation}\label{eq:vert_hori_alpha1}
@@
 
-It is interesting to examine the general effect of social association $\alpha$ on the evolution of cooperation.
-Define the social association thresholds, $a_1$ and $a_2$, as 
+It is interesting to examine the general effect of interaction-transmission association $\alpha$ on the evolution of cooperation.
+Define the interaction-transmission association thresholds, $a_1$ and $a_2$, as 
 \begin{equation} \label{eq:boundries_assortative_meeting_general_case}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Condition on social association $\alpha$ for cooperation to increase when it is rare]
+\begin{remark}[Condition on interaction-transmission association $\alpha$ for cooperation to increase when it is rare]
 \label{remark:intermediate_association_res3}
-Cooperation will increase when rare if social association is high enough, specifically if $a_2 < \alpha$.
+Cooperation will increase when rare if interaction-transmission association is high enough, specifically if $a_2 < \alpha$.
 \end{remark}
@@
 With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in the figures). 
-With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if social association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism if social association is intermediate, $a_2<\alpha<a_1$ (yellow area).
-Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if social association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if interaction-transmission association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism if interaction-transmission association is intermediate, $a_2<\alpha<a_1$ (yellow area).
+Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if interaction-transmission association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Evolution of social association}
-
-We now focus on the evolution of social association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
+\subsection*{Evolution of interaction-transmission association}
+
+We now focus on the evolution of interaction-transmission association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
 Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}), see \autoref{fig:equilibria_v1}b.
 The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
-Therefore, if social association increases, the population mean fitness also increases.
-But can this population-level advantage lead to the evolution of social association?
-
-To answer this question, we extend our model to include a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines social association, but has no direct effect on fitness.
-The modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
+Therefore, if interaction-transmission association increases, the population mean fitness also increases.
+But can this population-level advantage lead to the evolution of interaction-transmission association?
+
+To answer this question, we extend our model to include a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines interaction-transmission association, but has no direct effect on fitness.
+The modifier locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
 Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}[Reduction principle for social association] 
+\begin{result}[Reduction principle for interaction-transmission association] 
 \label{result:evol_social_association}
-From a stable polymorphism between cooperation and defection, a modifier allele can successfully invade the population if it decreases the social association $\alpha$.
+From a stable polymorphism between cooperation and defection, a modifier allele can successfully invade the population if it decreases the interaction-transmission association $\alpha$.
 \end{result}
@@
 Note that this reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we assume that modifier alleles with decreased social association appear and invade the population from time to time, then social association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
+Furthermore, if we assume that modifier alleles with decreased interaction-transmission association appear and invade the population from time to time, then interaction-transmission association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
 This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c).
-Thus, we can expect social association to eventually approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
+Thus, we can expect interaction-transmission association to eventually approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
 
@@
 
-Social association may also emerge from population structure.
+interaction-transmission association may also emerge from population structure.
 Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
@@
 The expected number of each of these interactions per individual per generation is one.
-The effective social association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
+The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
 On an infinite grid, $M=8$, but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
@@
 These comparisons between the deterministic unstructured model and the stochastic structured model show that the conditions derived for the deterministic model can be useful for predicting the dynamics under complex scenarios.
-Moreover, this structured population model demonstrates that our parameter for social association ($\alpha$) can represent local interactions between individuals.
+Moreover, this structured population model demonstrates that our parameter for interaction-transmission association ($\alpha$) can represent local interactions between individuals.
 
@@
 This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
-Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both the cost of cooperation and social association are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
-
-We find that stronger social association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, social association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
-Without social association, the benefit of cooperation cannot facilitate its evolution, and cooperation can only succeed if horizontal transmission is biased in its favor.
+Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both the cost of cooperation and interaction-transmission association are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
+
+We find that stronger interaction-transmission association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
+Nevertheless, when cooperation and defection coexist, interaction-transmission association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
+Without interaction-transmission association, the benefit of cooperation cannot facilitate its evolution, and cooperation can only succeed if horizontal transmission is biased in its favor.
 
@@
 The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
-In these structured populations social association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
+In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
 
@@
 \citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation and
-carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or social association ($\alpha=0$).
+carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or interaction-transmission association ($\alpha=0$).
 Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
@@
 This mechanism does not require repeated interactions, population structure, or individual recognition.
-We show that high levels of such social association greatly increase the potential for evolution of cooperation.
-With enough social association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$).
+We show that high levels of such interaction-transmission association greatly increase the potential for evolution of cooperation.
+With enough interaction-transmission association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$).
 
@@
 Cultural horizontal transmission can similarly generate assortment between cooperators and enhance the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
-when there is social association, so that the recipient of help may also be the recipient of the cultural trait for cooperation.
+when there is interaction-transmission association, so that the recipient of help may also be the recipient of the cultural trait for cooperation.
 Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Effect of social association on mean fitness} \label{sec:appendixC}
+\section{Effect of interaction-transmission association on mean fitness} \label{sec:appendixC}
 
@@
 Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_polymorphism_derivative} is also positive, and hence the derivative $\partial \hat{p}^* / \partial \alpha$ is positive.
-Thus, the population mean fitness increases as social association $\alpha$ increases.
+Thus, the population mean fitness increases as interaction-transmission association $\alpha$ increases.
 
@@
 This is a sufficient condition for external instability.
-So, if $\alpha_2$, the social association of the invading modifier allele $m$, is less than $\alpha_1$, the social association of the resident allele $M$, then invasion will be successful.
+So, if $\alpha_2$, the interaction-transmission association of the invading modifier allele $m$, is less than $\alpha_1$, the interaction-transmission association of the resident allele $M$, then invasion will be successful.
 
@@
 $b$ & Benefit of cooperation & $c<b$ \\
-$\alpha$ & Probability of social association & $[0,1]$ \\
+$\alpha$ & Probability of interaction-transmission association & $[0,1]$ \\
 $T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $(0,1)$ \\
@@
   \includegraphics[width=0.7\textwidth]{Illustration.pdf}
-  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{social association} parameter.
+  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{interaction-transmission association} parameter.
   }
@@
 	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d})~Social association $\alpha$ is on the y-axis and the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d})~interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
     Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
@@
     In panels (a) and (b), the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
-	In panel (c), social association $\alpha$ is on the y-axis and the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+	In panel (c), interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
     Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
@@
   \caption{
-  \textbf{Reduction principle for social association.} 
-  Consecutive fixation of modifier alleles that reduce social association in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
-  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces social association by 5\% is introduced (at initial frequency 0.5\%).
+  \textbf{Reduction principle for interaction-transmission association.} 
+  Consecutive fixation of modifier alleles that reduce interaction-transmission association in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
+  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
   \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
@@
   \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
-  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial social association $\alpha_1=0.7$, lower social association threshold $a_2=0.605$.  
+  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
   }
@@
 	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~(a), or the transmission bias, $T_A-T_B$, on the x-axis of panel~(b).
-  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for  panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for~(b).
+  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for  panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for~(b).
 	The inset in panel~(b) focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
@@
   Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with social association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for panel (b).
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for panel (b).
   The population evolves on a 100-by-100 grid.

### 2020-11-23 ms/main.tex
mwf comments

@@
 Cultural evolution of cooperation under vertical and non-vertical cultural transmission is studied, and conditions are found for fixation and coexistence of cooperation and defection. 
-The evolution of cooperation is facilitated by horizontal transmission and by an association between social interactions and horizontal transmission.
+The evolution of cooperation is facilitated by its horizontal transmission and by an association between social interactions and horizontal transmission.
 The effect of oblique transmission depends on the horizontal transmission bias.
@@
 $\hat{p}^*$ is unstable when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:equilibria_v1}d shows the mapping $\hat{p} \to \hat{p}'-\hat{p}$.
+\autoref{fig:equilibria_v1}d shows $\hat{p}'-\hat{p}$ as a function of $\hat{p}$.
 
@@
 	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d})~interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d})~interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
     Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
@@
     In panels (a) and (b), the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
-	In panel (c), interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+	In panel (c), interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
     Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
     \textbf{(d)} Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
-    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$).
+    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$). % todo ref eq 12
     The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
@@
 	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~(a), or the transmission bias, $T_A-T_B$, on the x-axis of panel~(b).
-  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for  panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for~(b).
+  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~(a) and in inequality~\ref{eq:cost_thresholds_v_threshold} for~(b).
 	The inset in panel~(b) focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
@@
 
-%%% Figure: frequency dynamics
-\begin{figure}[p]
-  \centering
-    \includegraphics[scale=0.45]{Time_Figure_Equal_Horizontal.pdf}
-    ~\\
-    \includegraphics[scale=0.45]{Time_Figure_Only_Vertical_No_Alpha.pdf}
-    ~\\
-    \includegraphics[scale=0.45]{Time_Figure_No_Vertical.pdf}
-  \caption{
-  \textbf{Dynamics of the frequency of cooperation.}
-  The frequency $\tilde{p}$ of cooperator parents in \textbf{(a-b)} and the frequency $p$ of adults cooperators in \textbf{(c)}.
-  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable polymorphism of cooperators and defectors (yellow).
-  \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
-  }
-  \label{fig:results}
-\end{figure}
-
 %%% Figure: Spatial model - local selection
@@
   Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in \autoref{eq:equal_transmission} for panel~(a) and in \autoref{eq:cost_thresholds_v_threshold} for panel (b).
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for panel~(a) and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel (b).
   The population evolves on a 100-by-100 grid.

### 2020-11-23 ms/main.tex
fig 1 caption by OLE

@@
   \includegraphics[width=0.7\textwidth]{Illustration.pdf}
-  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{interaction-transmission association} parameter.
+  \caption{\textbf{Model illustration.} 
+  \textbf{(a)} Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+  \textbf{(b)} Individuals socially interact in pairs in a prisoners' dilemma game.
+Horizontal cultural transmission occurs with a random individual from the population, with probability $1-\alpha$, or with the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
+  \textbf{(c)} The probability of successful horizontal  cultural transmission of phenotypes $A$ and $B$ is $T_A$ and $T_B$ respectively.
+  \textbf{(d)} Offspring inherit their parent phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
     }

### 2020-11-24 ms/main.tex
minor changes MWF

--- 2020-11-23 ms/main.tex
@@
 
-In the following sections, we determine the equilibria of the model in \autoref{eq:nextgen_juveniles}, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
-We then analyze the evolution of a modifier of interaction-transmission association.
+We determine the equilibria of the model in \autoref{eq:nextgen_juveniles}, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
+We then analyze the evolution of a modifier of interaction-transmission association,~$\alpha$.
 Finally, we compare derived conditions to outcomes of stochastic simulations with a structured population.
@@
 
-Importantly, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
+Importantly, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase in frequency when initially rare.
 Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
@@
 This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-\autoref{fig:results}a illustrates this condition.
 Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.
@@
 
-Next, we look at the roles of vertical and oblique transmission in the evolution of cooperation.
-%\begin{remark}[Necessary condition on the vertical transmission rate for fixation of cooperation]
+Next, we examine the roles of vertical and oblique transmission in the evolution of cooperation.
 Fixation of cooperation is possible only if the vertical transmission rate is high enough,
@@
 \subsection*{Population structure}
-
-interaction-transmission association may also emerge from population structure.
+Interaction-transmission association may also emerge from population structure.
 Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
@@
 initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoners' dilemma game (\autoref{table:prisoner_payoff}) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:horizontal}).
+individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
 The expected number of each of these interactions per individual per generation is one.
@@
 These comparisons between the deterministic unstructured model and the stochastic structured model show that the conditions derived for the deterministic model can be useful for predicting the dynamics under complex scenarios.
-Moreover, this structured population model demonstrates that our parameter for interaction-transmission association ($\alpha$) can represent local interactions between individuals.
+Moreover, this structured population model demonstrates that our parameter for interaction-transmission association, $\alpha$, can represent local interactions between individuals.
 
@@
   \includegraphics[width=0.7\textwidth]{Illustration.pdf}
-  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{interaction-transmission association} parameter.
+  \caption{\textbf{Model illustration.} 
+  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
+Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
+  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
+  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
     }
@@
 	In all cases the vertical transmission rate $v$ is on the x-axis.
-	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d})~interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (Eqs.~\ref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d})~Interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
     Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
@@
     (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
-    In panels (a) and (b), the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
-	In panel (c), interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+    In panels \textbf{(a)} and \textbf{(b)}, the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
+	In panel \textbf{(c)}, interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
     Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
-    \textbf{(d)} Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
+    \textbf{(d)}~Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
     The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$). % todo ref eq 12
     The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
-    Markers show the three equilibria.
+    Black circles show the three equilibria.
   	}
@@
   \textbf{Reduction principle for interaction-transmission association.} 
-  Consecutive fixation of modifier alleles that reduce interaction-transmission association in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
+  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
   When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
@@
   \textbf{Evolution of cooperation in a structured population.}
-	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~(a), or the transmission bias, $T_A-T_B$, on the x-axis of panel~(b).
-  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~(a) and in inequality~\ref{eq:cost_thresholds_v_threshold} for~(b).
-	The inset in panel~(b) focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
-	This stochastic polymorphism is illustrated in panel (c), which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~(b).
+	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~\textbf{(a)}, or the transmission bias, $T_A-T_B$, on the x-axis of panel~\textbf{(b)}.
+  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
+	The inset in panel~\textbf{(b)} focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
+	This stochastic polymorphism is illustrated in panel~\textbf{(c)}, which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~\textbf{(b)}.
   In all cases, the population evolves on a 100-by-100 grid.
@@
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
-  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$;
+  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
   \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
-  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$;
+  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
   \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
@@
   \textbf{Evolution of cooperation in a structured population with local selection.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel (a), or the transmission bias $T_A-T_B$ on the x-axis of panel (b).
-  The population evolves on a 100-by-100 grid.
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
   Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
   Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for panel~(a) and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel (b).
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
   The population evolves on a 100-by-100 grid.
@@
   50 simulations were executed for each parameter set.
-  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$;
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
-  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$;
+  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
   }

### 2020-11-30 ms/main.tex
appD proof - MWF, edited by YR

@@
 \newcommand{\cj}{\mathbf{J}}
-\newcommand{\ci}{I}
+\newcommand{\ci}{\mathbf{I}}
+\DeclareMathOperator{\sign}{sign}
 
@@
 
-The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
-$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1} as
+The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+$\cl^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\cl^*_{in}$ and $\cl^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
+The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1}, with $\bar{w}^*=1+(b-c)\tilde{p}^*$ as the stable population mean fitness,
 \begin{equation} \label{eq:external_stability_matrix}
 \begin{aligned}
-&\mathbf{L}^*_{ex} = 
+&\cl^*_{ex} = 
  \frac{1}{\bar{w}^*} \begin{bmatrix}
-	 X &
-	 Y \\
-	 Z &
-	 Q 
+	 l_{1 1} &
+	 l_{1 2} \\
+	 l_{2 1} &
+	 l_{2 2} 
 \end{bmatrix} = 
@@
 
-%\begin{equation} \label{eq:partial_derivatives}
-%  \begin{aligned}
-%%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
-%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
-%  b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
-%%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
-%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
-%  b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
-%% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
-%  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
-%  b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) + (1 - c) T_B (1 - \tilde{p}^*) \;,\\
-%%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
-%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
-%  b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* + 1 - T_A \tilde{p}^* \;.
-%  \end{aligned}
+Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\cl^*_{ex}$.
+This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\cl^*_{ex}$ is real and positive.
+Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
+The eigenvalues of $\cl^*_{ex}$ are the roots of the characteristic polynomial, $R(\lambda)$,
+%\begin{equation}\label{char_poly}
+%R(\lambda) = 
+%\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;,
 %\end{equation}
-
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$.
-This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\mathbf{L}^*_{ex}$ is real and positive.
-Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
-The eigenvalues of $\mathbf{L}^*_{ex}$ are the roots of the characteristic polynomial, 
-\begin{equation}\label{char_poly}
-R(\lambda) = 
-\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;,
-\end{equation}
-where $X$, $Y$, $Z$, and $Q$ are defined in \autoref{eq:external_stability_matrix}.
-%At $\lambda = 1$ the characteristic polynomial is equal to:
-%\begin{equation} \label{eq:characteristic_at_1}
-%  1-\frac{X+Q}{\bar{w}} + \frac{XQ-YZ}{\bar{w}^2}.
+%where $X$, $Y$, $Z$, and $Q$ are defined in \autoref{eq:external_stability_matrix}.
+which is a quadratic with a positive leading coefficient.
+Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
+Thus, a sufficient condition for external instability of $\vec{\tilde{p}^*}$ is $R(1) < 0$.
+%\begin{equation} \label{eq:R1_negative}
+%\begin{aligned}
+%R(1) < 0 \Leftrightarrow 
+%1 - \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} < 0 \Leftrightarrow 
+%\bar{w^*}^2 - \bar{w^*} (X+Q) + XQ - YZ < 0 \;.
+%\end{aligned}
 %\end{equation}
-%Because the discriminant of $R(\lambda)$ is positive, 
-%\begin{equation} \label{eq:delta}
-%  \Delta = 
-%  %\frac{(X+Q)^2}{\bar{w}^2}-\frac{4XQ-4YZ}{\bar{w}^2}=
-%  \frac{(X-Q)^2+4YZ}{\bar{w}^2} > 0 \;,
-%\end{equation}
-%it has two real roots.
-The characteristic polynomial $R(\lambda)$ is a quadratic with a positive leading coefficient.
-Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
-Thus, a sufficient condition for external instability of $\vec{\tilde{p}^*}$ is
-\begin{equation} \label{eq:R1_negative}
-\begin{aligned}
-R(1) < 0 \Leftrightarrow 
-1 - \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} < 0 \Leftrightarrow 
-\bar{w^*}^2 - \bar{w^*} (X+Q) + XQ - YZ < 0 \;.
-\end{aligned}
-\end{equation}
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that inequality~\ref{eq:R1_negative} is true if and only if
-\begin{equation} \label{eq:alpha2_alpha1_intermediate}
-\begin{aligned}
-\alpha_2 \big(b T_{A} + (T_A-T_B) - c(1-T_B)\big) <
-\alpha_1 \big(b T_{A} + (T_A-T_B) - c(1-T_B)\big) \;.
-\end{aligned}
-\end{equation}
-We assumed $c<\gamma_1$, that is,
+
+$R(\lambda)$ is defined as a determinant, $R(\lambda)=\det(\cl^*_{ex} - \lambda \ci)$, where $\ci$ is the 2-by-2 identify matrix. 
+Since multiplication by a positive doesn't change the sign, and using the properties of the determinant, 
+\begin{equation} \label{eq:signR1}
+\begin{aligned}
+\sign R(1) =
+& \sign\det(\cl^*_{ex} - \ci) =
+  \sign (\bar{w}^*)^2 \det(\cl^*_{ex} - \ci) = \\
+& \sign \det(\bar{w}^*\cl^*_{ex} - \bar{w}^* \ci) =
+  \sign \det\begin{bmatrix} l_{1 1} - \bar{w}^* & l_{1 2} \\ l_{2 1} & l_{2 2} - \bar{w}^* \end{bmatrix} \;,
+\end{aligned}
+\end{equation}
+where $l_{i j}$ are defined in \autoref{eq:external_stability_matrix}.
+Adding the second row in \autoref{eq:signR1} to the first row,  which does not change the determinant, and substituting $\bar{w}^*=1+(b-c)\tilde{p}^*$, we get
+\begin{equation} 
+\begin{aligned}
+\sign R(1) =
+& \sign\det\begin{bmatrix}
+	 -c(1-\tilde{p}^*) &&
+	 c \tilde{p}^* \\
+	 (1-\tilde{p}^*)\big[(1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* \big] &&
+	 \tilde{p}^*\big[-(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c\big]
+\end{bmatrix} = \\
+& \sign \Bigg[c \tilde{p}^* (1-\tilde{p}^*) \cdot \det\begin{bmatrix}
+	 -1 &&
+	 1 \\
+	 (1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* &&
+	 -(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c
+\end{bmatrix}\Bigg] = \\
+& \sign\det\begin{bmatrix}
+	 -1 &&
+	 1 \\
+	 (1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* &&
+	 -(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c
+\end{bmatrix} \;,
+\end{aligned}
+\end{equation}
+since $c>0$, $0<\tilde{p}^*<1$.
+That is, 
+\begin{equation}
+\begin{aligned}
+\sign R(1) = 
+&\sign\Big[
+(1+b\tilde{p}^*)T_A + b\alpha_2 T_A (1-\tilde{p}^*) - c - 
+(1+b\tilde{p}^*-c)T_B + b\tilde{p}^* \alpha_2 T_B \Big]
+= \\
+&\sign\Big[(1+b(1-\alpha_2)\tilde{p}^*)(T_A-T_B) + b\alpha_2 T_A - c (1-T_B) \Big]\;.
+\end{aligned}
+\end{equation}
+Substituting $\tilde{p}^*$ from \autoref{eq:p_tilde_star_alpha_1}, we get
+\begin{equation} \label{eq:R1_less}
+\begin{aligned}
+R(1)<0 \Leftrightarrow
+&\big[c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)\big] \frac{1-\alpha_2}{1-\alpha_1} - c (1-T_B) + b\alpha_2 T_A  + (T_A-T_B) < 0 \Leftrightarrow \\
+&(1-\alpha_2)\big[c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)\big] < (1-\alpha_1)\big[c (1-T_B) - b\alpha_2 T_A  - (T_A-T_B) \big] \Leftrightarrow \\
+& - b \alpha_1 T_A -\alpha_2 c(1-T_B) +\alpha_2(T_A - T_B) < 
+  - b\alpha_2 T_A -\alpha_1 c (1-T_B) +\alpha_1 (T_A-T_B)  \Leftrightarrow \\
+& \alpha_1 \big[c (1-T_B) - b T_A-(T_A-T_B)\big]  < 
+  \alpha_2 \big[c(1-T_B)-b T_A -(T_A - T_B)\big] \Leftrightarrow \\
+& \alpha_1 \big[b T_A + (T_A-T_B) - c (1-T_B)\big]  > 
+  \alpha_2 \big[b T_A + (T_A-T_B) - c (1-T_B)\big] \;.
+\end{aligned}
+\end{equation}
+We assumed $c<\gamma_1$, and since $0 \le \alpha_1 \le 1$,
 \begin{equation} \label{eq:c_gamma1_utility}
@@
 0 &< b \alpha_1 T_A + (T_A-T_B) - c(1-T_B) \; \Rightarrow \\
-0 &< b T_A + (T_A-T_B) - c(1-T_B) \;,
-\end{aligned}
-\end{equation}
-since $0 \le \alpha_1 \le 1$.
-Therefore, combining inequalities \ref{eq:R1_negative}, \ref{eq:alpha2_alpha1_intermediate}, and \ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_2 < \alpha_1$.
-This is a sufficient condition for external instability.
-So, if $\alpha_2$, the interaction-transmission association of the invading modifier allele $m$, is less than $\alpha_1$, the interaction-transmission association of the resident allele $M$, then invasion will be successful.
+0 &< b T_A + (T_A-T_B) - c(1-T_B) \;.
+\end{aligned}
+\end{equation}
+
+Combining inequalities~\ref{eq:R1_less} and~\ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_1 > \alpha_2$. This is a sufficient condition for external instability. 
+Therefore, if $\alpha_2$, the interaction-transmission association of the invading modifier allele $m$, is less than $\alpha_1$, the interaction-transmission association of the resident allele $M$, then invasion will be successful.
 
 Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-However, we numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_2<\alpha_1$.
+However, we numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_1>\alpha_2$.
 

### 2020-11-30 ms/main.tex
minor changes to app D by MWF

@@
 
-$R(\lambda)$ is defined as a determinant, $R(\lambda)=\det(\cl^*_{ex} - \lambda \ci)$, where $\ci$ is the 2-by-2 identify matrix. 
-Since multiplication by a positive doesn't change the sign, and using the properties of the determinant, 
+$R(\lambda)$ is defined as a determinant, $R(\lambda)=\det(\cl^*_{ex} - \lambda \ci)$, where $\ci$ is the 2-by-2 identity matrix. 
+Since multiplication by a positive factor doesn't change the sign, and using the properties of the determinant,  we have
 \begin{equation} \label{eq:signR1}
@@
 
-Combining inequalities~\ref{eq:R1_less} and~\ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_1 > \alpha_2$. This is a sufficient condition for external instability. 
+Combining inequalities~\ref{eq:R1_less} and~\ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_1 > \alpha_2$, which is a sufficient condition for external instability. 
 Therefore, if $\alpha_2$, the interaction-transmission association of the invading modifier allele $m$, is less than $\alpha_1$, the interaction-transmission association of the resident allele $M$, then invasion will be successful.
@@
 Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-However, we numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_1>\alpha_2$.
+However, we have numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_1>\alpha_2$.
 

### 2021-01-04 ms/main.tex
remove modifier work to meet maximum pages limit

--- 2020-11-24 ms/main.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Evolution of interaction-transmission association}
-
-We now focus on the evolution of interaction-transmission association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
-Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}), see \autoref{fig:equilibria_v1}b.
-The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
-Therefore, if interaction-transmission association increases, the population mean fitness also increases.
-But can this population-level advantage lead to the evolution of interaction-transmission association?
-
-To answer this question, we extend our model to include a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines interaction-transmission association, but has no direct effect on fitness.
-The modifier locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
-Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
-We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain the following result.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}[Reduction principle for interaction-transmission association] 
-\label{result:evol_social_association}
-From a stable polymorphism between cooperation and defection, a modifier allele can successfully invade the population if it decreases the interaction-transmission association $\alpha$.
-\end{result}
-
-The full analysis is in Appendix~\ref{sec:appendixD}.
-Note that this reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we assume that modifier alleles with decreased interaction-transmission association appear and invade the population from time to time, then interaction-transmission association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
-This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c).
-Thus, we can expect interaction-transmission association to eventually approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both the cost of cooperation and interaction-transmission association are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
-
-We find that stronger interaction-transmission association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, interaction-transmission association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
-Without interaction-transmission association, the benefit of cooperation cannot facilitate its evolution, and cooperation can only succeed if horizontal transmission is biased in its favor.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Reduction principle} \label{sec:appendixD}
-
-We assume here that $v=1$, i.e. no oblique transmission, and therefore $\hat{p}=\tilde{p}$.
-Denote the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ by $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
-The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
-\begin{equation} \label{eq:next_gen_p_1}
-  \begin{aligned}
-	% p1
-  \bar{w}\tilde{p}_1' = 
-  & \tilde{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \tilde{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) \;+ \\
-  & \tilde{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) \;+ \\
-  & \tilde{p}_2(1-x)x(1-\alpha_1)T_A \;,
-\\
-	% p2
-  \bar{w}\tilde{p}_2' = 
-  & \tilde{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \;+ \\
-  & \tilde{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \tilde{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) \;+ \\
-& \tilde{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;, 
-\\
-	% p3
-  \bar{w}\tilde{p}_3' =
-  & \tilde{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \tilde{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) \;+ \\
-  & \tilde{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) \;+ \\
-  & \tilde{p}_4(1-x) x (1-\alpha_2)T_A \;, 
-\\
-	% p4
-  \bar{w}\tilde{p}_4' =
-  & \tilde{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B \;+ \\
-  & \tilde{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \tilde{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) \;+ \\
-  & \tilde{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \;,
-  \end{aligned}
-\end{equation}
-%which we can write as 
-%\begin{equation}
-%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
-%\end{equation}
-where $x=\tilde{p}_1+\tilde{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-
-The equilibrium where only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
-\begin{equation} \label{eq:p_tilde_star_alpha_1}
-\tilde{p}^*=
-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)} \;,
-\end{equation}
-setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
-When $v=1$, $\tilde p^*$ is a feasible polymorphism ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
-
-The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
-$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1} as
-\begin{equation} \label{eq:external_stability_matrix}
-\begin{aligned}
-&\mathbf{L}^*_{ex} = 
- \frac{1}{\bar{w}^*} \begin{bmatrix}
-	 X &
-	 Y \\
-	 Z &
-	 Q 
-\end{bmatrix} = 
-\frac{1}{\bar{w}^*} \begin{bmatrix}
-\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
-\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) 
-\end{bmatrix} \;= \\
-& \frac{1}{\bar{w}^*} \begin{bmatrix}
-		(1+b \tilde{p}^* -c)(1-T_B(1-\tilde{p}^*)) + b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) & 
-		(1+b \tilde{p}^*) T_A \tilde{p}^* + b \tilde{p}^* \alpha_2 T_A(1-\tilde{p}^*) \\
-		(1+b \tilde{p}^* - c) T_B(1-\tilde{p}^*) - b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) &
-		(1+b \tilde{p}^*) (1-T_A \tilde{p}^*) - b \tilde{p}^* \alpha_2 T_A (1-\tilde{p}^*) \\
-  	\end{bmatrix} \;.
-\end{aligned}
-\end{equation}
-
-%\begin{equation} \label{eq:partial_derivatives}
-%  \begin{aligned}
-%%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
-%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
-%  b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
-%%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
-%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
-%  b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
-%% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
-%  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = 
-%  b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) + (1 - c) T_B (1 - \tilde{p}^*) \;,\\
-%%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
-%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 
-%  b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* + 1 - T_A \tilde{p}^* \;.
-%  \end{aligned}
-%\end{equation}
-
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$.
-This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\mathbf{L}^*_{ex}$ is real and positive.
-Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
-The eigenvalues of $\mathbf{L}^*_{ex}$ are the roots of the characteristic polynomial, 
-\begin{equation}\label{char_poly}
-R(\lambda) = 
-\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;,
-\end{equation}
-where $X$, $Y$, $Z$, and $Q$ are defined in \autoref{eq:external_stability_matrix}.
-%At $\lambda = 1$ the characteristic polynomial is equal to:
-%\begin{equation} \label{eq:characteristic_at_1}
-%  1-\frac{X+Q}{\bar{w}} + \frac{XQ-YZ}{\bar{w}^2}.
-%\end{equation}
-%Because the discriminant of $R(\lambda)$ is positive, 
-%\begin{equation} \label{eq:delta}
-%  \Delta = 
-%  %\frac{(X+Q)^2}{\bar{w}^2}-\frac{4XQ-4YZ}{\bar{w}^2}=
-%  \frac{(X-Q)^2+4YZ}{\bar{w}^2} > 0 \;,
-%\end{equation}
-%it has two real roots.
-The characteristic polynomial $R(\lambda)$ is a quadratic with a positive leading coefficient.
-Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
-Thus, a sufficient condition for external instability of $\vec{\tilde{p}^*}$ is
-\begin{equation} \label{eq:R1_negative}
-\begin{aligned}
-R(1) < 0 \Leftrightarrow 
-1 - \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} < 0 \Leftrightarrow 
-\bar{w^*}^2 - \bar{w^*} (X+Q) + XQ - YZ < 0 \;.
-\end{aligned}
-\end{equation}
-Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that inequality~\ref{eq:R1_negative} is true if and only if
-\begin{equation} \label{eq:alpha2_alpha1_intermediate}
-\begin{aligned}
-\alpha_2 \big(b T_{A} + (T_A-T_B) - c(1-T_B)\big) <
-\alpha_1 \big(b T_{A} + (T_A-T_B) - c(1-T_B)\big) \;.
-\end{aligned}
-\end{equation}
-We assumed $c<\gamma_1$, that is,
-\begin{equation} \label{eq:c_gamma1_utility}
-\begin{aligned}
-c &< \gamma_1 = \frac{b \alpha_1 T_A + (T_A-T_B)}{1-T_B} \; \Leftrightarrow \\
-%c(1-T_B) < b \alpha_1 T_A + (T_A-T_B) \Leftrightarrow \\
-0 &< b \alpha_1 T_A + (T_A-T_B) - c(1-T_B) \; \Rightarrow \\
-0 &< b T_A + (T_A-T_B) - c(1-T_B) \;,
-\end{aligned}
-\end{equation}
-since $0 \le \alpha_1 \le 1$.
-Therefore, combining inequalities \ref{eq:R1_negative}, \ref{eq:alpha2_alpha1_intermediate}, and \ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_2 < \alpha_1$.
-This is a sufficient condition for external instability.
-So, if $\alpha_2$, the interaction-transmission association of the invading modifier allele $m$, is less than $\alpha_1$, the interaction-transmission association of the resident allele $M$, then invasion will be successful.
-
-Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-However, we numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_2<\alpha_1$.
-
 \end{appendices}
@@
 
-%%% Figure: Invasion
-\begin{figure}[p]
-  \centering
-   \includegraphics[scale=0.5]{Figures/invasion.eps}
-  \caption{
-  \textbf{Reduction principle for interaction-transmission association.} 
-  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
-  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
-  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
-  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
-  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
-  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
-  }
-  \label{fig:invasion}
-\end{figure}
-
 %%% Figure: Spatial model - global selection

### 2021-01-06 ms/main.tex
reduced num of words; moved invasion fig to SI; moved appendices to SI

--- 2020-11-30 ms/main.tex
@@
 % less space before sections 
-% \@startsection {NAME}{LEVEL}{INDENT}{BEFORESKIP}{AFTERSKIP}{STYLE} 
-%            optional * [ALTHEADING]{HEADING} 
-\makeatletter
- \renewcommand\section{\@startsection {section}{1}{\z@}%
-     {-2.5ex \@plus -1ex \@minus -.2ex}%
-     {1.3ex \@plus.2ex}%
-    {\Large\bfseries}}
+% https://tex.stackexchange.com/a/101126
+\usepackage{titlesec}
+\titlespacing*{\section}{0pt}{0.5\baselineskip}{0\baselineskip}
+\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0\baselineskip}
 
@@
 Nevertheless, cooperative behavior appears to occur in many animals~\citep{dugatkin1997cooperation}, including humans, primates~\citep{jaeggi2013natural},  rats~\citep{rice1962altruism}, birds~\citep{stacey1990cooperative,krams2008experimental}, and lizards~\citep{sinervo2006self}.
-Evolution of cooperative behavior has been an important focus of research in evolutionary theory since at least the 1930s~\citep[Appendix]{Haldane1932book}.
-
+Evolution of cooperative behavior has been an important focus of research in evolutionary theory since at least the 1930s~\citep{Haldane1932book}.
 Since the work of  \citet{hamilton1964genetical} and \citet{axelrod1981evolution}, theories for the evolution of cooperative and altruistic behaviors have been intertwined often under the rubric of \emph{kin selection}.
@@
 Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
-This further emphasizes that treatment of cooperation as a cultural trait, rather than a genetic one, can lead to a broader understanding of its evolutionary dynamics.
 
@@
 Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
-
 \begin{equation} \label{eq:vertical_oblique_transmission}
@@
 Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
-
 \begin{equation}\label{eq:horizontal}
 \begin{aligned}
-\hat{p} =
-& \tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \;= \\
-& v \tilde{p} + (1-v) p \;.
-\end{aligned}
-\end{equation}
-
+\hat{p} \;=
+\tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \;= 
+v \tilde{p} + (1-v) p \;.
+\end{aligned}
+\end{equation}
 Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
@@
 \begin{aligned}
-p' = 
+p' \;= \;
 & \hat{p}^2 \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
 & \hat{p}(1-\hat{p}) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
-& (1-\hat{p})\hat{p} \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+ \\
-& (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
-\end{aligned}
-\end{equation}
-which simplifies to
-\begin{equation}\label{eq:nextgen_adults_slimpify}
-p' = \hat{p}^2(T_B-T_A) + \hat{p}(1+T_A-T_B) \;.
-\end{equation}
-
+& (1-\hat{p})\hat{p} \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+ 
+(1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \\
+=\; & \hat{p}^2(T_B-T_A) \;+\; \hat{p}(1+T_A-T_B) \;.
+\end{aligned}
+\end{equation}
 The frequency of $A$ among parents (i.e. after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
@@
 & \hat{p}(1-\hat{p}) (1-c) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
-& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+ \\
-& (1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
+& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+\; 
+(1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
 \end{aligned}
@@
 %\end{equation}
-\autoref{eq:nextgen_parents} can be simplified to
-\begin{equation}\label{eq:nextgen_parents_simplified}
-\begin{aligned}
-\bar{w} \tilde{p}' =
-& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] \;+ \\
-& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] \;+ \\
-& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A \;+ \\
-& (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
-\end{aligned}
-\end{equation}
+%\autoref{eq:nextgen_parents} can be simplified to
+%\begin{equation}\label{eq:nextgen_parents_simplified}
+%\begin{aligned}
+%\bar{w} \tilde{p}' =
+%& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] \;+ \\
+%& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] \;+ \\
+%& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A \;+ \\
+%& (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
+%\end{aligned}
+%\end{equation}
 %where $\hat{p}=v\tilde{p}+(1-v)p$.
-Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ from \autoref{eq:nextgen_parents_simplified} and obtain
+Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults} and $\tilde{p}'$ from \autoref{eq:nextgen_parents} and obtain
 \begin{equation} \label{eq:nextgen_juveniles}
@@
 & \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1+b)\big(\hat{p}(1-\alpha) + \alpha \big) T_A \Big] \;+ \\
-& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \;+ \\
-& (1-v)\hat{p}^2(T_B-T_A) \;+ \\
-& (1-v)\hat{p}(1+T_A-T_B) \;.
+& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \;+\;
+(1-v)\hat{p}^2(T_B-T_A) \;+\;
+(1-v)\hat{p}(1+T_A-T_B) \;.
 \end{aligned}
@@
 
-We determine the equilibria of the model in \autoref{eq:nextgen_juveniles}, namely, solutions of $\hat{p}' = \hat{p}$, and analyze their local stability.
+We determine the equilibria of the model in \autoref{eq:nextgen_juveniles}
+%namely, solutions of $\hat{p}' = \hat{p}$, 
+and analyze their local stability.
 We then analyze the evolution of a modifier of interaction-transmission association,~$\alpha$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}[Equilibria and stability] \label{result:vert_obli_hori}
+\begin{result}%[Equilibria and stability]
+\label{result:vert_obli_hori}
 With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
@@
 \end{result}
-These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the full analysis is in Appendix~\ref{sec:appendixB}.
+These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Condition on $c$ for cooperation to increase when rare, i.e., $\hat{p}'>p$ near $p=0$]
+\begin{remark}%[Condition on $c$ for cooperation to increase when rare, i.e., $\hat{p}'>p$ near $p=0$]
 \label{remark:rarity}
@@
 In general, this condition cannot be formulated in the form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
-When there is no horizontal transmission bias, $T_A=T_B$, the following applies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-From Result \ref{result:vert_obli_hori} and inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, if horizontal transmission is unbiased, $T=T_A=T_B$, then cooperation will take over the population from any initial frequency if the cost is low enough,
+If $T_A=T_B$, then, from Result~\ref{result:vert_obli_hori} and inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation will take over the population from any initial frequency if the cost is low enough,
 \begin{equation}
@@
 \autoref{fig:equilibria_v1}a illustrates this condition (for $v=1$), which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
-Importantly, the benefit of cooperation, $b$, does not affect the evolution of cooperation in the absence of interaction-transmission association, and the outcome is determined only by  cultural transmission.
+In this case, the benefit of cooperation, $b$, does not affect the evolution of cooperation, and the outcome is determined only by  cultural transmission.
 Further, inequality~\ref{eq:unequal_transmission_from_rarity_general_case} shows that with perfect interaction-transmission association ($\alpha=1$), cooperation will increase when rare if
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}[Condition on interaction-transmission association $\alpha$ for cooperation to increase when it is rare]
+\begin{remark}%[Condition on interaction-transmission association $\alpha$ for cooperation to increase when it is rare]
 \label{remark:intermediate_association_res3}
@@
 With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in the figures). 
-With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if interaction-transmission association is high, $a_1<\alpha$ (green area with $T_A<T_B$), and can also increase when rare and reach stable polymorphism if interaction-transmission association is intermediate, $a_2<\alpha<a_1$ (yellow area).
-Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if interaction-transmission association is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if $\alpha$ is large enough, $a_1<\alpha$ (green area with $T_A<T_B$), and can reach stable polymorphism if $\alpha$ is intermediate, $a_2<\alpha<a_1$ (yellow area).
+Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if $\alpha$ is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
 
 Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on $a_1$ and $a_2$ depends on the horizontal transmission bias.
-That is, with horizontal bias for cooperation, $T_A>T_B$, evolution of cooperation is facilitated by oblique transmission, whereas with horizontal bias for defection, $T_A<T_B$, evolution of cooperation is facilitated by vertical transmission.
-This is demonstrated in Figures~\ref{fig:equilibria}c and~\ref{fig:equilibria}d.
+That is, if $T_A>T_B$, then evolution of cooperation is facilitated by oblique transmission, whereas if $T_A<T_B$, then evolution of cooperation is facilitated by vertical transmission (Figures~\ref{fig:equilibria}c and~\ref{fig:equilibria}d).
 \\
@@
 
-With only vertical transmission ($v=1$), inequality~\ref{eq:unequal_transmission_from_rarity_general_case} entails that cooperation will increase when rare if
+With only vertical transmission ($v=1$), from inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation increases when rare if
 \begin{equation} \label{eq:vert_hori}
@@
 $p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely $T_A > T_B$.
-That is, in the absence of vertical transmission, selection plays no role in the evolution of cooperation (i.e., $b$ and $c$ do not affect $\hat p'$).
-The dynamics are determined solely by differential horizontal transmission of the two phenotypes, namely, the relative tendency of each phenotype to be horizontally transmitted to peers.
+That is, if $v=0$, then selection plays no role in the evolution of cooperation (i.e., $b$ and $c$ do not affect $\hat p'$).
+The dynamics are determined solely by differential horizontal transmission of the two phenotypes.
 With no bias in horizontal transmission, $T_A = T_B$, phenotype frequencies do not change, $\hat p'=\hat p$.
@@
 The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
-Therefore, if interaction-transmission association increases, the population mean fitness also increases.
-But can this population-level advantage lead to the evolution of interaction-transmission association?
-
-To answer this question, we extend our model to include a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines interaction-transmission association, but has no direct effect on fitness.
-The modifier locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
+Therefore, $\bar{w}^*$ increases as $\alpha$ increases.
+But can this population-level advantage lead to the evolution of $\alpha$?
+
+To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $alpha$ but has no direct effect on fitness.
+This locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
 Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}[Reduction principle for interaction-transmission association] 
+\begin{result}%[Reduction principle for interaction-transmission association] 
 \label{result:evol_social_association}
@@
 
-The full analysis is in Appendix~\ref{sec:appendixD}.
-Note that this reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we assume that modifier alleles with decreased interaction-transmission association appear and invade the population from time to time, then interaction-transmission association will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
+The analysis is in Appendix~\ref{sec:appendixD}.
+This reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
+Furthermore, if we a modifier allele that decreases $\alpha$ appears and invades the population from time to time, then the value of $\alpha$ will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
 This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c). 
-Thus, we can expect interaction-transmission association to eventually approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
+Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
 
@@
 Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~\ref{eq:unequal_transmission_from_rarity_general_case},
-\begin{equation}
+$
 c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;,
-\end{equation}
+$
 namely, the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
 This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
-Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both the cost of cooperation and interaction-transmission association are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
+Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both $c$ and $\alpha$ are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
 
 We find that stronger interaction-transmission association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, interaction-transmission association is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
-Without interaction-transmission association, the benefit of cooperation cannot facilitate its evolution, and cooperation can only succeed if horizontal transmission is biased in its favor.
+Nevertheless, when cooperation and defection coexist, $\alpha$ is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
+With $\alpha=0$, the benefit of cooperation cannot facilitate its evolution; it can only succeed if horizontal transmission is biased in its favor.
 
@@
 
-The conditions derived from our deterministic model provide a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
+Our deterministic model provides a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
 In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
@@
 and Minerva Stiftung Center for Lab Evolution (YR).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Bibliography
+\bibliographystyle{rsnat}
+\bibliography{bib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
+%%%%%%%%%% Tables %%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Tables}
+
+%%%% Table: payoff matrix
+%\bigskip
+%\begin{table}[h]
+%\centering
+%\caption{\textbf{Payoff matrix for prisoner's dilemma.}}
+%\begin{tabular}{lll}
+%\toprule
+%           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
+%$\phi_1=A$ & $1+b-c$ & $1-c$ \\
+%$\phi_1=B$ & $1+b$   & $1$
+%\\ \bottomrule
+%\end{tabular}
+%\label{table:prisoner_payoff}
+%\caption*{
+%The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
+$0<c<1$ and $c<b$.
+%}
+%\end{table}
+%\bigskip
+%%%%
+
+%%% Table: interactions
+\bigskip
+\begin{table}[h]
+\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
+\begin{tabular}{@{}llllll@{}}
+\toprule
+\multirow{2}{*}{Phenotype $\phi_1$} &
+  \multirow{2}{*}{Phenotype $\phi_2$} &
+  \multirow{2}{*}{Frequency} &
+  \multirow{2}{*}{Fitness of $\phi_1$} &
+  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
+    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
+$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
+$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
+$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
+\end{tabular}
+\label{table:interactions}
+\end{table}
+\bigskip
+%%%
+
+%%% Table: variables and parameters
+\bigskip
+\begin{table}[h]
+\centering
+\caption{\textbf{Model variables and parameters.}
+}
+\begin{tabular}{lll}
+\toprule
+Symbol & Description & Values \\ \cmidrule(r){1-3}
+$A$ & Cooperator phenotype & \\
+$B$ & Defector phenotype & \\
+$p$ & Frequency of phenotype $A$ among adults & $[0,1]$ \\
+$\tilde p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
+$\hat p$ & Frequency of phenotype $A$ among juveniles & $[0,1]$ \\
+$v$ & Vertical transmission rate & $[0,1]$ \\
+$c$ & Cost of cooperation & $(0,1)$ \\
+$b$ & Benefit of cooperation & $c<b$ \\
+$\alpha$ & Probability of interaction-transmission association & $[0,1]$ \\
+$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $(0,1)$ \\
+\\ \bottomrule
+\end{tabular}
+\label{table:vars_params}
+\end{table}
+%\bigskip
+%%%
+
+\newpage
+
+%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Figures}
+%%% Figure: model illustration
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
+  \caption{\textbf{Model illustration.} 
+  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
+Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
+  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
+  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
+    }
+  \label{fig:illustration}
+\end{figure}
+
+%%% Figure: thresholds figure - vertical and oblique
+
+\begin{figure}[p]
+  \centering       
+    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
+    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
+    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
+    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
+    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
+    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
+	In all cases the vertical transmission rate $v$ is on the x-axis.
+	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (Eqs.~\ref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
+    (\textbf{c-d})~Interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
+    Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
+    Here, $T_A = 0.5$, and
+    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
+    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
+    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
+    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
+    }
+    \label{fig:equilibria}
+\end{figure}
+
+%%% Figure: thresholds figure - only vertical
+
+\begin{figure}[p]
+  \centering       
+    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
+	  ~
+    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
+    ~
+    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
+    ~
+    \includegraphics[width=0.48\textwidth]{coexistence_without_oblique.eps}
+    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
+    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
+unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
+    (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
+    In panels \textbf{(a)} and \textbf{(b)}, the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
+	In panel \textbf{(c)}, interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
+    Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
+    \textbf{(d)}~Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
+    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$). % todo ref eq 12
+    The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
+    Black circles show the three equilibria.
+  	}
+    \label{fig:equilibria_v1}
+\end{figure}
+
+%%% Figure: Spatial model - global selection
+\begin{figure}[p]
+  \centering
+	\includegraphics[width=0.3\textwidth]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
+    ~
+	\includegraphics[width=0.3\textwidth]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
+    ~
+    \includegraphics[width=0.36\textwidth]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
+  \caption{
+  \textbf{Evolution of cooperation in a structured population.}
+	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~\textbf{(a)}, or the transmission bias, $T_A-T_B$, on the x-axis of panel~\textbf{(b)}.
+  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
+	The inset in panel~\textbf{(b)} focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
+	This stochastic polymorphism is illustrated in panel~\textbf{(c)}, which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~\textbf{(b)}.
+  In all cases, the population evolves on a 100-by-100 grid.
+  Cooperation and horizontal transmission are both local between neighboring sites, and each site has 8 neighbors.
+  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
+  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
+  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
+  \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
+  }
+  \label{fig:spatial}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section*{\huge{Supplementary material}}
+\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Bibliography
-\bibliographystyle{rsnat}
-\bibliography{bib}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+% Supporting figures
 \newpage
-
-%%%%%%%%%% Tables %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Tables}
-
-%%%% Table: payoff matrix
-%\bigskip
-%\begin{table}[h]
-%\centering
-%\caption{\textbf{Payoff matrix for prisoner's dilemma.}}
-%\begin{tabular}{lll}
-%\toprule
-%           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
-%$\phi_1=A$ & $1+b-c$ & $1-c$ \\
-%$\phi_1=B$ & $1+b$   & $1$
-%\\ \bottomrule
-%\end{tabular}
-%\label{table:prisoner_payoff}
-%\caption*{
-%The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
-$0<c<1$ and $c<b$.
-%}
-%\end{table}
-%\bigskip
-%%%%
-
-%%% Table: interactions
-\bigskip
-\begin{table}[h]
-\caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
-\begin{tabular}{@{}llllll@{}}
-\toprule
-\multirow{2}{*}{Phenotype $\phi_1$} &
-  \multirow{2}{*}{Phenotype $\phi_2$} &
-  \multirow{2}{*}{Frequency} &
-  \multirow{2}{*}{Fitness of $\phi_1$} &
-  \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
-    &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
-$A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-$B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
-$B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
-\end{tabular}
-\label{table:interactions}
-\end{table}
-\bigskip
-%%%
-
-%%% Table: variables and parameters
-\bigskip
-\begin{table}[h]
-\centering
-\caption{\textbf{Model variables and parameters.}
-}
-\begin{tabular}{lll}
-\toprule
-Symbol & Description & Values \\ \cmidrule(r){1-3}
-$A$ & Cooperator phenotype & \\
-$B$ & Defector phenotype & \\
-$p$ & Frequency of phenotype $A$ among adults & $[0,1]$ \\
-$\tilde p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
-$\hat p$ & Frequency of phenotype $A$ among juveniles & $[0,1]$ \\
-$v$ & Vertical transmission rate & $[0,1]$ \\
-$c$ & Cost of cooperation & $(0,1)$ \\
-$b$ & Benefit of cooperation & $c<b$ \\
-$\alpha$ & Probability of interaction-transmission association & $[0,1]$ \\
-$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $(0,1)$ \\
-\\ \bottomrule
-\end{tabular}
-\label{table:vars_params}
-\end{table}
-%\bigskip
-%%%
-
-\newpage
-
-%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Figures}
-%%% Figure: model illustration
+\section*{Supporting figures}
+
+%%% Figure: Invasion
 \begin{figure}[h]
-  \centering
-  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
-  \caption{\textbf{Model illustration.} 
-  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
-Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
-  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
-  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
-    }
-  \label{fig:illustration}
-\end{figure}
-
-%%% Figure: thresholds figure - vertical and oblique
-
-\begin{figure}[p]
-  \centering       
-    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
-    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
-    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
-unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-	In all cases the vertical transmission rate $v$ is on the x-axis.
-	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (Eqs.~\ref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d})~Interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
-    Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
-    Here, $T_A = 0.5$, and
-    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
-    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
-    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
-    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
-    }
-    \label{fig:equilibria}
-\end{figure}
-
-%%% Figure: thresholds figure - only vertical
-
-\begin{figure}[p]
-  \centering       
-    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
-	  ~
-    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
-    ~
-    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
-    ~
-    \includegraphics[width=0.48\textwidth]{coexistence_without_oblique.eps}
-    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
-    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
-unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-    (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
-    In panels \textbf{(a)} and \textbf{(b)}, the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
-	In panel \textbf{(c)}, interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
-    Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
-    \textbf{(d)}~Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
-    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$). % todo ref eq 12
-    The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
-    Black circles show the three equilibria.
-  	}
-    \label{fig:equilibria_v1}
-\end{figure}
-
-%%% Figure: Invasion
-\begin{figure}[p]
   \centering
@@
 \end{figure}
-
-%%% Figure: Spatial model - global selection
-\begin{figure}[p]
-  \centering
-	\includegraphics[width=0.3\textwidth]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
-    ~
-	\includegraphics[width=0.3\textwidth]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
-    ~
-    \includegraphics[width=0.36\textwidth]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
-  \caption{
-  \textbf{Evolution of cooperation in a structured population.}
-	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~\textbf{(a)}, or the transmission bias, $T_A-T_B$, on the x-axis of panel~\textbf{(b)}.
-  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
-	The inset in panel~\textbf{(b)} focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
-	This stochastic polymorphism is illustrated in panel~\textbf{(c)}, which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~\textbf{(b)}.
-  In all cases, the population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site has 8 neighbors.
-  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
-  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
-  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
-  \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
-  }
-  \label{fig:spatial}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-%\section*{Supplementary Material}
-\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
 

### 2021-01-23 ms/Thesis/thesis.tex
First commit

--- 2021-01-06 ms/main.tex
@@
 % TeX will automatically convert eps --> pdf in pdflatex
-\graphicspath{ {./Figures/} }
+\graphicspath{ {../Figures/} }
 \usepackage[labelfont=bf]{caption}
@@
 
-% less space before sections 
-% https://tex.stackexchange.com/a/101126
-\usepackage{titlesec}
-\titlespacing*{\section}{0pt}{0.5\baselineskip}{0\baselineskip}
-\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0\baselineskip}
+% Line Spacing 
+\linespread{1.25}
 
@@
 
+\tableofcontents
+\pagebreak
+
 % TODO change "scoail association" to "interaction-transmission association"
@@
 %%% Introduction
-\section*{Introduction}
+\section{Introduction}
 Cooperative behavior can reduce an individual's fitness and increase the fitness of its conspecifics or competitors~\citep{axelrod1981evolution}.
@@
 
+Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
+Cultural transmission may be  modeled as vertical, horizontal, or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
+from non-parental adults).
+Evolution under either of these transmission models can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
+Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior, the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by host-associated microbes.
+Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
+
+Here, we study models for the cultural evolution of cooperation that include both vertical and non-vertical transmission. 
+%We investigate these models using mathematical analysis and simulations.  
+In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
+For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission,
+or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
+Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
+
+\newpage
+\section{Related Work}
+
 \citet{Eshel1982} studied a related model for the evolution of cooperative behavior.
@@
 
-Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
 \citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission with kin selection and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
@@
 
-Cultural transmission may be  modeled as vertical, horizontal, or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
-from non-parental adults).
-Evolution under either of these transmission models can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior, the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by host-associated microbes.
-Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
-
-Here, we study models for the cultural evolution of cooperation that include both vertical and non-vertical transmission. 
-%We investigate these models using mathematical analysis and simulations.  
-In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
-For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission,
-or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Models
-\section*{Models}
+\newpage
+\section{Models}
 
@@
 %%% Results
-\section*{Results}
+\newpage
+\section{Results}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Evolution of cooperation}
+\subsection{Evolution of cooperation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Evolution of interaction-transmission association}
+\subsection{Evolution of interaction-transmission association}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Population structure}
+\subsection{Population structure}
 Interaction-transmission association may also emerge from population structure.
@@
 % Discussion
-\section*{Discussion}
+\newpage
+\section{Discussion}
 Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
@@
     \label{fig:equilibria}
+    %TODO update y label on c d
 \end{figure}
@@
     \label{fig:equilibria_v1}
+    %TODO update y label on c d
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section{Equilibria and stability} \label{sec:appendixB}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section{Effect of interaction-transmission association on mean fitness} \label{sec:appendixC}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section{Reduction principle} \label{sec:appendixD}
@@
   \centering
-   \includegraphics[scale=0.5]{Figures/invasion.eps}
+   \includegraphics[scale=0.5]{../Figures/invasion.eps}
   \caption{

### 2021-01-30 ms/Thesis/thesis.tex
Introduction - add group selection and reciprocity. Make figure inline

@@
 
+There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
+It has been suggested that kin selection to explain the cooperative behaviour of eusocial insects like the honey bee.
+The most significant argument against kin selection is that cooperation can evolve with zero relatedness \cite{wilson2005kin}.
+This makes Hamilton's rule incomplete according to Wilson \cite{wilson2005kin}.
+Foster et al.
+\cite{foster2006kin} reject this claim.
+They argue that altruism without relatedness can not evolve. They refer us to Hamilton who claimed that relatedness can arise without recent common ancestry. 
+Wilson also criticises kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions.
+On the other hand, Foster et al.
+\cite{foster2006kin} argue that kin selection does not ignore ecology.
+Hamilton’s rule shows that environmental factors causing a high benefit: cost ratio will favour cooperation.
+
+Beside kin selection, two more major theroies were suggested to explain to evolution of cooperation.
+
+\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation. 
+In \textit{direct reciprocity} there are a repeated encounters between the same two individuals.
+In every encounter, each player has a choice between cooperation and defection.
+If I cooperate now, you may cooperate later.
+Hence, it may pay off to cooperate.
+This game-theoretic framework is known as the repeated Prisoner's Dilemma. 
+Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit. 
+\begin{equation} \label{reciprocity}
+c<bw
+\end{equation}
+Direct reciprocity assumes that both players are in a position to cooperate.
+Direct reciprocity can not explain cooperation in asymmetric interactions.
+In humans, such interactions happen often, for example humans often donate money.
+\textit{Indirect reciprocity} has been suggested to explain this behavior. 
+Nowak \cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
+The money that "fuels the engines" of indirect reciprocity is reputation.
+However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.
+
+\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
+A common model for group selection work as is: the population is divided into groups.
+In each groups there are cooperators, which help to other group members and defectors which do not help.
+Individuals reproduce proportional to their fitness. Offspring are added to the same group.
+If a group reaches a certain size it can split to two groups. A group that grow faster will split more often. Groups of cooperators are growing faster than group of defectors.
+Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
+\begin{equation} \label{groupselection}
+\frac{b}{c}>1+\frac{n}{m}
+\end{equation}
+
+All three theories mentioned above assume that cooperation is genetically determined. This raise the question, is it possible that cooperation is determined by environmental or social influences.
 Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
@@
 Evolution under either of these transmission models can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior, the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by host-associated microbes.
-Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
 
@@
 
+Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior, the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by host-associated microbes.
+Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
+
+%%% Figure: model illustration
+\begin{figure}[pt]
+  \centering
+  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
+  \caption{\textbf{Model illustration.} 
+  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
+Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
+  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
+  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
+    }
+  \label{fig:illustration}
+\end{figure}
 
@@
 where fitness values are taken from \autoref{fig:illustration}a and \autoref{table:interactions}, and the population mean fitness is
-%\begin{equation} \label{eq:mean_fitness}
 $\bar{w} =  1 + \hat{p}(b-c)$.
-%\end{equation}
-%\autoref{eq:nextgen_parents} can be simplified to
-%\begin{equation}\label{eq:nextgen_parents_simplified}
-%\begin{aligned}
-%\bar{w} \tilde{p}' =
-%& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] \;+ \\
-%& \hat{p}(1-\hat{p}) (1-c) \big[\hat{p}(1-\alpha)T_B+1-T_B \big] \;+ \\
-%& (1-\hat{p})\hat{p} (1+b) \big[\hat{p}(1-\alpha) + \alpha \big] T_A \;+ \\
-%& (1-\hat{p})^2 \hat{p} (1-\alpha) T_A \;.
-%\end{aligned}
-%\end{equation}
-%where $\hat{p}=v\tilde{p}+(1-v)p$.
 Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults} and $\tilde{p}'$ from \autoref{eq:nextgen_parents} and obtain
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Results
-\newpage
-\section{Results}
-
-We determine the equilibria of the model in \autoref{eq:nextgen_juveniles}
-%namely, solutions of $\hat{p}' = \hat{p}$, 
-and analyze their local stability.
-We then analyze the evolution of a modifier of interaction-transmission association,~$\alpha$.
-Finally, we compare derived conditions to outcomes of stochastic simulations with a structured population.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolution of cooperation}
-
-The fixed points (equilibria) of  the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
-\begin{equation} \label{eq:general_equilibrium}
-  \hat{p}^* =  
-  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
-\end{equation}
-
-Define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
-\begin{equation} \label{eq:cost_thresholds_v_threshold} 
-\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
-\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}, \quad
-\hat v = \frac{T_B - T_A}{1-T_A} \;.
-\end{equation}
-
-Then we have the following result.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}%[Equilibria and stability]
-\label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
-
-% in gamma
-\begin{enumerate}
-\item \emph{Fixation of cooperation}: 
-	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or 
-	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \gamma_2$.
-\item \emph{Fixation of defection}: 
-    if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or 
-	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
-\item \emph{Stable polymorphism}: 
-    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
-    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
-\item \emph{Unstable polymorphism}:
-    if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
-\end{enumerate}
-
-\end{result}
-These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
-
-Much of the literature on evolution of cooperation focuses on conditions for  an initially rare cooperative phenotype to invade a population of defectors.
-The following remarks address this condition.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}%[Condition on $c$ for cooperation to increase when rare, i.e., $\hat{p}'>p$ near $p=0$]
-\label{remark:rarity}
-If the initial frequency of cooperation is very close to zero, then its frequency will increase if the cost of cooperation is low enough,
-\begin{equation} \label{eq:unequal_transmission_from_rarity_general_case}
-c < \gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)} \;.
-\end{equation} 
-\end{remark}
-
-This unites the conditions for fixation of cooperation and for stable polymorphism, both of which entail instability of the state where defection is fixed, $\hat{p}=0$.
-
-Importantly, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase in frequency when initially rare.
-Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
-However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost threshold, but it increases the cost threshold when the threshold is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
-Therefore, increasing $T_B$ decreases the cost threshold and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
-
-Increasing the vertical transmission rate, $v$, can either increase or decrease the cost threshold, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
-When $T_A<T_B$ we have $\partial \gamma_1 / \partial v >0$, and as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to increase when rare (\autoref{fig:equilibria}b).
-In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to increase when rare (\autoref{fig:equilibria}a).
-
-In general, this condition cannot be formulated in the form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
-If $T_A=T_B$, then, from Result~\ref{result:vert_obli_hori} and inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation will take over the population from any initial frequency if the cost is low enough,
-\begin{equation}
-\label{eq:equal_transmission}
-c < b \cdot \frac{\alpha T}{1-T} \;,
-\end{equation}
-and regardless of the vertical transmission rate, $v$.
-This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-From inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, without interaction-transmission association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
-\begin{equation}
-\label{eq:vert_hori_alpha0}
-c < \frac{T_A - T_B}{v(1-T_B)} \;.
-\end{equation}
-
-\autoref{fig:equilibria_v1}a illustrates this condition (for $v=1$), which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
-In this case, the benefit of cooperation, $b$, does not affect the evolution of cooperation, and the outcome is determined only by  cultural transmission.
-Further, inequality~\ref{eq:unequal_transmission_from_rarity_general_case} shows that with perfect interaction-transmission association ($\alpha=1$), cooperation will increase when rare if
-\begin{equation}\label{eq:vert_hori_alpha1}
-c < \frac{b v T_A + (T_A - T_B)}{v(1-T_B)} \;.
-\end{equation}
-
-In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
-This is similar to case of microbe-induced cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
-
-It is interesting to examine the general effect of interaction-transmission association $\alpha$ on the evolution of cooperation.
-Define the interaction-transmission association thresholds, $a_1$ and $a_2$, as 
-\begin{equation} \label{eq:boundries_assortative_meeting_general_case}
-  a_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
-  a_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A} \;.
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}%[Condition on interaction-transmission association $\alpha$ for cooperation to increase when it is rare]
-\label{remark:intermediate_association_res3}
-Cooperation will increase when rare if interaction-transmission association is high enough, specifically if $a_2 < \alpha$.
-\end{remark}
-Figures~\ref{fig:equilibria}c and \ref{fig:equilibria}d illustrate this condition.
-With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in the figures). 
-With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if $\alpha$ is large enough, $a_1<\alpha$ (green area with $T_A<T_B$), and can reach stable polymorphism if $\alpha$ is intermediate, $a_2<\alpha<a_1$ (yellow area).
-Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if $\alpha$ is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
-
-Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on $a_1$ and $a_2$ depends on the horizontal transmission bias.
-That is, if $T_A>T_B$, then evolution of cooperation is facilitated by oblique transmission, whereas if $T_A<T_B$, then evolution of cooperation is facilitated by vertical transmission (Figures~\ref{fig:equilibria}c and~\ref{fig:equilibria}d).
-\\
-
-Next, we examine the roles of vertical and oblique transmission in the evolution of cooperation.
-Fixation of cooperation is possible only if the vertical transmission rate is high enough,
-  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
-    \begin{aligned}
-      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
-    \end{aligned}
-    \end{equation} 
-This condition is necessary for fixation of cooperation, but it is not sufficient.
-If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
-In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see Figures~\ref{fig:equilibria}b and \ref{fig:equilibria}d).
-
-With only vertical transmission ($v=1$), from inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation increases when rare if
-\begin{equation} \label{eq:vert_hori}
-c < \frac{b \alpha T_A + (T_A - T_B)}{1-T_B} \;,
-\end{equation} 
-which can also be written as
-\begin{equation} \label{eq:vert_hori_alpha}
-\frac{c (1-T_B)-(T_A-T_B)}{b T_A} < \alpha \;.
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the absence of vertical transmission ($v=0$), from recursion~\ref{eq:nextgen_juveniles} we see that the frequency of the cooperator phenotype among adults increases every generation, i.e.
-$p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely $T_A > T_B$.
-That is, if $v=0$, then selection plays no role in the evolution of cooperation (i.e., $b$ and $c$ do not affect $\hat p'$).
-The dynamics are determined solely by differential horizontal transmission of the two phenotypes.
-With no bias in horizontal transmission, $T_A = T_B$, phenotype frequencies do not change, $\hat p'=\hat p$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cooperation and defection can coexist at frequencies $\hat{p}^*$ and $1-\hat{p}^*$ (\autoref{eq:general_equilibrium}). 
-When it is feasible, this equilibrium is stable or unstable under the conditions of Result \ref{result:vert_obli_hori}, parts 3 and 4, respectively.
-The yellow and blue areas in Figures~\ref{fig:equilibria_v1} and \ref{fig:equilibria} show cases of stable and unstable polymorphism, respectively.
-When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$.
-$\hat{p}^*$ is unstable when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:equilibria_v1}d shows $\hat{p}'-\hat{p}$ as a function of $\hat{p}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolution of interaction-transmission association}
-
-We now focus on the evolution of interaction-transmission association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
-Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}), see \autoref{fig:equilibria_v1}b.
-The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
-Therefore, $\bar{w}^*$ increases as $\alpha$ increases.
-But can this population-level advantage lead to the evolution of $\alpha$?
-
-To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $alpha$ but has no direct effect on fitness.
-This locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
-Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
-We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain the following result.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}%[Reduction principle for interaction-transmission association] 
-\label{result:evol_social_association}
-From a stable polymorphism between cooperation and defection, a modifier allele can successfully invade the population if it decreases the interaction-transmission association $\alpha$.
-\end{result}
-
-The analysis is in Appendix~\ref{sec:appendixD}.
-This reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we a modifier allele that decreases $\alpha$ appears and invades the population from time to time, then the value of $\alpha$ will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
-This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c). 
-Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Population structure}
-Interaction-transmission association may also emerge from population structure.
-Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
-Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
-Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
-In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
-initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
-The expected number of each of these interactions per individual per generation is one.
-The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
-On an infinite grid, $M=8$, but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
-As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
-
-The order of the interactions across the grid at each generation is random.
-After all interactions take place, an individual's fitness is determined by
-$w = 1 + b \cdot n_b - c \cdot n_c$,
-where $n_b$ is the number of interactions that individual had with cooperative neighbors,
-and $n_c$ is the number of interactions in which that individual cooperated (note that the phenotype may change between consecutive interactions due to horizontal transmission).
-Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
-Selection is global, rather than local, in accordance with our deterministic model:
-The parent is randomly drawn with probability proportional to its fitness, divided by the sum of the fitness values of all potential parents.
-Offspring are assumed to have the same phenotype as their parents (i.e. $v=1$).
-
-The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
-An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
-Changing the simulation so that selection is local (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
-
-These comparisons between the deterministic unstructured model and the stochastic structured model show that the conditions derived for the deterministic model can be useful for predicting the dynamics under complex scenarios.
-Moreover, this structured population model demonstrates that our parameter for interaction-transmission association, $\alpha$, can represent local interactions between individuals.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Discussion
-\newpage
-\section{Discussion}
-Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
-Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~\ref{eq:unequal_transmission_from_rarity_general_case},
-$
-c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;,
-$
-namely, the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
-This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
-Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both $c$ and $\alpha$ are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
-
-We find that stronger interaction-transmission association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, $\alpha$ is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
-With $\alpha=0$, the benefit of cooperation cannot facilitate its evolution; it can only succeed if horizontal transmission is biased in its favor.
-
-Indeed, in our model, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
-However, the effect of oblique transmission is more complicated.
-When there is horizontal transmission bias in favor of cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation.
-In contrast, when the bias is in favor of defection, $T_A<T_B$, higher rates of vertical transmission, $v$, are advantageous for cooperation, and the rate of vertical transmission must be high enough ($v>\hat v$) for cooperation to fix in the population.
-
-Our deterministic model provides a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
-In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
-
-\citet{feldman1985gene} studied the dynamics of an altruistic phenotype with vertical cultural transmission and a gene that modifies the transmission of the phenotype.
-Their results are very sensitive to this genetic modification: without it, the conditions for invasion of the altruistic phenotype reduce to Hamilton's rule.
-Further work is needed to incorporate such genetic modification of cultural transmission into our model.
-\citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation and
-carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or interaction-transmission association ($\alpha=0$).
-Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
-He further hypothesized that horizontal transmission can play an important role in the evolution of cooperation, and our results provide strong evidence for this hypothesis.
-
-To understand the role of horizontal transmission, we first review the role of \emph{assortment}.
-\citet{Eshel1982} showed that altruism can evolve when the tendency for \emph{assortative meeting}, i.e., for individuals to interact with others of their own phenotype, is strong enough.
-\citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
-They suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
-Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.
-This mechanism does not require repeated interactions, population structure, or individual recognition.
-We show that high levels of such interaction-transmission association greatly increase the potential for evolution of cooperation.
-With enough interaction-transmission association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$).
-
-How does non-vertical transmission generate assortment? 
-\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} 
-suggested that microbes that induce their hosts to act altruistically can be favored by selection, which may help to explain the evolution of cooperation. 
-%Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
-%Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others. 
-From the kin selection point-of-view, if microbes can be transmitted \emph{horizontally} from one host to another during host interactions, then following horizontal transmission the recipient host will carry microbes that are closely related to those of the donor host,
-even when the two hosts are (genetically) unrelated. 
-From the assortment point-of-view,
-infection by behavior-determining microbes during interactions effectively generates assortment because a recipient of help may be infected by a behavior-determining microbe and consequently become a helper.
-Cultural horizontal transmission can similarly generate assortment between cooperators and enhance the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
-when there is interaction-transmission association, so that the recipient of help may also be the recipient of the cultural trait for cooperation.
-Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
-environment''~\citep{Fletcher2009assortment} is generated not because the helper is likely to be helped, but rather because the helped is likely to become a helper.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \pagebreak
-% Acknowledgements
-{\small
-\section*{Acknowledgements}
-We thank Lilach Hadany, Ayelet Shavit, and Kaleda Krebs Denton for discussions and comments.
-This work was supported in part by
-the Clore Foundation Scholars Programme (OLE),
-the Morrison Institute for Population and Resources Studies at Stanford University (MWF),
-Israel Science Foundation (YR 552/19),
-and Minerva Stiftung Center for Lab Evolution (YR).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Bibliography
-\bibliographystyle{rsnat}
-\bibliography{bib}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
-%%%%%%%%%% Tables %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Tables}
-
-%%%% Table: payoff matrix
-%\bigskip
-%\begin{table}[h]
-%\centering
-%\caption{\textbf{Payoff matrix for prisoner's dilemma.}}
-%\begin{tabular}{lll}
-%\toprule
-%           & $\phi_2=A$ & $\phi_2=B$ \\ \cmidrule(r){1-3}
-%$\phi_1=A$ & $1+b-c$ & $1-c$ \\
-%$\phi_1=B$ & $1+b$   & $1$
-%\\ \bottomrule
-%\end{tabular}
-%\label{table:prisoner_payoff}
-%\caption*{
-%The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-$A$ is a cooperative phenotype, $B$ is a defector phenotype, $b$ is the benefit gained by an individual interacting with a cooperator, and $c$ is the cost of cooperation.
-$0<c<1$ and $c<b$.
-%}
-%\end{table}
-%\bigskip
-%%%%
-
-%%% Table: interactions
-\bigskip
+%%% Table: variables and parameters
+%%%% Table
 \begin{table}[h]
@@
 \bigskip
-%%%
-
-%%% Table: variables and parameters
-\bigskip
+
 \begin{table}[h]
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Results
 \newpage
-
-%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Figures}
-%%% Figure: model illustration
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
-  \caption{\textbf{Model illustration.} 
-  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
-Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
-  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
-  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
-    }
-  \label{fig:illustration}
-\end{figure}
-
-%%% Figure: thresholds figure - vertical and oblique
+\section{Results}
+
+We determine the equilibria of the model in \autoref{eq:nextgen_juveniles}
+%namely, solutions of $\hat{p}' = \hat{p}$, 
+and analyze their local stability.
+We then analyze the evolution of a modifier of interaction-transmission association,~$\alpha$.
+Finally, we compare derived conditions to outcomes of stochastic simulations with a structured population.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Evolution of cooperation}
+
+The fixed points (equilibria) of  the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
+\begin{equation} \label{eq:general_equilibrium}
+  \hat{p}^* =  
+  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
+\end{equation}
+
+Define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
+\begin{equation} \label{eq:cost_thresholds_v_threshold} 
+\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
+\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}, \quad
+\hat v = \frac{T_B - T_A}{1-T_A} \;.
+\end{equation}
+
+Then we have the following result.
+\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{result}%[Equilibria and stability]
+\label{result:vert_obli_hori}
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
+
+% in gamma
+\begin{enumerate}
+\item \emph{Fixation of cooperation}: 
+	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or 
+	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \gamma_2$.
+\item \emph{Fixation of defection}: 
+    if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or 
+	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
+\item \emph{Stable polymorphism}: 
+    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
+    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
+\item \emph{Unstable polymorphism}:
+    if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
+\end{enumerate}
+
+\end{result}
+These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
+
+Much of the literature on evolution of cooperation focuses on conditions for  an initially rare cooperative phenotype to invade a population of defectors.
+The following remarks address this condition.
+\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{remark}%[Condition on $c$ for cooperation to increase when rare, i.e., $\hat{p}'>p$ near $p=0$]
+\label{remark:rarity}
+If the initial frequency of cooperation is very close to zero, then its frequency will increase if the cost of cooperation is low enough,
+\begin{equation} \label{eq:unequal_transmission_from_rarity_general_case}
+c < \gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)} \;.
+\end{equation} 
+\end{remark}
+
+This unites the conditions for fixation of cooperation and for stable polymorphism, both of which entail instability of the state where defection is fixed, $\hat{p}=0$.
+
+Importantly, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase in frequency when initially rare.
+Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
+However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost threshold, but it increases the cost threshold when the threshold is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
+Therefore, increasing $T_B$ decreases the cost threshold and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
+
+Increasing the vertical transmission rate, $v$, can either increase or decrease the cost threshold, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
+When $T_A<T_B$ we have $\partial \gamma_1 / \partial v >0$, and as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to increase when rare (\autoref{fig:equilibria}b).
+In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to increase when rare (\autoref{fig:equilibria}a).
+
+In general, this condition cannot be formulated in the form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
+If $T_A=T_B$, then, from Result~\ref{result:vert_obli_hori} and inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation will take over the population from any initial frequency if the cost is low enough,
+\begin{equation}
+\label{eq:equal_transmission}
+c < b \cdot \frac{\alpha T}{1-T} \;,
+\end{equation}
+and regardless of the vertical transmission rate, $v$.
+This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+From inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, without interaction-transmission association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
+\begin{equation}
+\label{eq:vert_hori_alpha0}
+c < \frac{T_A - T_B}{v(1-T_B)} \;.
+\end{equation}
+
+\autoref{fig:equilibria_v1}a illustrates this condition (for $v=1$), which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
+In this case, the benefit of cooperation, $b$, does not affect the evolution of cooperation, and the outcome is determined only by  cultural transmission.
+Further, inequality~\ref{eq:unequal_transmission_from_rarity_general_case} shows that with perfect interaction-transmission association ($\alpha=1$), cooperation will increase when rare if
+\begin{equation}\label{eq:vert_hori_alpha1}
+c < \frac{b v T_A + (T_A - T_B)}{v(1-T_B)} \;.
+\end{equation}
+
+In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
+This is similar to case of microbe-induced cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
+
+It is interesting to examine the general effect of interaction-transmission association $\alpha$ on the evolution of cooperation.
+Define the interaction-transmission association thresholds, $a_1$ and $a_2$, as 
+\begin{equation} \label{eq:boundries_assortative_meeting_general_case}
+  a_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
+  a_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A} \;.
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{remark}%[Condition on interaction-transmission association $\alpha$ for cooperation to increase when it is rare]
+\label{remark:intermediate_association_res3}
+Cooperation will increase when rare if interaction-transmission association is high enough, specifically if $a_2 < \alpha$.
+\end{remark}
+Figures~\ref{fig:equilibria}c and \ref{fig:equilibria}d illustrate this condition.
+With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in the figures). 
+With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if $\alpha$ is large enough, $a_1<\alpha$ (green area with $T_A<T_B$), and can reach stable polymorphism if $\alpha$ is intermediate, $a_2<\alpha<a_1$ (yellow area).
+Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if $\alpha$ is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
+
+Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on $a_1$ and $a_2$ depends on the horizontal transmission bias.
+That is, if $T_A>T_B$, then evolution of cooperation is facilitated by oblique transmission, whereas if $T_A<T_B$, then evolution of cooperation is facilitated by vertical transmission (Figures~\ref{fig:equilibria}c and~\ref{fig:equilibria}d).
+\\
+
+Next, we examine the roles of vertical and oblique transmission in the evolution of cooperation.
+Fixation of cooperation is possible only if the vertical transmission rate is high enough,
+  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
+    \begin{aligned}
+      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
+    \end{aligned}
+    \end{equation} 
+This condition is necessary for fixation of cooperation, but it is not sufficient.
+If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
+In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see Figures~\ref{fig:equilibria}b and \ref{fig:equilibria}d).
+
+With only vertical transmission ($v=1$), from inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation increases when rare if
+\begin{equation} \label{eq:vert_hori}
+c < \frac{b \alpha T_A + (T_A - T_B)}{1-T_B} \;,
+\end{equation} 
+which can also be written as
+\begin{equation} \label{eq:vert_hori_alpha}
+\frac{c (1-T_B)-(T_A-T_B)}{b T_A} < \alpha \;.
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In the absence of vertical transmission ($v=0$), from recursion~\ref{eq:nextgen_juveniles} we see that the frequency of the cooperator phenotype among adults increases every generation, i.e.
+$p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely $T_A > T_B$.
+That is, if $v=0$, then selection plays no role in the evolution of cooperation (i.e., $b$ and $c$ do not affect $\hat p'$).
+The dynamics are determined solely by differential horizontal transmission of the two phenotypes.
+With no bias in horizontal transmission, $T_A = T_B$, phenotype frequencies do not change, $\hat p'=\hat p$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Cooperation and defection can coexist at frequencies $\hat{p}^*$ and $1-\hat{p}^*$ (\autoref{eq:general_equilibrium}). 
+When it is feasible, this equilibrium is stable or unstable under the conditions of Result \ref{result:vert_obli_hori}, parts 3 and 4, respectively.
+The yellow and blue areas in Figures~\ref{fig:equilibria_v1} and \ref{fig:equilibria} show cases of stable and unstable polymorphism, respectively.
+When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$.
+$\hat{p}^*$ is unstable when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
+\autoref{fig:equilibria_v1}d shows $\hat{p}'-\hat{p}$ as a function of $\hat{p}$.
 
@@
 
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Evolution of interaction-transmission association}
+
+We now focus on the evolution of interaction-transmission association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
+Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}), see \autoref{fig:equilibria_v1}b.
+The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
+Therefore, $\bar{w}^*$ increases as $\alpha$ increases.
+But can this population-level advantage lead to the evolution of $\alpha$?
+
+To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $alpha$ but has no direct effect on fitness.
+This locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
+Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
+We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain the following result.
+\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{result}%[Reduction principle for interaction-transmission association] 
+\label{result:evol_social_association}
+From a stable polymorphism between cooperation and defection, a modifier allele can successfully invade the population if it decreases the interaction-transmission association $\alpha$.
+\end{result}
+
+The analysis is in Appendix~\ref{sec:appendixD}.
+This reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
+Furthermore, if we a modifier allele that decreases $\alpha$ appears and invades the population from time to time, then the value of $\alpha$ will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
+This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c). 
+Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Population structure}
+Interaction-transmission association may also emerge from population structure.
+Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
+Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
+Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
+In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
+initiators interact with a random neighbor (i.e.
+individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
+The expected number of each of these interactions per individual per generation is one.
+The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
+On an infinite grid, $M=8$, but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
+As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
+
+The order of the interactions across the grid at each generation is random.
+After all interactions take place, an individual's fitness is determined by
+$w = 1 + b \cdot n_b - c \cdot n_c$,
+where $n_b$ is the number of interactions that individual had with cooperative neighbors,
+and $n_c$ is the number of interactions in which that individual cooperated (note that the phenotype may change between consecutive interactions due to horizontal transmission).
+Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
+Selection is global, rather than local, in accordance with our deterministic model:
+The parent is randomly drawn with probability proportional to its fitness, divided by the sum of the fitness values of all potential parents.
+Offspring are assumed to have the same phenotype as their parents (i.e. $v=1$).
+
+The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
+An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
+Changing the simulation so that selection is local (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+
+These comparisons between the deterministic unstructured model and the stochastic structured model show that the conditions derived for the deterministic model can be useful for predicting the dynamics under complex scenarios.
+Moreover, this structured population model demonstrates that our parameter for interaction-transmission association, $\alpha$, can represent local interactions between individuals.
+
+%%% Figure: Invasion
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.5]{../Figures/invasion.eps}
+  \caption{
+  \textbf{Reduction principle for interaction-transmission association.} 
+  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
+  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
+  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
+  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
+  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
+  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
+  }
+  \label{fig:invasion}
+\end{figure}
+
+\newpage
+
 %%% Figure: Spatial model - global selection
-\begin{figure}[p]
+\begin{figure}[h]
   \centering
@@
 \end{figure}
+
+\newpage
+
+%%% Figure: Spatial model - local selection
+\begin{figure}[h]
+  \centering
+   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
+    ~
+    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
+  \caption{
+  \textbf{Evolution of cooperation in a structured population with local selection.}
+  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
+  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
+  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
+  The population evolves on a 100-by-100 grid.
+  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
+  50 simulations were executed for each parameter set.
+  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
+  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
+  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
+  }
+  \label{fig:spatial_local_selection}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Discussion
+\newpage
+\section{Discussion}
+Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
+Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~\ref{eq:unequal_transmission_from_rarity_general_case},
+$
+c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;,
+$
+namely, the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
+This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
+Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both $c$ and $\alpha$ are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
+
+We find that stronger interaction-transmission association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
+Nevertheless, when cooperation and defection coexist, $\alpha$ is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
+With $\alpha=0$, the benefit of cooperation cannot facilitate its evolution; it can only succeed if horizontal transmission is biased in its favor.
+
+Indeed, in our model, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
+However, the effect of oblique transmission is more complicated.
+When there is horizontal transmission bias in favor of cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation.
+In contrast, when the bias is in favor of defection, $T_A<T_B$, higher rates of vertical transmission, $v$, are advantageous for cooperation, and the rate of vertical transmission must be high enough ($v>\hat v$) for cooperation to fix in the population.
+
+Our deterministic model provides a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
+In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
+
+\citet{feldman1985gene} studied the dynamics of an altruistic phenotype with vertical cultural transmission and a gene that modifies the transmission of the phenotype.
+Their results are very sensitive to this genetic modification: without it, the conditions for invasion of the altruistic phenotype reduce to Hamilton's rule.
+Further work is needed to incorporate such genetic modification of cultural transmission into our model.
+\citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation and
+carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or interaction-transmission association ($\alpha=0$).
+Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
+He further hypothesized that horizontal transmission can play an important role in the evolution of cooperation, and our results provide strong evidence for this hypothesis.
+
+To understand the role of horizontal transmission, we first review the role of \emph{assortment}.
+\citet{Eshel1982} showed that altruism can evolve when the tendency for \emph{assortative meeting}, i.e., for individuals to interact with others of their own phenotype, is strong enough.
+\citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
+They suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
+Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.
+This mechanism does not require repeated interactions, population structure, or individual recognition.
+We show that high levels of such interaction-transmission association greatly increase the potential for evolution of cooperation.
+With enough interaction-transmission association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$).
+
+How does non-vertical transmission generate assortment? 
+\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} 
+suggested that microbes that induce their hosts to act altruistically can be favored by selection, which may help to explain the evolution of cooperation. 
+%Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
+%Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others. 
+From the kin selection point-of-view, if microbes can be transmitted \emph{horizontally} from one host to another during host interactions, then following horizontal transmission the recipient host will carry microbes that are closely related to those of the donor host,
+even when the two hosts are (genetically) unrelated. 
+From the assortment point-of-view,
+infection by behavior-determining microbes during interactions effectively generates assortment because a recipient of help may be infected by a behavior-determining microbe and consequently become a helper.
+Cultural horizontal transmission can similarly generate assortment between cooperators and enhance the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
+when there is interaction-transmission association, so that the recipient of help may also be the recipient of the cultural trait for cooperation.
+Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
+environment''~\citep{Fletcher2009assortment} is generated not because the helper is likely to be helped, but rather because the helped is likely to become a helper.
+
+\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Bibliography
+\bibliographystyle{rsnat}
+\bibliography{bib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{appendices}
-
-% Supporting figures
-\newpage
-\section*{Supporting figures}
-
-%%% Figure: Invasion
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.5]{../Figures/invasion.eps}
-  \caption{
-  \textbf{Reduction principle for interaction-transmission association.} 
-  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
-  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
-  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
-  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
-  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
-  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
-  }
-  \label{fig:invasion}
-\end{figure}
-
-%%% Figure: Spatial model - local selection
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
-    ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
-  \caption{
-  \textbf{Evolution of cooperation in a structured population with local selection.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
-  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
-  The population evolves on a 100-by-100 grid.
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
-  50 simulations were executed for each parameter set.
-  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
-  }
-  \label{fig:spatial_local_selection}
-\end{figure}
-
-%%%
 \end{document}

### 2021-01-30 ms/Thesis/thesis.tex
Add note about ohad contrubation

@@
 \subsection{Population structure}
+All the simulations in this section were made by Ohad Lewin-Epstein from Tel Aviv University.
 Interaction-transmission association may also emerge from population structure.

### 2021-01-30 ms/Thesis/thesis.tex
Remove line numbers
Add idc format

@@
 
-% Authors
-\renewcommand\Affilfont{\small}
-
-\author[1]{Dor Cohen}
-\author[2]{Ohad Lewin-Epstein}
-\author[3]{Marcus W. Feldman}
-\author[1,4,5,*]{Yoav Ram}
-
-\affil[1]{School of Computer Science, Interdisciplinary Center Herzliya, Herzliya, Israel}
-\affil[2]{School of Plant Sciences and Food Security, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
-\affil[3]{Department of Biology, Stanford University, Stanford, CA}
-\affil[4]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
-\affil[5]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
-\affil[*]{Corresponding author: yoav@yoavram.com}
-
 \date{\today}
@@
 
-% Abstract
-\begin{abstract}
+\pagebreak
+{\large This work was carried out under the supervision of \textbf{Dr. Yoav Ram} from the Efi Arazi School of Computer Science, The Interdisciplinary Center, Herzliya.}
+\pagebreak
+
+{\huge \begin{center} \textbf{Abstract} \end{center}}
+
 Cultural evolution of cooperation under vertical and non-vertical cultural transmission is studied, and conditions are found for fixation and coexistence of cooperation and defection. 
@@
 Parallels are drawn with Hamilton's rule incorporating assortment and effective relatedness.
-\end{abstract}
 

### 2021-04-13 ms/main.tex
add todo
Address editors comments

@@
 Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
-An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}a).
+An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}d).
 Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
@@
 \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
 
@@
 	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
-\item \emph{Stable polymorphism}: 
+\item \emph{Stable polymorphism (coexistence)}: 
     if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
     if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
-\item \emph{Unstable polymorphism}:
+\item \emph{Unstable polymorphism (bistable competition)}:
     if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
@@
 
-Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on $a_1$ and $a_2$ depends on the horizontal transmission bias.
+Interestingly, because the sign of $\partial a_2 / \partial v$  is equal to the sign of $T_A-T_B$, the effect of the vertical transmission rate $v$ on $a_1$ and $a_2$ depends on the horizontal transmission bias.
 That is, if $T_A>T_B$, then evolution of cooperation is facilitated by oblique transmission, whereas if $T_A<T_B$, then evolution of cooperation is facilitated by vertical transmission (Figures~\ref{fig:equilibria}c and~\ref{fig:equilibria}d).
@@
 initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
+individual in a neighboring site) in a prisoner's dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
 The expected number of each of these interactions per individual per generation is one.
@@
   \caption{\textbf{Model illustration.} 
-  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
+  \textbf{(a)}~Prisoner's dilemma payoff matrix, showing the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+  \textbf{(b)}~Individuals socially interact in pairs in a prisoner's dilemma game.
 Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.

### 2021-04-13 ms/main.tex
Change \tilde to \dot

@@
 
-Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\tilde{p}$.
+Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\dot{p}$.
 Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
@@
 \hat{p} \;=
-\tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \;= 
-v \tilde{p} + (1-v) p \;.
+\dot{p} [v + (1-v)p] + (1-\dot{p}) [(1-v)p] \;= 
+v \dot{p} + (1-v) p \;.
 \end{aligned}
@@
 \begin{aligned}
-\bar{w} \tilde{p}' =
+\bar{w} \dot{p}' =
 & \hat{p}^2 (1+b-c) \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
@@
 %\begin{aligned}
-%\bar{w} \tilde{p}' =
+%\bar{w} \dot{p}' =
 %& \hat{p}^2 (1+b-c) \big[1-(1-\hat{p})(1-\alpha)T_B)\big] \;+ \\
@@
 %\end{equation}
-%where $\hat{p}=v\tilde{p}+(1-v)p$.
-Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults} and $\tilde{p}'$ from \autoref{eq:nextgen_parents} and obtain
+%where $\hat{p}=v\dot{p}+(1-v)p$.
+Starting from \autoref{eq:horizontal} with $\hat{p}'=v\dot{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults} and $\dot{p}'$ from \autoref{eq:nextgen_parents} and obtain
 \begin{equation} \label{eq:nextgen_juveniles}
@@
 
-In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
+In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\dot{p}=0$ and $\dot{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\dot{p}'>\dot{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
 This is similar to case of microbe-induced cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
@@
 $p$ & Frequency of phenotype $A$ among adults & $[0,1]$ \\
-$\tilde p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
+$\dot p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
 $\hat p$ & Frequency of phenotype $A$ among juveniles & $[0,1]$ \\
@@
 
-We assume here that $v=1$, i.e. no oblique transmission, and therefore $\hat{p}=\tilde{p}$.
-Denote the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ by $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
+We assume here that $v=1$, i.e. no oblique transmission, and therefore $\hat{p}=\dot{p}$.
+Denote the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ by $\vec{\dot{p}}= (\dot{p}_1$, $\dot{p}_2$, $\dot{p}_3$, $\dot{p}_4)$. 
 The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
@@
 	% p1
-  \bar{w}\tilde{p}_1' = 
-  & \tilde{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \tilde{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) \;+ \\
-  & \tilde{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) \;+ \\
-  & \tilde{p}_2(1-x)x(1-\alpha_1)T_A \;,
+  \bar{w}\dot{p}_1' = 
+  & \dot{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) \;+ \\
+  & \dot{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) \;+ \\
+  & \dot{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) \;+ \\
+  & \dot{p}_2(1-x)x(1-\alpha_1)T_A \;,
 \\
 	% p2
-  \bar{w}\tilde{p}_2' = 
-  & \tilde{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \;+ \\
-  & \tilde{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \tilde{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) \;+ \\
-& \tilde{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;, 
+  \bar{w}\dot{p}_2' = 
+  & \dot{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \;+ \\
+  & \dot{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) \;+ \\
+  & \dot{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) \;+ \\
+& \dot{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;, 
 \\
 	% p3
-  \bar{w}\tilde{p}_3' =
-  & \tilde{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \tilde{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) \;+ \\
-  & \tilde{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) \;+ \\
-  & \tilde{p}_4(1-x) x (1-\alpha_2)T_A \;, 
+  \bar{w}\dot{p}_3' =
+  & \dot{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) \;+ \\
+  & \dot{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) \;+ \\
+  & \dot{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) \;+ \\
+  & \dot{p}_4(1-x) x (1-\alpha_2)T_A \;, 
 \\
 	% p4
-  \bar{w}\tilde{p}_4' =
-  & \tilde{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B \;+ \\
-  & \tilde{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \tilde{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) \;+ \\
-  & \tilde{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \;,
+  \bar{w}\dot{p}_4' =
+  & \dot{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B \;+ \\
+  & \dot{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) \;+ \\
+  & \dot{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) \;+ \\
+  & \dot{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \;,
   \end{aligned}
@@
 %\begin{equation}
-%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
+%\bar{w} \vec{\dot{p}} = F(\vec{\dot{p}}),
 %\end{equation}
-where $x=\tilde{p}_1+\tilde{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-
-The equilibrium where only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
-\begin{equation} \label{eq:p_tilde_star_alpha_1}
-\tilde{p}^*=
+where $x=\dot{p}_1+\dot{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\dot{p}} = (\dot{p}_1,\dot{p}_2,\dot{p}_3,\dot{p}_4)$.
+
+The equilibrium where only allele $M$ is present is  $\vec{\dot{p}^*} = (\dot{p}^*, 1-\dot{p}^*, 0, 0)$, where
+\begin{equation} \label{eq:p_dot_star_alpha_1}
+\dot{p}^*=
 \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)} \;,
@@
 setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
-When $v=1$, $\tilde p^*$ is a feasible polymorphism ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
-
-The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+When $v=1$, $\dot p^*$ is a feasible polymorphism ($0 < \dot{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
+
+The local stability of $\vec{\dot{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\dot{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
 $\cl^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\cl^*_{in}$ and $\cl^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1}, with $\bar{w}^*=1+(b-c)\tilde{p}^*$ as the stable population mean fitness,
+The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\dot{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1}, with $\bar{w}^*=1+(b-c)\dot{p}^*$ as the stable population mean fitness,
 \begin{equation} \label{eq:external_stability_matrix}
@@
 \frac{1}{\bar{w}^*} \begin{bmatrix}
-\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
-\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) 
+\frac{\partial\bar{w}\dot{p}_3'}{\partial \dot{p}_3}(\vec{\dot{p}}^*) &
+\frac{\partial\bar{w}\dot{p}_3'}{\partial \dot{p}_4}(\vec{\dot{p}}^*) \\
+\frac{\partial\bar{w}\dot{p}_4'}{\partial \dot{p}_3}(\vec{\dot{p}}^*) &
+\frac{\partial\bar{w}\dot{p}_4'}{\partial \dot{p}_4}(\vec{\dot{p}}^*) 
 \end{bmatrix} \;= \\
 & \frac{1}{\bar{w}^*} \begin{bmatrix}
-		(1+b \tilde{p}^* -c)(1-T_B(1-\tilde{p}^*)) + b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) & 
-		(1+b \tilde{p}^*) T_A \tilde{p}^* + b \tilde{p}^* \alpha_2 T_A(1-\tilde{p}^*) \\
-		(1+b \tilde{p}^* - c) T_B(1-\tilde{p}^*) - b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) &
-		(1+b \tilde{p}^*) (1-T_A \tilde{p}^*) - b \tilde{p}^* \alpha_2 T_A (1-\tilde{p}^*) \\
+		(1+b \dot{p}^* -c)(1-T_B(1-\dot{p}^*)) + b \dot{p}^* \alpha_2 T_B (1-\dot{p}^*) & 
+		(1+b \dot{p}^*) T_A \dot{p}^* + b \dot{p}^* \alpha_2 T_A(1-\dot{p}^*) \\
+		(1+b \dot{p}^* - c) T_B(1-\dot{p}^*) - b \dot{p}^* \alpha_2 T_B (1-\dot{p}^*) &
+		(1+b \dot{p}^*) (1-T_A \dot{p}^*) - b \dot{p}^* \alpha_2 T_A (1-\dot{p}^*) \\
   	\end{bmatrix} \;.
@@
 
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\cl^*_{ex}$.
+Because we assume that $\vec{\dot{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+$\vec{\dot{p}^*}$ is determined by the eigenvalues of the external stability matrix $\cl^*_{ex}$.
 This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\cl^*_{ex}$ is real and positive.
-Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
+Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\dot{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
 The eigenvalues of $\cl^*_{ex}$ are the roots of the characteristic polynomial, $R(\lambda)$,
@@
 Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
-Thus, a sufficient condition for external instability of $\vec{\tilde{p}^*}$ is $R(1) < 0$.
+Thus, a sufficient condition for external instability of $\vec{\dot{p}^*}$ is $R(1) < 0$.
 %\begin{equation} \label{eq:R1_negative}
@@
 where $l_{i j}$ are defined in \autoref{eq:external_stability_matrix}.
-Adding the second row in \autoref{eq:signR1} to the first row,  which does not change the determinant, and substituting $\bar{w}^*=1+(b-c)\tilde{p}^*$, we get
+Adding the second row in \autoref{eq:signR1} to the first row,  which does not change the determinant, and substituting $\bar{w}^*=1+(b-c)\dot{p}^*$, we get
 \begin{equation} 
@@
 & \sign\det\begin{bmatrix}
-	 -c(1-\tilde{p}^*) &&
-	 c \tilde{p}^* \\
-	 (1-\tilde{p}^*)\big[(1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* \big] &&
-	 \tilde{p}^*\big[-(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c\big]
+	 -c(1-\dot{p}^*) &&
+	 c \dot{p}^* \\
+	 (1-\dot{p}^*)\big[(1+b\dot{p}^*-c)T_B - b \alpha_2 T_B \dot{p}^* \big] &&
+	 \dot{p}^*\big[-(1+b\dot{p}^*)T_A - b \alpha_2 T_A (1-\dot{p}^*) + c\big]
 \end{bmatrix} = \\
-& \sign \Bigg[c \tilde{p}^* (1-\tilde{p}^*) \cdot \det\begin{bmatrix}
+& \sign \Bigg[c \dot{p}^* (1-\dot{p}^*) \cdot \det\begin{bmatrix}
 	 -1 &&
 	 1 \\
-	 (1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* &&
-	 -(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c
+	 (1+b\dot{p}^*-c)T_B - b \alpha_2 T_B \dot{p}^* &&
+	 -(1+b\dot{p}^*)T_A - b \alpha_2 T_A (1-\dot{p}^*) + c
 \end{bmatrix}\Bigg] = \\
@@
 	 1 \\
-	 (1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* &&
-	 -(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c
+	 (1+b\dot{p}^*-c)T_B - b \alpha_2 T_B \dot{p}^* &&
+	 -(1+b\dot{p}^*)T_A - b \alpha_2 T_A (1-\dot{p}^*) + c
 \end{bmatrix} \;,
@@
 \end{equation}
-since $c>0$, $0<\tilde{p}^*<1$.
+since $c>0$, $0<\dot{p}^*<1$.
 That is, 
@@
 &\sign\Big[
-(1+b\tilde{p}^*)T_A + b\alpha_2 T_A (1-\tilde{p}^*) - c - 
-(1+b\tilde{p}^*-c)T_B + b\tilde{p}^* \alpha_2 T_B \Big]
+(1+b\dot{p}^*)T_A + b\alpha_2 T_A (1-\dot{p}^*) - c - 
+(1+b\dot{p}^*-c)T_B + b\dot{p}^* \alpha_2 T_B \Big]
 = \\
-&\sign\Big[(1+b(1-\alpha_2)\tilde{p}^*)(T_A-T_B) + b\alpha_2 T_A - c (1-T_B) \Big]\;.
-\end{aligned}
-\end{equation}
-Substituting $\tilde{p}^*$ from \autoref{eq:p_tilde_star_alpha_1}, we get
+&\sign\Big[(1+b(1-\alpha_2)\dot{p}^*)(T_A-T_B) + b\alpha_2 T_A - c (1-T_B) \Big]\;.
+\end{aligned}
+\end{equation}
+Substituting $\dot{p}^*$ from \autoref{eq:p_dot_star_alpha_1}, we get
 \begin{equation} \label{eq:R1_less}

### 2021-04-13 ms/main.tex
Added comment about stable and unstable polymorphism

@@
 	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
-\item \emph{Stable polymorphism (coexistence)}: 
+\item \emph{Stable polymorphism}: 
     if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
     if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
-\item \emph{Unstable polymorphism (bistable competition)}:
+\item \emph{Unstable polymorphism}:
     if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
@@
 These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
+Note that “stable polymorphism” is sometimes called “coexistence” and “unstable polymorphism” is “bistable competition.
 

### 2021-04-13 ms/main.tex
Fix bib style
Fixes around line 61

@@
 \end{equation}
-In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
+In inequality~\ref{eq:feldman1985}, $\varphi$ replaces relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
 This shows that under a cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).
@@
 % Bibliography
-\bibliographystyle{rsnat}
+\bibliographystyle{unsrtnat}
 \bibliography{bib}

### 2021-04-13 ms/main.tex
Address all the Hamliton commnets around lines 160-164

@@
 
-This unites the conditions for fixation of cooperation and for stable polymorphism, both of which entail instability of the state where defection is fixed, $\hat{p}=0$.
+This merges the conditions for fixation of cooperation and for stable polymorphism, both of which entail instability of the state where defection is fixed, $\hat{p}=0$.
 
@@
 
-In general, this condition cannot be formulated in the form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
+Importantly, this condition cannot be formulated in the commonly used form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
 If $T_A=T_B$, then, from Result~\ref{result:vert_obli_hori} and inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation will take over the population from any initial frequency if the cost is low enough,
@@
 and regardless of the vertical transmission rate, $v$.
-This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
+This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{cultural relatedness} or \emph{cultural assortment}, respectively.
 Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.

### 2021-04-13 ms/main.tex
1

@@
 
-To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $alpha$ but has no direct effect on fitness.
+To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $\alpha$ but has no direct effect on fitness.
 This locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.

### 2021-04-13 ms/main.tex
Refere 2's comments

@@
 Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
-An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}d).
+An offspring inherits its phenotype from its parent via cultural vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}d).
 Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is

### 2021-04-13 ms/main.tex
2

@@
 The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
-On an infinite grid, $M=8$, but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
+On an infinite grid, $M=8$ (i.e., Moore neighborhood), but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
 As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
@@
 \citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
-They suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
+They suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as spatial structure, repeated interactions, and individual recognition.
 Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.

### 2021-04-14 ms/main.tex
continued reply to minor revision, not done yet

@@
 \end{equation}
-where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{Inequality~\ref{eq:fletcher2009} generalizes inequalities~\ref{eq:hamilton_rule} and~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
-\citet{Bijma2010assortment} obtained a result related to inequality~\ref{eq:fletcher2009} for other types of games.
+where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help\footnote{Inequality~\ref{eq:fletcher2009} generalizes inequalities~\ref{eq:hamilton_rule} and~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}.
+\citet{Bijma2010assortment} obtained a result related to inequality~\ref{eq:fletcher2009} for other games.
+
+Cooperation can also evolve when interactions are determined by population structure.
+For example, \citet{Ohtsuki2006} studied populations on graphs with average degree $k$, that is, the average individual has $k$ potential interaction partners.
+Assuming that selection is weak and that the population size is much larger than $k$ (i.e.
+sparse structure), they found that cooperative behaviour can evolve if~\citep{Ohtsuki2006}
+\begin{equation} \label{eq:ohtsuki2006}
+c < b \cdot \frac{1}{k} \,.
+\end{equation}
+They thus interpret $1/k$ as \emph{social relatedness} or \emph{social viscosity}~\citep{Ohtsuki2006}.
 
@@
 or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
+Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because it diminishes the effect of selection (due to non-vertical transmission from non-reproducing individuals~\citep{ram2018evolution}).
 
@@
 
-Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
+Consider a very large well-mixed population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
 An offspring inherits its phenotype from its parent via cultural vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}d).
@@
 \end{equation}
-The frequency of $A$ among parents (i.e. after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
+The right-hand terms in \autoref{eq:nextgen_adults} give the frequencies of the different interactions that produce cooperator adults~(\autoref{table:interactions}).
+The frequency of $A$ among parents follows a similar dynamic but must also include the effect of natural selection.
+Therefore, each right-hand term from \autoref{eq:nextgen_adults} is multiplied by the corresponding fitness value (\autoref{table:interactions}, \autoref{fig:illustration}a), which depends on the phenotypes of the two interaction partners.
+Therefore, the frequency of phenotype $A$ among parents is
 \begin{equation}\label{eq:nextgen_parents}
@@
 \end{result}
+
+Thus, cooperation can take over the population if it either has a horizontal transmission advantage, or it has a horizontal transmission disadvantage, but the vertical transmission rate is high enough.
+In either case, the cost of cooperation must be small enough.
+A stable polymorphism can exist between cooperation and defection only if defection has a horizontal transmission advantage.
+In this case, the existence of a stable polymorphism depends on an interplay between the benefit and cost of cooperation and the vertical transmission rate.
 These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
-Note that “stable polymorphism” is sometimes called “coexistence” and “unstable polymorphism” is “bistable competition.
+Note that \emph{stable} and {unstable polymorphism} are also called, respectively, \emph{coexistence} and \emph{bistable competition}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}%[Condition on $c$ for cooperation to increase when rare, i.e., $\hat{p}'>p$ near $p=0$]
+\begin{remark}%[Condition on $c$ for cooperation to increase when rare, i.e. $\hat{p}'>p$ near $p=0$]
 \label{remark:rarity}
@@
 
-Importantly, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase in frequency when initially rare.
+Notably, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase in frequency when initially rare.
 Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
@@
 and regardless of the vertical transmission rate, $v$.
-This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{cultural relatedness} or \emph{cultural assortment}, respectively.
+This condition can be interpreted as a version of Hamilton's rule ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ is a measure of \emph{cultural relatedness}  or \emph{cultural assortment}, respectively, similar to the term \emph{social relatedness} used by \citet{Ohtsuki2006}.
 Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.
@@
 
-In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\dot{p}=0$ and $\dot{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\dot{p}'>\dot{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
+In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\dot{p}=0$ and $\dot{p}=1$, and cooperation will evolve from any initial frequency (i.e.
+$\dot{p}'>\dot{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
 This is similar to case of microbe-induced cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
@@
 $p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely $T_A > T_B$.
-That is, if $v=0$, then selection plays no role in the evolution of cooperation (i.e., $b$ and $c$ do not affect $\hat p'$).
+That is, if $v=0$, then selection plays no role in the evolution of cooperation (i.e. $b$ and $c$ do not affect $\hat p'$).
 The dynamics are determined solely by differential horizontal transmission of the two phenotypes.
@@
 The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
-On an infinite grid, $M=8$ (i.e., Moore neighborhood), but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
+On an infinite grid, $M=8$ (i.e. Moore neighborhood), but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
 As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
@@
 An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
-Changing the simulation so that selection is local (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+Changing the simulation so that selection is local (i.e.
+sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
 
@@
 To understand the role of horizontal transmission, we first review the role of \emph{assortment}.
-\citet{Eshel1982} showed that altruism can evolve when the tendency for \emph{assortative meeting}, i.e., for individuals to interact with others of their own phenotype, is strong enough.
+\citet{Eshel1982} showed that altruism can evolve when the tendency for \emph{assortative meeting}, i.e. for individuals to interact with others of their own phenotype, is strong enough.
 \citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
@@
 
-The local stability of $\vec{\dot{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\dot{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
+The local stability of $\vec{\dot{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\dot{p}^*}$ (i.e.
+the Jacobian of the transformation at the equilibrium).
 $\cl^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\cl^*_{in}$ and $\cl^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .

### 2021-04-17 ms/main.tex
Fix model illustration figure

@@
 Consider a very large well-mixed population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
-An offspring inherits its phenotype from its parent via cultural vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}d).
+An offspring inherits its phenotype from its parent via cultural vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}a).
 Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
@@
 Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
-\autoref{fig:illustration}a shows the payoff matrix, i.e.
+\autoref{fig:illustration}d shows the payoff matrix, i.e.
 the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
@@
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}b).
+It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}c).
 %The interaction-transmission association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
 However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
-The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}c).
+The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}b).
 Then, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 The frequency of $A$ among parents follows a similar dynamic but must also include the effect of natural selection.
-Therefore, each right-hand term from \autoref{eq:nextgen_adults} is multiplied by the corresponding fitness value (\autoref{table:interactions}, \autoref{fig:illustration}a), which depends on the phenotypes of the two interaction partners.
+Therefore, each right-hand term from \autoref{eq:nextgen_adults} is multiplied by the corresponding fitness value (\autoref{table:interactions}, \autoref{fig:illustration}d), which depends on the phenotypes of the two interaction partners.
 Therefore, the frequency of phenotype $A$ among parents is
@@
 \end{equation}
-where fitness values are taken from \autoref{fig:illustration}a and \autoref{table:interactions}, and the population mean fitness is
+where fitness values are taken from \autoref{fig:illustration}d and \autoref{table:interactions}, and the population mean fitness is
 %\begin{equation} \label{eq:mean_fitness}
@@
 initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoner's dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
+individual in a neighboring site) in a prisoner's dilemma game (\autoref{fig:illustration}d) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}c).
 The expected number of each of these interactions per individual per generation is one.
@@
   \caption{\textbf{Model illustration.} 
-  \textbf{(a)}~Prisoner's dilemma payoff matrix, showing the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-  \textbf{(b)}~Individuals socially interact in pairs in a prisoner's dilemma game.
+  \textbf{(a)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
+  \textbf{(b)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
+  \textbf{(c)}~Individuals socially interact in pairs in a prisoner's dilemma game.
 Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
-  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
-  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
+  \textbf{(d)}~Prisoner's dilemma payoff matrix, showing the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
     }

### 2021-04-18 ms/main.tex
finished my todos except for 'terse style'

@@
 The deterministic conditions are compared to outcomes of stochastic simulations of structured populations.
-Parallels are drawn with Hamilton's rule incorporating assortment and effective relatedness.
+Parallels are drawn with Hamilton's rule incorporating relatedness and assortment.
 \end{abstract}
@@
 
-To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $\alpha$ but has no direct effect on fitness.
+To answer this question, we add a \emph{modifier locus}~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $\alpha$ but has no direct effect on fitness.
 This locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
 Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
-We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain the following result.
+We study the local stability of this equilibrium to invasion by the modifier allele $m$ (this is called \emph{external stability} \citep{Liberman1986modifiers,Altenberg2017}) and obtain the following result.
 \\
@@
 The analysis is in Appendix~\ref{sec:appendixD}.
-This reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we a modifier allele that decreases $\alpha$ appears and invades the population from time to time, then the value of $\alpha$ will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
+This \emph{reduction principle}~\citep{Feldman1972,Altenberg2017} entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
+Furthermore, if a modifier allele that decreases $\alpha$ appears and invades the population from time to time, then the value of $\alpha$ will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
 This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c). 
 Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
+Note that $\alpha$ controls how often an individual \emph{learns} from its interaction partner.
+However, from the \emph{phenotype-centered view}, there is no incentive to do so: a cooperator interacting with a defector will not only pay the cost of cooperation but will also risk being "converted" to defection (with probability $T_B$), whereas a defector interacting with a cooperator will forfeit (with probability $T_A$) the benefit it received.
 
@@
 
-These comparisons between the deterministic unstructured model and the stochastic structured model show that the conditions derived for the deterministic model can be useful for predicting the dynamics under complex scenarios.
+These comparisons show that the conditions derived for the deterministic unstructured model can be useful for predicting the dynamics in stochastic and structured models. 
 Moreover, this structured population model demonstrates that our parameter for interaction-transmission association, $\alpha$, can represent local interactions between individuals.
@@
 
-Our deterministic model provides a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
+Our deterministic model provides a good approximation to outcomes of simulations of a stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
 In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
@@
 Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.
-This mechanism does not require repeated interactions, population structure, or individual recognition.
+This mechanism does not require repeated interactions, spatial structure, or individual recognition.
 We show that high levels of such interaction-transmission association greatly increase the potential for evolution of cooperation.
@@
 
-\newpage
+%\newpage
 

### 2021-04-21 ms/main.tex
More fixes
updated fig 1; revised structure pop

@@
 Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
-Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
-\autoref{fig:illustration}d shows the payoff matrix, i.e.
-the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
+Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$ (i.e.
+donation game).
+\autoref{fig:illustration}d shows the payoff matrix: the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
 
@@
 Note that $\alpha$ controls how often an individual \emph{learns} from its interaction partner.
-However, from the \emph{phenotype-centered view}, there is no incentive to do so: a cooperator interacting with a defector will not only pay the cost of cooperation but will also risk being "converted" to defection (with probability $T_B$), whereas a defector interacting with a cooperator will forfeit (with probability $T_A$) the benefit it received.
+However, from the \emph{phenotype-centred view}, there is no incentive to do so: a cooperator interacting with a defector will not only pay the cost of cooperation but will also risk being "converted" to defection (with probability $T_B$), whereas a defector interacting with a cooperator will forfeit (with probability $T_A$) the benefit it received.
 
@@
 Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
-In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
-initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoner's dilemma game (\autoref{fig:illustration}d) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}c).
-The expected number of each of these interactions per individual per generation is one.
-The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
-On an infinite grid, $M=8$ (i.e. Moore neighborhood), but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
+In each generation, half of the individuals are randomly chosen to "initiate" interactions. 
+These initiators interact (i) in a prisoner's dilemma game (\autoref{fig:illustration}d) with a random neighbour (i.e.
+individual in a neighbouring site); and (ii) in horizontal cultural transmission (\autoref{fig:illustration}c) with a random neighbour (with replacement, i.e.
+possibly the same neighbour).
+The expected number of each of these interactions per individual per generation is one, and in every interaction both individuals are affected, not just the initiator.
+The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbour is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbours.
+On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in edge neighbourhoods close to the grid border.
 As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
@@
 $w = 1 + b \cdot n_b - c \cdot n_c$,
-where $n_b$ is the number of interactions that individual had with cooperative neighbors,
+where $n_b$ is the number of interactions that individual had with cooperative neighbours,
 and $n_c$ is the number of interactions in which that individual cooperated (note that the phenotype may change between consecutive interactions due to horizontal transmission).
-Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
+Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighbouring parents.
 Selection is global, rather than local, in accordance with our deterministic model:
@@
 Changing the simulation so that selection is local (i.e.
-sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+sites can only be settled by offspring of neighbouring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
 
@@
 
-Our deterministic model provides a good approximation to outcomes of simulations of a stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
+Our deterministic model provides a good approximation to outcomes of simulations of a stochastic model with population structure in which individuals can only interact with and transmit to their neighbours.
 In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
@@
   \caption{\textbf{Model illustration.} 
-  \textbf{(a)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
-  \textbf{(b)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
-  \textbf{(c)}~Individuals socially interact in pairs in a prisoner's dilemma game.
+  \textbf{(a)}~First, offspring inherit their parent's phenotype via vertical cultural transmission with probability $v$, or the phenotype of a random non-parental adult via oblique cultural transmission with probability $1-v$.
+  \textbf{(b)}~Second, adults socially interact in pairs in a prisoner's dilemma game.
 Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
-  \textbf{(d)}~Prisoner's dilemma payoff matrix, showing the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+  \textbf{(c)}~The prisoner's dilemma payoff matrix shows the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+    \textbf{(d)}~The probabilities of successful horizontal cultural transmission of phenotypes $A$ (cooperator) and $B$ (defector) are $T_A$ and $T_B$, respectively.
     }
@@
   In all cases, the population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site has 8 neighbors.
+  Cooperation and horizontal transmission are both local between neighbouring sites, and each site has 8 neighbours.
   Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
@@
   The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
+  Cooperation and horizontal transmission are both local between neighbouring sites, and each site had 8 neighbours.
   Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).

### 2021-04-21 ms/main.tex
edits

@@
 Assuming that selection is weak and that the population size is much larger than $k$ (i.e.
-sparse structure), they found that cooperative behaviour can evolve if~\citep{Ohtsuki2006}
+sparse structure), they found that cooperative behaviour can evolve if
 \begin{equation} \label{eq:ohtsuki2006}
@@
 Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
-Note that $\alpha$ controls how often an individual \emph{learns} from its interaction partner.
+Note that $\alpha$ controls how often an individual learns from its interaction partner.
 However, from the \emph{phenotype-centred view}, there is no incentive to do so: a cooperator interacting with a defector will not only pay the cost of cooperation but will also risk being "converted" to defection (with probability $T_B$), whereas a defector interacting with a cooperator will forfeit (with probability $T_A$) the benefit it received.
@@
 In each generation, half of the individuals are randomly chosen to "initiate" interactions. 
-These initiators interact (i) in a prisoner's dilemma game (\autoref{fig:illustration}d) with a random neighbour (i.e.
-individual in a neighbouring site); and (ii) in horizontal cultural transmission (\autoref{fig:illustration}c) with a random neighbour (with replacement, i.e.
+These initiators interact (i) in a prisoner's dilemma game with a random neighbour (i.e.
+individual in a neighbouring site); and (ii) in horizontal cultural transmission with a random neighbour (with replacement, i.e.
 possibly the same neighbour).

### 2021-04-22 ms/main.tex
Fix illustration fig ref

@@
 donation game).
-\autoref{fig:illustration}d shows the payoff matrix: the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
+\autoref{fig:illustration}c shows the payoff matrix: the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
 
@@
 Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}c).
+It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}b).
 %The interaction-transmission association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
 However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
-The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}b).
+The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}d).
 Then, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 The frequency of $A$ among parents follows a similar dynamic but must also include the effect of natural selection.
-Therefore, each right-hand term from \autoref{eq:nextgen_adults} is multiplied by the corresponding fitness value (\autoref{table:interactions}, \autoref{fig:illustration}d), which depends on the phenotypes of the two interaction partners.
+Therefore, each right-hand term from \autoref{eq:nextgen_adults} is multiplied by the corresponding fitness value (\autoref{table:interactions}, \autoref{fig:illustration}c), which depends on the phenotypes of the two interaction partners.
 Therefore, the frequency of phenotype $A$ among parents is
@@
 \end{equation}
-where fitness values are taken from \autoref{fig:illustration}d and \autoref{table:interactions}, and the population mean fitness is
+where fitness values are taken from \autoref{fig:illustration}c and \autoref{table:interactions}, and the population mean fitness is
 %\begin{equation} \label{eq:mean_fitness}

### 2021-04-25 ms/main.tex
MWD and OLE comments

@@
 The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}d).
-Then, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
+Thus, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
 \begin{equation}\label{eq:nextgen_adults}
@@
 \end{equation}
-The right-hand terms in \autoref{eq:nextgen_adults} give the frequencies of the different interactions that produce cooperator adults~(\autoref{table:interactions}).
+For example, the first term in \autoref{eq:nextgen_adults} describes the case where two juveniles with phenotype $A$ interact with probability $\hat{p}^2$.
+In this case, the focal individual will retain its phenotype if (i) its social interaction partner is also its horizontal transmission partner, with probability $\alpha$; or (ii) its horizontal transmission partner is another individual, with probability $(1-\alpha)$, and (ii.a) that individual also has phenotype $A$, with probability $\hat{p}$, or (ii.b) that individual has phenotype $B$, with probability $(1-\hat{p})$, but horizontal transmission is unsuccessful, with probability $(1-T_B)$.
 The frequency of $A$ among parents follows a similar dynamic but must also include the effect of natural selection.
@@
 
-Thus, cooperation can take over the population if it either has a horizontal transmission advantage, or it has a horizontal transmission disadvantage, but the vertical transmission rate is high enough.
+Thus, cooperation can take over the population if it has either a horizontal transmission advantage, or if it has a horizontal transmission disadvantage but the vertical transmission rate is high enough.
 In either case, the cost of cooperation must be small enough.
 A stable polymorphism can exist between cooperation and defection only if defection has a horizontal transmission advantage.
-In this case, the existence of a stable polymorphism depends on an interplay between the benefit and cost of cooperation and the vertical transmission rate.
+In this case, the existence of a stable polymorphism depends on the interplay between the benefit and cost of cooperation and the vertical transmission rate.
 These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
@@
 possibly the same neighbour).
-The expected number of each of these interactions per individual per generation is one, and in every interaction both individuals are affected, not just the initiator.
+The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.
 The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbour is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbours.
-On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in edge neighbourhoods close to the grid border.
+On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in neighbourhoods close to the grid border.
 As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.

### 2021-04-26 ms/main.tex
move SM title to correct place
Fix typo and remove todo
use single pdf file figures

@@
 \pagebreak
-
-% TODO change "scoail association" to "interaction-transmission association"
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
+  \includegraphics[width=1\textwidth]{PRSB_figures/fig_1.pdf}
   \caption{\textbf{Model illustration.} 
@@
   \centering       
-    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
+    \includegraphics[width=1\textwidth]{PRSB_figures/fig_2.pdf}
     \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
@@
     \label{fig:equilibria}
-    %TODO update y label on c d
 \end{figure}
@@
   \centering       
-    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
-	  ~
-    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
-    ~
-    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
-    ~
-    \includegraphics[width=0.48\textwidth]{coexistence_without_oblique.eps}
+	\includegraphics[width=1\textwidth]{PRSB_figures/fig_3.pdf}
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
@@
     \label{fig:equilibria_v1}
-    %TODO update y label on c d
 \end{figure}
@@
   \centering
-	\includegraphics[width=0.3\textwidth]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
-    ~
-	\includegraphics[width=0.3\textwidth]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
-    ~
-    \includegraphics[width=0.36\textwidth]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
+  \includegraphics[width=1\textwidth]{PRSB_figures/fig_4.pdf}
   \caption{
@@
 \newpage
-\section*{\huge{Supplementary material}}
-\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % Appendices
@@
 
-% Supporting figures
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
-\section*{Supporting figures}
+
+\section*{\huge{Supplementary material}}
+\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \centering
-   \includegraphics[scale=0.5]{Figures/invasion.eps}
+  \includegraphics[width=1\textwidth]{PRSB_figures/fig_s1.pdf}
   \caption{
@@
   \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
-    ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
+  \includegraphics[width=1\textwidth]{PRSB_figures/fig_s2.pdf}
   \caption{

### 2021-04-27 ms/main.tex
typo in appB
extracted supp figs to si.tex

@@
 The analysis is in Appendix~\ref{sec:appendixD}.
-This \emph{reduction principle}~\citep{Feldman1972,Altenberg2017} entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
+This \emph{reduction principle}~\citep{Feldman1972,Altenberg2017} entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (Figure S1).
 Furthermore, if a modifier allele that decreases $\alpha$ appears and invades the population from time to time, then the value of $\alpha$ will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
 This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c). 
-Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
+Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (Figure S1).
 Note that $\alpha$ controls how often an individual learns from its interaction partner.
@@
 Changing the simulation so that selection is local (i.e.
-sites can only be settled by offspring of neighbouring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
+sites can only be settled by offspring of neighbouring parents) had only a minor effect on the agreement with the derived conditions (Figure S2).
 
@@
 We find that stronger interaction-transmission association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, $\alpha$ is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
+Nevertheless, when cooperation and defection coexist, $\alpha$ is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, Figure S1).
 With $\alpha=0$, the benefit of cooperation cannot facilitate its evolution; it can only succeed if horizontal transmission is biased in its favor.
@@
   Cooperation and horizontal transmission are both local between neighbouring sites, and each site has 8 neighbours.
-  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
+  Selection operates globally (see Figure S2 for results from a model with local selection).
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
@@
 	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
-\item \emph{polymorphism of both phenotypes at $\hat{p}^*$}: 
+\item \emph{Stable polymorphism with both phenotypes at $\hat{p}^*$}: 
 	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section*{\huge{Supplementary material}}
-\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% Figure: Invasion
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=1\textwidth]{PRSB_figures/fig_s1.pdf}
-  \caption{
-  \textbf{Reduction principle for interaction-transmission association.} 
-  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
-  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
-  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
-  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
-  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
-  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
-  }
-  \label{fig:invasion}
-\end{figure}
-
-%%% Figure: Spatial model - local selection
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=1\textwidth]{PRSB_figures/fig_s2.pdf}
-  \caption{
-  \textbf{Evolution of cooperation in a structured population with local selection.}
-  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
-  Cooperation and horizontal transmission are both local between neighbouring sites, and each site had 8 neighbours.
-  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
-  The population evolves on a 100-by-100 grid.
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed.
-  50 simulations were executed for each parameter set.
-  Here, benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
-  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
-  }
-  \label{fig:spatial_local_selection}
-\end{figure}
-
 %%%

### 2021-04-27 ms/si.tex
extracted supp figs to si.tex

--- 2021-01-30 ms/Thesis/thesis.tex
@@
 % TeX will automatically convert eps --> pdf in pdflatex
-\graphicspath{ {../Figures/} }
+\graphicspath{ {./Figures/} }
 \usepackage[labelfont=bf]{caption}
@@
 
-% Line Spacing 
-\linespread{1.25}
+% less space before sections 
+% https://tex.stackexchange.com/a/101126
+\usepackage{titlesec}
+\titlespacing*{\section}{0pt}{0.5\baselineskip}{0\baselineskip}
+\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0\baselineskip}
 
@@
 
-% Abstract
-\begin{abstract}
-Cultural evolution of cooperation under vertical and non-vertical cultural transmission is studied, and conditions are found for fixation and coexistence of cooperation and defection. 
-The evolution of cooperation is facilitated by its horizontal transmission and by an association between social interactions and horizontal transmission.
-The effect of oblique transmission depends on the horizontal transmission bias.
-Stable polymorphism of cooperation and defection can occur, and
-when it does, reduced association between social interactions and horizontal transmission evolves, which leads to a decreased frequency of cooperation and lower population mean fitness.
-The deterministic conditions are compared to outcomes of stochastic simulations of structured populations.
-Parallels are drawn with Hamilton's rule incorporating assortment and effective relatedness.
-\end{abstract}
-
-\pagebreak
-
-\tableofcontents
-\pagebreak
-
-% TODO change "scoail association" to "interaction-transmission association"
+\section*{\huge{Supplementary material}}
+\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Introduction
-\section{Introduction}
-Cooperative behavior can reduce an individual's fitness and increase the fitness of its conspecifics or competitors~\citep{axelrod1981evolution}.
-Nevertheless, cooperative behavior appears to occur in many animals~\citep{dugatkin1997cooperation}, including humans, primates~\citep{jaeggi2013natural},  rats~\citep{rice1962altruism}, birds~\citep{stacey1990cooperative,krams2008experimental}, and lizards~\citep{sinervo2006self}.
-Evolution of cooperative behavior has been an important focus of research in evolutionary theory since at least the 1930s~\citep{Haldane1932book}.
-Since the work of  \citet{hamilton1964genetical} and \citet{axelrod1981evolution}, theories for the evolution of cooperative and altruistic behaviors have been intertwined often under the rubric of \emph{kin selection}.
-Kin selection theory posits that natural selection is more likely to favor cooperation between more closely related individuals.
-The importance of \emph{relatedness} to the evolution of cooperation and altruism was demonstrated by \citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
-This condition is  known as \emph{Hamilton's rule}:
-\begin{equation} \label{eq:hamilton_rule}
-c < b \cdot r,
-\end{equation}
-where the relatedness coefficient $r$ measures the probability that an allele sampled from the cooperator is identical by descent to one at the same locus in the recipient.
-
-There is an ongoing debate about to what extent kin selection explains evolution of cooperation and altruism.
-It has been suggested that kin selection to explain the cooperative behaviour of eusocial insects like the honey bee.
-The most significant argument against kin selection is that cooperation can evolve with zero relatedness \cite{wilson2005kin}.
-This makes Hamilton's rule incomplete according to Wilson \cite{wilson2005kin}.
-Foster et al.
-\cite{foster2006kin} reject this claim.
-They argue that altruism without relatedness can not evolve. They refer us to Hamilton who claimed that relatedness can arise without recent common ancestry. 
-Wilson also criticises kin selection on the grounds that environmental or ecological factors probably be more important than relatedness in determining social actions.
-On the other hand, Foster et al.
-\cite{foster2006kin} argue that kin selection does not ignore ecology.
-Hamilton’s rule shows that environmental factors causing a high benefit: cost ratio will favour cooperation.
-
-Beside kin selection, two more major theroies were suggested to explain to evolution of cooperation.
-
-\textbf{Reciprocity} suggests repeating interactions or individual recognition as key factors for explaining the evolution of cooperation. 
-In \textit{direct reciprocity} there are a repeated encounters between the same two individuals.
-In every encounter, each player has a choice between cooperation and defection.
-If I cooperate now, you may cooperate later.
-Hence, it may pay off to cooperate.
-This game-theoretic framework is known as the repeated Prisoner's Dilemma. 
-Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit. 
-\begin{equation} \label{reciprocity}
-c<bw
-\end{equation}
-Direct reciprocity assumes that both players are in a position to cooperate.
-Direct reciprocity can not explain cooperation in asymmetric interactions.
-In humans, such interactions happen often, for example humans often donate money.
-\textit{Indirect reciprocity} has been suggested to explain this behavior. 
-Nowak \cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
-The money that "fuels the engines" of indirect reciprocity is reputation.
-However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.
-
-\textbf{Group Selection} theory posits that cooperation is favoured because of the advantage to the whole group, if selection acts at the group level in addition to the individual level.
-A common model for group selection work as is: the population is divided into groups.
-In each groups there are cooperators, which help to other group members and defectors which do not help.
-Individuals reproduce proportional to their fitness. Offspring are added to the same group.
-If a group reaches a certain size it can split to two groups. A group that grow faster will split more often. Groups of cooperators are growing faster than group of defectors.
-Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
-\begin{equation} \label{groupselection}
-\frac{b}{c}>1+\frac{n}{m}
-\end{equation}
-
-All three theories mentioned above assume that cooperation is genetically determined. This raise the question, is it possible that cooperation is determined by environmental or social influences.
-Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
-Cultural transmission may be  modeled as vertical, horizontal, or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
-from non-parental adults).
-Evolution under either of these transmission models can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-
-Here, we study models for the cultural evolution of cooperation that include both vertical and non-vertical transmission. 
-%We investigate these models using mathematical analysis and simulations.  
-In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
-For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission,
-or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it can facilitate the generation of assortment \citep{Fletcher2009assortment}, and partly because it can diminish the effect of natural selection \citep{ram2018evolution}.
-
-\newpage
-\section{Related Work}
-
-\citet{Eshel1982} studied a related model for the evolution of cooperative behavior.
-Their model included \emph{assortative meeting}, or non-random encounters, where a fraction $m$ of individuals in the population each interact specifically with an individual of the same phenotype, and a fraction $1-m$ interacts  with a randomly chosen individual.
-Such assortative meeting may be due, for example, to population structure or active partner choice.
-In their model, cooperative behavior can evolve if
-\citep[eq.~3.2]{Eshel1982}
-\begin{equation} \label{eq:eshel1982}
-c < b \cdot m \,,
-\end{equation}
-where $b$ and $c$ are the benefit and cost of cooperation\footnote{In an extended model, which allows an individual to encounter $N$ individuals before choosing a partner, the right hand side is multiplied by $E[N]$, the expected number of encounters \citep[eq.~4.6]{Eshel1982}.
-}. 
-%Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness coefficient $r$ in inequality~\ref{eq:hamilton_rule}.
-
-The role of assortment in the evolution of altruism was emphasized by \citet{Fletcher2009assortment}.
-They found that in a \emph{public-goods} game, altruism will evolve if cooperative individuals experience more cooperation, on average, than defecting individuals, and ``thus, the evolution of altruism requires (positive) assortment between focal \emph{cooperative} players and cooperative acts in their interaction environment.''
-With some change in parameters, this condition is summarized by \citep[eq.~2.3]{Fletcher2009assortment}
-\begin{equation} \label{eq:fletcher2009}
-c < b \cdot (p_C - p_D ) \,,
-\end{equation}
-where $p_C$ is the probability that a cooperator receives help, and $p_D$ is the probability that a defector receives help.\footnote{Inequality~\ref{eq:fletcher2009} generalizes inequalities~\ref{eq:hamilton_rule} and~\ref{eq:eshel1982} by substituting $p_C=r + p$, $p_D=p$ and $p_C=m + (1-m)p$, $p_D=(1-m)p$, respectively, where $p$ is the frequency of cooperators.}
-\citet{Bijma2010assortment} obtained a result related to inequality~\ref{eq:fletcher2009} for other types of games.
-
-\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission with kin selection and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
-\begin{equation} \label{eq:feldman1985}
-c < b \cdot \varphi - \frac{1-\varphi}{\varphi} \,.
-\end{equation}
-In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
-This shows that under a cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).
-
-Both \citet{woodcock2006significance} and \citet{lewin2017microbes} demonstrated that non-vertical transmission can help explain the evolution of cooperative behavior, the former using simulations with cultural transmission, the latter using a model where cooperation is mediated by host-associated microbes.
-Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Models
-\newpage
-\section{Models}
-
-Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
-An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}a).
-Following~\citet{ram2018evolution}, given that the parent's phenotype is $\phi$ and assuming uni-parental inheritance~\citep{Zefferman2016}, the conditional probability that the phenotype $\phi'$ of the offspring is $A$ is
-\begin{equation} \label{eq:vertical_oblique_transmission}
-P(\phi'=A \mid \phi) = \begin{cases}
-v + (1-v)p, & \text{if } \phi=A \\
-(1-v)p, & \text{if } \phi=B
-\end{cases},
-\end{equation}
-where $p=P(\phi=A)$ is the frequency of $A$ among all adults in the parental generation.
-
-Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\tilde{p}$.
-Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
-\begin{equation}\label{eq:horizontal}
-\begin{aligned}
-\hat{p} \;=
-\tilde{p} [v + (1-v)p] + (1-\tilde{p}) [(1-v)p] \;= 
-v \tilde{p} + (1-v) p \;.
-\end{aligned}
-\end{equation}
-Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
-Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
-\autoref{fig:illustration}a shows the payoff matrix, i.e.
-the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
-
-%%% Figure: model illustration
-\begin{figure}[pt]
-  \centering
-  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
-  \caption{\textbf{Model illustration.} 
-  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
-Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
-  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
-  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
-    }
-  \label{fig:illustration}
-\end{figure}
-
-Social interactions occur randomly:
-two juvenile individuals with phenotype $A$ interact with probability~$\hat{p}^2$, two juveniles with phenotype $B$ interact with probability $(1-\hat{p})^2$, and two juveniles with different phenotypes interact with probability $2\hat{p}(1-\hat{p})$.
-Horizontal cultural transmission occurs between pairs of individuals from the same generation. 
-It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}b).
-%The interaction-transmission association $\alpha$ is therefore the fraction of population that receives (horizontal transmission) from the social interaction partner, and $1-\alpha$ receives randomly.
-However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
-The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}c).
-Then, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
-\begin{equation}\label{eq:nextgen_adults}
-\begin{aligned}
-p' \;= \;
-& \hat{p}^2 \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
-& \hat{p}(1-\hat{p}) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
-& (1-\hat{p})\hat{p} \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+ 
-(1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \\
-=\; & \hat{p}^2(T_B-T_A) \;+\; \hat{p}(1+T_A-T_B) \;.
-\end{aligned}
-\end{equation}
-The frequency of $A$ among parents (i.e. after selection) follows a similar dynamic, but also includes the effect of natural selection, and is therefore
-\begin{equation}\label{eq:nextgen_parents}
-\begin{aligned}
-\bar{w} \tilde{p}' =
-& \hat{p}^2 (1+b-c) \big[\alpha + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
-& \hat{p}(1-\hat{p}) (1-c) \big[\alpha(1-T_B) + (1-\alpha)\big(\hat{p} + (1-\hat{p})(1-T_B)\big)\big] \;+ \\
-& (1-\hat{p})\hat{p} (1+b) \big[\alpha T_A + (1-\alpha) \hat{p} T_A \big] \;+\; 
-(1-\hat{p})^2 \big[(1-\alpha) \hat{p} T_A \big] \;,
-\end{aligned}
-\end{equation}
-where fitness values are taken from \autoref{fig:illustration}a and \autoref{table:interactions}, and the population mean fitness is
-$\bar{w} =  1 + \hat{p}(b-c)$.
-Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults} and $\tilde{p}'$ from \autoref{eq:nextgen_parents} and obtain
-\begin{equation} \label{eq:nextgen_juveniles}
-\begin{aligned}
-\hat{p}' =
-& \frac{v}{\bar{w}}\Big[\hat{p}^2(1+b-c)\Big(1-(1-\hat{p})(1-\alpha)T_B)\Big)\Big] \;+ \\
-& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1-c)\big( \hat{p}(1-\alpha)T_B + 1 - T_B \big) \Big] \;+ \\
-& \frac{v}{\bar{w}}\Big[ \hat{p}(1-\hat{p})(1+b)\big(\hat{p}(1-\alpha) + \alpha \big) T_A \Big] \;+ \\
-& \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \;+\;
-(1-v)\hat{p}^2(T_B-T_A) \;+\;
-(1-v)\hat{p}(1+T_A-T_B) \;.
-\end{aligned}
-\end{equation}
-\autoref{table:vars_params} lists the model variables and parameters.
-
-%%% Table: variables and parameters
-%%%% Table
-\begin{table}[h]
-  \caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
-  \begin{tabular}{@{}llllll@{}}
-  \toprule
-  \multirow{2}{*}{Phenotype $\phi_1$} &
-    \multirow{2}{*}{Phenotype $\phi_2$} &
-    \multirow{2}{*}{Frequency} &
-    \multirow{2}{*}{Fitness of $\phi_1$} &
-    \multicolumn{2}{l}{$P(\phi_1=A)$ via horizontal transmission:} \\ \cmidrule(l){5-6} 
-      &     &                      &         & from partner, $\alpha$ & from population, $(1-\alpha)$ \\ \cmidrule(r){1-6}
-  $A$ & $A$ & $\hat{p}^2$          & $1+b-c$ & 1                      & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-  $A$ & $B$ & $\hat{p}(1-\hat{p})$ & $1-c$   & $1-T_B$                & $\hat{p}+(1-\hat{p})(1-T_B)$  \\
-  $B$ & $A$ & $\hat{p}(1-\hat{p})$ & $1+b$   & $T_A$                  & $\hat{p} T_A$                 \\
-  $B$ & $B$ & $(1-\hat{p})^2$      & $1$     & $0$                    & $\hat{p} T_A$                 \\ \bottomrule
-  \end{tabular}
-  \label{table:interactions}
-\end{table}
-\bigskip
-
-\begin{table}[h]
-\centering
-\caption{\textbf{Model variables and parameters.}
-}
-\begin{tabular}{lll}
-\toprule
-Symbol & Description & Values \\ \cmidrule(r){1-3}
-$A$ & Cooperator phenotype & \\
-$B$ & Defector phenotype & \\
-$p$ & Frequency of phenotype $A$ among adults & $[0,1]$ \\
-$\tilde p$ & Frequency of phenotype $A$ among parents & $[0,1]$ \\
-$\hat p$ & Frequency of phenotype $A$ among juveniles & $[0,1]$ \\
-$v$ & Vertical transmission rate & $[0,1]$ \\
-$c$ & Cost of cooperation & $(0,1)$ \\
-$b$ & Benefit of cooperation & $c<b$ \\
-$\alpha$ & Probability of interaction-transmission association & $[0,1]$ \\
-$T_A, T_B$ & Horizontal transmission rates of phenotype $A$ and $B$ & $(0,1)$ \\
-\\ \bottomrule
-\end{tabular}
-\label{table:vars_params}
-\end{table}
-%\bigskip
-%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Results
-\newpage
-\section{Results}
-
-We determine the equilibria of the model in \autoref{eq:nextgen_juveniles}
-%namely, solutions of $\hat{p}' = \hat{p}$, 
-and analyze their local stability.
-We then analyze the evolution of a modifier of interaction-transmission association,~$\alpha$.
-Finally, we compare derived conditions to outcomes of stochastic simulations with a structured population.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolution of cooperation}
-
-The fixed points (equilibria) of  the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
-\begin{equation} \label{eq:general_equilibrium}
-  \hat{p}^* =  
-  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
-\end{equation}
-
-Define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
-\begin{equation} \label{eq:cost_thresholds_v_threshold} 
-\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
-\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}, \quad
-\hat v = \frac{T_B - T_A}{1-T_A} \;.
-\end{equation}
-
-Then we have the following result.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}%[Equilibria and stability]
-\label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
-
-% in gamma
-\begin{enumerate}
-\item \emph{Fixation of cooperation}: 
-	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or 
-	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \gamma_2$.
-\item \emph{Fixation of defection}: 
-    if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or 
-	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
-\item \emph{Stable polymorphism}: 
-    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
-    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
-\item \emph{Unstable polymorphism}:
-    if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
-\end{enumerate}
-
-\end{result}
-These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
-
-Much of the literature on evolution of cooperation focuses on conditions for  an initially rare cooperative phenotype to invade a population of defectors.
-The following remarks address this condition.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}%[Condition on $c$ for cooperation to increase when rare, i.e., $\hat{p}'>p$ near $p=0$]
-\label{remark:rarity}
-If the initial frequency of cooperation is very close to zero, then its frequency will increase if the cost of cooperation is low enough,
-\begin{equation} \label{eq:unequal_transmission_from_rarity_general_case}
-c < \gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)} \;.
-\end{equation} 
-\end{remark}
-
-This unites the conditions for fixation of cooperation and for stable polymorphism, both of which entail instability of the state where defection is fixed, $\hat{p}=0$.
-
-Importantly, increasing interaction-transmission association $\alpha$ increases the cost threshold ($\partial \gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase in frequency when initially rare.
-Similarly, increasing the horizontal transmission of cooperation, $T_A$, increases the threshold ($\partial \gamma_1 / \partial T_A > 0$), facilitating the evolution of cooperation ((\autoref{fig:equilibria_v1}a and \ref{fig:equilibria_v1}b).
-However, increasing the horizontal transmission of defection, $T_B$, can increase or decrease the cost threshold, but it increases the cost threshold when the threshold is already above one ($c<1<\gamma_1$): $\partial\gamma_1/\partial T_B$ is positive when $T_A > \frac{1}{1+\alpha b v}$, which gives $\gamma_1>1/v$.
-Therefore, increasing $T_B$ decreases the cost threshold and limits the evolution of cooperation, but only if $T_A < \frac{1}{1+\alpha b v}$.
-
-Increasing the vertical transmission rate, $v$, can either increase or decrease the cost threshold, depending on the horizontal transmission bias, $T_A-T_B$, because $\text{sign}(\partial \gamma_1 / \partial v) = -\text{sign}(T_A-T_B)$.
-When $T_A<T_B$ we have $\partial \gamma_1 / \partial v >0$, and as the vertical transmission rate increases, the cost threshold increases, making it easier for cooperation to increase when rare (\autoref{fig:equilibria}b).
-In contrast, when $T_A > T_B$ we get $\partial \gamma_1 / \partial v <0$, and therefore as the vertical transmission rate increases, the cost threshold decreases, making it harder for cooperation to increase when rare (\autoref{fig:equilibria}a).
-
-In general, this condition cannot be formulated in the form of Hamilton's rule due to the bias in horizontal transmission, represented by $T_A-T_B$.
-If $T_A=T_B$, then, from Result~\ref{result:vert_obli_hori} and inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation will take over the population from any initial frequency if the cost is low enough,
-\begin{equation}
-\label{eq:equal_transmission}
-c < b \cdot \frac{\alpha T}{1-T} \;,
-\end{equation}
-and regardless of the vertical transmission rate, $v$.
-This condition can be interpreted as a version of Hamilton's rule  ($c<b\cdot r$, inequality~\ref{eq:hamilton_rule}) or as a version of inequality~\ref{eq:fletcher2009}, where $\alpha T/(1-T)$ can be regarded as the \emph{effective relatedness} or \emph{effective assortment}, respectively.
-Note that the right-hand side of inequality~\ref{eq:equal_transmission} equals $\gamma_1$ when $T=T_A=T_B$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-From inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, without interaction-transmission association ($\alpha=0$), cooperation will increase when it is rare if there is horizontal transmission bias for cooperation, $T_A>T_B$, and
-\begin{equation}
-\label{eq:vert_hori_alpha0}
-c < \frac{T_A - T_B}{v(1-T_B)} \;.
-\end{equation}
-
-\autoref{fig:equilibria_v1}a illustrates this condition (for $v=1$), which is obtained by setting $\alpha=0$ in inequality~\ref{eq:unequal_transmission_from_rarity_general_case}.
-In this case, the benefit of cooperation, $b$, does not affect the evolution of cooperation, and the outcome is determined only by  cultural transmission.
-Further, inequality~\ref{eq:unequal_transmission_from_rarity_general_case} shows that with perfect interaction-transmission association ($\alpha=1$), cooperation will increase when rare if
-\begin{equation}\label{eq:vert_hori_alpha1}
-c < \frac{b v T_A + (T_A - T_B)}{v(1-T_B)} \;.
-\end{equation}
-
-In the absence of oblique transmission, $v=1$, the only equilibria are the fixation states, $\tilde{p}=0$ and $\tilde{p}=1$, and cooperation will evolve from any initial frequency (i.e., $\tilde{p}'>\tilde{p}$) if inequality~\ref{eq:vert_hori_alpha1} applies (\autoref{fig:equilibria_v1}).
-This is similar to case of microbe-induced cooperation studied by \citet{lewin2017microbes}; therefore when $v=1$, this remark is equivalent to their eq.~1.
-
-It is interesting to examine the general effect of interaction-transmission association $\alpha$ on the evolution of cooperation.
-Define the interaction-transmission association thresholds, $a_1$ and $a_2$, as 
-\begin{equation} \label{eq:boundries_assortative_meeting_general_case}
-  a_1 = \frac{c\cdot v(1-T_A) -(T_A-T_B)(1+b-c)}{b\cdot v \cdot T_B}, \quad
-  a_2 = \frac{c\cdot v(1-T_B)-(T_A-T_B)}{b\cdot v\cdot T_A} \;.
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{remark}%[Condition on interaction-transmission association $\alpha$ for cooperation to increase when it is rare]
-\label{remark:intermediate_association_res3}
-Cooperation will increase when rare if interaction-transmission association is high enough, specifically if $a_2 < \alpha$.
-\end{remark}
-Figures~\ref{fig:equilibria}c and \ref{fig:equilibria}d illustrate this condition.
-With horizontal transmission bias for cooperation, $T_A>T_B$, cooperation can fix from any initial frequency if $a_2<\alpha$ (green area in the figures). 
-With horizontal bias favoring defection, $T_A<T_B$, cooperation can fix from any frequency if $\alpha$ is large enough, $a_1<\alpha$ (green area with $T_A<T_B$), and can reach stable polymorphism if $\alpha$ is intermediate, $a_2<\alpha<a_1$ (yellow area).
-Without horizontal bias, $T_A=T_B$, fixation of cooperation occurs if $\alpha$ is high enough, $\frac{c}{b} \cdot \frac{1-T}{T} < \alpha$ (inequality~\ref{eq:equal_transmission}; in this case $a_1=a_2$).
-
-Interestingly, because $\text{sign} (\partial a_2 / \partial v) = \text{sign} (T_A-T_B)$, the effect of the vertical transmission rate $v$ on $a_1$ and $a_2$ depends on the horizontal transmission bias.
-That is, if $T_A>T_B$, then evolution of cooperation is facilitated by oblique transmission, whereas if $T_A<T_B$, then evolution of cooperation is facilitated by vertical transmission (Figures~\ref{fig:equilibria}c and~\ref{fig:equilibria}d).
-\\
-
-Next, we examine the roles of vertical and oblique transmission in the evolution of cooperation.
-Fixation of cooperation is possible only if the vertical transmission rate is high enough,
-  \begin{equation} \label{eq:fixation_of_cooperation_vertical_transmission_condition}
-    \begin{aligned}
-      v>\hat{v} = \frac{T_B - T_A}{1-T_A} \;.
-    \end{aligned}
-    \end{equation} 
-This condition is necessary for fixation of cooperation, but it is not sufficient.
-If horizontal transmission is biased for cooperation, $T_A>T_B$, cooperation can fix with any vertical transmission rate (because $\hat{v}<0$).
-In contrast, if horizontal transmission is biased for defection, $T_A<T_B$,  cooperation can fix only if the vertical transmission rate is high enough: in this case oblique transmission can prevent fixation of cooperation (see Figures~\ref{fig:equilibria}b and \ref{fig:equilibria}d).
-
-With only vertical transmission ($v=1$), from inequality~\ref{eq:unequal_transmission_from_rarity_general_case}, cooperation increases when rare if
-\begin{equation} \label{eq:vert_hori}
-c < \frac{b \alpha T_A + (T_A - T_B)}{1-T_B} \;,
-\end{equation} 
-which can also be written as
-\begin{equation} \label{eq:vert_hori_alpha}
-\frac{c (1-T_B)-(T_A-T_B)}{b T_A} < \alpha \;.
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the absence of vertical transmission ($v=0$), from recursion~\ref{eq:nextgen_juveniles} we see that the frequency of the cooperator phenotype among adults increases every generation, i.e.
-$p'>p$, if there is a horizontal transmission bias in favor of cooperation, namely $T_A > T_B$.
-That is, if $v=0$, then selection plays no role in the evolution of cooperation (i.e., $b$ and $c$ do not affect $\hat p'$).
-The dynamics are determined solely by differential horizontal transmission of the two phenotypes.
-With no bias in horizontal transmission, $T_A = T_B$, phenotype frequencies do not change, $\hat p'=\hat p$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Cooperation and defection can coexist at frequencies $\hat{p}^*$ and $1-\hat{p}^*$ (\autoref{eq:general_equilibrium}). 
-When it is feasible, this equilibrium is stable or unstable under the conditions of Result \ref{result:vert_obli_hori}, parts 3 and 4, respectively.
-The yellow and blue areas in Figures~\ref{fig:equilibria_v1} and \ref{fig:equilibria} show cases of stable and unstable polymorphism, respectively.
-When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$.
-$\hat{p}^*$ is unstable when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:equilibria_v1}d shows $\hat{p}'-\hat{p}$ as a function of $\hat{p}$.
-
-\begin{figure}[p]
-  \centering       
-    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
-    \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
-    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
-unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-	In all cases the vertical transmission rate $v$ is on the x-axis.
-	(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (Eqs.~\ref{eq:cost_thresholds_v_threshold}) are represented by the solid and dashed lines, respectively.
-    (\textbf{c-d})~Interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are represented by the solid and dashed lines, respectively.
-    Horizontal transmission is biased in favor of cooperation, $T_A>T_B$, in (\textbf{a}) and (\textbf{c}), or defection, $T_A<T_B$, in (\textbf{b}) and (\textbf{d}).    
-    Here, $T_A = 0.5$, and
-    (\textbf{a}) $b=1.2$, , $T_B = 0.4$, $\alpha = 0.4$;
-    (\textbf{b}) $b=2$, $T_B = 0.7$, $\alpha = 0.7$;
-    (\textbf{c}) $b=1.2$, $T_B = 0.4$, $c=0.5$;
-    (\textbf{d}) $b=2$, $T_B = 0.7$, $c=0.5$.
-    }
-    \label{fig:equilibria}
-    %TODO update y label on c d
-\end{figure}
-
-%%% Figure: thresholds figure - only vertical
-
-\begin{figure}[p]
-  \centering       
-    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
-	  ~
-    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
-    ~
-    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
-    ~
-    \includegraphics[width=0.48\textwidth]{coexistence_without_oblique.eps}
-    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
-    The figure shows parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e.
-unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
-    (\textbf{a-c})~The horizontal transmission bias ($T_A-T_B$) is on the x-axis.
-    In panels \textbf{(a)} and \textbf{(b)}, the cost of cooperation $c$ is on the y-axis and the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively.
-	In panel \textbf{(c)}, interaction-transmission association $\alpha$ is on the y-axis and the interaction-transmission association thresholds $a_1$ and $a_2$ (Eqs.~\ref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
-    Here, $b=1.3$, $T_A=0.4$, $v=1$, (a)~$\alpha = 0$, (b)~$\alpha = 0.7$, (c)~$c = 0.35$.    
-    \textbf{(d)}~Change in frequency of cooperation among juveniles ($\hat{p}'-\hat{p}$) as a function of the frequency ($\hat{p}$), see \autoref{eq:nextgen_juveniles}.
-    The orange curve shows convergence to a stable polymorphism ($T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $v=1$, and $\alpha = 0.45$). % todo ref eq 12
-    The blue curve shows fixation of either cooperation or defection, depending on the initial frequency ($T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $v=1$, and $\alpha = 0.4$).
-    Black circles show the three equilibria.
-  	}
-    \label{fig:equilibria_v1}
-    %TODO update y label on c d
-\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolution of interaction-transmission association}
-
-We now focus on the evolution of interaction-transmission association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
-Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}), see \autoref{fig:equilibria_v1}b.
-The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
-Therefore, $\bar{w}^*$ increases as $\alpha$ increases.
-But can this population-level advantage lead to the evolution of $\alpha$?
-
-To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $alpha$ but has no direct effect on fitness.
-This locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
-Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
-We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain the following result.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{result}%[Reduction principle for interaction-transmission association] 
-\label{result:evol_social_association}
-From a stable polymorphism between cooperation and defection, a modifier allele can successfully invade the population if it decreases the interaction-transmission association $\alpha$.
-\end{result}
-
-The analysis is in Appendix~\ref{sec:appendixD}.
-This reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
-Furthermore, if we a modifier allele that decreases $\alpha$ appears and invades the population from time to time, then the value of $\alpha$ will continue to decrease, further reducing the frequency of cooperation and the population mean fitness.
-This evolution will proceed as long as there is a stable polymorphism, that is, as long as $a_2 < \alpha < a_1$ (Remark~\ref{remark:intermediate_association_res3}, \autoref{fig:equilibria_v1}c). 
-Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Population structure}
-Interaction-transmission association may also emerge from population structure.
-Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
-Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
-Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
-In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
-initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
-The expected number of each of these interactions per individual per generation is one.
-The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
-On an infinite grid, $M=8$, but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
-As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
-
-The order of the interactions across the grid at each generation is random.
-After all interactions take place, an individual's fitness is determined by
-$w = 1 + b \cdot n_b - c \cdot n_c$,
-where $n_b$ is the number of interactions that individual had with cooperative neighbors,
-and $n_c$ is the number of interactions in which that individual cooperated (note that the phenotype may change between consecutive interactions due to horizontal transmission).
-Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
-Selection is global, rather than local, in accordance with our deterministic model:
-The parent is randomly drawn with probability proportional to its fitness, divided by the sum of the fitness values of all potential parents.
-Offspring are assumed to have the same phenotype as their parents (i.e. $v=1$).
-
-The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
-An example of stochastic stable polymorphism is shown in \autoref{fig:spatial}c.
-Changing the simulation so that selection is local (i.e., sites can only be settled by offspring of neighboring parents) had only a minor effect on the agreement with the derived conditions (\autoref{fig:spatial_local_selection}).
-
-These comparisons between the deterministic unstructured model and the stochastic structured model show that the conditions derived for the deterministic model can be useful for predicting the dynamics under complex scenarios.
-Moreover, this structured population model demonstrates that our parameter for interaction-transmission association, $\alpha$, can represent local interactions between individuals.
 
@@
   \centering
-   \includegraphics[scale=0.5]{../Figures/invasion.eps}
+  \includegraphics[width=1\textwidth]{PRSB_figures/fig_s1.pdf}
   \caption{
   \textbf{Reduction principle for interaction-transmission association.} 
-  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
+  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (Eq.~D1).
   When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
@@
 
-\newpage
-
-%%% Figure: Spatial model - global selection
-\begin{figure}[h]
-  \centering
-	\includegraphics[width=0.3\textwidth]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
-    ~
-	\includegraphics[width=0.3\textwidth]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
-    ~
-    \includegraphics[width=0.36\textwidth]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
-  \caption{
-  \textbf{Evolution of cooperation in a structured population.}
-	\textbf{(a-b)}~The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation, $c$, on the y-axis, and either the symmetric horizontal transmission rate, $T=T_A=T_B$, on the x-axis of panel~\textbf{(a)}, or the transmission bias, $T_A-T_B$, on the x-axis of panel~\textbf{(b)}.
-  Black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for  panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
-	The inset in panel~\textbf{(b)} focuses on an area of the parameter range in which neither phenotype is fixed throughout the simulation, maintaining a stochastic locally stable polymorphism~\citep{Karlin1975}.
-	This stochastic polymorphism is illustrated in panel~\textbf{(c)}, which shows the frequency of cooperators (green) and defectors (red) over time for the parameter set marked by an~\textit{x} in panel~\textbf{(b)}.
-  In all cases, the population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site has 8 neighbors.
-  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
-  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
-  Benefit of cooperation, $b=1.3$; perfect vertical transmission $v=1$.
-  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$;
-  \textbf{(b)} Horizontal transmission rate $T_A$ is fixed at $0.4$, and $T_B$ varies, $0.3<T_B<0.5$.
-  \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
-  }
-  \label{fig:spatial}
-\end{figure}
-
-\newpage
-
 %%% Figure: Spatial model - local selection
@@
   The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as a function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of panel~\textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of panel~\textbf{(b)}.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site had 8 neighbors.
-  Selection operates locally (see \autoref{fig:spatial} for results from a model with global selection).
-  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~\ref{eq:equal_transmission} for panel~\textbf{(a)} and in Eqs.~\ref{eq:cost_thresholds_v_threshold} for panel~\textbf{(b)}.
+  Cooperation and horizontal transmission are both local between neighbouring sites, and each site had 8 neighbours.
+  Selection operates locally (see Figure 4 for results from a model with global selection).
+  The black curves represent the cost thresholds for the evolution of cooperation in a well-mixed population with interaction-transmission association, where $\alpha=1/8$ in inequality~14 for panel~\textbf{(a)} and in Eqs.~12 for panel~\textbf{(b)}.
   The population evolves on a 100-by-100 grid.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Discussion
-\newpage
-\section{Discussion}
-Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
-Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~\ref{eq:unequal_transmission_from_rarity_general_case},
-$
-c \cdot v (1-T_B) < b \cdot v \alpha T_A + (T_A - T_B) \;,
-$
-namely, the effective cost of cooperation (left-hand side) is smaller then the effective benefit plus the horizontal transmission bias (right-hand side).
-This condition cannot be formulated in the form of Hamilton's rule, $c<b \cdot r$, due to the effect of biased horizontal transmission, represented by $(T_A-T_B)$.
-Remarkably, a polymorphism of cooperation and defection can be stable if horizontal transmission is biased in favor of defection ($T_A<T_B$) and both $c$ and $\alpha$ are intermediate (yellow areas in Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
-
-We find that stronger interaction-transmission association $\alpha$ leads to evolution of higher frequency of cooperation and increased population mean fitness.
-Nevertheless, when cooperation and defection coexist, $\alpha$ is expected to be reduced by natural selection, leading to extinction of cooperation and decreased population mean fitness (Result~\ref{result:evol_social_association}, \autoref{fig:invasion}).
-With $\alpha=0$, the benefit of cooperation cannot facilitate its evolution; it can only succeed if horizontal transmission is biased in its favor.
-
-Indeed, in our model, horizontal transmission plays a major role in the evolution of cooperation: increasing the transmission of cooperation, $T_A$, or decreasing the transmission of defection, $T_B$, facilitates the evolution of cooperation.
-However, the effect of oblique transmission is more complicated.
-When there is horizontal transmission bias in favor of cooperation, $T_A>T_B$, increasing the rate of oblique transmission, $1-v$, will facilitate the evolution of cooperation.
-In contrast, when the bias is in favor of defection, $T_A<T_B$, higher rates of vertical transmission, $v$, are advantageous for cooperation, and the rate of vertical transmission must be high enough ($v>\hat v$) for cooperation to fix in the population.
-
-Our deterministic model provides a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
-In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
-
-\citet{feldman1985gene} studied the dynamics of an altruistic phenotype with vertical cultural transmission and a gene that modifies the transmission of the phenotype.
-Their results are very sensitive to this genetic modification: without it, the conditions for invasion of the altruistic phenotype reduce to Hamilton's rule.
-Further work is needed to incorporate such genetic modification of cultural transmission into our model.
-\citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation and
-carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or interaction-transmission association ($\alpha=0$).
-Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
-He further hypothesized that horizontal transmission can play an important role in the evolution of cooperation, and our results provide strong evidence for this hypothesis.
-
-To understand the role of horizontal transmission, we first review the role of \emph{assortment}.
-\citet{Eshel1982} showed that altruism can evolve when the tendency for \emph{assortative meeting}, i.e., for individuals to interact with others of their own phenotype, is strong enough.
-\citet{Fletcher2009assortment}  further argued that a general explanation for the evolution of altruism is given by \emph{assortment}: the correlation between individuals that carry an altruistic trait and the amount of altruistic behavior in their interaction group (see also \citet{Bijma2010assortment}).
-They suggested that to explain the evolution of altruism, we should seek mechanisms that generate  assortment, such as population structure, repeated interactions, and individual recognition.
-Our results highlight another mechanism for generating assortment: an association between social interactions and horizontal transmission that creates a correlation between one's partner for interaction and the partner for transmission.
-This mechanism does not require repeated interactions, population structure, or individual recognition.
-We show that high levels of such interaction-transmission association greatly increase the potential for evolution of cooperation.
-With enough interaction-transmission association, cooperation can increase in frequency when initially rare even when there is horizontal transmission bias against it ($T_A<T_B$).
-
-How does non-vertical transmission generate assortment? 
-\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} 
-suggested that microbes that induce their hosts to act altruistically can be favored by selection, which may help to explain the evolution of cooperation. 
-%Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
-%Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others. 
-From the kin selection point-of-view, if microbes can be transmitted \emph{horizontally} from one host to another during host interactions, then following horizontal transmission the recipient host will carry microbes that are closely related to those of the donor host,
-even when the two hosts are (genetically) unrelated. 
-From the assortment point-of-view,
-infection by behavior-determining microbes during interactions effectively generates assortment because a recipient of help may be infected by a behavior-determining microbe and consequently become a helper.
-Cultural horizontal transmission can similarly generate assortment between cooperators and enhance the benefit of cooperation if cultural transmission and helping interactions occur between the same individuals, i.e.
-when there is interaction-transmission association, so that the recipient of help may also be the recipient of the cultural trait for cooperation.
-Thus, with horizontal transmission, ``assortment between focal cooperative players and cooperative acts in their interaction
-environment''~\citep{Fletcher2009assortment} is generated not because the helper is likely to be helped, but rather because the helped is likely to become a helper.
-
-\newpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Bibliography
-\bibliographystyle{rsnat}
-\bibliography{bib}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section*{\huge{Supplementary material}}
-\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Appendices
-\begin{appendices}
-\renewcommand{\theequation}{\thesection\arabic{equation}}
-\counterwithin*{equation}{section}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Local stability criterion} \label{sec:appendixA}
-
-Let $f(p)=\lambda \cdot (p'-p)$, where $\lambda>0$, and $0$ and $1$ are equilibria, that is, $f(0)=0$ and $f(1)=0$.
-
-Set $p>p^*=0$.
-Using a linear approximation for $f(p)$ near $0$, we have
-\begin{equation}
-p' < p \Leftrightarrow 
-f(p)/p < 0 \Leftrightarrow 
-\frac{f'(0) \cdot p + O(p^2)}{p} < 0 \Leftrightarrow 
-f'(0) + O(p) < 0 \;.
-\end{equation}
-Therefore, by definition of big-O notation, if $f'(0)<0$ then there exists $\epsilon>0$ such that for any local perturbation $0<p<\epsilon$, it is guaranteed that $0<p'<p$; that is, $p'$ is closer to zero than $p$.
-
-Set $p<p^*=1$
-Using a linear approximation for $f(p)$ near $1$, we have
-\begin{equation}
-1-p' < 1-p  \Leftrightarrow 
--\frac{f(p)}{1-p} < 0 \Leftrightarrow 
-\frac{f'(1)(p-1) + O\big((p-1)^2\big)}{p-1} < 0 \Leftrightarrow 
-f'(1) - O(1-p) < 0 \;.
-\end{equation}
-Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{Equilibria and stability} \label{sec:appendixB}
-
-Let $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
-Then, using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, this simplifies to
-\begin{equation} \label{eq:general_case_polynomial}
-\begin{aligned}
-  f(\hat{p}) &= \bar{w}(\hat{p}'-\hat{p}) =
-  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p} \;,
-\end{aligned}
-\end{equation}
-where 
-\begin{equation} \label{eq:polynomial_coefficients}
-\begin{aligned}
-  \beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \;, \\
-  \beta_2 &= -\beta_1 -\beta_3 \;, \\
-  \beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \;.
-\end{aligned}
-\end{equation}
-
-If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$, and $f(\hat{p})$ becomes a quadratic polynomial,
-\begin{equation} \label{eq:equal_horizontal_transmission}
-  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big] \;.
-\end{equation}
-Clearly the only two equilibria are the fixations $\hat{p} =  0$ and $\hat{p} = 1$, which are are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\ref{sec:appendixA}), where
-$f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big]$, so that
-\begin{equation} \label{eq:derivative_of_phattag-phat}
-\begin{aligned}
-	f'(0) &=	\alpha bvT - cv(1-T) \;, \\
-	f'(1) &=	-\alpha bvT + cv(1-T) \;.
-\end{aligned}
-\end{equation}
-%Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{remark:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
-
-In the general case where $T_A \neq T_B$, the coefficient $\beta_1$ is not necessarily zero, and $f(\hat{p})$ is a cubic polynomial.
-Therefore, three equilibria may exist, two of which are
-$\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
-\begin{equation} \label{eq:general_equilibrium_appendix}
-  \hat{p}^* =  
-  \frac{\beta_3}{\beta_1} =
-  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
-\end{equation}
-
-Note that the sign of the  cubic (Eq.\ \ref{eq:general_case_polynomial}) at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
-If $T_A>T_B$, then 
-\begin{equation} \label{eq:beta1}
-   \beta_1 < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) < 0 \;,
- \end{equation}
-since $c<b$ and $\alpha v < 1$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
-First, if $\beta_3<\beta_1$ then 
-$1<\hat{p}^*$. Also, $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable feasible equilibrium.
-Second, if $\beta_1<\beta_3<0$ then 
-$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$ so that both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
-Third, if $0<\beta_3$ then 
-$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$; that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
-
-Similarly, if $T_A<T_B$, then
-\begin{equation} \label{eq:beta1_rev}
-   \beta_1 > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) > 0 \;,
- \end{equation}
-since $c<b$ and $\alpha v < 1$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
-First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A$ is the only locally stable legitimate equilibrium.
-Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable feasible equilibrium.
-
-This analysis can be summarized as follows:
-% in beta
-\begin{enumerate}
-\item \emph{Fixation of cooperation}: 
-	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
-	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
-\item \emph{Fixation of the defection}: 
-	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-	if \emph{(v)} $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
-	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
-\item \emph{polymorphism of both phenotypes at $\hat{p}^*$}: 
-	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
-\item \emph{Fixation of either phenotype depending on initial frequency}:
-	if \emph{(viii)}  $T_A>T_B$ and $\beta_1<\beta_3<0$.
-\end{enumerate}
-
-We now proceed to use the cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}).
-First, assume $T_A<T_B$.
-$\beta_3<0$ requires $\gamma_1<c$.
-For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
-Note that the expression in the square brackets is positive if and only if $v > \hat v$.
-Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c$ or $v < \hat v$ and $c < \gamma_2$,
-and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c < \gamma_1$, or $v < \hat v$ and $c < \min(\gamma_1, \gamma_2)$.
-For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\gamma_2$ or $v < \hat v$ and $\gamma_2<c$.
-However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\gamma_2$.
-
-Second, assume $T_A>T_B$.
-$\beta_3>0$ requires $\gamma_1 > c$. 
-For $\beta_1<\beta_3$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] < bv\alpha T_B + (1+b)(T_A-T_B)$.
-Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \gamma_2 $ or $v < \hat v$ and $c > \gamma_2$.
-But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
-
-This analysis is summarized in Result~\ref{result:vert_obli_hori}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{Effect of interaction-transmission association on mean fitness} \label{sec:appendixC}
-
-To determine the effect of increasing $\alpha$ on the stable population mean fitness, $\bar{w}^*=1+(b-c)\hat{p}^*$, we must analyze its effect on $\hat{p}^*$, 
-\begin{equation} \label{eq:mean_fitness_stable_polymorphism_derivative}
-  \frac{\partial \hat{p}^*}{\partial \alpha} 
-%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
-%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
-  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
-\end{equation} 
-Note that stable polymorphism implies $c<\gamma_1$, and because $\alpha<1$, we have
-\begin{equation}
-c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
-\end{equation} 
-Therefore, the numerator in \autoref{eq:mean_fitness_stable_polymorphism_derivative} is positive.
-Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_polymorphism_derivative} is also positive, and hence the derivative $\partial \hat{p}^* / \partial \alpha$ is positive.
-Thus, the population mean fitness increases as interaction-transmission association $\alpha$ increases.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{Reduction principle} \label{sec:appendixD}
-
-We assume here that $v=1$, i.e. no oblique transmission, and therefore $\hat{p}=\tilde{p}$.
-Denote the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ by $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
-The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
-\begin{equation} \label{eq:next_gen_p_1}
-  \begin{aligned}
-	% p1
-  \bar{w}\tilde{p}_1' = 
-  & \tilde{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \tilde{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) \;+ \\
-  & \tilde{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) \;+ \\
-  & \tilde{p}_2(1-x)x(1-\alpha_1)T_A \;,
-\\
-	% p2
-  \bar{w}\tilde{p}_2' = 
-  & \tilde{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \;+ \\
-  & \tilde{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \tilde{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) \;+ \\
-& \tilde{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;, 
-\\
-	% p3
-  \bar{w}\tilde{p}_3' =
-  & \tilde{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \tilde{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) \;+ \\
-  & \tilde{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) \;+ \\
-  & \tilde{p}_4(1-x) x (1-\alpha_2)T_A \;, 
-\\
-	% p4
-  \bar{w}\tilde{p}_4' =
-  & \tilde{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B \;+ \\
-  & \tilde{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \tilde{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) \;+ \\
-  & \tilde{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \;,
-  \end{aligned}
-\end{equation}
-%which we can write as 
-%\begin{equation}
-%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
-%\end{equation}
-where $x=\tilde{p}_1+\tilde{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-
-The equilibrium where only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
-\begin{equation} \label{eq:p_tilde_star_alpha_1}
-\tilde{p}^*=
-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)} \;,
-\end{equation}
-setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
-When $v=1$, $\tilde p^*$ is a feasible polymorphism ($0 < \tilde{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
-
-The local stability of $\vec{\tilde{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
-$\cl^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\cl^*_{in}$ and $\cl^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1}, with $\bar{w}^*=1+(b-c)\tilde{p}^*$ as the stable population mean fitness,
-\begin{equation} \label{eq:external_stability_matrix}
-\begin{aligned}
-&\cl^*_{ex} = 
- \frac{1}{\bar{w}^*} \begin{bmatrix}
-	 l_{1 1} &
-	 l_{1 2} \\
-	 l_{2 1} &
-	 l_{2 2} 
-\end{bmatrix} = 
-\frac{1}{\bar{w}^*} \begin{bmatrix}
-\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-\frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
-\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
-\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) 
-\end{bmatrix} \;= \\
-& \frac{1}{\bar{w}^*} \begin{bmatrix}
-		(1+b \tilde{p}^* -c)(1-T_B(1-\tilde{p}^*)) + b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) & 
-		(1+b \tilde{p}^*) T_A \tilde{p}^* + b \tilde{p}^* \alpha_2 T_A(1-\tilde{p}^*) \\
-		(1+b \tilde{p}^* - c) T_B(1-\tilde{p}^*) - b \tilde{p}^* \alpha_2 T_B (1-\tilde{p}^*) &
-		(1+b \tilde{p}^*) (1-T_A \tilde{p}^*) - b \tilde{p}^* \alpha_2 T_A (1-\tilde{p}^*) \\
-  	\end{bmatrix} \;.
-\end{aligned}
-\end{equation}
-
-Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
-$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\cl^*_{ex}$.
-This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\cl^*_{ex}$ is real and positive.
-Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
-The eigenvalues of $\cl^*_{ex}$ are the roots of the characteristic polynomial, $R(\lambda)$,
-%\begin{equation}\label{char_poly}
-%R(\lambda) = 
-%\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;,
-%\end{equation}
-%where $X$, $Y$, $Z$, and $Q$ are defined in \autoref{eq:external_stability_matrix}.
-which is a quadratic with a positive leading coefficient.
-Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
-Thus, a sufficient condition for external instability of $\vec{\tilde{p}^*}$ is $R(1) < 0$.
-%\begin{equation} \label{eq:R1_negative}
-%\begin{aligned}
-%R(1) < 0 \Leftrightarrow 
-%1 - \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} < 0 \Leftrightarrow 
-%\bar{w^*}^2 - \bar{w^*} (X+Q) + XQ - YZ < 0 \;.
-%\end{aligned}
-%\end{equation}
-
-$R(\lambda)$ is defined as a determinant, $R(\lambda)=\det(\cl^*_{ex} - \lambda \ci)$, where $\ci$ is the 2-by-2 identity matrix. 
-Since multiplication by a positive factor doesn't change the sign, and using the properties of the determinant,  we have
-\begin{equation} \label{eq:signR1}
-\begin{aligned}
-\sign R(1) =
-& \sign\det(\cl^*_{ex} - \ci) =
-  \sign (\bar{w}^*)^2 \det(\cl^*_{ex} - \ci) = \\
-& \sign \det(\bar{w}^*\cl^*_{ex} - \bar{w}^* \ci) =
-  \sign \det\begin{bmatrix} l_{1 1} - \bar{w}^* & l_{1 2} \\ l_{2 1} & l_{2 2} - \bar{w}^* \end{bmatrix} \;,
-\end{aligned}
-\end{equation}
-where $l_{i j}$ are defined in \autoref{eq:external_stability_matrix}.
-Adding the second row in \autoref{eq:signR1} to the first row,  which does not change the determinant, and substituting $\bar{w}^*=1+(b-c)\tilde{p}^*$, we get
-\begin{equation} 
-\begin{aligned}
-\sign R(1) =
-& \sign\det\begin{bmatrix}
-	 -c(1-\tilde{p}^*) &&
-	 c \tilde{p}^* \\
-	 (1-\tilde{p}^*)\big[(1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* \big] &&
-	 \tilde{p}^*\big[-(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c\big]
-\end{bmatrix} = \\
-& \sign \Bigg[c \tilde{p}^* (1-\tilde{p}^*) \cdot \det\begin{bmatrix}
-	 -1 &&
-	 1 \\
-	 (1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* &&
-	 -(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c
-\end{bmatrix}\Bigg] = \\
-& \sign\det\begin{bmatrix}
-	 -1 &&
-	 1 \\
-	 (1+b\tilde{p}^*-c)T_B - b \alpha_2 T_B \tilde{p}^* &&
-	 -(1+b\tilde{p}^*)T_A - b \alpha_2 T_A (1-\tilde{p}^*) + c
-\end{bmatrix} \;,
-\end{aligned}
-\end{equation}
-since $c>0$, $0<\tilde{p}^*<1$.
-That is, 
-\begin{equation}
-\begin{aligned}
-\sign R(1) = 
-&\sign\Big[
-(1+b\tilde{p}^*)T_A + b\alpha_2 T_A (1-\tilde{p}^*) - c - 
-(1+b\tilde{p}^*-c)T_B + b\tilde{p}^* \alpha_2 T_B \Big]
-= \\
-&\sign\Big[(1+b(1-\alpha_2)\tilde{p}^*)(T_A-T_B) + b\alpha_2 T_A - c (1-T_B) \Big]\;.
-\end{aligned}
-\end{equation}
-Substituting $\tilde{p}^*$ from \autoref{eq:p_tilde_star_alpha_1}, we get
-\begin{equation} \label{eq:R1_less}
-\begin{aligned}
-R(1)<0 \Leftrightarrow
-&\big[c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)\big] \frac{1-\alpha_2}{1-\alpha_1} - c (1-T_B) + b\alpha_2 T_A  + (T_A-T_B) < 0 \Leftrightarrow \\
-&(1-\alpha_2)\big[c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)\big] < (1-\alpha_1)\big[c (1-T_B) - b\alpha_2 T_A  - (T_A-T_B) \big] \Leftrightarrow \\
-& - b \alpha_1 T_A -\alpha_2 c(1-T_B) +\alpha_2(T_A - T_B) < 
-  - b\alpha_2 T_A -\alpha_1 c (1-T_B) +\alpha_1 (T_A-T_B)  \Leftrightarrow \\
-& \alpha_1 \big[c (1-T_B) - b T_A-(T_A-T_B)\big]  < 
-  \alpha_2 \big[c(1-T_B)-b T_A -(T_A - T_B)\big] \Leftrightarrow \\
-& \alpha_1 \big[b T_A + (T_A-T_B) - c (1-T_B)\big]  > 
-  \alpha_2 \big[b T_A + (T_A-T_B) - c (1-T_B)\big] \;.
-\end{aligned}
-\end{equation}
-We assumed $c<\gamma_1$, and since $0 \le \alpha_1 \le 1$,
-\begin{equation} \label{eq:c_gamma1_utility}
-\begin{aligned}
-c &< \gamma_1 = \frac{b \alpha_1 T_A + (T_A-T_B)}{1-T_B} \; \Leftrightarrow \\
-%c(1-T_B) < b \alpha_1 T_A + (T_A-T_B) \Leftrightarrow \\
-0 &< b \alpha_1 T_A + (T_A-T_B) - c(1-T_B) \; \Rightarrow \\
-0 &< b T_A + (T_A-T_B) - c(1-T_B) \;.
-\end{aligned}
-\end{equation}
-
-Combining inequalities~\ref{eq:R1_less} and~\ref{eq:c_gamma1_utility}, we find that $R(1)<0$ if and only if $\alpha_1 > \alpha_2$, which is a sufficient condition for external instability. 
-Therefore, if $\alpha_2$, the interaction-transmission association of the invading modifier allele $m$, is less than $\alpha_1$, the interaction-transmission association of the resident allele $M$, then invasion will be successful.
-
-Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-However, we have numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_1>\alpha_2$.
-
-\end{appendices}
+%%%
 \end{document}

### 2021-05-01 ms/Thesis/thesis.tex
Add idc format
Replace all tilde to dot

@@
 $\bar{w} =  1 + \hat{p}(b-c)$.
-Starting from \autoref{eq:horizontal} with $\hat{p}'=v\tilde{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults} and $\tilde{p}'$ from \autoref{eq:nextgen_parents} and obtain
+Starting from \autoref{eq:horizontal} with $\hat{p}'=v\dot{p}'+(1-v)p'$, we substitute $p'$ from \autoref{eq:nextgen_adults} and $\dot{p}'$ from \autoref{eq:nextgen_parents} and obtain
 \begin{equation} \label{eq:nextgen_juveniles}
@@
 %\begin{equation}
-%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
+%\bar{w} \vec{\dot{p}} = F(\vec{\dot{p}}),
 %\end{equation}
-where $x=\tilde{p}_1+\tilde{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.
-
-The equilibrium where only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
+where $x=\dot{p}_1+\dot{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\dot{p}} = (\dot{p}_1,\dot{p}_2,\dot{p}_3,\dot{p}_4)$.
+
+The equilibrium where only allele $M$ is present is  $\vec{\dot{p}^*} = (\dot{p}^*, 1-\dot{p}^*, 0, 0)$, where
 \begin{equation} \label{eq:p_tilde_star_alpha_1}
-\tilde{p}^*=
+\dot{p}^*=
 \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)} \;,
@@
 &\sign\Big[
-(1+b\tilde{p}^*)T_A + b\alpha_2 T_A (1-\tilde{p}^*) - c - 
-(1+b\tilde{p}^*-c)T_B + b\tilde{p}^* \alpha_2 T_B \Big]
+(1+b\dot{p}^*)T_A + b\alpha_2 T_A (1-\dot{p}^*) - c - 
+(1+b\dot{p}^*-c)T_B + b\dot{p}^* \alpha_2 T_B \Big]
 = \\
-&\sign\Big[(1+b(1-\alpha_2)\tilde{p}^*)(T_A-T_B) + b\alpha_2 T_A - c (1-T_B) \Big]\;.
-\end{aligned}
-\end{equation}
-Substituting $\tilde{p}^*$ from \autoref{eq:p_tilde_star_alpha_1}, we get
+&\sign\Big[(1+b(1-\alpha_2)\dot{p}^*)(T_A-T_B) + b\alpha_2 T_A - c (1-T_B) \Big]\;.
+\end{aligned}
+\end{equation}
+Substituting $\dot{p}^*$ from \autoref{eq:p_tilde_star_alpha_1}, we get
 \begin{equation} \label{eq:R1_less}

### 2021-05-01 ms/Thesis/thesis.tex
Add comment about stable and unstable polymorphism
Thesis: add few of the fixes that we did before publishing to PRSB

@@
 
-% TODO change "scoail association" to "interaction-transmission association"
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}c).
-Then, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
+Thus, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
 \begin{equation}\label{eq:nextgen_adults}
@@
 \end{result}
+Thus, cooperation can take over the population if it has either a horizontal transmission advantage, or if it has a horizontal transmission disadvantage, but the vertical transmission rate is high enough.
+In either case, the cost of cooperation must be small enough.
+A stable polymorphism can exist between cooperation and defection only if defection has a horizontal transmission advantage.
+In this case, the existence of a stable polymorphism depends on the interplay between the benefit and cost of cooperation and the vertical transmission rate.
 These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
+Note that \emph{stable} and {unstable polymorphism} are also called, respectively, \emph{coexistence} and \emph{bistable competition}.
 
@@
 individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
-The expected number of each of these interactions per individual per generation is one.
+The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.
 The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
-On an infinite grid, $M=8$, but on a finite grid $M$ can be lower in edge neighborhoods close to the grid border.
+On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in neighbourhoods close to the grid border.
 As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.

### 2021-05-01 ms/Thesis/thesis.tex
Copy abstract from the paper

@@
 The deterministic conditions are compared to outcomes of stochastic simulations of structured populations.
-Parallels are drawn with Hamilton's rule incorporating assortment and effective relatedness.
+Parallels are drawn with Hamilton's rule incorporating relatedness and assortment.
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
+  \includegraphics[width=0.7\textwidth]{../PRSB_figures/fig_1.pdf}
   \caption{\textbf{Model illustration.} 
-  \textbf{(a)}~Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
-  \textbf{(b)}~Individuals socially interact in pairs in a prisoners' dilemma game.
+  \textbf{(a)}~First, offspring inherit their parent's phenotype via vertical cultural transmission with probability $v$, or the phenotype of a random non-parental adult via oblique cultural transmission with probability $1-v$.
+  \textbf{(b)}~Second, adults socially interact in pairs in a prisoner's dilemma game.
 Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
-  \textbf{(c)}~The probabilities of successful horizontal  cultural transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively.
-  \textbf{(d)}~Offspring inherit their parent's phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
+  \textbf{(c)}~The prisoner's dilemma payoff matrix shows the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+    \textbf{(d)}~The probabilities of successful horizontal cultural transmission of phenotypes $A$ (cooperator) and $B$ (defector) are $T_A$ and $T_B$, respectively.
     }
@@
 However, horizontal transmission is not always successful, as one partner may reject the other's phenotype.
-The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}c).
+The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}d).
 Thus, the frequency $p'$ of phenotype $A$ among adults in the next generation, after horizontal transmission, is 
@@
 \end{equation}
-where fitness values are taken from \autoref{fig:illustration}a and \autoref{table:interactions}, and the population mean fitness is
+where fitness values are taken from \autoref{fig:illustration}c and \autoref{table:interactions}, and the population mean fitness is
 $\bar{w} =  1 + \hat{p}(b-c)$.
@@
 initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}a) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
+individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}c) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
 The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.

### 2021-05-01 ms/Thesis/thesis.tex
Thesis: use PRSB figures

@@
   \centering       
-    \includegraphics[width=0.45\textwidth]{Result3_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_TB_TA.eps}
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TA_TB.eps}~
-    \includegraphics[width=0.45\textwidth]{Result3_alpha_Vs_v_TB_TA.eps}
+    \includegraphics[width=1\textwidth]{../PRSB_figures/fig_2.pdf}
     \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
@@
   \centering       
-    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
-	  ~
-    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
-    ~
-    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
-    ~
-    \includegraphics[width=0.48\textwidth]{coexistence_without_oblique.eps}
+	\includegraphics[width=1\textwidth]{../PRSB_figures/fig_3.pdf}
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
@@
     \label{fig:equilibria_v1}
-    %TODO update y label on c d
 \end{figure}
-
 \newpage
@@
 
+%%% Figure: Invasion
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_s1.pdf}
+  \caption{
+  \textbf{Reduction principle for interaction-transmission association.} 
+  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (Eq.~D1).
+  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
+  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
+  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
+  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
+  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
+  }
+  \label{fig:invasion}
+\end{figure}
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%% Figure: Invasion
-\begin{figure}[h]
-  \centering
-   \includegraphics[scale=0.5]{../Figures/invasion.eps}
-  \caption{
-  \textbf{Reduction principle for interaction-transmission association.} 
-  Consecutive fixation of modifier alleles that reduce interaction-transmission association $\alpha$ in numerical simulations of evolution with two modifier alleles (\autoref{eq:next_gen_p_1}).
-  When an invading modifier allele is established in the population (frequency > 99.95\%), a new modifier allele that reduces interaction-transmission association by 5\% is introduced (at initial frequency 0.5\%).
-  \textbf{(a)}~The frequency of the cooperative phenotype $A$ over time.
-  \textbf{(b)}~The frequency of the invading modifier allele $m$ over time. 
-  \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
-  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
-  }
-  \label{fig:invasion}
-\end{figure}
-
 \newpage
@@
   \centering
-	\includegraphics[width=0.3\textwidth]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
-    ~
-	\includegraphics[width=0.3\textwidth]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} 
-    ~
-    \includegraphics[width=0.36\textwidth]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
+  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_4.pdf}
   \caption{
@@
   In all cases, the population evolves on a 100-by-100 grid.
-  Cooperation and horizontal transmission are both local between neighboring sites, and each site has 8 neighbors.
-  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
+  Cooperation and horizontal transmission are both local between neighbouring sites, and each site has 8 neighbours.
+  Selection operates globally (see Figure S2 for results from a model with local selection).
   Simulations were stopped at generation 10,000 or if one of the phenotypes fixed. 50 simulations were executed for each parameter set.
@@
   \centering
-   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_localSelection}.pdf}
-    ~
-    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_localSelection}.pdf} \\
+  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_s2.pdf}
   \caption{

### 2021-05-03 ms/spatial_CIC_simulation - 2inter.py
Uploading spatial simulation code
Uploading the code of the spatial-stochastic simulation for Culture-induced cooperation paper PRSB2021

@@ -1,0 +1,262 @@
+import numpy as np
+import os
+import sys
+from datetime import datetime
+
+
+#%% functions ###
+
+def neighbours(mat, x, y, nx=1, ny=1):
+    ''' 
+    returns a slice from a lattice (mat) with radius (nx,ny) around 
+    coordinate x,y - trimmed by the borders
+    ''' 
+    return mat[max(x-nx, 0) : min(x+nx+1, mat.shape[0]), \
+                      max(y-ny, 0) : min(y+ny+1, mat.shape[1])]
+
+
+
+def individualInteraction_Behavior(mySub, neibSub, lattice_ab, params):
+    ''' 
+    returns the fitness delta of the two interactors according to the cost
+    and benefit of the interactions (b and c)
+    '''
+    c = params['c']
+    b = params['b']
+    my_ab = lattice_ab[mySub]
+    neib_ab = lattice_ab[neibSub]
+    
+    # coop level: coop only if ab=1 (phenotype a)
+    myC   = my_ab * c 
+    neibC = neib_ab * c
+    
+    # fitness calculation according to cooperation
+    myfi   = neib_ab * b - myC
+    neibfi = my_ab   * b - neibC
+    
+    return myfi, neibfi
+
+
+
+def individualInteraction_Infection(mySub, neibSub, lattice_ab, params):
+    ''' 
+    the function changes the phenotype lattice (lattice_ab)
+    according to horizontal transmission events
+    '''
+    Ta = params['Ta']
+    Tb = params['Tb']
+    my_ab   = lattice_ab[mySub]
+    neib_ab = lattice_ab[neibSub]
+        
+    if neib_ab != my_ab:
+        if neib_ab == 1: # namely phenotype a
+            if np.random.rand() < Ta: # a neib infects with prob Ta
+                lattice_ab[mySub] = 1
+
+            if np.random.rand() < Tb:
+                lattice_ab[neibSub] = 0
+
+        else: # neib ab is 0, namely phenotype b
+            if np.random.rand() < Tb: # b neib infects with prob Tb
+                lattice_ab[mySub] = 0
+
+            if np.random.rand() < Ta:
+                lattice_ab[neibSub] = 1
+
+
+
+def interactions(lattice_ab, params):
+    '''
+    Performs all the interactions (behavbior and horizontal tranmission) across the
+    population in a given generation. The function generates the fitness 
[…]

### 2021-05-28 ms/Thesis/thesis.tex
Thesis: few fixes
changes in the evolution of cooperation section

@@
 \end{table}
-%\bigskip
-%%%
 
@@
 We determine the equilibria of the model in \autoref{eq:nextgen_juveniles}
-%namely, solutions of $\hat{p}' = \hat{p}$, 
 and analyze their local stability.
@@
 
-The fixed points (equilibria) of  the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see \autoref{eq:general_equilibrium_appendix})
+To learn about the evolution of cooperation we investigate local stability of the equilibria of the model in \autoref{eq:nextgen_juveniles}.
+The equilibria are the solutions of $\hat{p}'-\hat{p}=0$. Note that \autoref{eq:nextgen_juveniles} is not simple polynomial but a polynomial fraction, therefore the solution is not trivial.
+%% DC: Yoav, I'm trying to write something like solving this is not trivial.
+The fixed points (equilibria) of the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see Appendix~\ref{sec:appendixB} \autoref{eq:general_equilibrium_appendix})
 \begin{equation} \label{eq:general_equilibrium}
@@
 \newpage
-\section*{\huge{Supplementary material}}
 \beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
@@
 \end{equation}
-%Therefore with symmetric horizontal transmission ($T_A=T_B$), fixation of the cooperative phenotype ($\hat{p}=1$) occurs under the same condition as Corollary \ref{remark:equal_transmission}, namely inequality~\ref{eq:equal_transmission}.
 

### 2021-05-28 ms/Thesis/thesis.tex
invasion with general vertical transmission

@@
 
+We can do similiar analysis for the general case where $0<v<1$ as we did in Appendix~\ref{sec:appendixD}.
+First we found the value of the characteristic polynomial at 1, $R(1)$ using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics.
+\begin{equation} \label{eq:value_at_1}
+  \begin{aligned}
+  R(1) &= \frac{c v \hat{p}^*[T_Ab\hat{p}^{*2}(v\alpha_2-1)-2T_Ab\hat{p}^*v\alpha_2 + T_Ab\hat{p}^*(1+v\alpha_2)]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} \\
+ & + \frac{c v \hat{p}^*[T_Ac\hat{p}^{*2}(1-v)+T_Ac\hat{p}^*(v-1)-T_A\hat{p}^*(1-c)+T_A]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} \\
+  &+ \frac{c v \hat{p}^*[T_Bb\hat{p}^{*2}(1-v\alpha_2)+T_Bb\hat{p}^2(v\alpha_2-1)+T_Bc\hat{p}^{*2}(v-1)]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1}\\
+  &+ \frac{c v \hat{p}^*[T_Bc\hat{p}^*(1-v) + T_Bcv(1-\hat{p}^*+T_B(\hat{p}^*-1)+cv(\hat{p}^*-1))]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1}
+  \end{aligned}
+\end{equation}
+Similarly to what we did in Appendix~\ref{sec:appendixD}, we should find when $R(1)<0$. However, when adding the vertical transmission into the system the math is more complicated. 
+Therefore, we will use a different technique. We know that when $\alpha_1 = \alpha_2$, $R(1)=0$. 
+% DC: Yoav should I proof the statement above?
+Now, let's assume that $\alpha_2 = \alpha_1 + \epsilon$. The derivative of $R(1)$ by $\epsilon$ will give us better understand about the sign of $R(1)$ when $\alpha_2<\alpha_1$.
+\begin{equation} \label{eq:value_at_1_derivative}
+  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b  v^2 \hat{p}^*[T_A\hat{p}^{*2}-2T_A\hat{p}^* + T_A-T_B\hat{p}^{*2}+T_B\hat{p}^*]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} 
+\end{equation}
+We can simplify \autoref{eq:value_at_1_derivative}
+\begin{equation} \label{eq:value_at_1_derivative_simplify}
+  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b v^2 \hat{p}^*[(T_A-T_B)\hat{p}^{*2}+(T_B-2T_A)\hat{p}^* + T_A]}{(b\hat{p}^*-c\hat{p}^*)^2+2\hat{p}^*(b-c)+1} 
+\end{equation}
+Since $b>c$ the denominator is always positive. The numerator is quadratic polynomial of $\hat{p}^*$ with the following roots:
+\begin{equation} \label{eq:numerator_roots}
+  \hat{p}^*_1 = \frac{T_A}{T_A-T_B} \hat{p}^*_2 = 1
+\end{equation}
+$\hat{p}^*_1 < 0$ since $T_B>T_A$ and since the quadratic polynomial has negative leading coefficient then the numerator is positive for every $\hat{p}^*_1<\hat{p}^*<1$ which is always true.
+We found that derivative of $R(1)$ by $\epsilon$ is positive for every $\epsilon$. 
+Therefore, $R(1)$ grows as $\epsilon$ grows, or in other words as $\alpha_2-\alpha_1$ grows.
+Thus, $R(1)<0$ if and only if $\alpha_2<\alpha_1$.
+Therefore, different value of vertical transmission does not change the evolution of social-interaction association and invasion is possible when $\alpha_2<\alpha_1$.
+% DC: can I say if and only if
+
 %%% Figure: Invasion
@@
   \textbf{(c)}~The population mean fitness ($\bar{w}$) over time.
-  Here, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
+  Here, $v=1$, $c = 0.05$, $b=1.3$, $T_A=0.4<T_B=0.7$, initial interaction-transmission association $\alpha_1=0.7$, lower interaction-transmission association threshold $a_2=0.605$.  
   }

### 2021-06-08 ms/Thesis/thesis.tex
Address other games such as Stag hunt in the model description

@@
 the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
+The choise of prisoner's dilemma as the interaction model was motividated by the fact that prisoner's dilemma is a common game used to study evolution of cooperation\citep{axelrod1981evolution}, \citep{milinski1987tit}, \citep{nowak1992tit}.
+Although we decided to focus on prisoner's dilemma, other games such as stag hunt\citep{skyrms2004stag} may be a better explaination of cooperation behavior in humman\citep{tomasello2012two}.
 

### 2021-06-08 ms/Thesis/thesis.tex
Reduce spacing in bib - idc requriemnt
Add paragraph about replicator dynamics

@@
 
+To understand the evolution of cooperation we are going to use \emph{replicator dynamics}. The replicator in replicator dynamics has the ability to make one or more copies of itself.
+The replicator can be a gene, a phenotype, a stragey in a game and etc. In cooperation context replicator is a different stragey in the game, whether the individual is a cooperative or a defector.
+In replicator dynamics we assume large population of replicators, which interact with respect to their proportion.
+Those interactions of different replicator affect the fitness acorrding to some payoff matrix. The payoff matrix depands on the game which is played. 
+The most common game to describe cooperation is prisoner's dilemma\citep{nowak1992tit}.
+Similar to dominant strategies bringing forth Nash equilibria when games are repeated, strategies in replicator dynamics can become evolutionary stable.
+Such strategies are called \emph{Evolutionarily Stable stragey (ESS)}.
+Such strategies cannot be invaded by any other strategy that is initially rare. 
+One of the main questions in the evolution of cooperation is under what conditions such invasions are possible.
+
 \newpage
@@
 }.
-%Here $m$ in inequality~\ref{eq:eshel1982} takes the role of the relatedness coefficient $r$ in inequality~\ref{eq:hamilton_rule}.
 
@@
 %%%% Table
-\begin{table}[h]
+\begin{table}[p]
   \caption{\textbf{Interaction frequency, fitness, and transmission probabilities.}}
@@
 
-\begin{table}[h]
+\begin{table}[p]
 \centering
@@
 
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Bibliography
+\begingroup
  \bibliographystyle{unsrtnat}
+ \linespread{1}\selectfont
+ \setlength{\bibsep}{2pt}
  \bibliography{bib}
+\endgroup
 
@@
 \begin{appendices}
+\linespread{1.25}
 \renewcommand{\theequation}{\thesection\arabic{equation}}

### 2021-06-12 ms/Thesis/thesis.tex
Add conditional cooperation paragraph in the discussion

@@
 Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Our deterministic model provides a good approximation to outcomes of simulations of a complex stochastic model with population structure in which individuals can only interact with and transmit to their neighbors.
-In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial}).
+In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial} and \autoref{fig:spatial_local_selection}).
+We did not find any significant difference between local and global selection. %DC: can we disucss why there is not difference?
 
@@
 Their results are very sensitive to this genetic modification: without it, the conditions for invasion of the altruistic phenotype reduce to Hamilton's rule.
-Further work is needed to incorporate such genetic modification of cultural transmission into our model.
+Further work is needed to incorporate such genetic modification of cultural transmission into our model. %DC: let's discuss it maybe we can do it.
 \citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation and
@@
 suggested that microbes that induce their hosts to act altruistically can be favored by selection, which may help to explain the evolution of cooperation. 
-%Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
-%Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others. 
+Indeed, it has been shown that microbes can mediate behavioral changes in their  hosts~\citep{dobson1988population,poulin2010parasite}. 
+Therefore, natural selection on microbes may favor manipulation of the host so that it cooperates with others.
 From the kin selection point-of-view, if microbes can be transmitted \emph{horizontally} from one host to another during host interactions, then following horizontal transmission the recipient host will carry microbes that are closely related to those of the donor host,
@@
 environment''~\citep{Fletcher2009assortment} is generated not because the helper is likely to be helped, but rather because the helped is likely to become a helper.
+
+Another mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e.
+individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community – provided that cooperation is already at a high level.
+Unlike \emph{conditional cooperation}, interaction-transmission association can sustain cooperation in community even if cooperation is initially rare. 
+\citet{morsky2020false} suggested that false beliefs on the frequencies of the cooperator can affect the individual decision whether to cooperate or not.
+If the individual over estimate the number of cooperators it will be more likely to cooperate.
+This flase belief can help sustain cooperation even if cooperartion is initially rare.
+% DC: Let's discuss this paragraph - is it good?
 

### 2021-06-12 ms/Thesis/thesis.tex
Add paragraph in the intro about 'Human large-scale cooperation as a product of competition between cultural groups'

@@
 Indeed, models in which microbes affect their host's behavior~\citep{lewin2017microbes,lewin2020rockpaperscissors,gurevich2020parental} are mathematically similar to models of cultural transmission, and they also emphasize the role of non-vertical transmission~\citep{cavalli1981cultural}.
+
+\citet{handley2020human} showed the importance of culture on the human behavior.
+They showed that the probablity of indvidual to cooperate with unrelated strangers from a different group in transient interactions corresponds to the degree of cultural similarity between those groups.
+Therefore, they have suggested that group-level selection on culturally differentiated populations can explain cooperation between unrelated humans from different groups.
 

### 2021-06-18 ms/Thesis/thesis.tex
Add more details why it is hard to 'solve' eq12

@@
 To learn about the evolution of cooperation we investigate local stability of the equilibria of the model in \autoref{eq:nextgen_juveniles}.
-The equilibria are the solutions of $\hat{p}'-\hat{p}=0$. Note that \autoref{eq:nextgen_juveniles} is not simple polynomial but a polynomial fraction, therefore the solution is not trivial.
-%% DC: Yoav, I'm trying to write something like solving this is not trivial.
+The equilibria are the solutions of $\hat{p}'-\hat{p}=0$.
+Note that \autoref{eq:nextgen_juveniles} may look simple cubic polynomial.
+However, because $\bar{w}$ is a function of $\hat{p}$, \autoref{eq:nextgen_juveniles} is not simple polynomial but a fractional polynomial.
+The solution of fractional polynomial is not trivial and that is why it is better to find the equilibria and analyze the stability.
 The fixed points (equilibria) of the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see Appendix~\ref{sec:appendixB} \autoref{eq:general_equilibrium_appendix})

### 2021-06-19 ms/Thesis/thesis.tex
ESS, EGS, local and external stability intro

@@
 \pagebreak
-{\large This work was carried out under the supervision of \textbf{Dr. Yoav Ram} from the Efi Arazi School of Computer Science, The Interdisciplinary Center, Herzliya.}
+{\large This work was carried out under the supervision of \textbf{Dr. Yoav Ram} from the School of Zoology, Faculty of Life Sciences, Tel Aviv University.}
 \pagebreak
@@
 Here, we study models for the cultural evolution of cooperation that include both vertical and non-vertical transmission. 
-%We investigate these models using mathematical analysis and simulations.  
 In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
@@
 Similar to dominant strategies bringing forth Nash equilibria when games are repeated, strategies in replicator dynamics can become evolutionary stable.
-Such strategies are called \emph{Evolutionarily Stable stragey (ESS)}.
-Such strategies cannot be invaded by any other strategy that is initially rare. 
-One of the main questions in the evolution of cooperation is under what conditions such invasions are possible.
-
-\newpage
-\section{Related Work}
+Such strategies are called \emph{Evolutionarily Stable Stragey (ESS)}.
+Such strategies cannot be invaded by any other strategy that is initially rare. Evolutionarily stable stragey maximizes the expected fitness of its chooser and therefore, causing maximum mean fitness.
+An interesting and fundamental question is to verify whether natural selection, operating within the framework of known genetical models leads to ESS.
+Note that usually natural selection does not lead to an increase in the average mean fitness of the population.
+Therefore, it is not generally true that natural selection does operate as to maximize the average individual fitness resulting in an optimal population strategy.
+%DC: I need reference for the statement above
+Instead of searching evolutionarily stable stragey, we focus on \emph{Evolutionary Genetic Stblility (EGS)}\citep{lessard1990evolutionary}.
+EGS is when the frequency of types (geneotype, phenotype etc.) stays the same.
+Here, we study both local stability and external stability. Equilibrium is consider \emph{Local stability} when a system near the equilibrium approaches it.
+\emph{External stability} is a  local stability of the equilibrium to invasion by the modifier allele m.
+One of the main questions in the evolution of cooperation is under what conditions such invasions are possible, or in other words under what conditions the system is external unstable.
 

### 2021-06-19 ms/Thesis/thesis.tex
Add new time series graph

@@
 \newpage
+
+%%% Figure: Time serires
+%DC: TODO: fix this figure
+
+\begin{figure}[h]
+  \centering       
+    \includegraphics[scale=0.5]{../Figures/Unstable_Time_series.eps}
+    \includegraphics[scale=0.5]{../Figures/Stable_Time_series.eps}
+    \caption{\textbf{Stable and unstable equilibrium dynamics} 
+    The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
+    In \textbf{(a)} the system has unstable equilibrium and therefore, all the curves are moving away from it.
+    In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
+    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b) $T_B=0.7$, $\alpha=0.6$ and $b=2.3$}.}
+    \label{fig:time_series}
+\end{figure}
 

### 2021-06-19 ms/Thesis/thesis.tex
Kill appendix B

@@
 The solution of fractional polynomial is not trivial and that is why it is better to find the equilibria and analyze the stability.
-The fixed points (equilibria) of the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see Appendix~\ref{sec:appendixB} \autoref{eq:general_equilibrium_appendix})
-\begin{equation} \label{eq:general_equilibrium}
+Let $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
+Then, using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, this simplifies to
+\begin{equation} \label{eq:general_case_polynomial}
+\begin{aligned}
+  f(\hat{p}) &= \bar{w}(\hat{p}'-\hat{p}) =
+  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p} \;,
+\end{aligned}
+\end{equation}
+where 
+\begin{equation} \label{eq:polynomial_coefficients}
+\begin{aligned}
+  \beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \;, \\
+  \beta_2 &= -\beta_1 -\beta_3 \;, \\
+  \beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \;.
+\end{aligned}
+\end{equation}
+
+If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$, and $f(\hat{p})$ becomes a quadratic polynomial,
+\begin{equation} \label{eq:equal_horizontal_transmission}
+  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big] \;.
+\end{equation}
+Clearly the only two equilibria are the fixations $\hat{p} =  0$ and $\hat{p} = 1$, which are are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\ref{sec:appendixA}), where
+$f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big]$, so that
+\begin{equation} \label{eq:derivative_of_phattag-phat}
+\begin{aligned}
+	f'(0) &=	\alpha bvT - cv(1-T) \;, \\
+	f'(1) &=	-\alpha bvT + cv(1-T) \;.
+\end{aligned}
+\end{equation}
+
+In the general case where $T_A \neq T_B$, the coefficient $\beta_1$ is not necessarily zero, and $f(\hat{p})$ is a cubic polynomial.
+Therefore, three equilibria may exist, two of which are
+$\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
+\begin{equation} \label{eq:general_equilibrium_appendix}
   \hat{p}^* =  
+  \frac{\beta_3}{\beta_1} =
   \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
@@
 
-Define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
-\begin{equation} \label{eq:cost_thresholds_v_threshold} 
-\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
-\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}, \quad
-\hat v = \frac{T_B - T_A}{1-T_A} \;.
-\end{equation}
+Note that the sign of the cubic (Eq.\ \ref{eq:general_case_polynomial}) at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
+If $T_A>T_B$, then 
+\begin{equation} \label{eq:beta1}
+   \beta_1 < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   = (1-\alpha v)(c-b)(T_A-T_B) < 0 \;,
+ \end{equation}
+since $c<b$ and $\alpha v < 1$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
+First, if $\beta_3<\beta_1$ then 
+$1<\hat{p}^*$. Also, $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable feasible equilibrium.
+Second, if $\beta_1<\beta_3<0$ then 
+$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$ so that both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
+Third, if $0<\beta_3$ then 
+$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$; that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
+
+Similarly, if $T_A<T_B$, then
+\begin{equation} \label{eq:beta1_rev}
+   \beta_1 > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
+   = (1-\alpha v)(c-b)(T_A-T_B) > 0 \;,
+ \end{equation}
+since $c<b$ and $\alpha v < 1$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
+First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A$ is the only locally stable legitimate equilibrium.
+Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
+Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable feasible equilibrium.
+
+This analysis can be summarized as follows:
+% in beta
+\begin{enumerate}
+\item \emph{Fixation of cooperation}: 
+	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
+	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
+	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
+\item \emph{Fixation of the defection}: 
+	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
+	if \emph{(v)} $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
+	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
+\item \emph{polymorphism of both phenotypes at $\hat{p}^*$}: 
+	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
+\item \emph{Fixation of either phenotype depending on initial frequency}:
+	if \emph{(viii)}  $T_A>T_B$ and $\beta_1<\beta_3<0$.
+\end{enumerate}
+
+We now proceed to use the cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}).
+First, assume $T_A<T_B$.
+$\beta_3<0$ requires $\gamma_1<c$.
+For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
+Note that the expression in the square brackets is positive if and only if $v > \hat v$.
+Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c$ or $v < \hat v$ and $c < \gamma_2$,
+and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c < \gamma_1$, or $v < \hat v$ and $c < \min(\gamma_1, \gamma_2)$.
+For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\gamma_2$ or $v < \hat v$ and $\gamma_2<c$.
+However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\gamma_2$.
+
+Second, assume $T_A>T_B$.
+$\beta_3>0$ requires $\gamma_1 > c$. 
+For $\beta_1<\beta_3$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] < bv\alpha T_B + (1+b)(T_A-T_B)$.
+Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \gamma_2 $ or $v < \hat v$ and $c > \gamma_2$.
+But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
 
@@
 \label{result:vert_obli_hori}
-With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}) :
+With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperation follows one of the following scenarios in terms of the cost thresholds $\gamma_1$ and $\gamma_2$ and the vertical transmission threshold $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}):
 
@@
 In this case, the existence of a stable polymorphism depends on the interplay between the benefit and cost of cooperation and the vertical transmission rate.
-These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
+These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b.
 Note that \emph{stable} and {unstable polymorphism} are also called, respectively, \emph{coexistence} and \emph{bistable competition}.
@@
 \newpage
-\section{Equilibria and stability} \label{sec:appendixB}
-
-Let $f(\hat{p}) = \bar{w}(\hat{p}' - \hat{p})$.
-Then, using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, this simplifies to
-\begin{equation} \label{eq:general_case_polynomial}
-\begin{aligned}
-  f(\hat{p}) &= \bar{w}(\hat{p}'-\hat{p}) =
-  \beta_1 \hat{p}^3 + \beta_2 \hat{p}^2 + \beta_3 \hat{p} \;,
-\end{aligned}
-\end{equation}
-where 
-\begin{equation} \label{eq:polynomial_coefficients}
-\begin{aligned}
-  \beta_1 &= \big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B) \;, \\
-  \beta_2 &= -\beta_1 -\beta_3 \;, \\
-  \beta_3 &= \alpha bvT_A - cv(1-T_B) + (T_A-T_B) \;.
-\end{aligned}
-\end{equation}
-
-If $T=T_A=T_B$ then $\beta_1=0$ and $\beta_3=-\beta_2=\alpha b vT -cv(1-T)$, and $f(\hat{p})$ becomes a quadratic polynomial,
-\begin{equation} \label{eq:equal_horizontal_transmission}
-  f(\hat{p}) = \hat{p}(1-\hat{p})\big[\alpha bvT - cv(1-T)\big] \;.
-\end{equation}
-Clearly the only two equilibria are the fixations $\hat{p} =  0$ and $\hat{p} = 1$, which are are locally stable if $f'(\hat{p})<0$ near the equilibrium (see Appendix~\ref{sec:appendixA}), where
-$f'(\hat{p})=(1-2\hat{p})\big[\alpha bvT - cv(1-T)\big]$, so that
-\begin{equation} \label{eq:derivative_of_phattag-phat}
-\begin{aligned}
-	f'(0) &=	\alpha bvT - cv(1-T) \;, \\
-	f'(1) &=	-\alpha bvT + cv(1-T) \;.
-\end{aligned}
-\end{equation}
-
-In the general case where $T_A \neq T_B$, the coefficient $\beta_1$ is not necessarily zero, and $f(\hat{p})$ is a cubic polynomial.
-Therefore, three equilibria may exist, two of which are
-$\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
-\begin{equation} \label{eq:general_equilibrium_appendix}
-  \hat{p}^* =  
-  \frac{\beta_3}{\beta_1} =
-  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
-\end{equation}
-
-Note that the sign of the cubic (Eq.\ \ref{eq:general_case_polynomial}) at positive (negative) infinity is equal (opposite) to the sign of $\beta_1$. 
-If $T_A>T_B$, then 
-\begin{equation} \label{eq:beta1}
-   \beta_1 < [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) < 0 \;,
- \end{equation}
-since $c<b$ and $\alpha v < 1$. Hence the signs of the cubic at positive and negative infinity are negative and positive, respectively.
-First, if $\beta_3<\beta_1$ then 
-$1<\hat{p}^*$. Also, $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $B$ is the only locally stable feasible equilibrium.
-Second, if $\beta_1<\beta_3<0$ then 
-$0<\hat{p}^*<1$ and therefore $f'(0)<0$ and $f'(1)<0$ so that both fixations are locally stable and $\hat{p}^*$ separates the domains of attraction.
-Third, if $0<\beta_3$ then 
-$\hat{p}^*<0$ and therefore $f'(0)>0$ and $f'(1)<0$; that is, fixation of the cooperator phenotype $A$ is the only locally stable legitimate equilibrium.
-
-Similarly, if $T_A<T_B$, then
-\begin{equation} \label{eq:beta1_rev}
-   \beta_1 > [c(1-\alpha v) - b(1-\alpha v)] (T_A-T_B) 
-   = (1-\alpha v)(c-b)(T_A-T_B) > 0 \;,
- \end{equation}
-since $c<b$ and $\alpha v < 1$, and the signs of the cubic at positive and negative infinity are positive and negative, respectively. 
-First, if $\beta_3<0$ then $\hat{p}^*<0$ and therefore $f'(0)<0$ and $f'(1)>0$; that is, fixation of the defector phenotype $A$ is the only locally stable legitimate equilibrium.
-Second, if $0<\beta_3<\beta_1$ then $0<\hat{p}^*<1$ and therefore $f'(0)>0$ and $f'(1)>0$; that is, both fixations are locally unstable and $\hat{p}^*$ is a stable polymorphic equilibrium.
-Third, if $\beta_1<\beta_3$ then $\hat{p}^*>1$ and therefore $f'(0)>0$ and $f'(1)<0$, and fixation of the cooperator phenotype $A$ is the only locally stable feasible equilibrium.
-
-This analysis can be summarized as follows:
-% in beta
-\begin{enumerate}
-\item \emph{Fixation of cooperation}: 
-	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
-	if \emph{(ii)} $T_A>T_B$ and $0<\beta_3$; or 
-	if \emph{(iii)} $T_A<T_B$ and $\beta_1<\beta_3$.
-\item \emph{Fixation of the defection}: 
-	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
-	if \emph{(v)} $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
-	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
-\item \emph{polymorphism of both phenotypes at $\hat{p}^*$}: 
-	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
-\item \emph{Fixation of either phenotype depending on initial frequency}:
-	if \emph{(viii)}  $T_A>T_B$ and $\beta_1<\beta_3<0$.
-\end{enumerate}
-
-We now proceed to use the cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}).
-First, assume $T_A<T_B$.
-$\beta_3<0$ requires $\gamma_1<c$.
-For $\beta_3<\beta_1$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] > bv\alpha T_B + (1+b)(T_A-T_B)$.
-Note that the expression in the square brackets is positive if and only if $v > \hat v$.
-Thus, for $\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c$ or $v < \hat v$ and $c < \gamma_2$,
-and for $0<\beta_3<\beta_1$ we need $v > \hat v$ and $\gamma_2 < c < \gamma_1$, or $v < \hat v$ and $c < \min(\gamma_1, \gamma_2)$.
-For $\beta_1<\beta_3$ we need $v > \hat v$ and $c<\gamma_2$ or $v < \hat v$ and $\gamma_2<c$.
-However, some of these conditions cannot be met, since $v < \hat v$ implies $c<1<\gamma_2$.
-
-Second, assume $T_A>T_B$.
-$\beta_3>0$ requires $\gamma_1 > c$. 
-For $\beta_1<\beta_3$ we need $c\big[v(1-T_B) + (1-v)(T_A-T_B)\big] < bv\alpha T_B + (1+b)(T_A-T_B)$.
-Thus for $\beta_1<\beta_3$ we need $v > \hat v$ and $c < \gamma_2 $ or $v < \hat v$ and $c > \gamma_2$.
-But $\hat{v}<0$ when $T_A > T_B$, and therefore we have $\beta_1<\beta_3$ if $c < \gamma_2$. Similarly, we have $\beta_3<\beta_1$ if $c > \hat{\gamma_2}$.
-
-This analysis is summarized in Result~\ref{result:vert_obli_hori}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
 \section{Effect of interaction-transmission association on mean fitness} \label{sec:appendixC}

### 2021-06-19 ms/Thesis/thesis.tex
Another fix to the remove of appendix B

@@
 
+Define the following cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$,
+\begin{equation} \label{eq:cost_thresholds_v_threshold} 
+\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{v(1-T_B)}, \quad
+\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}, \quad
+\hat v = \frac{T_B - T_A}{1-T_A} \;.
+\end{equation}
 We now proceed to use the cost thresholds, $\gamma_1$ and $\gamma_2$, and the vertical transmission threshold, $\hat v$ (\autoref{eq:cost_thresholds_v_threshold}).

### 2021-06-19 ms/Thesis/thesis.tex
Another fix after removing appendix B

@@
 $\hat{p} = 0 $ and $\hat{p} = 1$, and the third is
-\begin{equation} \label{eq:general_equilibrium_appendix}
+\begin{equation} \label{eq:general_equilibrium}
   \hat{p}^* =  
@@
 
-We now focus on the evolution of interaction-transmission association under perfect vertical transmission, $v=1$, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
+We now focus on the evolution of interaction-transmission association, assuming that the population is initially at a stable polymorphism of the two phenotypes, cooperation $A$ and defection $B$, where the frequency of $A$ among juveniles is $\hat{p}^*$ (\autoref{eq:general_equilibrium}).
 Note that for a stable polymorphism, there must be horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_thresholds_v_threshold}), see \autoref{fig:equilibria_v1}b.
-The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixC}).
+The equilibrium population mean fitness is $\bar{w}^* = 1 + \hat{p}^*(b-c)$, which is increasing in $\hat{p}^*$, and $\hat{p}^*$ is increasing in $\alpha$ (Appendix~\ref{sec:appendixB}).
 Therefore, $\bar{w}^*$ increases as $\alpha$ increases.
@@
 \newpage
-\section{Effect of interaction-transmission association on mean fitness} \label{sec:appendixC}
+\section{Effect of interaction-transmission association on mean fitness} \label{sec:appendixB}
 

### 2021-06-20 ms/Thesis/thesis.tex
Add the analysis of the reduction principal from appendix to main script

@@
 Suppose that the population has evolved to a stable equilibrium $\hat{p}^*$  when only allele $M$ is present.
-We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017} and obtain the following result.
+We study the local stability of this equilibrium to invasion by the modifier allele $m$; this is called ``external stability'' \citep{Liberman1986modifiers,Altenberg2017}.
+
+Denote the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ by $\vec{\hat{p}}= (\hat{p}_1$, $\hat{p}_2$, $\hat{p}_3$, $\hat{p}_4)$. 
+The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
+\begin{equation} \label{eq:next_gen_p_1}
+  \begin{aligned}
+	% p1
+  \bar{w}\hat{p}_1' = 
+  & v \hat{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) \;+ \\
+  & v \hat{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) \;+ \\
+  & v\hat{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) \;+ \\
+  & v\hat{p}_2(1-x)x(1-\alpha_1)T_A \;+ \\
+  & (1-v)\hat{p}_1(1-(1-x)T_B)\;+ \\
+  & (1-v)\hat{p}_2xT_A\;,
 \\
+	% p2
+  \bar{w}\hat{p}_2' = 
+  & v\hat{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \;+ \\
+  & v\hat{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) \;+ \\
+  & v\hat{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) \;+ \\
+  & v\hat{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;+ \\
+  & (1-v)\hat{p_2}(1-xT_A) \; + \\
+  & (1-v)\hat{p_1}T_B(1-x)\;,
+\\
+	% p3
+  \bar{w}\hat{p}_3' =
+  & \hat{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) \;+ \\
+  & \hat{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) \;+ \\
+  & \hat{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) \;+ \\
+  & \hat{p}_4(1-x) x (1-\alpha_2)T_A\; + \\
+  & (1-v)\hat{p}_3(1-(1-x)T_B)\;+ \\
+  & (1-v)\hat{p}_4xT_A\;,
+\\
+	% p4
+  \bar{w}\hat{p}_4' =
+  & \hat{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B \;+ \\
+  & \hat{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) \;+ \\
+  & \hat{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) \;+ \\
+  & \hat{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \; + \\
+  & (1-v)\hat{p_4}(1-xT_A) \; + \\
+  & (1-v)\hat{p_3}T_B(1-x)\;,
+  \end{aligned}
+\end{equation}
+%which we can write as 
+%\begin{equation}
+%\bar{w} \vec{\dot{p}} = F(\vec{\dot{p}}),
+%\end{equation}
+where $x=\hat{p}_1+\hat{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\dot{p}} = (\dot{p}_1,\dot{p}_2,\dot{p}_3,\dot{p}_4)$.
+
+The equilibrium where only allele $M$ is present is  $\vec{\hat{p}^*} = (\hat{p}^*, 1-\hat{p}^*, 0, 0)$, where
+\begin{equation} \label{eq:p_tilde_star_alpha_1}
+\hat{p}^*=
+\frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha_1 v)\big] (T_A-T_B)} \;,
+\end{equation}
+setting $\alpha=\alpha_1$ in \autoref{eq:general_equilibrium}.
+$\hat{p}^*$ is a feasible polymorphism ($0 < \hat{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
+
+The local stability of $\vec{\hat{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\hat{p}^*}$ (i.e.
+the Jacobian of the transformation at the equilibrium).
+$\cl^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\cl^*_{in}$ and $\cl^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
+The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\hat{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1}, with $\bar{w}^*=1+(b-c)\hat{p}^*$ as the stable population mean fitness,
+\begin{equation} \label{eq:external_stability_matrix}
+\begin{aligned}
+&\cl^*_{ex} = 
+ \frac{1}{\bar{w}^*} \begin{bmatrix}
+	 l_{1 1} &
+	 l_{1 2} \\
+	 l_{2 1} &
+	 l_{2 2} 
+\end{bmatrix} = 
+\frac{1}{\bar{w}^*} \begin{bmatrix}
+\frac{\partial\bar{w}\hat{p}_3'}{\partial \hat{p}_3}(\vec{\hat{p}}^*) &
+\frac{\partial\bar{w}\hat{p}_3'}{\partial \hat{p}_4}(\vec{\hat{p}}^*) \\
+\frac{\partial\bar{w}\hat{p}_4'}{\partial \hat{p}_3}(\vec{\hat{p}}^*) &
+\frac{\partial\bar{w}\hat{p}_4'}{\partial \hat{p}_4}(\vec{\hat{p}}^*) 
+\end{bmatrix} \;.
+\end{aligned}
+\end{equation}
+
+Because we assume that $\vec{\dot{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+$\vec{\dot{p}^*}$ is determined by the eigenvalues of the external stability matrix $\cl^*_{ex}$.
+This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\cl^*_{ex}$ is real and positive.
+Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\dot{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
+The eigenvalues of $\cl^*_{ex}$ are the roots of the characteristic polynomial, $R(\lambda)$,
+which is a quadratic with a positive leading coefficient.
+Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
+Thus, a sufficient condition for external instability of $\vec{\dot{p}^*}$ is $R(1) < 0$.
+$R(\lambda)$ is defined as a determinant, $R(\lambda)=\det(\cl^*_{ex} - \lambda \ci)$, where $\ci$ is the 2-by-2 identity matrix. 
+We did a full analysis without SymPy for the special case when $v=1$ (see Appendix~\ref{sec:appendixC}).
+We will use SymPy\citep{Meurer2017}, a Python library for symbolic mathematics to simplify $R(1)$ in the general case when $0<v\leq 1$. 
+\begin{equation} \label{eq:value_at_1}
+  \begin{aligned}
+  R(1) &= \frac{c v \hat{p}^*[T_Ab\hat{p}^{*2}(v\alpha_2-1)-2T_Ab\hat{p}^*v\alpha_2 + T_Ab\hat{p}^*(1+v\alpha_2)]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} \\
+ & + \frac{c v \hat{p}^*[T_Ac\hat{p}^{*2}(1-v)+T_Ac\hat{p}^*(v-1)-T_A\hat{p}^*(1-c)+T_A]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} \\
+  &+ \frac{c v \hat{p}^*[T_Bb\hat{p}^{*2}(1-v\alpha_2)+T_Bb\hat{p}^2(v\alpha_2-1)+T_Bc\hat{p}^{*2}(v-1)]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1}\\
+  &+ \frac{c v \hat{p}^*[T_Bc\hat{p}^*(1-v) + T_Bcv(1-\hat{p}^*+T_B(\hat{p}^*-1)+cv(\hat{p}^*-1))]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1}
+  \end{aligned}
+\end{equation}
+As explained, we should find when $R(1)<0$. We know that when $\alpha_1 = \alpha_2$, $R(1)=0$. 
+Now, let's assume that $\alpha_2 = \alpha_1 + \epsilon$. The derivative of $R(1)$ by $\epsilon$ will give us better understand about the sign of $R(1)$ when $\alpha_2<\alpha_1$.
+\begin{equation} \label{eq:value_at_1_derivative}
+  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b  v^2 \hat{p}^*[T_A\hat{p}^{*2}-2T_A\hat{p}^* + T_A-T_B\hat{p}^{*2}+T_B\hat{p}^*]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} 
+\end{equation}
+We can simplify \autoref{eq:value_at_1_derivative}
+\begin{equation} \label{eq:value_at_1_derivative_simplify}
+  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b v^2 \hat{p}^*[(T_A-T_B)\hat{p}^{*2}+(T_B-2T_A)\hat{p}^* + T_A]}{(b\hat{p}^*-c\hat{p}^*)^2+2\hat{p}^*(b-c)+1} 
+\end{equation}
+Since $b>c$ the denominator is always positive. The numerator is quadratic polynomial of $\hat{p}^*$ with the following roots:
+\begin{equation} \label{eq:numerator_roots}
+  \hat{p}^*_1 = \frac{T_A}{T_A-T_B} \hat{p}^*_2 = 1
+\end{equation}
+$\hat{p}^*_1 < 0$ since $T_B>T_A$ and since the quadratic polynomial has negative leading coefficient then the numerator is positive for every $\hat{p}^*_1<\hat{p}^*<1$ which is always true.
+We found that derivative of $R(1)$ by $\epsilon$ is positive for every $\epsilon$. 
+Therefore, $R(1)$ grows as $\epsilon$ grows, or in other words as $\alpha_2-\alpha_1$ grows.
+Thus, $R(1)<0$ if and only if $\alpha_2<\alpha_1$. This is a sufficient condition  for external instability.
+In addition, we also saw that $\frac{\partial R(1)}{\partial \epsilon} > 0$ for every $\epsilon$ which makes $\alpha_2<\alpha_1$ necessary and sufficient condition for successful invasion (external instability).
 
@@
 
-The analysis is in Appendix~\ref{sec:appendixD}.
 This reduction principle entails that successful invasions will reduce the frequency of cooperation, as well as the population mean fitness (\autoref{fig:invasion}).
@@
 Thus, we can expect the value of $\alpha$ to approach $a_2$, the frequency of cooperation to fall to zero, and the population mean fitness to decrease to one (\autoref{fig:invasion}).
-
-We can do similiar analysis for the general case where $0<v<1$ as we did in Appendix~\ref{sec:appendixD}.
-First we found the value of the characteristic polynomial at 1, $R(1)$ using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics.
-\begin{equation} \label{eq:value_at_1}
-  \begin{aligned}
-  R(1) &= \frac{c v \hat{p}^*[T_Ab\hat{p}^{*2}(v\alpha_2-1)-2T_Ab\hat{p}^*v\alpha_2 + T_Ab\hat{p}^*(1+v\alpha_2)]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} \\
- & + \frac{c v \hat{p}^*[T_Ac\hat{p}^{*2}(1-v)+T_Ac\hat{p}^*(v-1)-T_A\hat{p}^*(1-c)+T_A]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} \\
-  &+ \frac{c v \hat{p}^*[T_Bb\hat{p}^{*2}(1-v\alpha_2)+T_Bb\hat{p}^2(v\alpha_2-1)+T_Bc\hat{p}^{*2}(v-1)]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1}\\
-  &+ \frac{c v \hat{p}^*[T_Bc\hat{p}^*(1-v) + T_Bcv(1-\hat{p}^*+T_B(\hat{p}^*-1)+cv(\hat{p}^*-1))]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1}
-  \end{aligned}
-\end{equation}
-Similarly to what we did in Appendix~\ref{sec:appendixD}, we should find when $R(1)<0$. However, when adding the vertical transmission into the system the math is more complicated. 
-Therefore, we will use a different technique. We know that when $\alpha_1 = \alpha_2$, $R(1)=0$. 
-% DC: Yoav should I proof the statement above?
-Now, let's assume that $\alpha_2 = \alpha_1 + \epsilon$. The derivative of $R(1)$ by $\epsilon$ will give us better understand about the sign of $R(1)$ when $\alpha_2<\alpha_1$.
-\begin{equation} \label{eq:value_at_1_derivative}
-  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b  v^2 \hat{p}^*[T_A\hat{p}^{*2}-2T_A\hat{p}^* + T_A-T_B\hat{p}^{*2}+T_B\hat{p}^*]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} 
-\end{equation}
-We can simplify \autoref{eq:value_at_1_derivative}
-\begin{equation} \label{eq:value_at_1_derivative_simplify}
-  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b v^2 \hat{p}^*[(T_A-T_B)\hat{p}^{*2}+(T_B-2T_A)\hat{p}^* + T_A]}{(b\hat{p}^*-c\hat{p}^*)^2+2\hat{p}^*(b-c)+1} 
-\end{equation}
-Since $b>c$ the denominator is always positive. The numerator is quadratic polynomial of $\hat{p}^*$ with the following roots:
-\begin{equation} \label{eq:numerator_roots}
-  \hat{p}^*_1 = \frac{T_A}{T_A-T_B} \hat{p}^*_2 = 1
-\end{equation}
-$\hat{p}^*_1 < 0$ since $T_B>T_A$ and since the quadratic polynomial has negative leading coefficient then the numerator is positive for every $\hat{p}^*_1<\hat{p}^*<1$ which is always true.
-We found that derivative of $R(1)$ by $\epsilon$ is positive for every $\epsilon$. 
-Therefore, $R(1)$ grows as $\epsilon$ grows, or in other words as $\alpha_2-\alpha_1$ grows.
-Thus, $R(1)<0$ if and only if $\alpha_2<\alpha_1$.
-Therefore, different value of vertical transmission does not change the evolution of social-interaction association and invasion is possible when $\alpha_2<\alpha_1$.
-% DC: can I say if and only if
 
@@
 \newpage
-\section{Reduction principle} \label{sec:appendixD}
-
-We assume here that $v=1$, i.e. no oblique transmission, and therefore $\hat{p}=\dot{p}$.
-Denote the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ by $\vec{\dot{p}}= (\dot{p}_1$, $\dot{p}_2$, $\dot{p}_3$, $\dot{p}_4)$. 
-The frequencies of the pheno-genotypes in the next generation are defined by the recursion system, 
-\begin{equation} \label{eq:next_gen_p_1}
-  \begin{aligned}
-	% p1
-  \bar{w}\dot{p}_1' = 
-  & \dot{p}_1 x (1+b-c)(1 - (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \dot{p}_1(1-x)(1-c)(1-\alpha_1T_B x - T_B(1-x)) \;+ \\
-  & \dot{p}_2 x (1+b)T_A(x + \alpha_1(1-x)) \;+ \\
-  & \dot{p}_2(1-x)x(1-\alpha_1)T_A \;,
-\\
-	% p2
-  \bar{w}\dot{p}_2' = 
-  & \dot{p}_1 x (1+b-c)(1-\alpha_1)(1-x)T_B \;+ \\
-  & \dot{p}_1(1-x)(1-c)(\alpha_1 T_B + (1-\alpha_1)(1-x)T_B) \;+ \\
-  & \dot{p}_2 x (1+b)(1-\alpha_1 T_A(1-x) - T_A x) \;+ \\
-& \dot{p}_2(1-x)(1 - (1-\alpha_1) x T_A) \;, 
-\\
-	% p3
-  \bar{w}\dot{p}_3' =
-  & \dot{p}_3 x (1+b-c)(1 - (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \dot{p}_3(1-x)(1-c)(1-\alpha_2 T_B x - T_B(1-x)) \;+ \\
-  & \dot{p}_4 x (1+b)T_A(x + \alpha_2 (1-x)) \;+ \\
-  & \dot{p}_4(1-x) x (1-\alpha_2)T_A \;, 
-\\
-	% p4
-  \bar{w}\dot{p}_4' =
-  & \dot{p}_3 x (1+b-c)(1-\alpha_2)(1-x)T_B \;+ \\
-  & \dot{p}_3(1-x)(1-c)(\alpha_2 T_B + (1-\alpha_2)(1-x)T_B) \;+ \\
-  & \dot{p}_4 x (1+b)(1-\alpha_2T_A(1-x)-T_A x ) \;+ \\
-  & \dot{p}_4(1-x)(1 - (1-\alpha_2) x T_A) \;,
-  \end{aligned}
-\end{equation}
-%which we can write as 
-%\begin{equation}
-%\bar{w} \vec{\dot{p}} = F(\vec{\dot{p}}),
-%\end{equation}
-where $x=\dot{p}_1+\dot{p}_3$ is the total frequency of the cooperative phenotype $A$, and $\bar{w} = 1 + (b-c) x$ is the population mean fitness.% and $\vec{\dot{p}} = (\dot{p}_1,\dot{p}_2,\dot{p}_3,\dot{p}_4)$.
-
-The equilibrium where only allele $M$ is present is  $\vec{\dot{p}^*} = (\dot{p}^*, 1-\dot{p}^*, 0, 0)$, where
-\begin{equation} \label{eq:p_tilde_star_alpha_1}
-\dot{p}^*=
-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)} \;,
-\end{equation}
-setting $\alpha=\alpha_1$ and $v=1$ in \autoref{eq:general_equilibrium}.
-When $v=1$, $\dot p^*$ is a feasible polymorphism ($0 < \dot{p}^* < 1$) if $T_A<T_B$ and $\gamma_2<c<\gamma_1$ (Result~\ref{result:vert_obli_hori}).
-
-The local stability of $\vec{\dot{p}^*}$ to the introduction of allele $m$ is determined by the linear approximation $\cl^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\dot{p}^*}$ (i.e.
-the Jacobian of the transformation at the equilibrium).
-$\cl^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\cl^*_{in}$ and $\cl^*_{ex}$ \citep{Liberman1986modifiers,Altenberg2017} .
-The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\dot{p}^*}$ involving only the pheno-genotypes $Am$ and $Bm$, derived from \autoref{eq:next_gen_p_1}, with $\bar{w}^*=1+(b-c)\dot{p}^*$ as the stable population mean fitness,
-\begin{equation} \label{eq:external_stability_matrix}
+\section{Reduction principle} \label{sec:appendixC}
+Here, we assume perfect vertical transmission $v=1$. We start from \autoref{eq:external_stability_matrix} and we substitute $v=1$ and we get
+\begin{equation} \label{eq:external_stability_matrix_v1}
   \begin{aligned}
@@
   \frac{1}{\bar{w}^*} \begin{bmatrix}
-\frac{\partial\bar{w}\dot{p}_3'}{\partial \dot{p}_3}(\vec{\dot{p}}^*) &
-\frac{\partial\bar{w}\dot{p}_3'}{\partial \dot{p}_4}(\vec{\dot{p}}^*) \\
-\frac{\partial\bar{w}\dot{p}_4'}{\partial \dot{p}_3}(\vec{\dot{p}}^*) &
-\frac{\partial\bar{w}\dot{p}_4'}{\partial \dot{p}_4}(\vec{\dot{p}}^*) 
-\end{bmatrix} \;= \\
+  \frac{\partial\bar{w}\hat{p}_3'}{\partial \hat{p}_3}(\vec{\hat{p}}^*) &
+  \frac{\partial\bar{w}\hat{p}_3'}{\partial \hat{p}_4}(\vec{\hat{p}}^*) \\
+  \frac{\partial\bar{w}\hat{p}_4'}{\partial \hat{p}_3}(\vec{\hat{p}}^*) &
+  \frac{\partial\bar{w}\hat{p}_4'}{\partial \hat{p}_4}(\vec{\hat{p}}^*) 
+  \end{bmatrix} \; = \\
   & \frac{1}{\bar{w}^*} \begin{bmatrix}
@@
       (1+b \dot{p}^*) (1-T_A \dot{p}^*) - b \dot{p}^* \alpha_2 T_A (1-\dot{p}^*) \\
-  	\end{bmatrix} \;.
-\end{aligned}
-\end{equation}
-
-Because we assume that $\vec{\dot{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
-$\vec{\dot{p}^*}$ is determined by the eigenvalues of the external stability matrix $\cl^*_{ex}$.
-This is a positive matrix, and due to the Perron-Frobenius theorem, the leading eigenvalue of $\cl^*_{ex}$ is real and positive.
-Thus, if the leading eigenvalue is less (greater) than one, then the equilibrium $\vec{\dot{p}^*}$ is externally stable (unstable) and allele $m$ cannot (can) invade the population of allele $M$. 
-The eigenvalues of $\cl^*_{ex}$ are the roots of the characteristic polynomial, $R(\lambda)$,
-%\begin{equation}\label{char_poly}
-%R(\lambda) = 
-%\lambda^2 -\lambda \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} \;,
-%\end{equation}
-%where $X$, $Y$, $Z$, and $Q$ are defined in \autoref{eq:external_stability_matrix}.
-which is a quadratic with a positive leading coefficient.
-Therefore, $\lim_{\lambda \to \pm \infty} R(\lambda) = \infty$, and the leading eigenvalue is less than one (implying stability) if and only if $R(1)>0$ and $R'(1)>0$.
-Thus, a sufficient condition for external instability of $\vec{\dot{p}^*}$ is $R(1) < 0$.
-%\begin{equation} \label{eq:R1_negative}
-%\begin{aligned}
-%R(1) < 0 \Leftrightarrow 
-%1 - \frac{(X+Q)}{\bar{w^*}} + \frac{XQ - YZ}{\bar{w^*}^2} < 0 \Leftrightarrow 
-%\bar{w^*}^2 - \bar{w^*} (X+Q) + XQ - YZ < 0 \;.
-%\end{aligned}
-%\end{equation}
-
-$R(\lambda)$ is defined as a determinant, $R(\lambda)=\det(\cl^*_{ex} - \lambda \ci)$, where $\ci$ is the 2-by-2 identity matrix. 
+      \end{bmatrix} \;
+  \end{aligned}
+  \end{equation}
 Since multiplication by a positive factor doesn't change the sign, and using the properties of the determinant,  we have
@@
 Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-However, we have numerically validated that the leading eigenvalue is greater than one if and only if $\alpha_1>\alpha_2$.
+We did it in the general case.
 

### 2021-07-02 ms/Thesis/thesis.tex
minor fix
Improve intro

@@
 To understand the evolution of cooperation we are going to use \emph{replicator dynamics}. The replicator in replicator dynamics has the ability to make one or more copies of itself.
-The replicator can be a gene, a phenotype, a stragey in a game and etc. In cooperation context replicator is a different stragey in the game, whether the individual is a cooperative or a defector.
+The replicator can be a gene, a phenotype, a strategy in a game and etc.
+In evolutionary game theory context replicator is a different strategy in the game.
+For example, in the case of cooperation whether the individual is a cooperative or a defector.
 In replicator dynamics we assume large population of replicators, which interact with respect to their proportion.
@@
 Similar to dominant strategies bringing forth Nash equilibria when games are repeated, strategies in replicator dynamics can become evolutionary stable.
-Such strategies are called \emph{Evolutionarily Stable Stragey (ESS)}.
-Such strategies cannot be invaded by any other strategy that is initially rare. Evolutionarily stable stragey maximizes the expected fitness of its chooser and therefore, causing maximum mean fitness.
+Such strategies are called \emph{Evolutionarily Stable strategy (ESS)}.
+Such strategies cannot be invaded by any other strategy that is initially rare.
+Evolutionarily stable strategy maximizes the expected fitness of its chooser and therefore, causing maximum mean fitness.
 An interesting and fundamental question is to verify whether natural selection, operating within the framework of known genetical models leads to ESS.
-Note that usually natural selection does not lead to an increase in the average mean fitness of the population.
-Therefore, it is not generally true that natural selection does operate as to maximize the average individual fitness resulting in an optimal population strategy.
-%DC: I need reference for the statement above
-Instead of searching evolutionarily stable stragey, we focus on \emph{Evolutionary Genetic Stblility (EGS)}\citep{lessard1990evolutionary}.
-EGS is when the frequency of types (geneotype, phenotype etc.) stays the same.
+The answer to the question above is that natural selection usually does not lead to an increase in the average mean fitness of the population.
+Therefore, it is not generally true that natural selection does operate as to maximize the average individual fitness resulting in an ESS.
+\citet{sacks1967stable} even showed that natural selection at a diploid locus model when relative fitnesses of the different genotypes are functions of gene frequency leads to stable equilibrium gene frequency that corresponds to minimum mean fitness.
+Instead of searching evolutionarily stable strategy, we focus on \emph{Evolutionary Genetic Stblility (EGS)}\citep{lessard1990evolutionary}.
+EGS is when the frequency of types (genotype, phenotype etc.) stays the same.
 Here, we study both local stability and external stability. Equilibrium is consider \emph{Local stability} when a system near the equilibrium approaches it.
-\emph{External stability} is a  local stability of the equilibrium to invasion by the modifier allele m.
+\emph{External stability}\citep{Liberman1986modifiers,Altenberg2017} is a local stability of the equilibrium to invasion by the modifier allele m.
 One of the main questions in the evolution of cooperation is under what conditions such invasions are possible, or in other words under what conditions the system is external unstable.
@@
 The yellow and blue areas in Figures~\ref{fig:equilibria_v1} and \ref{fig:equilibria} show cases of stable and unstable polymorphism, respectively.
-When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$.
+When $\hat{p}^*$ is unstable, cooperation will fix if its initial frequency is $\hat{p}>\hat{p}^*$, and defection will fix if $\hat{p}<\hat{p}^*$ as shown in \autoref{fig:time_series}a.
 $\hat{p}^*$ is unstable when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
-\autoref{fig:equilibria_v1}d shows $\hat{p}'-\hat{p}$ as a function of $\hat{p}$.
+\autoref{fig:equilibria_v1}d shows $\hat{p}'-\hat{p}$ as a function of $\hat{p}$ and \autoref{fig:time_series} shows the frequency of cooperation over time in both stable and unstable equilibrium regimes.
 
@@
     In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
-    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b) $T_B=0.7$, $\alpha=0.6$ and $b=2.3$}.}
+    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b)} $T_B=0.7$, $\alpha=0.6$ and $b=2.3$.}
     \label{fig:time_series}
@@
 Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-We did it in the general case.
+We did it in the general case (starting from \autoref{eq:value_at_1_derivative}).
 

### 2021-07-04 ms/Thesis/thesis.tex

@@
 Therefore, $\bar{w}^*$ increases as $\alpha$ increases.
-But can this population-level advantage lead to the evolution of $\alpha$?
-
-To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $alpha$ but has no direct effect on fitness.
+But can this population-level advantage lead to the evolution of increased $\alpha$?
+
+To answer this question, we add a ``modifier locus''~\citep{Feldman1972,Liberman1986general,Liberman1986modifiers,Liberman1988} that determines the value of $\alpha$ but has no direct effect on fitness.
 This locus has two alleles, $M$ and $m$, which induce interaction-transmission associations $\alpha_1$ and $\alpha_2$, respectively.
@@
 
-The equilibrium where only allele $M$ is present is  $\vec{\hat{p}^*} = (\hat{p}^*, 1-\hat{p}^*, 0, 0)$, where
+The stable equilibrium where only allele $M$ is present is  $\vec{\hat{p}^*} = (\hat{p}^*, 1-\hat{p}^*, 0, 0)$, where
 \begin{equation} \label{eq:p_tilde_star_alpha_1}
@@
 
-Because we assume that $\vec{\dot{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
+Because we already assumed that $\vec{\dot{p}^*}$ is internally stable at the beginning of the analysis (i.e.
+locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of
 $\vec{\dot{p}^*}$ is determined by the eigenvalues of the external stability matrix $\cl^*_{ex}$.
@@
 $R(\lambda)$ is defined as a determinant, $R(\lambda)=\det(\cl^*_{ex} - \lambda \ci)$, where $\ci$ is the 2-by-2 identity matrix. 
-We did a full analysis without SymPy for the special case when $v=1$ (see Appendix~\ref{sec:appendixC}).
-We will use SymPy\citep{Meurer2017}, a Python library for symbolic mathematics to simplify $R(1)$ in the general case when $0<v\leq 1$. 
+We will use SymPy \citep{Meurer2017}, a Python library for symbolic mathematics to simplify $R(1)$ in the general case when $0<v\leq 1$ (We did a full analysis without SymPy for the special case when $v=1$ in Appendix~\ref{sec:appendixC}),
 \begin{equation} \label{eq:value_at_1}
@@
 \end{equation}
-As explained, we should find when $R(1)<0$. We know that when $\alpha_1 = \alpha_2$, $R(1)=0$. 
-Now, let's assume that $\alpha_2 = \alpha_1 + \epsilon$. The derivative of $R(1)$ by $\epsilon$ will give us better understand about the sign of $R(1)$ when $\alpha_2<\alpha_1$.
-\begin{equation} \label{eq:value_at_1_derivative}
-  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b  v^2 \hat{p}^*[T_A\hat{p}^{*2}-2T_A\hat{p}^* + T_A-T_B\hat{p}^{*2}+T_B\hat{p}^*]}{b\hat{p}(b\hat{p}^*-2\hat{p}^*+2)+c\hat{p}^*(c\hat{p}^*-2)+1} 
-\end{equation}
-We can simplify \autoref{eq:value_at_1_derivative}
+We should find when $R(1)<0$. Using SymPy we saw that when $\alpha_1=\alpha_2$, $R(1)=0$ which means that there is an eigenvalue that is equal to 1.
+Now, assume that $\epsilon = \alpha_2 - \alpha_1$. Using the derivative of $R(1)$ with respect to $\epsilon$ we will find the sign of $R(1)$ when $\alpha_2<\alpha_1$.
 \begin{equation} \label{eq:value_at_1_derivative_simplify}
-  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b v^2 \hat{p}^*[(T_A-T_B)\hat{p}^{*2}+(T_B-2T_A)\hat{p}^* + T_A]}{(b\hat{p}^*-c\hat{p}^*)^2+2\hat{p}^*(b-c)+1} 
-\end{equation}
-Since $b>c$ the denominator is always positive. The numerator is quadratic polynomial of $\hat{p}^*$ with the following roots:
+  \frac{\partial R(1)}{\partial \epsilon} = \frac{c b v^2 \hat{p}^*[(T_A-T_B)\hat{p}^{*2}+(T_B-2T_A)\hat{p}^* + T_A]}{(\hat{p}^*(b-c)+1)^2} 
+\end{equation}
+The denominator is always positive. The numerator is quadratic polynomial of $\hat{p}^*$ with the following roots:
 \begin{equation} \label{eq:numerator_roots}
-  \hat{p}^*_1 = \frac{T_A}{T_A-T_B} \hat{p}^*_2 = 1
-\end{equation}
-$\hat{p}^*_1 < 0$ since $T_B>T_A$ and since the quadratic polynomial has negative leading coefficient then the numerator is positive for every $\hat{p}^*_1<\hat{p}^*<1$ which is always true.
-We found that derivative of $R(1)$ by $\epsilon$ is positive for every $\epsilon$. 
-Therefore, $R(1)$ grows as $\epsilon$ grows, or in other words as $\alpha_2-\alpha_1$ grows.
-Thus, $R(1)<0$ if and only if $\alpha_2<\alpha_1$. This is a sufficient condition  for external instability.
+  \hat{p}^*_1 = \frac{T_A}{T_A-T_B} \,\,\,\, \hat{p}^*_2 = 1
+\end{equation}
+We assumed $T_B > T_A$ thus, $\hat{p}^*_1<0$. The quadratic polynomial has negative leading coefficient ($T_A-T_B$), and therefore,the numerator is positive for any $\hat{p}^*_1<\hat{p}^*<1$.
+Thus, the derivative of $R(1)$ with respect to $\epsilon$ is positive for any $\epsilon$ and R(1) grows as $\alpha_2-\alpha_1$ grows. 
+Therefore, because $R(1)$ grows as $\alpha_2-\alpha_1$ grows and $R(1)=0$ when $\alpha_2-\alpha_1=0$, we get that $R(1)<0$ if and only if $\alpha_2<\alpha_1$.
+This is a sufficient condition  for external instability.
 In addition, we also saw that $\frac{\partial R(1)}{\partial \epsilon} > 0$ for every $\epsilon$ which makes $\alpha_2<\alpha_1$ necessary and sufficient condition for successful invasion (external instability).

### 2021-07-08 ms/Thesis/thesis.tex
Move the description of the invasion model and the population str. model to the model section

@@
 
+\subsection{Basic Model}
+\label{section:basicmodel}
 Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
@@
 
-%%% Figure: model illustration
+%%% Figure: model illustration - basic model
 \begin{figure}[pt]
@@
 
+\subsection{Invasion Model}
+In this section, we use the model described in \autoref{section:basicmodel}. 
+Here we assume a coexistence of both phenotypes (cooperators and defectors) and that the frequency of each phenotye stays the same each generation.
+Henece, we assume that the we start from one of the equilibrium.
+In addition, we assume that the equilibria is stable.  Denote the frequency of cooperators in the population in $\hat{p}^*$ and frequency of defectors $1-\hat{p}^*$.
+
+Starting from the assumption described above we want to investigate the evolution of interaction-transmission association $\alpha$.
+We assume that the initial population has interaction-transmission association $\alpha_1$. 
+We want to answer the question what would happen to cooperators frequency if a new mutation would occur and change the interaction-transmission association to a different value $\alpha_2$ without direct effect on fitness.
+We can think of this model as an invasion model where the invadors are the individuals with interaction-transmission association $\alpha_2$.
+\autoref{fig:invasion_illustration} illustrates the invasion.
+
+%%% Figure: model illustration - invasion model
+\begin{figure}[pt]
+  \centering
+  \includegraphics[width=0.7\textwidth]{../PRSB_figures/fig_2.pdf}
+  \caption{\textbf{Invasion model illustration.} Starting from stable equilibrium with coexistence of both phenotypes. 
+  A mutation that has effect only the interaction-transmission association tries to invade. }
+  \label{fig:invasion_illustration}
+\end{figure}
+
+\newpage
+\subsection{Population structure model}
+\label{sec:spatialModel}
+Interaction-transmission association may also emerge from population structure.
+Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
+Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
+Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
+In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
+initiators interact with a random neighbor (i.e.
+individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}c) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
+The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.
+The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
+On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in neighbourhoods close to the grid border.
+As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
+
+The order of the interactions across the grid at each generation is random.
+After all interactions take place, an individual's fitness is determined by
+$w = 1 + b \cdot n_b - c \cdot n_c$,
+where $n_b$ is the number of interactions that individual had with cooperative neighbors,
+and $n_c$ is the number of interactions in which that individual cooperated (note that the phenotype may change between consecutive interactions due to horizontal transmission).
+Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
+Selection is global, rather than local, in accordance with our deterministic model:
+The parent is randomly drawn with probability proportional to its fitness, divided by the sum of the fitness values of all potential parents.
+Offspring are assumed to have the same phenotype as their parents (i.e. $v=1$).
+
 \newpage
@@
   \centering       
-    \includegraphics[width=1\textwidth]{../PRSB_figures/fig_2.pdf}
+    \includegraphics[width=1\textwidth]{../PRSB_figures/fig_3.pdf}
     \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
@@
   \centering       
-	\includegraphics[width=1\textwidth]{../PRSB_figures/fig_3.pdf}
+	\includegraphics[width=1\textwidth]{../PRSB_figures/fig_4.pdf}
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
@@
     \includegraphics[scale=0.5]{../Figures/Stable_Time_series.eps}
-    \caption{\textbf{Stable and unstable equilibrium dynamics} 
+    \caption{\textbf{Unstable and stable equilibrium dynamics} 
     The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
@@
   \centering
-  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_s1.pdf}
+  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_6.pdf}
   \caption{
@@
 \subsection{Population structure}
+Here, we are going to run stochastic simulations to learn more about evolution of Cooperation when the population is structured. 
+The model is described in \autoref{sec:spatialModel}.
 All the simulations in this section were made by Ohad Lewin-Epstein from Tel Aviv University.
-Interaction-transmission association may also emerge from population structure.
-Consider a  population colonizing a two-dimensional grid of size 100-by-100, where each site is inhabited by one individual, similarly to the model of \citet{lewin2020rockpaperscissors}.
-Each individual is characterized by its phenotype: either cooperator, $A$, or defector, $B$.
-Initially, each site in the grid is randomly colonized by either a cooperator or a defector, with equal probability.
-In each generation, half of the individuals are randomly chosen to "initiate" interactions, and these
-initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}c) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
-The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.
-The effective interaction-transmission association $\alpha$ in this model is the probability that the same neighbor is picked for both interactions, or $\alpha=1/M$, where $M$ is the number of neighbors.
-On an infinite grid, $M=8$ (i.e. Moore neighbourhood~\citep{moore1962machine}), but on a finite grid $M$ can be lower in neighbourhoods close to the grid border.
-As before, $T_A$ and $T_B$ are the probabilities of successful horizontal transmission of phenotypes $A$ and $B$, respectively.
-
-The order of the interactions across the grid at each generation is random.
-After all interactions take place, an individual's fitness is determined by
-$w = 1 + b \cdot n_b - c \cdot n_c$,
-where $n_b$ is the number of interactions that individual had with cooperative neighbors,
-and $n_c$ is the number of interactions in which that individual cooperated (note that the phenotype may change between consecutive interactions due to horizontal transmission).
-Then, a new generation is produced, and the sites can be settled by offspring of any parent, not just the neighboring parents.
-Selection is global, rather than local, in accordance with our deterministic model:
-The parent is randomly drawn with probability proportional to its fitness, divided by the sum of the fitness values of all potential parents.
-Offspring are assumed to have the same phenotype as their parents (i.e. $v=1$).
-
 The outcomes of stochastic simulations with such a structured population are shown in \autoref{fig:spatial}, which demonstrates that the highest cost of cooperation $c$ that permits the evolution of cooperation agrees with the conditions derived above for our model without population structure or stochasticity.
@@
   \centering
-  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_4.pdf}
+  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_7.pdf}
   \caption{
@@
   \centering
-  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_s2.pdf}
+  \includegraphics[width=1\textwidth]{../PRSB_figures/fig_8.pdf}
   \caption{

### 2021-07-11 ms/Thesis/thesis.tex
Add (a) and (b) labels to figure 5 - time series
Add feuture work to the discussion

@@
   \centering       
-    \includegraphics[scale=0.5]{../Figures/Unstable_Time_series.eps}
-    \includegraphics[scale=0.5]{../Figures/Stable_Time_series.eps}
+    \includegraphics[scale=0.5]{../PRSB_figures/fig_5.pdf}
     \caption{\textbf{Unstable and stable equilibrium dynamics} 
@@
 If the individual over estimate the number of cooperators it will be more likely to cooperate.
-This flase belief can help sustain cooperation even if cooperartion is initially rare.
+This false belief can help sustain cooperation even if cooperartion is initially rare.
 % DC: Let's discuss this paragraph - is it good?
+
+In this work, we have studied a cultural evolution model in which interactions are modeled as a prisoner's dilemma game.
+We also assumed that in each generation individuals have only one meaningful interaction.
+It would be interesting to investigate a model in which multiple games are played in each generation. 
+This would make the model more realistic and more complicated to solve. To overcome the math complication, a numerical simulations can be used. 
+The model can be further expand by changing the game to Stag Hunt game. \citet{tomasello2012two} claim that Stag Hunt game can better explain evolution of cooperation in humans. 
+Humans often collobrate in Stag Hunt type situations in which all participants had alternatives but anticipated an even greater benefit from
+successful capturing of the stag\citep{mitani2012evolution}.
 

### 2021-07-11 ms/Thesis/thesis.tex
Go over Yoav's comments

@@
 
-Beside kin selection, two more major theroies were suggested to explain to evolution of cooperation.
+Beside kin selection, two other major theroies were suggested to explain to evolution of cooperation.
 
@@
 Hence, it may pay off to cooperate.
-This game-theoretic framework is known as the repeated Prisoner's Dilemma. 
-Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit. 
+This game-theoretic framework is known as the \emph{repeated Prisoner's Dilemma}. 
+Direct reciprocity can only lead to the evolution of cooperation if the cost is smaller than $w$ the probability for another encounter between the same two individuals multiplied by the benefit, 
 \begin{equation} \label{reciprocity}
-c<bw
+c<b\cdot w \,.
 \end{equation}
 Direct reciprocity assumes that both players are in a position to cooperate.
-Direct reciprocity can not explain cooperation in asymmetric interactions.
-In humans, such interactions happen often, for example humans often donate money.
+Direct reciprocity can not explain cooperation in asymmetric interactions\citep{su2021evolution}.
+In humans, such interactions happen often, for example, humans donate money.
 \textit{Indirect reciprocity} has been suggested to explain this behavior. 
-Nowak \cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of money.
-The money that "fuels the engines" of indirect reciprocity is reputation.
-However, Reciprocity assume repeating interactions and therefore, has difficulty explaining evolution of cooperation if the no repeating interactions occurs.
+Nowak \cite{nowak2006five} claims that direct reciprocity is like a barter economy based on the immediate exchange of goods, while indirect reciprocity resembles the invention of currercy.
+The currercy that "fuels the engines" of indirect reciprocity is \emph{reputation}.
+However, reciprocity assumes repeating interactions and therefore, has difficulty explaining evolution of cooperation if no repeating interactions occurs.
 
@@
 A common model for group selection work as is: the population is divided into groups.
-In each groups there are cooperators, which help to other group members and defectors which do not help.
+In each group there are cooperators, which help other group members, and defectors, which do not help.
 Individuals reproduce proportional to their fitness. Offspring are added to the same group.
-If a group reaches a certain size it can split to two groups. A group that grow faster will split more often. Groups of cooperators are growing faster than group of defectors.
-Therefore, cooperation can evolve in this model when the ratio between benefit b and cost c is more than one plus the ratio between the maximum group size n and the number of groups m:
+If a group reaches a certain size it can split to two groups. A group that grows faster will split more often. Groups of cooperators grow faster than groups of defectors.
+Therefore, cooperation can evolve in this model when
 \begin{equation} \label{groupselection}
-\frac{b}{c}>1+\frac{n}{m}
-\end{equation}
+\frac{b}{c}>1+\frac{n}{m}\, ,
+\end{equation}
+where \emph{n} is the maximum group size and \emph{m} is the number of groups.
+\\
 
 All three theories mentioned above assume that cooperation is genetically determined. This raise the question, is it possible that cooperation is determined by environmental or social influences.
-Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
+Cooperative behavior may be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
 Cultural transmission may be  modeled as vertical, horizontal, or oblique:  vertical transmission occurs between parents and offspring, horizontal transmission occurs between individuals from the same generation, and oblique transmission occurs  to offspring from the generation to which their parents belong (i.e.
@@
 Evolution under either of these transmission models can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
-
-Here, we study models for the cultural evolution of cooperation that include both vertical and non-vertical transmission. 
-In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
-For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission,
-or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
-Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because it diminishes the effect of selection (due to non-vertical transmission from non-reproducing individuals~\citep{ram2018evolution}).
-
-To understand the evolution of cooperation we are going to use \emph{replicator dynamics}. The replicator in replicator dynamics has the ability to make one or more copies of itself.
-The replicator can be a gene, a phenotype, a strategy in a game and etc.
-In evolutionary game theory context replicator is a different strategy in the game.
-For example, in the case of cooperation whether the individual is a cooperative or a defector.
-In replicator dynamics we assume large population of replicators, which interact with respect to their proportion.
-Those interactions of different replicator affect the fitness acorrding to some payoff matrix. The payoff matrix depands on the game which is played. 
-The most common game to describe cooperation is prisoner's dilemma\citep{nowak1992tit}.
-Similar to dominant strategies bringing forth Nash equilibria when games are repeated, strategies in replicator dynamics can become evolutionary stable.
-Such strategies are called \emph{Evolutionarily Stable strategy (ESS)}.
-Such strategies cannot be invaded by any other strategy that is initially rare.
-Evolutionarily stable strategy maximizes the expected fitness of its chooser and therefore, causing maximum mean fitness.
-An interesting and fundamental question is to verify whether natural selection, operating within the framework of known genetical models leads to ESS.
-The answer to the question above is that natural selection usually does not lead to an increase in the average mean fitness of the population.
-Therefore, it is not generally true that natural selection does operate as to maximize the average individual fitness resulting in an ESS.
-\citet{sacks1967stable} even showed that natural selection at a diploid locus model when relative fitnesses of the different genotypes are functions of gene frequency leads to stable equilibrium gene frequency that corresponds to minimum mean fitness.
-Instead of searching evolutionarily stable strategy, we focus on \emph{Evolutionary Genetic Stblility (EGS)}\citep{lessard1990evolutionary}.
-EGS is when the frequency of types (genotype, phenotype etc.) stays the same.
-Here, we study both local stability and external stability. Equilibrium is consider \emph{Local stability} when a system near the equilibrium approaches it.
-\emph{External stability}\citep{Liberman1986modifiers,Altenberg2017} is a local stability of the equilibrium to invasion by the modifier allele m.
-One of the main questions in the evolution of cooperation is under what conditions such invasions are possible, or in other words under what conditions the system is external unstable.
 
@@
 
-\citet{handley2020human} showed the importance of culture on the human behavior.
+\citet{handley2020human} studied the importance of culture on human behavior.
 They showed that the probablity of indvidual to cooperate with unrelated strangers from a different group in transient interactions corresponds to the degree of cultural similarity between those groups.
 Therefore, they have suggested that group-level selection on culturally differentiated populations can explain cooperation between unrelated humans from different groups.
+
+To understand the evolution of cooperation we are going to use \emph{replicator dynamics}. The replicator in replicator dynamics has the ability to make one or more copies of itself.
+The replicator can be a gene, a phenotype, a strategy in a game and etc.
+In evolutionary game theory context replicator is a different strategy in the game.
+For example, in the case of cooperation whether the individual is a cooperative or a defector.
+In replicator dynamics we assume large population of replicators, which interact with respect to their frequency.
+Interactions of different replicator affect the fitness acorrding to some payoff matrix. This payoff matrix depands on the game which is played. 
+The most common game to describe cooperation is the \emph{Prisoner's Dilemma}\citep{nowak1992tit}.
+Similar to dominant strategies bringing forth Nash equilibria when games are repeated, strategies in replicator dynamics can become evolutionary stable.
+Such strategies are called \emph{evolutionarily stable strategies (ESS)}.
+Such strategies cannot be invaded by any other strategy that is initially rare.
+Evolutionarily stable strategies maximize the expected fitness of its replicators and therefore, maximize the population mean fitness.
+A fundamental question is to test if natural selection, operating within the framework of known genetical models, leads to ESS.
+The answer to the question above is that natural selection in many cases does not lead to an increase in the population mean fitness.
+Therefore, it is not generally true that natural selection does operate as to maximize the average individual fitness resulting in an ESS.
+\citet{sacks1967stable} even showed that natural selection at a diploid locus model, when relative fitnesses of the different genotypes are functions of gene frequency, leads to stable equilibrium gene frequencies that corresponds to not maximum mean fitness.
+Instead of searching for evolutionarily stable strategies, we focus on \emph{evolutionary genetic stblility (EGS)}\citep{lessard1990evolutionary}.
+EGS occurs when the frequencies of types (genotypes, phenotypes etc.) remains stable.
+Here, we study both \emph{local stability} and \emph{external stability}. \emph{Local stability} occurs when a system near the equilibrium wiil approach it.
+\emph{External stability} \citep{Liberman1986modifiers,Altenberg2017} is local stability of the equilibrium to invasion by a modifier allele \emph{m}.
+One of the main questions in the evolution of cooperation is under what conditions such invasions are possible, or in other words under what conditions the system is externally unstable?
+
+Here, we study models for the cultural evolution of cooperation that include both vertical and non-vertical transmission. 
+In our models behavioral changes are mediated by cultural transmission that can occur specifically during social interactions.
+For instance, there may be an association between the choice of partner for social interaction and the choice of partner for cultural transmission,
+or when an individual interacts with an individual of a different phenotype,  exposure to the latter may lead the former to  convert its phenotype.
+Our results demonstrate that cultural transmission, when associated with social interactions, can enhance the evolution of cooperation even when genetic transmission cannot, partly because it facilitates the generation of assortment \citep{Fletcher2009assortment}, and partly because it diminishes the effect of selection (due to non-vertical transmission from non-reproducing individuals~\citep{ram2018evolution}).
 
@@
 \label{section:basicmodel}
-Consider a large population whose members can be one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
+Consider a large population whose members can have one of two phenotypes: $\phi=A$ for cooperators or $\phi=B$ for defectors.
 An offspring inherits its phenotype from its parent via vertical transmission with probability $v$ or from a random individual in the parental population via oblique transmission with probability $(1-v)$ (\autoref{fig:illustration}a).
@@
 \subsection{Invasion Model}
-In this section, we use the model described in \autoref{section:basicmodel}. 
-Here we assume a coexistence of both phenotypes (cooperators and defectors) and that the frequency of each phenotye stays the same each generation.
-Henece, we assume that the we start from one of the equilibrium.
-In addition, we assume that the equilibria is stable.  Denote the frequency of cooperators in the population in $\hat{p}^*$ and frequency of defectors $1-\hat{p}^*$.
-
-Starting from the assumption described above we want to investigate the evolution of interaction-transmission association $\alpha$.
+In this section, we extend the model described in \autoref{section:basicmodel}. 
+We assume coexistence of both phenotypes (cooperators and defectors) and that the frequency of each phenotye stays stable over time.
+Hence, we assume that the we start from a stable equilibrium. Denote the frequency of cooperators in the population as $\hat{p}^*$ and frequency of defectors as $1-\hat{p}^*$.
+
+We investigate the evolution of interaction-transmission association $\alpha$.
 We assume that the initial population has interaction-transmission association $\alpha_1$. 
-We want to answer the question what would happen to cooperators frequency if a new mutation would occur and change the interaction-transmission association to a different value $\alpha_2$ without direct effect on fitness.
-We can think of this model as an invasion model where the invadors are the individuals with interaction-transmission association $\alpha_2$.
-\autoref{fig:invasion_illustration} illustrates the invasion.
+What would happen to cooperators frequency if a new mutation would occur that changed the interaction-transmission association to a different value $\alpha_2$ without direct effect on fitness?
+Here, the invaders are the individuals with interaction-transmission association $\alpha_2$. \autoref{fig:invasion_illustration} illustrates the invasion.
 
@@
   \caption{\textbf{Invasion model illustration.} Starting from stable equilibrium with coexistence of both phenotypes. 
-  A mutation that has effect only the interaction-transmission association tries to invade. }
+  A mutation that affected only the interaction-transmission association $\alpha$ invades the population }
   \label{fig:invasion_illustration}
@@
 In these structured populations interaction-transmission association arises due to both social interactions and horizontal cultural transmission being local (\autoref{fig:spatial} and \autoref{fig:spatial_local_selection}).
-We did not find any significant difference between local and global selection. %DC: can we disucss why there is not difference?
+We did not find any significant difference between local and global selection.
+
+Another mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e.
+individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community – provided that cooperation is already at a high frequency.
+Unlike \emph{conditional cooperation}, interaction-transmission association can sustain cooperation in a community even if cooperation is initially rare. 
+\citet{morsky2020false} suggested that false beliefs on the frequencies of the cooperator can affect the individual decision whether to cooperate or not.
+If the individual over-estimates the number of cooperators it will be more likely to cooperate.
+This false belief can help sustain cooperation even if cooperartion is initially rare.
 
@@
 environment''~\citep{Fletcher2009assortment} is generated not because the helper is likely to be helped, but rather because the helped is likely to become a helper.
-
-Another mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e.
-individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community – provided that cooperation is already at a high level.
-Unlike \emph{conditional cooperation}, interaction-transmission association can sustain cooperation in community even if cooperation is initially rare. 
-\citet{morsky2020false} suggested that false beliefs on the frequencies of the cooperator can affect the individual decision whether to cooperate or not.
-If the individual over estimate the number of cooperators it will be more likely to cooperate.
-This false belief can help sustain cooperation even if cooperartion is initially rare.
-% DC: Let's discuss this paragraph - is it good?
 

### 2021-07-18 ms/Thesis/thesis.tex

@@
 \end{equation}
-Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
+Individuals are assumed to interact according to a \emph{Prisoner's Dilemma}.
 Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$.
@@
 the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
-The choise of prisoner's dilemma as the interaction model was motividated by the fact that prisoner's dilemma is a common game used to study evolution of cooperation\citep{axelrod1981evolution}, \citep{milinski1987tit}, \citep{nowak1992tit}.
-Although we decided to focus on prisoner's dilemma, other games such as stag hunt\citep{skyrms2004stag} may be a better explaination of cooperation behavior in humman\citep{tomasello2012two}.
+The choise of Prisoner's Dilemma as the interaction model was motividated by the fact that prisoner's dilemma is a common game used to study evolution of cooperation\citep{axelrod1981evolution}, \citep{milinski1987tit}, \citep{nowak1992tit}.
+Although we decided to focus on Prisoner's Dilemma, other games such as stag hunt\citep{skyrms2004stag} may be a better explaination of cooperation behavior in humman\citep{tomasello2012two}.
 
@@
   \textbf{(a)}~First, offspring inherit their parent's phenotype via vertical cultural transmission with probability $v$, or the phenotype of a random non-parental adult via oblique cultural transmission with probability $1-v$.
-  \textbf{(b)}~Second, adults socially interact in pairs in a prisoner's dilemma game.
+  \textbf{(b)}~Second, adults socially interact in pairs in a Prisoner's Dilemma game.
 Horizontal cultural transmission occurs from a random individual in the population, with probability $1-\alpha$, or from the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
-  \textbf{(c)}~The prisoner's dilemma payoff matrix shows the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
+  \textbf{(c)}~The Prisoner's Dilemma payoff matrix shows the fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
     \textbf{(d)}~The probabilities of successful horizontal cultural transmission of phenotypes $A$ (cooperator) and $B$ (defector) are $T_A$ and $T_B$, respectively.
@@
 initiators interact with a random neighbor (i.e.
-individual in a neighboring site) in a prisoners' dilemma game (\autoref{fig:illustration}c) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
+individual in a neighboring site) in a Prisoner's Dilemma game (\autoref{fig:illustration}c) and a random neighbor (with replacement) for horizontal cultural transmission (\autoref{fig:illustration}b).
 The expected number of each of these interactions per individual per generation is one, but the realized number of interactions can be zero, one, or even more than one, and in every interaction both individuals are affected, not just the initiator.
@@
 \section{Discussion}
-Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a prisoner's dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
+Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a Prisoner's Dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
 Importantly, cooperation can increase when initially rare (i.e. invade a population of defectors) if and only if, rewriting inequality~\ref{eq:unequal_transmission_from_rarity_general_case},
@@
 \citet{woodcock2006significance} stressed the significance of non-vertical transmission for the evolution of cooperation and
-carried out simulations with prisoner's dilemma payoffs but without horizontal transmission or interaction-transmission association ($\alpha=0$).
+carried out simulations with Prisoner's Dilemma payoffs but without horizontal transmission or interaction-transmission association ($\alpha=0$).
 Nevertheless, his results demonstrated that it is possible to sustain altruistic behavior via cultural transmission for a substantial length of time.
@@
 
-In this work, we have studied a cultural evolution model in which interactions are modeled as a prisoner's dilemma game.
+In this work, we have studied a cultural evolution model in which interactions are modeled as a Prisoner's Dilemma game.
 We also assumed that in each generation individuals have only one meaningful interaction.
@@
 successful capturing of the stag\citep{mitani2012evolution}.
+
+In our model we assumed that the model variables such as vertical transmission($v$), horizontal transmission ($T_A \,, T_B$), benfit from cooperartion ($b$) and etc. do not change over time.
+However, in reality things are changing.
+For example, during different time of the year, behavior can be changed due to weather \citep{azcarate2007microclimatic}, predator abundance \citep{briffa2008comparing} and food abundance \citep{johnson2001foraging}.
+This could lead to changes in the model's parameters.
+Further investigation is needed to learn about the effect of this change in behavior.
 

### 2021-07-18 ms/Thesis/thesis.tex
Fix yoav comments on the discussion section

@@
 Kin selection theory posits that natural selection is more likely to favor cooperation between more closely related individuals.
-The importance of \emph{relatedness} to the evolution of cooperation and altruism was demonstrated by \citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benefit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
+The importance of \emph{relatedness} to the evolution of cooperation and altruism was demonstrated by \citet{hamilton1964genetical}, who showed that an allele that determines cooperative behavior will increase in frequency if the reproductive cost to the actor that cooperates, $c$, is less than the benfit to the recipient, $b$, times the relatedness, $r$, between the recipient and the actor.
 This condition is  known as \emph{Hamilton's rule}:
@@
 
-Another mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e.
+In this work, we have studied a cultural evolution model in which interactions are modeled as a Prisoner's Dilemma game.
+We also assumed that in each generation individuals have only one meaningful interaction.
+It would be interesting to investigate a model in which multiple games are played in each generation. 
+This would make the model more realistic and more complicated to solve. To overcome the math complication, numerical simulations can be used. 
+The model can be further expanded by changing the game to Stag Hunt game. \citet{tomasello2012two} claim that Stag Hunt game can better explain evolution of cooperation in humans,
+because humans often collobrate in Stag Hunt type situations in which all participants had alternatives but anticipated an even greater benefit from
+successful capturing of the stag \citep{mitani2012evolution}. Therefore, changing the model so each interaction would be model as Stag Hunt game could help us better understand cooperartion in humans.
+
+In our model we assumed that the model parameters such as vertical transmission($v$), horizontal transmission ($T_A \,, T_B$), benfit from cooperartion ($b$), cost of cooperartion ($c$) and interaction-transmission association ($\alpha$) do not change over time.
+However, in reality things are changing.
+For example, during different time of the year, behavior can be changed due to weather \citep{azcarate2007microclimatic}, predator abundance \citep{briffa2008comparing} and food abundance \citep{johnson2001foraging}.
+This could lead to changes in the model parameters.
+Further investigation is needed to learn about the effect of such changes in behavior.
+
+Mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e.
 individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community – provided that cooperation is already at a high frequency.
@@
 
-In this work, we have studied a cultural evolution model in which interactions are modeled as a Prisoner's Dilemma game.
-We also assumed that in each generation individuals have only one meaningful interaction.
-It would be interesting to investigate a model in which multiple games are played in each generation. 
-This would make the model more realistic and more complicated to solve. To overcome the math complication, a numerical simulations can be used. 
-The model can be further expand by changing the game to Stag Hunt game. \citet{tomasello2012two} claim that Stag Hunt game can better explain evolution of cooperation in humans. 
-Humans often collobrate in Stag Hunt type situations in which all participants had alternatives but anticipated an even greater benefit from
-successful capturing of the stag\citep{mitani2012evolution}.
-
-In our model we assumed that the model variables such as vertical transmission($v$), horizontal transmission ($T_A \,, T_B$), benfit from cooperartion ($b$) and etc. do not change over time.
-However, in reality things are changing.
-For example, during different time of the year, behavior can be changed due to weather \citep{azcarate2007microclimatic}, predator abundance \citep{briffa2008comparing} and food abundance \citep{johnson2001foraging}.
-This could lead to changes in the model's parameters.
-Further investigation is needed to learn about the effect of this change in behavior.
-
 \newpage
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+
 \section{Effect of interaction-transmission association on mean fitness} \label{sec:appendixB}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+\
 \section{Reduction principle} \label{sec:appendixC}
@@
 Determining a necessary and sufficient condition for successful invasion is more complicated, requiring analysis of the sign of $R'(1)$.
-We did it in the general case (starting from \autoref{eq:value_at_1_derivative}).
+We did it in the general case (starting from \autoref{eq:value_at_1_derivative_simplify}).
 

### 2021-07-18 ms/Thesis/thesis.tex
add first page

@@
 %\usepackage{endfloat}
+
+\usepackage{datetime}
+\newdateformat{monthyeardate}{%
+  \monthname[\THEMONTH], \THEYEAR}
 
@@
 \begin{document}
-\maketitle
-
-\pagebreak
-{\large This work was carried out under the supervision of \textbf{Dr. Yoav Ram} from the School of Zoology, Faculty of Life Sciences, Tel Aviv University.}
-\pagebreak
+\begin{titlepage}
+	\centering
+	\includegraphics[width=0.4\textwidth]{IDC_logo}\par\vspace{1cm}
+	{\huge Interdisciplinary Center Herzliya \par}
+	{\Large Efi Arazi School of Computer Science \par}
+	{\Large M.Sc. Program - Research Track \par}
+
+	\vspace{1.5cm}
+	{\Huge Non-Vertical Cultural 
+  Transmission, 
+  Assortment, and the 
+  Evolution of 
+  Cooperation \par}
+	\vspace{1.5cm}
+	{\large by\par}
+	{\Large\bfseries Dor Cohen\par}
+	\vspace{1cm}
+	{\large Supervised by Dr. Yoav Ram\par}
+	{School of Zoology, Faculty of Life Sciences, Tel Aviv University\par}
+
+	\vspace{1cm}
+	{M.Sc. dissertation, submitted in partial fulfillment of the requirements\par}
+	{for the M.Sc. degree, research track, School of Computer Science\par}
+	{Interdisciplinary Center Herzliya}
+
+	\vspace{1cm}
+	% Bottom of the page
+	{\large \monthyeardate\today \par}
+
+\end{titlepage}
 
@@
 successful capturing of the stag \citep{mitani2012evolution}. Therefore, changing the model so each interaction would be model as Stag Hunt game could help us better understand cooperartion in humans.
-
+e
 In our model we assumed that the model parameters such as vertical transmission($v$), horizontal transmission ($T_A \,, T_B$), benfit from cooperartion ($b$), cost of cooperartion ($c$) and interaction-transmission association ($\alpha$) do not change over time.

### 2021-07-23 ms/Thesis/thesis.tex
formatting; ackwoledgements

@@
 \usepackage{lipsum}  
-\usepackage[title,page]{appendix}
+\usepackage[title,page,titletoc]{appendix}
 \usepackage{chngcntr}
 %\usepackage{endfloat}
+\usepackage[nottoc,numbib]{tocbibind} % bibliography in toc
 
@@
 % Line Spacing 
-\linespread{1.25}
-
-% Species names
-%% Meta-Command for defining new species macros
-\usepackage{xspace}
-
-\newcommand{\species}[3]{%
-  \newcommand{#1}{\gdef#1{\textit{#3}\xspace}\textit{#2}\xspace}}
-
-\species{\yeast}{Saccharomyces cerevisiae}{S.~cerevisiae}
-\species{\calbicans}{Candida albicans}{C.~albicans}
-\species{\cneoformans}{Cryptococcus neoformans}{C.~neoformans}
+\linespread{1.5}
 
 % line numbers
-\usepackage[displaymath, mathlines]{lineno}
-\renewcommand\linenumberfont{\normalfont\small\sffamily}
-\linenumbers
-\modulolinenumbers[2]
+%\usepackage[displaymath, mathlines]{lineno}
+%\renewcommand\linenumberfont{\normalfont\small\sffamily}
+%\linenumbers
+%\modulolinenumbers[2]
 
@@
 % Title page
-\title{Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation}
+\title{Non-Vertical Cultural Transmission, Assortment, and the Evolution of Cooperation}
 
@@
   Cooperation \par}
-	\vspace{1.5cm}
+%	\vspace{1cm}
 	{\large by\par}
@@
 	% Bottom of the page
-	{\large \monthyeardate\today \par}
+	{\large \today \par}
 
@@
 
-{\huge \begin{center} \textbf{Abstract} \end{center}}
-
+% Abstract
+\begin{abstract}
 Cultural evolution of cooperation under vertical and non-vertical cultural transmission is studied, and conditions are found for fixation and coexistence of cooperation and defection. 
@@
 Parallels are drawn with Hamilton's rule incorporating relatedness and assortment.
-
-\pagebreak
+\end{abstract}
+
+%\pagebreak
 
@@
 \cite{foster2006kin} argue that kin selection does not ignore ecology.
-Hamilton’s rule shows that environmental factors causing a high benefit: cost ratio will favour cooperation.
-
+Hamilton's rule shows that environmental factors causing a high benefit: cost ratio will favour cooperation.\\
 Beside kin selection, two other major theroies were suggested to explain to evolution of cooperation.
@@
 where \emph{n} is the maximum group size and \emph{m} is the number of groups.
-\\
 
@@
 Such assortative meeting may be due, for example, to population structure or active partner choice.
-In their model, cooperative behavior can evolve if
-\citep[eq.~3.2]{Eshel1982}
+In their model, cooperative behavior can evolve if~\citep[eq.~3.2]{Eshel1982}
 \begin{equation} \label{eq:eshel1982}
@@
 \citet{sacks1967stable} even showed that natural selection at a diploid locus model, when relative fitnesses of the different genotypes are functions of gene frequency, leads to stable equilibrium gene frequencies that corresponds to not maximum mean fitness.
-Instead of searching for evolutionarily stable strategies, we focus on \emph{evolutionary genetic stblility (EGS)}\citep{lessard1990evolutionary}.
+Instead of searching for evolutionarily stable strategies, we focus on \emph{evolutionary genetic stblility (EGS)}~\citep{lessard1990evolutionary}.
 EGS occurs when the frequencies of types (genotypes, phenotypes etc.) remains stable.
@@
 % Models
-\newpage
+%\newpage
 \section{Models}
 
-\subsection{Basic Model}
+\subsection{Basic model}
 \label{section:basicmodel}
@@
 
-\subsection{Invasion Model}
+\subsection{Modifier model}
 In this section, we extend the model described in \autoref{section:basicmodel}. 
-We assume coexistence of both phenotypes (cooperators and defectors) and that the frequency of each phenotye stays stable over time.
+We assume coexistence of both phenotypes (cooperators and defectors) and that the frequency of each phenotype stays stable over time.
 Hence, we assume that the we start from a stable equilibrium. Denote the frequency of cooperators in the population as $\hat{p}^*$ and frequency of defectors as $1-\hat{p}^*$.
@@
   \includegraphics[width=0.7\textwidth]{../PRSB_figures/fig_2.pdf}
-  \caption{\textbf{Invasion model illustration.} Starting from stable equilibrium with coexistence of both phenotypes. 
-  A mutation that affected only the interaction-transmission association $\alpha$ invades the population }
+  \caption{\textbf{Modifier model illustration.} Starting from stable equilibrium with coexistence of both phenotypes (red and green) and the resident modifier allele with interaction-transmission association $\alpha_1$.
+  An invading modifier allele that modifies the interaction-transmission association to $\alpha_2$ invades the population.
+  }
   \label{fig:invasion_illustration}
@@
 \newpage
-\subsection{Population structure model}
+\subsection{Spatial model}
 \label{sec:spatialModel}
@@
 
-\newpage
+%\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% Results
-\newpage
+%\newpage
 \section{Results}
@@
 \end{equation}
+\\
 
@@
   \centering       
-    \includegraphics[width=1\textwidth]{../PRSB_figures/fig_3.pdf}
+    \includegraphics[width=0.9\textwidth]{../PRSB_figures/fig_3.pdf}
     \caption{\textbf{Evolution of cooperation under vertical, oblique, and horizontal cultural transmission.} 
@@
   \centering       
-	\includegraphics[width=1\textwidth]{../PRSB_figures/fig_4.pdf}
+	\includegraphics[width=0.9\textwidth]{../PRSB_figures/fig_4.pdf}
     \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
@@
     \includegraphics[scale=0.5]{../PRSB_figures/fig_5.pdf}
-    \caption{\textbf{Unstable and stable equilibrium dynamics} 
+    \caption{\textbf{Unstable and stable equilibrium dynamics.} 
     The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
-    In \textbf{(a)} the system has unstable equilibrium and therefore, all the curves are moving away from it.
-    In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
-    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b)} $T_B=0.7$, $\alpha=0.6$ and $b=2.3$.}
+    \textbf{(a)} The system has an unstable equilibrium and therefore all the curves are moving away from it.
+    \textbf{(b)} The system has a stable equilibrium and therefore all the curves moves towards it. 
+    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b)} $T_B=0.7$, $\alpha=0.6$ and $b=2.3$.
+    }
     \label{fig:time_series}
@@
 In addition, we also saw that $\frac{\partial R(1)}{\partial \epsilon} > 0$ for every $\epsilon$ which makes $\alpha_2<\alpha_1$ necessary and sufficient condition for successful invasion (external instability).
+\\
 
@@
 \end{figure}
-\newpage
+%\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\newpage
+%\newpage
 
 %%% Figure: Spatial model - global selection
-\begin{figure}[h]
+\begin{figure}[p]
   \centering
@@
 
-\newpage
+%\newpage
 
 %%% Figure: Spatial model - local selection
-\begin{figure}[h]
+\begin{figure}[p]
   \centering
@@
 % Discussion
-\newpage
+%\newpage
 \section{Discussion}
+
 Under a combination of vertical, oblique, and horizontal transmission with payoffs in the form of a Prisoner's Dilemma game, cooperation or defection can either fix or coexist, depending on the relationship between the cost and benefit of cooperation, the horizontal transmission bias, and the association between social interaction and horizontal transmission (Result~\ref{result:vert_obli_hori}, Figures~\ref{fig:equilibria} and~\ref{fig:equilibria_v1}).
@@
 Mechanism that was suggested by \citet{traxler2011social} showed that \emph{conditional cooperation} based on norm-dependent relational utilities, i.e.
-individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community – provided that cooperation is already at a high frequency.
+individual will only cooperate if it knows that others will cooperate too, can sustain cooperation in a community|provided that cooperation is already at a high frequency.
 Unlike \emph{conditional cooperation}, interaction-transmission association can sustain cooperation in a community even if cooperation is initially rare. 
@@
 
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \pagebreak
+% Acknowledgements
+{\small
+\section*{Acknowledgements}
+We thank Lilach Hadany, Ayelet Shavit, and Kaleda Krebs Denton for discussions and comments.
+This work was supported in part by
+the Clore Foundation Scholars Programme (OLE),
+the Morrison Institute for Population and Resources Studies at Stanford University (MWF),
+Israel Science Foundation (YR 552/19),
+and Minerva Stiftung Center for Lab Evolution (YR).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Bibliography
+\newpage
+{\small
 \begingroup
@@
 \endgroup
+}
 
